### 2021-02-25 publication_materials/ms_rbc.tex
plotting tools

\documentclass[reprint,amsmath,amssymb,aps]{revtex4-1}

\usepackage{graphicx}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{gensymb}
\usepackage{enumerate}
\usepackage{varwidth}

\usepackage[usenames, dvipsnames]{color}
\newcommand{\note}[1]{\noindent \textbf{\textit{\textcolor{Red}{#1}}}}

\newcommand\mnras{\rmfamily{Mon. Not. R. Astron. Soc.}}
\newcommand\aap{\rmfamily{Astron. Astrophys.}}
\newcommand\apjl{\rmfamily{Astrophys. J. Lett.}}

\newcommand\Beq{\begin{eqnarray}} 
\newcommand\Eeq{\end{eqnarray}}

\newcommand\Bfig{\begin{figure}} 
\newcommand\Efig{\end{figure}}

\newcommand\Ra{\mathrm{Ra}}
\newcommand\Pran{\mathrm{Pr}}
\newcommand\Rac{\mathrm{Ra}_{\mathrm{c}}}
\newcommand\Ek{\mathrm{Ek}}
\newcommand\Ro{\mathrm{Ro}}
\newcommand\Nu{\mathrm{Nu}}
\newcommand\Sc{\mathrm{Sc}}

\newcommand\eps{\varepsilon}
\renewcommand\L {\mathcal{L}}

\newcommand{\n}{\\ \nonumber \\ }
\newcommand{\nn}{\nonumber}
\newcommand{\nnn}{\\ \nonumber \\ \nonumber}

\newcommand\ie{\textit{i.e.},~}
\newcommand\eg{\textit{e.g.},~}
\newcommand{\omicron}{o}

\newcommand{\pd}[1]{\partial_{#1}}
\renewcommand{\vec}[1]{\boldsymbol{#1}}
\newcommand{\M}[1]{\mathbf{#1}}
\newcommand{\grad}{\vec{\nabla}}
\newcommand{\cross}{\vec{\times}}
\newcommand{\laplacian}{\nabla^2}

\newcommand{\sump}[2]{\sideset{}{'}\sum_{{#1}=0}^{#2}}

\newcommand{\eq}[1]{eq.~(\ref{#1})}
\newcommand{\eqs}[2]{eqs.~(\ref{#1})~\&~(\ref{#2})}
\newcommand{\eqss}[2]{eqs.~(\ref{#1})--(\ref{#2})}

\newcommand{\Eq}[1]{Eq.~(\ref{#1})}
\newcommand{\Eqs}[2]{Eqs.~(\ref{#1})~\&~(\ref{#2})}
\newcommand{\Eqss}[2]{Eqs.~(\ref{#1})--(\ref{#2})}

\newcommand{\fig}[1]{Fig.~(\ref{#1})}
\newcommand{\figs}[2]{Figs.~(\ref{#1})~\&~(\ref{#2})}
\newcommand{\T}{{\cal T}}
\newcommand{\Z}{{\cal Z}}

\bibliographystyle{apsrev4-1}

\makeatletter
\let\Hy@backout\@gobble
\makeatother

\newcommand*{\GtrSim}{\smallrel\gtrsim}

\makeatletter
\newcommand*{\smallrel}[2][.8]{%
  \mathrel{\mathpalette{\smallrel@{#1}}{#2}}%
}
\newcommand*{\smallrel@}[3]{%
  % #1: scale factor
  % #2: math style
  % #3: symbol
  \sbox0{$#2\vcenter{}$}%
  \dimen@=\ht0 %
  \raise\dimen@\hbox{%
    \scalebox{#1}{%
      \raise-\dimen@\hbox{$#2#3\m@th$}%
    }%
  }%
}
\makeatother

\begin{document}

\title{Marginally-Stable Thermal Equilibria of Rayleigh-Bénard Convection}

\author{Sharrod Brown}
\affiliation{%
Senator (D), Ohio}

% \author{Daniel Lecoanet}
% \affiliation{%
% Physics Department, University of California, Berkeley, CA 94720, USA\\
% Astronomy Department and Theoretical Astrophysics Center, University of California, Berkeley, CA 94720, USA\\
% Princeton Center for Theoretical Science, Princeton University, Princeton, NJ 08544, USA\\
% Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA\\
% Kavli Institute for Theoretical Physics, University of California, Santa Barbara, CA 93106, USA}

% \author{Rich R. Kerswell}
% \affiliation{%
% DAMTP, Centre for Mathematical Sciences, Cambridge University, Cambridge CB3 0WA, UK \\
% School of Mathematics, University of Bristol, Bristol BS8 1TW, UK\\
% Kavli Institute for Theoretical Physics, University of California, Santa Barbara, CA 93106, USA}
% \date{\today}% It is always \today, today,
%              %  but any date may be explicitly specified

\begin{abstract}

A novel iterative time-marching method is derived by introducing time-dependence in the background temperature profile of the classical Rayleigh-B\'enard Boussinesq linear stability analysis. Eigenfunction amplitudes are obtained by requiring marginal-stability. Symmetric thermally-equilibrated states are then obtained and their intrinsic properties are analyzed. Such states are compared with statistically-steady 2-dimensional Rayleigh-Be\'nard convection simulations: marginally-stable thermally-equilibrated states have thinner boundary layers which scale like $\delta \sim Ra^{-1/3}$. 2-dimensional simulations run with thermally-equilibrated initial conditions turn out to be kinetically exaggerated, consequently requiring increased computational expense when compared to the conventional diffusive initial condition.

\end{abstract}

\maketitle

\section{Introduction}

The introduction leads the reader from a general subject area to a particular topic of inquiry. It establishes the scope, context, and significance of the research being conducted by summarizing current understanding and background information about the topic, stating the purpose of the work in the form of the research problem supported by a hypothesis or a set of questions, explaining briefly the methodological approach used to examine the research problem, highlighting the potential outcomes your study can reveal, and outlining the remaining structure and organization of the paper.

% \section{Procedures}\label{sec:procedures}
\section{Conventional Boussinesq Linear Stability Analysis}\label{sec:boussinesq}
We begin with the non-dimensionalized Boussinesq approximation for Rayleigh-Bénard Convection. The domain is 2-dimensional rectangular and horizontally periodic with spatial dimensions $x$ and $z$ where $0 < x < 4$ and $-1/2 < z < 1/2$. The fluid of interest is constrained between two planar boundaries at $z = -1/2$ and $z = 1/2$ with fixed temperatures $1$ and $0$ respectively. At both boundaries we specify impenetrable, no-slip conditions, such that the velocity $\mathbf{u} = u \hat{x} + w \hat{z} = \mathbf{0}$ at $z = \pm 1/2$. The equations of motion are then given by
\begin{align}
    \nabla \cdot \mathbf{u} &= 0 \label{EQ:motion1}\\
    \frac{\partial \mathbf{u}}{\partial t} + \mathbf{u} \cdot \nabla \mathbf{u} &= - \nabla p + T \hat{z} + \sqrt{\frac{Pr}{Ra}} \nabla^2 \mathbf{u} \label{EQ:motion2}\\
    \frac{\partial T}{\partial t} + \mathbf{u} \cdot \nabla T &= \frac{1}{\sqrt{RaPr}} \nabla^2 T \label{EQ:motion3}
\end{align}
where $p$ is pressure and $T$ is temperature. For completeness, we specify a final boundary condition $p = p_0$ at $z = \pm 1/2$. Any system of this form can be characterized by its Rayleigh number $Ra$ and Prandtl number $Pr$, where $Ra$ is the timescale ratio of thermal diffusion to convection and $Pr$ is the ratio of momentum diffusivity to thermal diffusivity.  For convenience, we define 
\begin{equation}
\mathcal{R} = \sqrt{\frac{Pr}{Ra}}, \qquad \mathcal{P} = \frac{1}{\sqrt{Pr Ra}}
\end{equation}
\par To derive the linearized system, we posit that each field can be represented as the sum of a background profile (denoted by $\bar{\cdot } \;$) and a perturbation function (denoted by $\cdot'$). Suppose $\frac{\partial \bar{T}}{\partial z}\big|_{t=t_0} (z)$ is some given function which satisfies
\begin{equation}
    \int_{-\frac{1}{2}}^{\frac{1}{2}} \frac{\partial \bar{T}}{\partial z}\Big|_{t=t_0} dz = -1
\end{equation}
then the background profiles are given by
\begin{align}
    \mathbf{\bar{u}} &= \mathbf{0} \\
    \bar{T}(z) &= 1 + \int_{-\frac{1}{2}}^{z} \frac{\partial \bar{T}}{\partial \zeta}\Big|_{t=t_0}(\zeta) d\zeta \\
    \bar{p}(z) &= p_0 - \int_{-\frac{1}{2}}^z \bar{T}(\zeta) d\zeta
\end{align}
Accordingly, the fields are rewritten as
\begin{align}
    \mathbf{u}(x, z, t) &= \mathbf{u'}(x, z, t) \label{EQ:reynolds_dc_u}\\
    &= u'(x, z, t)\hat{x} + w'(x, z, t)\hat{z} \\
    T(x, z, t) &= \bar{T}(z) + T'(x, z, t) \label{EQ:reynolds_dc_T}\\
    p(x, z, t) &= \bar{p}(z) + p'(x, z, t)
\end{align}
Upon substitution, we equate terms which scale linearly with the perturbations, yielding the linearized stability equations
\begin{align}
    \nabla \cdot \mathbf{u'} &= 0 \label{EQ:linear1}\\
    \frac{\partial\mathbf{u'}}{\partial t} &= - \nabla p' + T'\hat{z} + \mathcal{R} \nabla^2 \mathbf{u'} \label{EQ:linear2}\\
    \frac{\partial T'}{\partial t} + \frac{\partial \bar{T}}{\partial z} w' &= \mathcal{P} \nabla^2 T' \label{EQ:linear3}
\end{align}
with Dirichlet boundary conditions 
\begin{equation}
    T'|_{z = \pm \frac{1}{2}} = 0, \quad u'|_{z = \pm \frac{1}{2}} = 0, \quad p'|_{z = \pm \frac{1}{2}} = 0
\end{equation}
In 1916, Lord Rayleigh observed that (\ref{EQ:linear1}) and (\ref{EQ:linear3}) can be manipulated into a separable form with generalized solutions
\begin{align}
    w'(x, z, t) &= W(z) \, e^{i(k_xx-st)} \label{EQ:normal_modes1}\\ 
    u'(x, z, t) &= U(z) \, e^{i(k_xx-st)} \label{EQ:normal_modes2}\\ 
    T'(x, z, t) &= \Theta(z) \, e^{i(k_xx-st)} \label{EQ:normal_modes3}\\ 
    p'(x, z, t) &= P(z) \, e^{i(k_xx-st)}\label{EQ:normal_modes4}
\end{align}
where $s = \sigma + i\omega$ and $k_x$ is constricted by periodicity to the countably infinite set (spectrum) of wavenumbers
\begin{align}
    k_x \in \big\{\frac{n\pi}{2} \, \big| \, n \in \mathbb{N}\big\}
\end{align}
For each $k_x$, we can assess the stability of the perturbations by solving for the eigenvalue $s$, whose imaginary component $\omega$ plays the role of an exponential growth rate. Solution yields a finite set of eigenvalues, among which, that with the maximum value of $\omega$ is assumed to be dominant. Positive eigenvalues indicate that the system is unstable to small disturbances of wavenumber $k_x$, while negative eigenvalues indicate stability. A complete linear stability analysis requires that we solve over the full spectrum of wavenumbers. The prototypical case is used to demonstrate that the critical Rayleigh number $Ra_c = 1708$ when $\frac{\partial \bar{T}}{\partial z}\big|_{t=t_0} = -1$.

\section{Temperature profile evolution}\label{sec:evolution}
For this investigation, we allow $ \bar{T}$ to vary in $z$ and $t$. Substituting (\ref{EQ:reynolds_dc_T}) into (\ref{EQ:motion3}) yields
\begin{align}
    \frac{\partial \bar{T}}{\partial t} + \mathbf{u}' \cdot \nabla T' + \frac{\partial T'}{\partial t} + \frac{\partial \bar{T}}{\partial z} w' = \mathcal{P} \nabla^2 T' + \mathcal{P} \nabla^2 \bar{T}.
    \label{EQ:T't_xz}
\end{align}
Subtracting (\ref{EQ:linear3}) from (\ref{EQ:T't_xz}) eliminates several terms. We can replace the advective term $\mathbf{u}' \cdot \nabla T'$ with $\grad \cdot (\mathbf{u}'T')$ due to (\ref{EQ:linear1}). Taking the horizontal average of (\ref{EQ:T't_xz}), this advective term can be reduced to
\begin{align}
    \frac{1}{4}\int_0^4 \grad \cdot (\mathbf{u}'T') dx &= \frac{\partial }{\partial z}  \langle w'T' \rangle
\end{align}
where $\langle \cdot \rangle$ denotes the horizontal average. The remaining terms in (\ref{EQ:T't_xz}) are unaffected as they are independent of $x$. The eigenfunctions $W(z),\, U(z),\, \Theta(z),$ and $P(z)$ do not admit any natural normalization, as (\ref{EQ:linear1}) - (\ref{EQ:linear3}) and their subsequent forms are linear with respect to the perturbations. For completeness, we provide the normalization 
\begin{equation}
    \int_{-\frac{1}{2}}^{\frac{1}{2}} \big| \Theta (z) \big| dz = 1
\end{equation}
and assign each perturbation a yet-unknown amplitude $A \in \mathbb{R}$, thereby allowing us to rewrite (\ref{EQ:T't_xz}) as an initial value problem (IVP)
\begin{equation}
    \frac{\partial \bar{T}}{\partial t} + A^2 \langle w'T' \rangle = \mathcal{P}  \frac{\partial^2 \bar{T}}{\partial z^2} \label{EQ:T0_IVP}
\end{equation}
upon which the remainder of this investigation is centered. It is important to keep in mind that the forcing term $\langle w'T' \rangle$ is obtained by solving an eigenvalue problem (EVP) which itself involves $\frac{\partial \bar{T}}{\partial z}$. We assume that stable modes do not affect the evolution of $\bar{T}$.
\par For various $Ra$ and fixed $Pr = 1$, we seek symmetric, marginally-stable temperature profiles $\bar{T}_{eq}(z)$ which are thermally equilibrated, thereby satisfying $\frac{\partial \bar{T}_{eq}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}). We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:boussinesq} as well as the IVP (\ref{EQ:T0_IVP}) by representing each field with a dealiased Chebshev polynomial basis. The necessary number of basis functions varies, as temperature profiles associated with large Rayleigh numbers require increasingly small-scale structures to resolve their aggressive boundary layers. We supplement \texttt{Dedalus} with the \texttt{Eigentools} package to obtain the eigenfunctions in (\ref{EQ:T0_IVP}).
\par To find an equilibrated profile, we begin with a marginally-stable initial profile $\bar{T}_0(z)$ whose construction is outlined in \ref{sec:initial_profile}. We seek to evolve $\bar{T}_0(z)$ into a new marginally-stable profile $\bar{T}_1(z)$ according to (\ref{EQ:T0_IVP}) using forward-Euler. This generally involves a unique and unknown value $A^2 > 0$. Our method of finding $A^2$ is best illustrated through example.

\begin{figure}[h]
    \includegraphics[width=3.4in]{EV_spectrum_ol.png}
    \caption{Eigenvalue spectra for $Ra = 10^5$. The spectrum of a marginally-stable background temperature profile $\bar{T}_0$ (shown in black) has a maximum eigenvalue of 0. Given a small constant timestep $\Delta t$, diffusion destabilizes the system, increasing its eigenvalues (shown in blue). Advection tends to stabilize the system, decreasing its eigenvalues (shown in red). It follows that there exists some proportion ($A^2$) of these two terms which yields a new marginally-stable background temperature profile $\bar{T}_1$, whose spectrum is shown in green.}
    \label{fig:iteration_spectra} 
\end{figure}

An iteration is performed as follows: diffusing a marginally-stable temperature profile $\bar{T}_0$ tends to increase its eigenvalues. Ignoring the diffusive term and evolving according to advection tends the stabilize the system. The appropriate amplitude $A^2$ can then be approximated by
\begin{equation}
    A^2 \sim -\frac{\omega_{\rm{diff}}}{\omega_{\rm{adv}}}
\end{equation}
where $\omega_{\rm{diff}}$ and $\omega_{\rm{adv}}$ refer to the diffused and advected eigenvalues (corresponding to the blue and red points respectively at $k_x = \pi$ in Figure \ref{fig:iteration_spectra}) of the previously marginal mode. $\bar{T}_0$ is then evolved according to (\ref{EQ:T0_IVP}) and another eigenvalue solve is performed on the evolve temperature profile. Given a fixed timestep $\Delta t$, we assume the dominant eigenvalue can be described by a smooth function $\omega (A^2)$. Newton's method is used to find the appropriate amplitude by approximating $\omega'(A^2)$ with 1st-order finite-differences and specifying a tolerance $1e-9$. The dominant mode is not fixed; an iteration can facilitate the transfer of marginal-stability from one mode to another. In section \ref{sec:multiple_modes} we specify procedures for the treatment of multiple simultaneously marginal modes.

\subsection{Initial buoyancy profile} \label{sec:initial_profile}
In an attempt to minimize the required number of iterations, we employ the analytical thermal boundary layer equation for turbulent Rayleigh-B\'enard convection given by \ref{ref:BL_EQs}
\begin{align}
    \bar{T}_0(\xi) &= \frac{\sqrt{3}}{4\pi} \log \frac{(1 + a\xi)^3}{1 + (a\xi)^3} + \frac{3}{2\pi} \arctan \Big( \frac{4\pi}{9}\xi - \frac{1}{\sqrt{3}} \Big) + \frac{1}{4} \nonumber \\
    \xi &= \frac{z}{\delta_0}, \qquad a = \frac{2\pi}{3\sqrt{3}}\label{EQ:T0}
\end{align}
where $\delta_0$ is the boundary layer thickness. We expect that each $\Ra$ is associated with a unique $\delta_0$ for which $\bar{T}_0(z)$ is marginally-stable. It should be noted that when experimenting with different initial profiles, we obtain congruent equilibrated states, suggesting that these states may be unique. An example of (\ref{EQ:T0}) is given by the blue curve in Figure \ref{fig:T0_profiles}.

\subsection{Treatment of multiple marginally-stable modes} \label{sec:multiple_modes}
In most cases, we eventually encounter eigenvalue spectra with multiple simultaneously marginal modes. If ignored, we are forced to reduce the timestep and allow the modes to alternate. Instead, we generalize the advective term in (\ref{EQ:T0_IVP}) to accommodate $N$ simultaneously marginal modes
\begin{equation}
    A^2 \langle w' b' \rangle = \sum_{n = 1}^{N} A^2_{n} \langle w' b' \rangle_{n}
\end{equation}
where  $\langle w' b' \rangle_{n}$ is composed of perturbations associated with $k_x = \frac{n\pi}{2}$. There are now $N$ amplitudes to solve for and $N$ eigenvalues to keep marginally-stable. In general, we expect a function $\mathbf{\omega} \, : \, \mathbb{R}^N \to  \mathbb{R}^N$ to have isolated roots (should they exist). We employ Broyden's method for root-finding in multi-dimensional functions whose derivatives are not explicitly known. Difficulty arises when transitioning between different numbers of marginal modes. Here we rely on $A^2 > 0$ by asserting that a mode which is \textit{close enough} to marginal-stability can be included in the iteration provided that its respective amplitude is positive. Should we converge upon a negative amplitude, that mode is discarded and the iteration is repeated. In general we find that any other course of action fails to equilibrate.

\section{Properties of Thermally Equilibrated States}\label{sec:properties}
Thermally equilibrated states of this kind are solutions to the quasilinear Rayleigh-B\'enard convection equations. For this investigation, we calculate solutions for $Ra$ in the range $10^5 - 10^9$. Thermal equilibrium is synonymous with constant heat flux by (\ref{EQ:T0_IVP}). Solutions are symmetric about $z = 0$ by design. This, combined with the fact that we did initialize a background horizontal flow implies the absence of any nonconstant horizontal flow perturbations.

\begin{figure}[h]
    \centering
    \includegraphics[width=3.4in]{T_profs_na.png}
    \caption{Background temperature profiles $\bar{T}$ for $Ra = 10^8$. The initial profile is given by (\ref{EQ:T0}). The equilibrated curve refers to the background temperature profile of the marginally-stable thermally equilibrated state. The simulation profile is obtained by performing a 2-dimensional nonlinear simulation with \texttt{Dedalus} until thermal and kinetic relaxation. The simulation temperature data are horizontally and time averaged. The initial, equilibrated, and simulation profiles have increasingly relaxed boundary regions (respectively). The equilibrated profile exhibits prominent dips, nested alongside the boundary regions. The purpose of this feature is not well understood.}
    \label{fig:T0_profiles}
\end{figure}

\begin{figure*}[t]
    \centering
    \begin{tabular}{@{}c@{}}
        \includegraphics[width=3.4in]{flux_sup_n.png}
    \end{tabular}
    \begin{tabular}{@{}c@{}}
        \includegraphics[width=3.4in]{EV_spectra_2ra.png}
    \end{tabular}
    \caption{Heat fluxes (left) and eigenvalue spectra (right) of equilibrated states $Ra = 2 \times 10^5$ (top) and $Ra = 10^9$ (bottom). Advection profiles belong to marginally-stable modes. For low $Ra$ a single mode with $k_x = 1.5\pi$ is sufficient to oppose  boundary layer diffusion and facilitate heat flux throughout the bulk of the domain. For large $Ra$, high-wavenumber marginally-stable modes contribute pronounced small-scale advection profiles which tightly hug the thin boundary layers. A combination of these of gradually widening advection profiles is necessary to transition to the $k_x = 1.5\pi$ mode.}
    \label{fig:flux}
\end{figure*}

\par Figure \ref{fig:T0_profiles} gives temperature profiles for $Ra = 10^8$, where the initial profile, given by (\ref{EQ:T0}), is employed at iteration 0; the equilibrated profile corresponds to the thermally relaxed state; and the simulation profile is obtained by performing a nonlinear simulation of (\ref{EQ:motion1})-(\ref{EQ:motion3}) with \texttt{Dedalus}, followed by horizontal and time averaging. The simulation curve is more diffuse than the equilibrated curve, which in turn, is more diffuse than the initial curve. Performing an eigenvalue solve by setting $\bar{T}$ equal to the simulation profile yields positive eigenvalues. Comprehensively, this suggests that thermally-equilibrated states might maximize boundary layer thickness, while subject to the marginal stability constraint.
\par The most resilient and unexpected feature of thermally equilibrated background temperature profiles are the pronounced dips adjacent to the boundary layers. These dips appear in every solution, regardless of $Ra$. Physically, they correspond to thin layers in which the temperature gradient reverses. This counter-diffusion, which opposes the overall heat transfer, is overcome by the coinciding advective flux, shown in Figure \ref{fig:flux}.

Equilibrated states exhibit distinct behaviors for large and small $Ra$. This contrast is illustrated in Figure \ref{fig:flux}, where we give heat flux profiles and eigenvalue spectra for two cases: $Ra = 2 \times 10^5$ and $Ra = 10^9$. For lower $Ra$, there is a single presumed local maximum in the eigenvalue spectrum, whose adjacent modes' advection profiles occupy the bulk of the domain. These states have relaxed boundary regions which gradually subside as the advection becomes the dominant component of the total flux. These transitional regions do not appear in high $Ra$ cases, where the shift from diffusion to advection is sharp, requiring pronounced, small-scale advection profiles belonging to modes adjacent to the third presumed local maximum in the eigenvalue spectrum. Traversing towards the midplane of the domain, we see increasingly thicker advection profiles corresponding the wavenumbers adjacent to the second local maximum, eventually culminating in the dominant $k_x = 1.5\pi$ mode.

\begin{figure}[h]
    \centering
    \includegraphics[width=3.4in]{del_ra.PNG}
    \caption{Boundary layer widths $\delta$ of marginally-stable thermal equilibria. We define the threshold of each boundary layer as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, corresponding to the local extrema of the equilibrated curve in Figure \ref{fig:T0_profiles}. Plotting on a log-log scale, we find $\delta$ and $Ra$ obey a power-law relationship. We also demonstrate that $Ra^{1/3}\delta$ is approximately constant with respect to $Ra$ implying $Ra \propto  \delta^{-3}$, as predicted by \ref{source:???} (scaling arguments literature)}
    \label{fig:bl_ra}
\end{figure}

Thermally equilibrated states with large $Ra$ tend to have a more diverse set of marginal modes as compared to small $Ra$ state. In every case, the $k_x = 1.5\pi$ mode is included and is often unaccompanied by adjacent modes. In Figure \ref{fig:kx_marginals} we give the wavenumbers $k_x$ of marginal modes, color coded accordingly to their adjacency to each other. Marginal modes often appear in neighboring pairs, in which case the larger mode is denoted with an x marker and the smaller mode is denoted with a + marker. In these cases we infer the existence of a local maximum eigenvalue between the two adjacent marginally-stable modes. For $Ra \geq 10^6$, a second branch of marginal modes is introduced as shown in green, increasing according to some power-law with respect to $Ra$. The introduction of this largest branch is likely required to oppose the diffusion of the thinner boundary layers. For $Ra \geq 10^8$, a third branch of modes appears (shown in red), splitting the widening gap between the blue branch and the green branch. This development is associated with the relatively thick advection profiles, filling a niche in the total flux by uniting the sharp advection profiles of the largest branch (green) and the bulk-domain-oriented smallest branch (blue).

\begin{figure}[t]
    \centering
    \includegraphics[width=3.4in]{kx_m_ra1.png}
    \caption{Wavenumbers of marginally-stable modes of thermally equilibrated states. Markers are color-coded according to their adjacent local maxima index in the eigenvalue spectrum. For example, the spectrum corresponding to $Ra = 10^5$ has marginal wavenumbers $k_x = \pi, \, 1.5\pi$ adjacent to a presumed local maximum between these two allowed values. The $Ra = 10^9$ spectrum, shown in lower right corner of Figure \ref{fig:flux}, has three presumed local maxima, with a single marginal mode adjacent to the first maximum ($k_x = 1.5\pi$), two marginal modes adjacent to the second maximum ($k_x = 6\pi, \, 6.5\pi$), and two marginal modes adjacent to the third maximum ($k_x = 23.5\pi, \, 24\pi$). The largest wavenumbers of the green branch obey a power-law relationship with $Ra$}
    \label{fig:kx_marginals}
\end{figure}

\par In general, marginally-stable thermal equilibria can be characterized by their boundary layer thicknesses, from which, the rest of their properties follow. Letting the interior boundary layer threshold be the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, we find that $Ra \propto  \delta^{-3}$ as illustrated in Figure \ref{fig:bl_ra}. This is consistent with Malkus' marginal-stability theory, a scaling argument which perceives the boundary regions as subdomains which are themselves marginally-stable \ref{source:Malkus?}.

\begin{figure}[t]
    \centering
    \includegraphics[width=3.4in]{del_kx_inv.png}
    \caption{For $Ra \geq 10^6$, the maximum marginally-stable wavenumber (corresponding to the green X markers in Figure \ref{fig:kx_marginals}) are inversely related to the boundary layer thicknesses $\delta$. $(\max \{ k_x \})^{-1}$ gives a minimum $x$ length scale for the perturbations, and consequently, the advection. We expect the minimum $z$ length scale to agree with the boundary layer thickness $\delta$ because otherwise the boundary layer would continue to diffuse. This is well illustrated in the lower left corner of Figure \ref{fig:flux}, where the advection profile for $k_x = 24\pi$ is tightly flanked by the surrounding boundary layers. This suggests that the minimum $x$ and $z$ length scales obey some constant ratio.}
    \label{fig:del_inv}
\end{figure}

Nusselt numbers $Nu$ for marginally-stable thermally-equilibrated states and direct numerical simulations are given in Figure \ref{fig:nu_vs_ra}. Marginally-stable $Nu$ exceed simulation $Nu$, in agreement with the differing boundary layer geometries shown in Figure \ref{fig:T0_profiles}. Both datasets exhibit power-law relationships with $Ra$, and more specifically, $Ra \sim Nu^3$ which agrees with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} and the scaling argument given by \ref{source:Malkus}.

\begin{figure*}[t]
    \centering
    \includegraphics[width=7.1in]{nu_ra.PNG}
    \caption{Nusselt numbers are shown for marginally-stable thermally-equilibrated states and statistically-steady nonlinear simulations performed on Equations (\ref{EQ:motion1}) - (\ref{EQ:motion3}) with ??? other spectral methods ???. Both obey power-law relationships with $Ra$, with $Ra \sim Nu^3$ in agreement with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} as well as \ref{source:Malkus} Malkus??? ($\gamma = 3$ marginally-stable boundary layer scaling argument). Marginally-stable states' Nusselt numbers exceed simulation Nusselt numbers. This can be well explained by the contrasting boundary region geometries shown in Figure \ref{fig:T0_profiles}.}
    \label{fig:nu_vs_ra}
\end{figure*}

\section{Simulations with Thermally Equilibrated Initial Conditions}
This is investigation is partially motivated by the prospect of decreasing nonlinear simulation relaxation times by employing thermally-equilibrated initial conditions. Conventionally, (\ref{EQ:motion1}) - (\ref{EQ:motion3}) are solved via direct numerical simulation (DNS) with initial conditions
\begin{align}
    T(x, z)\big|_{t=0} &= 0.5 - z \\
    \mathbf{u}(x, z)\big|_{t=0} &= \mathbf{0} \\
    p(x, z)\big|_{t=0} &= 0
\end{align}
which will hereby be referred to as the conductive initial condition. $t$ in this section now refers to the simulation time as opposed to the thermal equilibration time parameter used previously. We define the equilibrated initial conditions
\begin{align}
    T(x, z)\big|_{t=0} &= \bar{T}(z) + \sqrt{2} \sum_{n=1}^N  A^2_n \text{ Re} \Big[ \Theta_n(z) e^{ik_{x_n}x} \Big] \nonumber \\
    \mathbf{u}(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A^2_n \text{ Re} \Big[\Big( U_n (z) \hat{x} + W_n(z) \hat{z} \Big) e^{ik_{x_n}x} \Big] \nonumber\\
    p(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A^2_n \text{ Re} \Big[P_n (z) e^{ik_{x_n}x}\Big]
\end{align}
\begin{figure}[h]
    \centering
    \includegraphics[width=3.4in]{sim_eq_nu.png}
    \caption{Nusselt numbers of simulations performed at $Ra \, = \, 10^8$ with conventional initial conditions (red) and marginally-stable thermally-equilibrated initial conditions (blue). Simulations launched with thermally-equilibrated states do not undergo a convective-transient period because the characteristic plume structure exists on initialization. This is illustrated by the $Nu$ spike at $t \sim 15$ in the convectional simulation.}
    \label{fig:nu_sim}
\end{figure}
Where $\Theta_n(z), U_n(z), W_n(z), P_n(z); \, A^2; $ and $k_{x_n}$ refer to the complex eigenfunctions, amplitude, and wavenumber at the $n$th marginal mode. The $\sqrt{2}$ factor is necessary normalize the eigenfunctions according to the new domain ???. By construction, these initial conditions are thermally equilibrated. 
Simulations launched with equilibrated initial conditions do not exhibit a convective-transient period, as the large-scale anatomy of the characteristic plumes and convective winds of Rayleigh-B\'enard convection exist on initialization. This is illustrated in Figure \ref{fig:nu_sim}, where the sharp spike in $Nu$ is associated with the turbulent transition period of upwelling until the distinctive jet-like structure is established. 
\par The marginally-stable equilibria are associated with a combination of eigenfunctions whose average kinetic energy is significantly larger than the statistical steady state, as given by Figure \ref{fig:ke_sim}. This is impairs kinetic relaxation because the large horizontal flows decay on a viscous timescale
\begin{equation}
    t_{\nu} \sim \frac{Pr}{\sqrt{Ra}}. \nonumber
\end{equation}
Consequently, marginally-stable thermally-equilibrated initial conditions do not reduce the simulation time required to achieve a statistically steady state, rather, they increase it considerably.
\begin{figure}[h]
    \centering
    \includegraphics[width=3.4in]{sim_eq_ke.png}
    \caption{Average kinetic energies of the same simulations performed in Figure \ref{fig:nu_sim} ($Ra \, = \, 10^8$). The combination of eigenfunctions which give thermal equilibrium have significantly more kinetic energy than the statistically steady state. Kinetic equilibrium is achieved according to the viscous timescale $t_{\nu} \sim Pr Ra^{-1/2}$.}
    \label{fig:ke_sim}
\end{figure}

\section{Conclusion}\label{sec:conclusion}

\section*{Appendix}
This is an appendix

\section*{Acknowledgments}
We thank the people of Ohio.

\bibliography{she}

\end{document}

### 2021-02-25 publication_materials/ms_revised.tex
plotting tools

--- 2021-02-25 publication_materials/ms_rbc.tex
@@
 \usepackage{varwidth}
+\usepackage{{subfig}
 
@@
 
-\title{Marginally-Stable Thermal Equilibria of Rayleigh-Bénard Convection}
+\title{Marginally-Stable Thermal Equilibria of Rayleigh Benard Convection}
 
@@
 
-A novel iterative time-marching method is derived by introducing time-dependence in the background temperature profile of the classical Rayleigh-B\'enard Boussinesq linear stability analysis.
-Eigenfunction amplitudes are obtained by requiring marginal-stability.
-Symmetric thermally-equilibrated states are then obtained and their intrinsic properties are analyzed.
-Such states are compared with statistically-steady 2-dimensional Rayleigh-Be\'nard convection simulations: marginally-stable thermally-equilibrated states have thinner boundary layers which scale like $\delta \sim Ra^{-1/3}$.
-2-dimensional simulations run with thermally-equilibrated initial conditions turn out to be kinetically exaggerated, consequently requiring increased computational expense when compared to the conventional diffusive initial condition.
+Sometimes your professor will ask you to include an abstract, or general summary of your work, with your research paper.
+The abstract allows you to elaborate upon each major aspect of the paper and helps readers decide whether they want to read the rest of the paper.
+Therefore, enough key information [e.g., summary results, observations, trends, etc.] must be included to make the abstract useful to someone who may want to examine your work.
+
+How do you know when you have enough information in your abstract?
+A simple rule-of-thumb is to imagine that you are another researcher doing a similar study.
+Then ask yourself: if your abstract was the only part of the paper you could access, would you be happy with the amount of information presented there?
+Does it tell the whole story about your study?
+If the answer is "no" then the abstract likely needs to be revised.
 
@@
 We begin with the non-dimensionalized Boussinesq approximation for Rayleigh-Bénard Convection.
-The domain is 2-dimensional rectangular and horizontally periodic with spatial dimensions $x$ and $z$ where $0 < x < 4$ and $-1/2 < z < 1/2$.
-The fluid of interest is constrained between two planar boundaries at $z = -1/2$ and $z = 1/2$ with fixed temperatures $1$ and $0$ respectively.
-At both boundaries we specify impenetrable, no-slip conditions, such that the velocity $\mathbf{u} = u \hat{x} + w \hat{z} = \mathbf{0}$ at $z = \pm 1/2$.
+The domain is 2-dimensional rectangular with spatial dimensions $x$ and $z$ where $0 < x < 4$ and $-1/2 < z < 1/2$.
+The fluid is constrained between two planar boundaries at $z = -1/2$ and $z = 1/2$ with fixed temperatures $1$ and $0$ respectively.
+At both boundaries we specify impenetrable and no-slip conditions, such that the velocity $\mathbf{u} = u \hat{x} + w \hat{z} = \mathbf{0}$ at $z = \pm 1/2$.
+The domain is periodic in the horizontal direction.
 The equations of motion are then given by
@@
 \end{align}
-Accordingly, the fields are rewritten as
+Accordingly, we rewrite the fields as
 \begin{align}
@@
 \end{align}
-Upon substitution, we equate terms which scale linearly with the perturbations, yielding the linearized stability equations
+Upon substitution, we equate terms which scale linearly with the perturbations, yielding the following linearized stability equations
 \begin{align}
@@
     \frac{\partial\mathbf{u'}}{\partial t} &= - \nabla p' + T'\hat{z} + \mathcal{R} \nabla^2 \mathbf{u'} \label{EQ:linear2}\\
-    \frac{\partial T'}{\partial t} + \frac{\partial \bar{T}}{\partial z} w' &= \mathcal{P} \nabla^2 T' \label{EQ:linear3}
+    \frac{\partial T'}{\partial t} + \frac{\partial \bar{T}}{\partial z} w' &= \mathcal{P} \nabla^2 T'\label{EQ:linear3}
 \end{align}
-with Dirichlet boundary conditions 
+With Dirichlet boundary conditions 
 \begin{equation}
@@
 \end{align}
-where $s = \sigma + i\omega$ and $k_x$ is constricted by periodicity to the countably infinite set (spectrum) of wavenumbers
+where $s = \sigma + i\omega$ and $k_x$ is restricted by periodicity to the countably infinite set (spectrum) of wavenumbers
 \begin{align}
@@
 For each $k_x$, we can assess the stability of the perturbations by solving for the eigenvalue $s$, whose imaginary component $\omega$ plays the role of an exponential growth rate.
-Solution yields a finite set of eigenvalues, among which, that with the maximum value of $\omega$ is assumed to be dominant.
+Solution generally yields a finite set of eigenvalues, among which, that with the maximum value of $\omega$ is assumed to be dominant.
 Positive eigenvalues indicate that the system is unstable to small disturbances of wavenumber $k_x$, while negative eigenvalues indicate stability.
@@
 Subtracting (\ref{EQ:linear3}) from (\ref{EQ:T't_xz}) eliminates several terms.
-We can replace the advective term $\mathbf{u}' \cdot \nabla T'$ with $\grad \cdot (\mathbf{u}'T')$ due to (\ref{EQ:linear1}).
-Taking the horizontal average of (\ref{EQ:T't_xz}), this advective term can be reduced to
+We can also replace the advective term $\mathbf{u}' \cdot \nabla T'$ with $\grad \cdot (\mathbf{u}'T')$ due to (\ref{EQ:linear1}).
+By taking the horizontal average of (\ref{EQ:T't_xz}), this advective term can be reduced to
 \begin{align}
@@
 The remaining terms in (\ref{EQ:T't_xz}) are unaffected as they are independent of $x$.
-The eigenfunctions $W(z),\, U(z),\, \Theta(z),$ and $P(z)$ do not admit any natural normalization, as (\ref{EQ:linear1}) - (\ref{EQ:linear3}) and their subsequent forms are linear with respect to the perturbations.
+Lastly, it is important to note that the eigenfunctions do not admit any natural normalization, as (\ref{EQ:linear1}) - (\ref{EQ:linear3}) and their subsequent forms are linear with respect to the perturbations.
 For completeness, we provide the normalization
@@
 \end{equation}
-upon which the remainder of this investigation is centered.
+which can be characterized as a nonhomogeneous  1-dimensional diffusion equation, upon which the rest of this investigation is focused.
 It is important to keep in mind that the forcing term $\langle w'T' \rangle$ is obtained by solving an eigenvalue problem (EVP) which itself involves $\frac{\partial \bar{T}}{\partial z}$.
-We assume that stable modes do not affect the evolution of $\bar{T}$.
-\par For various $Ra$ and fixed $Pr = 1$, we seek symmetric, marginally-stable temperature profiles $\bar{T}_{eq}(z)$ which are thermally equilibrated, thereby satisfying $\frac{\partial \bar{T}_{eq}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}).
-We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:boussinesq} as well as the IVP (\ref{EQ:T0_IVP}) by representing each field with a dealiased Chebshev polynomial basis.
-The necessary number of basis functions varies, as temperature profiles associated with large Rayleigh numbers require increasingly small-scale structures to resolve their aggressive boundary layers.
-We supplement \texttt{Dedalus} with the \texttt{Eigentools} package to obtain the eigenfunctions in (\ref{EQ:T0_IVP}).
-\par To find an equilibrated profile, we begin with a marginally-stable initial profile $\bar{T}_0(z)$ whose construction is outlined in \ref{sec:initial_profile}.
-We seek to evolve $\bar{T}_0(z)$ into a new marginally-stable profile $\bar{T}_1(z)$ according to (\ref{EQ:T0_IVP}) using forward-Euler.
-This generally involves a unique and unknown value $A^2 > 0$.
+More specifically, we assume that stable modes do not affect the evolution of $\bar{T}$.
+\par For various Rayleigh numbers and fixed $Pr = 1$, we seek symmetric, marginally-stable temperature profiles $\bar{T}_{eq}(z)$ which are thermally equilibrated, thereby satisfying $\frac{\partial \bar{T}_{eq}}{\partial t} = 0$, according to (\ref{EQ:T0_IVP}).
+We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:boussinesq} as well as the IVP (\ref{EQ:T0_IVP}) by representing each field with a dealiased Chebshev Polynomial basis.
+The required number of basis functions varies, as Temperature profiles associated with higher Rayleigh numbers demand increasingly small-scale structures to resolve their aggressive boundary layers.
+We supplement \texttt{Dedalus} with the \texttt{Eigentools} package to obtain the eigenfunctions included in (\ref{EQ:T0_IVP}).
+\par To find an equilibrated profile, we begin with a marginally-stable initial profile $\bar{T}_0(z)$ which is constructed as described in \ref{sec:initial_profile}.
+We seek to evolve $\bar{T}_0(z)$ into a new marginally-stable profile $\bar{T}_1(z)$ according to (\ref{EQ:T0_IVP}) by using forward-Euler.
+This generally requires a unique and unknown value $A^2 > 0$.
 Our method of finding $A^2$ is best illustrated through example.
@@
     \caption{Eigenvalue spectra for $Ra = 10^5$.
-The spectrum of a marginally-stable background temperature profile $\bar{T}_0$ (shown in black) has a maximum eigenvalue of 0.
-Given a small constant timestep $\Delta t$, diffusion destabilizes the system, increasing its eigenvalues (shown in blue).
-Advection tends to stabilize the system, decreasing its eigenvalues (shown in red).
-It follows that there exists some proportion ($A^2$) of these two terms which yields a new marginally-stable background temperature profile $\bar{T}_1$, whose spectrum is shown in green.}
+The spectrum of a marginally-stable background temperature profile $\bar{T}_0$ has a maximum eigenvalue of 0.
+Given a small constant timestep $\Delta t$, diffusion destabilizes the system, increasing its eigenvalues.
+Advection tends to stabilize the system, decreasing its eigenvalues.
+It follows that there exists some proportion ($A^2$) of these two terms which yields a new marginally-stable background temperature profile $\bar{T}_1$ when the original profile $\bar{T}_0$ is evolved according to (\ref{EQ:T0_IVP}).}
     \label{fig:iteration_spectra} 
@@
 
-An iteration is performed as follows: diffusing a marginally-stable temperature profile $\bar{T}_0$ tends to increase its eigenvalues.
+In Figure \ref{fig:iteration_spectra} we perform an iteration as follows: diffusing a marginally-stable temperature profile $\bar{T}_0$ tends to increase its eigenvalues.
 Ignoring the diffusive term and evolving according to advection tends the stabilize the system.
@@
 \begin{equation}
-    A^2 \sim -\frac{\omega_{\rm{diff}}}{\omega_{\rm{adv}}}
+    A^2 \sim -\frac{\omega_{diff}}{\omega_{adv}}
 \end{equation}
-where $\omega_{\rm{diff}}$ and $\omega_{\rm{adv}}$ refer to the diffused and advected eigenvalues (corresponding to the blue and red points respectively at $k_x = \pi$ in Figure \ref{fig:iteration_spectra}) of the previously marginal mode.
-$\bar{T}_0$ is then evolved according to (\ref{EQ:T0_IVP}) and another eigenvalue solve is performed on the evolve temperature profile.
-Given a fixed timestep $\Delta t$, we assume the dominant eigenvalue can be described by a smooth function $\omega (A^2)$.
-Newton's method is used to find the appropriate amplitude by approximating $\omega'(A^2)$ with 1st-order finite-differences and specifying a tolerance $1e-9$.
-The dominant mode is not fixed; an iteration can facilitate the transfer of marginal-stability from one mode to another.
+where $\omega_{diff}$ and $\omega_{adv}$ refer to the diffused and advected eigenvalues of the initially marginally-stable mode respectively.
+$\bar{T}_0$ is then evolved according to (\ref{EQ:T0_IVP}), after which another eigenvalue solve is performed on the evolve temperture profile.
+Given a fixed timestep $\Delta t$, we assume the dominant eigenvalue can be described by a smooth function $\omega (A^2) = \max \{ \omega_{kx} \}$.
+We then employ Newton's method to find the appropriate amplitude by approximating $\omega'(A^2)$ with 1st-order finite-differences and specifying a tolerance $1e-9$.
+The dominant mode is not fixed; an iteration can facilitate the transfer of marginal stability from one mode to another.
 In section \ref{sec:multiple_modes} we specify procedures for the treatment of multiple simultaneously marginal modes.
-
+% How does the EV spectrum respond to diffusion (amplitudes are zero)?
+This is likely due to growth in the boundary layer height.
+How does it respond to advective fluxes of differing wavenumbers (amplitudes are large).
+Point out that the amplitude is not constrained mathematically (but it must be nonnegative!), then use the fact that the new state must be marginally-stable to find the appropriate amplitude(s).
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=3.4in]{b0_evolution.PNG}
+%     \caption{b0z over several iterations}
+%     \label{fig:b0z_iterations}
+% \end{figure}
+% We can do the same with the horizontal momentum equation but in this case we seek symmetrical solutions, implying the mean horizontal flow is zero.
+More investigation is needed for systems with flux-temperature boundary conditions or asymmetrical solutions in general.
+Show b0z evolution fig?
 \subsection{Initial buoyancy profile} \label{sec:initial_profile}
-In an attempt to minimize the required number of iterations, we employ the analytical thermal boundary layer equation for turbulent Rayleigh-B\'enard convection given by \ref{ref:BL_EQs}
+In an attempt to minimize the required number of iterations, we employ the analytical thermal boundary layer equation for turbulent Rayleigh-Benard convection given by \ref{ref:BL_EQs}
 \begin{align}
@@
 where $\delta_0$ is the boundary layer thickness.
-We expect that each $\Ra$ is associated with a unique $\delta_0$ for which $\bar{T}_0(z)$ is marginally-stable.
-It should be noted that when experimenting with different initial profiles, we obtain congruent equilibrated states, suggesting that these states may be unique.
-An example of (\ref{EQ:T0}) is given by the blue curve in Figure \ref{fig:T0_profiles}.
+Anticipating $Ra \sim \delta^{-3}_0$, we expect that each $\Ra$ is associated with a unique $\delta_0$ for which $\bar{T}_0(z)$ is marginally stable.
+It should be noted that while experimenting with different initial profiles, we still obtain congruent equilibrated profiles $\bar{T}_{eq}(z)$, suggesting that these states may be unique.
+An example of (\ref{EQ:T0}) is shown in Figure \ref{fig:b0z_iterations}.
+
+% \begin{figure}[h]
+%     \centering
+%     \includegraphics[width=3.4in]{QG0.png}
+%     \caption{Kx marginals vs sim time or iteration}
+%     \label{fig:my_label}
+% \end{figure}
 
 \subsection{Treatment of multiple marginally-stable modes} \label{sec:multiple_modes}
-In most cases, we eventually encounter eigenvalue spectra with multiple simultaneously marginal modes.
+In most cases, we eventually encounter eigenvalue spectra with multiple marginally stable modes.
 If ignored, we are forced to reduce the timestep and allow the modes to alternate.
@@
 \end{equation}
-where  $\langle w' b' \rangle_{n}$ is composed of perturbations associated with $k_x = \frac{n\pi}{2}$.
-There are now $N$ amplitudes to solve for and $N$ eigenvalues to keep marginally-stable.
+where  $\langle w' b' \rangle_{n}$ is composed of eigenfunctions associated with $k_x = \frac{n\pi}{2}$.
+There are now $N$ amplitudes to solve for and $N$ eigenvalues to keep marginally stable.
 In general, we expect a function $\mathbf{\omega} \, : \, \mathbb{R}^N \to  \mathbb{R}^N$ to have isolated roots (should they exist).
-We employ Broyden's method for root-finding in multi-dimensional functions whose derivatives are not explicitly known.
-Difficulty arises when transitioning between different numbers of marginal modes.
-Here we rely on $A^2 > 0$ by asserting that a mode which is \textit{close enough} to marginal-stability can be included in the iteration provided that its respective amplitude is positive.
+We employ Broyden's method for root-finding in multiple dimensions with discretized data.
+The difficulty arises when transitioning between different numbers of marginal modes.
+Here we rely on $A^2 > 0$ by asserting that a mode which is \textit{close enough} to marginal stability can be included in the iteration provided that its respective amplitude is positive.
 Should we converge upon a negative amplitude, that mode is discarded and the iteration is repeated.
 In general we find that any other course of action fails to equilibrate.
-
+\newline
+% \begin{figure}[t]
+%     \centering
+%     \includegraphics[width=3.1in]{EV_spectrum_lapse2.png}
+%     \caption{Marginally stable eigenvalue spectra: $Ra = 2e9$}
+%     \label{fig:spectra_lapse}
+% \end{figure}
 \section{Properties of Thermally Equilibrated States}\label{sec:properties}
-Thermally equilibrated states of this kind are solutions to the quasilinear Rayleigh-B\'enard convection equations.
-For this investigation, we calculate solutions for $Ra$ in the range $10^5 - 10^9$.
+Thermally equilibrated states of this kind are solutions to the quasilinear Rayleigh Benard convection equations.
+For this investigation, we calculate solutions for Rayleigh numbers in the range $10^5 - 10^9$.
 Thermal equilibrium is synonymous with constant heat flux by (\ref{EQ:T0_IVP}).
@@
 This, combined with the fact that we did initialize a background horizontal flow implies the absence of any nonconstant horizontal flow perturbations.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=3.4in]{T_profs_na.png}
-    \caption{Background temperature profiles $\bar{T}$ for $Ra = 10^8$.
-The initial profile is given by (\ref{EQ:T0}).
-The equilibrated curve refers to the background temperature profile of the marginally-stable thermally equilibrated state.
-The simulation profile is obtained by performing a 2-dimensional nonlinear simulation with \texttt{Dedalus} until thermal and kinetic relaxation.
-The simulation temperature data are horizontally and time averaged.
-The initial, equilibrated, and simulation profiles have increasingly relaxed boundary regions (respectively).
-The equilibrated profile exhibits prominent dips, nested alongside the boundary regions.
-The purpose of this feature is not well understood.}
-    \label{fig:T0_profiles}
-\end{figure}
-
-\begin{figure*}[t]
-    \centering
-    \begin{tabular}{@{}c@{}}
-        \includegraphics[width=3.4in]{flux_sup_n.png}
-    \end{tabular}
-    \begin{tabular}{@{}c@{}}
-        \includegraphics[width=3.4in]{EV_spectra_2ra.png}
-    \end{tabular}
-    \caption{Heat fluxes (left) and eigenvalue spectra (right) of equilibrated states $Ra = 2 \times 10^5$ (top) and $Ra = 10^9$ (bottom).
-Advection profiles belong to marginally-stable modes.
-For low $Ra$ a single mode with $k_x = 1.5\pi$ is sufficient to oppose  boundary layer diffusion and facilitate heat flux throughout the bulk of the domain.
-For large $Ra$, high-wavenumber marginally-stable modes contribute pronounced small-scale advection profiles which tightly hug the thin boundary layers.
-A combination of these of gradually widening advection profiles is necessary to transition to the $k_x = 1.5\pi$ mode.}
-    \label{fig:flux}
-\end{figure*}
-
-\par Figure \ref{fig:T0_profiles} gives temperature profiles for $Ra = 10^8$, where the initial profile, given by (\ref{EQ:T0}), is employed at iteration 0; the equilibrated profile corresponds to the thermally relaxed state; and the simulation profile is obtained by performing a nonlinear simulation of (\ref{EQ:motion1})-(\ref{EQ:motion3}) with \texttt{Dedalus}, followed by horizontal and time averaging.
-The simulation curve is more diffuse than the equilibrated curve, which in turn, is more diffuse than the initial curve.
-Performing an eigenvalue solve by setting $\bar{T}$ equal to the simulation profile yields positive eigenvalues.
-Comprehensively, this suggests that thermally-equilibrated states might maximize boundary layer thickness, while subject to the marginal stability constraint.
-\par The most resilient and unexpected feature of thermally equilibrated background temperature profiles are the pronounced dips adjacent to the boundary layers.
-These dips appear in every solution, regardless of $Ra$.
-Physically, they correspond to thin layers in which the temperature gradient reverses.
-This counter-diffusion, which opposes the overall heat transfer, is overcome by the coinciding advective flux, shown in Figure \ref{fig:flux}.
-
-Equilibrated states exhibit distinct behaviors for large and small $Ra$.
-This contrast is illustrated in Figure \ref{fig:flux}, where we give heat flux profiles and eigenvalue spectra for two cases: $Ra = 2 \times 10^5$ and $Ra = 10^9$.
-For lower $Ra$, there is a single presumed local maximum in the eigenvalue spectrum, whose adjacent modes' advection profiles occupy the bulk of the domain.
-These states have relaxed boundary regions which gradually subside as the advection becomes the dominant component of the total flux.
-These transitional regions do not appear in high $Ra$ cases, where the shift from diffusion to advection is sharp, requiring pronounced, small-scale advection profiles belonging to modes adjacent to the third presumed local maximum in the eigenvalue spectrum.
-Traversing towards the midplane of the domain, we see increasingly thicker advection profiles corresponding the wavenumbers adjacent to the second local maximum, eventually culminating in the dominant $k_x = 1.5\pi$ mode.
+\par In general, marginally-stable thermal equilibria can be characterized by their boundary layer thicknesses, from which, the rest of their properties follow.
+Letting the interior boundary layer threshold be the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, we find that $Ra \propto  \delta^{-3}$ as illustrated in Figure \ref{fig:bl_ra}.
+This is consistent with Malkus' marginal stability theory, a scaling argument which perceives the boundary regions as subdomains which are themselves marginally stable \ref{source:Malkus?}.
 
@@
     \caption{Boundary layer widths $\delta$ of marginally-stable thermal equilibria.
-We define the threshold of each boundary layer as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, corresponding to the local extrema of the equilibrated curve in Figure \ref{fig:T0_profiles}.
-Plotting on a log-log scale, we find $\delta$ and $Ra$ obey a power-law relationship.
+We define the threshold of each boundary layer as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, corresponding to the local extrema of the ``Thermally Equilibrated" curve in Figure \ref{fig:T0_profiles}.
+Plotting on a log-log scale, we find that $\delta$ and $Ra$ obey a power-law relationship.
 We also demonstrate that $Ra^{1/3}\delta$ is approximately constant with respect to $Ra$ implying $Ra \propto  \delta^{-3}$, as predicted by \ref{source:???} (scaling arguments literature)}
@@
 
-Thermally equilibrated states with large $Ra$ tend to have a more diverse set of marginal modes as compared to small $Ra$ state.
-In every case, the $k_x = 1.5\pi$ mode is included and is often unaccompanied by adjacent modes.
-In Figure \ref{fig:kx_marginals} we give the wavenumbers $k_x$ of marginal modes, color coded accordingly to their adjacency to each other.
-Marginal modes often appear in neighboring pairs, in which case the larger mode is denoted with an x marker and the smaller mode is denoted with a + marker.
-In these cases we infer the existence of a local maximum eigenvalue between the two adjacent marginally-stable modes.
-For $Ra \geq 10^6$, a second branch of marginal modes is introduced as shown in green, increasing according to some power-law with respect to $Ra$.
-The introduction of this largest branch is likely required to oppose the diffusion of the thinner boundary layers.
-For $Ra \geq 10^8$, a third branch of modes appears (shown in red), splitting the widening gap between the blue branch and the green branch.
-This development is associated with the relatively thick advection profiles, filling a niche in the total flux by uniting the sharp advection profiles of the largest branch (green) and the bulk-domain-oriented smallest branch (blue).
+\begin{figure*}[t]
+    \centering
+    \subfloat{\includegraphics[width=3.4in]{flux_sup_n.png}}
+    \hfill
+    \subfloat{\includegraphics[width=3.4in]{EV_spectra_2ra.png}}
+    \caption{Heat fluxes (left) and eigenvalue spectra (right) of equilibrated states $Ra = 2 \times 10^5$ (top) and $Ra = 10^9$ (bottom).
+Advection profiles belong to marginally-stable modes.
+For low $Ra$ a single mode with $k_x = 1.5\pi$ is sufficient to oppose  boundary layer diffusion and facilitate heat flux throughout the bulk of the domain.
+For large $Ra$, high-wavenumber marginally-stable modes contribute small-scale advection profiles which tightly hug the thin boundary layers.
+A combination of these of profiles is necessary to transition to the $k_x = 1.5\pi$ mode.}
+    \label{fig:flux}
+\end{figure*}
 
-\begin{figure}[t]
+Equilibrated states exhibit distinct behaviors for large and small $Ra$.
+This contrast is well illustrated in Figure \ref{fig:flux}, where we give heat flux profiles and eigenvalue spectra for two cases: $Ra = 2 \times 10^5$ and $Ra = 10^9$.
+For lower $Ra$, there is a single presumed local maximum in the eigenvalue spectrum, whose adjacent modes' advection profiles occupy the bulk of the domain.
+Accordingly, these states have relaxed boundary regions which gradually diminish as the advection becomes the dominant component of the total flux.
+These transitional regions do not appear in the high $Ra$ cases, where the shift from diffusion to advection is sharp, requiring small-scale advection profiles belonging to modes adjacent to the third presumed local maximum in the eigenvalue spectrum.
+Traversing towards the midplane of the domain, we see increasingly thicker advection profiles corresponding the wavenumbers adjacent to the second local maximum, eventually culminating in the dominant $k_x = 1.5\pi$ mode.
+
+\par The most resilient and unexpected feature of the associated background temperature profiles are the pronounced dips adjacent to the boundary layers.
+These dips appear in every solution, regardless of $Ra$.
+Physically, they correspond to thin layers in which the temperature gradient reverses.
+This counter-diffusion, which opposes the overall heat transfer, is overcome by the coinciding advective flux.
+High-wavenumber modes with large amplitudes oppose the intense diffusion by facilitating heat transfer towards the bulk of the domain via progressively lower wavenumber modes.
+In this bulk region, the $k_x = 1.5\pi$ mode is dominant regardless of $Ra$, suggesting that this mode is particularly important for systems of this kind.
+In the lower Rayleigh number cases, high-wavenumber modes are stable.
+The boundary layers and advective fluxes are relaxed, achieving equilibrium via a gradual transition from diffusion to advection.
+
+% symmetry; batman ears; Nusselt number, BL thickness, and marginal kx's wrt Ra; flux figures w/ corresponding EV spectra; 
+\begin{figure}[h]
     \centering
@@
 
-\par In general, marginally-stable thermal equilibria can be characterized by their boundary layer thicknesses, from which, the rest of their properties follow.
-Letting the interior boundary layer threshold be the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, we find that $Ra \propto  \delta^{-3}$ as illustrated in Figure \ref{fig:bl_ra}.
-This is consistent with Malkus' marginal-stability theory, a scaling argument which perceives the boundary regions as subdomains which are themselves marginally-stable \ref{source:Malkus?}.
-
-\begin{figure}[t]
+\begin{figure}[h]
     \centering
@@
     \caption{For $Ra \geq 10^6$, the maximum marginally-stable wavenumber (corresponding to the green X markers in Figure \ref{fig:kx_marginals}) are inversely related to the boundary layer thicknesses $\delta$.
-$(\max \{ k_x \})^{-1}$ gives a minimum $x$ length scale for the perturbations, and consequently, the advection.
+$\max \{ k_x \}$ gives a minimum $x$ length scale for the perturbations, and consequently, the advection.
 We expect the minimum $z$ length scale to agree with the boundary layer thickness $\delta$ because otherwise the boundary layer would continue to diffuse.
@@
 This suggests that the minimum $x$ and $z$ length scales obey some constant ratio.}
-    \label{fig:del_inv}
+    \label{fig:my_label}
 \end{figure}
 
-Nusselt numbers $Nu$ for marginally-stable thermally-equilibrated states and direct numerical simulations are given in Figure \ref{fig:nu_vs_ra}.
-Marginally-stable $Nu$ exceed simulation $Nu$, in agreement with the differing boundary layer geometries shown in Figure \ref{fig:T0_profiles}.
-Both datasets exhibit power-law relationships with $Ra$, and more specifically, $Ra \sim Nu^3$ which agrees with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} and the scaling argument given by \ref{source:Malkus}.
-
-\begin{figure*}[t]
+\begin{figure*}[h]
     \centering
     \includegraphics[width=7.1in]{nu_ra.PNG}
-    \caption{Nusselt numbers are shown for marginally-stable thermally-equilibrated states and statistically-steady nonlinear simulations performed on Equations (\ref{EQ:motion1}) - (\ref{EQ:motion3}) with ???
-other spectral methods ???.
-Both obey power-law relationships with $Ra$, with $Ra \sim Nu^3$ in agreement with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} as well as \ref{source:Malkus} Malkus???
-($\gamma = 3$ marginally-stable boundary layer scaling argument).
-Marginally-stable states' Nusselt numbers exceed simulation Nusselt numbers.
-This can be well explained by the contrasting boundary region geometries shown in Figure \ref{fig:T0_profiles}.}
+    \caption{Nusselt number of iterative marginal convection solutions.}
     \label{fig:nu_vs_ra}
 \end{figure*}
-
-\section{Simulations with Thermally Equilibrated Initial Conditions}
-This is investigation is partially motivated by the prospect of decreasing nonlinear simulation relaxation times by employing thermally-equilibrated initial conditions.
-Conventionally, (\ref{EQ:motion1}) - (\ref{EQ:motion3}) are solved via direct numerical simulation (DNS) with initial conditions
-\begin{align}
-    T(x, z)\big|_{t=0} &= 0.5 - z \\
-    \mathbf{u}(x, z)\big|_{t=0} &= \mathbf{0} \\
-    p(x, z)\big|_{t=0} &= 0
-\end{align}
-which will hereby be referred to as the conductive initial condition.
-$t$ in this section now refers to the simulation time as opposed to the thermal equilibration time parameter used previously.
-We define the equilibrated initial conditions
-\begin{align}
-    T(x, z)\big|_{t=0} &= \bar{T}(z) + \sqrt{2} \sum_{n=1}^N  A^2_n \text{ Re} \Big[ \Theta_n(z) e^{ik_{x_n}x} \Big] \nonumber \\
-    \mathbf{u}(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A^2_n \text{ Re} \Big[\Big( U_n (z) \hat{x} + W_n(z) \hat{z} \Big) e^{ik_{x_n}x} \Big] \nonumber\\
-    p(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A^2_n \text{ Re} \Big[P_n (z) e^{ik_{x_n}x}\Big]
-\end{align}
 \begin{figure}[h]
     \centering
-    \includegraphics[width=3.4in]{sim_eq_nu.png}
-    \caption{Nusselt numbers of simulations performed at $Ra \, = \, 10^8$ with conventional initial conditions (red) and marginally-stable thermally-equilibrated initial conditions (blue).
-Simulations launched with thermally-equilibrated states do not undergo a convective-transient period because the characteristic plume structure exists on initialization.
-This is illustrated by the $Nu$ spike at $t \sim 15$ in the convectional simulation.}
-    \label{fig:nu_sim}
+    \includegraphics[width=3.4in]{b0z_profs.png}
+    \caption{Background temperature profiles.}
+    \label{fig:my_label}
 \end{figure}
-Where $\Theta_n(z), U_n(z), W_n(z), P_n(z); \, A^2; $ and $k_{x_n}$ refer to the complex eigenfunctions, amplitude, and wavenumber at the $n$th marginal mode.
-The $\sqrt{2}$ factor is necessary normalize the eigenfunctions according to the new domain ???.
-By construction, these initial conditions are thermally equilibrated.
-Simulations launched with equilibrated initial conditions do not exhibit a convective-transient period, as the large-scale anatomy of the characteristic plumes and convective winds of Rayleigh-B\'enard convection exist on initialization.
-This is illustrated in Figure \ref{fig:nu_sim}, where the sharp spike in $Nu$ is associated with the turbulent transition period of upwelling until the distinctive jet-like structure is established.
-\par The marginally-stable equilibria are associated with a combination of eigenfunctions whose average kinetic energy is significantly larger than the statistical steady state, as given by Figure \ref{fig:ke_sim}.
-This is impairs kinetic relaxation because the large horizontal flows decay on a viscous timescale
-\begin{equation}
-    t_{\nu} \sim \frac{Pr}{\sqrt{Ra}}. \nonumber
-\end{equation}
-Consequently, marginally-stable thermally-equilibrated initial conditions do not reduce the simulation time required to achieve a statistically steady state, rather, they increase it considerably.
+
+% \begin{figure}[h]
+%     \centering
+%     \includegraphics[width=3.4in]{wb_profiles_norm.png}
+%     \caption{Horizontally-averaged advective flux}
+%     \label{fig:my_label}
+% \end{figure}
+ \newpage
+\section{Simulations with Thermally Equilibrated Initial Conditions}
+
 \begin{figure}[h]
     \centering
-    \includegraphics[width=3.4in]{sim_eq_ke.png}
-    \caption{Average kinetic energies of the same simulations performed in Figure \ref{fig:nu_sim} ($Ra \, = \, 10^8$).
-The combination of eigenfunctions which give thermal equilibrium have significantly more kinetic energy than the statistically steady state.
-Kinetic equilibrium is achieved according to the viscous timescale $t_{\nu} \sim Pr Ra^{-1/2}$.}
-    \label{fig:ke_sim}
+    \includegraphics[width=3.4in]{nu_good.png}
+    \caption{Simulation Nusselt number: 2-dimensional nonlinear simulations were performed with identical parameters.}
+    \label{fig:my_label}
 \end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=3.4in]{ke_good.png}
+    \caption{Maximum simulation kinetic energy}
+    \label{fig:my_label}
+\end{figure}
+
+% \begin{figure}[h]
+%     \centering
+%     \subfloat{\includegraphics[width=3.4in]{write_000001.png}}
+%     \hfill
+%     \subfloat{\includegraphics[width=3.4in]{write_000004.png}}
+%     \caption{Quasi-geostrophic potential vorticity (PV) with an overwhelming beta-effect shown at time $t \approx 0.5$.
+Disco-ball initial conditions are employed.
+Left and right figures obtained from finite difference and \texttt{Dedalus} solvers respectively.}
+%     \label{beta}
+% \end{figure}
 

### 2021-02-25 publication_materials/rbctest.tex
plotting tools

--- 2021-02-25 publication_materials/ms_revised.tex
@@
 \usepackage{varwidth}
-\usepackage{{subfig}
 
@@
 The equations of motion are then given by
-\begin{align}
-    \nabla \cdot \mathbf{u} &= 0 \label{EQ:motion1}\\
-    \frac{\partial \mathbf{u}}{\partial t} + \mathbf{u} \cdot \nabla \mathbf{u} &= - \nabla p + T \hat{z} + \sqrt{\frac{Pr}{Ra}} \nabla^2 \mathbf{u} \label{EQ:motion2}\\
-    \frac{\partial T}{\partial t} + \mathbf{u} \cdot \nabla T &= \frac{1}{\sqrt{RaPr}} \nabla^2 T \label{EQ:motion3}
-\end{align}
+% \begin{align}
+%     \nabla \cdot \mathbf{u} &= 0 \label{EQ:motion1}\\
+%     \frac{\partial \mathbf{u}}{\partial t} + \mathbf{u} \cdot \nabla \mathbf{u} &= - \nabla p + T \mathhat{z} + \sqrt{\frac{Pr}{Ra}} \nabla^2 \mathbf{u} \label{EQ:motion2}\\
+%     \frac{\partial T}{\partial t} + \mathbf{u} \cdot \nabla T &= \frac{1}{\sqrt{RaPr}} \nabla^2 T \label{EQ:motion3}
+% \end{align}
 where $p$ is pressure and $T$ is temperature.
@@
 
-\begin{figure*}[t]
-    \centering
-    \subfloat{\includegraphics[width=3.4in]{flux_sup_n.png}}
-    \hfill
-    \subfloat{\includegraphics[width=3.4in]{EV_spectra_2ra.png}}
-    \caption{Heat fluxes (left) and eigenvalue spectra (right) of equilibrated states $Ra = 2 \times 10^5$ (top) and $Ra = 10^9$ (bottom).
+% \begin{figure*}[t]
+%     \centering
+%     \subfloat{\includegraphics[width=3.4in]{flux_sup_n.png}}
+%     \hfill
+%     \subfloat{\includegraphics[width=3.4in]{EV_spectra_2ra.png}}
+%     \caption{Heat fluxes (left) and eigenvalue spectra (right) of equilibrated states $Ra = 2 \times 10^5$ (top) and $Ra = 10^9$ (bottom).
 Advection profiles belong to marginally-stable modes.
@@
 A combination of these of profiles is necessary to transition to the $k_x = 1.5\pi$ mode.}
-    \label{fig:flux}
-\end{figure*}
+%     \label{fig:flux}
+% \end{figure*}
 

### 2021-02-25 RA1E8/Main.py

@@ -20,7 +20,7 @@ from Simulation import *     # pylint: disable=unused-wildcard-import
 # Settings/options
 restart = False
 load_profile = False
-subDir = '/results'
+subDir = '/results_new'
 profile_file_name = os.path.dirname(os.path.abspath(__file__)) + '/avg_profs/averaged_avg_profs_ra1e8.h5'
 path = os.path.dirname(os.path.abspath(__file__)) + subDir
 if (not os.path.exists(path)):
@@ -376,6 +376,7 @@ else:
         sim.ev_dict = dict(sim.evs)
         pickle.dump(sim.evs, open(sim.iteration_path + '/evs.pick', 'wb'))
 
+# sim.store_avg_eigenfunctions(2)
 print_nu_del()
 
 ##################################################

### 2021-02-25 RA1E8/Simulation.py

@@ -1047,9 +1047,11 @@ class Simulation():
             kx1 = conv_data['kx1']
             kx2 = conv_data['kx2']
             kx3 = conv_data['kx3']
+            kx4 = conv_data['kx4']
             amp1 = conv_data['amp1']            
             amp2 = conv_data['amp2']
             amp3 = conv_data['amp3']
+            amp4 = conv_data['amp4']
             delta_T += del_t
             for file in os.listdir(iteration_i_path + 'data'):
                 if (not file.endswith('.pick')):
@@ -1063,6 +1065,8 @@ class Simulation():
                     amp = np.sqrt(amp2)
                 elif (abs(kx - kx3) < 1e-8):
                     amp = np.sqrt(amp3)
+                elif (abs(kx - kx4) < 1e-8):
+                    amp = np.sqrt(amp4)
                 else:
                     raise ValueError('Wavenumber in data file matches none of the converged wavenumbers!')
                 if (not kx in fields_dict.keys()):

### 2021-02-25 plot_ke.py

@@ -31,7 +31,7 @@ def main(filename, start, count, output):
 
     # Plot writes
     with h5py.File(filename, mode='r') as file:
-        ke_data = pickle.load(open(path + '/ke_data_eq.pick', 'rb'))
+        ke_data = pickle.load(open(path + '/ke_data_nom.pick', 'rb'))
         ke_ar = ke_data['ke_ar']
         # ke_max_ar = ke_data['ke_max_ar']
         sim_times_ar = ke_data['sim_times_ar']
@@ -41,7 +41,7 @@ def main(filename, start, count, output):
             sim_times_ar.append(file['scales/sim_time'][index])
         ke_data['ke_ar'] = ke_ar
         ke_data['sim_times_ar'] = sim_times_ar
-        pickle.dump(ke_data, open(path + '/ke_data_eq.pick', 'wb'))
+        pickle.dump(ke_data, open(path + '/ke_data_nom.pick', 'wb'))
         
 
 
@@ -61,7 +61,7 @@ if __name__ == "__main__":
     write_data = False
     if (write_data):
         ke_data = {'ke_ar' : [], 'sim_times_ar' : []}
-        pickle.dump(ke_data, open(path + '/ke_data_eq.pick', 'wb'))
+        pickle.dump(ke_data, open(path + '/ke_data_nom.pick', 'wb'))
 
         # Create output directory if needed
         with Sync() as sync:
@@ -71,14 +71,17 @@ if __name__ == "__main__":
         post.visit_writes(args['<files>'], main, output=output_path)
     else:
         ke_data_eq = pickle.load(open(path + '/ke_data_eq.pick', 'rb'))
-        # ke_data = pickle.load(open(path + '/ke_data.pick', 'rb'))
+        ke_data = pickle.load(open(path + '/ke_data_nom.pick', 'rb'))
 
         ke_ar_eq = ke_data_eq['ke_ar']
-        # ke_ar = ke_data['ke_ar']
+        ke_ar = ke_data['ke_ar']
         sim_times_ar_eq = ke_data_eq['sim_times_ar']
-        # sim_times_ar = ke_data['sim_times_ar']
-        # plt.plot(sim_times_ar, ke_ar, color='firebrick', label = 'Conductive I.C.')
-        plt.plot(sim_times_ar_eq, ke_ar_eq, color='midnightblue', label = 'Equilibrated I.C.')
[…]

### 2021-02-25 plot_nu.py

@@ -1,0 +1,118 @@
+"""
+Plot planes from joint analysis files.
+
+Usage:
+    plot_slices.py <files>... [--output=<dir>]
+
+Options:
+    --output=<dir>  Output directory [default: ./frames]
+
+"""
+
+import h5py
+import pickle
+import os
+import sys
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+plt.ioff()
+import dedalus.public as de
+from dedalus.extras import plot_tools
+import publication_settings
+
+matplotlib.rcParams.update(publication_settings.params)
+plt.rcParams.update({'figure.autolayout': True})
+plt.gcf().subplots_adjust(left=0.15)
+
+fig = plt.figure()
+
+def main(filename, start, count, output):
+    """Save plot of specified tasks for given range of analysis writes."""
+
+    # Plot writes
+    with h5py.File(filename, mode='r') as file:
+        nu_data = pickle.load(open(path + '/nu_data_eq.pick', 'rb'))
+        wb_ar = nu_data['wb_ar']
+        diff_ar = nu_data['diff_ar']
+        # nu_max_ar = nu_data['nu_max_ar']
+        z = file['/scales/z/1.0'][:]
+        sim_times_ar = nu_data['sim_times_ar']
+        nu_data['z'] = z
+        for index in range(start, start+count):
+            wb = file['tasks']['adv_flux'][index][0]
+            wb_ar.append(wb)
+            diff = file['tasks']['diffusive_flux'][index][0]
+            diff_ar.append(diff)
+            sim_times_ar.append(file['scales/sim_time'][index])
+        nu_data['wb_ar'] = wb_ar
+        nu_data['diff_ar'] = diff_ar
+        nu_data['sim_times_ar'] = sim_times_ar
+        pickle.dump(nu_data, open(path + '/nu_data_eq.pick', 'wb'))
+        
+
+
+if __name__ == "__main__":
+
+    import pathlib
+    from docopt import docopt
+    from dedalus.tools import logging
+    from dedalus.tools import post
+    from dedalus.tools.parallel import Sync
+
+    args = docopt(__doc__)
+
+    output_path = pathlib.Path(args['--output']).absolute()
+    global path 
+    path = os.path.dirname(os.path.abspath(__file__))
+    write_data = False
+    if (write_data):
[…]

### 2021-02-25 rbc_sim_nom.py

@@ -84,75 +84,22 @@ logger.info('Solver built')
 # Initial conditions or restart
 if not pathlib.Path('restart.h5').exists():
     
-    path = os.path.dirname(os.path.abspath(__file__)) + '/RA1E8/results_conv1'
-    iteration = 9228
-    iteration_path = path + '/Iteration'+str(iteration)
-    fields_dict = pickle.load(open(iteration_path + '/fields_dict.pick', 'rb'))
-    b0z_g = fields_dict[list(fields_dict.keys())[0]]['b0z']
-
-    # Accomodate differing resolutions in EVP and IVP processes
-    N_evp = len(b0z_g)
-    evp_scale = int(N_evp / Nz)
-    x_evp, z_evp = domain.all_grids(scales=evp_scale)
-    
-    # Random perturbations, initialized globally for same results in parallel
-    gshape = domain.dist.grid_layout.global_shape(scales=evp_scale)
-    slices = domain.dist.grid_layout.slices(scales=evp_scale)
-    rand = np.random.RandomState(seed=42)
-    noise = rand.standard_normal(gshape)[slices]
-    b0z = b0z_g.real[slices[1]]
-    fields_lst = list(fields_dict.values())
-
-    eikx_lst = [np.exp(1j*fields['kx']*x_evp) for fields in fields_lst]
-    exp_fields = list(zip(eikx_lst, fields_lst))
-
     # Initial conditions
     x, z = domain.all_grids()
-    w = solver.state['w']
-    wz = solver.state['wz']
     b = solver.state['b']
     bz = solver.state['bz']
-    p = solver.state['p']
-    u = solver.state['u']
-    uz = solver.state['uz']
-    
-    w.set_scales(evp_scale)
-    wz.set_scales(evp_scale)
-    b.set_scales(evp_scale)
-    bz.set_scales(evp_scale)
-    p.set_scales(evp_scale)
-    u.set_scales(evp_scale)
-    uz.set_scales(evp_scale)
+
+    # Random perturbations, initialized globally for same results in parallel
+    gshape = domain.dist.grid_layout.global_shape(scales=1)
+    slices = domain.dist.grid_layout.slices(scales=1)
+    rand = np.random.RandomState(seed=42)
+    noise = rand.standard_normal(gshape)[slices]
 
[…]

### 2021-02-25 rbc_sim_nom.sh

@@ -1,0 +1,17 @@
+#PBS -S /bin/bash
+#PBS -N rbc_sim_nom
+#PBS -l select=4:ncpus=28:mpiprocs=28:model=bro
+#PBS -l walltime=24:00:00
+#PBS -j oe
+module load mpi-sgi/mpt
+module load comp-intel
+export PATH=$HOME/scripts:$PATH
+deactivate
+unset PYTHONPATH
+source ~/miniconda3/etc/profile.d/conda.sh
+export PYTHONNOUSERSITE=1
+conda activate dedalus
+# support lots of text output to stdio for analysis
+export MPI_UNBUFFERED_STDIO=true
+cd ~/scratch/dedalus/EVP_evolution/
+mpiexec_mpt -np 112 python3 rbc_sim_nom.py

### 2021-02-26 rbc_j1.sh
purge repo thorough

@@ -1,17 +1,0 @@
-#PBS -S /bin/bash
-#PBS -N rbc_j1
-#PBS -l select=1:ncpus=28:mpiprocs=28:model=bro
-#PBS -l walltime=24:00:00
-#PBS -j oe
-module load mpi-sgi/mpt
-module load comp-intel
-export PATH=$HOME/scripts:$PATH
-deactivate
-unset PYTHONPATH
-source ~/miniconda3/etc/profile.d/conda.sh
-export PYTHONNOUSERSITE=1
-conda activate dedalus
-# support lots of text output to stdio for analysis
-export MPI_UNBUFFERED_STDIO=true
-cd ~/scratch/dedalus/EVP_evolution/
-mpiexec_mpt -np 28 python3 Main.py

### 2021-02-26 sim_old.py

@@ -1,1311 +1,0 @@
-import time
-import matplotlib
-import matplotlib.pyplot as plt
-import matplotlib.ticker as tck
-import dedalus.public as de
-import eigentools as eig
-import numpy as np
-from collections import OrderedDict
-from mpi4py import MPI
-import os
-import pickle
-import h5py
-import scipy.sparse.linalg
-import scipy.signal
-from multiprocessing import Process
-CW = MPI.COMM_WORLD
-import logging
-logger = logging.getLogger(__name__)
-import sys
-
-class Simulation():
-    def __init__(self, subDir, Nz, pi_range, del_t_newton, del_t_broyden, T_mem_coeff, rayleigh, ra_growth_coeff, prandtl, growth_tol):
-        self.path = os.path.dirname(os.path.abspath(__file__)) + subDir
-        self.Nz = Nz
-        self.z_basis = de.Chebyshev('z', Nz, interval=(-1/2, 1/2), dealias=3/2)
-        self.domain = de.Domain([self.z_basis], grid_dtype=np.complex128, comm=MPI.COMM_SELF)
-        self.z = self.domain.grid(0)
-        self.b0z = self.domain.new_field()
-        self.wb = self.domain.new_field()
-        self.b0z_a = self.domain.new_field()
-        self.evs = None
-        self.ev_dict = None
-        self.ev_maxima_count = 0
-        self.wb_ar = None
-        self.b0z_d = None
-        self.wb_mem = None
-        self.Rayleigh = rayleigh
-        self.ra_growth_coeff = ra_growth_coeff
-        self.Prandtl = prandtl
-        self.pi_range = pi_range
-        self.del_t_newton = del_t_newton
-        self.del_t_broyden = del_t_broyden
-        self.T_mem = del_t_broyden*T_mem_coeff
-        self.suppress_memory = True
-        self.del_t = 0.0
-        self.dT_regime = False
-        self.attempt = 0
-        self.iters_new_ts = []
-        self.v0_eig = np.random.RandomState(seed=42).rand(Nz*7)
-        self.kx_domain = list(map(lambda n: n*np.pi/2, range(1, pi_range*2)))
-        self.growth_tol = growth_tol
-        self.ivp_partitions = 5
-        self.kx_regime = 1
-        self.iteration = 0
-        self.sim_time = 0.0
-        self.sim_times = [0.0]
-        self.RBC_EVP = self.build_EVP()
[…]

### 2021-02-26 plot_flux.py
pfe figs update1

@@ -71,10 +71,10 @@ def plot_flux(Rayleigh, ax, path, iteration):
         ax.plot(z, advection4, label = 'Advection ($k_x  = $' + pi_mult4 + '$\pi$)')
         ax.plot(z, advection5, label = 'Advection ($k_x  = $' + pi_mult5 + '$\pi$)')
         ax.plot(z, flux, label = 'Total', color='black')
-        ax.set_xlim(-0.5, 0.5)
+        ax.set_xlim(-0.5, 0.0)
         ax.set_yticks([0.000, 0.001, 0.002, 0.003])
         # ax.set_ylim(-0.0002, 0.0039)
-        ax.legend(prop={'size': 8}, frameon=False)
+        ax.legend(prop={'size': 7.5}, frameon=False, loc='center right', bbox_to_anchor=(0.52, 0.25, 0.5, 0.5))
         ax.set_title(r'$Ra \, = \, 10^9$')
         # plt.title('Heat Flux')
         ax.set_xlabel(r'$z$')
@@ -95,8 +95,8 @@ def plot_flux(Rayleigh, ax, path, iteration):
         pi_mult = str(round(kx/np.pi, 1))
         ax.plot(z, advection, label = 'Advection ($k_x  = $' + pi_mult + '$\pi$)')
         ax.plot(z, flux, label = 'Total', color='black')
-        ax.set_xlim(-0.5, 0.5)
-        ax.legend(frameon=False)
+        ax.set_xlim(-0.5, 0.0)
+        ax.legend(frameon=False, loc='center right')
         ax.set_title(r'$Ra \, = \, 2 \times  10^5$')
         ax.set_xlabel(r'$z$')
         ax.set_ylabel('Flux')
@@ -131,5 +131,6 @@ plt.subplots_adjust(right=1.0)
 # fig.text(0.00, 0.5, 'Flux', ha='center', va='center', rotation='vertical', fontsize=10)
 # plt.ylabel('Flux')
 plt.savefig(root_path + '/pubfigs/flux_sup_n', bbox_inches='tight')
+plt.savefig(root_path + '/publication_materials/flux_sup_n', bbox_inches='tight')
 
 

### 2021-02-26 plot_spectra_2ra.py

@@ -32,16 +32,27 @@ def format_func(value, tick_number):
 def plot_EVs(evs_mat, labels):
     fig, axs = plt.subplots(2, sharex=False)
     # fig.suptitle(r'$Ra 2e9$')
-    ylims = [(-2, 0.01), (-0.001, 0.00001)]
+    ylims = [(-2, 0.1), (-0.001, 0.0001)]
     xlims = [(0, 12*np.pi), (0, 30*np.pi)]
     maj_loc = [2*np.pi, 5*np.pi]
     for i, evs in enumerate(evs_mat):
         ax = axs[i]
         [kxs, EVs] = list(zip(*evs))
-        ax.plot(kxs, EVs, '.', linestyle='None')
+        kx_m, evs_m = [], []
+        kx_s, evs_s = [], []
+        for j in range(len(kxs)):
+            if (EVs[j] > -1e-9):
+                kx_m.append(kxs[j])
+                evs_m.append(EVs[j])
+            else:
+                kx_s.append(kxs[j])
+                evs_s.append(EVs[j])
+        ax.plot(kx_s, evs_s, '.', label='Stable', linestyle='None')
+        ax.plot(kx_m, evs_m, 'x', label='Marginal', markersize=3, linestyle='None')
         ax.set_title(labels[i])
         ax.set_xlim(xlims[i])
         ax.set_ylim(ylims[i])
+        ax.legend(loc='lower left')
         ax.xaxis.set_major_locator(tck.MultipleLocator(maj_loc[i]))
         ax.xaxis.set_minor_locator(tck.MultipleLocator(np.pi / 2))
         ax.xaxis.set_major_formatter(plt.FuncFormatter(format_func))
@@ -55,6 +66,7 @@ def plot_EVs(evs_mat, labels):
     # plt.legend(loc='lower right')
     # fig.text(0.00, 0.5, r'$\omega$', ha='center', va='center', rotation='vertical', fontsize=10)
     plt.savefig(path + '/pubfigs/EV_spectra_2ra', bbox_inches='tight')
+    plt.savefig(path + '/publication_materials/EV_spectra_2ra', bbox_inches='tight')
 
 # fig = plt.figure()
 path = os.path.dirname(os.path.abspath(__file__))

### 2021-02-26 publication_settings.py

@@ -20,10 +20,12 @@ colors = [
 params = {#'backend': 'eps',
           'axes.prop_cycle' : matplotlib.cycler(color=colors),
           'axes.labelsize': 10,
-          'font.family':'CMU Serif',
+          'font.family':'serif',
           #'text.fontsize': 8,
           'font.size':8,
-          'font.serif': 'CMU Serif Roman',
+          'font.serif': 'stix',
+          'mathtext.fontset' : 'stix',
+        #   'text.usetex' : True,
           'legend.fontsize': 8,
           'legend.markerscale': 1,
           'xtick.labelsize': 10,

### 2021-02-26 plot_ke.py
plot legends: frames off

@@ -79,7 +79,7 @@ if __name__ == "__main__":
         plt.plot(sim_times_ar, ke_ar, color='darkred', label = 'Conductive I.C.')
         plt.plot(sim_times_ar_eq, ke_ar_eq, color='darkblue', label = 'Equilibrated I.C.')
         plt.xlim(0, 400)
-        plt.legend()
+        plt.legend(frameon=False)
         plt.xlabel(r'$t$')
         plt.ylabel(r'$\overline{|\mathbf{u}|^2}$')
         plt.title(r'$Ra \, = \, 10^8$')

### 2021-02-26 plot_nu.py

@@ -111,7 +111,7 @@ if __name__ == "__main__":
         plt.plot(sim_times_ar, nu_ar, color='darkred', label = 'Conductive I.C.')
         plt.plot(sim_times_ar_eq, nu_ar_eq, color='darkblue', label = 'Equilibrated I.C.')
         plt.xlim(0, 100)
-        plt.legend()
+        plt.legend(frameon=False)
         plt.xlabel(r'$t$')
         plt.ylabel(r'$Nu$')
         plt.title(r'$Ra \, = \, 10^8$')

### 2021-02-26 publication_materials/ms_rbc.tex

@@
 
-A novel iterative time-marching method is derived by introducing time-dependence in the background temperature profile of the classical Rayleigh-B\'enard Boussinesq linear stability analysis.
+boiii A novel iterative time-marching method is derived by introducing time-dependence in the background temperature profile of the classical Rayleigh-B\'enard Boussinesq linear stability analysis.
 Eigenfunction amplitudes are obtained by requiring marginal-stability.
@@
 
-The introduction leads the reader from a general subject area to a particular topic of inquiry.
+boii The introduction leads the reader from a general subject area to a particular topic of inquiry.
 It establishes the scope, context, and significance of the research being conducted by summarizing current understanding and background information about the topic, stating the purpose of the work in the form of the research problem supported by a hypothesis or a set of questions, explaining briefly the methodological approach used to examine the research problem, highlighting the potential outcomes your study can reveal, and outlining the remaining structure and organization of the paper.

### 2021-03-01 RA1E5/rbc_sim_nom.py
nominal 2d simulations for each ra

@@ -1,0 +1,166 @@
+"""
+Dedalus script for 2D Rayleigh-Benard convection.
+
+This script uses a Fourier basis in the x direction with periodic boundary
+conditions.  The equations are scaled in units of the buoyancy time (Fr = 1).
+
+This script can be ran serially or in parallel, and uses the built-in analysis
+framework to save data snapshots in HDF5 files.  The `merge_procs` command can
+be used to merge distributed analysis sets from parallel runs, and the
+`plot_slices.py` script can be used to plot the snapshots.
+
+To run, merge, and plot using 4 processes, for instance, you could use:
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+    $ mpiexec -n 4 python3 -m dedalus merge_procs snapshots
+    $ mpiexec -n 4 python3 plot_slices.py snapshots/*.h5
+
+This script can restart the simulation from the last save of the original
+output to extend the integration.  This requires that the output files from
+the original simulation are merged, and the last is symlinked or copied to
+`restart.h5`.
+
+To run the original example and the restart, you could use:
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+    $ mpiexec -n 4 python3 -m dedalus merge_procs snapshots
+    $ ln -s snapshots/snapshots_s2.h5 restart.h5
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+
+The simulations should take a few process-minutes to run.
+
+"""
+
+import numpy as np
+from mpi4py import MPI
+import time
+import pathlib
+import pickle
+import os
+
+from dedalus import public as de
+from dedalus.extras import flow_tools
+from dedalus.extras.plot_tools import plot_bot_2d
+
+import logging
+logger = logging.getLogger(__name__)
+
+
+# Parameters
+Lx, Lz = (4., 1.)
+Prandtl = 1.
+Rayleigh = 1e5
+
+# Create bases and domain
+Nx, Nz = 2048, 512
+x_basis = de.Fourier('x', Nx, interval=(0, Lx), dealias=3/2)
+z_basis = de.Chebyshev('z', Nz, interval=(-Lz/2, Lz/2), dealias=3/2)
[…]

### 2021-03-01 RA1E5/rbc_sim_nom_1e5.sh

@@ -1,0 +1,17 @@
+#PBS -S /bin/bash
+#PBS -N rbc_sim_nom_1e5
+#PBS -l select=4:ncpus=28:mpiprocs=28:model=bro
+#PBS -l walltime=24:00:00
+#PBS -j oe
+module load mpi-sgi/mpt
+module load comp-intel
+export PATH=$HOME/scripts:$PATH
+deactivate
+unset PYTHONPATH
+source ~/miniconda3/etc/profile.d/conda.sh
+export PYTHONNOUSERSITE=1
+conda activate dedalus
+# support lots of text output to stdio for analysis
+export MPI_UNBUFFERED_STDIO=true
+cd ~/scratch/dedalus/EVP_evolution/RA1E5/
+mpiexec_mpt -np 112 python3 rbc_sim_nom.py

### 2021-03-01 RA1E6/rbc_sim_nom.py

@@ -1,0 +1,166 @@
+"""
+Dedalus script for 2D Rayleigh-Benard convection.
+
+This script uses a Fourier basis in the x direction with periodic boundary
+conditions.  The equations are scaled in units of the buoyancy time (Fr = 1).
+
+This script can be ran serially or in parallel, and uses the built-in analysis
+framework to save data snapshots in HDF5 files.  The `merge_procs` command can
+be used to merge distributed analysis sets from parallel runs, and the
+`plot_slices.py` script can be used to plot the snapshots.
+
+To run, merge, and plot using 4 processes, for instance, you could use:
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+    $ mpiexec -n 4 python3 -m dedalus merge_procs snapshots
+    $ mpiexec -n 4 python3 plot_slices.py snapshots/*.h5
+
+This script can restart the simulation from the last save of the original
+output to extend the integration.  This requires that the output files from
+the original simulation are merged, and the last is symlinked or copied to
+`restart.h5`.
+
+To run the original example and the restart, you could use:
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+    $ mpiexec -n 4 python3 -m dedalus merge_procs snapshots
+    $ ln -s snapshots/snapshots_s2.h5 restart.h5
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+
+The simulations should take a few process-minutes to run.
+
+"""
+
+import numpy as np
+from mpi4py import MPI
+import time
+import pathlib
+import pickle
+import os
+
+from dedalus import public as de
+from dedalus.extras import flow_tools
+from dedalus.extras.plot_tools import plot_bot_2d
+
+import logging
+logger = logging.getLogger(__name__)
+
+
+# Parameters
+Lx, Lz = (4., 1.)
+Prandtl = 1.
+Rayleigh = 1e6
+
+# Create bases and domain
+Nx, Nz = 2048, 512
+x_basis = de.Fourier('x', Nx, interval=(0, Lx), dealias=3/2)
+z_basis = de.Chebyshev('z', Nz, interval=(-Lz/2, Lz/2), dealias=3/2)
[…]

### 2021-03-01 RA1E6/rbc_sim_nom_1e6.sh

@@ -1,0 +1,17 @@
+#PBS -S /bin/bash
+#PBS -N rbc_sim_nom_1e6
+#PBS -l select=4:ncpus=28:mpiprocs=28:model=bro
+#PBS -l walltime=24:00:00
+#PBS -j oe
+module load mpi-sgi/mpt
+module load comp-intel
+export PATH=$HOME/scripts:$PATH
+deactivate
+unset PYTHONPATH
+source ~/miniconda3/etc/profile.d/conda.sh
+export PYTHONNOUSERSITE=1
+conda activate dedalus
+# support lots of text output to stdio for analysis
+export MPI_UNBUFFERED_STDIO=true
+cd ~/scratch/dedalus/EVP_evolution/RA1E6/
+mpiexec_mpt -np 112 python3 rbc_sim_nom.py

### 2021-03-01 RA1E7/rbc_sim_nom.py

@@ -1,0 +1,166 @@
+"""
+Dedalus script for 2D Rayleigh-Benard convection.
+
+This script uses a Fourier basis in the x direction with periodic boundary
+conditions.  The equations are scaled in units of the buoyancy time (Fr = 1).
+
+This script can be ran serially or in parallel, and uses the built-in analysis
+framework to save data snapshots in HDF5 files.  The `merge_procs` command can
+be used to merge distributed analysis sets from parallel runs, and the
+`plot_slices.py` script can be used to plot the snapshots.
+
+To run, merge, and plot using 4 processes, for instance, you could use:
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+    $ mpiexec -n 4 python3 -m dedalus merge_procs snapshots
+    $ mpiexec -n 4 python3 plot_slices.py snapshots/*.h5
+
+This script can restart the simulation from the last save of the original
+output to extend the integration.  This requires that the output files from
+the original simulation are merged, and the last is symlinked or copied to
+`restart.h5`.
+
+To run the original example and the restart, you could use:
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+    $ mpiexec -n 4 python3 -m dedalus merge_procs snapshots
+    $ ln -s snapshots/snapshots_s2.h5 restart.h5
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+
+The simulations should take a few process-minutes to run.
+
+"""
+
+import numpy as np
+from mpi4py import MPI
+import time
+import pathlib
+import pickle
+import os
+
+from dedalus import public as de
+from dedalus.extras import flow_tools
+from dedalus.extras.plot_tools import plot_bot_2d
+
+import logging
+logger = logging.getLogger(__name__)
+
+
+# Parameters
+Lx, Lz = (4., 1.)
+Prandtl = 1.
+Rayleigh = 1e7
+
+# Create bases and domain
+Nx, Nz = 2048, 512
+x_basis = de.Fourier('x', Nx, interval=(0, Lx), dealias=3/2)
+z_basis = de.Chebyshev('z', Nz, interval=(-Lz/2, Lz/2), dealias=3/2)
[…]

### 2021-03-01 RA1E8/rbc_sim_nom.py

@@ -1,0 +1,166 @@
+"""
+Dedalus script for 2D Rayleigh-Benard convection.
+
+This script uses a Fourier basis in the x direction with periodic boundary
+conditions.  The equations are scaled in units of the buoyancy time (Fr = 1).
+
+This script can be ran serially or in parallel, and uses the built-in analysis
+framework to save data snapshots in HDF5 files.  The `merge_procs` command can
+be used to merge distributed analysis sets from parallel runs, and the
+`plot_slices.py` script can be used to plot the snapshots.
+
+To run, merge, and plot using 4 processes, for instance, you could use:
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+    $ mpiexec -n 4 python3 -m dedalus merge_procs snapshots
+    $ mpiexec -n 4 python3 plot_slices.py snapshots/*.h5
+
+This script can restart the simulation from the last save of the original
+output to extend the integration.  This requires that the output files from
+the original simulation are merged, and the last is symlinked or copied to
+`restart.h5`.
+
+To run the original example and the restart, you could use:
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+    $ mpiexec -n 4 python3 -m dedalus merge_procs snapshots
+    $ ln -s snapshots/snapshots_s2.h5 restart.h5
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+
+The simulations should take a few process-minutes to run.
+
+"""
+
+import numpy as np
+from mpi4py import MPI
+import time
+import pathlib
+import pickle
+import os
+
+from dedalus import public as de
+from dedalus.extras import flow_tools
+from dedalus.extras.plot_tools import plot_bot_2d
+
+import logging
+logger = logging.getLogger(__name__)
+
+
+# Parameters
+Lx, Lz = (4., 1.)
+Prandtl = 1.
+Rayleigh = 1e8
+
+# Create bases and domain
+Nx, Nz = 2048, 512
+x_basis = de.Fourier('x', Nx, interval=(0, Lx), dealias=3/2)
+z_basis = de.Chebyshev('z', Nz, interval=(-Lz/2, Lz/2), dealias=3/2)
[…]

### 2021-03-01 RA1E8/rbc_sim_nom_1e8.sh

@@ -1,0 +1,17 @@
+#PBS -S /bin/bash
+#PBS -N rbc_sim_nom_1e8
+#PBS -l select=4:ncpus=28:mpiprocs=28:model=bro
+#PBS -l walltime=24:00:00
+#PBS -j oe
+module load mpi-sgi/mpt
+module load comp-intel
+export PATH=$HOME/scripts:$PATH
+deactivate
+unset PYTHONPATH
+source ~/miniconda3/etc/profile.d/conda.sh
+export PYTHONNOUSERSITE=1
+conda activate dedalus
+# support lots of text output to stdio for analysis
+export MPI_UNBUFFERED_STDIO=true
+cd ~/scratch/dedalus/EVP_evolution/RA1E8/
+mpiexec_mpt -np 112 python3 rbc_sim_nom.py

### 2021-03-01 RA2E6/rbc_sim_nom.py

@@ -1,0 +1,166 @@
+"""
+Dedalus script for 2D Rayleigh-Benard convection.
+
+This script uses a Fourier basis in the x direction with periodic boundary
+conditions.  The equations are scaled in units of the buoyancy time (Fr = 1).
+
+This script can be ran serially or in parallel, and uses the built-in analysis
+framework to save data snapshots in HDF5 files.  The `merge_procs` command can
+be used to merge distributed analysis sets from parallel runs, and the
+`plot_slices.py` script can be used to plot the snapshots.
+
+To run, merge, and plot using 4 processes, for instance, you could use:
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+    $ mpiexec -n 4 python3 -m dedalus merge_procs snapshots
+    $ mpiexec -n 4 python3 plot_slices.py snapshots/*.h5
+
+This script can restart the simulation from the last save of the original
+output to extend the integration.  This requires that the output files from
+the original simulation are merged, and the last is symlinked or copied to
+`restart.h5`.
+
+To run the original example and the restart, you could use:
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+    $ mpiexec -n 4 python3 -m dedalus merge_procs snapshots
+    $ ln -s snapshots/snapshots_s2.h5 restart.h5
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+
+The simulations should take a few process-minutes to run.
+
+"""
+
+import numpy as np
+from mpi4py import MPI
+import time
+import pathlib
+import pickle
+import os
+
+from dedalus import public as de
+from dedalus.extras import flow_tools
+from dedalus.extras.plot_tools import plot_bot_2d
+
+import logging
+logger = logging.getLogger(__name__)
+
+
+# Parameters
+Lx, Lz = (4., 1.)
+Prandtl = 1.
+Rayleigh = 2e6
+
+# Create bases and domain
+Nx, Nz = 2048, 512
+x_basis = de.Fourier('x', Nx, interval=(0, Lx), dealias=3/2)
+z_basis = de.Chebyshev('z', Nz, interval=(-Lz/2, Lz/2), dealias=3/2)
[…]

### 2021-03-01 RA2E8/rbc_sim_nom.py

@@ -1,0 +1,166 @@
+"""
+Dedalus script for 2D Rayleigh-Benard convection.
+
+This script uses a Fourier basis in the x direction with periodic boundary
+conditions.  The equations are scaled in units of the buoyancy time (Fr = 1).
+
+This script can be ran serially or in parallel, and uses the built-in analysis
+framework to save data snapshots in HDF5 files.  The `merge_procs` command can
+be used to merge distributed analysis sets from parallel runs, and the
+`plot_slices.py` script can be used to plot the snapshots.
+
+To run, merge, and plot using 4 processes, for instance, you could use:
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+    $ mpiexec -n 4 python3 -m dedalus merge_procs snapshots
+    $ mpiexec -n 4 python3 plot_slices.py snapshots/*.h5
+
+This script can restart the simulation from the last save of the original
+output to extend the integration.  This requires that the output files from
+the original simulation are merged, and the last is symlinked or copied to
+`restart.h5`.
+
+To run the original example and the restart, you could use:
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+    $ mpiexec -n 4 python3 -m dedalus merge_procs snapshots
+    $ ln -s snapshots/snapshots_s2.h5 restart.h5
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+
+The simulations should take a few process-minutes to run.
+
+"""
+
+import numpy as np
+from mpi4py import MPI
+import time
+import pathlib
+import pickle
+import os
+
+from dedalus import public as de
+from dedalus.extras import flow_tools
+from dedalus.extras.plot_tools import plot_bot_2d
+
+import logging
+logger = logging.getLogger(__name__)
+
+
+# Parameters
+Lx, Lz = (4., 1.)
+Prandtl = 1.
+Rayleigh = 2e8
+
+# Create bases and domain
+Nx, Nz = 2048, 512
+x_basis = de.Fourier('x', Nx, interval=(0, Lx), dealias=3/2)
+z_basis = de.Chebyshev('z', Nz, interval=(-Lz/2, Lz/2), dealias=3/2)
[…]

### 2021-03-01 RA2E8/rbc_sim_nom_2e8.sh

@@ -1,0 +1,17 @@
+#PBS -S /bin/bash
+#PBS -N rbc_sim_nom_2e8
+#PBS -l select=4:ncpus=28:mpiprocs=28:model=bro
+#PBS -l walltime=24:00:00
+#PBS -j oe
+module load mpi-sgi/mpt
+module load comp-intel
+export PATH=$HOME/scripts:$PATH
+deactivate
+unset PYTHONPATH
+source ~/miniconda3/etc/profile.d/conda.sh
+export PYTHONNOUSERSITE=1
+conda activate dedalus
+# support lots of text output to stdio for analysis
+export MPI_UNBUFFERED_STDIO=true
+cd ~/scratch/dedalus/EVP_evolution/RA2E8/
+mpiexec_mpt -np 112 python3 rbc_sim_nom.py

### 2021-03-01 RA4E6/rbc_sim_nom.py

@@ -1,0 +1,166 @@
+"""
+Dedalus script for 2D Rayleigh-Benard convection.
+
+This script uses a Fourier basis in the x direction with periodic boundary
+conditions.  The equations are scaled in units of the buoyancy time (Fr = 1).
+
+This script can be ran serially or in parallel, and uses the built-in analysis
+framework to save data snapshots in HDF5 files.  The `merge_procs` command can
+be used to merge distributed analysis sets from parallel runs, and the
+`plot_slices.py` script can be used to plot the snapshots.
+
+To run, merge, and plot using 4 processes, for instance, you could use:
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+    $ mpiexec -n 4 python3 -m dedalus merge_procs snapshots
+    $ mpiexec -n 4 python3 plot_slices.py snapshots/*.h5
+
+This script can restart the simulation from the last save of the original
+output to extend the integration.  This requires that the output files from
+the original simulation are merged, and the last is symlinked or copied to
+`restart.h5`.
+
+To run the original example and the restart, you could use:
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+    $ mpiexec -n 4 python3 -m dedalus merge_procs snapshots
+    $ ln -s snapshots/snapshots_s2.h5 restart.h5
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+
+The simulations should take a few process-minutes to run.
+
+"""
+
+import numpy as np
+from mpi4py import MPI
+import time
+import pathlib
+import pickle
+import os
+
+from dedalus import public as de
+from dedalus.extras import flow_tools
+from dedalus.extras.plot_tools import plot_bot_2d
+
+import logging
+logger = logging.getLogger(__name__)
+
+
+# Parameters
+Lx, Lz = (4., 1.)
+Prandtl = 1.
+Rayleigh = 4e6
+
+# Create bases and domain
+Nx, Nz = 2048, 512
+x_basis = de.Fourier('x', Nx, interval=(0, Lx), dealias=3/2)
+z_basis = de.Chebyshev('z', Nz, interval=(-Lz/2, Lz/2), dealias=3/2)
[…]

### 2021-03-01 RA4E7/rbc_sim_nom.py

@@ -1,0 +1,166 @@
+"""
+Dedalus script for 2D Rayleigh-Benard convection.
+
+This script uses a Fourier basis in the x direction with periodic boundary
+conditions.  The equations are scaled in units of the buoyancy time (Fr = 1).
+
+This script can be ran serially or in parallel, and uses the built-in analysis
+framework to save data snapshots in HDF5 files.  The `merge_procs` command can
+be used to merge distributed analysis sets from parallel runs, and the
+`plot_slices.py` script can be used to plot the snapshots.
+
+To run, merge, and plot using 4 processes, for instance, you could use:
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+    $ mpiexec -n 4 python3 -m dedalus merge_procs snapshots
+    $ mpiexec -n 4 python3 plot_slices.py snapshots/*.h5
+
+This script can restart the simulation from the last save of the original
+output to extend the integration.  This requires that the output files from
+the original simulation are merged, and the last is symlinked or copied to
+`restart.h5`.
+
+To run the original example and the restart, you could use:
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+    $ mpiexec -n 4 python3 -m dedalus merge_procs snapshots
+    $ ln -s snapshots/snapshots_s2.h5 restart.h5
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+
+The simulations should take a few process-minutes to run.
+
+"""
+
+import numpy as np
+from mpi4py import MPI
+import time
+import pathlib
+import pickle
+import os
+
+from dedalus import public as de
+from dedalus.extras import flow_tools
+from dedalus.extras.plot_tools import plot_bot_2d
+
+import logging
+logger = logging.getLogger(__name__)
+
+
+# Parameters
+Lx, Lz = (4., 1.)
+Prandtl = 1.
+Rayleigh = 4e7
+
+# Create bases and domain
+Nx, Nz = 2048, 512
+x_basis = de.Fourier('x', Nx, interval=(0, Lx), dealias=3/2)
+z_basis = de.Chebyshev('z', Nz, interval=(-Lz/2, Lz/2), dealias=3/2)
[…]

### 2021-03-01 RA4E7/rbc_sim_nom_4e7.sh

@@ -1,0 +1,17 @@
+#PBS -S /bin/bash
+#PBS -N rbc_sim_nom_4e7
+#PBS -l select=4:ncpus=28:mpiprocs=28:model=bro
+#PBS -l walltime=24:00:00
+#PBS -j oe
+module load mpi-sgi/mpt
+module load comp-intel
+export PATH=$HOME/scripts:$PATH
+deactivate
+unset PYTHONPATH
+source ~/miniconda3/etc/profile.d/conda.sh
+export PYTHONNOUSERSITE=1
+conda activate dedalus
+# support lots of text output to stdio for analysis
+export MPI_UNBUFFERED_STDIO=true
+cd ~/scratch/dedalus/EVP_evolution/RA4E7/
+mpiexec_mpt -np 112 python3 rbc_sim_nom.py

### 2021-03-01 RA4E9/rbc_sim_nom.py

@@ -1,0 +1,166 @@
+"""
+Dedalus script for 2D Rayleigh-Benard convection.
+
+This script uses a Fourier basis in the x direction with periodic boundary
+conditions.  The equations are scaled in units of the buoyancy time (Fr = 1).
+
+This script can be ran serially or in parallel, and uses the built-in analysis
+framework to save data snapshots in HDF5 files.  The `merge_procs` command can
+be used to merge distributed analysis sets from parallel runs, and the
+`plot_slices.py` script can be used to plot the snapshots.
+
+To run, merge, and plot using 4 processes, for instance, you could use:
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+    $ mpiexec -n 4 python3 -m dedalus merge_procs snapshots
+    $ mpiexec -n 4 python3 plot_slices.py snapshots/*.h5
+
+This script can restart the simulation from the last save of the original
+output to extend the integration.  This requires that the output files from
+the original simulation are merged, and the last is symlinked or copied to
+`restart.h5`.
+
+To run the original example and the restart, you could use:
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+    $ mpiexec -n 4 python3 -m dedalus merge_procs snapshots
+    $ ln -s snapshots/snapshots_s2.h5 restart.h5
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+
+The simulations should take a few process-minutes to run.
+
+"""
+
+import numpy as np
+from mpi4py import MPI
+import time
+import pathlib
+import pickle
+import os
+
+from dedalus import public as de
+from dedalus.extras import flow_tools
+from dedalus.extras.plot_tools import plot_bot_2d
+
+import logging
+logger = logging.getLogger(__name__)
+
+
+# Parameters
+Lx, Lz = (4., 1.)
+Prandtl = 1.
+Rayleigh = 4e9
+
+# Create bases and domain
+Nx, Nz = 2048, 512
+x_basis = de.Fourier('x', Nx, interval=(0, Lx), dealias=3/2)
+z_basis = de.Chebyshev('z', Nz, interval=(-Lz/2, Lz/2), dealias=3/2)
[…]

### 2021-03-01 RA4E9/rbc_sim_nom_4e9.sh

@@ -1,0 +1,17 @@
+#PBS -S /bin/bash
+#PBS -N rbc_sim_nom_4e9
+#PBS -l select=4:ncpus=28:mpiprocs=28:model=bro
+#PBS -l walltime=24:00:00
+#PBS -j oe
+module load mpi-sgi/mpt
+module load comp-intel
+export PATH=$HOME/scripts:$PATH
+deactivate
+unset PYTHONPATH
+source ~/miniconda3/etc/profile.d/conda.sh
+export PYTHONNOUSERSITE=1
+conda activate dedalus
+# support lots of text output to stdio for analysis
+export MPI_UNBUFFERED_STDIO=true
+cd ~/scratch/dedalus/EVP_evolution/RA4E9/
+mpiexec_mpt -np 112 python3 rbc_sim_nom.py

### 2021-03-02 publication_materials/ms_rbc.tex
repaired formatting

--- 2021-02-25 publication_materials/ms_rbc.tex
@@
 \usepackage{varwidth}
+\usepackage{float}
+\usepackage{nonfloat}
+\usepackage{afterpage}
 
@@
 
-\author{Sharrod Brown}
+\author{Liam O'Connor$^1$}
+\author{Daniel Lecoanet$^{1, 2}$}
+\author{Evan Anders$^2$}
 \affiliation{%
-Senator (D), Ohio}
-
-% \author{Daniel Lecoanet}
-% \affiliation{%
-% Physics Department, University of California, Berkeley, CA 94720, USA\\
-% Astronomy Department and Theoretical Astrophysics Center, University of California, Berkeley, CA 94720, USA\\
-% Princeton Center for Theoretical Science, Princeton University, Princeton, NJ 08544, USA\\
-% Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA\\
-% Kavli Institute for Theoretical Physics, University of California, Santa Barbara, CA 93106, USA}
-
-% \author{Rich R. Kerswell}
-% \affiliation{%
-% DAMTP, Centre for Mathematical Sciences, Cambridge University, Cambridge CB3 0WA, UK \\
-% School of Mathematics, University of Bristol, Bristol BS8 1TW, UK\\
-% Kavli Institute for Theoretical Physics, University of California, Santa Barbara, CA 93106, USA}
-% \date{\today}% It is always \today, today,
-%              %  but any date may be explicitly specified
+$^1$Department of Engineering Sciences and Applied Mathematics, Northwestern University, Evanston, IL 60208 USA}
+\affiliation{%
+$^2$Center for Interdisciplinary Exploration and Research in Astrophysics, Northwestern University, Evanston, IL, 60201 USA}
 
 \begin{abstract}
-
-A novel iterative time-marching method is derived by introducing time-dependence in the background temperature profile of the classical Rayleigh-B\'enard Boussinesq linear stability analysis.
+A novel quasilinear form of the Boussinesq Rayleigh-B\'enard equations is derived from the classical linear stability analysis.
 Eigenfunction amplitudes are obtained by requiring marginal-stability.
-Symmetric thermally-equilibrated states are then obtained and their intrinsic properties are analyzed.
+Symmetric thermally-equilibrated states are then obtained and their properties are analyzed.
 Such states are compared with statistically-steady 2-dimensional Rayleigh-Be\'nard convection simulations: marginally-stable thermally-equilibrated states have thinner boundary layers which scale like $\delta \sim Ra^{-1/3}$.
-2-dimensional simulations run with thermally-equilibrated initial conditions turn out to be kinetically exaggerated, consequently requiring increased computational expense when compared to the conventional diffusive initial condition.
-
+2-dimensional simulations are initialized with solutions to the quasilinear problem;
+they do not undergo a convective transient period but turn out to be kinetically exaggerated.
 \end{abstract}
@@
 \section{Introduction}
-
-The introduction leads the reader from a general subject area to a particular topic of inquiry.
-It establishes the scope, context, and significance of the research being conducted by summarizing current understanding and background information about the topic, stating the purpose of the work in the form of the research problem supported by a hypothesis or a set of questions, explaining briefly the methodological approach used to examine the research problem, highlighting the potential outcomes your study can reveal, and outlining the remaining structure and organization of the paper.
-
-% \section{Procedures}\label{sec:procedures}
+Rayleigh-B\'enard convection plays a foundational role in large-scale astrophysical and geophysical systems.
+Highly turbulent systems, such as the convective regions of stars, are not well understood.
+Numerical simulations provide insight into the behavior of convective systems but often times the computational expense is inhibitive.
+convection is important, particularly rbc; full rbc equations are complicated; simplified models give insight into complicated problem; chini's paper gives interesting new way to develop quasilinear approximation; jklfjakjdfskdjfajlsdjfalskdjflaskjdlfjaljsdklfjlajdlfjaklsjdklfjaljklfjakjdf skdjfajlsdjfalskdjflaskjdlfjaljsdklfjlajdlfjaklsjdklfjaljklfjakjdfskdjfajlsdjfa skdjfajlsdjfalskdjflaskjdlfjaljsdklfjlajdlfjaklsjdklfjaljklfjakjdfskdjfajlsdjfalskdjfajlsdjfalskdjflaskjdlfjaljsdklfjlajdlfjaklsjdklfjaljklfjakjdfskdjfajlsdjfal
 \section{Conventional Boussinesq Linear Stability Analysis}\label{sec:boussinesq}
 We begin with the non-dimensionalized Boussinesq approximation for Rayleigh-Bénard Convection.
-The domain is 2-dimensional rectangular and horizontally periodic with spatial dimensions $x$ and $z$ where $0 < x < 4$ and $-1/2 < z < 1/2$.
+The domain is 2-dimensional rectangular and horizontally periodic with spatial dimensions $0 < x < 4$ and $-1/2 < z < 1/2$.
 The fluid of interest is constrained between two planar boundaries at $z = -1/2$ and $z = 1/2$ with fixed temperatures $1$ and $0$ respectively.
@@
 \begin{equation}
-\mathcal{R} = \sqrt{\frac{Pr}{Ra}}, \qquad \mathcal{P} = \frac{1}{\sqrt{Pr Ra}}
+\mathcal{R} = \sqrt{\frac{Pr}{Ra}}, \qquad \mathcal{P} = \frac{1}{\sqrt{Pr Ra}}.
 \end{equation}
 \par To derive the linearized system, we posit that each field can be represented as the sum of a background profile (denoted by $\bar{\cdot } \;$) and a perturbation function (denoted by $\cdot'$).
-Suppose $\frac{\partial \bar{T}}{\partial z}\big|_{t=t_0} (z)$ is some given function which satisfies
+At an arbitrary time $t_0$, suppose $\frac{\partial \bar{T}}{\partial z} (z)$ is some given function which satisfies
 \begin{equation}
-    \int_{-\frac{1}{2}}^{\frac{1}{2}} \frac{\partial \bar{T}}{\partial z}\Big|_{t=t_0} dz = -1
+    \int_{-\frac{1}{2}}^{\frac{1}{2}} \frac{\partial \bar{T}}{\partial z}\Big|_{t=t_0} dz = -1.
 \end{equation}
-then the background profiles are given by
+Then the background profiles are given by
 \begin{align}
@@
     \bar{T}(z) &= 1 + \int_{-\frac{1}{2}}^{z} \frac{\partial \bar{T}}{\partial \zeta}\Big|_{t=t_0}(\zeta) d\zeta \\
-    \bar{p}(z) &= p_0 - \int_{-\frac{1}{2}}^z \bar{T}(\zeta) d\zeta
+    \bar{p}(z) &= p_0 - \int_{-\frac{1}{2}}^z \bar{T}\Big|_{t=t_0}(\zeta) d\zeta.
 \end{align}
-Accordingly, the fields are rewritten as
+Accordingly, the fields are defined as
 \begin{align}
@@
     T(x, z, t) &= \bar{T}(z) + T'(x, z, t) \label{EQ:reynolds_dc_T}\\
-    p(x, z, t) &= \bar{p}(z) + p'(x, z, t)
+    p(x, z, t) &= \bar{p}(z) + p'(x, z, t).
 \end{align}
@@
 \begin{equation}
-    T'|_{z = \pm \frac{1}{2}} = 0, \quad u'|_{z = \pm \frac{1}{2}} = 0, \quad p'|_{z = \pm \frac{1}{2}} = 0
+    T'|_{z = \pm \frac{1}{2}} = 0, \quad u'|_{z = \pm \frac{1}{2}} = 0, \quad p'|_{z = \pm \frac{1}{2}} = 0.
 \end{equation}
@@
     u'(x, z, t) &= U(z) \, e^{i(k_xx-st)} \label{EQ:normal_modes2}\\ 
-    T'(x, z, t) &= \Theta(z) \, e^{i(k_xx-st)} \label{EQ:normal_modes3}\\ 
+    T'(x, z, t) &= \theta(z) \, e^{i(k_xx-st)} \label{EQ:normal_modes3}\\ 
     p'(x, z, t) &= P(z) \, e^{i(k_xx-st)}\label{EQ:normal_modes4}
 \end{align}
-where $s = \sigma + i\omega$ and $k_x$ is constricted by periodicity to the countably infinite set (spectrum) of wavenumbers
+where $s = \sigma + i\omega$ and $k_x$ is constrained, by periodicity, to the countably infinite set (spectrum) of wavenumbers
 \begin{align}
-    k_x \in \big\{\frac{n\pi}{2} \, \big| \, n \in \mathbb{N}\big\}
+    k_x \in \big\{\frac{n\pi}{2} \, \big| \, n \in \mathbb{N}\big\}.
 \end{align}
 For each $k_x$, we can assess the stability of the perturbations by solving for the eigenvalue $s$, whose imaginary component $\omega$ plays the role of an exponential growth rate.
-Solution yields a finite set of eigenvalues, among which, that with the maximum value of $\omega$ is assumed to be dominant.
+Solution yields a finite set of eigenvalues, among which, that with maximum $\omega$ is assumed to be dominant.
 Positive eigenvalues indicate that the system is unstable to small disturbances of wavenumber $k_x$, while negative eigenvalues indicate stability.
-A complete linear stability analysis requires that we solve over the full spectrum of wavenumbers.
-The prototypical case is used to demonstrate that the critical Rayleigh number $Ra_c = 1708$ when $\frac{\partial \bar{T}}{\partial z}\big|_{t=t_0} = -1$.
+A complete linear stability analysis requires solution over the full spectrum of wavenumbers.
+The prototypical case is used to demonstrate that the critical Rayleigh number $Ra_c = 1708$ when $\frac{\partial \bar{T}}{\partial z} = -1$.
 
@@
 The remaining terms in (\ref{EQ:T't_xz}) are unaffected as they are independent of $x$.
-The eigenfunctions $W(z),\, U(z),\, \Theta(z),$ and $P(z)$ do not admit any natural normalization, as (\ref{EQ:linear1}) - (\ref{EQ:linear3}) and their subsequent forms are linear with respect to the perturbations.
+The eigenfunctions $W(z),\, U(z),\, \theta(z),$ and $P(z)$ do not admit any natural normalization, as (\ref{EQ:linear1}) - (\ref{EQ:linear3}) and their subsequent forms are linear with respect to the perturbations.
 For completeness, we provide the normalization
 \begin{equation}
-    \int_{-\frac{1}{2}}^{\frac{1}{2}} \big| \Theta (z) \big| dz = 1
+    \int_{-\frac{1}{2}}^{\frac{1}{2}} \big| \theta (z) \big| dz = 1
 \end{equation}
-and assign each perturbation a yet-unknown amplitude $A \in \mathbb{R}$, thereby allowing us to rewrite (\ref{EQ:T't_xz}) as an initial value problem (IVP)
+and assign each perturbation a yet-unknown amplitude $A \in \mathbb{R}$, thereby allowing us to reduce (\ref{EQ:T't_xz}) to the initial value problem (IVP)
 \begin{equation}
-    \frac{\partial \bar{T}}{\partial t} + A^2 \langle w'T' \rangle = \mathcal{P}  \frac{\partial^2 \bar{T}}{\partial z^2} \label{EQ:T0_IVP}
+    \frac{\partial \bar{T}}{\partial t} + A^2 \langle w'T' \rangle = \mathcal{P}  \frac{\partial^2 \bar{T}}{\partial z^2}, \label{EQ:T0_IVP}
 \end{equation}
@@
 It is important to keep in mind that the forcing term $\langle w'T' \rangle$ is obtained by solving an eigenvalue problem (EVP) which itself involves $\frac{\partial \bar{T}}{\partial z}$.
-We assume that stable modes do not affect the evolution of $\bar{T}$.
+We also assume this term is composed of eigenfunctions belonging to the dominant mode.
 \par For various $Ra$ and fixed $Pr = 1$, we seek symmetric, marginally-stable temperature profiles $\bar{T}_{eq}(z)$ which are thermally equilibrated, thereby satisfying $\frac{\partial \bar{T}_{eq}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}).
 We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:boussinesq} as well as the IVP (\ref{EQ:T0_IVP}) by representing each field with a dealiased Chebshev polynomial basis.
-The necessary number of basis functions varies, as temperature profiles associated with large Rayleigh numbers require increasingly small-scale structures to resolve their aggressive boundary layers.
+The necessary number of basis functions varies, as eigenfunctions and temperature profiles associated with large Rayleigh numbers admit increasingly small-scale features.
 We supplement \texttt{Dedalus} with the \texttt{Eigentools} package to obtain the eigenfunctions in (\ref{EQ:T0_IVP}).
@@
 The spectrum of a marginally-stable background temperature profile $\bar{T}_0$ (shown in black) has a maximum eigenvalue of 0.
-Given a small constant timestep $\Delta t$, diffusion destabilizes the system, increasing its eigenvalues (shown in blue).
+Given a small fixed timestep $\Delta t$, diffusion destabilizes the system, increasing its eigenvalues (shown in blue).
 Advection tends to stabilize the system, decreasing its eigenvalues (shown in red).
@@
 \end{equation}
-where $\omega_{\rm{diff}}$ and $\omega_{\rm{adv}}$ refer to the diffused and advected eigenvalues (corresponding to the blue and red points respectively at $k_x = \pi$ in Figure \ref{fig:iteration_spectra}) of the previously marginal mode.
-$\bar{T}_0$ is then evolved according to (\ref{EQ:T0_IVP}) and another eigenvalue solve is performed on the evolve temperature profile.
-Given a fixed timestep $\Delta t$, we assume the dominant eigenvalue can be described by a smooth function $\omega (A^2)$.
-Newton's method is used to find the appropriate amplitude by approximating $\omega'(A^2)$ with 1st-order finite-differences and specifying a tolerance $1e-9$.
+where $\omega_{\rm{diff}}$ and $\omega_{\rm{adv}}$ refer to the diffused and advected eigenvalues of the initially marginal mode (corresponding to the blue and red points respectively at $k_x = \pi$ in Figure \ref{fig:iteration_spectra}).
+$\bar{T}_0$ is then evolved according to (\ref{EQ:T0_IVP}) and another eigenvalue solve is performed.
+Given a fixed timestep $\Delta t$, we assume the dominant eigenvalue can be described by a continuous function $\omega_{\rm{max}} (A^2)$ which is locally differentiable.
+Newton's method is used to find an amplitude which meets our marginal stability tolerance criterion $|\omega_{\rm{max}} (A^2)| \leq 10^{-9}$.
 The dominant mode is not fixed; an iteration can facilitate the transfer of marginal-stability from one mode to another.
@@
 \subsection{Initial buoyancy profile} \label{sec:initial_profile}
-In an attempt to minimize the required number of iterations, we employ the analytical thermal boundary layer equation for turbulent Rayleigh-B\'enard convection given by \ref{ref:BL_EQs}
+In an attempt to minimize the required number of iterations, we initialize with \cite{Shishkina}'s analytical thermal boundary layer equation for turbulent Rayleigh-B\'enard convection, given by 
 \begin{align}
@@
 We expect that each $\Ra$ is associated with a unique $\delta_0$ for which $\bar{T}_0(z)$ is marginally-stable.
-It should be noted that when experimenting with different initial profiles, we obtain congruent equilibrated states, suggesting that these states may be unique.
+It should be noted that when experimenting with various initial profiles $(\tanh, \rm{erf}, \rm{etc.})$, we obtain indistinguishable equilibrated states, implying that solutions may be unique.
 An example of (\ref{EQ:T0}) is given by the blue curve in Figure \ref{fig:T0_profiles}.
@@
 Should we converge upon a negative amplitude, that mode is discarded and the iteration is repeated.
-In general we find that any other course of action fails to equilibrate.
+In general we find that no other obvious course of action yields equilibria.
 
 \section{Properties of Thermally Equilibrated States}\label{sec:properties}
-Thermally equilibrated states of this kind are solutions to the quasilinear Rayleigh-B\'enard convection equations.
+Thermally equilibrated states of this kind are solutions to a particular quasilinear form of the Rayleigh-B\'enard convection equations.
 For this investigation, we calculate solutions for $Ra$ in the range $10^5 - 10^9$.
-Thermal equilibrium is synonymous with constant heat flux by (\ref{EQ:T0_IVP}).
 Solutions are symmetric about $z = 0$ by design.
-This, combined with the fact that we did initialize a background horizontal flow implies the absence of any nonconstant horizontal flow perturbations.
+This, combined with the fact that we did initialize a background horizontal flow implies the absence of any nonconstant horizontal velocity perturbations.
 
@@
 The initial profile is given by (\ref{EQ:T0}).
-The equilibrated curve refers to the background temperature profile of the marginally-stable thermally equilibrated state.
+The equilibrated curve refers to the background temperature profile of the marginally-stable thermally-equilibrated state.
 The simulation profile is obtained by performing a 2-dimensional nonlinear simulation with \texttt{Dedalus} until thermal and kinetic relaxation.
-The simulation temperature data are horizontally and time averaged.
+The simulation temperature data are horizontally- and time-averaged.
 The initial, equilibrated, and simulation profiles have increasingly relaxed boundary regions (respectively).
@@
 Advection profiles belong to marginally-stable modes.
-For low $Ra$ a single mode with $k_x = 1.5\pi$ is sufficient to oppose  boundary layer diffusion and facilitate heat flux throughout the bulk of the domain.
-For large $Ra$, high-wavenumber marginally-stable modes contribute pronounced small-scale advection profiles which tightly hug the thin boundary layers.
-A combination of these of gradually widening advection profiles is necessary to transition to the $k_x = 1.5\pi$ mode.}
+For low $Ra$, a single mode with $k_x = 1.5\pi$ is sufficient to oppose boundary layer diffusion and facilitate heat flux throughout the bulk of the domain.
+For large $Ra$, high-wavenumber modes contribute pronounced small-scale advection profiles which tightly hug the thin boundary layers.
+A combination of of progressively wider advection profiles is necessary to transition to the $k_x = 1.5\pi$ mode.}
     \label{fig:flux}
@@
 
-\par Figure \ref{fig:T0_profiles} gives temperature profiles for $Ra = 10^8$, where the initial profile, given by (\ref{EQ:T0}), is employed at iteration 0; the equilibrated profile corresponds to the thermally relaxed state; and the simulation profile is obtained by performing a nonlinear simulation of (\ref{EQ:motion1})-(\ref{EQ:motion3}) with \texttt{Dedalus}, followed by horizontal and time averaging.
-The simulation curve is more diffuse than the equilibrated curve, which in turn, is more diffuse than the initial curve.
-Performing an eigenvalue solve by setting $\bar{T}$ equal to the simulation profile yields positive eigenvalues.
-Comprehensively, this suggests that thermally-equilibrated states might maximize boundary layer thickness, while subject to the marginal stability constraint.
-\par The most resilient and unexpected feature of thermally equilibrated background temperature profiles are the pronounced dips adjacent to the boundary layers.
-These dips appear in every solution, regardless of $Ra$.
-Physically, they correspond to thin layers in which the temperature gradient reverses.
-This counter-diffusion, which opposes the overall heat transfer, is overcome by the coinciding advective flux, shown in Figure \ref{fig:flux}.
-
-Equilibrated states exhibit distinct behaviors for large and small $Ra$.
-This contrast is illustrated in Figure \ref{fig:flux}, where we give heat flux profiles and eigenvalue spectra for two cases: $Ra = 2 \times 10^5$ and $Ra = 10^9$.
-For lower $Ra$, there is a single presumed local maximum in the eigenvalue spectrum, whose adjacent modes' advection profiles occupy the bulk of the domain.
-These states have relaxed boundary regions which gradually subside as the advection becomes the dominant component of the total flux.
-These transitional regions do not appear in high $Ra$ cases, where the shift from diffusion to advection is sharp, requiring pronounced, small-scale advection profiles belonging to modes adjacent to the third presumed local maximum in the eigenvalue spectrum.
-Traversing towards the midplane of the domain, we see increasingly thicker advection profiles corresponding the wavenumbers adjacent to the second local maximum, eventually culminating in the dominant $k_x = 1.5\pi$ mode.
-
 \begin{figure}[h]
-    \centering
-    \includegraphics[width=3.4in]{del_ra.PNG}
-    \caption{Boundary layer widths $\delta$ of marginally-stable thermal equilibria.
-We define the threshold of each boundary layer as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, corresponding to the local extrema of the equilibrated curve in Figure \ref{fig:T0_profiles}.
-Plotting on a log-log scale, we find $\delta$ and $Ra$ obey a power-law relationship.
-We also demonstrate that $Ra^{1/3}\delta$ is approximately constant with respect to $Ra$ implying $Ra \propto  \delta^{-3}$, as predicted by \ref{source:???} (scaling arguments literature)}
-    \label{fig:bl_ra}
-\end{figure}
-
-Thermally equilibrated states with large $Ra$ tend to have a more diverse set of marginal modes as compared to small $Ra$ state.
-In every case, the $k_x = 1.5\pi$ mode is included and is often unaccompanied by adjacent modes.
-In Figure \ref{fig:kx_marginals} we give the wavenumbers $k_x$ of marginal modes, color coded accordingly to their adjacency to each other.
-Marginal modes often appear in neighboring pairs, in which case the larger mode is denoted with an x marker and the smaller mode is denoted with a + marker.
-In these cases we infer the existence of a local maximum eigenvalue between the two adjacent marginally-stable modes.
-For $Ra \geq 10^6$, a second branch of marginal modes is introduced as shown in green, increasing according to some power-law with respect to $Ra$.
-The introduction of this largest branch is likely required to oppose the diffusion of the thinner boundary layers.
-For $Ra \geq 10^8$, a third branch of modes appears (shown in red), splitting the widening gap between the blue branch and the green branch.
-This development is associated with the relatively thick advection profiles, filling a niche in the total flux by uniting the sharp advection profiles of the largest branch (green) and the bulk-domain-oriented smallest branch (blue).
-
-\begin{figure}[t]
     \centering
@@
 \end{figure}
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=3.4in]{del_ra.PNG}
+    \caption{Boundary layer widths $\delta$ of marginally-stable thermal equilibria.
+We define the threshold of each boundary layer as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, corresponding to the local extrema of the equilibrated curve in Figure \ref{fig:T0_profiles}.
+Plotting on a log-log scale, we find $\delta$ and $Ra$ obey a power-law relationship.
+We also demonstrate that $Ra^{1/3}\delta$ is approximately constant with respect to $Ra$ implying $Ra \propto  \delta^{-3}$, as predicted by \cite{Malkus}}
+    \label{fig:bl_ra}
+\end{figure}
+\par Figure \ref{fig:T0_profiles} gives temperature profiles for $Ra = 10^8$ where the initial profile, given by (\ref{EQ:T0}), is employed at iteration 0; the equilibrated profile corresponds to the thermally relaxed state; and the simulation profile is obtained by performing a nonlinear simulation of (\ref{EQ:motion1})-(\ref{EQ:motion3}) with \texttt{Dedalus}, followed by horizontal and time averaging.
+The simulation curve is more diffuse than the equilibrated curve, which in turn, is more diffuse than the initial curve.
+Performing an eigenvalue solve by setting $\bar{T}$ equal to the simulation profile yields positive eigenvalues.
+Comprehensively, this suggests that thermally-equilibrated states might maximize boundary layer thickness, while subject to the marginal stability constraint.
+\par The most resilient and unexpected feature of thermally equilibrated background temperature profiles are the pronounced dips adjacent to the boundary layers.
+These dips appear in every solution, regardless of $Ra$.
+Physically, they correspond to thin layers in which the temperature gradient reverses, contradicting a hypothesis of \cite{Malkus}.
+This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure \ref{fig:flux}.
 
-\par In general, marginally-stable thermal equilibria can be characterized by their boundary layer thicknesses, from which, the rest of their properties follow.
-Letting the interior boundary layer threshold be the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, we find that $Ra \propto  \delta^{-3}$ as illustrated in Figure \ref{fig:bl_ra}.
-This is consistent with Malkus' marginal-stability theory, a scaling argument which perceives the boundary regions as subdomains which are themselves marginally-stable \ref{source:Malkus?}.
+Equilibrated states exhibit distinct behaviors for large and small $Ra$.
+This contrast is illustrated in Figure \ref{fig:flux}, where we give heat flux profiles and eigenvalue spectra for two cases: $Ra = 2 \times 10^5$ and $Ra = 10^9$.
+For lower $Ra$, there is a single presumed local maximum in the eigenvalue spectrum, whose adjacent modes' advection profiles occupy the bulk of the domain.
+These states have relaxed boundary layers which gradually subside as advection becomes the dominant component of the total flux.
+Such transitional regions do not appear in high $Ra$ cases, where the shift from diffusion to advection is sharp, requiring pronounced, small-scale advection profiles belonging to modes adjacent to the third presumed local maximum in the eigenvalue spectrum.
+Traversing towards the midplane of the domain, we see increasingly thicker advection profiles corresponding the wavenumbers adjacent to the second local maximum, eventually culminating in the dominant $k_x = 1.5\pi$ mode.
 
-\begin{figure}[t]
+\begin{figure}[h]
     \centering
@@
 
-Nusselt numbers $Nu$ for marginally-stable thermally-equilibrated states and direct numerical simulations are given in Figure \ref{fig:nu_vs_ra}.
-Marginally-stable $Nu$ exceed simulation $Nu$, in agreement with the differing boundary layer geometries shown in Figure \ref{fig:T0_profiles}.
-Both datasets exhibit power-law relationships with $Ra$, and more specifically, $Ra \sim Nu^3$ which agrees with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} and the scaling argument given by \ref{source:Malkus}.
+Thermally equilibrated states with large $Ra$ tend to have a more diverse set of marginal modes as compared to small $Ra$ states.
+In every case, the $k_x = 1.5\pi$ mode is included and is often unaccompanied by adjacent modes.
+In Figure \ref{fig:kx_marginals} we give the wavenumbers $k_x$ of marginal modes, color coded accordingly to their respective adjacencies.
+Marginal modes often appear in neighboring pairs, in which case the larger mode is denoted with an x and the smaller mode is denoted with a +.
+In these cases we infer the existence of a local maximum eigenvalue between the two adjacent marginally-stable modes.
+For $Ra \geq 10^6$, a second branch of marginal modes is introduced as shown in green, increasing according to some power-law with respect to $Ra$.
+The introduction of this largest branch is likely required to oppose the diffusion of the thinning boundary layers.
+For $Ra \geq 10^8$, a third branch appears (shown in red), splitting the widening gap between the blue branch and the green branch.
+This development is associated with relatively thick advection profiles, filling a niche in the total flux by uniting the sharp profiles of the largest branch (green) and those of the bulk-domain-oriented smallest branch (blue).
 
-\begin{figure*}[t]
-    \centering
+\par In general, marginally-stable thermal equilibria can be characterized by their boundary layer thicknesses, from which, the rest of their properties follow.
+Letting the interior boundary layer threshold be the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, we find that $Ra \propto  \delta^{-3}$ as illustrated in Figure \ref{fig:bl_ra}.
+This is consistent with Malkus' marginal-stability theory, a scaling argument which perceives the boundary regions as subdomains which are themselves marginally-stable.
+
+Nusselt numbers $Nu$ of various solutions are given in Figure \ref{fig:nu_vs_ra}.
+The marginally-stable thermally-equilibrated states and numerical simulation data exhibit power-law relationships with $Ra$.
+More specifically, $Ra \sim Nu^3$ which agrees with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} and the scaling argument given by \cite{Malkus}.
+The nonlinear solutions, which maximize heat flux, are obtained \cite{Waleffe}.
+$Nu$ of both equilibria exceed that of simulations, which might be due to the transitional behaviors outlined by \cite{Yalniz} inhibitting heat flux.
+\begin{figure*}
+    \centering%
     \includegraphics[width=7.1in]{nu_ra.PNG}
-    \caption{Nusselt numbers are shown for marginally-stable thermally-equilibrated states and statistically-steady nonlinear simulations performed on Equations (\ref{EQ:motion1}) - (\ref{EQ:motion3}) with ???
-other spectral methods ???.
-Both obey power-law relationships with $Ra$, with $Ra \sim Nu^3$ in agreement with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} as well as \ref{source:Malkus} Malkus???
-($\gamma = 3$ marginally-stable boundary layer scaling argument).
+    \caption{Nusselt numbers are shown for marginally-stable thermally-equilibrated states, statistically-steady direct numericals simulations performed with \texttt{Dedalus} \cite{Anders_cd}, and equilibrated nonlinear solutions, which maximize heat flux, given by \cite{Waleffe}.
+Both obey power-law relationships with $Ra$, with $Ra \sim Nu^3$ in agreement with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} as well as \cite{Malkus}.
 Marginally-stable states' Nusselt numbers exceed simulation Nusselt numbers.
-This can be well explained by the contrasting boundary region geometries shown in Figure \ref{fig:T0_profiles}.}
-    \label{fig:nu_vs_ra}
+This can be well explained by the contrasting boundary region geometries shown in Figure \ref{fig:T0_profiles}.}%
+    \label{fig:nu_vs_ra}%
 \end{figure*}
@@
 \section{Simulations with Thermally Equilibrated Initial Conditions}
-This is investigation is partially motivated by the prospect of decreasing nonlinear simulation relaxation times by employing thermally-equilibrated initial conditions.
+This investigation is partially motivated by the prospect of decreasing nonlinear simulation relaxation times by employing thermally-equilibrated initial conditions.
 Conventionally, (\ref{EQ:motion1}) - (\ref{EQ:motion3}) are solved via direct numerical simulation (DNS) with initial conditions
@@
 \begin{align}
-    T(x, z)\big|_{t=0} &= \bar{T}(z) + \sqrt{2} \sum_{n=1}^N  A^2_n \text{ Re} \Big[ \Theta_n(z) e^{ik_{x_n}x} \Big] \nonumber \\
-    \mathbf{u}(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A^2_n \text{ Re} \Big[\Big( U_n (z) \hat{x} + W_n(z) \hat{z} \Big) e^{ik_{x_n}x} \Big] \nonumber\\
-    p(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A^2_n \text{ Re} \Big[P_n (z) e^{ik_{x_n}x}\Big]
+    T(x, z)\big|_{t=0} &= \bar{T}(z) + \sqrt{2} \sum_{n=1}^N  A_n \text{ Re} \Big[ \theta_n(z) e^{ik_{x_n}x} \Big] \nonumber \\
+    \mathbf{u}(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A_n \text{ Re} \Big[\Big( U_n (z) \hat{x} + W_n(z) \hat{z} \Big) e^{ik_{x_n}x} \Big] \nonumber\\
+    p(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A_n \text{ Re} \Big[P_n (z) e^{ik_{x_n}x}\Big]
 \end{align}
-\begin{figure}[h]
+Where $\theta_n(z), U_n(z), W_n(z), P_n(z); \, A_n; $ and $k_{x_n}$ refer to the complex eigenfunctions, amplitude, and wavenumber at the $n$th marginal mode.
+The $\sqrt{2}$ factor is necessary for eigenfunction normalization.
+By construction, these initial conditions are thermally equilibrated.
+Simulations launched with equilibrated initial conditions do not exhibit a convective-transient period, as the large-scale anatomy of plumes and convective winds which are characteristic of Rayleigh-B\'enard convection exist on initialization.
+This is illustrated in Figure \ref{fig:nu_sim}, where the sharp spike in $Nu$ is associated with a turbulent transitional period of upwelling until the distinctive jet-like structure is established.
+\begin{figure}
     \centering
@@
 \end{figure}
-Where $\Theta_n(z), U_n(z), W_n(z), P_n(z); \, A^2; $ and $k_{x_n}$ refer to the complex eigenfunctions, amplitude, and wavenumber at the $n$th marginal mode.
-The $\sqrt{2}$ factor is necessary normalize the eigenfunctions according to the new domain ???.
-By construction, these initial conditions are thermally equilibrated.
-Simulations launched with equilibrated initial conditions do not exhibit a convective-transient period, as the large-scale anatomy of the characteristic plumes and convective winds of Rayleigh-B\'enard convection exist on initialization.
-This is illustrated in Figure \ref{fig:nu_sim}, where the sharp spike in $Nu$ is associated with the turbulent transition period of upwelling until the distinctive jet-like structure is established.
 \par The marginally-stable equilibria are associated with a combination of eigenfunctions whose average kinetic energy is significantly larger than the statistical steady state, as given by Figure \ref{fig:ke_sim}.
-This is impairs kinetic relaxation because the large horizontal flows decay on a viscous timescale
+This is postpones kinetic relaxation because the large horizontal flows decay on a viscous timescale
 \begin{equation}
-    t_{\nu} \sim \frac{Pr}{\sqrt{Ra}}. \nonumber
+    t_{\nu} \sim \sqrt{\frac{Ra}{Pr}}. \nonumber
 \end{equation}
@@
     \includegraphics[width=3.4in]{sim_eq_ke.png}
-    \caption{Average kinetic energies of the same simulations performed in Figure \ref{fig:nu_sim} ($Ra \, = \, 10^8$).
+    \caption{Average kinetic energies of the same simulations performed in Figure \ref{fig:nu_sim} ($Ra = 10^8$).
 The combination of eigenfunctions which give thermal equilibrium have significantly more kinetic energy than the statistically steady state.
@@
 \section*{Acknowledgments}
-We thank the people of Ohio.
+Jeff Vassil, Greg Chini,
 
-\bibliography{she}
+% \bibliography{she}
+\begin{thebibliography}{99}
+
+\bibitem{Malkus} Malkus W. V. R. 1954 The heat transport and spectrum of thermal turbulenceProc. R. Soc. Lond. A225196–212
+
+\bibitem{Howard} Howard L.N. (1966) Convection at high Rayleigh number. In: Görtler H. (eds) Applied Mechanics
+
+\bibitem{Chini_la} Chini, G., Malecha, Z., \& Dreeben, T. (2014). Large-amplitude acoustic streaming. Journal of Fluid Mechanics, 744, 329-351. doi:10.1017/jfm.2014.61
+
+\bibitem{Chini_sw} Michel, G., \& Chini, G. (2019). Strong wave–mean-flow coupling in baroclinic acoustic streaming. Journal of Fluid Mechanics, 858, 536-564. doi:10.1017/jfm.2018.785
+
+\bibitem{Shishkina} Olga Shishkina, Susanne Horn, Sebastian Wagner, Phys. Rev. Lett. 114
+
+\bibitem{Anders_cd} Evan H. Anders, Geoffrey M. Vasil, Benjamin P. Brown, and Lydia Korre Phys. Rev. Fluids 5, 083501
+
+\bibitem{Waleffe} Waleffe F., Boonkasame A., Smith L.M. Heat transport by coherent Rayleigh–Bénard convection Phys. Fluids, 27 (2015), Article 051702
+
+\bibitem{Yalniz} Coarse graining the state space of a turbulent flow using periodic orbits Yalnız, Gökhan; Hof, Björn; Burak Budanur, Nazmi
+
+\end{thebibliography}
 

### 2021-03-02 publication_materials/ms_rbc.tex
introduction rev 1

@@
 Symmetric thermally-equilibrated states are then obtained and their properties are analyzed.
-Such states are compared with statistically-steady 2-dimensional Rayleigh-Be\'nard convection simulations: marginally-stable thermally-equilibrated states have thinner boundary layers which scale like $\delta \sim Ra^{-1/3}$.
+Such states are compared with statistically-steady 2-dimensional Rayleigh-Be\'nard convection simulations; marginally-stable thermally-equilibrated states have thinner boundary layers which scale like $\delta \sim Ra^{-1/3}$.
 2-dimensional simulations are initialized with solutions to the quasilinear problem;
@@
 \section{Introduction}
-Rayleigh-B\'enard convection plays a foundational role in large-scale astrophysical and geophysical systems.
-Highly turbulent systems, such as the convective regions of stars, are not well understood.
-Numerical simulations provide insight into the behavior of convective systems but often times the computational expense is inhibitive.
-convection is important, particularly rbc; full rbc equations are complicated; simplified models give insight into complicated problem; chini's paper gives interesting new way to develop quasilinear approximation; jklfjakjdfskdjfajlsdjfalskdjflaskjdlfjaljsdklfjlajdlfjaklsjdklfjaljklfjakjdf skdjfajlsdjfalskdjflaskjdlfjaljsdklfjlajdlfjaklsjdklfjaljklfjakjdfskdjfajlsdjfa skdjfajlsdjfalskdjflaskjdlfjaljsdklfjlajdlfjaklsjdklfjaljklfjakjdfskdjfajlsdjfalskdjfajlsdjfalskdjflaskjdlfjaljsdklfjlajdlfjaklsjdklfjaljklfjakjdfskdjfajlsdjfal
+Rayleigh-B\'enard convection plays a foundational role in large-scale astrophysical and geophysical settings.
+Our understanding of highly turbulent convective systems is generally limited by the prohibitive computational costs associated with direct numerical simulations \cite{Zhu}.
+There exists a substantial body of work concerning the asymptotic scaling laws of such systems with no general consensous.
+Reduced models are particularly useful in this context because they allow us to study the underlying behavior of turbulent convection with relatively low expense.
+\par In this investigation, we derive and solve a quasilinear form of the Boussinesq Rayleigh–Bénard convection equations using a strategy similar to \cite{Chini_sw}.
+This is realized by solving the linearized equations and evolving a mean temperature profile according to the perturbation variables.
+In general, each set of perturbations has an arbitrary amplitude which we obtain by imposing marginal stability.
+The application of this procedure yields time-invariant solutions to the quasilinear problem with a range of expected and unexpected features.
+\par Reduced models are often valuable when supplemented by direct simulation [source?].
+Nonlinear simulations perfomed with quasilinear solutions as initial conditions do not undergo a convective transient period of turbulent upwelling.
+Instead, the characteristic jet-like structure is somewhat present on initialization.
+This is practical because the convective transient period generally involves high-Reynolds number flows whose resolution is prohibitive.
 \section{Conventional Boussinesq Linear Stability Analysis}\label{sec:boussinesq}
@@
 \end{equation}
-\par To derive the linearized system, we posit that each field can be represented as the sum of a background profile (denoted by $\bar{\cdot } \;$) and a perturbation function (denoted by $\cdot'$).
+\par To derive the linearized system, we posit that each field can be represented as the sum of a mean profile (denoted by $\bar{\cdot } \;$) and a perturbation function (denoted by $\cdot'$).
 At an arbitrary time $t_0$, suppose $\frac{\partial \bar{T}}{\partial z} (z)$ is some given function which satisfies
@@
 \end{equation}
-Then the background profiles are given by
+Then the mean profiles are given by
 \begin{align}
@@
     \caption{Eigenvalue spectra for $Ra = 10^5$.
-The spectrum of a marginally-stable background temperature profile $\bar{T}_0$ (shown in black) has a maximum eigenvalue of 0.
+The spectrum of a marginally-stable mean temperature profile $\bar{T}_0$ (shown in black) has a maximum eigenvalue of 0.
 Given a small fixed timestep $\Delta t$, diffusion destabilizes the system, increasing its eigenvalues (shown in blue).
 Advection tends to stabilize the system, decreasing its eigenvalues (shown in red).
-It follows that there exists some proportion ($A^2$) of these two terms which yields a new marginally-stable background temperature profile $\bar{T}_1$, whose spectrum is shown in green.}
+It follows that there exists some proportion ($A^2$) of these two terms which yields a new marginally-stable mean temperature profile $\bar{T}_1$, whose spectrum is shown in green.}
     \label{fig:iteration_spectra} 
@@
 Solutions are symmetric about $z = 0$ by design.
-This, combined with the fact that we did initialize a background horizontal flow implies the absence of any nonconstant horizontal velocity perturbations.
-
+This, combined with the fact that we did initialize a mean horizontal flow implies the absence of any nonconstant horizontal velocity perturbations.
+\par Figure \ref{fig:T0_profiles} gives temperature profiles for $Ra = 10^8$ where the initial profile, given by (\ref{EQ:T0}), is employed at iteration 0; the equilibrated profile corresponds to the thermally relaxed state; and the simulation profile is obtained by performing a nonlinear simulation of (\ref{EQ:motion1})-(\ref{EQ:motion3}) with \texttt{Dedalus}, followed by horizontal and time averaging.
+The simulation curve is more diffuse than the equilibrated curve, which in turn, is more diffuse than the initial curve.
+Performing an eigenvalue solve by setting $\bar{T}$ equal to the simulation profile yields positive eigenvalues.
+Comprehensively, this suggests that thermally-equilibrated states might maximize boundary layer thickness, while subject to the marginal stability constraint.
+\par The most resilient and unexpected feature of thermally equilibrated mean temperature profiles are the pronounced dips adjacent to the boundary layers.
+These dips appear in every solution, regardless of $Ra$.
+Physically, they correspond to thin layers in which the temperature gradient reverses, contradicting a hypothesis of \cite{Malkus}.
+This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure \ref{fig:flux}.
 \begin{figure}[h]
@@
     \includegraphics[width=3.4in]{T_profs_na.png}
-    \caption{Background temperature profiles $\bar{T}$ for $Ra = 10^8$.
+    \caption{mean temperature profiles $\bar{T}$ for $Ra = 10^8$.
 The initial profile is given by (\ref{EQ:T0}).
-The equilibrated curve refers to the background temperature profile of the marginally-stable thermally-equilibrated state.
+The equilibrated curve refers to the mean temperature profile of the marginally-stable thermally-equilibrated state.
 The simulation profile is obtained by performing a 2-dimensional nonlinear simulation with \texttt{Dedalus} until thermal and kinetic relaxation.
@@
 
-\begin{figure*}[t]
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=3.4in]{kx_m_ra1.png}
+    \caption{Wavenumbers of marginally-stable modes of thermally equilibrated states.
+Markers are color-coded according to their adjacent local maxima index in the eigenvalue spectrum.
+For example, the spectrum corresponding to $Ra = 10^5$ has marginal wavenumbers $k_x = \pi, \, 1.5\pi$ adjacent to a presumed local maximum between these two allowed values.
+The $Ra = 10^9$ spectrum, shown in lower right corner of Figure \ref{fig:flux}, has three presumed local maxima, with a single marginal mode adjacent to the first maximum ($k_x = 1.5\pi$), two marginal modes adjacent to the second maximum ($k_x = 6\pi, \, 6.5\pi$), and two marginal modes adjacent to the third maximum ($k_x = 23.5\pi, \, 24\pi$).
+The largest wavenumbers of the green branch obey a power-law relationship with $Ra$}
+    \label{fig:kx_marginals}
+\end{figure}
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=3.4in]{del_kx_inv.png}
+    \caption{For $Ra \geq 10^6$, the maximum marginally-stable wavenumber (corresponding to the green X markers in Figure \ref{fig:kx_marginals}) are inversely related to the boundary layer thicknesses $\delta$.
+$(\max \{ k_x \})^{-1}$ gives a minimum $x$ length scale for the perturbations, and consequently, the advection.
+We expect the minimum $z$ length scale to agree with the boundary layer thickness $\delta$ because otherwise the boundary layer would continue to diffuse.
+This is well illustrated in the lower left corner of Figure \ref{fig:flux}, where the advection profile for $k_x = 24\pi$ is tightly flanked by the surrounding boundary layers.
+This suggests that the minimum $x$ and $z$ length scales obey some constant ratio.}
+    \label{fig:del_inv}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=3.4in]{del_ra.PNG}
+    \caption{Boundary layer widths $\delta$ of marginally-stable thermal equilibria.
+We define the threshold of each boundary layer as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, corresponding to the local extrema of the equilibrated curve in Figure \ref{fig:T0_profiles}.
+Plotting on a log-log scale, we find $\delta$ and $Ra$ obey a power-law relationship.
+We also demonstrate that $Ra^{1/3}\delta$ is approximately constant with respect to $Ra$ implying $Ra \propto  \delta^{-3}$, as predicted by \cite{Malkus}}
+    \label{fig:bl_ra}
+\end{figure}
+
+\begin{figure*}
     \centering
@@
     \label{fig:flux}
+    \vspace{0.4in}
+    \includegraphics[width=7.1in]{nu_ra.PNG}
+    \caption{Nusselt numbers are shown for marginally-stable thermally-equilibrated states, statistically-steady direct numericals simulations performed with \texttt{Dedalus} \cite{Anders_cd}, and equilibrated nonlinear solutions, which maximize heat flux, given by \cite{Waleffe}.
+Both obey power-law relationships with $Ra$, with $Ra \sim Nu^3$ in agreement with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} as well as \cite{Malkus}.
+Marginally-stable states' Nusselt numbers exceed simulation Nusselt numbers.
+This can be well explained by the contrasting boundary region geometries shown in Figure \ref{fig:T0_profiles}.}%
+    \label{fig:nu_vs_ra}%
 \end{figure*}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=3.4in]{kx_m_ra1.png}
-    \caption{Wavenumbers of marginally-stable modes of thermally equilibrated states.
-Markers are color-coded according to their adjacent local maxima index in the eigenvalue spectrum.
-For example, the spectrum corresponding to $Ra = 10^5$ has marginal wavenumbers $k_x = \pi, \, 1.5\pi$ adjacent to a presumed local maximum between these two allowed values.
-The $Ra = 10^9$ spectrum, shown in lower right corner of Figure \ref{fig:flux}, has three presumed local maxima, with a single marginal mode adjacent to the first maximum ($k_x = 1.5\pi$), two marginal modes adjacent to the second maximum ($k_x = 6\pi, \, 6.5\pi$), and two marginal modes adjacent to the third maximum ($k_x = 23.5\pi, \, 24\pi$).
-The largest wavenumbers of the green branch obey a power-law relationship with $Ra$}
-    \label{fig:kx_marginals}
-\end{figure}
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=3.4in]{del_ra.PNG}
-    \caption{Boundary layer widths $\delta$ of marginally-stable thermal equilibria.
-We define the threshold of each boundary layer as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, corresponding to the local extrema of the equilibrated curve in Figure \ref{fig:T0_profiles}.
-Plotting on a log-log scale, we find $\delta$ and $Ra$ obey a power-law relationship.
-We also demonstrate that $Ra^{1/3}\delta$ is approximately constant with respect to $Ra$ implying $Ra \propto  \delta^{-3}$, as predicted by \cite{Malkus}}
-    \label{fig:bl_ra}
-\end{figure}
-\par Figure \ref{fig:T0_profiles} gives temperature profiles for $Ra = 10^8$ where the initial profile, given by (\ref{EQ:T0}), is employed at iteration 0; the equilibrated profile corresponds to the thermally relaxed state; and the simulation profile is obtained by performing a nonlinear simulation of (\ref{EQ:motion1})-(\ref{EQ:motion3}) with \texttt{Dedalus}, followed by horizontal and time averaging.
-The simulation curve is more diffuse than the equilibrated curve, which in turn, is more diffuse than the initial curve.
-Performing an eigenvalue solve by setting $\bar{T}$ equal to the simulation profile yields positive eigenvalues.
-Comprehensively, this suggests that thermally-equilibrated states might maximize boundary layer thickness, while subject to the marginal stability constraint.
-\par The most resilient and unexpected feature of thermally equilibrated background temperature profiles are the pronounced dips adjacent to the boundary layers.
-These dips appear in every solution, regardless of $Ra$.
-Physically, they correspond to thin layers in which the temperature gradient reverses, contradicting a hypothesis of \cite{Malkus}.
-This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure \ref{fig:flux}.
 
@@
 Traversing towards the midplane of the domain, we see increasingly thicker advection profiles corresponding the wavenumbers adjacent to the second local maximum, eventually culminating in the dominant $k_x = 1.5\pi$ mode.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=3.4in]{del_kx_inv.png}
-    \caption{For $Ra \geq 10^6$, the maximum marginally-stable wavenumber (corresponding to the green X markers in Figure \ref{fig:kx_marginals}) are inversely related to the boundary layer thicknesses $\delta$.
-$(\max \{ k_x \})^{-1}$ gives a minimum $x$ length scale for the perturbations, and consequently, the advection.
-We expect the minimum $z$ length scale to agree with the boundary layer thickness $\delta$ because otherwise the boundary layer would continue to diffuse.
-This is well illustrated in the lower left corner of Figure \ref{fig:flux}, where the advection profile for $k_x = 24\pi$ is tightly flanked by the surrounding boundary layers.
-This suggests that the minimum $x$ and $z$ length scales obey some constant ratio.}
-    \label{fig:del_inv}
-\end{figure}
 
@@
 $Nu$ of both equilibria exceed that of simulations, which might be due to the transitional behaviors outlined by \cite{Yalniz} inhibitting heat flux.
-\begin{figure*}
-    \centering%
-    \includegraphics[width=7.1in]{nu_ra.PNG}
-    \caption{Nusselt numbers are shown for marginally-stable thermally-equilibrated states, statistically-steady direct numericals simulations performed with \texttt{Dedalus} \cite{Anders_cd}, and equilibrated nonlinear solutions, which maximize heat flux, given by \cite{Waleffe}.
-Both obey power-law relationships with $Ra$, with $Ra \sim Nu^3$ in agreement with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} as well as \cite{Malkus}.
-Marginally-stable states' Nusselt numbers exceed simulation Nusselt numbers.
-This can be well explained by the contrasting boundary region geometries shown in Figure \ref{fig:T0_profiles}.}%
-    \label{fig:nu_vs_ra}%
-\end{figure*}
 
@@
 
+\bibitem{Zhu} Xiaojue Zhu, Varghese Mathai, Richard J.
+A.
+M.
+Stevens, Roberto Verzicco, and Detlef Lohse (2018).
+Transition to the Ultimate Regime in Two-Dimensional Rayleigh-Bénard Convection.
+Phys.
+Rev.
+Lett.
+120, 144502
+
 \bibitem{Malkus} Malkus W. V. R. 1954 The heat transport and spectrum of thermal turbulenceProc. R. Soc. Lond. A225196–212

### 2021-03-03 publication_materials/ms_rbc.tex
reformatted with subfigs

@@
 Solutions are symmetric about $z = 0$ by design.
-This, combined with the fact that we did initialize a mean horizontal flow implies the absence of any nonconstant horizontal velocity perturbations.
+This, combined with the fact that we did initialize a mean horizontal flow implies the absence of any nonconstant horizontal velocity perturbations, as is the case in \cite{Waleffe}.
 \par Figure \ref{fig:T0_profiles} gives temperature profiles for $Ra = 10^8$ where the initial profile, given by (\ref{EQ:T0}), is employed at iteration 0; the equilibrated profile corresponds to the thermally relaxed state; and the simulation profile is obtained by performing a nonlinear simulation of (\ref{EQ:motion1})-(\ref{EQ:motion3}) with \texttt{Dedalus}, followed by horizontal and time averaging.
@@
 This is illustrated in Figure \ref{fig:nu_sim}, where the sharp spike in $Nu$ is associated with a turbulent transitional period of upwelling until the distinctive jet-like structure is established.
-\begin{figure}
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=3.4in]{sim_eq_nu.png}
+%     \caption{Nusselt numbers of simulations performed at $Ra \, = \, 10^8$ with conventional initial conditions (red) and marginally-stable thermally-equilibrated initial conditions (blue).
+Simulations launched with thermally-equilibrated states do not undergo a convective-transient period because the characteristic plume structure exists on initialization.
+This is illustrated by the $Nu$ spike at $t \sim 15$ in the convectional simulation.}
+%     \label{fig:nu_sim}
+% \end{figure}
+\par The marginally-stable equilibria are associated with a combination of eigenfunctions whose average kinetic energy is significantly larger than the statistical steady state, as given by Figure \ref{fig:ke_sim}.
+This is postpones kinetic relaxation because the large horizontal flows decay on a viscous timescale
+\begin{equation}
+    t_{\nu} \sim \sqrt{\frac{Ra}{Pr}}. \nonumber
+\end{equation}
+Consequently, marginally-stable thermally-equilibrated initial conditions do not reduce the simulation time required to achieve a statistically steady state, rather, they increase it considerably.
+% \begin{figure}[h]
+%     \centering
+%     \includegraphics[width=3.4in]{sim_eq_ke.png}
+%     \caption{Average kinetic energies of the same simulations performed in Figure \ref{fig:nu_sim} ($Ra = 10^8$).
+The combination of eigenfunctions which give thermal equilibrium have significantly more kinetic energy than the statistically steady state.
+Kinetic equilibrium is achieved according to the viscous timescale $t_{\nu} \sim Pr Ra^{-1/2}$.}
+%     \label{fig:ke_sim}
+% \end{figure}
+\begin{figure*}
+    \begin{minipage}[t]{3.4in}
         \centering
@@
         \label{fig:nu_sim}
-\end{figure}
-\par The marginally-stable equilibria are associated with a combination of eigenfunctions whose average kinetic energy is significantly larger than the statistical steady state, as given by Figure \ref{fig:ke_sim}.
-This is postpones kinetic relaxation because the large horizontal flows decay on a viscous timescale
-\begin{equation}
-    t_{\nu} \sim \sqrt{\frac{Ra}{Pr}}. \nonumber
-\end{equation}
-Consequently, marginally-stable thermally-equilibrated initial conditions do not reduce the simulation time required to achieve a statistically steady state, rather, they increase it considerably.
-\begin{figure}[h]
+    \end{minipage}
+    \hfill
+    \begin{minipage}[t]{3.4in}
         \centering
@@
         \label{fig:ke_sim}
-\end{figure}
-
-\section{Conclusion}\label{sec:conclusion}
-
-\section*{Appendix}
-This is an appendix
+    \end{minipage}
+\end{figure*}
+\section{Discussion}\label{sec:Discussion}
+In general, the reduced form we derive and solve in this paper can be perceived as a unique way to describe Rayleigh–Bénard convection.
+Solutions to the quasilinear problem retain several key features that are ubiquitous in experiments and simulations: power-law $Nu$ scaling, plume-like structures, and minimum length-scale approximations \cite{Malkus}.
+They also exhibit unique and unexpected features: temperature profile geometries, thinner boundary layers, and greater $Nu$ than other time-invarient solutions.
+% \section*{Appendix}
+% This is an appendix
 
 \section*{Acknowledgments}
-Jeff Vassil, Greg Chini,
+The authors thank Jeff Vassil, Greg Chini, Emma Kaufman for feedback and suggestions.
 

### 2021-03-03 publication_materials/ms_rbc.tex
conclusion rev 1

@@
 \usepackage{nonfloat}
-\usepackage{afterpage}
-
+% \usepackage{afterpage}
 \usepackage[usenames, dvipsnames]{color}
@@
 Our understanding of highly turbulent convective systems is generally limited by the prohibitive computational costs associated with direct numerical simulations \cite{Zhu}.
-There exists a substantial body of work concerning the asymptotic scaling laws of such systems with no general consensous.
+There exists a substantial body of work concerning the asymptotic scaling laws of such systems with no general consensus.
 Reduced models are particularly useful in this context because they allow us to study the underlying behavior of turbulent convection with relatively low expense.
@@
 \par Reduced models are often valuable when supplemented by direct simulation [source?].
-Nonlinear simulations perfomed with quasilinear solutions as initial conditions do not undergo a convective transient period of turbulent upwelling.
+Nonlinear simulations performed with quasilinear solutions as initial conditions do not undergo a convective transient period of turbulent upwelling.
 Instead, the characteristic jet-like structure is somewhat present on initialization.
@@
 The nonlinear solutions, which maximize heat flux, are obtained \cite{Waleffe}.
-$Nu$ of both equilibria exceed that of simulations, which might be due to the transitional behaviors outlined by \cite{Yalniz} inhibitting heat flux.
+$Nu$ of both equilibria exceed that of simulations, which might be due to the transitional behaviors outlined by \cite{Yalniz} inhibiting heat flux.
 
@@
 % \end{figure}
-\begin{figure*}
+\begin{figure*}[t]
     \begin{minipage}[t]{3.4in}
@@
 The combination of eigenfunctions which give thermal equilibrium have significantly more kinetic energy than the statistically steady state.
-Kinetic equilibrium is achieved according to the viscous timescale $t_{\nu} \sim Pr Ra^{-1/2}$.}
+Kinetic equilibrium is achieved according to the viscous timescale $t_{\nu} \sim \sqrt{Ra / Pr}$.}
         \label{fig:ke_sim}
@@
 \section{Discussion}\label{sec:Discussion}
-In general, the reduced form we derive and solve in this paper can be perceived as a unique way to describe Rayleigh–Bénard convection.
+In general, the reduced model we study in this paper can be perceived as a unique way to describe Rayleigh–Bénard convection.
 Solutions to the quasilinear problem retain several key features that are ubiquitous in experiments and simulations: power-law $Nu$ scaling, plume-like structures, and minimum length-scale approximations \cite{Malkus}.
-They also exhibit unique and unexpected features: temperature profile geometries, thinner boundary layers, and greater $Nu$ than other time-invarient solutions.
+They also exhibit unique and unexpected features: gradient-reversal/dips in temperature profiles, kinetic exaggeration, and greater $Nu$ than other time-invariant solutions.
+We also obtain indistinguishable solutions despite initializing with different mean temperature profiles $\bar{T}$.
+Thus solutions might be unique, but we cannot demonstrate this rigorously.
+\par The quasilinear problem can also be generalized to include an asymmetric mean horizontal-flow.
+Specifically, a second initial value problem, similar to (\ref{EQ:T0_IVP}), can be derived for $\bar{u}$.
+Doing so might yield solutions with greater resemblance to DNS results because we expect the Reynolds stress tensor to combat the kinetic exaggeration shown in Figure \ref{fig:ke_sim}.
+For this investigation, we require symmetry at each iteration, but the thermal evolution procedure appears unstable to asymmetry.
+This could be accommodated by requiring rotational symmetry about the midplane $\bar{u}(z, t) = -\bar{u}(z, t)$.
+It's unclear whether solutions with nontrivial $\bar{u}$ exist or whether our algorithm would converge under these different circumstances.
+
 % \section*{Appendix}
@@
 \section*{Acknowledgments}
-The authors thank Jeff Vassil, Greg Chini, Emma Kaufman for feedback and suggestions.
+The authors thank Jeff Vassil, Greg Chini, Emma Kaufman for their valuable feedback and suggestions.
+We also thank the \texttt{Dedalus} and \texttt{Eigentools} developers.
+Computations were performed on the NASA Pleiades system.
 

### 2021-03-05 publication_materials/ms_rbc.tex
doc formatting; append gitignore

@@
 \end{figure}
-
 \begin{figure}[h]
@@
 \end{figure}
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=3.4in]{del_kx_inv.png}
-    \caption{For $Ra \geq 10^6$, the maximum marginally-stable wavenumber (corresponding to the green X markers in Figure \ref{fig:kx_marginals}) are inversely related to the boundary layer thicknesses $\delta$.
-$(\max \{ k_x \})^{-1}$ gives a minimum $x$ length scale for the perturbations, and consequently, the advection.
-We expect the minimum $z$ length scale to agree with the boundary layer thickness $\delta$ because otherwise the boundary layer would continue to diffuse.
-This is well illustrated in the lower left corner of Figure \ref{fig:flux}, where the advection profile for $k_x = 24\pi$ is tightly flanked by the surrounding boundary layers.
-This suggests that the minimum $x$ and $z$ length scales obey some constant ratio.}
-    \label{fig:del_inv}
-\end{figure}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=3.4in]{del_ra.PNG}
-    \caption{Boundary layer widths $\delta$ of marginally-stable thermal equilibria.
-We define the threshold of each boundary layer as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, corresponding to the local extrema of the equilibrated curve in Figure \ref{fig:T0_profiles}.
-Plotting on a log-log scale, we find $\delta$ and $Ra$ obey a power-law relationship.
-We also demonstrate that $Ra^{1/3}\delta$ is approximately constant with respect to $Ra$ implying $Ra \propto  \delta^{-3}$, as predicted by \cite{Malkus}}
-    \label{fig:bl_ra}
-\end{figure}
-
 \begin{figure*}
@@
     \includegraphics[width=7.1in]{nu_ra.PNG}
-    \caption{Nusselt numbers are shown for marginally-stable thermally-equilibrated states, statistically-steady direct numericals simulations performed with \texttt{Dedalus} \cite{Anders_cd}, and equilibrated nonlinear solutions, which maximize heat flux, given by \cite{Waleffe}.
+    \caption{Nusselt numbers are shown for marginally-stable thermally-equilibrated states, statistically-steady direct numerical simulations performed with \texttt{Dedalus} \cite{Anders_cd}, and equilibrated nonlinear solutions, which maximize heat flux, given by \cite{Waleffe}.
 Both obey power-law relationships with $Ra$, with $Ra \sim Nu^3$ in agreement with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} as well as \cite{Malkus}.
@@
 \end{figure*}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=3.4in]{del_kx_inv.png}
+    \caption{For $Ra \geq 10^6$, the maximum marginally-stable wavenumber (corresponding to the green X markers in Figure \ref{fig:kx_marginals}) are inversely related to the boundary layer thicknesses $\delta$.
+$(\max \{ k_x \})^{-1}$ gives a minimum $x$ length scale for the perturbations, and consequently, the advection.
+We expect the minimum $z$ length scale to agree with the boundary layer thickness $\delta$ because otherwise the boundary layer would continue to diffuse.
+This is well illustrated in the lower left corner of Figure \ref{fig:flux}, where the advection profile for $k_x = 24\pi$ is tightly flanked by the surrounding boundary layers.
+This suggests that the minimum $x$ and $z$ length scales obey some constant ratio.}
+    \label{fig:del_inv}
+\end{figure}
 
@@
 For this investigation, we require symmetry at each iteration, but the thermal evolution procedure appears unstable to asymmetry.
-This could be accommodated by requiring rotational symmetry about the midplane $\bar{u}(z, t) = -\bar{u}(z, t)$.
+This could be accommodated by requiring rotational symmetry about the midplane $\bar{u}(z, t) = -\bar{u}(-z, t)$.
 It's unclear whether solutions with nontrivial $\bar{u}$ exist or whether our algorithm would converge under these different circumstances.

### 2021-03-17 plot_ke.py
append p0 to sim IC

@@ -31,7 +31,7 @@ def main(filename, start, count, output):
 
     # Plot writes
     with h5py.File(filename, mode='r') as file:
-        ke_data = pickle.load(open(path + '/ke_data_nom.pick', 'rb'))
+        ke_data = pickle.load(open(path + '/ke_data_eq2.pick', 'rb'))
         ke_ar = ke_data['ke_ar']
         # ke_max_ar = ke_data['ke_max_ar']
         sim_times_ar = ke_data['sim_times_ar']
@@ -41,7 +41,7 @@ def main(filename, start, count, output):
             sim_times_ar.append(file['scales/sim_time'][index])
         ke_data['ke_ar'] = ke_ar
         ke_data['sim_times_ar'] = sim_times_ar
-        pickle.dump(ke_data, open(path + '/ke_data_nom.pick', 'wb'))
+        pickle.dump(ke_data, open(path + '/ke_data_eq2.pick', 'wb'))
         
 
 
@@ -60,7 +60,7 @@ if __name__ == "__main__":
         args = docopt(__doc__)
         output_path = pathlib.Path(args['--output']).absolute()
         ke_data = {'ke_ar' : [], 'sim_times_ar' : []}
-        pickle.dump(ke_data, open(path + '/ke_data_nom.pick', 'wb'))
+        pickle.dump(ke_data, open(path + '/ke_data_eq2.pick', 'wb'))
 
         # Create output directory if needed
         with Sync() as sync:
@@ -69,7 +69,7 @@ if __name__ == "__main__":
                     output_path.mkdir()
         post.visit_writes(args['<files>'], main, output=output_path)
     else:
-        ke_data_eq = pickle.load(open(path + '/ke_data_eq.pick', 'rb'))
+        ke_data_eq = pickle.load(open(path + '/ke_data_eq2.pick', 'rb'))
         ke_data = pickle.load(open(path + '/ke_data_nom.pick', 'rb'))
 
         ke_ar_eq = ke_data_eq['ke_ar']
@@ -84,4 +84,4 @@ if __name__ == "__main__":
         plt.ylabel(r'$\overline{|\mathbf{u}|^2}$')
         plt.title(r'$Ra \, = \, 10^8$')
         # plt.savefig(path + '/pubfigs/sim_eq_ke')
-        plt.savefig(path + '/publication_materials/sim_eq_ke')
+        plt.savefig(path + '/publication_materials/sim_eq_ke_p0')

### 2021-03-17 rbc_sim_load_ic.py

@@ -140,8 +140,10 @@ if not pathlib.Path('restart.h5').exists():
     # plot_bot_2d(b)
     # plt.show()
 
+    p0 = b0.antidifferentiate(z_basis, ('left', 0))
+    p0.set_scales(evp_scale)
+    p['g'] = -p0['g'] + np.sqrt(2)*(sum([exp*fields['p'][:, None][slices[1]].transpose() for (exp, fields) in exp_fields])).real
     w['g'] = np.sqrt(2)*(sum([exp*fields['w'][:, None][slices[1]].transpose() for (exp, fields) in exp_fields])).real
-    p['g'] = np.sqrt(2)*(sum([exp*fields['p'][:, None][slices[1]].transpose() for (exp, fields) in exp_fields])).real
     u['g'] = np.sqrt(2)*(sum([exp*fields['u'][:, None][slices[1]].transpose() for (exp, fields) in exp_fields])).real
     wz = w.differentiate('z')
     uz = u.differentiate('z')
@@ -178,13 +180,13 @@ solver.stop_sim_time = stop_sim_time
 # snapshots.add_task('w')
 # snapshots.add_task('u')
 
-profiles = solver.evaluator.add_file_handler('profiles_eq', sim_dt=0.1, max_writes=100, mode=fh_mode)
+profiles = solver.evaluator.add_file_handler('profiles_eq_p0', sim_dt=0.1, max_writes=100, mode=fh_mode)
 profiles.add_task("P*integ(dz(b) - 1, 'x') / Lx", name='diffusive_flux')
 profiles.add_task("integ(w*b, 'x') / Lx", name='adv_flux')
 profiles.add_task("integ(integ(w**2 + u**2, 'x'), 'z') / Lx", name='ke')
 profiles.add_task("integ(integ((dx(w) - uz)**2, 'x'), 'z') / Lx", name='enst')
 
-checkpoints = solver.evaluator.add_file_handler('checkpoints_eq', sim_dt=0.5, max_writes=50, mode=fh_mode)
+checkpoints = solver.evaluator.add_file_handler('checkpoints_eq_p0', sim_dt=0.5, max_writes=50, mode=fh_mode)
 checkpoints.add_system(solver.state)
 # snapshots.add_task('b')
 

### 2021-03-17 publication_materials/ms_rbc.tex

@@
 \newcommand{\note}[1]{\noindent \textbf{\textit{\textcolor{Red}{#1}}}}
-
-\newcommand\mnras{\rmfamily{Mon. Not. R. Astron. Soc.}}
-\newcommand\aap{\rmfamily{Astron. Astrophys.}}
-\newcommand\apjl{\rmfamily{Astrophys. J. Lett.}}
-
-\newcommand\Beq{\begin{eqnarray}} 
-\newcommand\Eeq{\end{eqnarray}}
-
-\newcommand\Bfig{\begin{figure}} 
-\newcommand\Efig{\end{figure}}
 
@@
     \bar{T}(z) &= 1 + \int_{-\frac{1}{2}}^{z} \frac{\partial \bar{T}}{\partial \zeta}\Big|_{t=t_0}(\zeta) d\zeta \\
-    \bar{p}(z) &= p_0 - \int_{-\frac{1}{2}}^z \bar{T}\Big|_{t=t_0}(\zeta) d\zeta.
+    \bar{p}(z) &= p_0 + \int_{-\frac{1}{2}}^z \bar{T}\Big|_{t=t_0}(\zeta) d\zeta.
 \end{align}
@@
 
-\subsection{Initial buoyancy profile} \label{sec:initial_profile}
-In an attempt to minimize the required number of iterations, we initialize with \cite{Shishkina}'s analytical thermal boundary layer equation for turbulent Rayleigh-B\'enard convection, given by 
-\begin{align}
-    \bar{T}_0(\xi) &= \frac{\sqrt{3}}{4\pi} \log \frac{(1 + a\xi)^3}{1 + (a\xi)^3} + \frac{3}{2\pi} \arctan \Big( \frac{4\pi}{9}\xi - \frac{1}{\sqrt{3}} \Big) + \frac{1}{4} \nonumber \\
-    \xi &= \frac{z}{\delta_0}, \qquad a = \frac{2\pi}{3\sqrt{3}}\label{EQ:T0}
-\end{align}
-where $\delta_0$ is the boundary layer thickness.
-We expect that each $\Ra$ is associated with a unique $\delta_0$ for which $\bar{T}_0(z)$ is marginally-stable.
-It should be noted that when experimenting with various initial profiles $(\tanh, \rm{erf}, \rm{etc.})$, we obtain indistinguishable equilibrated states, implying that solutions may be unique.
-An example of (\ref{EQ:T0}) is given by the blue curve in Figure \ref{fig:T0_profiles}.
-
 \subsection{Treatment of multiple marginally-stable modes} \label{sec:multiple_modes}
@@
     \caption{Nusselt numbers are shown for marginally-stable thermally-equilibrated states, statistically-steady direct numerical simulations performed with \texttt{Dedalus} \cite{Anders_cd}, and equilibrated nonlinear solutions, which maximize heat flux, given by \cite{Waleffe}.
-Both obey power-law relationships with $Ra$, with $Ra \sim Nu^3$ in agreement with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} as well as \cite{Malkus}.
+Both obey power-law relationships with $Ra$, with $Ra \sim \Nu^3$ in agreement with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} as well as \cite{Malkus}.
 Marginally-stable states' Nusselt numbers exceed simulation Nusselt numbers.
@@
     \label{fig:del_inv}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=3.4in]{del_ra.PNG}
+    \caption{Boundary layer widths $\delta$ of marginally-stable thermal equilibria.
+We define the threshold of each boundary layer as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, corresponding to the local extrema of the equilibrated curve in Figure \ref{fig:T0_profiles}.
+Plotting on a log-log scale, we find $\delta$ and $Ra$ obey a power-law relationship.
+We also demonstrate that $Ra^{1/3}\delta$ is approximately constant with respect to $Ra$ implying $Ra \propto  \delta^{-3}$, as predicted by \cite{Malkus}}
+    \label{fig:bl_ra}
 \end{figure}
@@
 
-Nusselt numbers $Nu$ of various solutions are given in Figure \ref{fig:nu_vs_ra}.
+Nusselt numbers $\Nu$ of various solutions are given in Figure \ref{fig:nu_vs_ra}.
 The marginally-stable thermally-equilibrated states and numerical simulation data exhibit power-law relationships with $Ra$.
-More specifically, $Ra \sim Nu^3$ which agrees with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} and the scaling argument given by \cite{Malkus}.
+More specifically, $Ra \sim \Nu^3$ which agrees with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} and the scaling argument given by \cite{Malkus}.
 The nonlinear solutions, which maximize heat flux, are obtained \cite{Waleffe}.
-$Nu$ of both equilibria exceed that of simulations, which might be due to the transitional behaviors outlined by \cite{Yalniz} inhibiting heat flux.
+$\Nu$ of both equilibria exceed that of simulations, which might be due to the transitional behaviors outlined by \cite{Yalniz} inhibiting heat flux.
 
@@
 Simulations launched with equilibrated initial conditions do not exhibit a convective-transient period, as the large-scale anatomy of plumes and convective winds which are characteristic of Rayleigh-B\'enard convection exist on initialization.
-This is illustrated in Figure \ref{fig:nu_sim}, where the sharp spike in $Nu$ is associated with a turbulent transitional period of upwelling until the distinctive jet-like structure is established.
+This is illustrated in Figure \ref{fig:nu_sim}, where the sharp spike in $\Nu$ is associated with a turbulent transitional period of upwelling until the distinctive jet-like structure is established.
 % \begin{figure}
@@
 Simulations launched with thermally-equilibrated states do not undergo a convective-transient period because the characteristic plume structure exists on initialization.
-This is illustrated by the $Nu$ spike at $t \sim 15$ in the convectional simulation.}
+This is illustrated by the $\Nu$ spike at $t \sim 15$ in the convectional simulation.}
         \label{fig:nu_sim}
@@
 In general, the reduced model we study in this paper can be perceived as a unique way to describe Rayleigh–Bénard convection.
-Solutions to the quasilinear problem retain several key features that are ubiquitous in experiments and simulations: power-law $Nu$ scaling, plume-like structures, and minimum length-scale approximations \cite{Malkus}.
-They also exhibit unique and unexpected features: gradient-reversal/dips in temperature profiles, kinetic exaggeration, and greater $Nu$ than other time-invariant solutions.
+Solutions to the quasilinear problem retain several key features that are ubiquitous in experiments and simulations: power-law $\Nu$ scaling, plume-like structures, and minimum length-scale approximations \cite{Malkus}.
+They also exhibit unique and unexpected features: gradient-reversal/dips in temperature profiles, kinetic exaggeration, and greater $\Nu$ than other time-invariant solutions.
 We also obtain indistinguishable solutions despite initializing with different mean temperature profiles $\bar{T}$.
@@
 
-% \section*{Appendix}
-% This is an appendix
+\section*{Appendix}
+\subsection{Initial buoyancy profile} \label{sec:initial_profile}
+In an attempt to minimize the required number of iterations, we initialize with \cite{Shishkina}'s analytical thermal boundary layer equation for turbulent Rayleigh-B\'enard convection, given by 
+\begin{align}
+    \bar{T}_0(\xi) &= \frac{\sqrt{3}}{4\pi} \log \frac{(1 + a\xi)^3}{1 + (a\xi)^3} + \frac{3}{2\pi} \arctan \Big( \frac{4\pi}{9}\xi - \frac{1}{\sqrt{3}} \Big) + \frac{1}{4} \nonumber \\
+    \xi &= \frac{z}{\delta_0}, \qquad a = \frac{2\pi}{3\sqrt{3}}\label{EQ:T0}
+\end{align}
+where $\delta_0$ is the boundary layer thickness.
+We expect that each $\Ra$ is associated with a unique $\delta_0$ for which $\bar{T}_0(z)$ is marginally-stable.
+It should be noted that when experimenting with various initial profiles $(\tanh, \rm{erf}, \rm{etc.})$, we obtain indistinguishable equilibrated states, implying that solutions may be unique.
+An example of (\ref{EQ:T0}) is given by the blue curve in Figure \ref{fig:T0_profiles}.
 

### 2021-04-07 publication_materials/ms_rbc.tex
abstract rev2a

@@
 \begin{abstract}
-A novel quasilinear form of the Boussinesq Rayleigh-B\'enard equations is derived from the classical linear stability analysis.
+Reduced models give us some understanding of the behavior of complicated systems.
+We derive a quasilinear form of the Boussinesq Rayleigh-B\'enard equations from the classical linear stability analysis.
 Eigenfunction amplitudes are obtained by requiring marginal-stability.
-Symmetric thermally-equilibrated states are then obtained and their properties are analyzed.
-Such states are compared with statistically-steady 2-dimensional Rayleigh-Be\'nard convection simulations; marginally-stable thermally-equilibrated states have thinner boundary layers which scale like $\delta \sim Ra^{-1/3}$.
-2-dimensional simulations are initialized with solutions to the quasilinear problem;
+We obtain symmetric thermally-equilibrated states and analyze their properties.
+Such states are compared with statistically-steady 2-dimensional Rayleigh-Be\'nard convection simulations; marginally-stable thermally-equilibrated states have thinner boundary layers and larger Nusselt numbers $\Nu$ which scale like $\Nu \sim Ra^{1/3}$.
+We initialize 2-dimensional simulations with solutions to the quasilinear problem;
 they do not undergo a convective transient period but turn out to be kinetically exaggerated.

### 2021-04-07 publication_materials/ms_rbc.tex
abstract rev2b

--- 2021-03-17 publication_materials/ms_rbc.tex
@@
 \begin{abstract}
-A novel quasilinear form of the Boussinesq Rayleigh-B\'enard equations is derived from the classical linear stability analysis.
-Eigenfunction amplitudes are obtained by requiring marginal-stability.
-Symmetric thermally-equilibrated states are then obtained and their properties are analyzed.
-Such states are compared with statistically-steady 2-dimensional Rayleigh-Be\'nard convection simulations; marginally-stable thermally-equilibrated states have thinner boundary layers which scale like $\delta \sim Ra^{-1/3}$.
-2-dimensional simulations are initialized with solutions to the quasilinear problem;
-they do not undergo a convective transient period but turn out to be kinetically exaggerated.
+Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important properties remain elusive -- particularly in the large Rayleigh number limit.
+In this investigation, we derive and solve a quasilinear form of the Boussinesq Rayleigh-B\'enard equations. 
+Eigenfunction amplitudes are obtained by requiring marginal-stability. We obtain symmetric thermally-equilibrated solutions and analyze their properties. 
+We compare these solutions with statistically-steady 2-dimensional Rayleigh-Be\'nard convection simulations; marginally-stable thermally-equilibrated states have thinner boundary layers and larger Nusselt numbers $\Nu$ which scale like $\Nu \sim Ra^{1/3}$.
+We initialize 2-dimensional simulations with solutions to the quasilinear problem; they do not undergo a convective transient period and are kinetically exaggerated.
 \end{abstract}
@@
 Rayleigh-B\'enard convection plays a foundational role in large-scale astrophysical and geophysical settings.
-Our understanding of highly turbulent convective systems is generally limited by the prohibitive computational costs associated with direct numerical simulations \cite{Zhu}.
+Our understanding of turbulent convective systems is generally limited by the prohibitive computational costs associated with direct numerical simulations \cite{Zhu}.
 There exists a substantial body of work concerning the asymptotic scaling laws of such systems with no general consensus.
 Reduced models are particularly useful in this context because they allow us to study the underlying behavior of turbulent convection with relatively low expense.
-\par In this investigation, we derive and solve a quasilinear form of the Boussinesq Rayleigh–Bénard convection equations using a strategy similar to \cite{Chini_sw}.
+
+In this investigation, we derive and solve a quasilinear form of the Boussinesq Rayleigh–Bénard convection equations using a strategy similar to \cite{Chini_sw}.
 This is realized by solving the linearized equations and evolving a mean temperature profile according to the perturbation variables.

### 2021-04-07 publication_materials/ms_rbc.tex
formatting: new lines for sentences

@@
 The application of this procedure yields time-invariant solutions to the quasilinear problem with a range of expected and unexpected features.
-\par Reduced models are often valuable when supplemented by direct simulation [source?].
+
+Reduced models are often valuable when supplemented by direct simulation [source?]. 
 Nonlinear simulations performed with quasilinear solutions as initial conditions do not undergo a convective transient period of turbulent upwelling. 
@@
 This is practical because the convective transient period generally involves high-Reynolds number flows whose resolution is prohibitive.
+
 \section{Conventional Boussinesq Linear Stability Analysis}\label{sec:boussinesq}
@@
 \end{equation}
-\par To derive the linearized system, we posit that each field can be represented as the sum of a mean profile (denoted by $\bar{\cdot } \;$) and a perturbation function (denoted by $\cdot'$).
+
+To derive the linearized system, we posit that each field can be represented as the sum of a mean profile (denoted by $\bar{\cdot } \;$) and a perturbation function (denoted by $\cdot'$). 
 At an arbitrary time $t_0$, suppose $\frac{\partial \bar{T}}{\partial z} (z)$ is some given function which satisfies
@@
 \par For various $Ra$ and fixed $Pr = 1$, we seek symmetric, marginally-stable temperature profiles $\bar{T}_{eq}(z)$ which are thermally equilibrated, thereby satisfying $\frac{\partial \bar{T}_{eq}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}).
-We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:boussinesq} as well as the IVP (\ref{EQ:T0_IVP}) by representing each field with a dealiased Chebshev polynomial basis.
+We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:boussinesq} as well as the IVP (\ref{EQ:T0_IVP}) by representing each field with a dealiased Chebyshev polynomial basis.
 The necessary number of basis functions varies, as eigenfunctions and temperature profiles associated with large Rayleigh numbers admit increasingly small-scale features. 
 We supplement \texttt{Dedalus} with the \texttt{Eigentools} package to obtain the eigenfunctions in (\ref{EQ:T0_IVP}).
-\par To find an equilibrated profile, we begin with a marginally-stable initial profile $\bar{T}_0(z)$ whose construction is outlined in \ref{sec:initial_profile}.
+
+To find an equilibrated profile, we begin with a marginally-stable initial profile $\bar{T}_0(z)$ whose construction is outlined in \ref{sec:initial_profile}. 
 We seek to evolve $\bar{T}_0(z)$ into a new marginally-stable profile $\bar{T}_1(z)$ according to (\ref{EQ:T0_IVP}) using forward-Euler. 
@@
 
-\begin{figure}[h]
+\begin{figure}
     \includegraphics[width=3.4in]{EV_spectrum_ol.png}
-    \caption{Eigenvalue spectra for $Ra = 10^5$.
-The spectrum of a marginally-stable mean temperature profile $\bar{T}_0$ (shown in black) has a maximum eigenvalue of 0.
+    \caption{Eigenvalue spectra for $Ra = 10^5$. The spectrum of a marginally-stable mean temperature profile $\bar{T}_0$ (shown in black) has a maximum eigenvalue of 0. 
     Given a small fixed timestep $\Delta t$, diffusion destabilizes the system, increasing its eigenvalues (shown in blue). 
@@
 An iteration is performed as follows: diffusing a marginally-stable temperature profile $\bar{T}_0$ tends to increase its eigenvalues. 
-Ignoring the diffusive term and evolving according to advection tends the stabilize the system.
-The appropriate amplitude $A^2$ can then be approximated by
+Ignoring the diffusive term and evolving according to advection tends the stabilize the system. The appropriate amplitude $A^2$ can then be approximated by
 \begin{equation}
@@
 For this investigation, we calculate solutions for $Ra$ in the range $10^5 - 10^9$. 
-Solutions are symmetric about $z = 0$ by design.
-This, combined with the fact that we did initialize a mean horizontal flow implies the absence of any nonconstant horizontal velocity perturbations, as is the case in \cite{Waleffe}.
-\par Figure \ref{fig:T0_profiles} gives temperature profiles for $Ra = 10^8$ where the initial profile, given by (\ref{EQ:T0}), is employed at iteration 0; the equilibrated profile corresponds to the thermally relaxed state; and the simulation profile is obtained by performing a nonlinear simulation of (\ref{EQ:motion1})-(\ref{EQ:motion3}) with \texttt{Dedalus}, followed by horizontal and time averaging.
+Solutions are symmetric about $z = 0$ by construction. 
+This, combined with the fact that we did initialize a mean horizontal flow implies the absence of any nonzero horizontal velocity perturbations, as is the case in \cite{Waleffe}.
+
+Figure \ref{fig:T0_profiles} gives temperature profiles for $Ra = 10^8$ where the initial profile, given by (\ref{EQ:T0}), is employed at iteration 0; the equilibrated profile corresponds to the thermally relaxed state; and the simulation profile is obtained by performing a nonlinear simulation of (\ref{EQ:motion1})-(\ref{EQ:motion3}) with \texttt{Dedalus}, followed by horizontal and time averaging.
 The simulation curve is more diffuse than the equilibrated curve, which in turn, is more diffuse than the initial curve. 
@@
 Comprehensively, this suggests that thermally-equilibrated states might maximize boundary layer thickness, while subject to the marginal stability constraint.
-\par The most resilient and unexpected feature of thermally equilibrated mean temperature profiles are the pronounced dips adjacent to the boundary layers.
+
+The most resilient and unexpected feature of thermally equilibrated mean temperature profiles are the pronounced dips adjacent to the boundary layers. 
 These dips appear in every solution, regardless of $Ra$. 
@@
 This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure \ref{fig:flux}. 
-\begin{figure}[h]
+\begin{figure}
     \centering
@@
 \end{figure}
-\begin{figure}[h]
+\begin{figure}
     \centering
@@
 
-\begin{figure}[h]
+\begin{figure}
     \centering
@@
     We expect the minimum $z$ length scale to agree with the boundary layer thickness $\delta$ because otherwise the boundary layer would continue to diffuse. 
-This is well illustrated in the lower left corner of Figure \ref{fig:flux}, where the advection profile for $k_x = 24\pi$ is tightly flanked by the surrounding boundary layers.
+    This is illustrated in the lower left corner of Figure \ref{fig:flux}, where the advection profile for $k_x = 24\pi$ is tightly flanked by the surrounding boundary layers. 
     This suggests that the minimum $x$ and $z$ length scales obey some constant ratio.}
@@
 
-\par In general, marginally-stable thermal equilibria can be characterized by their boundary layer thicknesses, from which, the rest of their properties follow.
+In general, marginally-stable thermal equilibria can be characterized by their boundary layer thicknesses, from which, the rest of their properties follow.
 Letting the interior boundary layer threshold be the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, we find that $Ra \propto  \delta^{-3}$ as illustrated in Figure \ref{fig:bl_ra}.
-This is consistent with Malkus' marginal-stability theory, a scaling argument which perceives the boundary regions as subdomains which are themselves marginally-stable.
+This is consistent with Malkus' classical marginal-stability theory, a scaling argument which perceives the boundary regions as subdomains which are themselves marginally-stable.
 
@@
 \end{align}
-Where $\theta_n(z), U_n(z), W_n(z), P_n(z); \, A_n; $ and $k_{x_n}$ refer to the complex eigenfunctions, amplitude, and wavenumber at the $n$th marginal mode.
+Where $\theta_n(z), U_n(z), W_n(z), P_n(z); \, A_n; $ and $k_{x_n}$ refer to the complex eigenfunctions, amplitude, and wavenumber at the $n$th marginal mode respectively. 
 The $\sqrt{2}$ factor is necessary for eigenfunction normalization. 
@@
 Consequently, marginally-stable thermally-equilibrated initial conditions do not reduce the simulation time required to achieve a statistically steady state, rather, they increase it considerably.
-% \begin{figure}[h]
+% \begin{figure}
 %     \centering
@@
 % \end{figure}
-\begin{figure*}[t]
-    \begin{minipage}[t]{3.4in}
+\begin{figure}
+    \begin{minipage}{3.4in}
         \centering
@@
         \caption{Nusselt numbers of simulations performed at $Ra \, = \, 10^8$ with conventional initial conditions (red) and marginally-stable thermally-equilibrated initial conditions (blue). 
-Simulations launched with thermally-equilibrated states do not undergo a convective-transient period because the characteristic plume structure exists on initialization.
+        Simulations run with thermally-equilibrated states do not undergo a convective-transient period because the characteristic plume structure exists on initialization. 
         This is illustrated by the $\Nu$ spike at $t \sim 15$ in the convectional simulation.}
@@
     \end{minipage}
-    \hfill
-    \begin{minipage}[t]{3.4in}
+\end{figure}
+
+\begin{figure}
+    \begin{minipage}{3.4in}
         \centering
@@
     \end{minipage}
-\end{figure*}
+\end{figure}
+
 \section{Discussion}\label{sec:Discussion}
@@
 Thus solutions might be unique, but we cannot demonstrate this rigorously.
-\par The quasilinear problem can also be generalized to include an asymmetric mean horizontal-flow.
+
+The quasilinear problem can also be generalized to include an asymmetric mean horizontal-flow. 
 Specifically, a second initial value problem, similar to (\ref{EQ:T0_IVP}), can be derived for $\bar{u}$. 
@@
 The authors thank Jeff Vassil, Greg Chini, Emma Kaufman for their valuable feedback and suggestions. 
-We also thank the \texttt{Dedalus} and \texttt{Eigentools} developers.
+We also thank the \texttt{Dedalus} and \texttt{Eigentools} development teams. 
 Computations were performed on the NASA Pleiades system.

### 2021-04-07 publication_materials/ms_rbc.tex
intro rev2a

@@
 Rayleigh-B\'enard convection plays a foundational role in large-scale astrophysical and geophysical settings.
-Our understanding of turbulent convective systems is generally limited by the prohibitive computational costs associated with direct numerical simulations \cite{Zhu}. 
-There exists a substantial body of work concerning the asymptotic scaling laws of such systems with no general consensus. 
-Reduced models are particularly useful in this context because they allow us to study the underlying behavior of turbulent convection with relatively low expense.
+Such systems regulate heat transfer and can be associated with violently turbulent flows.
+
+Aggressive convection is associated with large Rayleigh numbers $Ra$ and is difficult to simulate.
+State of the art convection simulations performed by \cite{Zhu} have reached $Ra = 10^{14}$ but estimates for stars are $Ra \sim 10^{20}$ \cite{Ossendrijver}.
+The scaling behavior of the Nusselt number $\Nu$ (convective strength) in the highly turbulent ultimate regime is of particular interest.
+There exists a substantial body of work pertaining to this specific topic with no general consensus \cite{Malkus}, \cite{Kraichnan} \cite{Spiegel}, \cite{Castaing}, \cite{Grossman}, \cite{Ahlers}.
+
+Reduced models are particularly useful in this context because they allow us to study the system with relatively low expense. 
+Much of the published work on this topic relates to unstable time-invariant solutions \cite{Waleffe}, \cite{Sondak}, \cite{Wen}, \cite{chini_cells}. 
+Simulations and analysis performed by \cite{Yalniz} suggest that solution trajectories can be described by a Markov process, vacillating between these steady solutions.
 
@@
 The application of this procedure yields time-invariant solutions to the quasilinear problem with a range of expected and unexpected features.
-
-Reduced models are often valuable when supplemented by direct simulation [source?]. 
-Nonlinear simulations performed with quasilinear solutions as initial conditions do not undergo a convective transient period of turbulent upwelling. 
-Instead, the characteristic jet-like structure is somewhat present on initialization. 
-This is practical because the convective transient period generally involves high-Reynolds number flows whose resolution is prohibitive.
 
@@
     \label{fig:flux}
-    \vspace{0.4in}
+\end{figure*}
+\begin{figure*}
+    \centering
     \includegraphics[width=7.1in]{nu_ra.PNG}
@@
 
-\bibitem{Yalniz} Coarse graining the state space of a turbulent flow using periodic orbits Yalnız, Gökhan; Hof, Björn; Burak Budanur, Nazmi
+\bibitem{Yalniz} Yalnız, Gökhan; Hof, Björn; Burak Budanur, Nazmi. Coarse graining the state space of a turbulent flow using periodic orbits
+
+\bibitem{Ossendrijver} The solar dynamo. Ossendrijver, M. The Astron. Astrophys. Rev. 11, 287–367 (2003).
+
+\bibitem{Kraichnan} Kraichnan, R. Turbulent Thermal Convection at Arbitrary Prandtl Number (1962). https://doi.org/10.1063/1.1706533
+
+% \bibitem{Featherstone} The Spectral Amplitude of Stellar Convection and its Scaling in the High-Rayleigh-Number Regime.
+Featherstone, N.
+A., \& Hindman, B.
+W.
+(2016).
+The Astrophysical Journal, 818, 32–45.
+
+\bibitem{chini_cells} Large Rayleigh number thermal convection: heat flux predictions and strongly nonlinear solutions. Chini, G. P., \& Cox, S. M. (2009). Physics of Fluids, 21, doi:10.1063/1.3210777
+
+\bibitem{Sondak} Sondak, D., Smith, L., \& Waleffe, F. (2015). Optimal heat transport solutions for Rayleigh–Bénard convection. Journal of Fluid Mechanics, 784, 565-595. doi:10.1017/jfm.2015.615
+
+% scaling review
+\bibitem{Grossman} Grossman, S., \& Lohse, D. (2000). Scaling in thermal convection: A unifying theory. Journal of Fluid Mechanics, 407, 27-56. doi:10.1017/S0022112099007545
+
+% modal convection: scaling
+\bibitem{Spiegel} Thermal Turbulence at Very Small Prandtl Number. Spiegel, E. (1962) Journal of Geophysical Research, https://doi.org/10.1029/JZ067i008p03063
+
+\bibitem{Castaing} Castaing, B. et al. (1988) Scaling of hard Thermal Turbulence in Rayleigh-B\'enard Convection
+
+\bibitem{Ahlers} Ahlers, G. Heat transfer \& large-scale dynamics in turbulent Rayleigh-B´enard convection
+
+\bibitem{Shraiman} Shraiman BI, Siggia ED. Heat transport in high-Rayleigh-number convection. Phys Rev A. 1990 Sep 15;42(6):3650-3653. doi: 10.1103/physreva.42.3650. PMID: 9904456.
+
+\bibitem{Wen} Wen, B., Goluskin, D., Doering, C. (2020) Steady Rayleigh–B´enard convection between no-slip boundaries
 

### 2021-04-09 publication_materials/ms_rbc.tex
intro rev2b

@@
 Rayleigh-B\'enard convection plays a foundational role in large-scale astrophysical and geophysical settings.
-Such systems regulate heat transfer and can be associated with violently turbulent flows.
+Buoyancy-driven convection regulates heat transfer and often gives way to violently turbulent flows.
 
@@
 Much of the published work on this topic relates to unstable time-invariant solutions \cite{Waleffe}, \cite{Sondak}, \cite{Wen}, \cite{chini_cells}. 
-Simulations and analysis performed by \cite{Yalniz} suggest that solution trajectories can be described by a Markov process, vacillating between these steady solutions.
+Simulations and analysis performed by \cite{Yalniz} and \cite{Cvitanovic} suggest that chaotic solution trajectories can be modelled as a Markov chain whose long-term behavior is given by the time-weighted-average of a finite set of time-invariant unstable solutions.
+Should that be the case, it is crucial that we discover and classify such time-invariant solutions.
 
-In this investigation, we derive and solve a quasilinear form of the Boussinesq Rayleigh–Bénard convection equations using a strategy similar to \cite{Chini_sw}. 
-This is realized by solving the linearized equations and evolving a mean temperature profile according to the perturbation variables. 
-In general, each set of perturbations has an arbitrary amplitude which we obtain by imposing marginal stability. 
+In \cite{Chini_sw}, researchers develop and solve a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments.
+This is realized by defining a mean state, which which is marginally stable, then analytically deriving an equation for then first-order perturbations' amplitude.
+In this investigation, we seek to solve the Boussinesq Rayleigh–Bénard convection equations using an analogous strategy. 
 The application of this procedure yields time-invariant solutions to the quasilinear problem with a range of expected and unexpected features.
@@
 
+\bibitem{Cvitanovic} P Cvitanovic and J F Gibson (2010). Geometry of the turbulence in wall-bounded shear flows: periodic orbits. http://dx.doi.org/10.1088/0031-8949/2010/T142/014007
+
 \end{thebibliography}

### 2021-04-09 publication_materials/ms_rbc.tex
sections 2 and 3: rev 2a

@@
 
-Aggressive convection is associated with large Rayleigh numbers $Ra$ and is difficult to simulate.
+The simulation of aggressive convection, which is associated with large Rayleigh numbers $Ra$, is expensive. 
 State of the art convection simulations performed by \cite{Zhu} have reached $Ra = 10^{14}$ but estimates for stars are $Ra \sim 10^{20}$ \cite{Ossendrijver}. 
@@
 
-\section{Conventional Boussinesq Linear Stability Analysis}\label{sec:boussinesq}
+\section{Model Setup}\label{sec:model}
 We begin with the non-dimensionalized Boussinesq approximation for Rayleigh-Bénard Convection. 
@@
     \nabla \cdot \mathbf{u} &= 0 \label{EQ:motion1}\\
-    \frac{\partial \mathbf{u}}{\partial t} + \mathbf{u} \cdot \nabla \mathbf{u} &= - \nabla p + T \hat{z} + \sqrt{\frac{Pr}{Ra}} \nabla^2 \mathbf{u} \label{EQ:motion2}\\
-    \frac{\partial T}{\partial t} + \mathbf{u} \cdot \nabla T &= \frac{1}{\sqrt{RaPr}} \nabla^2 T \label{EQ:motion3}
+    \frac{\partial \mathbf{u}}{\partial t} + \mathbf{u} \cdot \nabla \mathbf{u} &= - \nabla p + T \hat{z} + \mathcal{R} \nabla^2 \mathbf{u} \label{EQ:motion2}\\
+    \frac{\partial T}{\partial t} + \mathbf{u} \cdot \nabla T &= \mathcal{P} \nabla^2 T \label{EQ:motion3}
 \end{align}
@@
 For completeness, we specify a final boundary condition $p = p_0$ at $z = \pm 1/2$. 
-Any system of this form can be characterized by its Rayleigh number $Ra$ and Prandtl number $Pr$, where $Ra$ is the timescale ratio of thermal diffusion to convection and $Pr$ is the ratio of momentum diffusivity to thermal diffusivity.
-For convenience, we define 
+Any system of this form can be characterized by its dimensionless Rayleigh number $Ra = \frac{g\alpha L^3 \Delta T}{\nu \kappa}$ and Prandtl number $Pr = \frac{\nu}{\kappa}$, where $g, \, \alpha, \, L, \, \Delta T, \nu, \kappa$ are the gravitational acceleration, coefficient of thermal expansion, domain height, boundary temperature difference, kinematic viscosity, and thermal diffusivity respectively.
 \begin{equation}
@@
 To derive the linearized system, we posit that each field can be represented as the sum of a mean profile (denoted by $\bar{\cdot } \;$) and a perturbation function (denoted by $\cdot'$).
-At an arbitrary time $t_0$, suppose $\frac{\partial \bar{T}}{\partial z} (z)$ is some given function which satisfies
-\begin{equation}
-    \int_{-\frac{1}{2}}^{\frac{1}{2}} \frac{\partial \bar{T}}{\partial z}\Big|_{t=t_0} dz = -1.
-\end{equation}
-Then the mean profiles are given by
-\begin{align}
-    \mathbf{\bar{u}} &= \mathbf{0} \\
-    \bar{T}(z) &= 1 + \int_{-\frac{1}{2}}^{z} \frac{\partial \bar{T}}{\partial \zeta}\Big|_{t=t_0}(\zeta) d\zeta \\
-    \bar{p}(z) &= p_0 + \int_{-\frac{1}{2}}^z \bar{T}\Big|_{t=t_0}(\zeta) d\zeta.
-\end{align}
-Accordingly, the fields are defined as
 \begin{align}
@@
 
-\section{Temperature profile evolution}\label{sec:evolution}
-For this investigation, we allow $ \bar{T}$ to vary in $z$ and $t$. Substituting (\ref{EQ:reynolds_dc_T}) into (\ref{EQ:motion3}) yields
+For this investigation, we allow $\bar{T}$ to vary in $z$ and $t$. Substituting (\ref{EQ:reynolds_dc_T}) into (\ref{EQ:motion3}) yields
 \begin{align}
@@
 The remaining terms in (\ref{EQ:T't_xz}) are unaffected as they are independent of $x$. 
-The eigenfunctions $W(z),\, U(z),\, \theta(z),$ and $P(z)$ do not admit any natural normalization, as (\ref{EQ:linear1}) - (\ref{EQ:linear3}) and their subsequent forms are linear with respect to the perturbations.
+The eigenfunctions $W(z),\, U(z),\, \theta(z),$ and $P(z)$ do not admit any natural normalization, as (\ref{EQ:linear1}) -- (\ref{EQ:linear3}) and their subsequent forms are linear with respect to the perturbations.
 For completeness, we provide the normalization 
@@
 We also assume this term is composed of eigenfunctions belonging to the dominant mode.
-\par For various $Ra$ and fixed $Pr = 1$, we seek symmetric, marginally-stable temperature profiles $\bar{T}_{eq}(z)$ which are thermally equilibrated, thereby satisfying $\frac{\partial \bar{T}_{eq}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}).
-We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:boussinesq} as well as the IVP (\ref{EQ:T0_IVP}) by representing each field with a dealiased Chebyshev polynomial basis.
+
+\section{Perturbation Evolution}
+Solving the linearized system (\ref{EQ:linear1}) -- (\ref{EQ:linear3}) does not yield $A^2$. 
+To evolve $\bar{T}$ numerically, we assume the perturbations and mean quantities depend on different time-scales, as in \cite{Chini_sw}.
+On the fast time-scale, stable modes will decay and unstable modes will act according to (\ref{EQ:T0_IVP}).
+We make the ansatz that only marginally stable modes will affect $\bar{T}$ on long time-scales
+\begin{equation}
+    \max_{k_x} \{ \omega \} = 0
+\end{equation}
+thereby constraining $A^2$ at each timestep.
+
+For various $Ra$ and fixed $Pr = 1$, we seek symmetric, marginally-stable temperature profiles $\bar{T}_{eq}(z)$ which are thermally equilibrated, thereby satisfying $\frac{\partial \bar{T}_{eq}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}).
+We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:model} as well as the IVP (\ref{EQ:T0_IVP}) by representing each field with a dealiased Chebyshev polynomial basis.
 The necessary number of basis functions varies, as eigenfunctions and temperature profiles associated with large Rayleigh numbers admit increasingly small-scale features. 
@@
 More specifically, $Ra \sim \Nu^3$ which agrees with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} and the scaling argument given by \cite{Malkus}. 
-The nonlinear solutions, which maximize heat flux, are obtained \cite{Waleffe}. 
-$\Nu$ of both equilibria exceed that of simulations, which might be due to the transitional behaviors outlined by \cite{Yalniz} inhibiting heat flux.
+The nonlinear solutions, which maximize heat flux, are obtained by \cite{Waleffe}. 
+$\Nu$ of both equilibria exceed that of simulations, which might be due to the transitional behaviors outlined by \cite{Yalniz} and \cite{Cvitanovic} inhibiting heat flux. 
+Alternatively, we might anticipate the existence of exact coherent states with smaller $\Nu$, forming another node in the Markov chain whose long-term behavior agrees with the simulation data.
 
@@
 % \end{figure}
-\par The marginally-stable equilibria are associated with a combination of eigenfunctions whose average kinetic energy is significantly larger than the statistical steady state, as given by Figure \ref{fig:ke_sim}.
+The marginally-stable equilibria are associated with a combination of eigenfunctions whose average kinetic energy is significantly larger than the statistical steady state, as given by Figure \ref{fig:ke_sim}.
 This is postpones kinetic relaxation because the large horizontal flows decay on a viscous timescale

### 2021-04-09 publication_materials/ms_rbc.tex
intro/abstract rev2c

@@
 \begin{abstract}
-Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important properties remain elusive -- particularly in the large Rayleigh number limit.
+Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important properties remain elusive -- particularly in the large Rayleigh number regime.
 In this investigation, we derive and solve a quasilinear form of the Boussinesq Rayleigh-B\'enard equations. 
 Eigenfunction amplitudes are obtained by requiring marginal-stability. We obtain symmetric thermally-equilibrated solutions and analyze their properties. 
-We compare these solutions with statistically-steady 2-dimensional Rayleigh-Be\'nard convection simulations; marginally-stable thermally-equilibrated states have thinner boundary layers and larger Nusselt numbers $\Nu$ which scale like $\Nu \sim Ra^{1/3}$.
+Solutions to the quasilinear problem differ from statistically-steady 2-dimensional Rayleigh-Be\'nard convection simulation data, having thinner boundary layers and larger Nusselt numbers $\Nu$ which scale like $\Nu \sim Ra^{1/3}$.
 We initialize 2-dimensional simulations with solutions to the quasilinear problem; they do not undergo a convective transient period and are kinetically exaggerated.
@@
 Rayleigh-B\'enard convection plays a foundational role in large-scale astrophysical and geophysical settings.
-Buoyancy-driven convection regulates heat transfer and often gives way to violently turbulent flows.
+Buoyancy-driven convection regulates heat transfer and often gives way to violently turbulent flows, thereby dominating the large-scale behaviors and fueling small-scale processes \cite{Couston} in important systems.
 
-The simulation of aggressive convection, which is associated with large Rayleigh numbers $Ra$, is expensive. 
+Aggressive convection, which is associated with large Rayleigh numbers $Ra$, is difficult to simulate. 
 State of the art convection simulations performed by \cite{Zhu} have reached $Ra = 10^{14}$ but estimates for stars are $Ra \sim 10^{20}$ \cite{Ossendrijver}. 
-The scaling behavior of the Nusselt number $\Nu$ (convective strength) in the highly turbulent ultimate regime is of particular interest.
+The scaling behavior of the Nusselt number $\Nu$ (nondimensionalized heat transfer) in the highly turbulent ultimate regime is of particular interest.
 There exists a substantial body of work pertaining to this specific topic with no general consensus \cite{Malkus}, \cite{Kraichnan} \cite{Spiegel}, \cite{Castaing}, \cite{Grossman}, \cite{Ahlers}.
 
-Reduced models are particularly useful in this context because they allow us to study the system with relatively low expense. 
-Much of the published work on this topic relates to unstable time-invariant solutions \cite{Waleffe}, \cite{Sondak}, \cite{Wen}, \cite{chini_cells}. 
-Simulations and analysis performed by \cite{Yalniz} and \cite{Cvitanovic} suggest that chaotic solution trajectories can be modelled as a Markov chain whose long-term behavior is given by the time-weighted-average of a finite set of time-invariant unstable solutions.
-Should that be the case, it is crucial that we discover and classify such time-invariant solutions.
+Reduced models are particularly useful in this context because they allow us to study the problem with relatively low expense. 
+Much of the published work on this topic relates to unstable coherent solutions \cite{Waleffe}, \cite{Sondak}, \cite{Wen}, \cite{chini_cells}. 
+Simulations and analysis performed by \cite{Yalniz} and \cite{Cvitanovic} suggest that chaotic solution trajectories can be modelled as a Markov chain whose long-term behavior is given by the time-weighted-average of a finite set of unstable coherent solutions.
+Should that be the case, it is crucial that we discover and classify such states.
 
 In \cite{Chini_sw}, researchers develop and solve a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments.
-This is realized by defining a mean state, which which is marginally stable, then analytically deriving an equation for then first-order perturbations' amplitude.
-In this investigation, we seek to solve the Boussinesq Rayleigh–Bénard convection equations using an analogous strategy. 
+This is realized by defining a mean state which hypothetically evolves on a slow time-scale.
+An analytic expression for the first-order perturbations' amplitude is found by deriving a solvability condition of the second-order perturbations and integrating over the domain spatially.
+We seek to solve the Boussinesq Rayleigh–Bénard convection equations using an analogous strategy. 
 The application of this procedure yields time-invariant solutions to the quasilinear problem with a range of expected and unexpected features.
@@
 
+\bibitem{Couston} Couston, L.A., Lacoanet, D., Favier, B., Bars, M. (2019). Shape and size of large-scale vortices: a universal fluid pattern in geophysical dynamics
+
 \end{thebibliography}

### 2021-04-12 publication_materials/ms_rbc.tex
broken build

@@
 Rayleigh-B\'enard convection plays a foundational role in large-scale astrophysical and geophysical settings.
-Buoyancy-driven convection regulates heat transfer and often gives way to violently turbulent flows, thereby dominating the large-scale behaviors and fueling small-scale processes \cite{Couston} in important systems.
+% Buoyancy-driven convection regulates heat transfer and often gives way to violently turbulent flows, thereby dominating large-scale behaviors and fueling small-scale processes in important systems \cite{Couston}.
 
 Aggressive convection, which is associated with large Rayleigh numbers $Ra$, is difficult to simulate. 
-State of the art convection simulations performed by \cite{Zhu} have reached $Ra = 10^{14}$ but estimates for stars are $Ra \sim 10^{20}$ \cite{Ossendrijver}. 
+% State of the art convection simulations performed by \cite{Zhu_2018} have reached $Ra = 10^{14}$ but estimates for stars are $Ra \sim 10^{20}$ \cite{Ossendrijver}. 
 The scaling behavior of the Nusselt number $\Nu$ (nondimensionalized heat transfer) in the highly turbulent ultimate regime is of particular interest.
-There exists a substantial body of work pertaining to this specific topic with no general consensus \cite{Malkus}, \cite{Kraichnan} \cite{Spiegel}, \cite{Castaing}, \cite{Grossman}, \cite{Ahlers}.
+There exists a substantial body of work pertaining to this specific topic with no general consensus \cite{Malkus}, \cite{Kraichnan} \cite{Spiegel}, \cite{Castaing}, \cite{Grossman}, \cite{Ahlers}, \cite{Malkus}.
 
 Reduced models are particularly useful in this context because they allow us to study the problem with relatively low expense. 
-Much of the published work on this topic relates to unstable coherent solutions \cite{Waleffe}, \cite{Sondak}, \cite{Wen}, \cite{chini_cells}. 
-Simulations and analysis performed by \cite{Yalniz} and \cite{Cvitanovic} suggest that chaotic solution trajectories can be modelled as a Markov chain whose long-term behavior is given by the time-weighted-average of a finite set of unstable coherent solutions.
+Much of the published work on this topic relates to unstable exact coherent states (ECS) \cite{Waleffe}, \cite{Sondak}, \cite{Wen}, \cite{chini_cells}. 
+Simulations and analysis performed by \cite{Yalniz} and \cite{Cvitanovic} suggest that chaotic simulation trajectories can be represented by a Markov chain whose long-term behavior is given by the time-weighted-average of a finite set of ECS.
 Should that be the case, it is crucial that we discover and classify such states.
@@
 In \cite{Chini_sw}, researchers develop and solve a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments.
-This is realized by defining a mean state which hypothetically evolves on a slow time-scale.
+This is realized by defining a mean state which, hypothetically, evolves on a slow time-scale.
 An analytic expression for the first-order perturbations' amplitude is found by deriving a solvability condition of the second-order perturbations and integrating over the domain spatially.
@@
 Any system of this form can be characterized by its dimensionless Rayleigh number $Ra = \frac{g\alpha L^3 \Delta T}{\nu \kappa}$ and Prandtl number $Pr = \frac{\nu}{\kappa}$, where $g, \, \alpha, \, L, \, \Delta T, \nu, \kappa$ are the gravitational acceleration, coefficient of thermal expansion, domain height, boundary temperature difference, kinematic viscosity, and thermal diffusivity respectively.
+For convenience, we define
 \begin{equation}
@@
 \begin{align}
-    \mathbf{u}(x, z, t) &= \mathbf{u'}(x, z, t) \label{EQ:reynolds_dc_u}\\
-    &= u'(x, z, t)\hat{x} + w'(x, z, t)\hat{z} \\
-    T(x, z, t) &= \bar{T}(z) + T'(x, z, t) \label{EQ:reynolds_dc_T}\\
-    p(x, z, t) &= \bar{p}(z) + p'(x, z, t).
+    \mathbf{u}(x, z, t) &= A\mathbf{u'}(x, z, t) \label{EQ:reynolds_dc_u}\\
+    &= Au'(x, z, t)\hat{x} + Aw'(x, z, t)\hat{z} \\
+    T(x, z, t) &= \bar{T}(z) + AT'(x, z, t) \label{EQ:reynolds_dc_T}\\
+    p(x, z, t) &= \bar{p}(z) + Ap'(x, z, t).
 \end{align}
+where $A$ is some unknown real amplitude and the normalization
+\begin{equation}
+    \int_{-\frac{1}{2}}^{\frac{1}{2}} \big| \theta (z) \big| dz = 1
+\end{equation}
+is specified for completion.
 Upon substitution, we equate terms which scale linearly with the perturbations, yielding the linearized stability equations
@@
 \begin{align}
-    \frac{1}{4}\int_0^4 \grad \cdot (\mathbf{u}'T') dx &= \frac{\partial }{\partial z}  \langle w'T' \rangle
+    \frac{1}{4}\int_0^4 \grad \cdot (\mathbf{u}'T') dx &= \frac{\partial }{\partial z}  \langle w'T' \rangle.
 \end{align}
-where $\langle \cdot \rangle$ denotes the horizontal average. 
-The remaining terms in (\ref{EQ:T't_xz}) are unaffected as they are independent of $x$. 
-The eigenfunctions $W(z),\, U(z),\, \theta(z),$ and $P(z)$ do not admit any natural normalization, as (\ref{EQ:linear1}) -- (\ref{EQ:linear3}) and their subsequent forms are linear with respect to the perturbations.
-For completeness, we provide the normalization 
-\begin{equation}
-    \int_{-\frac{1}{2}}^{\frac{1}{2}} \big| \theta (z) \big| dz = 1
-\end{equation}
-and assign each perturbation a yet-unknown amplitude $A \in \mathbb{R}$, thereby allowing us to reduce (\ref{EQ:T't_xz}) to the initial value problem (IVP)
+The remaining terms in (\ref{EQ:T't_xz}) are unaffected as they are independent of $x$, thereby allowing us to reduce (\ref{EQ:T't_xz}) to the initial value problem (IVP)
 \begin{equation}
@@
 These dips appear in every solution, regardless of $Ra$. 
-Physically, they correspond to thin layers in which the temperature gradient reverses, contradicting a hypothesis of \cite{Malkus}. 
+Physically, they correspond to thin layers in which the temperature gradient reverses, contradicting a hypothesis of \cite{Malkus_1954}. 
 This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure \ref{fig:flux}.  
@@
         Simulations run with thermally-equilibrated states do not undergo a convective-transient period because the characteristic plume structure exists on initialization. 
-        This is illustrated by the $\Nu$ spike at $t \sim 15$ in the convectional simulation.}
+        % This is illustrated by the $\Nu$ spike at $t \sim 15$ in the convectional simulation.}
         \label{fig:nu_sim}
@@
 
-% \bibliography{she}
 \begin{thebibliography}{99}
@@
 
+% \bibliographystyle{plain}
+% \bibliography{he}
+
 \end{document}

### 2021-04-12 publication_materials/ms_rbc.tex
stable build: bibtex implemented

@@
 Rayleigh-B\'enard convection plays a foundational role in large-scale astrophysical and geophysical settings.
-% Buoyancy-driven convection regulates heat transfer and often gives way to violently turbulent flows, thereby dominating large-scale behaviors and fueling small-scale processes in important systems \cite{Couston}.
+Buoyancy-driven convection regulates heat transfer and often gives way to violently turbulent flows, thereby dominating large-scale behaviors and fueling small-scale processes in important systems \cite{Couston}.
 
 Aggressive convection, which is associated with large Rayleigh numbers $Ra$, is difficult to simulate. 
-% State of the art convection simulations performed by \cite{Zhu_2018} have reached $Ra = 10^{14}$ but estimates for stars are $Ra \sim 10^{20}$ \cite{Ossendrijver}. 
+State of the art convection simulations performed by \cite{Zhu_2018} have reached $Ra = 10^{14}$ but estimates for stars are $Ra \sim 10^{20}$ \cite{Ossendrijver}. 
 The scaling behavior of the Nusselt number $\Nu$ (nondimensionalized heat transfer) in the highly turbulent ultimate regime is of particular interest.
-There exists a substantial body of work pertaining to this specific topic with no general consensus \cite{Malkus}, \cite{Kraichnan} \cite{Spiegel}, \cite{Castaing}, \cite{Grossman}, \cite{Ahlers}, \cite{Malkus}.
+There exists a substantial body of work pertaining to this specific topic with no general consensus \cite{Malkus_1954}, \cite{Howard_1966}, \cite{Kraichnan} \cite{Spiegel}, \cite{Castaing}, \cite{Grossman}, \cite{Ahlers}.
 
@@
 
-In \cite{Chini_sw}, researchers develop and solve a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments.
+In \cite{michel_chini_2019}, researchers develop and solve a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments.
 This is realized by defining a mean state which, hypothetically, evolves on a slow time-scale.
@@
 
-To derive the linearized system, we posit that each field can be represented as the sum of a mean profile (denoted by $\bar{\cdot } \;$) and a perturbation function (denoted by $\cdot'$).
+To derive the quasilinear form, we posit that each field can be represented as the sum of a mean profile (denoted by $\bar{\cdot } \;$) and a perturbation function (denoted by $\cdot'$).
 \begin{align}
-    \mathbf{u}(x, z, t) &= A\mathbf{u'}(x, z, t) \label{EQ:reynolds_dc_u}\\
-    &= Au'(x, z, t)\hat{x} + Aw'(x, z, t)\hat{z} \\
-    T(x, z, t) &= \bar{T}(z) + AT'(x, z, t) \label{EQ:reynolds_dc_T}\\
-    p(x, z, t) &= \bar{p}(z) + Ap'(x, z, t).
+    \mathbf{u}(x, z, t) &= A(t) \mathbf{u'}(x, z, t) \label{EQ:reynolds_dc_u}\\
+    &= A(t) u'(x, z, t)\hat{x} + A(t) w'(x, z, t)\hat{z} \\
+    T(x, z, t) &= \bar{T}(z) + A(t) T'(x, z, t) \label{EQ:reynolds_dc_T}\\
+    p(x, z, t) &= \bar{p}(z) + A(t) p'(x, z, t).
 \end{align}
-where $A$ is some unknown real amplitude and the normalization
+where $A(t)$ is some unknown real amplitude and the mean-velocity components vanish due to incompressibility and symmetry.
+We require that perturbations have no horizontal-average, i.e.
+an arbitrary perturbation $f'$ obeys
 \begin{equation}
-    \int_{-\frac{1}{2}}^{\frac{1}{2}} \big| \theta (z) \big| dz = 1
+    \langle f'(x, z, t) \rangle_x \equiv \int_{0}^4 f'(x, z, t) dx = 0.
 \end{equation}
-is specified for completion.
+Assuming the existance of nontrivial solutions, we also fix the volume-average
+\begin{equation}
+  \langle \langle T'^2 \rangle_x \rangle_z = 1
+\end{equation}
+thereby constraining $A(t)$. 
+Substituting (\ref{EQ:reynolds_dc_T}) into (\ref{EQ:motion3}) yields
+
 Upon substitution, we equate terms which scale linearly with the perturbations, yielding the linearized stability equations
@@
 Solving the linearized system (\ref{EQ:linear1}) -- (\ref{EQ:linear3}) does not yield $A^2$. 
-To evolve $\bar{T}$ numerically, we assume the perturbations and mean quantities depend on different time-scales, as in \cite{Chini_sw}.
+To evolve $\bar{T}$ numerically, we assume the perturbations and mean quantities depend on different time-scales, as in \cite{michel_chini_2019}.
 On the fast time-scale, stable modes will decay and unstable modes will act according to (\ref{EQ:T0_IVP}).
@@
     \caption{Nusselt numbers are shown for marginally-stable thermally-equilibrated states, statistically-steady direct numerical simulations performed with \texttt{Dedalus} \cite{Anders_cd}, and equilibrated nonlinear solutions, which maximize heat flux, given by \cite{Waleffe}.
-    Both obey power-law relationships with $Ra$, with $Ra \sim \Nu^3$ in agreement with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} as well as \cite{Malkus}. 
+    Both obey power-law relationships with $Ra$, with $Ra \sim \Nu^3$ in agreement with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} as well as \cite{Malkus_1954}. 
     Marginally-stable states' Nusselt numbers exceed simulation Nusselt numbers. 
@@
     Plotting on a log-log scale, we find $\delta$ and $Ra$ obey a power-law relationship.
-We also demonstrate that $Ra^{1/3}\delta$ is approximately constant with respect to $Ra$ implying $Ra \propto  \delta^{-3}$, as predicted by \cite{Malkus}}
+We also demonstrate that $Ra^{1/3}\delta$ is approximately constant with respect to $Ra$ implying $Ra \propto  \delta^{-3}$, as predicted by \cite{Malkus_1954}}
     \label{fig:bl_ra}
@@
 The marginally-stable thermally-equilibrated states and numerical simulation data exhibit power-law relationships with $Ra$. 
-More specifically, $Ra \sim \Nu^3$ which agrees with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} and the scaling argument given by \cite{Malkus}. 
+More specifically, $Ra \sim \Nu^3$ which agrees with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} and the scaling argument given by \cite{Malkus_1954}. 
 The nonlinear solutions, which maximize heat flux, are obtained by \cite{Waleffe}. 
@@
         \includegraphics[width=3.4in]{sim_eq_nu.png}
-        \caption{Nusselt numbers of simulations performed at $Ra \, = \, 10^8$ with conventional initial conditions (red) and marginally-stable thermally-equilibrated initial conditions (blue). 
-        Simulations run with thermally-equilibrated states do not undergo a convective-transient period because the characteristic plume structure exists on initialization. 
+        \caption{Nusselt numbers of simulations performed at $Ra = 10^8$ with conventional initial conditions (red) and marginally-stable thermally-equilibrated initial conditions (blue). 
+        Simulations run with thermally-equilibrated states do not undergo a convective-transient period because the characteristic plume structure exists on initialization.}
         % This is illustrated by the $\Nu$ spike at $t \sim 15$ in the convectional simulation.}
@@
 In general, the reduced model we study in this paper can be perceived as a unique way to describe Rayleigh–Bénard convection. 
-Solutions to the quasilinear problem retain several key features that are ubiquitous in experiments and simulations: power-law $\Nu$ scaling, plume-like structures, and minimum length-scale approximations \cite{Malkus}.
+Solutions to the quasilinear problem retain several key features that are ubiquitous in experiments and simulations: power-law $\Nu$ scaling, plume-like structures, and minimum length-scale approximations \cite{Malkus_1954}.
 They also exhibit unique and unexpected features: gradient-reversal/dips in temperature profiles, kinetic exaggeration, and greater $\Nu$ than other time-invariant solutions. 
@@
 
-\begin{thebibliography}{99}
-
-\bibitem{Zhu} Xiaojue Zhu, Varghese Mathai, Richard J.
-A.
-M.
-Stevens, Roberto Verzicco, and Detlef Lohse (2018).
-Transition to the Ultimate Regime in Two-Dimensional Rayleigh-Bénard Convection.
-Phys.
-Rev.
-Lett.
-120, 144502
-
-\bibitem{Malkus} Malkus W. V. R. 1954 The heat transport and spectrum of thermal turbulenceProc. R. Soc. Lond. A225196–212
-
-\bibitem{Howard} Howard L.N. (1966) Convection at high Rayleigh number. In: Görtler H. (eds) Applied Mechanics
-
-\bibitem{Chini_la} Chini, G., Malecha, Z., \& Dreeben, T. (2014). Large-amplitude acoustic streaming. Journal of Fluid Mechanics, 744, 329-351. doi:10.1017/jfm.2014.61
-
-\bibitem{Chini_sw} Michel, G., \& Chini, G. (2019). Strong wave–mean-flow coupling in baroclinic acoustic streaming. Journal of Fluid Mechanics, 858, 536-564. doi:10.1017/jfm.2018.785
-
-\bibitem{Shishkina} Olga Shishkina, Susanne Horn, Sebastian Wagner, Phys. Rev. Lett. 114
-
-\bibitem{Anders_cd} Evan H. Anders, Geoffrey M. Vasil, Benjamin P. Brown, and Lydia Korre Phys. Rev. Fluids 5, 083501
-
-\bibitem{Waleffe} Waleffe F., Boonkasame A., Smith L.M. Heat transport by coherent Rayleigh–Bénard convection Phys. Fluids, 27 (2015), Article 051702
-
-\bibitem{Yalniz} Yalnız, Gökhan; Hof, Björn; Burak Budanur, Nazmi. Coarse graining the state space of a turbulent flow using periodic orbits
-
-\bibitem{Ossendrijver} The solar dynamo. Ossendrijver, M. The Astron. Astrophys. Rev. 11, 287–367 (2003).
-
-\bibitem{Kraichnan} Kraichnan, R. Turbulent Thermal Convection at Arbitrary Prandtl Number (1962). https://doi.org/10.1063/1.1706533
-
-% \bibitem{Featherstone} The Spectral Amplitude of Stellar Convection and its Scaling in the High-Rayleigh-Number Regime.
-Featherstone, N.
-A., \& Hindman, B.
-W.
-(2016).
-The Astrophysical Journal, 818, 32–45.
-
-\bibitem{chini_cells} Large Rayleigh number thermal convection: heat flux predictions and strongly nonlinear solutions. Chini, G. P., \& Cox, S. M. (2009). Physics of Fluids, 21, doi:10.1063/1.3210777
-
-\bibitem{Sondak} Sondak, D., Smith, L., \& Waleffe, F. (2015). Optimal heat transport solutions for Rayleigh–Bénard convection. Journal of Fluid Mechanics, 784, 565-595. doi:10.1017/jfm.2015.615
-
-% scaling review
-\bibitem{Grossman} Grossman, S., \& Lohse, D. (2000). Scaling in thermal convection: A unifying theory. Journal of Fluid Mechanics, 407, 27-56. doi:10.1017/S0022112099007545
-
-% modal convection: scaling
-\bibitem{Spiegel} Thermal Turbulence at Very Small Prandtl Number. Spiegel, E. (1962) Journal of Geophysical Research, https://doi.org/10.1029/JZ067i008p03063
-
-\bibitem{Castaing} Castaing, B. et al. (1988) Scaling of hard Thermal Turbulence in Rayleigh-B\'enard Convection
-
-\bibitem{Ahlers} Ahlers, G. Heat transfer \& large-scale dynamics in turbulent Rayleigh-B´enard convection
-
-\bibitem{Shraiman} Shraiman BI, Siggia ED. Heat transport in high-Rayleigh-number convection. Phys Rev A. 1990 Sep 15;42(6):3650-3653. doi: 10.1103/physreva.42.3650. PMID: 9904456.
-
-\bibitem{Wen} Wen, B., Goluskin, D., Doering, C. (2020) Steady Rayleigh–B´enard convection between no-slip boundaries
-
-\bibitem{Cvitanovic} P Cvitanovic and J F Gibson (2010). Geometry of the turbulence in wall-bounded shear flows: periodic orbits. http://dx.doi.org/10.1088/0031-8949/2010/T142/014007
-
-\bibitem{Couston} Couston, L.A., Lacoanet, D., Favier, B., Bars, M. (2019). Shape and size of large-scale vortices: a universal fluid pattern in geophysical dynamics
-
-\end{thebibliography}
-
 % \bibliographystyle{plain}
-% \bibliography{he}
+\bibliography{he}
 

### 2021-04-12 publication_materials/ms_rbc.tex
abstract-section 3: rev2

@@
 The scaling behavior of the Nusselt number $\Nu$ (nondimensionalized heat transfer) in the highly turbulent ultimate regime is of particular interest.
-There exists a substantial body of work pertaining to this specific topic with no general consensus \cite{Malkus_1954}, \cite{Howard_1966}, \cite{Kraichnan} \cite{Spiegel}, \cite{Castaing}, \cite{Grossman}, \cite{Ahlers}.
+There exists a substantial body of work pertaining to this specific topic with no general consensus \cite{Malkus_1954, Howard_1966, Kraichnan, Spiegel, Castaing, Grossman, Ahlers}.
 
 Reduced models are particularly useful in this context because they allow us to study the problem with relatively low expense. 
-Much of the published work on this topic relates to unstable exact coherent states (ECS) \cite{Waleffe}, \cite{Sondak}, \cite{Wen}, \cite{chini_cells}. 
-Simulations and analysis performed by \cite{Yalniz} and \cite{Cvitanovic} suggest that chaotic simulation trajectories can be represented by a Markov chain whose long-term behavior is given by the time-weighted-average of a finite set of ECS.
+Much of the published work on this topic relates to unstable exact coherent states (ECS) \cite{Waleffe, Sondak, Wen,chini_cells}. 
+Simulations and analysis performed by \cite{Yalniz, Cvitanovic} suggest that chaotic simulation trajectories can be represented by a Markov chain whose long-term behavior is given by the time-weighted-average of a finite set of ECS.
 Should that be the case, it is crucial that we discover and classify such states.
@@
     &= A(t) u'(x, z, t)\hat{x} + A(t) w'(x, z, t)\hat{z} \\
-    T(x, z, t) &= \bar{T}(z) + A(t) T'(x, z, t) \label{EQ:reynolds_dc_T}\\
-    p(x, z, t) &= \bar{p}(z) + A(t) p'(x, z, t).
+    T(x, z, t) &= \bar{T}(z, t) + A(t) T'(x, z, t) \label{EQ:reynolds_dc_T}\\
+    p(x, z, t) &= \bar{p}(z, t) + A(t) p'(x, z, t) \label{EQ:reynolds_dc_p}.
 \end{align}
 where $A(t)$ is some unknown real amplitude and the mean-velocity components vanish due to incompressibility and symmetry.
-We require that perturbations have no horizontal-average, i.e.
-an arbitrary perturbation $f'$ obeys
+Perturbations must admit no horizontal-average; an arbitrary perturbation $f'$ obeys
 \begin{equation}
@@
 \end{equation}
-thereby constraining $A(t)$. 
-Substituting (\ref{EQ:reynolds_dc_T}) into (\ref{EQ:motion3}) yields
+thereby alleviating any ambiguity in $A(t)$. 
+Substituting (\ref{EQ:reynolds_dc_T}) into (\ref{EQ:motion3}) and taking the horizontal average reduces the system to a simple initial value problem (IVP) for $\bar{T}$
+\begin{equation}
+  \frac{\partial \bar{T}}{\partial t} + A^2 \langle w'T' \rangle = \mathcal{P}  \frac{\partial^2 \bar{T}}{\partial z^2}, \label{EQ:T0_IVP}
+\end{equation}
+with associated boundary conditions $\bar{T}(-1/2, t) = 1$ and $\bar{T}(1/2, t) = 0$.
+It should be noted that we could obtain a similar IVP for $u$ by breaking symmetry and considering some nontrivial mean horizontal flow $\bar{u}(z, t)$.
+However we must have $\bar{w}(z, t) = 0$ due to incompressibility.
 
-Upon substitution, we equate terms which scale linearly with the perturbations, yielding the linearized stability equations
+To solve (\ref{EQ:T0_IVP}) numerically, we need the perturbations and their associated amplitude function $A(t)$. 
+The former is obtained by solving the linearized system.
+Substituting (\ref{EQ:reynolds_dc_u})--(\ref{EQ:reynolds_dc_p}) into (\ref{EQ:motion1})--(\ref{EQ:motion3}) and subtracting (\ref{EQ:T0_IVP}) from the resulting temperature equation gives
 \begin{align}
@@
 \end{equation}
+
 In 1916, Lord Rayleigh observed that (\ref{EQ:linear1}) and (\ref{EQ:linear3}) can be manipulated into a separable form with generalized solutions
@@
 
-For this investigation, we allow $\bar{T}$ to vary in $z$ and $t$. Substituting (\ref{EQ:reynolds_dc_T}) into (\ref{EQ:motion3}) yields
-\begin{align}
-    \frac{\partial \bar{T}}{\partial t} + \mathbf{u}' \cdot \nabla T' + \frac{\partial T'}{\partial t} + \frac{\partial \bar{T}}{\partial z} w' = \mathcal{P} \nabla^2 T' + \mathcal{P} \nabla^2 \bar{T}.
-    \label{EQ:T't_xz}
-\end{align}
-Subtracting (\ref{EQ:linear3}) from (\ref{EQ:T't_xz}) eliminates several terms. 
-We can replace the advective term $\mathbf{u}' \cdot \nabla T'$ with $\grad \cdot (\mathbf{u}'T')$ due to (\ref{EQ:linear1}). 
-Taking the horizontal average of (\ref{EQ:T't_xz}), this advective term can be reduced to
-\begin{align}
-    \frac{1}{4}\int_0^4 \grad \cdot (\mathbf{u}'T') dx &= \frac{\partial }{\partial z}  \langle w'T' \rangle.
-\end{align}
-The remaining terms in (\ref{EQ:T't_xz}) are unaffected as they are independent of $x$, thereby allowing us to reduce (\ref{EQ:T't_xz}) to the initial value problem (IVP)
-\begin{equation}
-    \frac{\partial \bar{T}}{\partial t} + A^2 \langle w'T' \rangle = \mathcal{P}  \frac{\partial^2 \bar{T}}{\partial z^2}, \label{EQ:T0_IVP}
-\end{equation}
-upon which the remainder of this investigation is centered. 
-It is important to keep in mind that the forcing term $\langle w'T' \rangle$ is obtained by solving an eigenvalue problem (EVP) which itself involves $\frac{\partial \bar{T}}{\partial z}$. 
-We also assume this term is composed of eigenfunctions belonging to the dominant mode.
+At some arbitrary time $t_0$, the forcing term $\langle w'T' \rangle$ can be found by solving an eigenvalue problem (EVP) which itself involves $\frac{\partial \bar{T}}{\partial z}$. 
+We also assume this term is composed of eigenfunctions belonging to the dominant mode(s).
 
@@
 
-For various $Ra$ and fixed $Pr = 1$, we seek symmetric, marginally-stable temperature profiles $\bar{T}_{eq}(z)$ which are thermally equilibrated, thereby satisfying $\frac{\partial \bar{T}_{eq}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}).
+For various $Ra$ and fixed $Pr = 1$, we seek symmetric marginally-stable thermal equilibria (MSTE), thereby satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}). 
 We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:model} as well as the IVP (\ref{EQ:T0_IVP}) by representing each field with a dealiased Chebyshev polynomial basis.
-The necessary number of basis functions varies, as eigenfunctions and temperature profiles associated with large Rayleigh numbers admit increasingly small-scale features. 
-We supplement \texttt{Dedalus} with the \texttt{Eigentools} package to obtain the eigenfunctions in (\ref{EQ:T0_IVP}).
+The necessary number of basis functions varies, as eigenfunctions and temperature profiles associated with large $Ra$ admit increasingly small-scale features. 
+We supplement \texttt{Dedalus} with the \texttt{Eigentools} package to compute $\langle w' T' \rangle$.
 
-To find an equilibrated profile, we begin with a marginally-stable initial profile $\bar{T}_0(z)$ whose construction is outlined in \ref{sec:initial_profile}. 
-We seek to evolve $\bar{T}_0(z)$ into a new marginally-stable profile $\bar{T}_1(z)$ according to (\ref{EQ:T0_IVP}) using forward-Euler. 
-This generally involves a unique and unknown value $A^2 > 0$. 
-Our method of finding $A^2$ is best illustrated through example.
+At $t = 0$, we begin with a marginally-stable initial profile $\bar{T}(z, 0)$ whose construction is outlined in \ref{sec:initial_profile}. 
+At some time $t = t_0$, we seek to evolve $\bar{T}(z, t_0)$ into a new marginally-stable profile $\bar{T}(z, t_0 + \Delta t)$ according to (\ref{EQ:T0_IVP}) using forward-Euler. 
+This generally involves a unique and unknown value $A^2(t_0) > 0$. 
+Our method of finding $A^2(t_0)$ is best illustrated through example.
 
@@
     \includegraphics[width=3.4in]{EV_spectrum_ol.png}
-    \caption{Eigenvalue spectra for $Ra = 10^5$. The spectrum of a marginally-stable mean temperature profile $\bar{T}_0$ (shown in black) has a maximum eigenvalue of 0. 
+    \caption{Eigenvalue spectra for $Ra = 10^5$. The spectrum of a marginally-stable mean temperature profile $\bar{T}(z, t_0)$ (shown in black) has a maximum eigenvalue of 0. 
     Given a small fixed timestep $\Delta t$, diffusion destabilizes the system, increasing its eigenvalues (shown in blue). 
     Advection tends to stabilize the system, decreasing its eigenvalues (shown in red). 
-    It follows that there exists some proportion ($A^2$) of these two terms which yields a new marginally-stable mean temperature profile $\bar{T}_1$, whose spectrum is shown in green.}
+    It follows that there exists some proportion ($A^2(t_0)$) of these two terms which yields a new marginally-stable mean temperature profile $\bar{T}(z, t_0 + \Delta t)$, whose spectrum is shown in green.}
     \label{fig:iteration_spectra} 
@@
 
-An iteration is performed as follows: diffusing a marginally-stable temperature profile $\bar{T}_0$ tends to increase its eigenvalues. 
-Ignoring the diffusive term and evolving according to advection tends the stabilize the system. The appropriate amplitude $A^2$ can then be approximated by
+An iteration is performed as follows: diffusing a marginally-stable temperature profile $\bar{T}(z, t_0)$ tends to increase its eigenvalues. 
+Ignoring the diffusive term and evolving according to advection tends the stabilize the system. The appropriate amplitude $A^2(t_0)$ can then be approximated by
 \begin{equation}
-    A^2 \sim -\frac{\omega_{\rm{diff}}}{\omega_{\rm{adv}}}
+    A^2(t_0) \sim -\frac{\omega_{\rm{diff}}}{\omega_{\rm{adv}}}
 \end{equation}
 where $\omega_{\rm{diff}}$ and $\omega_{\rm{adv}}$ refer to the diffused and advected eigenvalues of the initially marginal mode (corresponding to the blue and red points respectively at $k_x = \pi$ in Figure \ref{fig:iteration_spectra}).
-$\bar{T}_0$ is then evolved according to (\ref{EQ:T0_IVP}) and another eigenvalue solve is performed. 
+$\bar{T}(z, t)$ is then evolved according to (\ref{EQ:T0_IVP}) and another eigenvalue solve is performed. 
 Given a fixed timestep $\Delta t$, we assume the dominant eigenvalue can be described by a continuous function $\omega_{\rm{max}} (A^2)$ which is locally differentiable. 
-Newton's method is used to find an amplitude which meets our marginal stability tolerance criterion $|\omega_{\rm{max}} (A^2)| \leq 10^{-9}$. 
+We use Newton's method to find an amplitude which satisfies our marginal stability tolerance criterion $|\omega_{\rm{max}} (A^2)| \leq 10^{-9}$. 
 The dominant mode is not fixed; an iteration can facilitate the transfer of marginal-stability from one mode to another. 
@@
 \section{Properties of Thermally Equilibrated States}\label{sec:properties}
-Thermally equilibrated states of this kind are solutions to a particular quasilinear form of the Rayleigh-B\'enard convection equations. 
+MSTE are solutions to the quasilinear form of the Rayleigh-B\'enard convection equations derived in section \ref{sec:model}. 
 For this investigation, we calculate solutions for $Ra$ in the range $10^5 - 10^9$. 
 Solutions are symmetric about $z = 0$ by construction.
-This, combined with the fact that we did initialize a mean horizontal flow implies the absence of any nonzero horizontal velocity perturbations, as is the case in \cite{Waleffe}.
 
-Figure \ref{fig:T0_profiles} gives temperature profiles for $Ra = 10^8$ where the initial profile, given by (\ref{EQ:T0}), is employed at iteration 0; the equilibrated profile corresponds to the thermally relaxed state; and the simulation profile is obtained by performing a nonlinear simulation of (\ref{EQ:motion1})-(\ref{EQ:motion3}) with \texttt{Dedalus}, followed by horizontal and time averaging.
+Figure \ref{fig:T0_profiles} gives temperature profiles for $Ra = 10^8$ where the initial profile, given by (\ref{EQ:T0}), is employed at iteration 0; the equilibrated profile corresponds to the thermally relaxed state; and the simulation profile is obtained by performing a nonlinear simulation of (\ref{EQ:motion1})--(\ref{EQ:motion3}) with \texttt{Dedalus}, followed by horizontal and time averaging.
 The simulation curve is more diffuse than the equilibrated curve, which in turn, is more diffuse than the initial curve. 

### 2021-04-13 plot_ke.py
updated p0 simulations

@@ -2,7 +2,7 @@
 Plot planes from joint analysis files.
 
 Usage:
-    plot_slices.py <files>... [--output=<dir>]
+    plot_slices.py <files>... [--output=<dir>] 
 
 Options:
     --output=<dir>  Output directory [default: ./frames]
@@ -84,4 +84,4 @@ if __name__ == "__main__":
         plt.ylabel(r'$\overline{|\mathbf{u}|^2}$')
         plt.title(r'$Ra \, = \, 10^8$')
         # plt.savefig(path + '/pubfigs/sim_eq_ke')
-        plt.savefig(path + '/publication_materials/sim_eq_ke_p0')
+        plt.savefig(path + '/publication_materials/sim_eq_ke_p0_2')

### 2021-04-13 rbc_sim_load_ic.py

@@ -142,7 +142,7 @@ if not pathlib.Path('restart.h5').exists():
 
     p0 = b0.antidifferentiate(z_basis, ('left', 0))
     p0.set_scales(evp_scale)
-    p['g'] = -p0['g'] + np.sqrt(2)*(sum([exp*fields['p'][:, None][slices[1]].transpose() for (exp, fields) in exp_fields])).real
+    p['g'] = p0['g'] + np.sqrt(2)*(sum([exp*fields['p'][:, None][slices[1]].transpose() for (exp, fields) in exp_fields])).real
     w['g'] = np.sqrt(2)*(sum([exp*fields['w'][:, None][slices[1]].transpose() for (exp, fields) in exp_fields])).real
     u['g'] = np.sqrt(2)*(sum([exp*fields['u'][:, None][slices[1]].transpose() for (exp, fields) in exp_fields])).real
     wz = w.differentiate('z')

### 2021-04-13 publication_materials/ms_rbc.tex

@@
 Aggressive convection, which is associated with large Rayleigh numbers $Ra$, is difficult to simulate. 
-State of the art convection simulations performed by \cite{Zhu_2018} have reached $Ra = 10^{14}$ but estimates for stars are $Ra \sim 10^{20}$ \cite{Ossendrijver}. 
+State of the art convection simulations performed by \cite{Zhu_2018} have reached $Ra \sim 10^{14}$ but estimates for stars are $Ra \sim 10^{20}$ \cite{Ossendrijver}. 
 The scaling behavior of the Nusselt number $\Nu$ (nondimensionalized heat transfer) in the highly turbulent ultimate regime is of particular interest.

### 2021-04-13 plot_flux.py
figs preview 1

@@ -59,7 +59,7 @@ def plot_flux(Rayleigh, ax, path, iteration):
         advection4 = wb4*amp4
         advection5 = wb5*amp5
         flux = diffusion + advection1 + advection2 + advection3 + advection4 + advection5
-        plt.plot(z, diffusion, label = 'Diffusion')
+        ax.plot(z, diffusion, label = 'Diffusion', color='black', linestyle=(0, (5, 1)), zorder=10)
         pi_mult1 = str(round(kx1/np.pi, 1))
         pi_mult2 = str(round(kx2/np.pi, 1))
         pi_mult3 = str(round(kx3/np.pi, 1))
@@ -91,9 +91,9 @@ def plot_flux(Rayleigh, ax, path, iteration):
         diffusion = - P*b0z
         advection = wb*amp
         flux = diffusion + advection
-        ax.plot(z, diffusion, label = 'Diffusion')
         pi_mult = str(round(kx/np.pi, 1))
-        ax.plot(z, advection, label = 'Advection ($k_x  = $' + pi_mult + '$\pi$)')
+        ax.plot(z, diffusion, label = 'Diffusion', color='black', linestyle=(0, (5, 1)), zorder=10)
+        ax.plot(z, advection, label = 'Advection ($k_x  = $' + pi_mult + '$\pi$)', color='#08589e')
         ax.plot(z, flux, label = 'Total', color='black')
         ax.set_xlim(-0.5, 0.0)
         ax.legend(frameon=False, loc='center right')

### 2021-04-13 plot_ke.py

@@ -76,12 +76,12 @@ if __name__ == "__main__":
         ke_ar = ke_data['ke_ar']
         sim_times_ar_eq = ke_data_eq['sim_times_ar']
         sim_times_ar = ke_data['sim_times_ar']
-        plt.plot(sim_times_ar, ke_ar, color='darkred', label = 'Conductive I.C.')
-        plt.plot(sim_times_ar_eq, ke_ar_eq, color='darkblue', label = 'Equilibrated I.C.')
+        plt.plot(sim_times_ar, ke_ar, color='black', label = 'Conductive I.C.')
+        plt.plot(sim_times_ar_eq, ke_ar_eq, color='#08589e', label = 'Equilibrated I.C.')
         plt.xlim(0, 400)
         plt.legend(frameon=False)
         plt.xlabel(r'$t$')
         plt.ylabel(r'$\overline{|\mathbf{u}|^2}$')
         plt.title(r'$Ra \, = \, 10^8$')
-        # plt.savefig(path + '/pubfigs/sim_eq_ke')
-        plt.savefig(path + '/publication_materials/sim_eq_ke_p0_2')
+        plt.savefig(path + '/publication_materials/sim_eq_ke')
+        # plt.savefig(path + '/publication_materials/sim_eq_ke_p0_2')

### 2021-04-13 plot_nu.py

@@ -108,12 +108,12 @@ if __name__ == "__main__":
         nu_ar = nu_data['nu_ar']
         sim_times_ar_eq = nu_data_eq['sim_times_ar']
         sim_times_ar = nu_data['sim_times_ar']
-        plt.plot(sim_times_ar, nu_ar, color='darkred', label = 'Conductive I.C.')
-        plt.plot(sim_times_ar_eq, nu_ar_eq, color='darkblue', label = 'Equilibrated I.C.')
+        plt.plot(sim_times_ar, nu_ar, color='black', label = 'Conductive I.C.')
+        plt.plot(sim_times_ar_eq, nu_ar_eq, color='#08589e', label = 'Equilibrated I.C.')
         plt.xlim(0, 100)
         plt.legend(frameon=False)
         plt.xlabel(r'$t$')
-        plt.ylabel(r'$Nu$')
+        plt.ylabel(r'$\mathrm{Nu}$')
         plt.title(r'$Ra \, = \, 10^8$')
         # plt.savefig(path + '/pubfigs/sim_eq_nu')
         plt.savefig(path + '/publication_materials/sim_eq_nu')

### 2021-04-13 plot_spectra_2ra.py

@@ -47,8 +47,8 @@ def plot_EVs(evs_mat, labels):
             else:
                 kx_s.append(kxs[j])
                 evs_s.append(EVs[j])
-        ax.plot(kx_s, evs_s, '.', label='Stable', linestyle='None')
-        ax.plot(kx_m, evs_m, 'x', label='Marginal', markersize=3, linestyle='None')
+        ax.plot(kx_s, evs_s, '.', label='Stable', linestyle='None', color='#08589e')
+        ax.plot(kx_m, evs_m, 'x', label='Marginal', markersize=3, linestyle='None', color='black')
         ax.set_title(labels[i])
         ax.set_xlim(xlims[i])
         ax.set_ylim(ylims[i])
@@ -56,7 +56,8 @@ def plot_EVs(evs_mat, labels):
         ax.xaxis.set_major_locator(tck.MultipleLocator(maj_loc[i]))
         ax.xaxis.set_minor_locator(tck.MultipleLocator(np.pi / 2))
         ax.xaxis.set_major_formatter(plt.FuncFormatter(format_func))
-        ax.grid(True)
+        ax.grid(False)
+        ax.axhline(y=0.0, color='black', alpha=0.2)
         ax.set_xlabel(r'$k_x$')
         ax.set_ylabel(r'$\omega$')
         ax.yaxis.set_major_formatter(FormatStrFormatter('%.4f'))

### 2021-04-13 plot_spectra_modes.py

@@ -43,7 +43,8 @@ def plot_EVs(evs_mat, labels):
         ax.xaxis.set_major_locator(tck.MultipleLocator(5*np.pi))
         ax.xaxis.set_minor_locator(tck.MultipleLocator(np.pi / 2))
         ax.xaxis.set_major_formatter(plt.FuncFormatter(format_func))
-        ax.grid(True)
+        ax.grid(False)
+        ax.axhline(y=0.0, color='black', alpha=0.2)
         if (i == 1):
             ax.set_ylabel(r'$\omega$')
 

### 2021-04-13 publication_settings.py

@@ -7,15 +7,12 @@ fig_width = 3.4 # in column width
 # fig_width = 7.1 # in page width
 fig_height = fig_width * golden_mean
 fig_size =  [fig_width,fig_height]
-colors = [
-    "darkblue",
-    "darkred",
-    "darkgreen",
-    "darkorange",
-    "indigo",
-    "darkslategrey",
-    "darkgoldenrod"
-]
+colors = ['#ccebc5',
+  '#a8ddb5',
+  '#7bccc4',
+  '#4eb3d3',
+  '#2b8cbe',
+  '#08589e']
 
 params = {#'backend': 'eps',
           'axes.prop_cycle' : matplotlib.cycler(color=colors),

### 2021-04-13 write_figs.sh

@@ -1,0 +1,9 @@
+mpiexec_mpt -np 1 python3 plot_flux.py
+
+python3 plot_spectra_2ra.py
+
+mpiexec_mpt -np 1 python3 plot_ke.py
+
+mpiexec_mpt -np 1 python3 plot_nu.py
+
+mpiexec_mpt -np 1 python3 plot_profiles.py

### 2021-04-13 plot_ke.py
pfe figs written

@@ -76,8 +76,9 @@ if __name__ == "__main__":
         ke_ar = ke_data['ke_ar']
         sim_times_ar_eq = ke_data_eq['sim_times_ar']
         sim_times_ar = ke_data['sim_times_ar']
+        colors = plt.rcParams['axes.prop_cycle'].by_key()['color']
         plt.plot(sim_times_ar, ke_ar, color='black', label = 'Conductive I.C.')
-        plt.plot(sim_times_ar_eq, ke_ar_eq, color='#08589e', label = 'Equilibrated I.C.')
+        plt.plot(sim_times_ar_eq, ke_ar_eq, color=colors[-1], label = 'Equilibrated I.C.')
         plt.xlim(0, 400)
         plt.legend(frameon=False)
         plt.xlabel(r'$t$')

### 2021-04-13 plot_nu.py

@@ -108,8 +108,9 @@ if __name__ == "__main__":
         nu_ar = nu_data['nu_ar']
         sim_times_ar_eq = nu_data_eq['sim_times_ar']
         sim_times_ar = nu_data['sim_times_ar']
+        colors = plt.rcParams['axes.prop_cycle'].by_key()['color']
         plt.plot(sim_times_ar, nu_ar, color='black', label = 'Conductive I.C.')
-        plt.plot(sim_times_ar_eq, nu_ar_eq, color='#08589e', label = 'Equilibrated I.C.')
+        plt.plot(sim_times_ar_eq, nu_ar_eq, color=colors[-1], label = 'Equilibrated I.C.')
         plt.xlim(0, 100)
         plt.legend(frameon=False)
         plt.xlabel(r'$t$')

### 2021-04-13 plot_spectra_2ra.py

@@ -47,7 +47,8 @@ def plot_EVs(evs_mat, labels):
             else:
                 kx_s.append(kxs[j])
                 evs_s.append(EVs[j])
-        ax.plot(kx_s, evs_s, '.', label='Stable', linestyle='None', color='#08589e')
+        colors = plt.rcParams['axes.prop_cycle'].by_key()['color']
+        ax.plot(kx_s, evs_s, '.', label='Stable', linestyle='None', color=colors[-1])
         ax.plot(kx_m, evs_m, 'x', label='Marginal', markersize=3, linestyle='None', color='black')
         ax.set_title(labels[i])
         ax.set_xlim(xlims[i])

### 2021-04-13 publication_settings.py

@@ -7,12 +7,12 @@ fig_width = 3.4 # in column width
 # fig_width = 7.1 # in page width
 fig_height = fig_width * golden_mean
 fig_size =  [fig_width,fig_height]
-colors = ['#ccebc5',
-  '#a8ddb5',
+colors = ['#a8ddb5',
   '#7bccc4',
   '#4eb3d3',
   '#2b8cbe',
-  '#08589e']
+  '#08589e',
+  '#0324fc']
 
 params = {#'backend': 'eps',
           'axes.prop_cycle' : matplotlib.cycler(color=colors),

### 2021-04-13 plot_flux.py
complete pfe figs

@@ -93,7 +93,8 @@ def plot_flux(Rayleigh, ax, path, iteration):
         flux = diffusion + advection
         pi_mult = str(round(kx/np.pi, 1))
         ax.plot(z, diffusion, label = 'Diffusion', color='black', linestyle=(0, (5, 1)), zorder=10)
-        ax.plot(z, advection, label = 'Advection ($k_x  = $' + pi_mult + '$\pi$)', color='#08589e')
+        colors = plt.rcParams['axes.prop_cycle'].by_key()['color']
+        ax.plot(z, advection, label = 'Advection ($k_x  = $' + pi_mult + '$\pi$)', color=colors[-1])
         ax.plot(z, flux, label = 'Total', color='black')
         ax.set_xlim(-0.5, 0.0)
         ax.legend(frameon=False, loc='center right')

### 2021-04-13 publication_settings.py

@@ -11,8 +11,7 @@ colors = ['#a8ddb5',
   '#7bccc4',
   '#4eb3d3',
   '#2b8cbe',
-  '#08589e',
-  '#0324fc']
+  '#08589e']
 
 params = {#'backend': 'eps',
           'axes.prop_cycle' : matplotlib.cycler(color=colors),

### 2021-04-13 plot_ke.py
sim figs nomenclature

@@ -77,8 +77,8 @@ if __name__ == "__main__":
         sim_times_ar_eq = ke_data_eq['sim_times_ar']
         sim_times_ar = ke_data['sim_times_ar']
         colors = plt.rcParams['axes.prop_cycle'].by_key()['color']
-        plt.plot(sim_times_ar, ke_ar, color='black', label = 'Conductive I.C.')
-        plt.plot(sim_times_ar_eq, ke_ar_eq, color=colors[-1], label = 'Equilibrated I.C.')
+        plt.plot(sim_times_ar, ke_ar, color='black', label = 'Linear IC')
+        plt.plot(sim_times_ar_eq, ke_ar_eq, color=colors[-1], label = 'MSTE IC')
         plt.xlim(0, 400)
         plt.legend(frameon=False)
         plt.xlabel(r'$t$')

### 2021-04-13 plot_nu.py

@@ -109,8 +109,8 @@ if __name__ == "__main__":
         sim_times_ar_eq = nu_data_eq['sim_times_ar']
         sim_times_ar = nu_data['sim_times_ar']
         colors = plt.rcParams['axes.prop_cycle'].by_key()['color']
-        plt.plot(sim_times_ar, nu_ar, color='black', label = 'Conductive I.C.')
-        plt.plot(sim_times_ar_eq, nu_ar_eq, color=colors[-1], label = 'Equilibrated I.C.')
+        plt.plot(sim_times_ar, nu_ar, color='black', label = 'Linear IC')
+        plt.plot(sim_times_ar_eq, nu_ar_eq, color=colors[-1], label = 'MSTE IC')
         plt.xlim(0, 100)
         plt.legend(frameon=False)
         plt.xlabel(r'$t$')

### 2021-04-13 write_figs.sh

@@ -1,3 +1,5 @@
+conda activate dedalus
+
 mpiexec_mpt -np 1 python3 plot_flux.py
 
 python3 plot_spectra_2ra.py

### 2021-04-13 publication_materials/ms_rbc.tex

@@
 \section{Perturbation Evolution}
-Solving the linearized system (\ref{EQ:linear1}) -- (\ref{EQ:linear3}) does not yield $A^2$. 
-To evolve $\bar{T}$ numerically, we assume the perturbations and mean quantities depend on different time-scales, as in \cite{michel_chini_2019}.
-On the fast time-scale, stable modes will decay and unstable modes will act according to (\ref{EQ:T0_IVP}).
-We make the ansatz that only marginally stable modes will affect $\bar{T}$ on long time-scales
+Solving the linearized system (\ref{EQ:linear1}) -- (\ref{EQ:linear3}) does not yield $A(t)$. 
+To evolve $\bar{T}$, we assume the perturbations and mean quantities evolve according to different time-scales, as in \cite{michel_chini_2019}.
+Stable modes decay away rapidly. 
+Unstable modes will not persist on the slow time-scale because the advective term $\langle w'T' \rangle$ tends to tends to stabilize $\bar{T}$, thereby creating a negative feedback loop.
+Only marginally stable modes can traverse this hypothetical time-scale separation.
+Therefore the amplitude function $A(t)$ must satisfy
 \begin{equation}
-    \max_{k_x} \{ \omega \} = 0
+    \max_{k_x} \{ \omega \} = 0.
 \end{equation}
-thereby constraining $A^2$ at each timestep.
 
@@
 At $t = 0$, we begin with a marginally-stable initial profile $\bar{T}(z, 0)$ whose construction is outlined in \ref{sec:initial_profile}. 
-At some time $t = t_0$, we seek to evolve $\bar{T}(z, t_0)$ into a new marginally-stable profile $\bar{T}(z, t_0 + \Delta t)$ according to (\ref{EQ:T0_IVP}) using forward-Euler. 
+At some arbitrary time $t = t_0$, we seek to evolve $\bar{T}(z, t_0)$ into a new marginally-stable profile $\bar{T}(z, t_0 + \Delta t)$ according to (\ref{EQ:T0_IVP}) using forward-Euler. 
 This generally involves a unique and unknown value $A^2(t_0) > 0$. 
@@
     \includegraphics[width=3.4in]{EV_spectrum_ol.png}
-    \caption{Eigenvalue spectra for $Ra = 10^5$. The spectrum of a marginally-stable mean temperature profile $\bar{T}(z, t_0)$ (shown in black) has a maximum eigenvalue of 0. 
-    Given a small fixed timestep $\Delta t$, diffusion destabilizes the system, increasing its eigenvalues (shown in blue). 
-    Advection tends to stabilize the system, decreasing its eigenvalues (shown in red). 
-    It follows that there exists some proportion ($A^2(t_0)$) of these two terms which yields a new marginally-stable mean temperature profile $\bar{T}(z, t_0 + \Delta t)$, whose spectrum is shown in green.}
+    \caption{Eigenvalue spectra for $Ra = 10^5$. The spectrum of an ``initial" marginally-stable mean temperature profile $\bar{T}(z, t_0)$ has a maximum eigenvalue of 0. 
+    Given a small fixed timestep $\Delta t$, diffusion destabilizes the system, increasing its eigenvalues. 
+    Advection tends to stabilize the system, decreasing its eigenvalues. 
+    It follows that there exists some proportion ($A^2(t_0)$) of these two terms which yields a new marginally-stable mean temperature profile $\bar{T}(z, t_0 + \Delta t)$, whose spectrum is ``evolved".}
     \label{fig:iteration_spectra} 
@@
 \end{equation}
-where $\omega_{\rm{diff}}$ and $\omega_{\rm{adv}}$ refer to the diffused and advected eigenvalues of the initially marginal mode (corresponding to the blue and red points respectively at $k_x = \pi$ in Figure \ref{fig:iteration_spectra}).
+where $\omega_{\rm{diff}}$ and $\omega_{\rm{adv}}$ refer to the diffused and advected eigenvalues of the initially marginal mode (corresponding to the light blue and green points respectively at $k_x = \pi$ in Figure \ref{fig:iteration_spectra}).
 $\bar{T}(z, t)$ is then evolved according to (\ref{EQ:T0_IVP}) and another eigenvalue solve is performed. 
@@
 Performing an eigenvalue solve by setting $\bar{T}$ equal to the simulation profile yields positive eigenvalues. 
-Comprehensively, this suggests that thermally-equilibrated states might maximize boundary layer thickness, while subject to the marginal stability constraint.
+Comprehensively, this suggests that MSTE might maximize boundary layer thickness, while subject to the marginal stability constraint.
 
@@
     Markers are color-coded according to their adjacent local maxima index in the eigenvalue spectrum. 
-    For example, the spectrum corresponding to $Ra = 10^5$ has marginal wavenumbers $k_x = \pi, \, 1.5\pi$ adjacent to a presumed local maximum between these two allowed values. 
-    The $Ra = 10^9$ spectrum, shown in lower right corner of Figure \ref{fig:flux}, has three presumed local maxima, with a single marginal mode adjacent to the first maximum ($k_x = 1.5\pi$), two marginal modes adjacent to the second maximum ($k_x = 6\pi, \, 6.5\pi$), and two marginal modes adjacent to the third maximum ($k_x = 23.5\pi, \, 24\pi$).
+    For example, the spectrum corresponding to $Ra = 10^5$ has adjacent marginal wavenumbers $k_x = \pi, \, 1.5\pi$. 
+    The $Ra = 10^9$ spectrum, shown in lower right corner of Figure \ref{fig:flux}, has three groups of maxima, with a single marginal mode in the first group ($k_x = 1.5\pi$), two adjacent marginal modes in the second group ($k_x = 6\pi, \, 6.5\pi$), and two adjacent marginal modes in the third group ($k_x = 23.5\pi, \, 24\pi$).
     The largest wavenumbers of the green branch obey a power-law relationship with $Ra$}
@@
     \caption{Nusselt numbers are shown for marginally-stable thermally-equilibrated states, statistically-steady direct numerical simulations performed with \texttt{Dedalus} \cite{Anders_cd}, and equilibrated nonlinear solutions, which maximize heat flux, given by \cite{Waleffe}.
-    Both obey power-law relationships with $Ra$, with $Ra \sim \Nu^3$ in agreement with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} as well as \cite{Malkus_1954}. 
+    Both obey power-law relationships with $Ra$, with $\Nu \sim Ra^{1/3}$ in agreement with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} as well as \cite{Malkus_1954}. 
     Marginally-stable states' Nusselt numbers exceed simulation Nusselt numbers. 
-    This can be well explained by the contrasting boundary region geometries shown in Figure \ref{fig:T0_profiles}.}%
+    This can be explained by the contrasting boundary region geometries shown in Figure \ref{fig:T0_profiles}.}%
     \label{fig:nu_vs_ra}%
@@
         \includegraphics[width=3.4in]{sim_eq_nu.png}
-        \caption{Nusselt numbers of simulations performed at $Ra = 10^8$ with conventional initial conditions (red) and marginally-stable thermally-equilibrated initial conditions (blue). 
-        Simulations run with thermally-equilibrated states do not undergo a convective-transient period because the characteristic plume structure exists on initialization.}
-        % This is illustrated by the $\Nu$ spike at $t \sim 15$ in the convectional simulation.}
+        \caption{Nusselt numbers of simulations performed at $Ra = 10^8$ with the conventional initial conditions (black) and MSTE initial conditions (blue). 
+        MSTE simulations do not undergo a convective-transient period because the characteristic large-scale convective cell structure exists on initialization.
+For high $Ra$ simulations, researchers often choose to recycle the results of similar $Ra$ runs \cite{Verzicco, Johnston} because the high-Reynolds number flows associated with the convective transient period are computationally prohibitive \cite{Anders_AE}.}
         \label{fig:nu_sim}
@@
 
-The quasilinear problem can also be generalized to include an asymmetric mean horizontal-flow. 
-Specifically, a second initial value problem, similar to (\ref{EQ:T0_IVP}), can be derived for $\bar{u}$. 
-Doing so might yield solutions with greater resemblance to DNS results because we expect the Reynolds stress tensor to combat the kinetic exaggeration shown in Figure \ref{fig:ke_sim}. 
-For this investigation, we require symmetry at each iteration, but the thermal evolution procedure appears unstable to asymmetry. 
-This could be accommodated by requiring rotational symmetry about the midplane $\bar{u}(z, t) = -\bar{u}(-z, t)$. 
-It's unclear whether solutions with nontrivial $\bar{u}$ exist or whether our algorithm would converge under these different circumstances.
+As previously noted, solving the EVP for statistically steady DNS data yields positive eigenvalues; the system is in a perpetual state of instability. 
+Unstable modes tend to stabilize the system rapidly, creating a negative feedback loop whose average state is linearly unstable. 
+We might curtail the disagreement between MSTE and DNS by loosening our marginal-stability criterion. 
+Should the time-scales not be entirely separate, we might anticipate the long-term persistance of nearly-marginal unstable modes. 
+This perpetual linear instability cannot be described by our model independently (we do not know, a priori, how unstable such modes are) but it might prove fruitful to investigate moderately unstable quasilinear thermal equilibria.
+More precisely, instead of traversing the manifold of marginally-stable states toward MSTE, we could consider the manifold of states whose maximum eigenvalue(s) $\omega_{\rm{max}}$ agree with simulation data.
+Doing so would almost certainly yield more diffuse equilibria $\bar{T}$ whose scaling behavior would likely differ from that of MSTE.
 

### 2021-04-14 plot_flow.py
pfe figs final

@@ -1,0 +1,135 @@
+import numpy as np
+from mpi4py import MPI
+import time
+import pathlib
+import pickle
+import os
+import matplotlib.pyplot as plt
+
+from dedalus import public as de
+from dedalus.extras import flow_tools
+from dedalus.extras.plot_tools import plot_bot_2d
+
+import logging
+logger = logging.getLogger(__name__)
+
+
+# Parameters
+Lx, Lz = (4., 1.)
+Prandtl = 1.
+Rayleigh = 1e8
+
+# Create bases and domain
+Nx, Nz = 32, 32
+x_basis = de.Fourier('x', Nx, interval=(0, Lx), dealias=3/2)
+z_basis = de.Chebyshev('z', Nz, interval=(-Lz/2, Lz/2), dealias=3/2)
+domain = de.Domain([x_basis, z_basis], grid_dtype=np.float64)
+
+# 2D Boussinesq hydrodynamics
+problem = de.IVP(domain, variables=['p','b','u','w','bz','uz','wz'])
+problem.meta['p','b','u','w']['z']['dirichlet'] = True
+problem.parameters['P'] = (Rayleigh * Prandtl)**(-1/2)
+problem.parameters['R'] = (Rayleigh / Prandtl)**(-1/2)
+problem.parameters['F'] = F = 1
+problem.parameters['Lx'] = Lx
+problem.add_equation("dx(u) + wz = 0")
+problem.add_equation("dt(b) - P*(dx(dx(b)) + dz(bz)) - F*w       = -(u*dx(b) + w*bz)")
+problem.add_equation("dt(u) - R*(dx(dx(u)) + dz(uz)) + dx(p)     = -(u*dx(u) + w*uz)")
+problem.add_equation("dt(w) - R*(dx(dx(w)) + dz(wz)) + dz(p) - b = -(u*dx(w) + w*wz)")
+problem.add_equation("bz - dz(b) = 0")
+problem.add_equation("uz - dz(u) = 0")
+problem.add_equation("wz - dz(w) = 0")
+problem.add_bc("left(b) = 0")
+problem.add_bc("left(u) = 0")
+problem.add_bc("left(w) = 0")
+problem.add_bc("right(b) = 0")
+problem.add_bc("right(u) = 0")
+problem.add_bc("right(w) = 0", condition="(nx != 0)")
+problem.add_bc("right(p) = 0", condition="(nx == 0)")
+
+# Build solver
[…]

### 2021-04-14 rbc_sim_eq_b0z.py

@@ -1,0 +1,243 @@
+"""
+Dedalus script for 2D Rayleigh-Benard convection.
+
+This script uses a Fourier basis in the x direction with periodic boundary
+conditions.  The equations are scaled in units of the buoyancy time (Fr = 1).
+
+This script can be ran serially or in parallel, and uses the built-in analysis
+framework to save data snapshots in HDF5 files.  The `merge_procs` command can
+be used to merge distributed analysis sets from parallel runs, and the
+`plot_slices.py` script can be used to plot the snapshots.
+
+To run, merge, and plot using 4 processes, for instance, you could use:
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+    $ mpiexec -n 4 python3 -m dedalus merge_procs snapshots
+    $ mpiexec -n 4 python3 plot_slices.py snapshots/*.h5
+
+This script can restart the simulation from the last save of the original
+output to extend the integration.  This requires that the output files from
+the original simulation are merged, and the last is symlinked or copied to
+`restart.h5`.
+
+To run the original example and the restart, you could use:
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+    $ mpiexec -n 4 python3 -m dedalus merge_procs snapshots
+    $ ln -s snapshots/snapshots_s2.h5 restart.h5
+    $ mpiexec -n 4 python3 rayleigh_benard.py
+
+The simulations should take a few process-minutes to run.
+
+"""
+
+import numpy as np
+from mpi4py import MPI
+import time
+import pathlib
+import pickle
+import os
+
+from dedalus import public as de
+from dedalus.extras import flow_tools
+from dedalus.extras.plot_tools import plot_bot_2d
+
+import logging
+logger = logging.getLogger(__name__)
+
+
+# Parameters
+Lx, Lz = (4., 1.)
+Prandtl = 1.
+Rayleigh = 1e8
+
+# Create bases and domain
+Nx, Nz = 256, 64
+x_basis = de.Fourier('x', Nx, interval=(0, Lx), dealias=3/2)
+z_basis = de.Chebyshev('z', Nz, interval=(-Lz/2, Lz/2), dealias=3/2)
[…]

### 2021-04-14 publication_materials/ms_rbc.tex
local figs -- append references

@@
 State of the art convection simulations performed by \cite{Zhu_2018} have reached $Ra \sim 10^{14}$ but estimates for stars are $Ra \sim 10^{20}$ \cite{Ossendrijver}. 
-The scaling behavior of the Nusselt number $\Nu$ (nondimensionalized heat transfer) in the highly turbulent ultimate regime is of particular interest.
+The scaling behavior of the Nusselt number $\Nu \sim Ra^{\beta}$ in the asymptotic ultimate regime is of particular interest.
 There exists a substantial body of work pertaining to this specific topic with no general consensus \cite{Malkus_1954, Howard_1966, Kraichnan, Spiegel, Castaing, Grossman, Ahlers}.
@@
 Reduced models are particularly useful in this context because they allow us to study the problem with relatively low expense. 
-Much of the published work on this topic relates to unstable exact coherent states (ECS) \cite{Waleffe, Sondak, Wen,chini_cells}. 
+Much of the published work on this topic relates to unstable exact coherent states (ECS) \cite{Waleffe, Sondak, Wen, chini_cells}. 
 Simulations and analysis performed by \cite{Yalniz, Cvitanovic} suggest that chaotic simulation trajectories can be represented by a Markov chain whose long-term behavior is given by the time-weighted-average of a finite set of ECS.
@@
 
-In \cite{michel_chini_2019}, researchers develop and solve a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments.
+In \cite{Beaume_2015}, researchers compute ECS in parallel shear flows by deriving and solving a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments. 
 This is realized by defining a mean state which, hypothetically, evolves on a slow time-scale. 
-An analytic expression for the first-order perturbations' amplitude is found by deriving a solvability condition of the second-order perturbations and integrating over the domain spatially.
+Marginal stability is required at each successive timestep to constrain the perturbation amplitudes. 
+A similar strategy is employed by \cite{michel_chini_2019}, where an analytic expression for the first-order perturbations' amplitude is found by deriving a solvability condition of the second-order perturbations and integrating over the domain spatially.
 We seek to solve the Boussinesq Rayleigh–Bénard convection equations using an analogous strategy. 
@@
 We begin with the non-dimensionalized Boussinesq approximation for Rayleigh-Bénard Convection. 
-The domain is 2-dimensional rectangular and horizontally periodic with spatial dimensions $0 < x < 4$ and $-1/2 < z < 1/2$. 
+The domain $\mathcal{D}$ is 2-dimensional rectangular and horizontally periodic with spatial dimensions $0 < x < 4$ and $-1/2 < z < 1/2$. 
 The fluid of interest is constrained between two planar boundaries at $z = -1/2$ and $z = 1/2$ with fixed temperatures $1$ and $0$ respectively. 
@@
 
-To derive the quasilinear form, we posit that each field can be represented as the sum of a mean profile (denoted by $\bar{\cdot } \;$) and a perturbation function (denoted by $\cdot'$).
+To derive the quasilinear form, we posit that an arbitrary field $f$ can be represented as the sum of a mean profile (denoted by $\bar{f}$) and a perturbation function (denoted by $f'$).
 \begin{align}
@@
 \end{equation}
-Assuming the existance of nontrivial solutions, we also fix the volume-average 
+Assuming the existance of nontrivial solutions, we also fix the volume-average over the entire domain
 \begin{equation}
-  \langle \langle T'^2 \rangle_x \rangle_z = 1
+  \langle T'^2 \rangle_{\mathcal{D}} = 1
 \end{equation}
@@
 \begin{equation}
-  \frac{\partial \bar{T}}{\partial t} + A^2 \langle w'T' \rangle = \mathcal{P}  \frac{\partial^2 \bar{T}}{\partial z^2}, \label{EQ:T0_IVP}
+  \frac{\partial \bar{T}}{\partial t} + A^2 \langle w'T' \rangle_x = \mathcal{P}  \frac{\partial^2 \bar{T}}{\partial z^2}, \label{EQ:T0_IVP}
 \end{equation}
@@
 
-At some arbitrary time $t_0$, the forcing term $\langle w'T' \rangle$ can be found by solving an eigenvalue problem (EVP) which itself involves $\frac{\partial \bar{T}}{\partial z}$. 
+At some arbitrary time $t_0$, the forcing term $\langle w'T' \rangle_x$ can be found by solving an eigenvalue problem (EVP) which itself involves $\frac{\partial \bar{T}}{\partial z}$. 
 We also assume this term is composed of eigenfunctions belonging to the dominant mode(s).
@@
 Stable modes decay away rapidly. 
-Unstable modes will not persist on the slow time-scale because the advective term $\langle w'T' \rangle$ tends to tends to stabilize $\bar{T}$, thereby creating a negative feedback loop.
+Unstable modes will not persist on the slow time-scale because the advective term $\langle w'T' \rangle_x$ tends to tends to stabilize $\bar{T}$, thereby creating a negative feedback loop.
 Only marginally stable modes can traverse this hypothetical time-scale separation.
@@
 
-For various $Ra$ and fixed $Pr = 1$, we seek symmetric marginally-stable thermal equilibria (MSTE), thereby satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}). 
+For various $Ra$ and fixed $Pr = 1$, we seek symmetric marginally-stable thermal equilibria (MSTE) $\bar{T}_{\rm{MSTE}}$, thereby satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}).
 We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:model} as well as the IVP (\ref{EQ:T0_IVP}) by representing each field with a dealiased Chebyshev polynomial basis.
 The necessary number of basis functions varies, as eigenfunctions and temperature profiles associated with large $Ra$ admit increasingly small-scale features. 
-We supplement \texttt{Dedalus} with the \texttt{Eigentools} package to compute $\langle w' T' \rangle$.
+We supplement \texttt{Dedalus} with the \texttt{Eigentools} package to compute $\langle w' T' \rangle_x$.
 
@@
 \begin{equation}
-    A^2 \langle w' b' \rangle = \sum_{n = 1}^{N} A^2_{n} \langle w' b' \rangle_{n}
+    A^2 \langle w' b' \rangle_x = \sum_{n = 1}^{N} A^2_{n} \langle w' b' \rangle_{x, \, n}
 \end{equation}
-where  $\langle w' b' \rangle_{n}$ is composed of perturbations associated with $k_x = \frac{n\pi}{2}$. 
+where  $\langle w' b' \rangle_{x, \, n}$ is composed of perturbations associated with $k_x = \frac{n\pi}{2}$. 
 There are now $N$ amplitudes to solve for and $N$ eigenvalues to keep marginally-stable. 
@@
 For this investigation, we calculate solutions for $Ra$ in the range $10^5 - 10^9$. 
-Solutions are symmetric about $z = 0$ by construction.
+Their mean temperatures $\bar{T}_{\rm{MSTE}}$ are symmetric about $z = 0$ by construction.
 
-Figure \ref{fig:T0_profiles} gives temperature profiles for $Ra = 10^8$ where the initial profile, given by (\ref{EQ:T0}), is employed at iteration 0; the equilibrated profile corresponds to the thermally relaxed state; and the simulation profile is obtained by performing a nonlinear simulation of (\ref{EQ:motion1})--(\ref{EQ:motion3}) with \texttt{Dedalus}, followed by horizontal and time averaging.
-The simulation curve is more diffuse than the equilibrated curve, which in turn, is more diffuse than the initial curve. 
-Performing an eigenvalue solve by setting $\bar{T}$ equal to the simulation profile yields positive eigenvalues. 
+Figure \ref{fig:T0_profiles} gives temperature profiles for $Ra = 10^8$ where the initial profile, given by (\ref{EQ:T0}), is employed at iteration 0; the MSTE profile corresponds to the thermally relaxed state; and the DNS (direct numerical simulations) profile is obtained by solving (\ref{EQ:motion1})--(\ref{EQ:motion3}) with \texttt{Dedalus}, followed by horizontal and time averaging.
+The DNS curve is more diffuse than the MSTE curve, which in turn, is more diffuse than the initial curve. 
+Performing an eigenvalue solve by setting $\bar{T}$ equal to the DNS profile yields positive eigenvalues. 
 Comprehensively, this suggests that MSTE might maximize boundary layer thickness, while subject to the marginal stability constraint.
@@
 These dips appear in every solution, regardless of $Ra$. 
-Physically, they correspond to thin layers in which the temperature gradient reverses, contradicting a hypothesis of \cite{Malkus_1954}. 
+Physically, they correspond to thin layers in which the temperature gradient reverses, contradicting an important hypothesis of \cite{Malkus_1954}. 
 This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure \ref{fig:flux}.  
@@
     \includegraphics[width=3.4in]{T_profs_na.png}
-    \caption{mean temperature profiles $\bar{T}$ for $Ra = 10^8$. 
+    \caption{Mean temperature profiles $\bar{T}$ for $Ra = 10^8$. 
     The initial profile is given by (\ref{EQ:T0}). 
-    The equilibrated curve refers to the mean temperature profile of the marginally-stable thermally-equilibrated state. 
-    The simulation profile is obtained by performing a 2-dimensional nonlinear simulation with \texttt{Dedalus} until thermal and kinetic relaxation. 
-    The simulation temperature data are horizontally- and time-averaged. 
-    The initial, equilibrated, and simulation profiles have increasingly relaxed boundary regions (respectively). 
-    The equilibrated profile exhibits prominent dips, nested alongside the boundary regions. 
-    The purpose of this feature is not well understood.}
+    The MSTE curve refers to the mean temperature profile of the marginally-stable thermally-equilibrated state. 
+    The DNS profile is obtained by performing a 2-dimensional nonlinear simulation of (\ref{EQ:motion1})--(\ref{EQ:motion3}) with \texttt{Dedalus} until thermal and kinetic relaxation. 
+    The DNS temperature data are horizontally- and time-averaged. 
+    The initial, MSTE, and DNS profiles have increasingly relaxed boundary regions (respectively). 
+    The MSTE profile exhibits prominent dips, nested alongside the boundary regions. 
+    The source of this feature is not well understood, but similar temperature gradient reversal regions were found by \cite{chini_cells} along the midplanes of 2-dimensional convective cellular solutions at $Ra \sim 10^6$.}
     \label{fig:T0_profiles}
@@
 The introduction of this largest branch is likely required to oppose the diffusion of the thinning boundary layers. 
-For $Ra \geq 10^8$, a third branch appears (shown in red), splitting the widening gap between the blue branch and the green branch. 
+For $Ra \geq 10^8$, a third branch appears (shown in blue), splitting the widening gap between the blue branch and the green branch. 
 This development is associated with relatively thick advection profiles, filling a niche in the total flux by uniting the sharp profiles of the largest branch (green) and those of the bulk-domain-oriented smallest branch (blue).
@@
 
-Nusselt numbers $\Nu$ of various solutions are given in Figure \ref{fig:nu_vs_ra}. 
+The Nusselt number, which describes convective performance, is given by
+\begin{equation}
+  \Nu = \frac{\langle A^2 \langle w'T' \rangle_x - \mathcal{P}\frac{\partial \bar{T}}{\partial z} \rangle_z}{\langle- \mathcal{P}\frac{\partial \bar{T}}{\partial z} \rangle_z}.
+\end{equation}
+There is no general consensus surrounding the scaling behavior $\Nu \sim Ra^{\beta}$ for high $Ra$ systems.
+The asymptotic value of $\beta$ is of particular importance in astrophysical systems.
+In Figure \ref{fig:nu_vs_ra} we report $\Nu$ for MSTE, DNS, along with several ECS.
 The marginally-stable thermally-equilibrated states and numerical simulation data exhibit power-law relationships with $Ra$. 
-More specifically, $Ra \sim \Nu^3$ which agrees with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} and the scaling argument given by \cite{Malkus_1954}. 
+More specifically, $\beta = 1/3$ which agrees with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} and the scaling argument given by \cite{Malkus_1954}. 
 The nonlinear solutions, which maximize heat flux, are obtained by \cite{Waleffe}. 
@@
 This investigation is partially motivated by the prospect of decreasing nonlinear simulation relaxation times by employing thermally-equilibrated initial conditions. 
-Conventionally, (\ref{EQ:motion1}) - (\ref{EQ:motion3}) are solved via direct numerical simulation (DNS) with initial conditions
+Conventionally, (\ref{EQ:motion1}) - (\ref{EQ:motion3}) are solved via direct numerical simulation (DNS) with the linear initial conditions
 \begin{align}
@@
     \mathbf{u}(x, z)\big|_{t=0} &= \mathbf{0} \\
-    p(x, z)\big|_{t=0} &= 0
+    p(x, z)\big|_{t=0} &= 0.
 \end{align}
-which will hereby be referred to as the conductive initial condition. 
 $t$ in this section now refers to the simulation time as opposed to the thermal equilibration time parameter used previously. 
-We define the equilibrated initial conditions
+We define the MSTE initial conditions
 \begin{align}
-    T(x, z)\big|_{t=0} &= \bar{T}(z) + \sqrt{2} \sum_{n=1}^N  A_n \text{ Re} \Big[ \theta_n(z) e^{ik_{x_n}x} \Big] \nonumber \\
+    T(x, z)\big|_{t=0} &= \bar{T}_{\rm{MSTE}}(z) + \sqrt{2} \sum_{n=1}^N  A_n \text{ Re} \Big[ \theta_n(z) e^{ik_{x_n}x} \Big] \nonumber \\
     \mathbf{u}(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A_n \text{ Re} \Big[\Big( U_n (z) \hat{x} + W_n(z) \hat{z} \Big) e^{ik_{x_n}x} \Big] \nonumber\\
@@
 The $\sqrt{2}$ factor is necessary for eigenfunction normalization.
-By construction, these initial conditions are thermally equilibrated. 
-Simulations launched with equilibrated initial conditions do not exhibit a convective-transient period, as the large-scale anatomy of plumes and convective winds which are characteristic of Rayleigh-B\'enard convection exist on initialization.
-This is illustrated in Figure \ref{fig:nu_sim}, where the sharp spike in $\Nu$ is associated with a turbulent transitional period of upwelling until the distinctive jet-like structure is established. 
+
+Simulations launched with MSTE initial conditions do not exhibit a convective-transient period, as the large-scale anatomy of convective cells, which are characteristic of Rayleigh-B\'enard convection, exist on initialization.
+This is illustrated in Figure \ref{fig:nu_sim}, where the sharp spike in $\Nu$ is associated with a turbulent transitional period of upwelling until the distinctive plume-like structure is established.
+Simulation of this transitional period is prohibitive \cite{Anders_AE}. 
+For high $Ra$ experiments, researchers often  ``bootstrap" data by initializing simulations with the results of similar $Ra$ runs \cite{Verzicco, Johnston}. 
+MSTE can be perceived as a set of initial conditions, designed for avoiding the simulation of transitional high Reynolds number flows.
+
+MSTE are laminar, lacking the small-scale structures associated with moderate to high $Ra$ experiments.
+The absence of chaotic dynamics is an apparent consequence of the quasilinear assumptions.
+If we treat MSTE as background states, DNS suggest that plumes, vortex sheets, and other unstable turbulent features inhibit total heat transfer.
+This perspective agrees with convectional models of transitions to turbulent flows, such as Boussinesq's turbulent-viscosity hypothesis \cite{boussinesq_1877}, where the emergence of small-scale velocity structures tends to increase total shear \cite{Lecoanet_KH, drazin_reid_2004, pope_2000}, thereby impeding buoyancy-driven flows and decreasing advection in the bulk of the domain.
+We could also atribute the diffuse DNS temperature profile in Figure \ref{fig:T0_profiles} with unsteady boundary-layer penetration and mixing that MSTE do not exhibit.
+
 % \begin{figure}
@@
 Consequently, marginally-stable thermally-equilibrated initial conditions do not reduce the simulation time required to achieve a statistically steady state, rather, they increase it considerably.
+Further, this suggests that the MSTE background state perspective is, at least partially, flawed as an appropriate background state would approximate $\langle|\mathbf{u}|^2 \rangle_{\mathcal{D}}$
 % \begin{figure}
@@
 They also exhibit unique and unexpected features: gradient-reversal/dips in temperature profiles, kinetic exaggeration, and greater $\Nu$ than other time-invariant solutions. 
-We also obtain indistinguishable solutions despite initializing with different mean temperature profiles $\bar{T}$. 
+We also obtain indistinguishable solutions despite initializing with various mean temperature profiles $\bar{T}(z, 0)$. 
 Thus solutions might be unique, but we cannot demonstrate this rigorously.
@@
 Should the time-scales not be entirely separate, we might anticipate the long-term persistance of nearly-marginal unstable modes. 
-This perpetual linear instability cannot be described by our model independently (we do not know, a priori, how unstable such modes are) but it might prove fruitful to investigate moderately unstable quasilinear thermal equilibria.
-More precisely, instead of traversing the manifold of marginally-stable states toward MSTE, we could consider the manifold of states whose maximum eigenvalue(s) $\omega_{\rm{max}}$ agree with simulation data.
-Doing so would almost certainly yield more diffuse equilibria $\bar{T}$ whose scaling behavior would likely differ from that of MSTE.
+This perpetual linear instability cannot be described by our model independently (we do not know, a priori, how unstable such modes are) but it might prove fruitful to investigate moderately unstable thermal equilibria (MUTE).
+More precisely, instead of traversing the manifold of marginally-stable states toward MSTE, we could consider the manifold of states whose maximum eigenvalue(s) $\omega_{\rm{max}}$ agree with some other stability constraint.
+Note that under this definition, 2-dimensional ECS and temporally-averaged steady DNS data are subsets of MUTE, since they are thermally-equilibrated and generally unstable, though they need not necessarily satisfy the quasilinear form.
+
+We cannot use our reduced quasilinear model to predict $\Nu \sim Ra^{\beta}$ for large $Ra$ without some complementary stability constraint. 
+The eigenvalues of DNS data might provide an informative stability constraint (we could find MUTE and compare them with DNS data), but this would be self-defeating in general. 
+Instead we seek to combine reduced models to approximate $\beta$ without DNS.
+Under the marginal-stability constraint, we found that MSTE exhibit classical Malkus scaling, having marginally-stable boundary layers with $\beta = 1/3$.
+We could instead require that the eigenvalues of MUTE agree with the eigenvalues of the analytic 1-dimensional boundary layer predictions of \cite{Shishkina, Zhang_20} (which remain in development), allowing us to refine and expand these estimates into 2-dimensional MUTE.
+Accessible MUTE states would not rely on DNS, satisfying only the quasilinear problem and stability constraint. 
+Such MUTE ought to agree with DNS data more precisely then MSTE, ideally having less extreme velocities. 
+This is reasonable to expect, since accurate boundary layer approximations and DNS data should have similar stability characteristics. 
+By definition, $\bar{T}_{\rm{MUTE}}$ is unstable and would therefore admit more diffuse boundary layer structures, requiring smaller $A^2(t)$ (less advection) to satisfy the stability constraint and thereby reducing $\Nu$, $\langle \langle |\mathbf{u}|^2 \rangle_x \rangle_z$ and possibly $\beta$.
 
@@
 \subsection{Initial buoyancy profile} \label{sec:initial_profile}
-In an attempt to minimize the required number of iterations, we initialize with \cite{Shishkina}'s analytical thermal boundary layer equation for turbulent Rayleigh-B\'enard convection, given by 
+We initialize the thermal-equilibration algorithm with \cite{Shishkina}'s analytical thermal boundary layer equation for turbulent Rayleigh-B\'enard convection, given by 
 \begin{align}

### 2021-04-14 publication_materials/ms_rbc.tex

@@
 State of the art convection simulations performed by \cite{Zhu_2018} have reached $Ra \sim 10^{14}$ but estimates for stars are $Ra \sim 10^{20}$ \cite{Ossendrijver}. 
-The scaling behavior of the Nusselt number $\Nu \sim Ra^{\beta}$ in the asymptotic ultimate regime is of particular interest.
+The scaling behavior of the Nusselt number $\Nu$ (nondimensionalized heat transfer) in the highly turbulent ultimate regime is of particular interest.
 There exists a substantial body of work pertaining to this specific topic with no general consensus \cite{Malkus_1954, Howard_1966, Kraichnan, Spiegel, Castaing, Grossman, Ahlers}.
@@
 Reduced models are particularly useful in this context because they allow us to study the problem with relatively low expense. 
-Much of the published work on this topic relates to unstable exact coherent states (ECS) \cite{Waleffe, Sondak, Wen, chini_cells}. 
+Much of the published work on this topic relates to unstable exact coherent states (ECS) \cite{Waleffe, Sondak, Wen,chini_cells}. 
 Simulations and analysis performed by \cite{Yalniz, Cvitanovic} suggest that chaotic simulation trajectories can be represented by a Markov chain whose long-term behavior is given by the time-weighted-average of a finite set of ECS.
@@
 
-In \cite{Beaume_2015}, researchers compute ECS in parallel shear flows by deriving and solving a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments. 
+In \cite{michel_chini_2019}, researchers develop and solve a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments.
 This is realized by defining a mean state which, hypothetically, evolves on a slow time-scale.
-Marginal stability is required at each successive timestep to constrain the perturbation amplitudes. 
-A similar strategy is employed by \cite{michel_chini_2019}, where an analytic expression for the first-order perturbations' amplitude is found by deriving a solvability condition of the second-order perturbations and integrating over the domain spatially.
+An analytic expression for the first-order perturbations' amplitude is found by deriving a solvability condition of the second-order perturbations and integrating over the domain spatially.
 We seek to solve the Boussinesq Rayleigh–Bénard convection equations using an analogous strategy. 
@@
 We begin with the non-dimensionalized Boussinesq approximation for Rayleigh-Bénard Convection. 
-The domain $\mathcal{D}$ is 2-dimensional rectangular and horizontally periodic with spatial dimensions $0 < x < 4$ and $-1/2 < z < 1/2$. 
+The domain is 2-dimensional rectangular and horizontally periodic with spatial dimensions $0 < x < 4$ and $-1/2 < z < 1/2$. 
 The fluid of interest is constrained between two planar boundaries at $z = -1/2$ and $z = 1/2$ with fixed temperatures $1$ and $0$ respectively. 
@@
 
-To derive the quasilinear form, we posit that an arbitrary field $f$ can be represented as the sum of a mean profile (denoted by $\bar{f}$) and a perturbation function (denoted by $f'$).
+To derive the quasilinear form, we posit that each field can be represented as the sum of a mean profile (denoted by $\bar{\cdot } \;$) and a perturbation function (denoted by $\cdot'$).
 \begin{align}
@@
 \end{equation}
-Assuming the existance of nontrivial solutions, we also fix the volume-average over the entire domain
+Assuming the existance of nontrivial solutions, we also fix the volume-average 
 \begin{equation}
-  \langle T'^2 \rangle_{\mathcal{D}} = 1
+  \langle \langle T'^2 \rangle_x \rangle_z = 1
 \end{equation}
@@
 \begin{equation}
-  \frac{\partial \bar{T}}{\partial t} + A^2 \langle w'T' \rangle_x = \mathcal{P}  \frac{\partial^2 \bar{T}}{\partial z^2}, \label{EQ:T0_IVP}
+  \frac{\partial \bar{T}}{\partial t} + A^2 \langle w'T' \rangle = \mathcal{P}  \frac{\partial^2 \bar{T}}{\partial z^2}, \label{EQ:T0_IVP}
 \end{equation}
@@
 
-At some arbitrary time $t_0$, the forcing term $\langle w'T' \rangle_x$ can be found by solving an eigenvalue problem (EVP) which itself involves $\frac{\partial \bar{T}}{\partial z}$. 
+At some arbitrary time $t_0$, the forcing term $\langle w'T' \rangle$ can be found by solving an eigenvalue problem (EVP) which itself involves $\frac{\partial \bar{T}}{\partial z}$. 
 We also assume this term is composed of eigenfunctions belonging to the dominant mode(s).
@@
 Stable modes decay away rapidly. 
-Unstable modes will not persist on the slow time-scale because the advective term $\langle w'T' \rangle_x$ tends to tends to stabilize $\bar{T}$, thereby creating a negative feedback loop.
+Unstable modes will not persist on the slow time-scale because the advective term $\langle w'T' \rangle$ tends to tends to stabilize $\bar{T}$, thereby creating a negative feedback loop.
 Only marginally stable modes can traverse this hypothetical time-scale separation.
@@
 
-For various $Ra$ and fixed $Pr = 1$, we seek symmetric marginally-stable thermal equilibria (MSTE) $\bar{T}_{\rm{MSTE}}$, thereby satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}).
+For various $Ra$ and fixed $Pr = 1$, we seek symmetric marginally-stable thermal equilibria (MSTE), thereby satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}). 
 We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:model} as well as the IVP (\ref{EQ:T0_IVP}) by representing each field with a dealiased Chebyshev polynomial basis.
 The necessary number of basis functions varies, as eigenfunctions and temperature profiles associated with large $Ra$ admit increasingly small-scale features. 
-We supplement \texttt{Dedalus} with the \texttt{Eigentools} package to compute $\langle w' T' \rangle_x$.
+We supplement \texttt{Dedalus} with the \texttt{Eigentools} package to compute $\langle w' T' \rangle$.
 
@@
 \begin{equation}
-    A^2 \langle w' b' \rangle_x = \sum_{n = 1}^{N} A^2_{n} \langle w' b' \rangle_{x, \, n}
+    A^2 \langle w' b' \rangle = \sum_{n = 1}^{N} A^2_{n} \langle w' b' \rangle_{n}
 \end{equation}
-where  $\langle w' b' \rangle_{x, \, n}$ is composed of perturbations associated with $k_x = \frac{n\pi}{2}$. 
+where  $\langle w' b' \rangle_{n}$ is composed of perturbations associated with $k_x = \frac{n\pi}{2}$. 
 There are now $N$ amplitudes to solve for and $N$ eigenvalues to keep marginally-stable. 
@@
 For this investigation, we calculate solutions for $Ra$ in the range $10^5 - 10^9$. 
-Their mean temperatures $\bar{T}_{\rm{MSTE}}$ are symmetric about $z = 0$ by construction.
+Solutions are symmetric about $z = 0$ by construction.
 
@@
     \includegraphics[width=3.4in]{T_profs_na.png}
-    \caption{Mean temperature profiles $\bar{T}$ for $Ra = 10^8$. 
+    \caption{mean temperature profiles $\bar{T}$ for $Ra = 10^8$. 
     The initial profile is given by (\ref{EQ:T0}). 
@@
 The introduction of this largest branch is likely required to oppose the diffusion of the thinning boundary layers. 
-For $Ra \geq 10^8$, a third branch appears (shown in blue), splitting the widening gap between the blue branch and the green branch. 
+For $Ra \geq 10^8$, a third branch appears (shown in red), splitting the widening gap between the blue branch and the green branch. 
 This development is associated with relatively thick advection profiles, filling a niche in the total flux by uniting the sharp profiles of the largest branch (green) and those of the bulk-domain-oriented smallest branch (blue).
@@
 
-The Nusselt number, which describes convective performance, is given by
-\begin{equation}
-  \Nu = \frac{\langle A^2 \langle w'T' \rangle_x - \mathcal{P}\frac{\partial \bar{T}}{\partial z} \rangle_z}{\langle- \mathcal{P}\frac{\partial \bar{T}}{\partial z} \rangle_z}.
-\end{equation}
-There is no general consensus surrounding the scaling behavior $\Nu \sim Ra^{\beta}$ for high $Ra$ systems.
-The asymptotic value of $\beta$ is of particular importance in astrophysical systems.
-In Figure \ref{fig:nu_vs_ra} we report $\Nu$ for MSTE, DNS, along with several ECS.
+Nusselt numbers $\Nu$ of various solutions are given in Figure \ref{fig:nu_vs_ra}. 
 The marginally-stable thermally-equilibrated states and numerical simulation data exhibit power-law relationships with $Ra$. 
-More specifically, $\beta = 1/3$ which agrees with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} and the scaling argument given by \cite{Malkus_1954}. 
+More specifically, $Ra \sim \Nu^3$ which agrees with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} and the scaling argument given by \cite{Malkus_1954}. 
 The nonlinear solutions, which maximize heat flux, are obtained by \cite{Waleffe}. 
@@
 \begin{align}
-    T(x, z)\big|_{t=0} &= \bar{T}_{\rm{MSTE}}(z) + \sqrt{2} \sum_{n=1}^N  A_n \text{ Re} \Big[ \theta_n(z) e^{ik_{x_n}x} \Big] \nonumber \\
+    T(x, z)\big|_{t=0} &= \bar{T}(z) + \sqrt{2} \sum_{n=1}^N  A_n \text{ Re} \Big[ \theta_n(z) e^{ik_{x_n}x} \Big] \nonumber \\
     \mathbf{u}(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A_n \text{ Re} \Big[\Big( U_n (z) \hat{x} + W_n(z) \hat{z} \Big) e^{ik_{x_n}x} \Big] \nonumber\\
@@
 Consequently, marginally-stable thermally-equilibrated initial conditions do not reduce the simulation time required to achieve a statistically steady state, rather, they increase it considerably.
-Further, this suggests that the MSTE background state perspective is, at least partially, flawed as an appropriate background state would approximate $\langle|\mathbf{u}|^2 \rangle_{\mathcal{D}}$
+Further, this suggests that the MSTE background state perspective is, at least partially, flawed as an appropriate background state would approximate $\langle \langle |\mathbf{u}|^2 \rangle_x \rangle_z$
 % \begin{figure}
@@
 They also exhibit unique and unexpected features: gradient-reversal/dips in temperature profiles, kinetic exaggeration, and greater $\Nu$ than other time-invariant solutions. 
-We also obtain indistinguishable solutions despite initializing with various mean temperature profiles $\bar{T}(z, 0)$. 
+We also obtain indistinguishable solutions despite initializing with different mean temperature profiles $\bar{T}$. 
 Thus solutions might be unique, but we cannot demonstrate this rigorously.

### 2021-04-15 publication_materials/ms_rbc.tex
pre touch up

--- 2021-04-14 publication_materials/ms_rbc.tex
@@
 \begin{abstract}
-Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important properties remain elusive -- particularly in the large Rayleigh number regime.
+Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important trends remain elusive -- particularly in the large Rayleigh number regime.
 In this investigation, we derive and solve a quasilinear form of the Boussinesq Rayleigh-B\'enard equations. 
@@
     Advection tends to stabilize the system, decreasing its eigenvalues. 
-    It follows that there exists some proportion ($A^2(t_0)$) of these two terms which yields a new marginally-stable mean temperature profile $\bar{T}(z, t_0 + \Delta t)$, whose spectrum is ``evolved".}
+    It follows that there exists some proportion $A^2(t_0)$ of these two terms which yields a new marginally-stable mean temperature profile $\bar{T}(z, t_0 + \Delta t)$, whose spectrum is ``evolved".}
     \label{fig:iteration_spectra} 
@@
 \begin{equation}
-    A^2 \langle w' b' \rangle_x = \sum_{n = 1}^{N} A^2_{n} \langle w' b' \rangle_{x, \, n}
+    A^2 \langle w' T' \rangle_x = \sum_{n = 1}^{N} A^2_{n} \langle w' T' \rangle_{x, \, n}
 \end{equation}
-where  $\langle w' b' \rangle_{x, \, n}$ is composed of perturbations associated with $k_x = \frac{n\pi}{2}$. 
+where  $\langle w' T' \rangle_{x, \, n}$ is composed of perturbations associated with $k_x = \frac{n\pi}{2}$. 
 There are now $N$ amplitudes to solve for and $N$ eigenvalues to keep marginally-stable. 
@@
     \includegraphics[width=7.1in]{nu_ra.PNG}
-    \caption{Nusselt numbers are shown for marginally-stable thermally-equilibrated states, statistically-steady direct numerical simulations performed with \texttt{Dedalus} \cite{Anders_cd}, and equilibrated nonlinear solutions, which maximize heat flux, given by \cite{Waleffe}.
-    Both obey power-law relationships with $Ra$, with $\Nu \sim Ra^{1/3}$ in agreement with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} as well as \cite{Malkus_1954}. 
-    Marginally-stable states' Nusselt numbers exceed simulation Nusselt numbers. 
-    This can be explained by the contrasting boundary region geometries shown in Figure \ref{fig:T0_profiles}.}%
+    \caption{Nusselt numbers are shown for MSTE, aspect-ratio optimized ECS \cite{Wen}, and statistically-steady DNS \cite{Johnston, Scheel_2016}.
+    All datasets obey power-law relationships, with MSTE admitting classical scaling $\Nu \sim Ra^{1/3}$. 
+    MSTE facilitate more heat transfer than the ECS and DNS, as can be explained by the contrasting boundary region geometries shown in Figure \ref{fig:T0_profiles}.}%
     \label{fig:nu_vs_ra}%
@@
 
-The Nusselt number, which describes convective performance, is given by
+The Nusselt number, which measures convective performance, is given by
 \begin{equation}
@@
 \end{equation}
-There is no general consensus surrounding the scaling behavior $\Nu \sim Ra^{\beta}$ for high $Ra$ systems.
-The asymptotic value of $\beta$ is of particular importance in astrophysical systems.
-In Figure \ref{fig:nu_vs_ra} we report $\Nu$ for MSTE, DNS, along with several ECS.
-The marginally-stable thermally-equilibrated states and numerical simulation data exhibit power-law relationships with $Ra$. 
-More specifically, $\beta = 1/3$ which agrees with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} and the scaling argument given by \cite{Malkus_1954}. 
-The nonlinear solutions, which maximize heat flux, are obtained by \cite{Waleffe}. 
-$\Nu$ of both equilibria exceed that of simulations, which might be due to the transitional behaviors outlined by \cite{Yalniz} and \cite{Cvitanovic} inhibiting heat flux. 
-Alternatively, we might anticipate the existence of exact coherent states with smaller $\Nu$, forming another node in the Markov chain whose long-term behavior agrees with the simulation data.
+There is no general consensus surrounding the scaling behavior of $\Nu$ for high $Ra$ systems, which are of particular importance in astrophysical systems.
+In Figure \ref{fig:nu_vs_ra} we report $\Nu$ for MSTE and DNS states.
+Both exhibit power-law dependence $\Nu \sim Ra^{\beta}$ with classical Malkus scaling $\beta = 1/3$ \cite{Malkus_1954}. 
+\cite{Wen} hypothesized that $\Nu$ of ECS which admit classical Malkus scaling must always exceed $\Nu$ of turbulent convection.
+Our findings agree; $\Nu$ of MSTE exceed 2D and 3D DNS. 
+This might be due to the chaotic transitions among unstable periodic orbits outlined by \cite{Yalniz, Cvitanovic} inhibiting heat flux. 
+We might also anticipate the existence of exact coherent states with smaller $\Nu$, occupying neighboring nodes in the Markov chain whose long-term behavior agrees with DNS.
 
@@
 \end{equation}
-Consequently, marginally-stable thermally-equilibrated initial conditions do not reduce the simulation time required to achieve a statistically steady state, rather, they increase it considerably.
-Further, this suggests that the MSTE background state perspective is, at least partially, flawed as an appropriate background state would approximate $\langle|\mathbf{u}|^2 \rangle_{\mathcal{D}}$
+Consequently, marginally-stable thermally-equilibrated initial conditions do not reduce the simulation time required to achieve a statistically steady state--rather, they increase it considerably.
+This suggests the MSTE background state perspective is, at least partially, flawed as an appropriate background state would approximate $\langle|\mathbf{u}|^2 \rangle_{\mathcal{D}}$ with more fidelity.
 % \begin{figure}
@@
 This is reasonable to expect, since accurate boundary layer approximations and DNS data should have similar stability characteristics. 
-By definition, $\bar{T}_{\rm{MUTE}}$ is unstable and would therefore admit more diffuse boundary layer structures, requiring smaller $A^2(t)$ (less advection) to satisfy the stability constraint and thereby reducing $\Nu$, $\langle \langle |\mathbf{u}|^2 \rangle_x \rangle_z$ and possibly $\beta$.
+By definition, $\bar{T}_{\rm{MUTE}}$ is unstable and would therefore admit more diffuse boundary layer structures, requiring smaller $A^2(t)$ (less advection) to satisfy the stability constraint and thereby reducing $\Nu$, $\langle |\mathbf{u}|^2 \rangle_{\mathcal{D}}$ and possibly $\beta$.
 

### 2021-04-15 publication_materials/ms_rbc.tex
rev2a

@@
 \begin{abstract}
-Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important trends remain elusive -- particularly in the large Rayleigh number regime.
+Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important properties remain elusive -- particularly in the large Rayleigh number regime.
 In this investigation, we derive and solve a quasilinear form of the Boussinesq Rayleigh-B\'enard equations. 
@@
 Rayleigh-B\'enard convection plays a foundational role in large-scale astrophysical and geophysical settings.
-Buoyancy-driven convection regulates heat transfer and often gives way to violently turbulent flows, thereby dominating large-scale behaviors and fueling small-scale processes in important systems \cite{Couston}.
+Buoyancy-driven convection regulates heat transfer and often gives way to violently turbulent flows, thereby dominating large-scale behaviors and generating small-scale processes in important systems \cite{Couston}.
 
 Aggressive convection, which is associated with large Rayleigh numbers $Ra$, is difficult to simulate. 
-State of the art convection simulations performed by \cite{Zhu_2018} have reached $Ra \sim 10^{14}$ but estimates for stars are $Ra \sim 10^{20}$ \cite{Ossendrijver}. 
+State of the art simulations performed by \cite{Zhu_2018} have reached $Ra \sim 10^{14}$ but estimates for stars are $Ra \sim 10^{20}$ \cite{Ossendrijver}. 
 The scaling behavior of the Nusselt number $\Nu \sim Ra^{\beta}$ in the asymptotic ultimate regime is of particular interest.
@@
 Much of the published work on this topic relates to unstable exact coherent states (ECS) \cite{Waleffe, Sondak, Wen, chini_cells}. 
-Simulations and analysis performed by \cite{Yalniz, Cvitanovic} suggest that chaotic simulation trajectories can be represented by a Markov chain whose long-term behavior is given by the time-weighted-average of a finite set of ECS.
-Should that be the case, it is crucial that we discover and classify such states.
+Simulations and analysis performed by \cite{Yalniz, Cvitanovic} suggest that chaotic simulation trajectories can be represented by a Markov chain whose long-term behavior is given by the time-weighted-average of a finite set of unstable equilibria.
+Should that be the case, it is crucial that we discover and classify such equilibria.
 
@@
 The domain $\mathcal{D}$ is 2-dimensional rectangular and horizontally periodic with spatial dimensions $0 < x < 4$ and $-1/2 < z < 1/2$. 
-The fluid of interest is constrained between two planar boundaries at $z = -1/2$ and $z = 1/2$ with fixed temperatures $1$ and $0$ respectively. 
+The fluid of interest is constrained between two flat boundaries at $z = -1/2$ and $z = 1/2$ with fixed temperatures $1$ and $0$ respectively. 
 At both boundaries we specify impenetrable, no-slip conditions, such that the velocity $\mathbf{u} = u \hat{x} + w \hat{z} = \mathbf{0}$ at $z = \pm 1/2$. 
@@
 For completeness, we specify a final boundary condition $p = p_0$ at $z = \pm 1/2$. 
-Any system of this form can be characterized by its dimensionless Rayleigh number $Ra = \frac{g\alpha L^3 \Delta T}{\nu \kappa}$ and Prandtl number $Pr = \frac{\nu}{\kappa}$, where $g, \, \alpha, \, L, \, \Delta T, \nu, \kappa$ are the gravitational acceleration, coefficient of thermal expansion, domain height, boundary temperature difference, kinematic viscosity, and thermal diffusivity respectively.
+Any system of this form can be characterized by its dimensionless Rayleigh number $Ra = \frac{g\alpha L^3 \Delta T}{\nu \kappa}$ and Prandtl number $Pr = \frac{\nu}{\kappa}$, where $g, \, \alpha, \, L, \, \Delta T, \nu, \kappa$ are the gravitational acceleration, coefficient of thermal expansion, domain height, opposed temperature difference, kinematic viscosity, and thermal diffusivity respectively.
 For convenience, we define
@@
 \end{align}
-where $A(t)$ is some unknown real amplitude and the mean-velocity components vanish due to incompressibility and symmetry.
-Perturbations must admit no horizontal-average; an arbitrary perturbation $f'$ obeys
+where $A(t)$ is some unknown real amplitude and the mean-velocity components vanish due to incompressibility and symmetry. Perturbations must admit no horizontal-average
 \begin{equation}
@@
 At some arbitrary time $t_0$, the forcing term $\langle w'T' \rangle_x$ can be found by solving an eigenvalue problem (EVP) which itself involves $\frac{\partial \bar{T}}{\partial z}$.
-We also assume this term is composed of eigenfunctions belonging to the dominant mode(s).
 
@@
 Stable modes decay away rapidly. 
-Unstable modes will not persist on the slow time-scale because the advective term $\langle w'T' \rangle_x$ tends to tends to stabilize $\bar{T}$, thereby creating a negative feedback loop.
+Unstable modes will not persist on the slow time-scale because the advective term $\langle w'T' \rangle_x$ tends to stabilize $\bar{T}$, thereby creating a negative feedback loop.
 Only marginally stable modes can traverse this hypothetical time-scale separation.
@@
 
-For various $Ra$ and fixed $Pr = 1$, we seek symmetric marginally-stable thermal equilibria (MSTE) $\bar{T}_{\rm{MSTE}}$, thereby satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}).
+For various $Ra$ and fixed $Pr = 1$, we seek symmetric marginally-stable thermal equilibria (MSTE), thereby satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}). 
 We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:model} as well as the IVP (\ref{EQ:T0_IVP}) by representing each field with a dealiased Chebyshev polynomial basis.
@@
 At $t = 0$, we begin with a marginally-stable initial profile $\bar{T}(z, 0)$ whose construction is outlined in \ref{sec:initial_profile}. 
-At some arbitrary time $t = t_0$, we seek to evolve $\bar{T}(z, t_0)$ into a new marginally-stable profile $\bar{T}(z, t_0 + \Delta t)$ according to (\ref{EQ:T0_IVP}) using forward-Euler. 
+At some arbitrary time $t = t_0$, we seek to evolve $\bar{T}(z, t_0)$ into a new marginally-stable profile $\bar{T}(z, t_0 + \Delta t)$ according to (\ref{EQ:T0_IVP}) via forward-Euler. 
 This generally involves a unique and unknown value $A^2(t_0) > 0$. 
@@
 \end{equation}
-where $\omega_{\rm{diff}}$ and $\omega_{\rm{adv}}$ refer to the diffused and advected eigenvalues of the initially marginal mode (corresponding to the light blue and green points respectively at $k_x = \pi$ in Figure \ref{fig:iteration_spectra}).
+where $\omega_{\rm{diff}}$ and $\omega_{\rm{adv}}$ refer to the diffused and advected eigenvalues of the initially marginal mode.
+These quantities correspond to the light blue and green points at $k_x = \pi$ in Figure \ref{fig:iteration_spectra}).
 $\bar{T}(z, t)$ is then evolved according to (\ref{EQ:T0_IVP}) and another eigenvalue solve is performed. 
 Given a fixed timestep $\Delta t$, we assume the dominant eigenvalue can be described by a continuous function $\omega_{\rm{max}} (A^2)$ which is locally differentiable. 
-We use Newton's method to find an amplitude which satisfies our marginal stability tolerance criterion $|\omega_{\rm{max}} (A^2)| \leq 10^{-9}$. 
+We use Newton's method to find an amplitude which satisfies our marginal stability tolerance criterion. 
 The dominant mode is not fixed; an iteration can facilitate the transfer of marginal-stability from one mode to another. 
@@
 For this investigation, we calculate solutions for $Ra$ in the range $10^5 - 10^9$. 
-Their mean temperatures $\bar{T}_{\rm{MSTE}}$ are symmetric about $z = 0$ by construction.
+Their mean temperatures $\bar{T}$ are symmetric about $z = 0$ by construction.
 
-Figure \ref{fig:T0_profiles} gives temperature profiles for $Ra = 10^8$ where the initial profile, given by (\ref{EQ:T0}), is employed at iteration 0; the MSTE profile corresponds to the thermally relaxed state; and the DNS (direct numerical simulations) profile is obtained by solving (\ref{EQ:motion1})--(\ref{EQ:motion3}) with \texttt{Dedalus}, followed by horizontal and time averaging.
-The DNS curve is more diffuse than the MSTE curve, which in turn, is more diffuse than the initial curve. 
-Performing an eigenvalue solve by setting $\bar{T}$ equal to the DNS profile yields positive eigenvalues. 
-Comprehensively, this suggests that MSTE might maximize boundary layer thickness, while subject to the marginal stability constraint.
-
-The most resilient and unexpected feature of thermally equilibrated mean temperature profiles are the pronounced dips adjacent to the boundary layers. 
-These dips appear in every solution, regardless of $Ra$. 
-Physically, they correspond to thin layers in which the temperature gradient reverses, contradicting an important hypothesis of \cite{Malkus_1954}. 
-This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure \ref{fig:flux}.  
 \begin{figure}
@@
     The MSTE profile exhibits prominent dips, nested alongside the boundary regions. 
-    The source of this feature is not well understood, but similar temperature gradient reversal regions were found by \cite{chini_cells} along the midplanes of 2-dimensional convective cellular solutions at $Ra \sim 10^6$.}
+    The source of this feature is not well understood, but similar temperature gradient reversal regions were found by \cite{chini_cells} along the midlines of 2-dimensional convective cellular solutions at $Ra \sim 10^6$.}
     \label{fig:T0_profiles}
 \end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=3.4in]{kx_m_ra1.png}
-    \caption{Wavenumbers of marginally-stable modes of thermally equilibrated states. 
-    Markers are color-coded according to their adjacent local maxima index in the eigenvalue spectrum. 
-    For example, the spectrum corresponding to $Ra = 10^5$ has adjacent marginal wavenumbers $k_x = \pi, \, 1.5\pi$. 
-    The $Ra = 10^9$ spectrum, shown in lower right corner of Figure \ref{fig:flux}, has three groups of maxima, with a single marginal mode in the first group ($k_x = 1.5\pi$), two adjacent marginal modes in the second group ($k_x = 6\pi, \, 6.5\pi$), and two adjacent marginal modes in the third group ($k_x = 23.5\pi, \, 24\pi$).
-    The largest wavenumbers of the green branch obey a power-law relationship with $Ra$}
-    \label{fig:kx_marginals}
-\end{figure}
+
+Figure \ref{fig:T0_profiles} gives temperature profiles for $Ra = 10^8$ where the initial profile, given by (\ref{EQ:T0}), is employed at iteration 0; the MSTE profile corresponds to the thermally relaxed state; and the DNS (direct numerical simulations) profile is obtained by solving (\ref{EQ:motion1})--(\ref{EQ:motion3}) with \texttt{Dedalus}, followed by horizontal and time averaging.
+The DNS curve is more diffuse than the MSTE curve, which in turn, is more diffuse than the initial curve. 
+Performing an eigenvalue solve by setting $\bar{T}$ equal to the DNS profile yields positive eigenvalues. 
+Comprehensively, this suggests that MSTE might maximize boundary layer thickness, while subject to the marginal stability constraint.
+
+The most resilient and unexpected feature of MSTE temperature profiles are the pronounced dips adjacent to the boundary layers. 
+These dips appear in every solution, regardless of $Ra$. 
+Physically, they correspond to thin layers in which the mean temperature gradient reverses, contradicting an important hypothesis of \cite{Malkus_1954}. 
+This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure \ref{fig:flux}. 
+We don't understand the source of these dips, but similar temperature gradient reversals were reported by \cite{chini_cells} along the midlines of 2-dimensional convective cellular solutions at $Ra \sim 10^6$.
+
 \begin{figure*}
@@
 \end{figure*}
+
+Equilibrated states exhibit distinct behaviors for large and small $Ra$. 
+This contrast is illustrated in Figure \ref{fig:flux}, where we give heat flux profiles and eigenvalue spectra for two cases: $Ra = 2 \times 10^5$ and $Ra = 10^9$. 
+For $Ra = 2 \times 10^5$, there is a single presumed local maximum in the eigenvalue spectrum, whose adjacent modes' advection profiles occupy the bulk of the domain. 
+These states have relaxed boundary layers which gradually subside as advection becomes the dominant flux component. 
+Such transitional regions do not appear for $Ra = 10^9$, where the shift from diffusion to advection is sharp, requiring pronounced, small-scale advection profiles belonging to modes in the third local maxima pair of the eigenvalue spectrum.
+Traversing towards the midline of the domain, we see increasingly thicker advection profiles corresponding to modes in the second local maxima pair, eventually culminating in the dominant $k_x = 1.5\pi$ mode.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=3.4in]{kx_m_ra1.png}
+    \caption{Wavenumbers of marginally-stable modes of thermally equilibrated states. 
+    Markers are color-coded according to their adjacent local maxima index in the eigenvalue spectrum. 
+    For example, the spectrum corresponding to $Ra = 10^5$ has adjacent marginal wavenumbers $k_x = \pi, \, 1.5\pi$. 
+    The $Ra = 10^9$ spectrum, shown in lower right corner of Figure \ref{fig:flux}, has three groups of maxima, with a single marginal mode in the first group ($k_x = 1.5\pi$), two adjacent marginal modes in the second group ($k_x = 6\pi, \, 6.5\pi$), and two adjacent marginal modes in the third group ($k_x = 23.5\pi, \, 24\pi$).
+    The largest wavenumbers of the green branch obey a power-law relationship with $Ra$}
+    \label{fig:kx_marginals}
+\end{figure}
+
+Thermally equilibrated states with large $Ra$ tend to have diverse combinations of marginal modes. 
+In every case, the $k_x = 1.5\pi$ mode is included and is often unaccompanied by adjacent modes. 
+In Figure \ref{fig:kx_marginals} we give the wavenumbers $k_x$ of marginal modes, color-coded according to their adjacencies. 
+Marginal modes often appear in neighboring pairs, where the larger mode is denoted with an x and the smaller mode is denoted with a +. 
+In these cases we infer the existence of a local maximum eigenvalue between the two adjacent marginally-stable modes. 
+For $Ra \geq 10^6$, a second branch of marginal modes is introduced as shown in light green, obeying some power-law with respect to $Ra$. 
+The introduction of this largest branch is likely required to oppose the diffusion of the thinning boundary layers. 
+For $Ra \geq 10^8$, a third branch appears (shown in light blue), splitting the widening gap between the other branches. 
+This development is associated with moderately thick advection profiles, filling a niche in the total flux by uniting the sharp profiles of the largest branch and those of the bulk-domain-oriented smallest branch.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=3.4in]{del_kx_inv.png}
+    \caption{For $Ra \geq 10^6$, the maximum marginally-stable wavenumbers (corresponding to the green X markers in Figure \ref{fig:kx_marginals}) are inversely related to the boundary layer heights $\delta$.
+    $(\max \{ k_x \})^{-1}$ gives a minimum $x$ length scale for the perturbations, and consequently, the advection. 
+    We expect the minimum $z$ length scale to agree with the boundary layer height $\delta$ because otherwise the boundary layer would continue to diffuse. 
+    This is illustrated in the lower left corner of Figure \ref{fig:flux}, where the advection profile for $k_x = 24\pi$ is tightly flanked by the surrounding boundary layer. 
+    This suggests that the minimum $x$ and $z$ length scales obey some constant ratio over various $Ra$.}
+    \label{fig:del_inv}
+\end{figure}
+
+The largest marginal wavenumber $\max \{ k_x \}$ (represented by the light green branch in Figure \ref{fig:kx_marginals}) serves as a inverse minimum length-scale in the $x$ direction.
+The finest structures in $\bar{T}(z)$ appear near the boundaries, providing us with a complementary minimum length-scale for $z$.
+We define the interior boundary layer threshold as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$.
+In Figure \ref{fig:del_inv}, we illustrate the constant ratio between these two quantities for various $Ra$.
+The quasilinear model cannot describe small-scale behaviors in either direction.
+Discretization of the normal modes allows us to collapse the problem into a single dimension, but this comes at a cost.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=3.4in]{del_ra.PNG}
+    \caption{Boundary layer height $\delta$ of marginally-stable thermal equilibria. 
+    We define the threshold of each boundary layer as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, corresponding to the local extrema of the equilibrated curve in Figure \ref{fig:T0_profiles}.
+    Plotting on a log-log scale, we find that $\delta$ and $Ra$ obey a power-law relationship.
+We also demonstrate that $Ra^{1/3}\delta$ is approximately constant with respect to $Ra$, implying $Ra \propto  \delta^{-3}$ which remains consistent with \cite{Malkus_1954}}
+    \label{fig:bl_ra}
+\end{figure}
+
+In general, MSTE can be characterized by their boundary layer height, from which, the rest of their properties follow.
+In Figure \ref{fig:bl_ra}, we illustrate the scaling behavior of the boundary layer height $\delta = Ra^{-1/3}$.
+This is consistent with Malkus' classical marginal-stability theory, a scaling argument which perceives the boundary regions as subdomains which are themselves marginally-stable \cite{Malkus_1954}.
+
 \begin{figure*}
@@
     \caption{Nusselt numbers are shown for MSTE, aspect-ratio optimized ECS \cite{Wen}, and statistically-steady DNS \cite{Johnston, Scheel_2016}.
-    All datasets obey power-law relationships, with MSTE admitting classical scaling $\Nu \sim Ra^{1/3}$. 
-    MSTE facilitate more heat transfer than the ECS and DNS, as can be explained by the contrasting boundary region geometries shown in Figure \ref{fig:T0_profiles}.}%
+    All datasets obey power-law relationships, with the MSTE and ECS admitting classical scaling $\Nu \sim Ra^{1/3}$. 
+    MSTE have greater $\Nu$ than the ECS, which in turn, have greater $\Nu$ than the DNS. This can be explained by the contrasting boundary layer geometries shown in Figure \ref{fig:T0_profiles}.}%
     \label{fig:nu_vs_ra}%
 \end{figure*}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=3.4in]{del_kx_inv.png}
-    \caption{For $Ra \geq 10^6$, the maximum marginally-stable wavenumber (corresponding to the green X markers in Figure \ref{fig:kx_marginals}) are inversely related to the boundary layer thicknesses $\delta$.
-    $(\max \{ k_x \})^{-1}$ gives a minimum $x$ length scale for the perturbations, and consequently, the advection. 
-    We expect the minimum $z$ length scale to agree with the boundary layer thickness $\delta$ because otherwise the boundary layer would continue to diffuse. 
-    This is illustrated in the lower left corner of Figure \ref{fig:flux}, where the advection profile for $k_x = 24\pi$ is tightly flanked by the surrounding boundary layers. 
-    This suggests that the minimum $x$ and $z$ length scales obey some constant ratio.}
-    \label{fig:del_inv}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=3.4in]{del_ra.PNG}
-    \caption{Boundary layer widths $\delta$ of marginally-stable thermal equilibria. 
-    We define the threshold of each boundary layer as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, corresponding to the local extrema of the equilibrated curve in Figure \ref{fig:T0_profiles}.
-    Plotting on a log-log scale, we find $\delta$ and $Ra$ obey a power-law relationship.
-We also demonstrate that $Ra^{1/3}\delta$ is approximately constant with respect to $Ra$ implying $Ra \propto  \delta^{-3}$, as predicted by \cite{Malkus_1954}}
-    \label{fig:bl_ra}
-\end{figure}
-
-Equilibrated states exhibit distinct behaviors for large and small $Ra$. 
-This contrast is illustrated in Figure \ref{fig:flux}, where we give heat flux profiles and eigenvalue spectra for two cases: $Ra = 2 \times 10^5$ and $Ra = 10^9$. 
-For lower $Ra$, there is a single presumed local maximum in the eigenvalue spectrum, whose adjacent modes' advection profiles occupy the bulk of the domain. 
-These states have relaxed boundary layers which gradually subside as advection becomes the dominant component of the total flux. 
-Such transitional regions do not appear in high $Ra$ cases, where the shift from diffusion to advection is sharp, requiring pronounced, small-scale advection profiles belonging to modes adjacent to the third presumed local maximum in the eigenvalue spectrum.
-Traversing towards the midplane of the domain, we see increasingly thicker advection profiles corresponding the wavenumbers adjacent to the second local maximum, eventually culminating in the dominant $k_x = 1.5\pi$ mode.
-
-Thermally equilibrated states with large $Ra$ tend to have a more diverse set of marginal modes as compared to small $Ra$ states. 
-In every case, the $k_x = 1.5\pi$ mode is included and is often unaccompanied by adjacent modes. 
-In Figure \ref{fig:kx_marginals} we give the wavenumbers $k_x$ of marginal modes, color coded accordingly to their respective adjacencies. 
-Marginal modes often appear in neighboring pairs, in which case the larger mode is denoted with an x and the smaller mode is denoted with a +. 
-In these cases we infer the existence of a local maximum eigenvalue between the two adjacent marginally-stable modes. 
-For $Ra \geq 10^6$, a second branch of marginal modes is introduced as shown in green, increasing according to some power-law with respect to $Ra$. 
-The introduction of this largest branch is likely required to oppose the diffusion of the thinning boundary layers. 
-For $Ra \geq 10^8$, a third branch appears (shown in blue), splitting the widening gap between the blue branch and the green branch. 
-This development is associated with relatively thick advection profiles, filling a niche in the total flux by uniting the sharp profiles of the largest branch (green) and those of the bulk-domain-oriented smallest branch (blue).
-
-In general, marginally-stable thermal equilibria can be characterized by their boundary layer thicknesses, from which, the rest of their properties follow.
-Letting the interior boundary layer threshold be the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, we find that $Ra \propto  \delta^{-3}$ as illustrated in Figure \ref{fig:bl_ra}.
-This is consistent with Malkus' classical marginal-stability theory, a scaling argument which perceives the boundary regions as subdomains which are themselves marginally-stable.
 
@@
 In Figure \ref{fig:nu_vs_ra} we report $\Nu$ for MSTE and DNS states.
-Both exhibit power-law dependence $\Nu \sim Ra^{\beta}$ with classical Malkus scaling $\beta = 1/3$ \cite{Malkus_1954}. 
+Both exhibit power-law dependence $\Nu \sim Ra^{\beta}$ with classical scaling $\beta = 1/3$. 
 \cite{Wen} hypothesized that $\Nu$ of ECS which admit classical Malkus scaling must always exceed $\Nu$ of turbulent convection.
@@
 This might be due to the chaotic transitions among unstable periodic orbits outlined by \cite{Yalniz, Cvitanovic} inhibiting heat flux. 
-We might also anticipate the existence of exact coherent states with smaller $\Nu$, occupying neighboring nodes in the Markov chain whose long-term behavior agrees with DNS.
+We might also anticipate the existence of similar equilibria, having smaller $\Nu$ and occupying neighboring nodes in the Markov chain whose long-term behavior agrees with DNS.
 
 \section{Simulations with Thermally Equilibrated Initial Conditions}
-This investigation is partially motivated by the prospect of decreasing nonlinear simulation relaxation times by employing thermally-equilibrated initial conditions. 
-Conventionally, (\ref{EQ:motion1}) - (\ref{EQ:motion3}) are solved via direct numerical simulation (DNS) with the linear initial conditions
+This investigation is partially motivated by the prospect of decreasing DNS times by employing MSTE initial conditions. 
+Conventionally, (\ref{EQ:motion1}) - (\ref{EQ:motion3}) are solved via DNS with the linear initial conditions
 \begin{align}
@@
 
-Simulations launched with MSTE initial conditions do not exhibit a convective-transient period, as the large-scale anatomy of convective cells, which are characteristic of Rayleigh-B\'enard convection, exist on initialization.
+Simulations with MSTE initial conditions do not exhibit a convective-transient period, as the large-scale anatomy of convective cells exists on initialization. 
 This is illustrated in Figure \ref{fig:nu_sim}, where the sharp spike in $\Nu$ is associated with a turbulent transitional period of upwelling until the distinctive plume-like structure is established.
@@
 If we treat MSTE as background states, DNS suggest that plumes, vortex sheets, and other unstable turbulent features inhibit total heat transfer. 
-This perspective agrees with convectional models of transitions to turbulent flows, such as Boussinesq's turbulent-viscosity hypothesis \cite{boussinesq_1877}, where the emergence of small-scale velocity structures tends to increase total shear \cite{Lecoanet_KH, drazin_reid_2004, pope_2000}, thereby impeding buoyancy-driven flows and decreasing advection in the bulk of the domain.
-We could also atribute the diffuse DNS temperature profile in Figure \ref{fig:T0_profiles} with unsteady boundary-layer penetration and mixing that MSTE do not exhibit.
+This perspective agrees with conventional models of transitions to turbulent flows, such as Boussinesq's turbulent-viscosity hypothesis \cite{boussinesq_1877}, where the emergence of small-scale velocity structures tends to increase total shear \cite{Lecoanet_KH, drazin_reid_2004, pope_2000}, thereby impeding buoyancy-driven flows and decreasing advection in the bulk of the domain.
+We could also attribute the diffuse DNS temperature profile in Figure \ref{fig:T0_profiles} with unsteady boundary-layer penetration and mixing that MSTE do not exhibit.
 
@@
 % \end{figure}
-The marginally-stable equilibria are associated with a combination of eigenfunctions whose average kinetic energy is significantly larger than the statistical steady state, as given by Figure \ref{fig:ke_sim}.
-This is postpones kinetic relaxation because the large horizontal flows decay on a viscous timescale
+The average kinetic energy MSTE is significantly larger than the statistical steady state, as shown Figure \ref{fig:ke_sim}. 
+This is postpones kinetic relaxation because the large-scale flows decay on a viscous time-scale
 \begin{equation}
@@
 \end{equation}
-Consequently, marginally-stable thermally-equilibrated initial conditions do not reduce the simulation time required to achieve a statistically steady state--rather, they increase it considerably.
-This suggests the MSTE background state perspective is, at least partially, flawed as an appropriate background state would approximate $\langle|\mathbf{u}|^2 \rangle_{\mathcal{D}}$ with more fidelity.
+Consequently, MSTE initial conditions do not reduce the simulation time required to achieve a statistically steady state--rather, they increase it considerably.
+This suggests the MSTE background state perspective is partially flawed, since an appropriate background state would approximate $\langle|\mathbf{u}|^2 \rangle_{\mathcal{D}}$ with more fidelity.
 % \begin{figure}
@@
         \caption{Nusselt numbers of simulations performed at $Ra = 10^8$ with the conventional initial conditions (black) and MSTE initial conditions (blue). 
-        MSTE simulations do not undergo a convective-transient period because the characteristic large-scale convective cell structure exists on initialization.
-For high $Ra$ simulations, researchers often choose to recycle the results of similar $Ra$ runs \cite{Verzicco, Johnston} because the high-Reynolds number flows associated with the convective transient period are computationally prohibitive \cite{Anders_AE}.}
+        MSTE simulations do not undergo a convective-transient period because the characteristic large-scale convective cell structure exists on initialization.}
         \label{fig:nu_sim}
@@
 In general, the reduced model we study in this paper can be perceived as a unique way to describe Rayleigh–Bénard convection. 
-Solutions to the quasilinear problem retain several key features that are ubiquitous in experiments and simulations: power-law $\Nu$ scaling, plume-like structures, and minimum length-scale approximations \cite{Malkus_1954}.
+Solutions to the quasilinear problem retain several key features that are ubiquitous in experiments and simulations: power-law $\Nu$ scaling, convective cell structures, and minimum length-scale approximations \cite{Malkus_1954}.
 They also exhibit unique and unexpected features: gradient-reversal/dips in temperature profiles, kinetic exaggeration, and greater $\Nu$ than other time-invariant solutions. 
-We also obtain indistinguishable solutions despite initializing with various mean temperature profiles $\bar{T}(z, 0)$. 
+We obtain indistinguishable solutions despite initializing with various mean temperature profiles $\bar{T}(z, 0)$. 
 Thus solutions might be unique, but we cannot demonstrate this rigorously.
@@
 We might curtail the disagreement between MSTE and DNS by loosening our marginal-stability criterion. 
-Should the time-scales not be entirely separate, we might anticipate the long-term persistance of nearly-marginal unstable modes. 
-This perpetual linear instability cannot be described by our model independently (we do not know, a priori, how unstable such modes are) but it might prove fruitful to investigate moderately unstable thermal equilibria (MUTE).
+Should the time-scales not be entirely separate, we might anticipate the long-term persistance of moderately unstable modes. 
+This perpetual instability cannot be described by our model independently (we do not know, a priori, how unstable such modes are) but it might prove fruitful to investigate moderately unstable thermal equilibria (MUTE).
 More precisely, instead of traversing the manifold of marginally-stable states toward MSTE, we could consider the manifold of states whose maximum eigenvalue(s) $\omega_{\rm{max}}$ agree with some other stability constraint.
-Note that under this definition, 2-dimensional ECS and temporally-averaged steady DNS data are subsets of MUTE, since they are thermally-equilibrated and generally unstable, though they need not necessarily satisfy the quasilinear form.
+Note that under this definition, 2-dimensional ECS are themselves MUTE, because they are thermally-equilibrated and generally unstable, though they need not satisfy the quasilinear form.
 
@@
 Accessible MUTE states would not rely on DNS, satisfying only the quasilinear problem and stability constraint. 
-Such MUTE ought to agree with DNS data more precisely then MSTE, ideally having less extreme velocities. 
+Such MUTE ought to agree with DNS data more precisely than MSTE, ideally having slower flows. 
 This is reasonable to expect, since accurate boundary layer approximations and DNS data should have similar stability characteristics. 
-By definition, $\bar{T}_{\rm{MUTE}}$ is unstable and would therefore admit more diffuse boundary layer structures, requiring smaller $A^2(t)$ (less advection) to satisfy the stability constraint and thereby reducing $\Nu$, $\langle |\mathbf{u}|^2 \rangle_{\mathcal{D}}$ and possibly $\beta$.
+By definition, MUTE are unstable and would therefore admit more diffuse boundary layer structures, requiring smaller $A^2(t)$ (less advection) to satisfy the stability constraint and thereby reducing $\Nu$, $\langle |\mathbf{u}|^2 \rangle_{\mathcal{D}}$ and possibly $\beta$.
 
@@
 \end{align}
-where $\delta_0$ is the boundary layer thickness. 
+where $\delta_0$ is the boundary layer height. 
 We expect that each $\Ra$ is associated with a unique $\delta_0$ for which $\bar{T}_0(z)$ is marginally-stable. 

### 2021-04-15 publication_materials/ms_rbc.tex
Rayleigh 1917 citation: published in during WWI?

@@
 thereby alleviating any ambiguity in $A(t)$. 
-Substituting (\ref{EQ:reynolds_dc_T}) into (\ref{EQ:motion3}) and taking the horizontal average reduces the system to a simple initial value problem (IVP) for $\bar{T}$
+Substituting (\ref{EQ:reynolds_dc_T}) into (\ref{EQ:motion3}) and taking the horizontal-average reduces the system to a simple initial value problem (IVP) for $\bar{T}$
 \begin{equation}
@@
 
-In 1916, Lord Rayleigh observed that (\ref{EQ:linear1}) and (\ref{EQ:linear3}) can be manipulated into a separable form with generalized solutions
+In his groundbreaking report \cite{Rayleigh_1916}, Lord Rayleigh observed that (\ref{EQ:linear1}) and (\ref{EQ:linear3}) can be manipulated into a separable form with generalized solutions
 \begin{align}
@@
 \section{Perturbation Evolution}
-Solving the linearized system (\ref{EQ:linear1}) -- (\ref{EQ:linear3}) does not yield $A(t)$. 
+Solving the linearized system (\ref{EQ:linear1})--(\ref{EQ:linear3}) does not yield $A(t)$. 
 To evolve $\bar{T}$, we assume the perturbations and mean quantities evolve according to different time-scales, as in \cite{michel_chini_2019}.
@@
 \section{Properties of Thermally Equilibrated States}\label{sec:properties}
-MSTE are solutions to the quasilinear form of the Rayleigh-B\'enard convection equations derived in section \ref{sec:model}. 
+MSTE are fixed points of the quasilinear form derived in section \ref{sec:model}, differing from ECS in that ECS are fixed points of the full nonlinear problem (\ref{EQ:motion1})--(\ref{EQ:motion3}). 
+Such definitions are not mutually exclusive, but in general we can assume that MSTE and ECS are not steady with respect to their counterparts' problems.
 For this investigation, we calculate solutions for $Ra$ in the range $10^5 - 10^9$. 
@@
 
-Figure \ref{fig:T0_profiles} gives temperature profiles for $Ra = 10^8$ where the initial profile, given by (\ref{EQ:T0}), is employed at iteration 0; the MSTE profile corresponds to the thermally relaxed state; and the DNS (direct numerical simulations) profile is obtained by solving (\ref{EQ:motion1})--(\ref{EQ:motion3}) with \texttt{Dedalus}, followed by horizontal and time averaging.
+Figure \ref{fig:T0_profiles} gives temperature profiles for $Ra = 10^8$ where the initial profile, given by (\ref{EQ:T0}), is employed at iteration 0; the MSTE profile corresponds to the thermally relaxed state; and the DNS (direct numerical simulations) profile is obtained by solving (\ref{EQ:motion1})--(\ref{EQ:motion3}) with \texttt{Dedalus}, followed by horizontal- and time- averaging.
 The DNS curve is more diffuse than the MSTE curve, which in turn, is more diffuse than the initial curve. 
@@
     \includegraphics[width=7.1in]{nu_ra.PNG}
-    \caption{Nusselt numbers are shown for MSTE, aspect-ratio optimized ECS \cite{Wen}, and statistically-steady DNS \cite{Johnston, Scheel_2016}.
+    \caption{Nusselt numbers are shown for MSTE, aspect-ratio-optimized ``steady rolls'' ECS \cite{Wen}, as well as statistically-steady 2D and 3D DNS \cite{Johnston, Scheel_2016}.
     All datasets obey power-law relationships, with the MSTE and ECS admitting classical scaling $\Nu \sim Ra^{1/3}$. 
@@
 \begin{equation}
-  \Nu = \frac{\langle A^2 \langle w'T' \rangle_x - \mathcal{P}\frac{\partial \bar{T}}{\partial z} \rangle_z}{\langle- \mathcal{P}\frac{\partial \bar{T}}{\partial z} \rangle_z}.
+  \Nu = 1 + \frac{A^2}{\mathcal{P}} \langle w'T' \rangle_x.
 \end{equation}
 There is no general consensus surrounding the scaling behavior of $\Nu$ for high $Ra$ systems, which are of particular importance in astrophysical systems.
-In Figure \ref{fig:nu_vs_ra} we report $\Nu$ for MSTE and DNS states.
-Both exhibit power-law dependence $\Nu \sim Ra^{\beta}$ with classical scaling $\beta = 1/3$. 
+In Figure \ref{fig:nu_vs_ra} we report $\Nu$ for MSTE, ``steady rolls" ECS \cite{Wen}, and DNS \cite{Scheel_2016, Johnston}.
+All states obey $\Nu \sim Ra^{\beta}$ with classical scaling $\beta = 1/3$ in the ECS and MSTE. 
 \cite{Wen} hypothesized that $\Nu$ of ECS which admit classical Malkus scaling must always exceed $\Nu$ of turbulent convection.
-Our findings agree; $\Nu$ of MSTE exceed 2D and 3D DNS. 
-This might be due to the chaotic transitions among unstable periodic orbits outlined by \cite{Yalniz, Cvitanovic} inhibiting heat flux. 
-We might also anticipate the existence of similar equilibria, having smaller $\Nu$ and occupying neighboring nodes in the Markov chain whose long-term behavior agrees with DNS.
+If we generalize this notion to include quasilinear equilibria, our findings agree; MSTE have larger $\Nu$ than 2D and 3D DNS.
+This might be due to the chaotic transitions, among the unstable periodic orbits outlined by \cite{Yalniz, Cvitanovic}, inhibiting heat flux. 
+We might also anticipate the existence of similar equilibria, having smaller $\Nu$ and occupying complementary nodes in the Markov chain whose long-term behavior agrees with DNS.
 
@@
 This investigation is partially motivated by the prospect of decreasing DNS times by employing MSTE initial conditions. 
-Conventionally, (\ref{EQ:motion1}) - (\ref{EQ:motion3}) are solved via DNS with the linear initial conditions
+Conventionally, (\ref{EQ:motion1})--(\ref{EQ:motion3}) are solved via DNS with the linear initial conditions
 \begin{align}
@@
 \end{equation}
-Consequently, MSTE initial conditions do not reduce the simulation time required to achieve a statistically steady state--rather, they increase it considerably.
-This suggests the MSTE background state perspective is partially flawed, since an appropriate background state would approximate $\langle|\mathbf{u}|^2 \rangle_{\mathcal{D}}$ with more fidelity.
+Consequently, MSTE initial conditions do not reduce the simulation time required to achieve a statistically steady state -- instead they increase it considerably.
+This suggests the MSTE background state perspective is partially flawed, as an appropriate background state would approximate $\langle|\mathbf{u}|^2 \rangle_{\mathcal{D}}$ with more fidelity.
 % \begin{figure}
@@
         \includegraphics[width=3.4in]{sim_eq_ke.png}
-        \caption{Average kinetic energies of the same simulations performed in Figure \ref{fig:nu_sim} ($Ra = 10^8$). 
-        The combination of eigenfunctions which give thermal equilibrium have significantly more kinetic energy than the statistically steady state. 
+        \caption{Average kinetic energies are reported for the simulations performed in Figure \ref{fig:nu_sim} at $Ra = 10^8$. 
+        The combination of eigenfunctions associated with MSTE have significantly more kinetic energy than the statistically steady state. 
         Kinetic equilibrium is achieved according to the viscous timescale $t_{\nu} \sim \sqrt{Ra / Pr}$.}
@@
 In general, the reduced model we study in this paper can be perceived as a unique way to describe Rayleigh–Bénard convection. 
-Solutions to the quasilinear problem retain several key features that are ubiquitous in experiments and simulations: power-law $\Nu$ scaling, convective cell structures, and minimum length-scale approximations \cite{Malkus_1954}.
-They also exhibit unique and unexpected features: gradient-reversal/dips in temperature profiles, kinetic exaggeration, and greater $\Nu$ than other time-invariant solutions. 
+To compute MSTE, we construct a marginally-stable mean temperature profile and develop the quasilinear model via independent time-scales.
+Solutions retain several key features that are ubiquitous in experiments and simulations: $\Nu \sim Ra^{1/3}$ scaling, large-scale convective cell structures, and agreement with classical minimum length-scale approximations \cite{Malkus_1954}.
+They also exhibit unique and unexpected features: mean temperature gradient-reversals/dips, kinetic exaggeration, and greater $\Nu$ than other time-invariant solutions. 
 We obtain indistinguishable solutions despite initializing with various mean temperature profiles $\bar{T}(z, 0)$. 
 Thus solutions might be unique, but we cannot demonstrate this rigorously.
+
+Simulations performed with MSTE initial conditions do not undergo an initial convective transient period,
 

### 2021-04-15 publication_materials/ms_rbc.tex
rev2bi

@@
     Plotting on a log-log scale, we find that $\delta$ and $Ra$ obey a power-law relationship.
-We also demonstrate that $Ra^{1/3}\delta$ is approximately constant with respect to $Ra$, implying $Ra \propto  \delta^{-3}$ which remains consistent with \cite{Malkus_1954}}
+We also demonstrate that $Ra^{1/3}\delta$ is approximately constant with respect to $Ra$ which is consistent with \cite{Malkus_1954, Wen}}
     \label{fig:bl_ra}
@@
 
-Simulations performed with MSTE initial conditions do not undergo an initial convective transient period,
+% Simulations performed with MSTE initial conditions do not undergo an initial convective transient period,
 

### 2021-04-15 publication_materials/ms_rbc.tex

@@
 \begin{abstract}
-Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important properties remain elusive -- particularly in the large Rayleigh number regime.
-In this investigation, we derive and solve a quasilinear form of the Boussinesq Rayleigh-B\'enard equations. 
-Eigenfunction amplitudes are obtained by requiring marginal-stability. We obtain symmetric thermally-equilibrated solutions and analyze their properties. 
-Solutions to the quasilinear problem differ from statistically-steady 2-dimensional Rayleigh-Be\'nard convection simulation data, having thinner boundary layers and larger Nusselt numbers $\Nu$ which scale like $\Nu \sim Ra^{1/3}$.
-We initialize 2-dimensional simulations with solutions to the quasilinear problem; they do not undergo a convective transient period and are kinetically exaggerated.
+Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important properties remain elusive---particularly in the large Rayleigh number regime.
+In this investigation, we derive and solve a quasilinear form of the Rayleigh-Benard problem by representing the perturbations in terms of marginally stable eigenmodes.
+The amplitude of each eigenmode is determined by requiring that the background state maintains marginal stability.
+The background temperature profile evolves due to the advective flux of each eigenmode, as well as diffusion.
+The entire calculation is one-dimensional, and can be run on a workstation.
+We find the background temperature field evolves to an equilibrium state, where the advective flux from the marginally-stable eigenmodes and the diffusive flux sum to a constant.
+These marginally-stable thermal equilibria are exact solutions of the quasilinear equations.
+The mean temperature profile has thinner boundary layers and larger Nusselt numbers than thermally-equilibrated 2D and 3D simulations of the full nonlinear equations.
+We find the Nusselt number scales like $\Nu \sim Ra^{1/3}$.
+When initializing a 2D simulation with a marginally-stable thermal equilibrium, we find the simulation does not exhibit the initial burst of turbulence typical of simulations initialized with the conductive background state plus noise.
+Although the $\Nu$ quickly equilibrates in these simulations, the kinetic energy evolves on a viscous timescale as domain-filling flywheel flows viscously attenuate.
 \end{abstract}

### 2021-04-15 publication_materials/ms_rbc.tex
migration stash

--- 2021-04-15 publication_materials/ms_rbc.tex
@@
 \usepackage{amsmath}
+\usepackage{longtable}
 \usepackage{gensymb}
@@
 \usepackage{nonfloat}
+% \usepackage{multicol}
 % \usepackage{afterpage}
@@
 
-For various $Ra$ and fixed $Pr = 1$, we seek symmetric marginally-stable thermal equilibria (MSTE), thereby satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}). 
+For various $Ra$ and fixed $Pr = 1$, we seek marginally-stable thermal equilibria (MSTE) satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}). 
 We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:model} as well as the IVP (\ref{EQ:T0_IVP}) by representing each field with a dealiased Chebyshev polynomial basis.
@@
 Such definitions are not mutually exclusive, but in general we can assume that MSTE and ECS are not steady with respect to their counterparts' problems.
-For this investigation, we calculate solutions for $Ra$ in the range $10^5 - 10^9$. 
-Their mean temperatures $\bar{T}$ are symmetric about $z = 0$ by construction.
+We compute symmetric MSTE for $Ra$ in the range $10^5 - 10^9$.
 
@@
 
-The most resilient and unexpected feature of MSTE temperature profiles are the pronounced dips adjacent to the boundary layers. 
-These dips appear in every solution, regardless of $Ra$. 
-Physically, they correspond to thin layers in which the mean temperature gradient reverses, contradicting an important hypothesis of \cite{Malkus_1954}. 
-This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure \ref{fig:flux}. 
-We don't understand the source of these dips, but similar temperature gradient reversals were reported by \cite{chini_cells} along the midlines of 2-dimensional convective cellular solutions at $Ra \sim 10^6$.
-
 \begin{figure*}
@@
 \end{figure*}
+
+The most resilient and unexpected feature of MSTE temperature profiles are the pronounced dips adjacent to the boundary layers. 
+These dips appear in every solution, regardless of $Ra$. 
+Physically, they correspond to thin layers in which the mean temperature gradient reverses, contradicting an important hypothesis of \cite{Malkus_1954}. 
+This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure \ref{fig:flux}. 
+We don't understand the source of these dips, but similar temperature gradient reversals were reported by \cite{chini_cells} along the midlines of 2-dimensional convective cellular solutions at $Ra \sim 10^6$.
 
@@
 
-The Nusselt number, which measures convective performance, is given by
-\begin{equation}
-  \Nu = 1 + \frac{A^2}{\mathcal{P}} \langle w'T' \rangle_x.
-\end{equation}
+The Nusselt number, which measures convective performance, reduces to
+\begin{equation*}
+    \Nu = \frac{\langle A^2 \langle w'T' \rangle_x - \mathcal{P}\frac{\partial \bar{T}}{\partial z} \rangle_z}{\langle- \mathcal{P}\frac{\partial \bar{T}}{\partial z} \rangle_z}.
+\end{equation*}
 There is no general consensus surrounding the scaling behavior of $\Nu$ for high $Ra$ systems, which are of particular importance in astrophysical systems.
@@
 \begin{align}
-    T(x, z)\big|_{t=0} &= 0.5 - z \\
-    \mathbf{u}(x, z)\big|_{t=0} &= \mathbf{0} \\
-    p(x, z)\big|_{t=0} &= 0.
+    T(x, z)\big|_{t=0} &= 0.5 - z \nonumber \\
+    \mathbf{u}(x, z)\big|_{t=0} &= \mathbf{0} \nonumber \\
+    p(x, z)\big|_{t=0} &= 0 \label{EQ:linear_ic}.
 \end{align}
@@
     \mathbf{u}(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A_n \text{ Re} \Big[\Big( U_n (z) \hat{x} + W_n(z) \hat{z} \Big) e^{ik_{x_n}x} \Big] \nonumber\\
-    p(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A_n \text{ Re} \Big[P_n (z) e^{ik_{x_n}x}\Big]
+    p(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A_n \text{ Re} \Big[P_n (z) e^{ik_{x_n}x}\Big] \label{EQ:mste_ic}
 \end{align}
-Where $\theta_n(z), U_n(z), W_n(z), P_n(z); \, A_n; $ and $k_{x_n}$ refer to the complex eigenfunctions, amplitude, and wavenumber at the $n$th marginal mode respectively. 
+where $\theta_n(z), U_n(z), W_n(z), P_n(z); \, A_n; $ and $k_{x_n}$ refer to the complex eigenfunctions, amplitude, and wavenumber at the $n$th marginal mode respectively. 
 The $\sqrt{2}$ factor is necessary for eigenfunction normalization.
+
+\begin{figure}
+    \begin{minipage}{3.4in}
+        \centering
+        \includegraphics[width=3.4in]{sim_eq_nu.png}
+        \caption{Nusselt numbers of simulations performed at $Ra = 10^8$ with the conventional initial conditions (black) and MSTE initial conditions (blue). 
+        MSTE simulations do not undergo a convective-transient period because the characteristic large-scale convective cell structure exists on initialization.}
+        \label{fig:nu_sim}
+    \end{minipage}
+\end{figure}
 
@@
 
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=3.4in]{sim_eq_nu.png}
-%     \caption{Nusselt numbers of simulations performed at $Ra \, = \, 10^8$ with conventional initial conditions (red) and marginally-stable thermally-equilibrated initial conditions (blue).
-Simulations launched with thermally-equilibrated states do not undergo a convective-transient period because the characteristic plume structure exists on initialization.
-This is illustrated by the $Nu$ spike at $t \sim 15$ in the convectional simulation.}
-%     \label{fig:nu_sim}
-% \end{figure}
-The average kinetic energy MSTE is significantly larger than the statistical steady state, as shown Figure \ref{fig:ke_sim}. 
-This is postpones kinetic relaxation because the large-scale flows decay on a viscous time-scale
-\begin{equation}
-    t_{\nu} \sim \sqrt{\frac{Ra}{Pr}}. \nonumber
-\end{equation}
-Consequently, MSTE initial conditions do not reduce the simulation time required to achieve a statistically steady state -- instead they increase it considerably.
-This suggests the MSTE background state perspective is partially flawed, as an appropriate background state would approximate $\langle|\mathbf{u}|^2 \rangle_{\mathcal{D}}$ with more fidelity.
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=3.4in]{sim_eq_ke.png}
-%     \caption{Average kinetic energies of the same simulations performed in Figure \ref{fig:nu_sim} ($Ra = 10^8$).
-The combination of eigenfunctions which give thermal equilibrium have significantly more kinetic energy than the statistically steady state.
-Kinetic equilibrium is achieved according to the viscous timescale $t_{\nu} \sim Pr Ra^{-1/2}$.}
-%     \label{fig:ke_sim}
-% \end{figure}
-\begin{figure}
-    \begin{minipage}{3.4in}
-        \centering
-        \includegraphics[width=3.4in]{sim_eq_nu.png}
-        \caption{Nusselt numbers of simulations performed at $Ra = 10^8$ with the conventional initial conditions (black) and MSTE initial conditions (blue). 
-        MSTE simulations do not undergo a convective-transient period because the characteristic large-scale convective cell structure exists on initialization.}
-        \label{fig:nu_sim}
-    \end{minipage}
-\end{figure}
-
 \begin{figure}
@@
         \caption{Average kinetic energies are reported for the simulations performed in Figure \ref{fig:nu_sim} at $Ra = 10^8$. 
-        The combination of eigenfunctions associated with MSTE have significantly more kinetic energy than the statistically steady state. 
-        Kinetic equilibrium is achieved according to the viscous timescale $t_{\nu} \sim \sqrt{Ra / Pr}$.}
+        The combination of eigenfunctions associated with MSTE have significantly more kinetic energy than the statistically-steady state. 
+        Kinetic equilibrium is achieved according to the viscous time-scale $t_{\nu} \sim \sqrt{Ra / Pr}$.}
         \label{fig:ke_sim}
@@
 \end{figure}
+
+The average kinetic energies of MSTE are significantly larger than those associated with the statistically-steady state, as shown Figure \ref{fig:ke_sim}. 
+This is postpones kinetic relaxation because the large-scale flows decay on a viscous time-scale
+
+\begin{equation}
+    t_{\nu} \sim \sqrt{\frac{Ra}{Pr}}. \nonumber
+\end{equation}
+
+Consequently, MSTE initial conditions do not reduce the simulation time required to achieve a statistically-steady state -- instead they increase it considerably. 
+This suggests the MSTE background state perspective is partially flawed, as an appropriate background state would approximate $\langle|\mathbf{u}|^2 \rangle_{\mathcal{D}}$ with more fidelity.
 
@@
 
-% Simulations performed with MSTE initial conditions do not undergo an initial convective transient period,
+Simulations performed with MSTE initial conditions (\ref{EQ:mste_ic}) do not undergo an early convective transient period, but have faster flows and greater $\Nu$ when compared with DNS. 
+From a dynamical systems perspective, unstable orbits depart from MSTE and approach the global attractor (the compact manifold of states whose weighted-average agrees with experiments) on a viscous time-scale.
+This requires more $CPU-hr$ to achieve relaxation as compared to the conventional linear initial condition (\ref{EQ:linear_ic}).
 
-As previously noted, solving the EVP for statistically steady DNS data yields positive eigenvalues; the system is in a perpetual state of instability. 
+As previously noted, solving the EVP for statistically-steady DNS data yields positive eigenvalues; the system is in a perpetual state of instability. 
 Unstable modes tend to stabilize the system rapidly, creating a negative feedback loop whose average state is linearly unstable. 
@@
 Should the time-scales not be entirely separate, we might anticipate the long-term persistance of moderately unstable modes. 
-This perpetual instability cannot be described by our model independently (we do not know, a priori, how unstable such modes are) but it might prove fruitful to investigate moderately unstable thermal equilibria (MUTE).
+Such an instability cannot be described by our model independently (we do not know, a priori, \textit{how unstable} MUTE should be) but it might prove fruitful to investigate moderately unstable thermal equilibria (MUTE).
 More precisely, instead of traversing the manifold of marginally-stable states toward MSTE, we could consider the manifold of states whose maximum eigenvalue(s) $\omega_{\rm{max}}$ agree with some other stability constraint.
@@
 
+% \begin{multicols}{1}
+\subsection{MSTE Metrics}
+\begin{longtable*}{cccccc}
+    %\begin{tabular}{cccccc}
+    %\hline
+    %\begin{longtable}[c]{@{}*{6}{>{\arraybackslash}p{0.15\linewidth}}@{}}
+    \quad\quad\quad Ra	\quad\quad\quad	&	\quad\quad\quad		Pr	\quad\quad\quad		&	\quad\quad\quad		$k=2\pi/\Gamma$	\quad\quad\quad		&	\quad\quad\quad		$N_x \times N_z$	\quad\quad\quad		&	\quad\quad\quad		Nu	\quad\quad\quad		&	\quad\quad\quad		Re	\quad\quad\quad\\
+    %\hline
+    $10^{13/4}$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.056590	&	1.617336\\
+    $1.9\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.145807	&	2.682155\\
+    $2\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.212037	&	3.317190\\
+    $2.25\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.355410	&	4.550975\\
+    $2.5\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.474455	&	5.537770\\
+    $2.75\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.575599	&	6.391812\\
+    $3\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.663162	&	7.159844\\
+    $10^{14/4}$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.714193	&	7.624400\\
+    $3.5\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.808754	&	8.526064\\
+    $4\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.926775	&	9.740578\\
+    $4.5\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	2.025985	&	10.85141\\
+    $5\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	2.111714	&	11.88534\\
+    $10^{15/4}$	&	1	&	$\pi$	&	128 $\times$ 65	&	2.204811	&	13.09152\\
+    $8\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	2.476330	&	17.05494\\
+    $10^4$	&	1	&	$\pi$	&	128 $\times$ 65	&	2.648664	&	20.07400\\
+    $10^{17/4}$	&	1	&	$\pi$	&	128 $\times$ 65	&	3.122843	&	29.50047\\
+    $10^{18/4}$	&	1	&	$\pi$	&	128 $\times$ 65	&	3.665041	&	42.29585\\
+    $10^{19/4}$	&	1	&	$\pi$	&	128 $\times$ 65	&	4.287042	&	59.56858\\
+    $10^{5}$	&	1	&	$\pi$	&	128 $\times$ 65	&	4.994322	&	82.84462\\
+    $10^{21/4}$	&	1	&	$\pi$	&	128 $\times$ 65	&	5.795869	&	114.2355\\
+    $10^{22/4}$	&	1	&	$\pi$	&	128 $\times$ 97	&	6.703915	&	156.5252\\
+    $10^{23/4}$	&	1	&	$\pi$	&	128 $\times$ 97	&	7.732236	&	213.4031\\
+    $10^{6}$	&	1	&	$\pi$	&	128 $\times$ 97	&	8.896615	&	289.7982\\
+    $10^{25/4}$	&	1	&	$\pi$	&	256 $\times$ 97	&	10.21546	&	392.2837\\
+    $10^{26/4}$	&	1	&	$\pi$	&	256 $\times$ 129	&	11.71065	&	529.6372\\
+    $10^{27/4}$	&	1	&	$\pi$	&	256 $\times$ 129	&	13.40898	&	713.6005\\
+    $10^{7}$	&	1	&	$\pi$	&	512 $\times$ 129	&	15.34493	&	959.9367\\
+    $1.35\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 129	&	16.46456	&	1119.932\\
+    $1.5\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 129	&	16.87881	&	1182.172\\
+    $1.6\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.13944	&	1222.005\\
+    $1.65\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.26636	&	1241.484\\
+    $1.7\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.39216	&	1260.709\\
+    $1.736\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.48282	&	1274.414\\
+    $1.76\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.54351	&	1283.493\\
+    $10^{29/4}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.58987	&	1290.377\\
+    $1.786\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.60946	&	1293.277\\
+    $1.8\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.64500	&	1298.522\\
+    $1.85\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.77160	&	1317.122\\
+    $1.9\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.89693	&	1335.501\\
+    $1.95\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	18.02044	&	1353.657\\
+    $2\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	18.14193	&	1371.593\\
+    $2.4\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	19.04221	&	1507.890\\
+    $2.8\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	19.83413	&	1633.418\\
+    $10^{30/4}$	&	1	&	$\pi$	&	512 $\times$ 193	&	20.47798	&	1739.647\\
+    $4.5\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	22.44036	&	2087.182\\
+    $10^{31/4}$	&	1	&	$\pi$	&	512 $\times$ 193	&	23.76002	&	2340.822\\
+    $10^{8}$	&	1	&	$\pi$	&	768 $\times$ 257	&	27.50669	&	3144.931\\
+    $10^{33/4}$	&	1	&	$\pi$	&	768 $\times$ 257	&	31.81154	&	4220.616\\
+    $2.15\times10^{8}$	&	1	&	$\pi$	&	768 $\times$ 257	&	33.36657	&	4649.541\\
+    $10^{34/4}$	&	1	&	$\pi$	&	768 $\times$ 257	&	36.75427	&	5658.648\\
+    $4.64\times10^{8}$	&	1	&	$\pi$	&	896 $\times$ 321	&	40.44652	&	6875.704\\
+    $10^{35/4}$	&	1	&	$\pi$	&	896 $\times$ 321	&	42.42917	&	7580.057\\
+    $10^{9}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	48.94284	&	10145.79\\
+    $10^{37/4}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	56.42926	&	13571.10\\
+    $2.15\times10^{9}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	59.13988	&	14935.81\\
+    $2.5\times10^{9}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	61.38714	&	16116.94\\
+    $10^{38/4}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	65.06338	&	18145.61\\
+    $10^{153/16}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	67.42466	&	19511.79\\
+    $4\times10^{9}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	68.96487	&	20429.24\\
+    $4.64\times10^{9}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	71.58241	&	22019.93\\
+    $10^{39/4}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	75.09725	&	24262.22\\
+    $10^{10}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	86.68318	&	32430.06\\
+    $10^{41/4}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	100.0909	&	43339.02\\
+    $2\times10^{10}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	103.0738	&	45995.60\\
+    $2.15\times10^{10}$ &	1	&	$\pi$	&	1024 $\times$ 321	&	104.9517	&	47705.08\vspace{0.1in}\\
+    %\hline
+    %  \end{tabular}
+    \caption*{Table S1: Details for numerical solutions with $\Pran=1$ and $\Gamma=2$.  $N_x$ and $N_z$ represent the numbers of Fourier and Chebyshev modes, respectively.}
+    {\label{tab:Gamma2}}
+    \end{longtable*}
+% \end{multicols}
+
 \section*{Acknowledgments}

### 2021-04-15 publication_materials/ms_rbc.tex
merged Daniel's commit

@@
 \begin{abstract}
-Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important properties remain elusive -- particularly in the large Rayleigh number regime.
-In this investigation, we derive and solve a quasilinear form of the Boussinesq Rayleigh-B\'enard equations. 
-Eigenfunction amplitudes are obtained by requiring marginal-stability. We obtain symmetric thermally-equilibrated solutions and analyze their properties. 
-Solutions to the quasilinear problem differ from statistically-steady 2-dimensional Rayleigh-Be\'nard convection simulation data, having thinner boundary layers and larger Nusselt numbers $\Nu$ which scale like $\Nu \sim Ra^{1/3}$.
-We initialize 2-dimensional simulations with solutions to the quasilinear problem; they do not undergo a convective transient period and are kinetically exaggerated.
+    Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important properties remain elusive---particularly in the large Rayleigh number regime.
+    In this investigation, we derive and solve a quasilinear form of the Rayleigh-Benard problem by representing the perturbations in terms of marginally stable eigenmodes.
+    The amplitude of each eigenmode is determined by requiring that the background state maintains marginal stability.
+    The background temperature profile evolves due to the advective flux of each eigenmode, as well as diffusion.
+    The entire calculation is one-dimensional, and can be run on a workstation.
+    We find the background temperature field evolves to an equilibrium state, where the advective flux from the marginally-stable eigenmodes and the diffusive flux sum to a constant.
+    These marginally-stable thermal equilibria are exact solutions of the quasilinear equations.
+    The mean temperature profile has thinner boundary layers and larger Nusselt numbers than thermally-equilibrated 2D and 3D simulations of the full nonlinear equations.
+    We find the Nusselt number scales like $\Nu \sim Ra^{1/3}$.
+    When initializing a 2D simulation with a marginally-stable thermal equilibrium, we find the simulation does not exhibit the initial burst of turbulence typical of simulations initialized with the conductive background state plus noise.
+    Although the $\Nu$ quickly equilibrates in these simulations, the kinetic energy evolves on a viscous timescale as domain-filling flywheel flows viscously attenuate.
 \end{abstract}
@@
 \section{Introduction}
-Rayleigh-B\'enard convection plays a foundational role in large-scale astrophysical and geophysical settings.
-Buoyancy-driven convection regulates heat transfer and often gives way to violently turbulent flows, thereby dominating large-scale behaviors and generating small-scale processes in important systems \cite{Couston}.
-
+Rayleigh-B\'enard convection plays a foundational role in astrophysical and geophysical settings.
+The resulting buoyancy-driven flows regulate heat transfer and generate large-scale vortices \cite{Couston}.
 Aggressive convection, which is associated with large Rayleigh numbers $Ra$, is difficult to simulate. 

### 2021-04-15 plot_flux.py

@@ -65,7 +65,7 @@ def plot_flux(Rayleigh, ax, path, iteration):
         pi_mult3 = str(round(kx3/np.pi, 1))
         pi_mult4 = str(round(kx4/np.pi, 1))
         pi_mult5 = str(round(kx5/np.pi, 1))
-        ax.plot(z, advection1, label = 'Advection ($k_x  = $' + pi_mult1 + '$\pi$)')
+        ax.plot(z, advection1, label = r'$\langle w\' T\' \rangle (k_x  = $' + pi_mult1 + r'$\pi$)')
         ax.plot(z, advection2, label = 'Advection ($k_x  = $' + pi_mult2 + '$\pi$)')
         ax.plot(z, advection3, label = 'Advection ($k_x  = $' + pi_mult3 + '$\pi$)')
         ax.plot(z, advection4, label = 'Advection ($k_x  = $' + pi_mult4 + '$\pi$)')
@@ -131,7 +131,7 @@ plt.tight_layout()
 plt.subplots_adjust(right=1.0)
 # fig.text(0.00, 0.5, 'Flux', ha='center', va='center', rotation='vertical', fontsize=10)
 # plt.ylabel('Flux')
-plt.savefig(root_path + '/pubfigs/flux_sup_n', bbox_inches='tight')
-plt.savefig(root_path + '/publication_materials/flux_sup_n', bbox_inches='tight')
+plt.savefig(root_path + '/pubfigs/flux_sup_n1', bbox_inches='tight')
+# plt.savefig(root_path + '/publication_materials/flux_sup_n', bbox_inches='tight')
 
 

### 2021-04-15 publication_settings.py

@@ -21,12 +21,11 @@ params = {#'backend': 'eps',
           'font.size':8,
           'font.serif': 'stix',
           'mathtext.fontset' : 'stix',
-        #   'text.usetex' : True,
           'legend.fontsize': 8,
           'legend.markerscale': 1,
           'xtick.labelsize': 10,
           'ytick.labelsize': 10,
-#          'text.usetex': True,
+          # 'text.usetex': True,
           'figure.figsize': fig_size,
           'figure.dpi': 600,
           'lines.markersize':3,

### 2021-04-16 publication_materials/ms_rbc.tex
Intro

@@
 The resulting buoyancy-driven flows regulate heat transfer and generate large-scale vortices \cite{Couston}.
-Aggressive convection, which is associated with large Rayleigh numbers $Ra$, is difficult to simulate. 
+Turbulent convection, which is associated with large Rayleigh numbers $Ra$, is difficult to simulate. 
 State of the art simulations performed by \cite{Zhu_2018} have reached $Ra \sim 10^{14}$ but estimates for stars are $Ra \sim 10^{20}$ \cite{Ossendrijver}. 
+\note{put in a number for earth's interior?}
 The scaling behavior of the Nusselt number $\Nu \sim Ra^{\beta}$ in the asymptotic ultimate regime is of particular interest.
@@
 
-Reduced models are particularly useful in this context because they allow us to study the problem with relatively low expense. 
-Much of the published work on this topic relates to unstable exact coherent states (ECS) \cite{Waleffe, Sondak, Wen, chini_cells}. 
-Simulations and analysis performed by \cite{Yalniz, Cvitanovic} suggest that chaotic simulation trajectories can be represented by a Markov chain whose long-term behavior is given by the time-weighted-average of a finite set of unstable equilibria.
+Absent solid evidence from direct numerical simulation, other methods have been developed to try to infer large-$Ra$ behavior or otherwise gain insight.
+In the presence of other physical effects (e.g., rotation, magnetic fields), one can sometimes derive an asymptotically consistent set of reduced equations \cite{Julien2007, Julien2012}.
+Reduced models are potentially useful in this context because they may allow us to study the problem with less expensive computations.
+Another approach relates to unstable exact coherent states (ECS) \cite{Waleffe, Sondak, Wen, chini_cells}. 
+Simulations and analysis performed by \cite{Yalniz, Cvitanovic} suggest that chaotic simulation trajectories can be represented by a Markov chain whose long-term behavior is given by the time-weighted-average over a finite set of unstable equilibria.
 Should that be the case, it is crucial that we discover and classify such equilibria.
 
+Others have turned to studying quasilinear systems.
+The quasilinear approximation starts with a decomposition of all variables into a background and perturbations about this background.
+The approximation is to neglect the influence of nonlinear interactions between the perturbations on the perturbations themselves \cite{marston2016}.
+This renders the perturbation equations linear.
+Although the quasilinear approximation greatly simplifies the problem, an additional condition must be imposed to determine the amplitude of the perturbations.
 In \cite{Beaume_2015}, researchers compute ECS in parallel shear flows by deriving and solving a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments. 
-This is realized by defining a mean state which, hypothetically, evolves on a slow time-scale. 
-Marginal stability is required at each successive timestep to constrain the perturbation amplitudes. 
-A similar strategy is employed by \cite{michel_chini_2019}, where an analytic expression for the first-order perturbations' amplitude is found by deriving a solvability condition of the second-order perturbations and integrating over the domain spatially.
-We seek to solve the Boussinesq Rayleigh–Bénard convection equations using an analogous strategy. 
-The application of this procedure yields time-invariant solutions to the quasilinear problem with a range of expected and unexpected features.
+They assume the background velocity evolves on a slow timescale, and to determine the perturbation amplitudes they require marginal stability at each timestep.
+A similar strategy is employed by \cite{michel_chini_2019} to studying acoustic streaming.
+In that work, an analytic expression for the first-order perturbation's amplitude is found by deriving a solvability condition.
+
+In this paper we solve the Rayleigh-B\'{e}nard convection problem using an analogous strategy.
+In section~\ref{sec:model} we recall the underlying equations, and in section~\ref{sec:evolution} we describe how we evolve the background temperature profile while maintaining marginal stability.
+Section~\ref{sec:properties} describes the properties of the marginally-stable thermal equilibria, in particular how the Nusselt number and characteristic wavenumbers vary with the Rayleigh number.
+Finally, we describe the results of simulations initialized with marginally-stable thermal equilibria in section~\ref{sec:sims}, and conclude in section~\ref{sec:Discussion}.
 
@@
 
-\section{Perturbation Evolution}
+\section{Perturbation Evolution}\label{sec:evolution}
 Solving the linearized system (\ref{EQ:linear1})--(\ref{EQ:linear3}) does not yield $A(t)$. 
@@
 
-\section{Simulations with Thermally Equilibrated Initial Conditions}
+\section{Simulations with Thermally Equilibrated Initial Conditions}\label{sec:sims}
 This investigation is partially motivated by the prospect of decreasing DNS times by employing MSTE initial conditions. 

### 2021-04-16 publication_materials/ms_rbc.tex
rev2c

--- 2021-04-15 publication_materials/ms_rbc.tex
@@
 
-\newcommand{\eq}[1]{eq.~(\ref{#1})}
-\newcommand{\eqs}[2]{eqs.~(\ref{#1})~\&~(\ref{#2})}
-\newcommand{\eqss}[2]{eqs.~(\ref{#1})--(\ref{#2})}
+\newcommand{\eq}[1]{Eq.~(\ref{#1})}
+\newcommand{\eqs}[2]{Eqs.~(\ref{#1})~\&~(\ref{#2})}
+\newcommand{\eqss}[2]{Eqs.~(\ref{#1})--(\ref{#2})}
 
@@
     The mean temperature profile has thinner boundary layers and larger Nusselt numbers than thermally-equilibrated 2D and 3D simulations of the full nonlinear equations.
-    We find the Nusselt number scales like $\Nu \sim Ra^{1/3}$.
+    We find the Nusselt number scales like $\Nu \sim\Ra^{1/3}$.
     When initializing a 2D simulation with a marginally-stable thermal equilibrium, we find the simulation does not exhibit the initial burst of turbulence typical of simulations initialized with the conductive background state plus noise.
@@
 The resulting buoyancy-driven flows regulate heat transfer and generate large-scale vortices \cite{Couston}.
-Aggressive convection, which is associated with large Rayleigh numbers $Ra$, is difficult to simulate. 
-State of the art simulations performed by \cite{Zhu_2018} have reached $Ra \sim 10^{14}$ but estimates for stars are $Ra \sim 10^{20}$ \cite{Ossendrijver}. 
-The scaling behavior of the Nusselt number $\Nu \sim Ra^{\beta}$ in the asymptotic ultimate regime is of particular interest.
+Aggressive convection, which is associated with large Rayleigh numbers $\Ra$, is difficult to simulate. 
+State of the art simulations performed by \cite{Zhu_2018} have reached $\Ra \sim 10^{14}$ but estimates for stars are $\Ra \sim 10^{20}$ \cite{Ossendrijver}. 
+The scaling behavior of the Nusselt number $\Nu \sim\Ra^{\beta}$ in the asymptotic ultimate regime $\Ra \to \infty$ is of particular interest.
 There exists a substantial body of work pertaining to this specific topic with no general consensus \cite{Malkus_1954, Howard_1966, Kraichnan, Spiegel, Castaing, Grossman, Ahlers}.
@@
 Much of the published work on this topic relates to unstable exact coherent states (ECS) \cite{Waleffe, Sondak, Wen, chini_cells}. 
-Simulations and analysis performed by \cite{Yalniz, Cvitanovic} suggest that chaotic simulation trajectories can be represented by a Markov chain whose long-term behavior is given by the time-weighted-average of a finite set of unstable equilibria.
-Should that be the case, it is crucial that we discover and classify such equilibria.
+Simulations and analysis performed by \cite{Yalniz, Cvitanovic} suggest that chaotic solutions to the full nonlinear problem can be represented by a Markov chain of unstable equilibria.
+Should that be the case, it is crucial that we discover and classify such states.
 
-In \cite{Beaume_2015}, researchers compute ECS in parallel shear flows by deriving and solving a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments. 
+In \cite{Beaume_2015}, researchers compute ECS in parallel shear flows by deriving and solving a reduced form of the Navier-Stokes equations via multi-scale asymptotic arguments. 
 This is realized by defining a mean state which, hypothetically, evolves on a slow time-scale. 
@@
 We begin with the non-dimensionalized Boussinesq approximation for Rayleigh-Bénard Convection. 
-The domain $\mathcal{D}$ is 2-dimensional rectangular and horizontally periodic with spatial dimensions $0 < x < 4$ and $-1/2 < z < 1/2$. 
+The domain $\mathcal{D}$ is 2D rectangular and horizontally periodic with spatial dimensions $0 < x < 4$ and $-1/2 < z < 1/2$. 
 The fluid of interest is constrained between two flat boundaries at $z = -1/2$ and $z = 1/2$ with fixed temperatures $1$ and $0$ respectively. 
@@
 For completeness, we specify a final boundary condition $p = p_0$ at $z = \pm 1/2$. 
-Any system of this form can be characterized by its dimensionless Rayleigh number $Ra = \frac{g\alpha L^3 \Delta T}{\nu \kappa}$ and Prandtl number $Pr = \frac{\nu}{\kappa}$, where $g, \, \alpha, \, L, \, \Delta T, \nu, \kappa$ are the gravitational acceleration, coefficient of thermal expansion, domain height, opposed temperature difference, kinematic viscosity, and thermal diffusivity respectively.
+Any system of this form can be characterized by its dimensionless Rayleigh number $\Ra = \frac{g\alpha L^3 \Delta T}{\nu \kappa}$ and Prandtl number $\Pr = \frac{\nu}{\kappa}$, where $g, \, \alpha, \, L, \, \Delta T, \nu, \kappa$ are the gravitational acceleration, coefficient of thermal expansion, domain height, opposed temperature difference, kinematic viscosity, and thermal diffusivity respectively.
 For convenience, we define
 \begin{equation}
-\mathcal{R} = \sqrt{\frac{Pr}{Ra}}, \qquad \mathcal{P} = \frac{1}{\sqrt{Pr Ra}}.
+\mathcal{R} = \sqrt{\frac{\Pr}{\Ra}}, \qquad \mathcal{P} = \frac{1}{\sqrt{\Pr \Ra}}.
 \end{equation}
@@
 thereby alleviating any ambiguity in $A(t)$. 
-Substituting (\ref{EQ:reynolds_dc_T}) into (\ref{EQ:motion3}) and taking the horizontal-average reduces the system to a simple initial value problem (IVP) for $\bar{T}$
+Substituting \eq{EQ:reynolds_dc_T} into \eq{EQ:motion3} and taking the horizontal-average reduces the system to a simple initial value problem (IVP) for $\bar{T}$
 \begin{equation}
@@
 
-To solve (\ref{EQ:T0_IVP}) numerically, we need the perturbations and their associated amplitude function $A(t)$. 
+To solve \eq{EQ:T0_IVP} numerically, we need the perturbations and their associated amplitude function $A(t)$. 
 The former is obtained by solving the linearized system. 
-Substituting (\ref{EQ:reynolds_dc_u})--(\ref{EQ:reynolds_dc_p}) into (\ref{EQ:motion1})--(\ref{EQ:motion3}) and subtracting (\ref{EQ:T0_IVP}) from the resulting temperature equation gives
+Substituting \eqss{EQ:reynolds_dc_u}{EQ:reynolds_dc_p} into \eqss{EQ:motion1}{EQ:motion3} and subtracting \eq{EQ:T0_IVP} from the resulting temperature equation gives
 \begin{align}
@@
 
-In his groundbreaking report \cite{Rayleigh_1916}, Lord Rayleigh observed that (\ref{EQ:linear1}) and (\ref{EQ:linear3}) can be manipulated into a separable form with generalized solutions
+In his famous report \cite{Rayleigh_1916}, Lord Rayleigh observed that \eqs{EQ:linear1}{EQ:linear3} can be manipulated into a separable form with generalized solutions
 \begin{align}
@@
 A complete linear stability analysis requires solution over the full spectrum of wavenumbers. 
-The prototypical case is used to demonstrate that the critical Rayleigh number $Ra_c = 1708$ when $\frac{\partial \bar{T}}{\partial z} = -1$.
+The prototypical case is used to demonstrate that the critical Rayleigh number $\Ra_c = 1708$ when $\frac{\partial \bar{T}}{\partial z} = -1$.
 
@@
 \section{Perturbation Evolution}
-Solving the linearized system (\ref{EQ:linear1})--(\ref{EQ:linear3}) does not yield $A(t)$. 
+Solving the linearized system \eqss{EQ:linear1}{EQ:linear3} does not yield $A(t)$. 
 To evolve $\bar{T}$, we assume the perturbations and mean quantities evolve according to different time-scales, as in \cite{michel_chini_2019}.
@@
 
-For various $Ra$ and fixed $Pr = 1$, we seek marginally-stable thermal equilibria (MSTE) satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}). 
-We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:model} as well as the IVP (\ref{EQ:T0_IVP}) by representing each field with a dealiased Chebyshev polynomial basis.
-The necessary number of basis functions varies, as eigenfunctions and temperature profiles associated with large $Ra$ admit increasingly small-scale features. 
+For various $\Ra$ and fixed $\Pr = 1$, we seek marginally stable thermal equilibria (MSTE) satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to \eq{EQ:T0_IVP}. 
+We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:model} as well as the IVP \eq{EQ:T0_IVP} by representing each field with a dealiased Chebyshev polynomial basis.
+The necessary number of basis functions varies, as eigenfunctions and temperature profiles associated with large $\Ra$ admit increasingly small-scale features. 
 We supplement \texttt{Dedalus} with the \texttt{Eigentools} package to compute $\langle w' T' \rangle_x$.
 
-At $t = 0$, we begin with a marginally-stable initial profile $\bar{T}(z, 0)$ whose construction is outlined in \ref{sec:initial_profile}. 
-At some arbitrary time $t = t_0$, we seek to evolve $\bar{T}(z, t_0)$ into a new marginally-stable profile $\bar{T}(z, t_0 + \Delta t)$ according to (\ref{EQ:T0_IVP}) via forward-Euler. 
+At $t = 0$, we begin with a marginally-stable initial profile $\bar{T}(z, 0)$ whose construction is outlined in Section \ref{sec:initial_profile}. 
+At some arbitrary time $t = t_0$, we seek to evolve $\bar{T}(z, t_0)$ into a new marginally stable profile $\bar{T}(z, t_0 + \Delta t)$ according to \eq{EQ:T0_IVP} via forward-Euler. 
 This generally involves a unique and unknown value $A^2(t_0) > 0$. 
@@
     \includegraphics[width=3.4in]{EV_spectrum_ol.png}
-    \caption{Eigenvalue spectra for $Ra = 10^5$. The spectrum of an ``initial" marginally-stable mean temperature profile $\bar{T}(z, t_0)$ has a maximum eigenvalue of 0. 
+    \caption{Eigenvalue spectra for $\Ra = 10^5$. The spectrum of an ``initial" marginally-stable mean temperature profile $\bar{T}(z, t_0)$ has a maximum eigenvalue of 0. 
     Given a small fixed timestep $\Delta t$, diffusion destabilizes the system, increasing its eigenvalues. 
@@
 These quantities correspond to the light blue and green points at $k_x = \pi$ in Figure \ref{fig:iteration_spectra}).
-$\bar{T}(z, t)$ is then evolved according to (\ref{EQ:T0_IVP}) and another eigenvalue solve is performed. 
+$\bar{T}(z, t)$ is then evolved according to \eq{EQ:T0_IVP} and another eigenvalue solve is performed. 
 Given a fixed timestep $\Delta t$, we assume the dominant eigenvalue can be described by a continuous function $\omega_{\rm{max}} (A^2)$ which is locally differentiable. 
@@
 
-\subsection{Treatment of multiple marginally-stable modes} \label{sec:multiple_modes}
+\subsection{Treatment of Multiple marginally-stable Modes} \label{sec:multiple_modes}
 In most cases, we eventually encounter eigenvalue spectra with multiple simultaneously marginal modes.
 If ignored, we are forced to reduce the timestep and allow the modes to alternate.
-Instead, we generalize the advective term in (\ref{EQ:T0_IVP}) to accommodate $N$ simultaneously marginal modes
+Instead, we generalize the advective term in \eq{EQ:T0_IVP} to accommodate $N$ simultaneously marginal modes
 \begin{equation}
@@
 \section{Properties of Thermally Equilibrated States}\label{sec:properties}
-MSTE are fixed points of the quasilinear form derived in section \ref{sec:model}, differing from ECS in that ECS are fixed points of the full nonlinear problem (\ref{EQ:motion1})--(\ref{EQ:motion3}). 
+MSTE are fixed points of the quasilinear form derived in section \ref{sec:model}, differing from ECS in that ECS are fixed points of the full nonlinear problem \eqss{EQ:motion1}{EQ:motion3}. 
 Such definitions are not mutually exclusive, but in general we can assume that MSTE and ECS are not steady with respect to their counterparts' problems.
-We compute symmetric MSTE for $Ra$ in the range $10^5 - 10^9$.
+We compute symmetric MSTE for $\Ra$ in the range $10^5 - 10^9$.
 
@@
     \includegraphics[width=3.4in]{T_profs_na.png}
-    \caption{Mean temperature profiles $\bar{T}$ for $Ra = 10^8$. 
-    The initial profile is given by (\ref{EQ:T0}). 
-    The MSTE curve refers to the mean temperature profile of the marginally-stable thermally-equilibrated state. 
-    The DNS profile is obtained by performing a 2-dimensional nonlinear simulation of (\ref{EQ:motion1})--(\ref{EQ:motion3}) with \texttt{Dedalus} until thermal and kinetic relaxation. 
-    The DNS temperature data are horizontally- and time-averaged. 
-    The initial, MSTE, and DNS profiles have increasingly relaxed boundary regions (respectively). 
+    \caption{Mean temperature profiles $\bar{T}$ for $\Ra = 10^8$. 
+    The initial profile is given by \eq{EQ:T0}. 
+    MSTE refers to the mean temperature profile of the marginally-stable thermally-equilibrated state. 
+    DNS was obtained by performing a 2D nonlinear simulation of \eqss{EQ:motion1}{EQ:motion3} with \texttt{Dedalus} until thermal and kinetic relaxation. 
+    DNS temperature data are horizontally- and time-averaged. 
+    The initial, MSTE, and DNS profiles have increasingly relaxed boundary regions respectively. 
     The MSTE profile exhibits prominent dips, nested alongside the boundary regions. 
-    The source of this feature is not well understood, but similar temperature gradient reversal regions were found by \cite{chini_cells} along the midlines of 2-dimensional convective cellular solutions at $Ra \sim 10^6$.}
+    The source of this feature is not well understood, but similar temperature gradient reversal regions were found by \cite{chini_cells} along the midlines of 2D convective cellular solutions at $\Ra \sim 10^6$.}
     \label{fig:T0_profiles}
@@
 
-Figure \ref{fig:T0_profiles} gives temperature profiles for $Ra = 10^8$ where the initial profile, given by (\ref{EQ:T0}), is employed at iteration 0; the MSTE profile corresponds to the thermally relaxed state; and the DNS (direct numerical simulations) profile is obtained by solving (\ref{EQ:motion1})--(\ref{EQ:motion3}) with \texttt{Dedalus}, followed by horizontal- and time- averaging.
+Figure \ref{fig:T0_profiles} gives temperature profiles for $\Ra = 10^8$ where the initial profile, whose construction is outlined in , is employed at iteration 0; the MSTE profile corresponds to the thermally relaxed state; and the DNS (direct numerical simulations) profile is obtained by solving \eqss{EQ:motion1}{EQ:motion3} with \texttt{Dedalus}, followed by horizontal- and time- averaging.
 The DNS curve is more diffuse than the MSTE curve, which in turn, is more diffuse than the initial curve. 
@@
     \end{tabular}
-    \caption{Heat fluxes (left) and eigenvalue spectra (right) of equilibrated states $Ra = 2 \times 10^5$ (top) and $Ra = 10^9$ (bottom). 
+    \caption{Heat fluxes (left) and eigenvalue spectra (right) of equilibrated states $\Ra = 2 \times 10^5$ (top) and $\Ra = 10^9$ (bottom). 
     Advection profiles belong to marginally-stable modes. 
-    For low $Ra$, a single mode with $k_x = 1.5\pi$ is sufficient to oppose boundary layer diffusion and facilitate heat flux throughout the bulk of the domain. 
-    For large $Ra$, high-wavenumber modes contribute pronounced small-scale advection profiles which tightly hug the thin boundary layers. 
+    For low $\Ra$, a single mode with $k_x = 1.5\pi$ is sufficient to oppose boundary layer diffusion and facilitate heat flux throughout the bulk of the domain. 
+    For large $\Ra$, high-wavenumber modes contribute pronounced small-scale advection profiles which tightly hug the thin boundary layers. 
     A combination of of progressively wider advection profiles is necessary to transition to the $k_x = 1.5\pi$ mode.}
@@
 The most resilient and unexpected feature of MSTE temperature profiles are the pronounced dips adjacent to the boundary layers. 
-These dips appear in every solution, regardless of $Ra$. 
+These dips appear in every solution, regardless of $\Ra$. 
 Physically, they correspond to thin layers in which the mean temperature gradient reverses, contradicting an important hypothesis of \cite{Malkus_1954}. 
 This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure \ref{fig:flux}. 
-We don't understand the source of these dips, but similar temperature gradient reversals were reported by \cite{chini_cells} along the midlines of 2-dimensional convective cellular solutions at $Ra \sim 10^6$.
+We don't understand the source of these dips, but similar temperature gradient reversals were reported by \cite{chini_cells} along the midlines of 2D convective cellular solutions at $\Ra \sim 10^6$.
 
-Equilibrated states exhibit distinct behaviors for large and small $Ra$. 
-This contrast is illustrated in Figure \ref{fig:flux}, where we give heat flux profiles and eigenvalue spectra for two cases: $Ra = 2 \times 10^5$ and $Ra = 10^9$. 
-For $Ra = 2 \times 10^5$, there is a single presumed local maximum in the eigenvalue spectrum, whose adjacent modes' advection profiles occupy the bulk of the domain. 
+Equilibrated states exhibit distinct behaviors for large and small $\Ra$. 
+This contrast is illustrated in Figure \ref{fig:flux}, where we give heat flux profiles and eigenvalue spectra for two cases: $\Ra = 2 \times 10^5$ and $\Ra = 10^9$. 
+For $\Ra = 2 \times 10^5$, there is a single presumed local maximum in the eigenvalue spectrum, whose adjacent modes' advection profiles occupy the bulk of the domain. 
 These states have relaxed boundary layers which gradually subside as advection becomes the dominant flux component. 
-Such transitional regions do not appear for $Ra = 10^9$, where the shift from diffusion to advection is sharp, requiring pronounced, small-scale advection profiles belonging to modes in the third local maxima pair of the eigenvalue spectrum.
+Such transitional regions do not appear for $\Ra = 10^9$, where the shift from diffusion to advection is sharp, requiring pronounced, small-scale advection profiles belonging to modes in the third local maxima pair of the eigenvalue spectrum.
 Traversing towards the midline of the domain, we see increasingly thicker advection profiles corresponding to modes in the second local maxima pair, eventually culminating in the dominant $k_x = 1.5\pi$ mode.
@@
     Markers are color-coded according to their adjacent local maxima index in the eigenvalue spectrum. 
-    For example, the spectrum corresponding to $Ra = 10^5$ has adjacent marginal wavenumbers $k_x = \pi, \, 1.5\pi$. 
-    The $Ra = 10^9$ spectrum, shown in lower right corner of Figure \ref{fig:flux}, has three groups of maxima, with a single marginal mode in the first group ($k_x = 1.5\pi$), two adjacent marginal modes in the second group ($k_x = 6\pi, \, 6.5\pi$), and two adjacent marginal modes in the third group ($k_x = 23.5\pi, \, 24\pi$).
-    The largest wavenumbers of the green branch obey a power-law relationship with $Ra$}
+    For example, the spectrum corresponding to $\Ra = 10^5$ has adjacent marginal wavenumbers $k_x = \pi, \, 1.5\pi$. 
+    The $\Ra = 10^9$ spectrum, shown in lower right corner of Figure \ref{fig:flux}, has three groups of maxima, with a single marginal mode in the first group ($k_x = 1.5\pi$), two adjacent marginal modes in the second group ($k_x = 6\pi, \, 6.5\pi$), and two adjacent marginal modes in the third group ($k_x = 23.5\pi, \, 24\pi$).
+    The largest wavenumbers of the green branch obey a power-law relationship with $\Ra$}
     \label{fig:kx_marginals}
@@
 
-Thermally equilibrated states with large $Ra$ tend to have diverse combinations of marginal modes. 
+Thermally equilibrated states with large $\Ra$ tend to have diverse combinations of marginal modes. 
 In every case, the $k_x = 1.5\pi$ mode is included and is often unaccompanied by adjacent modes. 
@@
 In these cases we infer the existence of a local maximum eigenvalue between the two adjacent marginally-stable modes. 
-For $Ra \geq 10^6$, a second branch of marginal modes is introduced as shown in light green, obeying some power-law with respect to $Ra$. 
+For $\Ra \geq 10^6$, a second branch of marginal modes is introduced as shown in light green, obeying some power-law with respect to $\Ra$. 
 The introduction of this largest branch is likely required to oppose the diffusion of the thinning boundary layers. 
-For $Ra \geq 10^8$, a third branch appears (shown in light blue), splitting the widening gap between the other branches. 
+For $\Ra \geq 10^8$, a third branch appears (shown in light blue), splitting the widening gap between the other branches. 
 This development is associated with moderately thick advection profiles, filling a niche in the total flux by uniting the sharp profiles of the largest branch and those of the bulk-domain-oriented smallest branch.
@@
     \includegraphics[width=3.4in]{del_kx_inv.png}
-    \caption{For $Ra \geq 10^6$, the maximum marginally-stable wavenumbers (corresponding to the green X markers in Figure \ref{fig:kx_marginals}) are inversely related to the boundary layer heights $\delta$.
+    \caption{For $\Ra \geq 10^6$, the maximum marginally-stable wavenumbers (corresponding to the green X markers in Figure \ref{fig:kx_marginals}) are inversely related to the boundary layer heights $\delta$.
     $(\max \{ k_x \})^{-1}$ gives a minimum $x$ length scale for the perturbations, and consequently, the advection. 
@@
     This is illustrated in the lower left corner of Figure \ref{fig:flux}, where the advection profile for $k_x = 24\pi$ is tightly flanked by the surrounding boundary layer. 
-    This suggests that the minimum $x$ and $z$ length scales obey some constant ratio over various $Ra$.}
+    This suggests that the minimum $x$ and $z$ length scales obey some constant ratio over various $\Ra$.}
     \label{fig:del_inv}
@@
 We define the interior boundary layer threshold as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$.
-In Figure \ref{fig:del_inv}, we illustrate the constant ratio between these two quantities for various $Ra$.
+In Figure \ref{fig:del_inv}, we illustrate the constant ratio between these two quantities for various $\Ra$.
 The quasilinear model cannot describe small-scale behaviors in either direction.
@@
     We define the threshold of each boundary layer as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, corresponding to the local extrema of the equilibrated curve in Figure \ref{fig:T0_profiles}.
-    Plotting on a log-log scale, we find that $\delta$ and $Ra$ obey a power-law relationship.
-We also demonstrate that $Ra^{1/3}\delta$ is approximately constant with respect to $Ra$ which is consistent with \cite{Malkus_1954, Wen}}
+    Plotting on a log-log scale, we find that $\delta$ and $\Ra$ obey a power-law relationship.
+We also demonstrate that $\Ra^{1/3}\delta$ is approximately constant with respect to $\Ra$ which is consistent with \cite{Malkus_1954, Wen}}
     \label{fig:bl_ra}
@@
 In general, MSTE can be characterized by their boundary layer height, from which, the rest of their properties follow.
-In Figure \ref{fig:bl_ra}, we illustrate the scaling behavior of the boundary layer height $\delta = Ra^{-1/3}$.
+In Figure \ref{fig:bl_ra}, we illustrate the scaling behavior of the boundary layer height $\delta = \Ra^{-1/3}$.
 This is consistent with Malkus' classical marginal-stability theory, a scaling argument which perceives the boundary regions as subdomains which are themselves marginally-stable \cite{Malkus_1954}.
@@
     \caption{Nusselt numbers are shown for MSTE, aspect-ratio-optimized ``steady rolls'' ECS \cite{Wen}, as well as statistically-steady 2D and 3D DNS \cite{Johnston, Scheel_2016}.
-    All datasets obey power-law relationships, with the MSTE and ECS admitting classical scaling $\Nu \sim Ra^{1/3}$. 
+    All datasets obey power-law relationships, with the MSTE and ECS admitting classical scaling $\Nu \sim\Ra^{1/3}$. 
     MSTE have greater $\Nu$ than the ECS, which in turn, have greater $\Nu$ than the DNS. This can be explained by the contrasting boundary layer geometries shown in Figure \ref{fig:T0_profiles}.}%
@@
 \end{equation*}
-There is no general consensus surrounding the scaling behavior of $\Nu$ for high $Ra$ systems, which are of particular importance in astrophysical systems.
+There is no general consensus surrounding the scaling behavior of $\Nu$ for high $\Ra$ systems, which are of particular importance in astrophysical systems.
 In Figure \ref{fig:nu_vs_ra} we report $\Nu$ for MSTE, ``steady rolls" ECS \cite{Wen}, and DNS \cite{Scheel_2016, Johnston}.
-All states obey $\Nu \sim Ra^{\beta}$ with classical scaling $\beta = 1/3$ in the ECS and MSTE. 
+All states obey $\Nu \sim\Ra^{\beta}$ with classical scaling $\beta = 1/3$ in the ECS and MSTE. 
 \cite{Wen} hypothesized that $\Nu$ of ECS which admit classical Malkus scaling must always exceed $\Nu$ of turbulent convection.
@@
 This investigation is partially motivated by the prospect of decreasing DNS times by employing MSTE initial conditions. 
-Conventionally, (\ref{EQ:motion1})--(\ref{EQ:motion3}) are solved via DNS with the linear initial conditions
+Conventionally, \eqss{EQ:motion1}{EQ:motion3} are solved via DNS with the linear initial conditions
 \begin{align}
@@
         \includegraphics[width=3.4in]{sim_eq_nu.png}
-        \caption{Nusselt numbers of simulations performed at $Ra = 10^8$ with the conventional initial conditions (black) and MSTE initial conditions (blue). 
+        \caption{Nusselt numbers of simulations performed at $\Ra = 10^8$ with the conventional initial conditions (black) and MSTE initial conditions (blue). 
         MSTE simulations do not undergo a convective-transient period because the characteristic large-scale convective cell structure exists on initialization.}
@@
 Simulation of this transitional period is prohibitive \cite{Anders_AE}. 
-For high $Ra$ experiments, researchers often ``bootstrap" data by initializing simulations with the results of similar $Ra$ runs \cite{Verzicco, Johnston}. 
+For high $\Ra$ experiments, researchers often ``bootstrap" data by initializing simulations with the results of similar $\Ra$ runs \cite{Verzicco, Johnston}. 
 MSTE can be perceived as a set of initial conditions, designed for avoiding the simulation of transitional high Reynolds number flows.
 
-MSTE are laminar, lacking the small-scale structures associated with moderate to high $Ra$ experiments. 
+MSTE are laminar, lacking the small-scale structures associated with moderate to high $\Ra$ experiments. 
 The absence of chaotic dynamics is an apparent consequence of the quasilinear assumptions. 
@@
         \includegraphics[width=3.4in]{sim_eq_ke.png}
-        \caption{Average kinetic energies are reported for the simulations performed in Figure \ref{fig:nu_sim} at $Ra = 10^8$. 
+        \caption{Average kinetic energies are reported for the simulations performed in Figure \ref{fig:nu_sim} at $\Ra = 10^8$. 
         The combination of eigenfunctions associated with MSTE have significantly more kinetic energy than the statistically-steady state. 
-        Kinetic equilibrium is achieved according to the viscous time-scale $t_{\nu} \sim \sqrt{Ra / Pr}$.}
+        Kinetic equilibrium is achieved according to the viscous time-scale $t_{\nu} \sim \sqrt{\Ra / \Pr}$.}
         \label{fig:ke_sim}
@@
 \begin{equation}
-    t_{\nu} \sim \sqrt{\frac{Ra}{Pr}}. \nonumber
+    t_{\nu} \sim \sqrt{\frac{\Ra}{\Pr}}. \nonumber
 \end{equation}
@@
 To compute MSTE, we construct a marginally-stable mean temperature profile and develop the quasilinear model via independent time-scales.
-Solutions retain several key features that are ubiquitous in experiments and simulations: $\Nu \sim Ra^{1/3}$ scaling, large-scale convective cell structures, and agreement with classical minimum length-scale approximations \cite{Malkus_1954}.
+Solutions retain several key features that are ubiquitous in experiments and simulations: $\Nu \sim\Ra^{1/3}$ scaling, large-scale convective cell structures, and agreement with classical minimum length-scale approximations \cite{Malkus_1954}.
 They also exhibit unique and unexpected features: mean temperature gradient-reversals/dips, kinetic exaggeration, and greater $\Nu$ than other time-invariant solutions. 
@@
 
-Simulations performed with MSTE initial conditions (\ref{EQ:mste_ic}) do not undergo an early convective transient period, but have faster flows and greater $\Nu$ when compared with DNS. 
+Simulations performed with MSTE initial conditions \eq{EQ:mste_ic} do not undergo an early convective transient period, but have faster flows and greater $\Nu$ when compared with DNS. 
 From a dynamical systems perspective, unstable orbits depart from MSTE and approach the global attractor (the compact manifold of states whose weighted-average agrees with experiments) on a viscous time-scale.
-This requires more $CPU-hr$ to achieve relaxation as compared to the conventional linear initial condition (\ref{EQ:linear_ic}).
+This requires more CPU-hr to achieve relaxation as compared to the conventional linear initial condition \eq{EQ:linear_ic}.
 
@@
 More precisely, instead of traversing the manifold of marginally-stable states toward MSTE, we could consider the manifold of states whose maximum eigenvalue(s) $\omega_{\rm{max}}$ agree with some other stability constraint.
-Note that under this definition, 2-dimensional ECS are themselves MUTE, because they are thermally-equilibrated and generally unstable, though they need not satisfy the quasilinear form.
+Note that under this definition, ECS are themselves MUTE, because they are thermally-equilibrated and generally unstable, though they need not satisfy the quasilinear form.
 
-We cannot use our reduced quasilinear model to predict $\Nu \sim Ra^{\beta}$ for large $Ra$ without some complementary stability constraint. 
+We cannot use our reduced quasilinear model to predict $\Nu \sim\Ra^{\beta}$ for large $\Ra$ without some complementary stability constraint. 
 The eigenvalues of DNS data might provide an informative stability constraint (we could find MUTE and compare them with DNS data), but this would be self-defeating in general. 
@@
 Under the marginal-stability constraint, we found that MSTE exhibit classical Malkus scaling, having marginally-stable boundary layers with $\beta = 1/3$.
-We could instead require that the eigenvalues of MUTE agree with the eigenvalues of the analytic 1-dimensional boundary layer predictions of \cite{Shishkina, Zhang_20} (which remain in development), allowing us to refine and expand these estimates into 2-dimensional MUTE.
+We could instead require that the eigenvalues of MUTE agree with the eigenvalues of the analytic 1D boundary layer predictions of \cite{Shishkina, Zhang_20} (which remain in development), allowing us to refine and expand these estimates into 2D MUTE.
 Accessible MUTE states would not rely on DNS, satisfying only the quasilinear problem and stability constraint. 
-Such MUTE ought to agree with DNS data more precisely than MSTE, ideally having slower flows. 
-This is reasonable to expect, since accurate boundary layer approximations and DNS data should have similar stability characteristics. 
+They ought to agree with DNS data more than MSTE, ideally having slower flows This is reasonable to expect because accurate boundary layer approximations and DNS data should have similar stability characteristics.
 By definition, MUTE are unstable and would therefore admit more diffuse boundary layer structures, requiring smaller $A^2(t)$ (less advection) to satisfy the stability constraint and thereby reducing $\Nu$, $\langle |\mathbf{u}|^2 \rangle_{\mathcal{D}}$ and possibly $\beta$.
@@
 It should be noted that when experimenting with various initial profiles $(\tanh, \rm{erf}, \rm{etc.})$, we obtain indistinguishable equilibrated states, implying that solutions may be unique. 
-An example of (\ref{EQ:T0}) is given by the blue curve in Figure \ref{fig:T0_profiles}.
+An example of \eq{EQ:T0} is given by the blue curve in Figure \ref{fig:T0_profiles}.
 

### 2021-04-16 plot_flux.py

@@ -127,7 +127,7 @@ iteration2 = 12638
 
 plot_flux(ra1, axs[0], path1, iteration1)
 plot_flux(ra2, axs[1], path2, iteration2)
-plt.tight_layout()
+# plt.tight_layout()
 plt.subplots_adjust(right=1.0)
 # fig.text(0.00, 0.5, 'Flux', ha='center', va='center', rotation='vertical', fontsize=10)
 # plt.ylabel('Flux')

### 2021-04-16 publication_settings.py

@@ -25,7 +25,7 @@ params = {#'backend': 'eps',
           'legend.markerscale': 1,
           'xtick.labelsize': 10,
           'ytick.labelsize': 10,
-          # 'text.usetex': True,
+          'text.usetex': True,
           'figure.figsize': fig_size,
           'figure.dpi': 600,
           'lines.markersize':3,

### 2021-04-16 publication_materials/ms_rbc.tex
Sections 2 & 3. I changed the location of the amplitude so that the perturbations are more in line with other authors.

--- 2021-04-16 publication_materials/ms_rbc.tex
@@
 We begin with the non-dimensionalized Boussinesq approximation for Rayleigh-Bénard Convection. 
-The domain $\mathcal{D}$ is 2-dimensional rectangular and horizontally periodic with spatial dimensions $0 < x < 4$ and $-1/2 < z < 1/2$. 
+The domain $\mathcal{D}$ is 2-dimensional, rectangular, and horizontally periodic with spatial dimensions $0 < x < 4$ and $-1/2 < z < 1/2$. 
 The fluid of interest is constrained between two flat boundaries at $z = -1/2$ and $z = 1/2$ with fixed temperatures $1$ and $0$ respectively. 
-At both boundaries we specify impenetrable, no-slip conditions, such that the velocity $\mathbf{u} = u \hat{x} + w \hat{z} = \mathbf{0}$ at $z = \pm 1/2$. 
+At both boundaries we specify impenetrable, no-slip conditions, such that the velocity $\mathbf{u} = u \hat{x} + w \hat{z} = \mathbf{0}$ at $z = \pm 1/2$, where $\hat{x}, \hat{z}$ are the unit vectors in the $x$ and $z$ directions.
 The equations of motion are then given by
@@
 \begin{align}
-    \mathbf{u}(x, z, t) &= A(t) \mathbf{u'}(x, z, t) \label{EQ:reynolds_dc_u}\\
-    &= A(t) u'(x, z, t)\hat{x} + A(t) w'(x, z, t)\hat{z} \\
-    T(x, z, t) &= \bar{T}(z, t) + A(t) T'(x, z, t) \label{EQ:reynolds_dc_T}\\
-    p(x, z, t) &= \bar{p}(z, t) + A(t) p'(x, z, t) \label{EQ:reynolds_dc_p}.
+    \mathbf{u}(x, z, t) &= \mathbf{u'}(x, z, t) \label{EQ:reynolds_dc_u}\\
+    &= u'(x, z, t)\hat{x} + w'(x, z, t)\hat{z} \\
+    T(x, z, t) &= \bar{T}(z, t) + T'(x, z, t) \label{EQ:reynolds_dc_T}\\
+    p(x, z, t) &= \bar{p}(z, t) +  p'(x, z, t) \label{EQ:reynolds_dc_p}.
 \end{align}
-where $A(t)$ is some unknown real amplitude and the mean-velocity components vanish due to incompressibility and symmetry. Perturbations must admit no horizontal-average
+where the mean-velocity components vanish due to incompressibility and symmetry. Perturbations are defined to have no horizontal-average
 \begin{equation}
@@
 \end{equation}
-Assuming the existance of nontrivial solutions, we also fix the volume-average over the entire domain
-\begin{equation}
-  \langle T'^2 \rangle_{\mathcal{D}} = 1
-\end{equation}
-thereby alleviating any ambiguity in $A(t)$. 
+%Assuming the existance of nontrivial solutions, we also fix the volume-average over the entire domain
+%\begin{equation}
+%  \langle T'^2 \rangle_{\mathcal{D}} = 1
+%\end{equation}
+%thereby alleviating any ambiguity in $A(t)$. 
 Substituting (\ref{EQ:reynolds_dc_T}) into (\ref{EQ:motion3}) and taking the horizontal-average reduces the system to a simple initial value problem (IVP) for $\bar{T}$
 \begin{equation}
-  \frac{\partial \bar{T}}{\partial t} + A^2 \langle w'T' \rangle_x = \mathcal{P}  \frac{\partial^2 \bar{T}}{\partial z^2}, \label{EQ:T0_IVP}
+  \frac{\partial \bar{T}}{\partial t} + \langle w'T' \rangle_x = \mathcal{P}  \frac{\partial^2 \bar{T}}{\partial z^2}, \label{EQ:T0_IVP}
 \end{equation}
+\note{need to define $\langle \cdot \rangle_x$}
 with associated boundary conditions $\bar{T}(-1/2, t) = 1$ and $\bar{T}(1/2, t) = 0$.
@@
 
-To solve (\ref{EQ:T0_IVP}) numerically, we need the perturbations and their associated amplitude function $A(t)$. 
-The former is obtained by solving the linearized system.
-Substituting (\ref{EQ:reynolds_dc_u})--(\ref{EQ:reynolds_dc_p}) into (\ref{EQ:motion1})--(\ref{EQ:motion3}) and subtracting (\ref{EQ:T0_IVP}) from the resulting temperature equation gives
+To solve (\ref{EQ:T0_IVP}) numerically, we need an expression for the perturbation so we can calculate the advective heat flux.
+Here we will make the quasilinear approximation, dropping the $\vec{u}'\vec{\cdot}\vec{\nabla}\vec{u}'$ and $\vec{u}'\vec{\cdot}\vec{\nabla}T'$ terms from the evolution equations for the perturbations.
+Substituting (\ref{EQ:reynolds_dc_u})--(\ref{EQ:reynolds_dc_p}) into (\ref{EQ:motion1})--(\ref{EQ:motion3}) and subtracting (\ref{EQ:T0_IVP}) from the resulting temperature equation, and linearizing gives
 \begin{align}
@@
 \end{equation}
+This is now a linear problem in $\vec{u}'$ and $T'$ which can be solved as an eigenvalue problem.
 
-In his groundbreaking report \cite{Rayleigh_1916}, Lord Rayleigh observed that (\ref{EQ:linear1}) and (\ref{EQ:linear3}) can be manipulated into a separable form with generalized solutions
+In his groundbreaking report \cite{Rayleigh_1916}, Lord Rayleigh observed that (\ref{EQ:linear1})--(\ref{EQ:linear3}) can be manipulated into a separable form with generalized solutions
 \begin{align}
-    w'(x, z, t) &= W(z) \, e^{i(k_xx-st)} \label{EQ:normal_modes1}\\ 
-    u'(x, z, t) &= U(z) \, e^{i(k_xx-st)} \label{EQ:normal_modes2}\\ 
-    T'(x, z, t) &= \theta(z) \, e^{i(k_xx-st)} \label{EQ:normal_modes3}\\ 
-    p'(x, z, t) &= P(z) \, e^{i(k_xx-st)}\label{EQ:normal_modes4}
+    w'(x, z, t) &= A\, \Re\left[W(z) \, e^{i(k_xx-st)}\right], \label{EQ:normal_modes1}\\ 
+    u'(x, z, t) &= A\, \Re\left[U(z) \, e^{i(k_xx-st)}\right], \label{EQ:normal_modes2}\\ 
+    T'(x, z, t) &= A\, \Re\left[\theta(z) \, e^{i(k_xx-st)}\right], \label{EQ:normal_modes3}\\ 
+    p'(x, z, t) &= A\, \Re\left[P(z) \, e^{i(k_xx-st)}\right], \label{EQ:normal_modes4}
 \end{align}
-where $s = \sigma + i\omega$ and $k_x$ is constrained, by periodicity, to the countably infinite set (spectrum) of wavenumbers
+where $A$ is the (undetermined) mode amplitude, $s = \sigma + i\omega$ and $k_x$ is constrained, by periodicity, to the countably infinite set (spectrum) of wavenumbers
 \begin{align}
-    k_x \in \big\{\frac{n\pi}{2} \, \big| \, n \in \mathbb{N}\big\}.
+    k_x \in \left\{\frac{n\pi}{2} \, \big| \, n \in \mathbb{N}\right\}.
 \end{align}
+We normalize the eigenmodes to have
+\begin{equation}
+  \langle |\theta|^2 \rangle_{\mathcal{D}} = 1.
+\end{equation}
 For each $k_x$, we can assess the stability of the perturbations by solving for the eigenvalue $s$, whose imaginary component $\omega$ plays the role of an exponential growth rate. 
-Solution yields a finite set of eigenvalues, among which, that with maximum $\omega$ is assumed to be dominant. 
+Solution yields a finite set of eigenvalues, among which, that with maximum $\omega$ is assumed to be dominant \note{I don't understand this sentence}. 
 Positive eigenvalues indicate that the system is unstable to small disturbances of wavenumber $k_x$, while negative eigenvalues indicate stability. 
@@
 
-At some arbitrary time $t_0$, the forcing term $\langle w'T' \rangle_x$ can be found by solving an eigenvalue problem (EVP) which itself involves $\frac{\partial \bar{T}}{\partial z}$.
+To calculate the advective heat flux in equation~\ref{EQ:T0_IVP}, we can sum $\langle w'T' \rangle_x$ from each horizontal wavenumber individually.
+In this way, the heat flux from the perturbations influence the evolution of $\bar{T}$.
+But the evolution of $\bar{T}$ also influences the perturbations, as equation~\ref{EQ:linear3} depends on $\partial_z \bar{T}$.
+Thus, the mean temperature and perturbations fields are coupled.
 
 \section{Perturbation Evolution}\label{sec:evolution}
-Solving the linearized system (\ref{EQ:linear1})--(\ref{EQ:linear3}) does not yield $A(t)$. 
-To evolve $\bar{T}$, we assume the perturbations and mean quantities evolve according to different time-scales, as in \cite{michel_chini_2019}.
+The linearized system (\ref{EQ:linear1})--(\ref{EQ:linear3}) cannot determine the amplitude of the eigenmodes, $A$.
+However, the advective heat flux is proportional to $A^2$, so we need to specify the amplitude in order to solve equation~\ref{EQ:T0_IVP}.
+To evolve $\bar{T}$, we assume the perturbations evolve on a much faster timescale than the mean temperature, as in \cite{michel_chini_2019}.
 Stable modes decay away rapidly. 
-Unstable modes will not persist on the slow time-scale because the advective term $\langle w'T' \rangle_x$ tends to stabilize $\bar{T}$, thereby creating a negative feedback loop.
-Only marginally stable modes can traverse this hypothetical time-scale separation.
-Therefore the amplitude function $A(t)$ must satisfy
+Unstable modes will not persist on the slow timescale because the advective term $\langle w'T' \rangle_x$ tends to stabilize $\bar{T}$, thereby creating a negative feedback loop.
+Only marginally stable modes can be maintained on the slow timescale.
+Therefore the amplitude $A$ must satisfy
 \begin{equation}
@@
 For various $Ra$ and fixed $Pr = 1$, we seek marginally-stable thermal equilibria (MSTE) satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}). 
-We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:model} as well as the IVP (\ref{EQ:T0_IVP}) by representing each field with a dealiased Chebyshev polynomial basis.
+We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:model} as well as the IVP (\ref{EQ:T0_IVP}) by representing each field with Chebyshev polynomials \note{cite dedalus}.
+We use the 3/2 dealiasing rule to calculate the advective heat flux.
 The necessary number of basis functions varies, as eigenfunctions and temperature profiles associated with large $Ra$ admit increasingly small-scale features. 
-We supplement \texttt{Dedalus} with the \texttt{Eigentools} package to compute $\langle w' T' \rangle_x$.
+We use the \texttt{Eigentools} package to manipulate the eigenfunctions and calculate the advective heat flux $\langle w' T' \rangle_x$ \note{cite eigentools}.
 
-At $t = 0$, we begin with a marginally-stable initial profile $\bar{T}(z, 0)$ whose construction is outlined in \ref{sec:initial_profile}. 
-At some arbitrary time $t = t_0$, we seek to evolve $\bar{T}(z, t_0)$ into a new marginally-stable profile $\bar{T}(z, t_0 + \Delta t)$ according to (\ref{EQ:T0_IVP}) via forward-Euler. 
-This generally involves a unique and unknown value $A^2(t_0) > 0$. 
-Our method of finding $A^2(t_0)$ is best illustrated through example.
+At $t = 0$, we begin with a marginally-stable initial profile $\bar{T}(z, 0)$ whose construction is outlined in appendix~\ref{sec:initial_profile}. 
+At some arbitrary time $t = t_0$, we seek to evolve $\bar{T}(z, t_0)$ into a new marginally-stable profile $\bar{T}(z, t_0 + \Delta t)$ according to (\ref{EQ:T0_IVP}), using backward Euler to evolve the diffusion term and forward Euler to evolve the advection term.
+This requires us to determine the amplitude of the eigenfunction $A$.
+We will now illustrate our method of finding $A^2$ through an example.
 
@@
     Advection tends to stabilize the system, decreasing its eigenvalues. 
-    It follows that there exists some proportion $A^2(t_0)$ of these two terms which yields a new marginally-stable mean temperature profile $\bar{T}(z, t_0 + \Delta t)$, whose spectrum is ``evolved".}
+    We find the eigenfunction amplitude $A^2$ such that the combination of diffusion and advection yields a new, ``evolved,'' marginally-stable mean temperature profile $\bar{T}(z, t_0 + \Delta t)$.}
     \label{fig:iteration_spectra} 
@@
 
-An iteration is performed as follows: diffusing a marginally-stable temperature profile $\bar{T}(z, t_0)$ tends to increase its eigenvalues. 
-Ignoring the diffusive term and evolving according to advection tends the stabilize the system. The appropriate amplitude $A^2(t_0)$ can then be approximated by
+An iteration is performed as follows.
+Consider a marginally-stable temperature profile $\bar{T}(z, t_0)$.
+By definition, its maximum eigenvalue is 0.
+Diffusing $\bar{T}(z, t_0)$ tends to increase its eigenvalues.
+Ignoring the diffusive term and evolving according to advection tends the stabilize the system.
+The appropriate amplitude $A^2$ can then be approximated by
 \begin{equation}
-    A^2(t_0) \sim -\frac{\omega_{\rm{diff}}}{\omega_{\rm{adv}}}
+    A^2 \approx -\frac{\omega_{\rm{diff}}}{\omega_{\rm{adv}}}
 \end{equation}
 where $\omega_{\rm{diff}}$ and $\omega_{\rm{adv}}$ refer to the diffused and advected eigenvalues of the initially marginal mode.
-These quantities correspond to the light blue and green points at $k_x = \pi$ in Figure \ref{fig:iteration_spectra}).
+We illustrate these trends in Figure~\ref{fig:iteration_spectra}. 
 $\bar{T}(z, t)$ is then evolved according to (\ref{EQ:T0_IVP}) and another eigenvalue solve is performed. 
 Given a fixed timestep $\Delta t$, we assume the dominant eigenvalue can be described by a continuous function $\omega_{\rm{max}} (A^2)$ which is locally differentiable. 
-We use Newton's method to find an amplitude which satisfies our marginal stability tolerance criterion. 
-The dominant mode is not fixed; an iteration can facilitate the transfer of marginal-stability from one mode to another. 
+We use Newton's method to find an amplitude which satisfies our marginal stability tolerance criterion \note{what is the criterion?}.
+Crucially, we do not assume the $k_x$ of the marginally-stable is fixed.
 In section \ref{sec:multiple_modes} we specify procedures for the treatment of multiple simultaneously marginal modes.
@@
 In most cases, we eventually encounter eigenvalue spectra with multiple simultaneously marginal modes.
-If ignored, we are forced to reduce the timestep and allow the modes to alternate.
+If ignored, we are forced to reduce the timestep and allow the modes to alternate which is marginally stable.
 Instead, we generalize the advective term in (\ref{EQ:T0_IVP}) to accommodate $N$ simultaneously marginal modes
 \begin{equation}
-    A^2 \langle w' T' \rangle_x = \sum_{n = 1}^{N} A^2_{n} \langle w' T' \rangle_{x, \, n}
+    \langle w' T' \rangle_x = \sum_{n = 1}^{N} 4 A_n^2 \int \, \Re\left[ W_n \theta_n^* \right] \,dz
 \end{equation}
-where  $\langle w' T' \rangle_{x, \, n}$ is composed of perturbations associated with $k_x = \frac{n\pi}{2}$. 
+where $W_n$ and $\theta_n$ are the eigenmodes associated with $k_x = \frac{n\pi}{2}$. 
 There are now $N$ amplitudes to solve for and $N$ eigenvalues to keep marginally-stable. 
 In general, we expect a function $\mathbf{\omega} \, : \, \mathbb{R}^N \to  \mathbb{R}^N$ to have isolated roots (should they exist). 
-We employ Broyden's method for root-finding in multi-dimensional functions whose derivatives are not explicitly known. 
+We employ Broyden's method for root-finding in multi-dimensional functions whose derivatives are not explicitly known \note{Should describe this better...
+don't you calculate the Jacobian, invert it, and then refine the roots using Broyden's method?}.
 Difficulty arises when transitioning between different numbers of marginal modes.
-Here we rely on $A^2 > 0$ by asserting that a mode which is \textit{close enough} to marginal-stability can be included in the iteration provided that its respective amplitude is positive. 
+\note{Should describe what happens when you add modes}
+Here we rely on $A^2 > 0$ by asserting that a mode which is \textit{close enough} to marginal-stability can be included in the iteration provided that its respective amplitude is positive \note{this is a description of how you remove modes, but it is a bit confusing}.
 Should we converge upon a negative amplitude, that mode is discarded and the iteration is repeated. 
-In general we find that no other obvious course of action yields equilibria.
+%In general we find that no other obvious course of action yields equilibria.
 
@@
 
-\section*{Appendix}
-\subsection{Initial buoyancy profile} \label{sec:initial_profile}
+\appendix
+
+\section{Initial buoyancy profile} \label{sec:initial_profile}
 We initialize the thermal-equilibration algorithm with \cite{Shishkina}'s analytical thermal boundary layer equation for turbulent Rayleigh-B\'enard convection, given by 
@@
 % \begin{multicols}{1}
-\subsection{MSTE Metrics}
+\section{MSTE Metrics}
 \begin{longtable*}{cccccc}

### 2021-04-16 publication_materials/ms_rbc.tex
misc. changes to be merged

@@
 
-\newcommand{\eq}[1]{eq.~(\ref{#1})}
-\newcommand{\eqs}[2]{eqs.~(\ref{#1})~\&~(\ref{#2})}
-\newcommand{\eqss}[2]{eqs.~(\ref{#1})--(\ref{#2})}
+\newcommand{\eq}[1]{(\ref{#1})}
+\newcommand{\eqs}[2]{(\ref{#1})~\&~(\ref{#2})}
+\newcommand{\eqss}[2]{(\ref{#1})--(\ref{#2})}
 
@@
 %thereby alleviating any ambiguity in $A(t)$. 
-Substituting (\ref{EQ:reynolds_dc_T}) into (\ref{EQ:motion3}) and taking the horizontal-average reduces the system to a simple initial value problem (IVP) for $\bar{T}$
+Substituting \eq{EQ:reynolds_dc_T} into \eq{EQ:motion3} and taking the horizontal-average reduces the system to a simple initial value problem (IVP) for $\bar{T}$
 \begin{equation}
@@
 \end{equation}
-\note{need to define $\langle \cdot \rangle_x$}
 with associated boundary conditions $\bar{T}(-1/2, t) = 1$ and $\bar{T}(1/2, t) = 0$.
@@
 
-To solve (\ref{EQ:T0_IVP}) numerically, we need an expression for the perturbation so we can calculate the advective heat flux.
+To solve \eq{EQ:T0_IVP} numerically, we need an expression for the perturbation so we can calculate the advective heat flux.
 Here we will make the quasilinear approximation, dropping the $\vec{u}'\vec{\cdot}\vec{\nabla}\vec{u}'$ and $\vec{u}'\vec{\cdot}\vec{\nabla}T'$ terms from the evolution equations for the perturbations.
-Substituting (\ref{EQ:reynolds_dc_u})--(\ref{EQ:reynolds_dc_p}) into (\ref{EQ:motion1})--(\ref{EQ:motion3}) and subtracting (\ref{EQ:T0_IVP}) from the resulting temperature equation, and linearizing gives
+Substituting \eqss{EQ:reynolds_dc_u}{EQ:reynolds_dc_p} into \eqss{EQ:motion1}{EQ:motion3} and subtracting \eq{EQ:T0_IVP} from the resulting temperature equation, and linearizing gives
 \begin{align}
@@
 
-In his groundbreaking report \cite{Rayleigh_1916}, Lord Rayleigh observed that (\ref{EQ:linear1})--(\ref{EQ:linear3}) can be manipulated into a separable form with generalized solutions
+In his groundbreaking report \cite{Rayleigh_1916}, Lord Rayleigh observed that \eqss{EQ:linear1}{EQ:linear3} can be manipulated into a separable form with generalized solutions
 \begin{align}
@@
 \section{Perturbation Evolution}\label{sec:evolution}
-The linearized system (\ref{EQ:linear1})--(\ref{EQ:linear3}) cannot determine the amplitude of the eigenmodes, $A$.
+The linearized system \eqss{EQ:linear1}{EQ:linear3} cannot determine the amplitude of the eigenmodes, $A$.
 However, the advective heat flux is proportional to $A^2$, so we need to specify the amplitude in order to solve equation~\ref{EQ:T0_IVP}.
@@
 
-For various $Ra$ and fixed $Pr = 1$, we seek marginally-stable thermal equilibria (MSTE) satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}). 
-We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:model} as well as the IVP (\ref{EQ:T0_IVP}) by representing each field with Chebyshev polynomials \note{cite dedalus}.
+For various $\Ra$ and fixed $\Pr = 1$, we seek marginally-stable thermal equilibria (MSTE) satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to . 
+We employ the \texttt{Dedalus} pseudo-spectral python framework \cite{Dedalus_2020} to solve the EVP outlined in Section \ref{sec:model} as well as the IVP \eq{EQ:T0_IVP} by representing each field with Chebyshev polynomials.
 We use the 3/2 dealiasing rule to calculate the advective heat flux.
-The necessary number of basis functions varies, as eigenfunctions and temperature profiles associated with large $Ra$ admit increasingly small-scale features. 
+The necessary number of basis functions varies, as eigenfunctions and temperature profiles associated with large $\Ra$ admit increasingly small-scale features. 
 We use the \texttt{Eigentools} package to manipulate the eigenfunctions and calculate the advective heat flux $\langle w' T' \rangle_x$ \note{cite eigentools}.
@@
 At $t = 0$, we begin with a marginally-stable initial profile $\bar{T}(z, 0)$ whose construction is outlined in appendix~\ref{sec:initial_profile}. 
-At some arbitrary time $t = t_0$, we seek to evolve $\bar{T}(z, t_0)$ into a new marginally-stable profile $\bar{T}(z, t_0 + \Delta t)$ according to (\ref{EQ:T0_IVP}), using backward Euler to evolve the diffusion term and forward Euler to evolve the advection term.
+At some arbitrary time $t = t_0$, we seek to evolve $\bar{T}(z, t_0)$ into a new marginally-stable profile $\bar{T}(z, t_0 + \Delta t)$ according to \eq{EQ:T0_IVP}, using backward Euler to evolve the diffusion term and forward Euler to evolve the advection term.
 This requires us to determine the amplitude of the eigenfunction $A$.
@@
 We illustrate these trends in Figure~\ref{fig:iteration_spectra}. 
-$\bar{T}(z, t)$ is then evolved according to (\ref{EQ:T0_IVP}) and another eigenvalue solve is performed. 
+$\bar{T}(z, t)$ is then evolved according to \eq{EQ:T0_IVP} and another eigenvalue solve is performed. 
 Given a fixed timestep $\Delta t$, we assume the dominant eigenvalue can be described by a continuous function $\omega_{\rm{max}} (A^2)$ which is locally differentiable. 
@@
 If ignored, we are forced to reduce the timestep and allow the modes to alternate which is marginally stable.
-Instead, we generalize the advective term in (\ref{EQ:T0_IVP}) to accommodate $N$ simultaneously marginal modes
+Instead, we generalize the advective term in \eq{EQ:T0_IVP} to accommodate $N$ simultaneously marginal modes
 \begin{equation}
@@
 \section{Properties of Thermally Equilibrated States}\label{sec:properties}
-MSTE are fixed points of the quasilinear form derived in section \ref{sec:model}, differing from ECS in that ECS are fixed points of the full nonlinear problem (\ref{EQ:motion1})--(\ref{EQ:motion3}). 
+MSTE are fixed points of the quasilinear form derived in section \ref{sec:model}, differing from ECS in that ECS are fixed points of the full nonlinear problem \eqss{EQ:motion1}{EQ:motion3}. 
 Such definitions are not mutually exclusive, but in general we can assume that MSTE and ECS are not steady with respect to their counterparts' problems.
@@
 
-Figure \ref{fig:T0_profiles} gives temperature profiles for $Ra = 10^8$ where the initial profile, given by (\ref{EQ:T0}), is employed at iteration 0; the MSTE profile corresponds to the thermally relaxed state; and the DNS (direct numerical simulations) profile is obtained by solving (\ref{EQ:motion1})--(\ref{EQ:motion3}) with \texttt{Dedalus}, followed by horizontal- and time- averaging.
+Figure \ref{fig:T0_profiles} gives temperature profiles for $\Ra = 10^8$ where the initial profile, whose construction is outlined in \ref{sec:initial_profile}, is employed at iteration 0. 
+DNS (direct numerical simulations) are performed by solving \eqss{EQ:motion1}{EQ:motion3} with \texttt{Dedalus}, followed by horizontal- and time- averaging. 
 The DNS curve is more diffuse than the MSTE curve, which in turn, is more diffuse than the initial curve. 
@@
 The most resilient and unexpected feature of MSTE temperature profiles are the pronounced dips adjacent to the boundary layers. 
-These dips appear in every solution, regardless of $Ra$. 
+These dips appear in every solution, regardless of $\Ra$. 
 Physically, they correspond to thin layers in which the mean temperature gradient reverses, contradicting an important hypothesis of \cite{Malkus_1954}. 
 This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure \ref{fig:flux}. 
-We don't understand the source of these dips, but similar temperature gradient reversals were reported by \cite{chini_cells} along the midlines of 2-dimensional convective cellular solutions at $Ra \sim 10^6$.
+We don't understand the source of these dips, but similar temperature gradient reversals were reported by \cite{chini_cells} along the midlines of 2D convective cellular solutions at $\Ra \sim 10^6$.
 
-Equilibrated states exhibit distinct behaviors for large and small $Ra$. 
-This contrast is illustrated in Figure \ref{fig:flux}, where we give heat flux profiles and eigenvalue spectra for two cases: $Ra = 2 \times 10^5$ and $Ra = 10^9$. 
-For $Ra = 2 \times 10^5$, there is a single presumed local maximum in the eigenvalue spectrum, whose adjacent modes' advection profiles occupy the bulk of the domain. 
+Equilibrated states exhibit distinct behaviors for large and small $\Ra$. 
+This contrast is illustrated in Figure \ref{fig:flux}, where we give heat flux profiles and eigenvalue spectra for two cases: $\Ra = 2 \times 10^5$ and $\Ra = 10^9$. 
+For $\Ra = 2 \times 10^5$, there is a single marginal mode at $k_x = 1.5\pi$ whose advection occupies the bulk of the domain. 
 These states have relaxed boundary layers which gradually subside as advection becomes the dominant flux component. 
-Such transitional regions do not appear for $Ra = 10^9$, where the shift from diffusion to advection is sharp, requiring pronounced, small-scale advection profiles belonging to modes in the third local maxima pair of the eigenvalue spectrum.
-Traversing towards the midline of the domain, we see increasingly thicker advection profiles corresponding to modes in the second local maxima pair, eventually culminating in the dominant $k_x = 1.5\pi$ mode.
+Such transitional regions do not appear for $\Ra = 10^9$.
+In this case the shift from diffusion to advection is sharp.
+Thin advection profiles, belonging to high-wavenumber modes, hug the boundary layer.
+Closer to the bulk of the domain, we see wider advection profiles corresponding to modes in the second marginal group $k_x = 6\pi, \, 6.5\pi$.
+The $k_x = 1.5\pi$ mode forms the large-scale convective cell structures observed in DNS, again occupying the bulk of the domain.
 
@@
     \caption{Wavenumbers of marginally-stable modes of thermally equilibrated states. 
-    Markers are color-coded according to their adjacent local maxima index in the eigenvalue spectrum. 
-    For example, the spectrum corresponding to $Ra = 10^5$ has adjacent marginal wavenumbers $k_x = \pi, \, 1.5\pi$. 
-    The $Ra = 10^9$ spectrum, shown in lower right corner of Figure \ref{fig:flux}, has three groups of maxima, with a single marginal mode in the first group ($k_x = 1.5\pi$), two adjacent marginal modes in the second group ($k_x = 6\pi, \, 6.5\pi$), and two adjacent marginal modes in the third group ($k_x = 23.5\pi, \, 24\pi$).
-    The largest wavenumbers of the green branch obey a power-law relationship with $Ra$}
+    Marginal modes often appear in adjacent pairs, which we denote with a common color. 
+    For example, the spectrum corresponding to $\Ra = 10^5$ has adjacent marginal wavenumbers $k_x = \pi, \, 1.5\pi$. 
+    The $\Ra = 10^9$ spectrum, shown in lower right corner of Figure \ref{fig:flux}, has three groups of maxima, with a single marginal mode in the first group ($k_x = 1.5\pi$), two adjacent marginal modes in the second group ($k_x = 6\pi, \, 6.5\pi$), and two adjacent marginal modes in the third group ($k_x = 23.5\pi, \, 24\pi$).
+    The largest wavenumbers of the green branch obey a power-law relationship with $\Ra$}
     \label{fig:kx_marginals}
@@
 
-Thermally equilibrated states with large $Ra$ tend to have diverse combinations of marginal modes. 
+MSTE of large $\Ra$ tend to have a diverse combination of marginal modes.
 In every case, the $k_x = 1.5\pi$ mode is included and is often unaccompanied by adjacent modes. 
-In Figure \ref{fig:kx_marginals} we give the wavenumbers $k_x$ of marginal modes, color-coded according to their adjacencies. 
-Marginal modes often appear in neighboring pairs, where the larger mode is denoted with an x and the smaller mode is denoted with a +. 
-In these cases we infer the existence of a local maximum eigenvalue between the two adjacent marginally-stable modes. 
-For $Ra \geq 10^6$, a second branch of marginal modes is introduced as shown in light green, obeying some power-law with respect to $Ra$. 
-The introduction of this largest branch is likely required to oppose the diffusion of the thinning boundary layers. 
-For $Ra \geq 10^8$, a third branch appears (shown in light blue), splitting the widening gap between the other branches. 
-This development is associated with moderately thick advection profiles, filling a niche in the total flux by uniting the sharp profiles of the largest branch and those of the bulk-domain-oriented smallest branch.
+In Figure \ref{fig:kx_marginals} we give the wavenumbers $k_x$ of marginal modes. 
+These wavenumbers often appear in adjacent pairs, where the larger mode is denoted with an x and the smaller with a +. 
+For $\Ra \geq 10^6$, a second branch of marginal modes is introduced as shown in light green, obeying some power-law with respect to $\Ra$. 
+For large $\Ra$, the advections of this maximum branch opposes the strong diffusion of the thin boundary layers. 
+At $\Ra \geq 10^8$, a third branch appears (shown in light blue), splitting the widening gap between the other two. 
+This development is associated with moderately wide advection profiles, filling a niche in the total flux by uniting the thin profiles of the maximum branch with those of the bulk-domain-oriented minimum branch.
 
@@
     \includegraphics[width=3.4in]{del_kx_inv.png}
-    \caption{For $Ra \geq 10^6$, the maximum marginally-stable wavenumbers (corresponding to the green X markers in Figure \ref{fig:kx_marginals}) are inversely related to the boundary layer heights $\delta$.
+    \caption{For $\Ra \geq 10^6$, the maximum marginally-stable wavenumbers (corresponding to the green x markers in Figure \ref{fig:kx_marginals}) are inversely related to the boundary layer heights $\delta$.
     $(\max \{ k_x \})^{-1}$ gives a minimum $x$ length scale for the perturbations, and consequently, the advection. 
-    We expect the minimum $z$ length scale to agree with the boundary layer height $\delta$ because otherwise the boundary layer would continue to diffuse. 
-    This is illustrated in the lower left corner of Figure \ref{fig:flux}, where the advection profile for $k_x = 24\pi$ is tightly flanked by the surrounding boundary layer. 
-    This suggests that the minimum $x$ and $z$ length scales obey some constant ratio over various $Ra$.}
+    For large $\Ra$, the boundary layers admit small scale features, requiring more basis functions (higher resolution).
+    It follows that the minimum $z$ length scale to agrees with the boundary layer height $\delta$. 
+    This suggests that the minimum $x$ and $z$ length scales obey some constant ratio over various $\Ra$ \note{There has to be published work on this length scale agreement}.}
     \label{fig:del_inv}
@@
 
-The largest marginal wavenumber $\max \{ k_x \}$ (represented by the light green branch in Figure \ref{fig:kx_marginals}) serves as a inverse minimum length-scale in the $x$ direction.
-The finest structures in $\bar{T}(z)$ appear near the boundaries, providing us with a complementary minimum length-scale for $z$.
+The largest marginal wavenumber $\max \{ k_x \}$ (represented by the light green branch in Figure \ref{fig:kx_marginals}) serves as an inverse minimum length-scale in the $x$ direction.
+The finest structures in $\bar{T}(z)$ appear near the boundaries, requiring more basis functions (resolution) at large $\Ra$.
+Naturally, this provides a complementary minimum length-scale for $z$.
 We define the interior boundary layer threshold as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$.
-In Figure \ref{fig:del_inv}, we illustrate the constant ratio between these two quantities for various $Ra$.
-The quasilinear model cannot describe small-scale behaviors in either direction.
+In Figure \ref{fig:del_inv}, we illustrate the constant ratio between these two quantities for various $\Ra$.
+The quasilinear model cannot describe arbitrarily small scale structures.
 Discretization of the normal modes allows us to collapse the problem into a single dimension, but this comes at a cost.
@@
     \includegraphics[width=3.4in]{del_ra.PNG}
-    \caption{Boundary layer height $\delta$ of marginally-stable thermal equilibria. 
-    We define the threshold of each boundary layer as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, corresponding to the local extrema of the equilibrated curve in Figure \ref{fig:T0_profiles}.
-    Plotting on a log-log scale, we find that $\delta$ and $Ra$ obey a power-law relationship.
-We also demonstrate that $Ra^{1/3}\delta$ is approximately constant with respect to $Ra$ which is consistent with \cite{Malkus_1954, Wen}}
+    \caption{Boundary layer height $\delta$ of MSTE. 
+    We define the threshold of each boundary layer as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, corresponding to the local extrema of the MSTE curve in Figure \ref{fig:T0_profiles}.
+    Plotting on a log-log scale, we find that $\delta$ and $\Ra$ obey a power-law relationship.
+We also demonstrate that $\Ra^{1/3}\delta$ is approximately constant with respect to $\Ra$ which is consistent with \cite{Malkus_1954}}
     \label{fig:bl_ra}
@@
 
-The Nusselt number, which measures convective performance, reduces to
+The Nusselt number, which measures convective performance is given by
 \begin{equation*}
@@
 \end{equation*}
-There is no general consensus surrounding the scaling behavior of $\Nu$ for high $Ra$ systems, which are of particular importance in astrophysical systems.
+\note{I'm giving the full Nu definition here so it's clear what's reported later in the simulations.}
+There is no general consensus surrounding the scaling behavior of $\Nu$ for high $\Ra$ systems, which are of particular importance in astrophysical and geophysical systems.
 In Figure \ref{fig:nu_vs_ra} we report $\Nu$ for MSTE, ``steady rolls" ECS \cite{Wen}, and DNS \cite{Scheel_2016, Johnston}.
-All states obey $\Nu \sim Ra^{\beta}$ with classical scaling $\beta = 1/3$ in the ECS and MSTE. 
-\cite{Wen} hypothesized that $\Nu$ of ECS which admit classical Malkus scaling must always exceed $\Nu$ of turbulent convection.
+All states obey $\Nu \sim\Ra^{\beta}$ with classical scaling $\beta = 1/3$ in the ECS and MSTE. 
+\cite{Wen} hypothesized that the $\Nu$ of all ECS which admit classical Malkus scaling must always exceed the $\Nu$ of turbulent convection.
 If we generalize this notion to include quasilinear equilibria, our findings agree; MSTE have larger $\Nu$ than 2D and 3D DNS.
-This might be due to the chaotic transitions, among the unstable periodic orbits outlined by \cite{Yalniz, Cvitanovic}, inhibiting heat flux. 
-We might also anticipate the existence of similar equilibria, having smaller $\Nu$ and occupying complementary nodes in the Markov chain whose long-term behavior agrees with DNS.
+This might be due to the chaotic transitions among the unstable periodic orbits outlined by \cite{Yalniz, Cvitanovic} inhibiting heat flux. 
+We might also anticipate the existence of similar equilibria with smaller $\Nu$, occupying complementary nodes in the Markov chain whose behavior agrees with DNS.
 
-\section{Simulations with Thermally Equilibrated Initial Conditions}\label{sec:sims}
-This investigation is partially motivated by the prospect of decreasing DNS times by employing MSTE initial conditions. 
-Conventionally, (\ref{EQ:motion1})--(\ref{EQ:motion3}) are solved via DNS with the linear initial conditions
+\section{Simulations with Thermally Equilibrated Initial Conditions}
+This investigation is partially motivated by the prospect of decreasing DNS times by employing MSTE as initial conditions. 
+Conventionally, \eqss{EQ:motion1}{EQ:motion3} are solved via DNS with the linear initial conditions
 \begin{align}
@@
     \mathbf{u}(x, z)\big|_{t=0} &= \mathbf{0} \nonumber \\
-    p(x, z)\big|_{t=0} &= 0 \label{EQ:linear_ic}.
+    p(x, z)\big|_{t=0} &= 0 \label{EQ:linear_ic}
 \end{align}
-$t$ in this section now refers to the simulation time as opposed to the thermal equilibration time parameter used previously. 
+where $t$ in this section now refers to the simulation time as opposed to the thermal equilibration time used previously. 
 We define the MSTE initial conditions
+\note{This needs to be updated}
 \begin{align}
@@
 Simulations with MSTE initial conditions do not exhibit a convective-transient period, as the large-scale anatomy of convective cells exists on initialization. 
-This is illustrated in Figure \ref{fig:nu_sim}, where the sharp spike in $\Nu$ is associated with a turbulent transitional period of upwelling until the distinctive plume-like structure is established.
+This is illustrated in Figure \ref{fig:nu_sim}, where the sharp spike in $\Nu$ is associated with a turbulent transitional period of upwelling until the distinctive flywheel structure is established. 
 Simulation of this transitional period is prohibitive \cite{Anders_AE}. 
-For high $Ra$ experiments, researchers often ``bootstrap" data by initializing simulations with the results of similar $Ra$ runs \cite{Verzicco, Johnston}. 
+For high $\Ra$ experiments, researchers often ``bootstrap" data by initializing simulations with the results of similar $\Ra$ runs \cite{Verzicco, Johnston}. 
 MSTE can be perceived as a set of initial conditions, designed for avoiding the simulation of transitional high Reynolds number flows.
 
-MSTE are laminar, lacking the small-scale structures associated with moderate to high $Ra$ experiments. 
-The absence of chaotic dynamics is an apparent consequence of the quasilinear assumptions. 
-If we treat MSTE as background states, DNS suggest that plumes, vortex sheets, and other unstable turbulent features inhibit total heat transfer. 
-This perspective agrees with conventional models of transitions to turbulent flows, such as Boussinesq's turbulent-viscosity hypothesis \cite{boussinesq_1877}, where the emergence of small-scale velocity structures tends to increase total shear \cite{Lecoanet_KH, drazin_reid_2004, pope_2000}, thereby impeding buoyancy-driven flows and decreasing advection in the bulk of the domain.
+MSTE are laminar, lacking the small-scale structures associated with moderate to high $\Ra$ experiments. 
+This is an apparent consequence of the quasilinear assumptions. 
+If we perceive MSTE as background states, DNS suggest that plumes, vortex sheets, and other unstable turbulent features inhibit total heat transfer. 
+This perspective agrees with conventional models of transitions to turbulent flows, such as Boussinesq's turbulent-viscosity hypothesis \cite{boussinesq_1877}.
+The emergence of small-scale velocity structures tends to increase total shear \cite{Lecoanet_KH, drazin_reid_2004, pope_2000}, thereby impeding buoyancy-driven flows and decreasing advection in the bulk of the domain.
 We could also attribute the diffuse DNS temperature profile in Figure \ref{fig:T0_profiles} with unsteady boundary-layer penetration and mixing that MSTE do not exhibit.
@@
         \includegraphics[width=3.4in]{sim_eq_ke.png}
-        \caption{Average kinetic energies are reported for the simulations performed in Figure \ref{fig:nu_sim} at $Ra = 10^8$. 
-        The combination of eigenfunctions associated with MSTE have significantly more kinetic energy than the statistically-steady state. 
-        Kinetic equilibrium is achieved according to the viscous time-scale $t_{\nu} \sim \sqrt{Ra / Pr}$.}
+        \caption{Average kinetic energies are reported for the same simulations illustrated in Figure \ref{fig:nu_sim} ($\Ra = 10^8$). 
+        The eigenfunctions belonging to MSTE have significantly more kinetic energy than the statistically-steady state. 
+        Kinetic equilibrium is achieved on the viscous time-scale $t_{\nu} \sim \sqrt{\Ra / \Pr}$.}
         \label{fig:ke_sim}
@@
 
-The average kinetic energies of MSTE are significantly larger than those associated with the statistically-steady state, as shown Figure \ref{fig:ke_sim}. 
+The average kinetic energies of MSTE are significantly larger than those of the statistically-steady state, as shown Figure \ref{fig:ke_sim}. 
 This is postpones kinetic relaxation because the large-scale flows decay on a viscous time-scale
@@
 In general, the reduced model we study in this paper can be perceived as a unique way to describe Rayleigh–Bénard convection. 
-To compute MSTE, we construct a marginally-stable mean temperature profile and develop the quasilinear model via independent time-scales.
-Solutions retain several key features that are ubiquitous in experiments and simulations: $\Nu \sim Ra^{1/3}$ scaling, large-scale convective cell structures, and agreement with classical minimum length-scale approximations \cite{Malkus_1954}.
-They also exhibit unique and unexpected features: mean temperature gradient-reversals/dips, kinetic exaggeration, and greater $\Nu$ than other time-invariant solutions. 
+To compute MSTE, we construct a marginally-stable mean temperature profile and evolved it according to its eigenfunctions' advection and its own diffusion. 
+We assume that stable and unstable modes cannot persist over a long time scale. 
+The marginal stability constraint then fixes the unknown ratio between advection and diffusion (eigenfunction amplitude $A^2$). 
+We use standard root-finding algorithms to solve for the appropriate $A^2$ at each iteration, until, the fixed combination of diffusion and advection sum to a constant flux.
+
+Solutions retain several key features that are ubiquitous in experiments and simulations: $\Nu \sim\Ra^{1/3}$ scaling, large-scale convective cell structures, and agreement with classical minimum length-scale approximations \cite{Malkus_1954}.
+They also exhibit unique and unexpected features: mean temperature gradient-reversals/dips, high kinetic energy flows, and greater $\Nu$ than other time-invariant solutions. 
 We obtain indistinguishable solutions despite initializing with various mean temperature profiles $\bar{T}(z, 0)$. 
@@
 
-Simulations performed with MSTE initial conditions (\ref{EQ:mste_ic}) do not undergo an early convective transient period, but have faster flows and greater $\Nu$ when compared with DNS. 
-From a dynamical systems perspective, unstable orbits depart from MSTE and approach the global attractor (the compact manifold of states whose weighted-average agrees with experiments) on a viscous time-scale.
-This requires more $CPU-hr$ to achieve relaxation as compared to the conventional linear initial condition (\ref{EQ:linear_ic}).
+Simulations performed with MSTE initial conditions \eq{EQ:mste_ic} do not undergo an early convective transient period, but have faster flows and greater $\Nu$ when compared with DNS. 
+From a dynamical systems perspective, in the space of nonlinear solution trajectories, unstable orbits depart from MSTE and approach the global attractor (the compact manifold of states whose weighted-average agrees with experiments) on a viscous time-scale.
+This requires more CPU-hr to achieve relaxation when compared to the conventional linear initial condition \eq{EQ:linear_ic}.
 
@@
 Unstable modes tend to stabilize the system rapidly, creating a negative feedback loop whose average state is linearly unstable. 
-We might curtail the disagreement between MSTE and DNS by loosening our marginal-stability criterion. 
-Should the time-scales not be entirely separate, we might anticipate the long-term persistance of moderately unstable modes. 
-Such an instability cannot be described by our model independently (we do not know, a priori, \textit{how unstable} MUTE should be) but it might prove fruitful to investigate moderately unstable thermal equilibria (MUTE).
+We might curtail the disagreement between MSTE and DNS adjusting our marginal-stability criterion. 
+Should the time scales not be entirely separate, we might anticipate the long-term persistance of moderately unstable modes. 
+Such an instability cannot be described by our model independently (we do not know, a priori, \textit{how unstable} the equilibria should be) but it might prove fruitful to investigate moderately unstable thermal equilibria (MUTE).
 More precisely, instead of traversing the manifold of marginally-stable states toward MSTE, we could consider the manifold of states whose maximum eigenvalue(s) $\omega_{\rm{max}}$ agree with some other stability constraint.
-Note that under this definition, 2-dimensional ECS are themselves MUTE, because they are thermally-equilibrated and generally unstable, though they need not satisfy the quasilinear form.
+Note that under this definition, ECS are themselves MUTE, because they are thermally-equilibrated and generally unstable, though they need not satisfy the quasilinear form.
 
-We cannot use our reduced quasilinear model to predict $\Nu \sim Ra^{\beta}$ for large $Ra$ without some complementary stability constraint. 
+We cannot use our reduced quasilinear model to predict $\Nu \sim\Ra^{\beta}$ for large $\Ra$ without some complementary stability constraint. 
 The eigenvalues of DNS data might provide an informative stability constraint (we could find MUTE and compare them with DNS data), but this would be self-defeating in general. 
 Instead we seek to combine reduced models to approximate $\beta$ without DNS.
-Under the marginal-stability constraint, we found that MSTE exhibit classical Malkus scaling, having marginally-stable boundary layers with $\beta = 1/3$.
-We could instead require that the eigenvalues of MUTE agree with the eigenvalues of the analytic 1-dimensional boundary layer predictions of \cite{Shishkina, Zhang_20} (which remain in development), allowing us to refine and expand these estimates into 2-dimensional MUTE.
-Accessible MUTE states would not rely on DNS, satisfying only the quasilinear problem and stability constraint. 
-Such MUTE ought to agree with DNS data more precisely than MSTE, ideally having slower flows. 
-This is reasonable to expect, since accurate boundary layer approximations and DNS data should have similar stability characteristics. 
-By definition, MUTE are unstable and would therefore admit more diffuse boundary layer structures, requiring smaller $A^2(t)$ (less advection) to satisfy the stability constraint and thereby reducing $\Nu$, $\langle |\mathbf{u}|^2 \rangle_{\mathcal{D}}$ and possibly $\beta$.
+Under the marginal-stability constraint, we found that MSTE exhibit classical Malkus scaling, having marginally-stable boundary layers.
+We could instead require that the eigenvalues of MUTE agree with the eigenvalues of the analytic 1D boundary layer predictions of \cite{Shishkina, Zhang_20} (which remain in development), allowing us to refine and expand these estimates into 2D MUTE.
+The process for finding such MUTE would not involve DNS. Equilibria would satisfy only the quasilinear problem and stability constraint. 
+They ought to agree with DNS data more than MSTE, ideally having slower flows. 
+This is reasonable to expect because accurate boundary layer approximations and DNS data should have similar stability characteristics. 
+We also observed that MSTE have marginally stable boundary layers, so it would be reasonable to place a hypothetical stability constraint on MUTE based on boundary layer approximations.
+By definition, MUTE are unstable and would likely admit more diffuse boundary layer structures, requiring smaller $A^2(t)$ (less advection) to satisfy the stability constraint and thereby reducing $\Nu$, $\langle |\mathbf{u}|^2 \rangle_{\mathcal{D}}$ and possibly $\beta$.
 
-\appendix
-
-\section{Initial buoyancy profile} \label{sec:initial_profile}
+\section*{Appendix}
+\subsection{Initial buoyancy profile} \label{sec:initial_profile}
 We initialize the thermal-equilibration algorithm with \cite{Shishkina}'s analytical thermal boundary layer equation for turbulent Rayleigh-B\'enard convection, given by 
@@
 It should be noted that when experimenting with various initial profiles $(\tanh, \rm{erf}, \rm{etc.})$, we obtain indistinguishable equilibrated states, implying that solutions may be unique. 
-An example of (\ref{EQ:T0}) is given by the blue curve in Figure \ref{fig:T0_profiles}.
+An example of \eq{EQ:T0} is given by the blue curve in Figure \ref{fig:T0_profiles}.
 
 % \begin{multicols}{1}
-\section{MSTE Metrics}
+\subsection{MSTE Metrics}\label{sec:tables}
 \begin{longtable*}{cccccc}

### 2021-04-16 publication_materials/ms_rbc.tex
Minor changes.

--- 2021-04-16 publication_materials/ms_rbc.tex
@@
 If ignored, we are forced to reduce the timestep and allow the modes to alternate which is marginally stable.
-Instead, we generalize the advective term in (\ref{EQ:T0_IVP}) to accommodate $N$ simultaneously marginal modes
+Instead, we calculate the advective term in (\ref{EQ:T0_IVP}) accommodating $N$ simultaneously marginal modes
 \begin{equation}
@@
 \section{Properties of Thermally Equilibrated States}\label{sec:properties}
-MSTE are fixed points of the quasilinear form derived in section \ref{sec:model}, differing from ECS in that ECS are fixed points of the full nonlinear problem (\ref{EQ:motion1})--(\ref{EQ:motion3}). 
-Such definitions are not mutually exclusive, but in general we can assume that MSTE and ECS are not steady with respect to their counterparts' problems.
-We compute symmetric MSTE for $Ra$ in the range $10^5 - 10^9$.
+We evolve $\bar{T}$ as described above until $\partial_t\bar{T}\approx 0$ \note{what is your criterion for equilibrium?}.
+In this marginally-stable thermal equilibrium, $\bar{T}$ does not evolve in time, and the perturbations also do not evolve in time, as they are marginally stable.
+Thus, these configurations are exact solutions to the quasilinear equations (equations~\ref{EQ:T0_IVP}--\ref{EQ:linear3}).
+They differ from the usual ECS in that ECS are fixed points of the full nonlinear problem (\ref{EQ:motion1})--(\ref{EQ:motion3}). 
+Such definitions are not mutually exclusive, but in general we can assume that MSTE and ECS are not steady with respect to their counterparts' equations.
+We compute symmetric MSTE for $Ra$ in the range $10^5 - 10^9$ \note{Somewhere you need to state we impose symmetry on the temperature field... this should got in section 3}.
 
@@
 Performing an eigenvalue solve by setting $\bar{T}$ equal to the DNS profile yields positive eigenvalues. 
-Comprehensively, this suggests that MSTE might maximize boundary layer thickness, while subject to the marginal stability constraint.
+This suggests that MSTE might maximize boundary layer thickness, while subject to the marginal stability constraint.
 
@@
 
+\section*{Acknowledgments}
+The authors thank Geoff Vasil, Greg Chini, and Emma Kaufman for their valuable feedback and suggestions. 
+We also thank the \texttt{Dedalus} and \texttt{Eigentools} development teams. 
+Computations were performed on the NASA Pleiades system.
+
 \appendix
@@
 
-\section*{Acknowledgments}
-The authors thank Jeff Vassil, Greg Chini, Emma Kaufman for their valuable feedback and suggestions. 
-We also thank the \texttt{Dedalus} and \texttt{Eigentools} development teams. 
-Computations were performed on the NASA Pleiades system.
-
 % \bibliographystyle{plain}

### 2021-04-16 publication_materials/ms_rbc.tex

--- 2021-04-16 publication_materials/ms_rbc.tex
@@
 \section{Properties of Thermally Equilibrated States}\label{sec:properties}
-MSTE are fixed points of the quasilinear form derived in section \ref{sec:model}, differing from ECS in that ECS are fixed points of the full nonlinear problem \eqss{EQ:motion1}{EQ:motion3}. 
-Such definitions are not mutually exclusive, but in general we can assume that MSTE and ECS are not steady with respect to their counterparts' problems.
-We compute symmetric MSTE for $Ra$ in the range $10^5 - 10^9$.
+We evolve $\bar{T}$ as described above until $\partial_t\bar{T}\approx 0$ \note{what is your criterion for equilibrium?}.
+In this marginally-stable thermal equilibrium, $\bar{T}$ does not evolve in time, and the perturbations also do not evolve in time, as they are marginally stable.
+Thus, these configurations are exact solutions to the quasilinear equations (equations~\ref{EQ:T0_IVP}--\ref{EQ:linear3}).
+They differ from the usual ECS in that ECS are fixed points of the full nonlinear problem (\ref{EQ:motion1})--(\ref{EQ:motion3}). 
+Such definitions are not mutually exclusive, but in general we can assume that MSTE and ECS are not steady with respect to their counterparts' equations.
+We compute symmetric MSTE for $Ra$ in the range $10^5 - 10^9$ \note{Somewhere you need to state we impose symmetry on the temperature field... this should got in section 3}.
 
@@
 
-\section*{Appendix}
-\subsection{Initial buoyancy profile} \label{sec:initial_profile}
+\section*{Acknowledgments}
+The authors thank Geoff Vasil, Greg Chini, and Emma Kaufman for their valuable feedback and suggestions. 
+We also thank the \texttt{Dedalus} and \texttt{Eigentools} development teams. 
+Computations were performed on the NASA Pleiades system.
+
+\appendix
+
+\section{Initial buoyancy profile} \label{sec:initial_profile}
 We initialize the thermal-equilibration algorithm with \cite{Shishkina}'s analytical thermal boundary layer equation for turbulent Rayleigh-B\'enard convection, given by 

### 2021-04-16 publication_materials/ms_rbc.tex
Misc. changes

@@
     It follows that the minimum $z$ length scale to agrees with the boundary layer height $\delta$. 
-    This suggests that the minimum $x$ and $z$ length scales obey some constant ratio over various $\Ra$ \note{There has to be published work on this length scale agreement}.}
+    This suggests that the minimum $x$ and $z$ length scales obey some constant ratio over various $\Ra$.}
     \label{fig:del_inv}
@@
     \caption{Nusselt numbers are shown for MSTE, aspect-ratio-optimized ``steady rolls'' ECS \cite{Wen}, as well as statistically-steady 2D and 3D DNS \cite{Johnston, Scheel_2016}.
-    All datasets obey power-law relationships, with the MSTE and ECS admitting classical scaling $\Nu \sim\Ra^{1/3}$. 
-    MSTE have greater $\Nu$ than the ECS, which in turn, have greater $\Nu$ than the DNS. This can be explained by the contrasting boundary layer geometries shown in Figure \ref{fig:T0_profiles}.}%
+    All datasets obey power-law relationships, with the MSTE and ECS scaling like $\Nu \sim\Ra^{1/3}$. 
+    MSTE have greater $\Nu$ than the ECS, which in turn, have greater $\Nu$ than the DNS. 
+    This can be explained by the contrasting boundary layer geometries shown in Figure \ref{fig:T0_profiles}.}%
     \label{fig:nu_vs_ra}%

### 2021-04-16 publication_materials/ms_rbc.tex
misc.

@@
 These dips appear in every solution, regardless of $\Ra$. 
-Physically, they correspond to thin layers in which the mean temperature gradient reverses, contradicting an important hypothesis of \cite{Malkus_1954}. 
+Physically, they correspond to thin layers in which the mean temperature gradient reverses, contradicting an important hypothesis of \cite{Malkus_1954,Howard_1966}. 
 This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure \ref{fig:flux}. 
@@
 For $\Ra \geq 10^6$, a second branch of marginal modes is introduced as shown in light green, obeying some power-law with respect to $\Ra$. 
-For large $\Ra$, the advections of this maximum branch opposes the strong diffusion of the thin boundary layers. 
+For large $\Ra$, the advections of this maximum branch opposes the strong diffusion of the thin MSTE boundary layers. 
 At $\Ra \geq 10^8$, a third branch appears (shown in light blue), splitting the widening gap between the other two. 
@@
 In Figure \ref{fig:del_inv}, we illustrate the constant ratio between these two quantities for various $\Ra$.
-The quasilinear model cannot describe arbitrarily small scale structures.
-Discretization of the normal modes allows us to collapse the problem into a single dimension, but this comes at a cost.
+We can assume from this length scale agreement that the mean-squared $x$ and $z$ components of the temperature and velocity gradients are proportional for various $\Ra$
+\begin{align*}
+    \Big\langle \frac{\partial T}{\partial x} \cdot \frac{\partial T}{\partial x} \Big\rangle_{\mathcal{D}} &\propto \Big\langle \frac{\partial T}{\partial z} \cdot \frac{\partial T}{\partial z} \Big\rangle_{\mathcal{D}}    \\
+    \Big\langle \frac{\partial \mathbf{u}}{\partial x} \cdot \frac{\partial \mathbf{u}}{\partial x} \Big\rangle_{\mathcal{D}} &\propto \Big\langle \frac{\partial \mathbf{u}}{\partial z} \cdot \frac{\partial \mathbf{u}}{\partial z} \Big\rangle_{\mathcal{D}}.
+\end{align*}
+This is consistent with the mean squared gradient assumptions of \cite{Malkus_1954}.
+The quasilinear model cannot describe arbitrarily small scale structures. This is a consequence of us collapsing the problem into a single dimension via mode-discretization.
 
@@
 
-Solutions retain several key features that are ubiquitous in experiments and simulations: $\Nu \sim\Ra^{1/3}$ scaling, large-scale convective cell structures, and agreement with classical minimum length-scale approximations \cite{Malkus_1954}.
+Solutions retain several key features that are prevalent in experiments and simulations: $\Nu \sim\Ra^{1/3}$ scaling, large-scale convective cell structures, and minimum length scale agreement. 
 They also exhibit unique and unexpected features: mean temperature gradient-reversals/dips, high kinetic energy flows, and greater $\Nu$ than other time-invariant solutions. 
@@
 Simulations performed with MSTE initial conditions \eq{EQ:mste_ic} do not undergo an early convective transient period, but have faster flows and greater $\Nu$ when compared with DNS. 
-From a dynamical systems perspective, in the space of nonlinear solution trajectories, unstable orbits depart from MSTE and approach the global attractor (the compact manifold of states whose weighted-average agrees with experiments) on a viscous time-scale.
+From a dynamical systems perspective, unstable orbits depart from MSTE and approach the global attractor on a viscous time-scale \note{Still reading about this}.
 This requires more CPU-hr to achieve relaxation when compared to the conventional linear initial condition \eq{EQ:linear_ic}.

### 2021-04-17 publication_materials/ms_rbc.tex
Edits on the rest of the paper.

@@
     The initial profile is given by \eq{EQ:T0}. 
-    MSTE refers to the mean temperature profile of the marginally-stable thermally-equilibrated state. 
-    DNS was obtained by performing a 2D nonlinear simulation of \eqss{EQ:motion1}{EQ:motion3} with \texttt{Dedalus} until thermal and kinetic relaxation. 
+    We evolve this background temperature profile according to section~\ref{sec:evolution} until we reach a marginally-stable thermal equilibrium (MSTE).
+    The DNS curve is obtained from a 2D nonlinear simulation of \eqss{EQ:motion1}{EQ:motion3} with \texttt{Dedalus}.
     DNS temperature data are horizontally- and time-averaged.
-    The initial, MSTE, and DNS profiles have increasingly relaxed boundary regions respectively. 
-    The MSTE profile exhibits prominent dips, nested alongside the boundary regions. 
-    The source of this feature is not well understood, but similar temperature gradient reversal regions were found by \cite{chini_cells} along the midlines of 2D convective cellular solutions at $\Ra \sim 10^6$.}
+    The initial profile has the narrowest boundary layer, while the DNS profile has the widest boundary layer.
+    The MSTE profile exhibits prominent dips, nested alongside the boundary regions. }
+%    The source of this feature is not well understood, but similar temperature gradient reversal regions were found by \cite{chini_cells} along the midlines of 2D convective cellular solutions at $\Ra \sim 10^6$.}
     \label{fig:T0_profiles}
@@
 
-Figure \ref{fig:T0_profiles} gives temperature profiles for $\Ra = 10^8$ where the initial profile, whose construction is outlined in \ref{sec:initial_profile}, is employed at iteration 0. 
-DNS (direct numerical simulations) are performed by solving \eqss{EQ:motion1}{EQ:motion3} with \texttt{Dedalus}, followed by horizontal- and time- averaging. 
+Figure \ref{fig:T0_profiles} gives temperature profiles for $\Ra = 10^8$ where the initial profile, whose construction is outlined in appendix~\ref{sec:initial_profile}, is employed at iteration 0. 
+Direct numerical simulations (DNS) are performed by solving \eqss{EQ:motion1}{EQ:motion3} with \texttt{Dedalus}, followed by horizontal- and time- averaging. 
 The DNS curve is more diffuse than the MSTE curve, which in turn, is more diffuse than the initial curve. 
-Performing an eigenvalue solve by setting $\bar{T}$ equal to the DNS profile yields positive eigenvalues. 
-This suggests that MSTE might maximize boundary layer thickness, while subject to the marginal stability constraint.
+Performing an eigenvalue solve by setting $\bar{T}$ equal to the DNS profile yields unstable eigenvalues. 
+This suggests that MSTE might maximize boundary layer thickness, subject to the marginal stability constraint.
 
@@
     \caption{Heat fluxes (left) and eigenvalue spectra (right) of equilibrated states $\Ra = 2 \times 10^5$ (top) and $\Ra = 10^9$ (bottom). 
+    The heat flux profiles are symmetric about $z=0$, so we only plot for $z<0$.
     Advection profiles belong to marginally-stable modes. 
@@
 This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure \ref{fig:flux}. 
-We don't understand the source of these dips, but similar temperature gradient reversals were reported by \cite{chini_cells} along the midlines of 2D convective cellular solutions at $\Ra \sim 10^6$.
+We do not understand the source of these dips, but similar temperature gradient reversals were reported by \cite{chini_cells} along the midlines of 2D convective cellular solutions at $\Ra \sim 10^6$.
+In that case, the reversals were due to nonlinear advection, which is not present in our quasilinear model.
 
@@
 This contrast is illustrated in Figure \ref{fig:flux}, where we give heat flux profiles and eigenvalue spectra for two cases: $\Ra = 2 \times 10^5$ and $\Ra = 10^9$. 
-For $\Ra = 2 \times 10^5$, there is a single marginal mode at $k_x = 1.5\pi$ whose advection occupies the bulk of the domain. 
-These states have relaxed boundary layers which gradually subside as advection becomes the dominant flux component. 
+For $\Ra = 2 \times 10^5$, there is a single marginal mode at $k_x = 1.5\pi$ whose advective flux occupies the bulk of the domain. 
+These states have wide boundary layers which gradually subside as advection becomes the dominant flux component. 
 Such transitional regions do not appear for $\Ra = 10^9$.
 In this case the shift from diffusion to advection is sharp.
-Thin advection profiles, belonging to high-wavenumber modes, hug the boundary layer.
-Closer to the bulk of the domain, we see wider advection profiles corresponding to modes in the second marginal group $k_x = 6\pi, \, 6.5\pi$.
+At $\Ra=10^9$ we find five marginally-stable modes are necessary to reach a MSTE.
+Thin advection profiles, belonging to high-wavenumber modes with $k_x=23.5\pi, \, 24\pi$, hug the boundary layer. 
+Closer to the bulk of the domain, we see wider advection profiles corresponding to modes in a second group of marginal modes $k_x = 6\pi, \, 6.5\pi$.
 The $k_x = 1.5\pi$ mode forms the large-scale convective cell structures observed in DNS, again occupying the bulk of the domain.
+The pairs of modes $k_x = 6\pi, \, 6.5\pi$ and $k_x=23.5\pi, \, 24\pi$ are each associated with a single maximum in our plots of growth rate $\omega$ as a function of $k_x$ (lower right panel of Figure~\ref{fig:flux}).
+If we allowed wavenumbers to vary continuously, there would be an unstable mode between these pairs of wavenumbers.
+However, since we have fixed the horizontal size of our domain, we are left with pairs of discrete margin modes.
 
@@
     \includegraphics[width=3.4in]{kx_m_ra1.png}
-    \caption{Wavenumbers of marginally-stable modes of thermally equilibrated states. 
+    \caption{Wavenumbers of marginally-stable modes in thermally equilibrated states. 
     Marginal modes often appear in adjacent pairs, which we denote with a common color. 
@@
 
-MSTE of large $\Ra$ tend to have a diverse combination of marginal modes.
-In every case, the $k_x = 1.5\pi$ mode is included and is often unaccompanied by adjacent modes. 
+MSTE for large $\Ra$ tend to have a diverse combination of marginal modes.
+In every case, the $k_x = 1.5\pi$ mode is included. 
 In Figure \ref{fig:kx_marginals} we give the wavenumbers $k_x$ of marginal modes. 
-These wavenumbers often appear in adjacent pairs, where the larger mode is denoted with an x and the smaller with a +. 
-For $\Ra \geq 10^6$, a second branch of marginal modes is introduced as shown in light green, obeying some power-law with respect to $\Ra$. 
-For large $\Ra$, the advections of this maximum branch opposes the strong diffusion of the thin MSTE boundary layers. 
+Sometimes we find two marginally-stable modes with wavenumbers separated by $\pi/2$.
+Like $k_x = 6\pi, \, 6.5\pi$ and $k_x=23.5\pi, \, 24\pi$ for the $\Ra=10^9$ MSTE, these are due to the discretization of wavenumbers from our domain of width 4.
+We think of the pairs of modes as acting together as part of a single maximum of the growth rate as a function of the wavenumber.
+When wavenumbers are adjacent, we plot them in the same color and denote the larger mode with an x and the smaller with a +.
+For $\Ra \geq 10^6$, a second branch of marginal modes is shown in light green. 
+For large $\Ra$, the advective fluxes of this maximum branch opposes the strong diffusion of the thin MSTE boundary layers. 
 At $\Ra \geq 10^8$, a third branch appears (shown in light blue), splitting the widening gap between the other two. 
@@
     \includegraphics[width=3.4in]{del_kx_inv.png}
-    \caption{For $\Ra \geq 10^6$, the maximum marginally-stable wavenumbers (corresponding to the green x markers in Figure \ref{fig:kx_marginals}) are inversely related to the boundary layer heights $\delta$.
+    \caption{For $\Ra \geq 10^6$, the maximum marginally-stable wavenumber (corresponding to the green x markers in Figure \ref{fig:kx_marginals}) are inversely related to the boundary layer height $\delta$.
     $(\max \{ k_x \})^{-1}$ gives a minimum $x$ length scale for the perturbations, and consequently, the advection. 
-    For large $\Ra$, the boundary layers admit small scale features, requiring more basis functions (higher resolution).
-    It follows that the minimum $z$ length scale to agrees with the boundary layer height $\delta$. 
-    This suggests that the minimum $x$ and $z$ length scales obey some constant ratio over various $\Ra$.}
+    For large $\Ra$, the boundary layers admit small scale features, requiring more vertical basis functions (higher resolution).
+    The boundary layer width gives an estimate of the minimum vertical lengthscale in the problem.
+    This suggests that the minimum horizontal and vertical lengthscales are proportional to each other over a wide range of $\Ra$.}
     \label{fig:del_inv}
@@
 The largest marginal wavenumber $\max \{ k_x \}$ (represented by the light green branch in Figure \ref{fig:kx_marginals}) serves as an inverse minimum length-scale in the $x$ direction.
-The finest structures in $\bar{T}(z)$ appear near the boundaries, requiring more basis functions (resolution) at large $\Ra$.
+The finest vertical structures in $\bar{T}(z)$ appear near the boundaries, requiring more basis functions (resolution) at large $\Ra$.
 Naturally, this provides a complementary minimum length-scale for $z$.
-We define the interior boundary layer threshold as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$.
-In Figure \ref{fig:del_inv}, we illustrate the constant ratio between these two quantities for various $\Ra$.
-We can assume from this length scale agreement that the mean-squared $x$ and $z$ components of the temperature and velocity gradients are proportional for various $\Ra$
+We define the boundary layer width $\delta$ as the distance from the boundary where $\partial_z T$ equals zero, i.e.,
+\begin{align}\label{eqn:delta}
+\left.\frac{\partial \bar{T}}{\partial z}\right|_{z=-\frac{1}{2}+\delta} = 0.
+\end{align}
+This height corresponds to the local extrema of the MSTE temperature profile, e.g., in Figure \ref{fig:T0_profiles}
+In Figure \ref{fig:del_inv}, we show $\max \{ k_x\}$ is proportional to $\delta$ over our range of $\Ra$.
+We can assume from this length scale agreement that the mean-squared $x$ and $z$ components of the temperature and velocity gradients are proportional
 \begin{align*}
@@
 This is consistent with the mean squared gradient assumptions of \cite{Malkus_1954}.
-The quasilinear model cannot describe arbitrarily small scale structures. This is a consequence of us collapsing the problem into a single dimension via mode-discretization.
+%The quasilinear model cannot describe arbitrarily small scale structures. This is a consequence of us collapsing the problem into a single dimension via mode-discretization.
 
@@
     \caption{Boundary layer height $\delta$ of MSTE. 
-    We define the threshold of each boundary layer as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, corresponding to the local extrema of the MSTE curve in Figure \ref{fig:T0_profiles}.
+    We define the boundary layer height based off the location where $\frac{\partial \bar{T}}{\partial z} = 0$ (see equation~\ref{eqn:delta}). 
     Plotting on a log-log scale, we find that $\delta$ and $\Ra$ obey a power-law relationship.
@@
 
-In general, MSTE can be characterized by their boundary layer height, from which, the rest of their properties follow.
+We find the MSTE can be characterized by their boundary layer height.
 In Figure \ref{fig:bl_ra}, we illustrate the scaling behavior of the boundary layer height $\delta = \Ra^{-1/3}$. 
@@
 \begin{equation*}
-    \Nu = \frac{\langle A^2 \langle w'T' \rangle_x - \mathcal{P}\frac{\partial \bar{T}}{\partial z} \rangle_z}{\langle- \mathcal{P}\frac{\partial \bar{T}}{\partial z} \rangle_z}.
+    \Nu = \frac{\langle \langle w'T' \rangle_x - \mathcal{P}\frac{\partial \bar{T}}{\partial z} \rangle_z}{\langle- \mathcal{P}\frac{\partial \bar{T}}{\partial z} \rangle_z}.
 \end{equation*}
@@
 In Figure \ref{fig:nu_vs_ra} we report $\Nu$ for MSTE, ``steady rolls" ECS \cite{Wen}, and DNS \cite{Scheel_2016, Johnston}.
-All states obey $\Nu \sim\Ra^{\beta}$ with classical scaling $\beta = 1/3$ in the ECS and MSTE. 
+We find that MSTE satisfy $\Nu \sim\Ra^{1/3}$, consistent with our finding that the boundary layer width scales like $\delta \sim \Ra^{1/3}$.
+The Nusselt numbers of the ECS are somewhat lower and the DNS Nusselt numbers are yet lower still.
+In both cases, the $\Ra$ dependence appear slightly more shallow than for the MSTE.
 \cite{Wen} hypothesized that the $\Nu$ of all ECS which admit classical Malkus scaling must always exceed the $\Nu$ of turbulent convection.
@@
 \section{Simulations with Thermally Equilibrated Initial Conditions}
-This investigation is partially motivated by the prospect of decreasing DNS times by employing MSTE as initial conditions. 
-Conventionally, \eqss{EQ:motion1}{EQ:motion3} are solved via DNS with the linear initial conditions
+This investigation is partially motivated by the prospect of decreasing DNS runtimes by employing MSTE as initial conditions. 
+One common choice of initial conditions for DNS of equations \eqss{EQ:motion1}{EQ:motion3} are
 \begin{align}
-    T(x, z)\big|_{t=0} &= 0.5 - z \nonumber \\
+    T(x, z)\big|_{t=0} &= 0.5 - z + N \nonumber \\
     \mathbf{u}(x, z)\big|_{t=0} &= \mathbf{0} \nonumber \\
@@
 \end{align}
-where $t$ in this section now refers to the simulation time as opposed to the thermal equilibration time used previously. 
-We define the MSTE initial conditions
+where $N$ is low-amplitude random noise.
+Here we instead initialize using the MSTE,
 \note{This needs to be updated}
@@
 The $\sqrt{2}$ factor is necessary for eigenfunction normalization. 
+Note that although the MSTE is an equilibrium of the quasilinear equations, it is not an equilibrium of the full nonlinear equations.
+\note{Say something about noise}
 
@@
         \includegraphics[width=3.4in]{sim_eq_nu.png}
-        \caption{Nusselt numbers of simulations performed at $\Ra = 10^8$ with the conventional initial conditions (black) and MSTE initial conditions (blue). 
+        \caption{Nusselt numbers of simulations performed at $\Ra = 10^8$, initialized with the conductive equilibrium plus thermal noise (black) and the MSTE (blue). 
         MSTE simulations do not undergo a convective-transient period because the characteristic large-scale convective cell structure exists on initialization.}
@@
 
-Simulations with MSTE initial conditions do not exhibit a convective-transient period, as the large-scale anatomy of convective cells exists on initialization. 
-This is illustrated in Figure \ref{fig:nu_sim}, where the sharp spike in $\Nu$ is associated with a turbulent transitional period of upwelling until the distinctive flywheel structure is established. 
+Simulations initialized with the conductive equilibrium plus low-amplitude thermal noise have a large peak in $\Nu$ early on in their evolution (Figure~\ref{fig:nu_sim}).
+This is due to a burst of turbulence which occurs when the convective motions first become nonlinear.
+A simulation initialized with the MSTE, however, does not exhibit this transient burst of turbulence, as the large-scale anatomy of convective cells exists on initialization. 
 Simulation of this transitional period is prohibitive \cite{Anders_AE}. 
@@
 
-The average kinetic energies of MSTE are significantly larger than those of the statistically-steady state, as shown Figure \ref{fig:ke_sim}. 
-This is postpones kinetic relaxation because the large-scale flows decay on a viscous time-scale
-
+We also find that the average kinetic energies of simulations initialized with MSTE are significantly larger than those found in simulations initialized with the conductive state plus noise, as shown Figure \ref{fig:ke_sim}.
+This is because the MSTE contain strong large-scale flows, which decay on a viscous time-scale
 \begin{equation}
@@
 \end{equation}
-
-Consequently, MSTE initial conditions do not reduce the simulation time required to achieve a statistically-steady state -- instead they increase it considerably. 
-This suggests the MSTE background state perspective is partially flawed, as an appropriate background state would approximate $\langle|\mathbf{u}|^2 \rangle_{\mathcal{D}}$ with more fidelity.
+Consequently, MSTE initial conditions do not reduce the simulation time required to achieve a statistically-steady state---rather they increase it considerably!
+This suggests the MSTE background state perspective is partially flawed, as a more useful background state would approximate the kinetic energy with more fidelity.
 
 \section{Discussion}\label{sec:Discussion}
-In general, the reduced model we study in this paper can be perceived as a unique way to describe Rayleigh–Bénard convection. 
-To compute MSTE, we construct a marginally-stable mean temperature profile and evolved it according to its eigenfunctions' advection and its own diffusion. 
-We assume that stable and unstable modes cannot persist over a long time scale. 
-The marginal stability constraint then fixes the unknown ratio between advection and diffusion (eigenfunction amplitude $A^2$). 
+In this paper we describe a new way to study Rayleigh–Bénard convection. 
+We compute marginally-stable thermal equilibria (MSTE), which are equilibria of the quasilinear equations.
+To compute MSTE, we construct a marginally-stable mean temperature profile and evolved it according to the advective flux of its marginally-stable eigenfunctions, and its own diffusion. 
+We assume that at least some modes are always in a marginally-stable configuration. 
+The marginal stability constraint then fixes the ratio between advection and diffusion (eigenfunction amplitude $A^2$). 
 We use standard root-finding algorithms to solve for the appropriate $A^2$ at each iteration, until, the fixed combination of diffusion and advection sum to a constant flux.
+The MSTE calculation is a one-dimensional problem, combining eigenvalue solves, and the time evolution of the one-dimensional mean temperature profile.
+Thus, they can be calculated on a single workstation.
 
-Solutions retain several key features that are prevalent in experiments and simulations: $\Nu \sim\Ra^{1/3}$ scaling, large-scale convective cell structures, and minimum length scale agreement. 
-They also exhibit unique and unexpected features: mean temperature gradient-reversals/dips, high kinetic energy flows, and greater $\Nu$ than other time-invariant solutions. 
-We obtain indistinguishable solutions despite initializing with various mean temperature profiles $\bar{T}(z, 0)$. 
-Thus solutions might be unique, but we cannot demonstrate this rigorously.
+The MSTE retain several key features that are prevalent in experiments and simulations: $\Nu \sim\Ra^{1/3}$ scaling, large-scale convective cell structures, and minimum length scale agreement. 
+They also exhibit unique and unexpected features: mean temperature gradient-reversals/dips, high kinetic energy flows, and a larger $\Nu$ than other time-invariant solutions. 
+When initializing with different mean temperature profile, we found the the same MSTE, suggesting these equilibria might be unique.
 
-Simulations performed with MSTE initial conditions \eq{EQ:mste_ic} do not undergo an early convective transient period, but have faster flows and greater $\Nu$ when compared with DNS. 
+Simulations initialized with the MSTE \eq{EQ:mste_ic} do not undergo an early convective transient period, but have faster flows and greater $\Nu$ when compared with DNS.
+\note{Do they have larger Nu?
+It looks like it's the same in the plot!!}
 From a dynamical systems perspective, unstable orbits depart from MSTE and approach the global attractor on a viscous time-scale \note{Still reading about this}.
-This requires more CPU-hr to achieve relaxation when compared to the conventional linear initial condition \eq{EQ:linear_ic}.
+This requires more computational effort to achieve relaxation when compared to the conventional conductive initial condition \eq{EQ:linear_ic}.
 
-As previously noted, solving the EVP for statistically-steady DNS data yields positive eigenvalues; the system is in a perpetual state of instability. 
+As previously noted, using the mean temperature in a statistically-steady DNS as a background state for an eigenvalue problem yields positive eigenvalues: the system is in a perpetual state of instability.
 Unstable modes tend to stabilize the system rapidly, creating a negative feedback loop whose average state is linearly unstable. 
-We might curtail the disagreement between MSTE and DNS adjusting our marginal-stability criterion. 
+We might curtail the disagreement between MSTE and DNS by adjusting our marginal-stability criterion. 
 Should the time scales not be entirely separate, we might anticipate the long-term persistance of moderately unstable modes. 
 Such an instability cannot be described by our model independently (we do not know, a priori, \textit{how unstable} the equilibria should be) but it might prove fruitful to investigate moderately unstable thermal equilibria (MUTE).
+\note{This is a bit too cute...
+Might be a risk for a reviewer?
+Your call.}
 More precisely, instead of traversing the manifold of marginally-stable states toward MSTE, we could consider the manifold of states whose maximum eigenvalue(s) $\omega_{\rm{max}}$ agree with some other stability constraint.
@@
 
+\note{This last paragraph is somewhat confusing to me.
+I think it's dangerous to say that we can predict Nu-Ra scaling using anything other than DNS or experiments.
+Why would 1D boundary-layer predictions give 2D equilibria?
+Right now we're using a 1D boundary-layer prediction.}
 We cannot use our reduced quasilinear model to predict $\Nu \sim\Ra^{\beta}$ for large $\Ra$ without some complementary stability constraint. 
@@
 We also thank the \texttt{Dedalus} and \texttt{Eigentools} development teams. 
-Computations were performed on the NASA Pleiades system.
+Computations were conducted with support by the NASA High End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades with allocation GIDs s2276.
 

### 2021-04-20 publication_materials/ms_rbc.tex
misc. edits

@@
 The resulting buoyancy-driven flows regulate heat transfer and generate large-scale vortices \cite{Couston}.
-Turbulent convection, which is associated with large Rayleigh numbers $Ra$, is difficult to simulate. 
-State of the art simulations performed by \cite{Zhu_2018} have reached $Ra \sim 10^{14}$ but estimates for stars are $Ra \sim 10^{20}$ \cite{Ossendrijver}. 
-\note{put in a number for earth's interior?}
+Turbulent convection, which is associated with large Rayleigh numbers $\Ra$, is difficult to simulate. 
+State of the art simulations performed by \cite{Zhu_2018} have reached $\Ra \sim 10^{14}$ but estimates for the sun's convective zone and earth's interior are $Ra \sim 10^{16}-10^{20}$ and $Ra \sim 10^{20}-10^{30}$ respectively \cite{Ossendrijver,Gubbins_2001}.
 The scaling behavior of the Nusselt number $\Nu \sim Ra^{\beta}$ in the asymptotic ultimate regime is of particular interest.
@@
 
-Absent solid evidence from direct numerical simulation, other methods have been developed to try to infer large-$Ra$ behavior or otherwise gain insight.
+Absent solid evidence from direct numerical simulation, other methods have been developed to try to infer large-$\Ra$ behavior or otherwise gain insight.
 In the presence of other physical effects (e.g., rotation, magnetic fields), one can sometimes derive an asymptotically consistent set of reduced equations \cite{Julien2007, Julien2012}.
@@
 Another approach relates to unstable exact coherent states (ECS) \cite{Waleffe, Sondak, Wen, chini_cells}. 
-Simulations and analysis performed by \cite{Yalniz, Cvitanovic} suggest that chaotic simulation trajectories can be represented by a Markov chain whose long-term behavior is given by the time-weighted-average over a finite set of unstable equilibria.
+Simulations and analysis performed by \cite{Yalniz, Cvitanovic} suggest that chaotic solution trajectories might ``visit'' these ECS.
 Should that be the case, it is crucial that we discover and classify such equilibria.
@@
 The domain $\mathcal{D}$ is 2-dimensional, rectangular, and horizontally periodic with spatial dimensions $0 < x < 4$ and $-1/2 < z < 1/2$. 
-The fluid of interest is constrained between two flat boundaries at $z = -1/2$ and $z = 1/2$ with fixed temperatures $1$ and $0$ respectively. 
-At both boundaries we specify impenetrable, no-slip conditions, such that the velocity $\mathbf{u} = u \hat{x} + w \hat{z} = \mathbf{0}$ at $z = \pm 1/2$, where $\hat{x}, \hat{z}$ are the unit vectors in the $x$ and $z$ directions.
+The fluid of interest is constrained between two flat boundaries at $z = -1/2$ and $z = 1/2$ with fixed temperatures $1/2$ and $-1/2$ respectively. 
+At both boundaries we specify impenetrable, no-slip conditions, such that the velocity $\vec{u} = u \hat{x} + w \hat{z} = \vec{0}$ at $z = \pm 1/2$, where $\hat{x}, \hat{z}$ are the unit vectors in the $x$ and $z$ directions.
 The equations of motion are then given by
 \begin{align}
-    \nabla \cdot \mathbf{u} &= 0 \label{EQ:motion1}\\
-    \frac{\partial \mathbf{u}}{\partial t} + \mathbf{u} \cdot \nabla \mathbf{u} &= - \nabla p + T \hat{z} + \mathcal{R} \nabla^2 \mathbf{u} \label{EQ:motion2}\\
-    \frac{\partial T}{\partial t} + \mathbf{u} \cdot \nabla T &= \mathcal{P} \nabla^2 T \label{EQ:motion3}
+    \nabla \cdot \vec{u} &= 0 \label{EQ:motion1}\\
+    \frac{\partial \vec{u}}{\partial t} + \vec{u} \cdot \nabla \vec{u} &= - \nabla p + T \hat{z} + \mathcal{R} \nabla^2 \vec{u} \label{EQ:motion2}\\
+    \frac{\partial T}{\partial t} + \vec{u} \cdot \nabla T &= \mathcal{P} \nabla^2 T \label{EQ:motion3}
 \end{align}
@@
 \begin{align}
-    \mathbf{u}(x, z, t) &= \mathbf{u'}(x, z, t) \label{EQ:reynolds_dc_u}\\
+    \vec{u}(x, z, t) &= \vec{u'}(x, z, t) \label{EQ:reynolds_dc_u}\\
     &= u'(x, z, t)\hat{x} + w'(x, z, t)\hat{z} \\
@@
 \end{equation}
-with associated boundary conditions $\bar{T}(-1/2, t) = 1$ and $\bar{T}(1/2, t) = 0$.
+with associated boundary conditions $\bar{T}(-1/2, t) = 1/2$ and $\bar{T}(1/2, t) = -1/2$.
 It should be noted that we could obtain a similar IVP for $u$ by breaking symmetry and considering some nontrivial mean horizontal flow $\bar{u}(z, t)$.
@@
 \begin{align}
-    \nabla \cdot \mathbf{u'} &= 0 \label{EQ:linear1}\\
-    \frac{\partial\mathbf{u'}}{\partial t} &= - \nabla p' + T'\hat{z} + \mathcal{R} \nabla^2 \mathbf{u'} \label{EQ:linear2}\\
+    \nabla \cdot \vec{u'} &= 0 \label{EQ:linear1}\\
+    \frac{\partial\vec{u'}}{\partial t} &= - \nabla p' + T'\hat{z} + \mathcal{R} \nabla^2 \vec{u'} \label{EQ:linear2}\\
     \frac{\partial T'}{\partial t} + \frac{\partial \bar{T}}{\partial z} w' &= \mathcal{P} \nabla^2 T' \label{EQ:linear3}
@@
 For each $k_x$, we can assess the stability of the perturbations by solving for the eigenvalue $s$, whose imaginary component $\omega$ plays the role of an exponential growth rate. 
-Solution yields a finite set of eigenvalues, among which, that with maximum $\omega$ is assumed to be dominant \note{I don't understand this sentence}. 
 Positive eigenvalues indicate that the system is unstable to small disturbances of wavenumber $k_x$, while negative eigenvalues indicate stability. 
@@
 \begin{equation}
-    A^2 \approx -\frac{\omega_{\rm{diff}}}{\omega_{\rm{adv}}}
+    A^2 \approx -\frac{\omega_{\rm{diff}}}{\omega_{\rm{adv}}} \label{EQ:amp_approx}
 \end{equation}
@@
 Given a fixed timestep $\Delta t$, we assume the dominant eigenvalue can be described by a continuous function $\omega_{\rm{max}} (A^2)$ which is locally differentiable. 
-We use Newton's method to find an amplitude which satisfies our marginal stability tolerance criterion \note{what is the criterion?}.
+We use Newton's method to find an amplitude which satisfies our marginal stability tolerance criterion $|\omega_{\rm{max}} (A^2)| < 10^{-9}$.
 Crucially, we do not assume the $k_x$ of the marginally-stable is fixed.
@@
 where $W_n$ and $\theta_n$ are the eigenmodes associated with $k_x = \frac{n\pi}{2}$. 
-There are now $N$ amplitudes to solve for and $N$ eigenvalues to keep marginally-stable. 
-In general, we expect a function $\mathbf{\omega} \, : \, \mathbb{R}^N \to  \mathbb{R}^N$ to have isolated roots (should they exist). 
-We employ Broyden's method for root-finding in multi-dimensional functions whose derivatives are not explicitly known \note{Should describe this better...
-don't you calculate the Jacobian, invert it, and then refine the roots using Broyden's method?}.
-Difficulty arises when transitioning between different numbers of marginal modes.
-\note{Should describe what happens when you add modes}
-Here we rely on $A^2 > 0$ by asserting that a mode which is \textit{close enough} to marginal-stability can be included in the iteration provided that its respective amplitude is positive \note{this is a description of how you remove modes, but it is a bit confusing}.
-Should we converge upon a negative amplitude, that mode is discarded and the iteration is repeated. 
+Given a fixed time step, there are now $N$ amplitudes to solve for and $N$ eigenvalues to keep marginally-stable. 
+In general, we expect a function $\vec{\omega} \, : \, \mathbb{R}^N \to  \mathbb{R}^N$ to have isolated roots (should they exist). 
+To approximate the appropriate amplitude vector $\vec{A^2}$ we assume that for small time steps, diffusion and advection act independently (just as before).
+We represent the influences of $N$ modes with the linear system
+\begin{equation}
+    \vec{\omega}_{\rm{diff}} \approx \Omega_{\rm{adv}} \vec{A^2}
+    \label{EQ:AN_approx}
+\end{equation}
+where $\vec{\omega}_{\rm{diff}}$ is the vector of previously marginally-stable eigenvalues obtained by solving the EVP with a diffused mean temperature profile. 
+$\Omega_{\rm{adv}} \in \mathbb{R}^{N \times N}$ is the Jacobian matrix of eigenvalues' partial derivatives with respect to the amplitudes (ignoring diffusion and centered at $\vec{A^2} = \vec{0}$).
+The $k$th row of $\Omega_{\rm{adv}}$ is then given by the gradient of the $k$th mode's eigenvalue $\nabla \omega_k$.
+We perform $N$ periods of advection (one for each mode) followed by EVP solves to approximate $\Omega_{\rm{adv}}$ via first-order finite differences. 
+In this way, an arbitrary element of $\Omega_{\rm{adv}}$ represents how a particular mode's eigenvalue responds to the advection of another mode. 
+Solving \eq{EQ:AN_approx} gives a mediocre estimate for $\vec{A^2}$. 
+We refine our estimate by constructing a new Jacobian matrix via first-order finite differences at the point of our initial estimate (this time including diffusion).
+The Jacobian is updated with each guess according to Broyden's method for root-finding in multi-dimensional functions \cite{Broyden}.
+We find $\vec{\omega}(\vec{A^2})$ does indeed have a unique root provided the time step is not too large and there are no numerical instabilities, as outlined in appendix \ref{sec:timestep}.
+Presumably this is due the dependence of $W(z)$ and $\theta(z)$ on $\bar{T}$.
+Over the course of a large time step, $\bar{T}$ evolves according to \eq{EQ:T0_IVP} and the eigenfunctions might cease to provide a stabilizing influence.
+
+Difficulty arises when transitioning between different numbers of marginal modes, particularly when stable modes become marginally-stable mid-iteration.
+We facilitate these transitions by defining an adjustable candidate tolerance $\varepsilon_{\rm{cand}} \in [10^{-6}, 10^{-8}]$.
+We rely on $A^2 > 0$ by asserting that a mode which meets the candidate tolerance can be included in an iteration provided that its respective amplitude is positive.
+Should that be the case, the candidate mode is now marginally-stable and included in the subsequent iteration.
+If however we converge on a negative amplitude, the candidate mode is discarded and the iteration is repeated. 
 %In general we find that no other obvious course of action yields equilibria.
 
+After several time steps, $\bar{T}$ tends to asymmetrize due to numerical noise. 
+Though asymmetric pairs of solutions may exist, we further constrain $\bar{T}$ by imposing symmetry. 
+This is accomplished at the start of each iteration by setting the coefficients of even Chebyshev polynomials to zero.
+
 \section{Properties of Thermally Equilibrated States}\label{sec:properties}
-We evolve $\bar{T}$ as described above until $\partial_t\bar{T}\approx 0$ \note{what is your criterion for equilibrium?}.
+We evolve $\bar{T}$ as described above until $|\partial_{t}\bar{T}| < 10^{-5}$.
 In this marginally-stable thermal equilibrium, $\bar{T}$ does not evolve in time, and the perturbations also do not evolve in time, as they are marginally stable.
 Thus, these configurations are exact solutions to the quasilinear equations (equations~\ref{EQ:T0_IVP}--\ref{EQ:linear3}).
-They differ from the usual ECS in that ECS are fixed points of the full nonlinear problem (\ref{EQ:motion1})--(\ref{EQ:motion3}). 
+They differ from the usual ECS in that ECS are fixed points of the full nonlinear problem \eqss{EQ:motion1}{EQ:motion3}. 
 Such definitions are not mutually exclusive, but in general we can assume that MSTE and ECS are not steady with respect to their counterparts' equations.
-We compute symmetric MSTE for $Ra$ in the range $10^5 - 10^9$ \note{Somewhere you need to state we impose symmetry on the temperature field... this should got in section 3}.
+We compute symmetric MSTE for $\Ra$ in the range $10^5 - 10^9$.
 
@@
 \end{align}
-This height corresponds to the local extrema of the MSTE temperature profile, e.g., in Figure \ref{fig:T0_profiles}
+This height corresponds to the local extrema of the MSTE temperature profile, e.g., in Figure \ref{fig:T0_profiles}.
 In Figure \ref{fig:del_inv}, we show $\max \{ k_x\}$ is proportional to $\delta$ over our range of $\Ra$.
@@
     \Big\langle \frac{\partial T}{\partial x} \cdot \frac{\partial T}{\partial x} \Big\rangle_{\mathcal{D}} &\propto \Big\langle \frac{\partial T}{\partial z} \cdot \frac{\partial T}{\partial z} \Big\rangle_{\mathcal{D}}    \\
-    \Big\langle \frac{\partial \mathbf{u}}{\partial x} \cdot \frac{\partial \mathbf{u}}{\partial x} \Big\rangle_{\mathcal{D}} &\propto \Big\langle \frac{\partial \mathbf{u}}{\partial z} \cdot \frac{\partial \mathbf{u}}{\partial z} \Big\rangle_{\mathcal{D}}.
+    \Big\langle \frac{\partial \vec{u}}{\partial x} \cdot \frac{\partial \vec{u}}{\partial x} \Big\rangle_{\mathcal{D}} &\propto \Big\langle \frac{\partial \vec{u}}{\partial z} \cdot \frac{\partial \vec{u}}{\partial z} \Big\rangle_{\mathcal{D}}.
 \end{align*}
@@
 \end{equation*}
-\note{I'm giving the full Nu definition here so it's clear what's reported later in the simulations.}
 There is no general consensus surrounding the scaling behavior of $\Nu$ for high $\Ra$ systems, which are of particular importance in astrophysical and geophysical systems.
@@
 
-\section{Simulations with Thermally Equilibrated Initial Conditions}
+\section{Simulations with Thermally Equilibrated Initial Conditions}\label{sec:sims}
 This investigation is partially motivated by the prospect of decreasing DNS runtimes by employing MSTE as initial conditions. 
@@
     T(x, z)\big|_{t=0} &= 0.5 - z + N \nonumber \\
-    \mathbf{u}(x, z)\big|_{t=0} &= \mathbf{0} \nonumber \\
+    \vec{u}(x, z)\big|_{t=0} &= \vec{0} \nonumber \\
     p(x, z)\big|_{t=0} &= 0 \label{EQ:linear_ic}
@@
     T(x, z)\big|_{t=0} &= \bar{T}(z) + \sqrt{2} \sum_{n=1}^N  A_n \text{ Re} \Big[ \theta_n(z) e^{ik_{x_n}x} \Big] \nonumber \\
-    \mathbf{u}(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A_n \text{ Re} \Big[\Big( U_n (z) \hat{x} + W_n(z) \hat{z} \Big) e^{ik_{x_n}x} \Big] \nonumber\\
+    \vec{u}(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A_n \text{ Re} \Big[\Big( U_n (z) \hat{x} + W_n(z) \hat{z} \Big) e^{ik_{x_n}x} \Big] \nonumber\\
     p(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A_n \text{ Re} \Big[P_n (z) e^{ik_{x_n}x}\Big] \label{EQ:mste_ic}
@@
 They also exhibit unique and unexpected features: mean temperature gradient-reversals/dips, high kinetic energy flows, and a larger $\Nu$ than other time-invariant solutions. 
-When initializing with different mean temperature profile, we found the the same MSTE, suggesting these equilibria might be unique.
+When initializing with different mean temperature profiles, we found the same MSTE, suggesting these equilibria might be unique.
 
-Simulations initialized with the MSTE \eq{EQ:mste_ic} do not undergo an early convective transient period, but have faster flows and greater $\Nu$ when compared with DNS.
-\note{Do they have larger Nu?
-It looks like it's the same in the plot!!}
-From a dynamical systems perspective, unstable orbits depart from MSTE and approach the global attractor on a viscous time-scale \note{Still reading about this}.
+Simulations initialized with the MSTE \eq{EQ:mste_ic} do not undergo an early convective transient period, but have faster flows when compared with DNS.
+From a dynamical systems perspective, unstable orbits depart from MSTE and approach the global attractor on a viscous time-scale.
 This requires more computational effort to achieve relaxation when compared to the conventional conductive initial condition \eq{EQ:linear_ic}.
@@
 We also observed that MSTE have marginally stable boundary layers, so it would be reasonable to place a hypothetical stability constraint on MUTE based on boundary layer approximations.
-By definition, MUTE are unstable and would likely admit more diffuse boundary layer structures, requiring smaller $A^2(t)$ (less advection) to satisfy the stability constraint and thereby reducing $\Nu$, $\langle |\mathbf{u}|^2 \rangle_{\mathcal{D}}$ and possibly $\beta$.
+By definition, MUTE are unstable and would likely admit more diffuse boundary layer structures, requiring smaller $A^2(t)$ (less advection) to satisfy the stability constraint and thereby reducing $\Nu$, $\langle |\vec{u}|^2 \rangle_{\mathcal{D}}$ and possibly $\beta$.
 

### 2021-04-20 plot_flux.py

@@ -75,7 +75,7 @@ def plot_flux(Rayleigh, ax, path, iteration):
         ax.set_yticks([0.000, 0.001, 0.002, 0.003])
         # ax.set_ylim(-0.0002, 0.0039)
         ax.legend(prop={'size': 7.5}, frameon=False, loc='center right', bbox_to_anchor=(0.52, 0.25, 0.5, 0.5))
-        ax.set_title(r'$Ra \, = \, 10^9$')
+        ax.set_title(r'$\rm{Ra} \, = \, 10^9$')
         # plt.title('Heat Flux')
         ax.set_xlabel(r'$z$')
         ax.set_ylabel('Flux')
@@ -98,7 +98,7 @@ def plot_flux(Rayleigh, ax, path, iteration):
         ax.plot(z, flux, label = 'Total', color='black')
         ax.set_xlim(-0.5, 0.0)
         ax.legend(frameon=False, loc='center right')
-        ax.set_title(r'$Ra \, = \, 2 \times  10^5$')
+        ax.set_title(r'$\rm{Ra} \, = \, 2 \times  10^5$')
         ax.set_xlabel(r'$z$')
         ax.set_ylabel('Flux')
         # plt.title('Heat Flux (Iteration ' + str(self.iteration) + ')')

### 2021-04-20 publication_settings.py
misc. changes: omega <-> sigma

@@ -19,13 +19,15 @@ params = {#'backend': 'eps',
           'font.family':'serif',
           #'text.fontsize': 8,
           'font.size':8,
-          'font.serif': 'stix',
+          'font.serif': [],
+          'font.sans-serif': ['DejaVu Sans'],
           'mathtext.fontset' : 'stix',
+        #   'text.usetex' : True,
           'legend.fontsize': 8,
           'legend.markerscale': 1,
           'xtick.labelsize': 10,
           'ytick.labelsize': 10,
-          'text.usetex': True,
+#          'text.usetex': True,
           'figure.figsize': fig_size,
           'figure.dpi': 600,
           'lines.markersize':3,

### 2021-04-20 plot_flux.py
figs: font consistency

@@ -65,7 +65,7 @@ def plot_flux(Rayleigh, ax, path, iteration):
         pi_mult3 = str(round(kx3/np.pi, 1))
         pi_mult4 = str(round(kx4/np.pi, 1))
         pi_mult5 = str(round(kx5/np.pi, 1))
-        ax.plot(z, advection1, label = r'$\langle w\' T\' \rangle (k_x  = $' + pi_mult1 + r'$\pi$)')
+        ax.plot(z, advection1, label = 'Advection ($k_x  = $' + pi_mult1 + '$\pi$)')
         ax.plot(z, advection2, label = 'Advection ($k_x  = $' + pi_mult2 + '$\pi$)')
         ax.plot(z, advection3, label = 'Advection ($k_x  = $' + pi_mult3 + '$\pi$)')
         ax.plot(z, advection4, label = 'Advection ($k_x  = $' + pi_mult4 + '$\pi$)')
@@ -75,7 +75,7 @@ def plot_flux(Rayleigh, ax, path, iteration):
         ax.set_yticks([0.000, 0.001, 0.002, 0.003])
         # ax.set_ylim(-0.0002, 0.0039)
         ax.legend(prop={'size': 7.5}, frameon=False, loc='center right', bbox_to_anchor=(0.52, 0.25, 0.5, 0.5))
-        ax.set_title(r'$Ra \, = \, 10^9$')
+        ax.set_title(r'$\rm{Ra} \, = \, 10^9$')
         # plt.title('Heat Flux')
         ax.set_xlabel(r'$z$')
         ax.set_ylabel('Flux')
@@ -98,7 +98,7 @@ def plot_flux(Rayleigh, ax, path, iteration):
         ax.plot(z, flux, label = 'Total', color='black')
         ax.set_xlim(-0.5, 0.0)
         ax.legend(frameon=False, loc='center right')
-        ax.set_title(r'$Ra \, = \, 2 \times  10^5$')
+        ax.set_title(r'$\rm{Ra} \, = \, 2 \times  10^5$')
         ax.set_xlabel(r'$z$')
         ax.set_ylabel('Flux')
         # plt.title('Heat Flux (Iteration ' + str(self.iteration) + ')')
@@ -131,7 +131,7 @@ plot_flux(ra2, axs[1], path2, iteration2)
 plt.subplots_adjust(right=1.0)
 # fig.text(0.00, 0.5, 'Flux', ha='center', va='center', rotation='vertical', fontsize=10)
[…]

### 2021-04-20 plot_ke.py

@@ -56,6 +56,7 @@ if __name__ == "__main__":
     global path 
     path = os.path.dirname(os.path.abspath(__file__))
     write_data = False
+    plot = True
     if (write_data):
         args = docopt(__doc__)
         output_path = pathlib.Path(args['--output']).absolute()
@@ -68,7 +69,7 @@ if __name__ == "__main__":
                 if not output_path.exists():
                     output_path.mkdir()
         post.visit_writes(args['<files>'], main, output=output_path)
-    else:
+    if (plot):
         ke_data_eq = pickle.load(open(path + '/ke_data_eq2.pick', 'rb'))
         ke_data = pickle.load(open(path + '/ke_data_nom.pick', 'rb'))
 
@@ -83,6 +84,6 @@ if __name__ == "__main__":
         plt.legend(frameon=False)
         plt.xlabel(r'$t$')
         plt.ylabel(r'$\langle |\mathbf{u}|^2 \rangle_{\mathcal{D}}$')
-        plt.title(r'$Ra \, = \, 10^8$')
-        plt.savefig(path + '/publication_materials/sim_eq_ke')
+        plt.title(r'$\rm{Ra} \, = \, 10^8$')
+        plt.savefig(path + '/publication_materials/sim_eq_ke_nonoise')
         # plt.savefig(path + '/publication_materials/sim_eq_ke_p0_2')

### 2021-04-20 plot_nu.py

@@ -115,6 +115,6 @@ if __name__ == "__main__":
         plt.legend(frameon=False)
         plt.xlabel(r'$t$')
         plt.ylabel(r'$\mathrm{Nu}$')
-        plt.title(r'$Ra \, = \, 10^8$')
+        plt.title(r'$\rm{Ra} \, = \, 10^8$')
         # plt.savefig(path + '/pubfigs/sim_eq_nu')
         plt.savefig(path + '/publication_materials/sim_eq_nu')

### 2021-04-20 plot_spectra_2ra.py

@@ -75,7 +75,7 @@ path = os.path.dirname(os.path.abspath(__file__))
 dir1 = path + '/RA2E5/results_conv/Iteration13597'
 dir2 = path + '/RA1E9/results/Iteration12638'
 iteration_strs_dir = [dir1, dir2]
-labels = [r'$Ra \, = \, 2 \times 10^5$', r'$Ra \, = \, 10^9$']
+labels = [r'$\rm{Ra} \, = \, 2 \times 10^5$', r'$\rm{Ra} \, = \, 10^9$']
 ev_mat = []
 for i, iteration_str in enumerate(iteration_strs_dir):
     evs = pickle.load(open(iteration_str + '/evs.pick', 'rb'))

### 2021-04-20 rbc_sim_load_ic.py

@@ -135,7 +135,8 @@ if not pathlib.Path('restart.h5').exists():
     b0z_f.set_scales(1)
     b0 = b0z_f.antidifferentiate(z_basis, ('left', 0))
     b0.set_scales(evp_scale)
-    b['g'] = b0['g'] + np.sqrt(2)*(sum([exp*fields['b'][:, None][slices[1]].transpose() for (exp, fields) in exp_fields])).real + F * pert
+    b['g'] = b0['g'] + np.sqrt(2)*(sum([exp*fields['b'][:, None][slices[1]].transpose() for (exp, fields) in exp_fields])).real
+    # b['g'] = b0['g'] + np.sqrt(2)*(sum([exp*fields['b'][:, None][slices[1]].transpose() for (exp, fields) in exp_fields])).real + F * pert
     bz = b.differentiate('z')
     # plot_bot_2d(b)
     # plt.show()
@@ -180,13 +181,13 @@ solver.stop_sim_time = stop_sim_time
 # snapshots.add_task('w')
 # snapshots.add_task('u')
 
-profiles = solver.evaluator.add_file_handler('profiles_eq_p0', sim_dt=0.1, max_writes=100, mode=fh_mode)
-profiles.add_task("P*integ(dz(b) - 1, 'x') / Lx", name='diffusive_flux')
-profiles.add_task("integ(w*b, 'x') / Lx", name='adv_flux')
-profiles.add_task("integ(integ(w**2 + u**2, 'x'), 'z') / Lx", name='ke')
-profiles.add_task("integ(integ((dx(w) - uz)**2, 'x'), 'z') / Lx", name='enst')
+# profiles = solver.evaluator.add_file_handler('profiles_nonoise', sim_dt=0.1, max_writes=100, mode=fh_mode)
+# profiles.add_task("P*integ(dz(b) - 1, 'x') / Lx", name='diffusive_flux')
+# profiles.add_task("integ(w*b, 'x') / Lx", name='adv_flux')
+# profiles.add_task("integ(integ(w**2 + u**2, 'x'), 'z') / Lx", name='ke')
+# profiles.add_task("integ(integ((dx(w) - uz)**2, 'x'), 'z') / Lx", name='enst')
 
-checkpoints = solver.evaluator.add_file_handler('checkpoints_eq_p0', sim_dt=0.5, max_writes=50, mode=fh_mode)
[…]

### 2021-04-20 publication_materials/ms_rbc.tex

@@
 \end{align}
-where $A$ is the (undetermined) mode amplitude, $s = \sigma + i\omega$ and $k_x$ is constrained, by periodicity, to the countably infinite set (spectrum) of wavenumbers
+where $A$ is the (undetermined) mode amplitude, $s = \omega + i\sigma$ and $k_x$ is constrained, by periodicity, to the countably infinite set (spectrum) of wavenumbers
 \begin{align}
@@
 \end{equation}
-For each $k_x$, we can assess the stability of the perturbations by solving for the eigenvalue $s$, whose imaginary component $\omega$ plays the role of an exponential growth rate. 
+For each $k_x$, we can assess the stability of the perturbations by solving for the eigenvalue $s$, whose imaginary component $\sigma$ plays the role of an exponential growth rate. 
 Positive eigenvalues indicate that the system is unstable to small disturbances of wavenumber $k_x$, while negative eigenvalues indicate stability. 
@@
 \begin{equation}
-    \max_{k_x} \{ \omega \} = 0.
+    \max_{k_x} \{ \sigma \} = 0.
 \end{equation}
@@
 \begin{equation}
-    A^2 \approx -\frac{\omega_{\rm{diff}}}{\omega_{\rm{adv}}} \label{EQ:amp_approx}
+    A^2 \approx -\frac{\sigma_{\rm{diff}}}{\sigma_{\rm{adv}}} \label{EQ:amp_approx}
 \end{equation}
-where $\omega_{\rm{diff}}$ and $\omega_{\rm{adv}}$ refer to the diffused and advected eigenvalues of the initially marginal mode.
+where $\sigma_{\rm{diff}}$ and $\sigma_{\rm{adv}}$ refer to the diffused and advected eigenvalues of the initially marginal mode.
 We illustrate these trends in Figure~\ref{fig:iteration_spectra}. 
 $\bar{T}(z, t)$ is then evolved according to \eq{EQ:T0_IVP} and another eigenvalue solve is performed. 
-Given a fixed timestep $\Delta t$, we assume the dominant eigenvalue can be described by a continuous function $\omega_{\rm{max}} (A^2)$ which is locally differentiable. 
-We use Newton's method to find an amplitude which satisfies our marginal stability tolerance criterion $|\omega_{\rm{max}} (A^2)| < 10^{-9}$.
+Given a fixed timestep $\Delta t$, we assume the dominant eigenvalue can be described by a continuous function $\sigma_{\rm{max}} (A^2)$ which is locally differentiable. 
+We use Newton's method to find an amplitude which satisfies our marginal stability tolerance criterion $|\sigma_{\rm{max}} (A^2)| < 10^{-9}$.
 Crucially, we do not assume the $k_x$ of the marginally-stable is fixed.
@@
 where $W_n$ and $\theta_n$ are the eigenmodes associated with $k_x = \frac{n\pi}{2}$. 
-Given a fixed time step, there are now $N$ amplitudes to solve for and $N$ eigenvalues to keep marginally-stable. 
-In general, we expect a function $\vec{\omega} \, : \, \mathbb{R}^N \to  \mathbb{R}^N$ to have isolated roots (should they exist). 
-To approximate the appropriate amplitude vector $\vec{A^2}$ we assume that for small time steps, diffusion and advection act independently (just as before).
-We represent the influences of $N$ modes with the linear system
+There are now $N$ amplitudes to solve for and $N$ eigenvalues to keep marginally-stable. 
+Given a fixed time step $\Delta t$, let $\vec{A^2}$ be the amplitude vector and $\vec{\sigma}(\vec{A^2})$ be the dependent eigenvalues.
+We expect a function $\vec{\sigma} \, : \, \mathbb{R}^N \to  \mathbb{R}^N$ to have isolated roots $\vec{A^2_m}$ (should they exist). 
+The appropriate amplitude vector $\vec{A^2_m}$ can be approximated by a generalized form of \eq{EQ:amp_approx}:
 \begin{equation}
-    \vec{\omega}_{\rm{diff}} \approx \Omega_{\rm{adv}} \vec{A^2}
+    \vec{A^2_m} \approx -\Sigma_{\rm{adv}}^{-1} \vec{\sigma_{\rm{diff}}}.
     \label{EQ:AN_approx}
 \end{equation}
-where $\vec{\omega}_{\rm{diff}}$ is the vector of previously marginally-stable eigenvalues obtained by solving the EVP with a diffused mean temperature profile. 
-$\Omega_{\rm{adv}} \in \mathbb{R}^{N \times N}$ is the Jacobian matrix of eigenvalues' partial derivatives with respect to the amplitudes (ignoring diffusion and centered at $\vec{A^2} = \vec{0}$).
-The $k$th row of $\Omega_{\rm{adv}}$ is then given by the gradient of the $k$th mode's eigenvalue $\nabla \omega_k$.
-We perform $N$ periods of advection (one for each mode) followed by EVP solves to approximate $\Omega_{\rm{adv}}$ via first-order finite differences. 
-In this way, an arbitrary element of $\Omega_{\rm{adv}}$ represents how a particular mode's eigenvalue responds to the advection of another mode. 
-Solving \eq{EQ:AN_approx} gives a mediocre estimate for $\vec{A^2}$. 
-We refine our estimate by constructing a new Jacobian matrix via first-order finite differences at the point of our initial estimate (this time including diffusion).
-The Jacobian is updated with each guess according to Broyden's method for root-finding in multi-dimensional functions \cite{Broyden}.
-We find $\vec{\omega}(\vec{A^2})$ does indeed have a unique root provided the time step is not too large and there are no numerical instabilities, as outlined in appendix \ref{sec:timestep}.
-Presumably this is due the dependence of $W(z)$ and $\theta(z)$ on $\bar{T}$.
+Here $\vec{\sigma_{\rm{diff}}} = \vec{\sigma} (\vec{0})$ refers to the eigenvalues after a brief $\Delta t$ period of diffusion. 
+$\Sigma_{\rm{adv}} \in \mathbb{R}^{N \times N}$ is the matrix of eigenvalues after $N$ $\Delta t$ periods of advection (one for each mode).
+% The $k$th row of $J_0$ is then given by the gradient of the $k$th mode's eigenvalue $\nabla \sigma_k$.
+In this way, an arbitrary element of $\sigma_{\rm{adv}}$ represents how a particular mode's eigenvalue responds to the advection of another mode. 
+Solving \eq{EQ:AN_approx} gives a coarse estimate for $\vec{A^2_m}$. 
+We refine our estimate by approximating the Jacobian matrix of $\vec{\sigma}(\vec{A^2})$ via first-order finite differences at the point of our coarse estimate.
+This involves $N^2$ more individual EVP solves.
+After its construction, the Jacobian is updated with each guess according to Broyden's method for root-finding in multi-dimensional functions \cite{Broyden}.
+We find $\vec{\sigma}(\vec{A^2})$ does indeed have a unique root provided the time step is not too large and there are no numerical instabilities, as outlined in appendix \ref{sec:timestep}.
+Presumably this is due to the dependence of $W(z)$ and $\theta(z)$ on $\bar{T}$.
 Over the course of a large time step, $\bar{T}$ evolves according to \eq{EQ:T0_IVP} and the eigenfunctions might cease to provide a stabilizing influence.
@@
 The $k_x = 1.5\pi$ mode forms the large-scale convective cell structures observed in DNS, again occupying the bulk of the domain.
-The pairs of modes $k_x = 6\pi, \, 6.5\pi$ and $k_x=23.5\pi, \, 24\pi$ are each associated with a single maximum in our plots of growth rate $\omega$ as a function of $k_x$ (lower right panel of Figure~\ref{fig:flux}).
+The pairs of modes $k_x = 6\pi, \, 6.5\pi$ and $k_x=23.5\pi, \, 24\pi$ are each associated with a single maximum in our plots of growth rate $\sigma$ as a function of $k_x$ (lower right panel of Figure~\ref{fig:flux}).
 If we allowed wavenumbers to vary continuously, there would be an unstable mode between these pairs of wavenumbers.
@@
 Your call.}
-More precisely, instead of traversing the manifold of marginally-stable states toward MSTE, we could consider the manifold of states whose maximum eigenvalue(s) $\omega_{\rm{max}}$ agree with some other stability constraint.
+More precisely, instead of traversing the manifold of marginally-stable states toward MSTE, we could consider the manifold of states whose maximum eigenvalue(s) $\sigma_{\rm{max}}$ agree with some other stability constraint.
 Note that under this definition, ECS are themselves MUTE, because they are thermally-equilibrated and generally unstable, though they need not satisfy the quasilinear form.

### 2021-04-20 publication_materials/ms_rbc.tex
IVP error

@@
 \begin{equation}
-  \frac{\partial \bar{T}}{\partial t} + \langle w'T' \rangle_x = \mathcal{P}  \frac{\partial^2 \bar{T}}{\partial z^2}, \label{EQ:T0_IVP}
+  \frac{\partial \bar{T}}{\partial t} + \frac{\partial}{\partial z} \langle w'T' \rangle_x = \mathcal{P} \frac{\partial^2 \bar{T}}{\partial z^2}, \label{EQ:T0_IVP}
 \end{equation}
@@
 We also observed that MSTE have marginally stable boundary layers, so it would be reasonable to place a hypothetical stability constraint on MUTE based on boundary layer approximations.
-By definition, MUTE are unstable and would likely admit more diffuse boundary layer structures, requiring smaller $A^2(t)$ (less advection) to satisfy the stability constraint and thereby reducing $\Nu$, $\langle |\vec{u}|^2 \rangle_{\mathcal{D}}$ and possibly $\beta$.
+By definition, MUTE are unstable and would likely admit more diffuse boundary layer structures, requiring smaller $A^2$ (less advection) to satisfy the stability constraint and thereby reducing $\Nu$, $\langle |\vec{u}|^2 \rangle_{\mathcal{D}}$ and possibly $\beta$.
 

### 2021-04-21 plot_ke.py
figs: ke final

@@ -85,5 +85,5 @@ if __name__ == "__main__":
         plt.xlabel(r'$t$')
         plt.ylabel(r'$\langle |\mathbf{u}|^2 \rangle_{\mathcal{D}}$')
         plt.title(r'$\rm{Ra} \, = \, 10^8$')
-        plt.savefig(path + '/publication_materials/sim_eq_ke_nonoise')
-        # plt.savefig(path + '/publication_materials/sim_eq_ke_p0_2')
+        # plt.savefig(path + '/publication_materials/sim_eq_ke_nonoise')
+        plt.savefig(path + '/publication_materials/sim_eq_ke')

### 2021-04-21 plot_spectra_2ra.py
fig: spectrum 2

@@ -60,7 +60,7 @@ def plot_EVs(evs_mat, labels):
         ax.grid(False)
         ax.axhline(y=0.0, color='black', alpha=0.2)
         ax.set_xlabel(r'$k_x$')
-        ax.set_ylabel(r'$\omega$')
+        ax.set_ylabel(r'$\sigma$')
         ax.yaxis.set_major_formatter(FormatStrFormatter('%.4f'))
 
     plt.tight_layout()

### 2021-04-21 publication_materials/ms_rbc.tex
rev3a?

@@
 Any system of this form can be characterized by its dimensionless Rayleigh number $\Ra = \frac{g\alpha L^3 \Delta T}{\nu \kappa}$ and Prandtl number $\Pr = \frac{\nu}{\kappa}$, where $g, \, \alpha, \, L, \, \Delta T, \nu, \kappa$ are the gravitational acceleration, coefficient of thermal expansion, domain height, opposed temperature difference, kinematic viscosity, and thermal diffusivity respectively.
+In this paper, we fix $\Pr = 1$.
 For convenience, we define
@@
 We use Newton's method to find an amplitude which satisfies our marginal stability tolerance criterion $|\sigma_{\rm{max}} (A^2)| < 10^{-9}$.
+Marginally-stable modes do not osscillate in time, i.e. $\sigma = 0$ implies $\omega = 0$.
+This agrees with the convectional notion of exchange of stabilities \cite{drazin_reid_2004}.
 Crucially, we do not assume the $k_x$ of the marginally-stable is fixed.
@@
 There are now $N$ amplitudes to solve for and $N$ eigenvalues to keep marginally-stable. 
-Given a fixed time step $\Delta t$, let $\vec{A^2}$ be the amplitude vector and $\vec{\sigma}(\vec{A^2})$ be the dependent eigenvalues.
+Given a small fixed time step $\Delta t$, let $\vec{A^2}$ be the amplitude vector and $\vec{\sigma}(\vec{A^2})$ be the dependent eigenvalues.
 We expect a function $\vec{\sigma} \, : \, \mathbb{R}^N \to  \mathbb{R}^N$ to have isolated roots $\vec{A^2_m}$ (should they exist). 
@@
 In Figure \ref{fig:del_inv}, we show $\max \{ k_x\}$ is proportional to $\delta$ over our range of $\Ra$.
+Least-squares regression gives $\delta^{-1} = 1.71 \max \{ k_x \} - 2.13$.
 We can assume from this length scale agreement that the mean-squared $x$ and $z$ components of the temperature and velocity gradients are proportional
-\begin{align*}
-    \Big\langle \frac{\partial T}{\partial x} \cdot \frac{\partial T}{\partial x} \Big\rangle_{\mathcal{D}} &\propto \Big\langle \frac{\partial T}{\partial z} \cdot \frac{\partial T}{\partial z} \Big\rangle_{\mathcal{D}}    \\
+\begin{align}
+    \Big\langle \frac{\partial T}{\partial x} \cdot \frac{\partial T}{\partial x} \Big\rangle_{\mathcal{D}} &\propto \Big\langle \frac{\partial T}{\partial z} \cdot \frac{\partial T}{\partial z} \Big\rangle_{\mathcal{D}} \nonumber   \\
     \Big\langle \frac{\partial \vec{u}}{\partial x} \cdot \frac{\partial \vec{u}}{\partial x} \Big\rangle_{\mathcal{D}} &\propto \Big\langle \frac{\partial \vec{u}}{\partial z} \cdot \frac{\partial \vec{u}}{\partial z} \Big\rangle_{\mathcal{D}}.
-\end{align*}
+\end{align}
 This is consistent with the mean squared gradient assumptions of \cite{Malkus_1954}.
@@
 The Nusselt number, which measures convective performance is given by
-\begin{equation*}
+\begin{equation}
     \Nu = \frac{\langle \langle w'T' \rangle_x - \mathcal{P}\frac{\partial \bar{T}}{\partial z} \rangle_z}{\langle- \mathcal{P}\frac{\partial \bar{T}}{\partial z} \rangle_z}.
-\end{equation*}
+\end{equation}
 There is no general consensus surrounding the scaling behavior of $\Nu$ for high $\Ra$ systems, which are of particular importance in astrophysical and geophysical systems.
@@
 Here we instead initialize using the MSTE,
-\note{This needs to be updated}
 \begin{align}
-    T(x, z)\big|_{t=0} &= \bar{T}(z) + \sqrt{2} \sum_{n=1}^N  A_n \text{ Re} \Big[ \theta_n(z) e^{ik_{x_n}x} \Big] \nonumber \\
-    \vec{u}(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A_n \text{ Re} \Big[\Big( U_n (z) \hat{x} + W_n(z) \hat{z} \Big) e^{ik_{x_n}x} \Big] \nonumber\\
-    p(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A_n \text{ Re} \Big[P_n (z) e^{ik_{x_n}x}\Big] \label{EQ:mste_ic}
+    T(x, z)\big|_{t=0} &= \bar{T}(z) + \sum_{n=1}^N  A_n \Re \Big[ \theta_n(z) e^{ik_{x_n}x} \Big] + N \nonumber \\
+    \vec{u}(x, z)\big|_{t=0} &= \sum_{n=1}^N A_n \Re \Big[\Big( U_n (z) \hat{x} + W_n(z) \hat{z} \Big) e^{ik_{x_n}x} \Big] \nonumber\\
+    p(x, z)\big|_{t=0} &= \sum_{n=1}^N A_n \Re \Big[P_n (z) e^{ik_{x_n}x}\Big] \label{EQ:mste_ic}
 \end{align}
 where $\theta_n(z), U_n(z), W_n(z), P_n(z); \, A_n; $ and $k_{x_n}$ refer to the complex eigenfunctions, amplitude, and wavenumber at the $n$th marginal mode respectively. 
-The $\sqrt{2}$ factor is necessary for eigenfunction normalization. 
 Note that although the MSTE is an equilibrium of the quasilinear equations, it is not an equilibrium of the full nonlinear equations.
-\note{Say something about noise}
+\note{Say something about noise. Not sure if noise is important?}
 
@@
 We might curtail the disagreement between MSTE and DNS by adjusting our marginal-stability criterion. 
-Should the time scales not be entirely separate, we might anticipate the long-term persistance of moderately unstable modes. 
-Such an instability cannot be described by our model independently (we do not know, a priori, \textit{how unstable} the equilibria should be) but it might prove fruitful to investigate moderately unstable thermal equilibria (MUTE).
-\note{This is a bit too cute...
-Might be a risk for a reviewer?
-Your call.}
-More precisely, instead of traversing the manifold of marginally-stable states toward MSTE, we could consider the manifold of states whose maximum eigenvalue(s) $\sigma_{\rm{max}}$ agree with some other stability constraint.
-Note that under this definition, ECS are themselves MUTE, because they are thermally-equilibrated and generally unstable, though they need not satisfy the quasilinear form.
+Should the fast and slow time scales not be entirely separate, we might anticipate the long-term persistance of moderately unstable modes. 
+To find MSTE, we initialize the time-evolution algorithm with the analytic temperature profile derived by \cite{Shishkina}.
+This involves modifying the boundary layer thickness $\delta_0$ to achieve marginal stability.
 
-\note{This last paragraph is somewhat confusing to me.
-I think it's dangerous to say that we can predict Nu-Ra scaling using anything other than DNS or experiments.
-Why would 1D boundary-layer predictions give 2D equilibria?
-Right now we're using a 1D boundary-layer prediction.}
-We cannot use our reduced quasilinear model to predict $\Nu \sim\Ra^{\beta}$ for large $\Ra$ without some complementary stability constraint. 
-The eigenvalues of DNS data might provide an informative stability constraint (we could find MUTE and compare them with DNS data), but this would be self-defeating in general. 
-Instead we seek to combine reduced models to approximate $\beta$ without DNS.
-Under the marginal-stability constraint, we found that MSTE exhibit classical Malkus scaling, having marginally-stable boundary layers.
-We could instead require that the eigenvalues of MUTE agree with the eigenvalues of the analytic 1D boundary layer predictions of \cite{Shishkina, Zhang_20} (which remain in development), allowing us to refine and expand these estimates into 2D MUTE.
-The process for finding such MUTE would not involve DNS. Equilibria would satisfy only the quasilinear problem and stability constraint. 
-They ought to agree with DNS data more than MSTE, ideally having slower flows. 
-This is reasonable to expect because accurate boundary layer approximations and DNS data should have similar stability characteristics. 
-We also observed that MSTE have marginally stable boundary layers, so it would be reasonable to place a hypothetical stability constraint on MUTE based on boundary layer approximations.
-By definition, MUTE are unstable and would likely admit more diffuse boundary layer structures, requiring smaller $A^2$ (less advection) to satisfy the stability constraint and thereby reducing $\Nu$, $\langle |\vec{u}|^2 \rangle_{\mathcal{D}}$ and possibly $\beta$.
+Instead of imposing marginal stability, we can use quasilinear model to thermally-equilibrate and expand 1D approximations into 2D.
+As previously noted, there is no shortage of theories pertaining to the scaling behavior $\Nu \sim \Ra^{\beta}$ \cite{Malkus_1954, Howard_1966, Kraichnan, Spiegel, Castaing, Grossman, Ahlers}.
+For large $\Ra$, we can approximate $\delta_0 \approx \Nu^{-1}$ and construct a 1D temperature profile according to \eq{EQ:T0} or some other approximation.
+In this way, other 2D quasilinear thermal equilibria can be obtained and analyzed.
 
@@
 % \begin{multicols}{1}
-\subsection{MSTE Metrics}\label{sec:tables}
+\section{MSTE Metrics}\label{sec:tables}
 \begin{longtable*}{cccccc}

### 2021-04-21 publication_materials/ms_rbc.tex
rev3ai
rev3aii

@@
 We expect a function $\vec{\sigma} \, : \, \mathbb{R}^N \to  \mathbb{R}^N$ to have isolated roots $\vec{A^2_m}$ (should they exist). 
-The appropriate amplitude vector $\vec{A^2_m}$ can be approximated by a generalized form of \eq{EQ:amp_approx}:
+A coarse approximation for the appropriate amplitude vector $\vec{A^2_m}$ is given by a generalized form of \eq{EQ:amp_approx}:
 \begin{equation}
@@
 Here $\vec{\sigma_{\rm{diff}}} = \vec{\sigma} (\vec{0})$ refers to the eigenvalues after a brief $\Delta t$ period of diffusion. 
-$\Sigma_{\rm{adv}} \in \mathbb{R}^{N \times N}$ is the matrix of eigenvalues after $N$ $\Delta t$ periods of advection (one for each mode).
+$\Sigma_{\rm{adv}} \in \mathbb{R}^{N \times N}$ is the matrix of eigenvalues after $N$ periods of advection (one for each mode).
 % The $k$th row of $J_0$ is then given by the gradient of the $k$th mode's eigenvalue $\nabla \sigma_k$.
 In this way, an arbitrary element of $\sigma_{\rm{adv}}$ represents how a particular mode's eigenvalue responds to the advection of another mode. 
-Solving \eq{EQ:AN_approx} gives a coarse estimate for $\vec{A^2_m}$. 
-We refine our estimate by approximating the Jacobian matrix of $\vec{\sigma}(\vec{A^2})$ via first-order finite differences at the point of our coarse estimate.
-This involves $N^2$ more individual EVP solves.
+We then approximate the Jacobian matrix of $\vec{\sigma}(\vec{A^2})$ via first-order finite differences at the point of our coarse estimate, requiring $N^2$ more individual EVP solves.
 After its construction, the Jacobian is updated with each guess according to Broyden's method for root-finding in multi-dimensional functions \cite{Broyden}.
@@
 Note that although the MSTE is an equilibrium of the quasilinear equations, it is not an equilibrium of the full nonlinear equations.
-\note{Say something about noise. Not sure if noise is important?}
+Accordingly the simulation state would evolve on initialization absent a random noise term.
+Here we include noise as a source of asymmetries.
 

### 2021-04-21 publication_materials/ms_rbc.tex
Eigentools citation

@@
 The necessary number of basis functions varies, as eigenfunctions and temperature profiles associated with large $\Ra$ admit increasingly small-scale features. 
-We use the \texttt{Eigentools} package to manipulate the eigenfunctions and calculate the advective heat flux $\langle w' T' \rangle_x$ \note{cite eigentools}.
+We use the \texttt{Eigentools} package \cite{Eigentools} to manipulate the eigenfunctions and calculate the advective heat flux $\langle w' T' \rangle_x$.
 

### 2021-04-21 publication_materials/ms_rbc.tex
eigentools cite, broyden's method details

@@
 We expect a function $\vec{\sigma} \, : \, \mathbb{R}^N \to  \mathbb{R}^N$ to have isolated roots $\vec{A^2_m}$ (should they exist). 
-A coarse approximation for the appropriate amplitude vector $\vec{A^2_m}$ is given by a generalized form of \eq{EQ:amp_approx}:
+A coarse approximation $\vec{A^2_0}$ for the appropriate amplitude vector $\vec{A^2_m}$ is given by a generalized form of \eq{EQ:amp_approx}:
 \begin{equation}
-    \vec{A^2_m} \approx -\Sigma_{\rm{adv}}^{-1} \vec{\sigma_{\rm{diff}}}.
+    \vec{A^2_0} = -\Sigma_{\rm{adv}}^{-1} \vec{\sigma_{\rm{diff}}}.
     \label{EQ:AN_approx}
@@
 % The $k$th row of $J_0$ is then given by the gradient of the $k$th mode's eigenvalue $\nabla \sigma_k$.
-In this way, an arbitrary element of $\sigma_{\rm{adv}}$ represents how a particular mode's eigenvalue responds to the advection of another mode. 
-We then approximate the Jacobian matrix of $\vec{\sigma}(\vec{A^2})$ via first-order finite differences at the point of our coarse estimate, requiring $N^2$ more individual EVP solves.
-After its construction, the Jacobian is updated with each guess according to Broyden's method for root-finding in multi-dimensional functions \cite{Broyden}.
+In this way, an arbitrary element of $\Sigma_{\rm{adv}}$ represents how a particular mode's eigenvalue responds to the advection of another mode. 
+At the point of our coarse estimate $\vec{A^2_0}$, we approximate the Jacobian matrix 
+\begin{equation}
+    J = \begin{bmatrix}
+        \nabla \sigma_1 (A_1, A_2, ..., A_N) \\
+        \nabla \sigma_2 (A_1, A_2, ..., A_N) \\
+        \vdots \\
+        \nabla \sigma_N (A_1, A_2, ..., A_N) 
+    \end{bmatrix}
+\end{equation}
+via first-order finite differences, requiring $N^2$ more individual EVP solves.
+A refined estimate is then given by
+\begin{equation}
+    \vec{A^2_1} = -J^{-1} \vec{\sigma}(\vec{A^2_0}).
+\end{equation}
+Once constructed we use each subsequent guess to update the Jacobian iteratively according to Broyden's method for root-finding in multi-dimensional functions \cite{Broyden}.
 We find $\vec{\sigma}(\vec{A^2})$ does indeed have a unique root provided the time step is not too large and there are no numerical instabilities, as outlined in appendix \ref{sec:timestep}.
-Presumably this is due to the dependence of $W(z)$ and $\theta(z)$ on $\bar{T}$.
+Presumably this is due to the coupling of $W(z)$ and $\theta(z)$ with $\bar{T}$.
 Over the course of a large time step, $\bar{T}$ evolves according to \eq{EQ:T0_IVP} and the eigenfunctions might cease to provide a stabilizing influence.

### 2021-04-21 publication_materials/ms_rbc.tex
misc. broyden/jacobian discussion

@@
 \end{equation}
-Once constructed we use each subsequent guess to update the Jacobian iteratively according to Broyden's method for root-finding in multi-dimensional functions \cite{Broyden}.
+Once constructed, we use each subsequent guess to adjust the Jacobian via Broyden's method for root-finding in multi-dimensional functions \cite{Broyden}.
 We find $\vec{\sigma}(\vec{A^2})$ does indeed have a unique root provided the time step is not too large and there are no numerical instabilities, as outlined in appendix \ref{sec:timestep}.
-Presumably this is due to the coupling of $W(z)$ and $\theta(z)$ with $\bar{T}$.
-Over the course of a large time step, $\bar{T}$ evolves according to \eq{EQ:T0_IVP} and the eigenfunctions might cease to provide a stabilizing influence.
+Presumably this is due to the coupling of $\langle w'T' \rangle_x$ with $\bar{T}$.
+Over the course of a large time step, $\bar{T}$ evolves according to \eq{EQ:T0_IVP} and eventually the original eigenfunctions cease to provide a stabilizing influence.
 

### 2021-04-30 sim_figs.sh
no flow sim

@@ -1,0 +1,20 @@
+#PBS -S /bin/bash
+#PBS -N sim_figs0
+#PBS -l select=32:ncpus=28:mpiprocs=28:model=bro
+#PBS -l walltime=24:00:00
+#PBS -j oe
+module load mpi-sgi/mpt
+module load comp-intel
+export PATH=$HOME/scripts:$PATH
+deactivate
+unset PYTHONPATH
+source ~/miniconda3/etc/profile.d/conda.sh
+export PYTHONNOUSERSITE=1
+conda activate dedalus
+# support lots of text output to stdio for analysis
+export MPI_UNBUFFERED_STDIO=true
+cd ~/scratch/dedalus/EVP_evolution/
+mpiexec_mpt -np 896 python3 rbc_sim_load_ic.py
+mpiexec_mpt -np 896 python3 -m dedalus merge_procs checkpoints_nonoise
+mpiexec_mpt -np 896 python3 plot_slices.py checkpoints_nonoise/*.h5 --output=frames_nonoise
+mpiexec_mpt -np 896 python3 -m dedalus merge_procs profiles_nonoise

### 2021-04-30 publication_materials/ms_rbc.tex

@@
 \author{Daniel Lecoanet$^{1, 2}$}
-\author{Evan Anders$^2$}
+\author{Evan H. Anders$^2$}
 \affiliation{%
@@
     Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important properties remain elusive---particularly in the large Rayleigh number regime.
-    In this investigation, we derive and solve a quasilinear form of the Rayleigh-Benard problem by representing the perturbations in terms of marginally stable eigenmodes.
+    In this investigation, we derive and solve a quasilinear form of the Rayleigh-Bénard problem by representing the perturbations in terms of marginally stable eigenmodes.
     The amplitude of each eigenmode is determined by requiring that the background state maintains marginal stability.
@@
 Turbulent convection, which is associated with large Rayleigh numbers $\Ra$, is difficult to simulate. 
-State of the art simulations performed by \cite{Zhu_2018} have reached $\Ra \sim 10^{14}$ but estimates for the sun's convective zone and earth's interior are $Ra \sim 10^{16}-10^{20}$ and $Ra \sim 10^{20}-10^{30}$ respectively \cite{Ossendrijver,Gubbins_2001}.
-The scaling behavior of the Nusselt number $\Nu \sim Ra^{\beta}$ in the asymptotic ultimate regime is of particular interest.
+State of the art simulations performed by \cite{Zhu_2018} have reached $\Ra \sim 10^{14}$ but estimates for the sun's convective zone and earth's interior are $\Ra \sim 10^{16}-10^{20}$ and $\Ra \sim 10^{20}-10^{30}$ respectively \cite{Ossendrijver,Gubbins_2001}.
+The scaling behavior of the Nusselt number $\Nu \sim \Ra^{\beta}$ in the asymptotic ultimate regime is of particular interest.
 There exists a substantial body of work pertaining to this specific topic with no general consensus \cite{Malkus_1954, Howard_1966, Kraichnan, Spiegel, Castaing, Grossman, Ahlers}.
@@
 \section{Model Setup}\label{sec:model}
-We begin with the non-dimensionalized Boussinesq approximation for Rayleigh-Bénard Convection. 
+We begin with the Boussinesq approximation for Rayleigh-Bénard Convection, nondimensionalized on the freefall timescale. 
 The domain $\mathcal{D}$ is 2-dimensional, rectangular, and horizontally periodic with spatial dimensions $0 < x < 4$ and $-1/2 < z < 1/2$. 
@@
 
+Substituting \eq{EQ:reynolds_dc_p} into \eq{EQ:motion2} and taking the horizontal average reveals that the mean pressure field $\bar{p}(z)$ must satisfy
+\begin{equation}
+    0 = -\frac{\partial \bar{p}}{\partial z} + \bar{T}\label{EQ:p_bar}
+\end{equation}
+
 To solve \eq{EQ:T0_IVP} numerically, we need an expression for the perturbation so we can calculate the advective heat flux.
 Here we will make the quasilinear approximation, dropping the $\vec{u}'\vec{\cdot}\vec{\nabla}\vec{u}'$ and $\vec{u}'\vec{\cdot}\vec{\nabla}T'$ terms from the evolution equations for the perturbations.
-Substituting \eqss{EQ:reynolds_dc_u}{EQ:reynolds_dc_p} into \eqss{EQ:motion1}{EQ:motion3} and subtracting \eq{EQ:T0_IVP} from the resulting temperature equation, and linearizing gives
+Substituting \eqss{EQ:reynolds_dc_u}{EQ:reynolds_dc_p} into \eqss{EQ:motion1}{EQ:motion3} followed by subtracting \eq{EQ:T0_IVP} and \eq{EQ:p_bar} from the resulting temperature and $\hat{z}$ momentum equations gives
 \begin{align}
@@
 \begin{equation}
-  \langle |\theta|^2 \rangle_{\mathcal{D}} = 1.
+  \langle |\theta|^2 \rangle_{\mathcal{D}} = 1
 \end{equation}
+where $\langle \cdot \rangle_{\mathcal{D}}$ denotes the spatial mean over the entire domain.
+
 For each $k_x$, we can assess the stability of the perturbations by solving for the eigenvalue $s$, whose imaginary component $\sigma$ plays the role of an exponential growth rate. 
@@
 To evolve $\bar{T}$, we assume the perturbations evolve on a much faster timescale than the mean temperature, as in \cite{michel_chini_2019}.
-Stable modes decay away rapidly. 
-Unstable modes will not persist on the slow timescale because the advective term $\langle w'T' \rangle_x$ tends to stabilize $\bar{T}$, thereby creating a negative feedback loop.
+Stable modes $(\sigma < 0)$ decay away rapidly. 
+Unstable modes $(\sigma > 0)$ will not persist on the slow timescale because the advective term $\langle w'T' \rangle_x$ tends to stabilize $\bar{T}$, thereby creating a negative feedback loop.
 Only marginally stable modes can be maintained on the slow timescale.
@@
 
-For various $\Ra$ and fixed $\Pr = 1$, we seek marginally-stable thermal equilibria (MSTE) satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to . 
+For various $\Ra$ and fixed $\Pr = 1$, we seek marginally-stable thermal equilibria (MSTE) satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to \eq{EQ:T0_IVP}. 
 We employ the \texttt{Dedalus} pseudo-spectral python framework \cite{Dedalus_2020} to solve the EVP outlined in Section \ref{sec:model} as well as the IVP \eq{EQ:T0_IVP} by representing each field with Chebyshev polynomials.
@@
 The necessary number of basis functions varies, as eigenfunctions and temperature profiles associated with large $\Ra$ admit increasingly small-scale features. 
+A two-stage Runge-Kutta timestepper is implemented for the IVP.
 We use the \texttt{Eigentools} package \cite{Eigentools} to manipulate the eigenfunctions and calculate the advective heat flux $\langle w' T' \rangle_x$.
@@
 At $t = 0$, we begin with a marginally-stable initial profile $\bar{T}(z, 0)$ whose construction is outlined in appendix~\ref{sec:initial_profile}. 
-At some arbitrary time $t = t_0$, we seek to evolve $\bar{T}(z, t_0)$ into a new marginally-stable profile $\bar{T}(z, t_0 + \Delta t)$ according to \eq{EQ:T0_IVP}, using backward Euler to evolve the diffusion term and forward Euler to evolve the advection term.
+At some arbitrary time $t = t_0 \geq 0$, we seek to evolve $\bar{T}(z, t_0)$ into a new marginally-stable profile $\bar{T}(z, t_0 + \Delta t)$ according to \eq{EQ:T0_IVP}, using backward Euler to evolve the diffusion term and forward Euler to evolve the advection term.
 This requires us to determine the amplitude of the eigenfunction $A$.
@@
 We use Newton's method to find an amplitude which satisfies our marginal stability tolerance criterion $|\sigma_{\rm{max}} (A^2)| < 10^{-9}$.
-Marginally-stable modes do not osscillate in time, i.e. $\sigma = 0$ implies $\omega = 0$.
-This agrees with the convectional notion of exchange of stabilities \cite{drazin_reid_2004}.
-Crucially, we do not assume the $k_x$ of the marginally-stable is fixed.
+Marginally-stable modes do not oscillate in time, i.e. $\sigma = 0$ implies $\omega = 0$.
+This agrees with the conventional notion of exchange of stabilities \cite{drazin_reid_2004}.
+Crucially, we do not assume the $k_x$ of the marginally-stable mode is fixed.
 In section \ref{sec:multiple_modes} we specify procedures for the treatment of multiple simultaneously marginal modes.
@@
 \subsection{Treatment of multiple marginally-stable modes} \label{sec:multiple_modes}
-In most cases, we eventually encounter eigenvalue spectra with multiple simultaneously marginal modes.
+In most cases, we encounter eigenvalue spectra with multiple simultaneously marginal modes.
 If ignored, we are forced to reduce the timestep and allow the modes to alternate which is marginally stable.
@@
 Given a small fixed time step $\Delta t$, let $\vec{A^2}$ be the amplitude vector and $\vec{\sigma}(\vec{A^2})$ be the dependent eigenvalues.
-We expect a function $\vec{\sigma} \, : \, \mathbb{R}^N \to  \mathbb{R}^N$ to have isolated roots $\vec{A^2_m}$ (should they exist). 
-A coarse approximation $\vec{A^2_0}$ for the appropriate amplitude vector $\vec{A^2_m}$ is given by a generalized form of \eq{EQ:amp_approx}:
+We expect a function $\vec{\sigma} \, : \, \mathbb{R}^N \to  \mathbb{R}^N$ to have isolated roots $\vec{\tilde{A}^2}$ (should they exist). 
+A coarse approximation $\vec{A^2_0}$ for the appropriate amplitude vector $\vec{\tilde{A}^2}$ is given by a generalized form of \eq{EQ:amp_approx}:
 \begin{equation}
-    \vec{A^2_0} = -\Sigma_{\rm{adv}}^{-1} \vec{\sigma_{\rm{diff}}}.
+    \vec{\tilde{A}^2} \approx \vec{A^2_0} = -\Sigma_{\rm{adv}}^{-1} \vec{\sigma_{\rm{diff}}}.
     \label{EQ:AN_approx}
@@
 \begin{equation}
-    \vec{A^2_1} = -J^{-1} \vec{\sigma}(\vec{A^2_0}).
+    \vec{\tilde{A}^2} \approx \vec{A^2_1} = -J^{-1} \vec{\sigma}(\vec{A^2_0}).
 \end{equation}
@@
 We facilitate these transitions by defining an adjustable candidate tolerance $\varepsilon_{\rm{cand}} \in [10^{-6}, 10^{-8}]$.
-We rely on $A^2 > 0$ by asserting that a mode which meets the candidate tolerance can be included in an iteration provided that its respective amplitude is positive.
-Should that be the case, the candidate mode is now marginally-stable and included in the subsequent iteration.
-If however we converge on a negative amplitude, the candidate mode is discarded and the iteration is repeated. 
-%In general we find that no other obvious course of action yields equilibria.
+We rely on $A^2 > 0$ by asserting that a mode which meets the candidate tolerance can be included as a candidate marginal mode.
+If the candidate mode's amplitude turns out to be positive, the candidate mode is now marginally-stable and can be regularly included in the subsequent iteration.
+If however we converge on a negative amplitude, the candidate mode must be discarded and the iteration is repeated.
 
 After several time steps, $\bar{T}$ tends to asymmetrize due to numerical noise. 
-Though asymmetric pairs of solutions may exist, we further constrain $\bar{T}$ by imposing symmetry. 
-This is accomplished at the start of each iteration by setting the coefficients of even Chebyshev polynomials to zero.
+Though asymmetric pairs of solutions may exist, we further constrain $\bar{T}$ by setting the coefficients of its even Chebyshev basis functions to zero at the start of each iteration.
 
 \section{Properties of Thermally Equilibrated States}\label{sec:properties}
-We evolve $\bar{T}$ as described above until $|\partial_{t}\bar{T}| < 10^{-5}$.
+We evolve $\bar{T}$ as described above until $\max\{|\partial_{t}\bar{T}|\} < 10^{-5}$.
 In this marginally-stable thermal equilibrium, $\bar{T}$ does not evolve in time, and the perturbations also do not evolve in time, as they are marginally stable.
@@
 
-Figure \ref{fig:T0_profiles} gives temperature profiles for $\Ra = 10^8$ where the initial profile, whose construction is outlined in appendix~\ref{sec:initial_profile}, is employed at iteration 0. 
+Figure~\ref{fig:T0_profiles} gives temperature profiles for $\Ra = 10^8$ where the initial profile, whose construction is outlined in appendix~\ref{sec:initial_profile}, is employed at iteration 0. 
 Direct numerical simulations (DNS) are performed by solving \eqss{EQ:motion1}{EQ:motion3} with \texttt{Dedalus}, followed by horizontal- and time- averaging. 
@@
 Physically, they correspond to thin layers in which the mean temperature gradient reverses, contradicting an important hypothesis of \cite{Malkus_1954,Howard_1966}. 
-This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure \ref{fig:flux}. 
+This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure~\ref{fig:flux}. 
 We do not understand the source of these dips, but similar temperature gradient reversals were reported by \cite{chini_cells} along the midlines of 2D convective cellular solutions at $\Ra \sim 10^6$.
@@
 
-Equilibrated states exhibit distinct behaviors for large and small $\Ra$. 
-This contrast is illustrated in Figure \ref{fig:flux}, where we give heat flux profiles and eigenvalue spectra for two cases: $\Ra = 2 \times 10^5$ and $\Ra = 10^9$. 
+In Figure~\ref{fig:flux}, where we give heat flux profiles and eigenvalue spectra for two cases: $\Ra = 2 \times 10^5$ (top) and $\Ra = 10^9$ (bottom). 
 For $\Ra = 2 \times 10^5$, there is a single marginal mode at $k_x = 1.5\pi$ whose advective flux occupies the bulk of the domain. 
 These states have wide boundary layers which gradually subside as advection becomes the dominant flux component. 
-Such transitional regions do not appear for $\Ra = 10^9$.
-In this case the shift from diffusion to advection is sharp.
-At $\Ra=10^9$ we find five marginally-stable modes are necessary to reach a MSTE.
+Transitional regions occur over a smaller length scale for $\Ra = 10^9$ where the shift from diffusion to advection is sharp.
+At $\Ra=10^9$ we find five marginally-stable modes are necessary to reach an MSTE.
 Thin advection profiles, belonging to high-wavenumber modes with $k_x=23.5\pi, \, 24\pi$, hug the boundary layer. 
@@
     For example, the spectrum corresponding to $\Ra = 10^5$ has adjacent marginal wavenumbers $k_x = \pi, \, 1.5\pi$. 
-    The $\Ra = 10^9$ spectrum, shown in lower right corner of Figure \ref{fig:flux}, has three groups of maxima, with a single marginal mode in the first group ($k_x = 1.5\pi$), two adjacent marginal modes in the second group ($k_x = 6\pi, \, 6.5\pi$), and two adjacent marginal modes in the third group ($k_x = 23.5\pi, \, 24\pi$).
+    The $\Ra = 10^9$ spectrum, shown in lower right corner of Figure~\ref{fig:flux}, has three groups of maxima, with a single marginal mode in the first group ($k_x = 1.5\pi$), two adjacent marginal modes in the second group ($k_x = 6\pi, \, 6.5\pi$), and two adjacent marginal modes in the third group ($k_x = 23.5\pi, \, 24\pi$).
     The largest wavenumbers of the green branch obey a power-law relationship with $\Ra$}
@@
 In every case, the $k_x = 1.5\pi$ mode is included. 
-In Figure \ref{fig:kx_marginals} we give the wavenumbers $k_x$ of marginal modes. 
+In Figure~\ref{fig:kx_marginals} we give the wavenumbers $k_x$ of marginal modes. 
 Sometimes we find two marginally-stable modes with wavenumbers separated by $\pi/2$.
@@
 For $\Ra \geq 10^6$, a second branch of marginal modes is shown in light green. 
+Least-squares regression gives $\max\{k_x\} \propto \Ra^{0.300}$ with $R^2 = 0.998$ for this maximum branch.
 For large $\Ra$, the advective fluxes of this maximum branch opposes the strong diffusion of the thin MSTE boundary layers. 
-At $\Ra \geq 10^8$, a third branch appears (shown in light blue), splitting the widening gap between the other two. 
+At $\Ra \geq 10^8$, a third branch appears (shown in blue), splitting the widening gap between the other two. 
+For these points regression gives $k_x \propto \Ra^{0.155}$ with $R^2 = 0.988$
 This development is associated with moderately wide advection profiles, filling a niche in the total flux by uniting the thin profiles of the maximum branch with those of the bulk-domain-oriented minimum branch.
@@
     \includegraphics[width=3.4in]{del_kx_inv.png}
-    \caption{For $\Ra \geq 10^6$, the maximum marginally-stable wavenumber (corresponding to the green x markers in Figure \ref{fig:kx_marginals}) are inversely related to the boundary layer height $\delta$.
+    \caption{For $\Ra \geq 10^6$, the maximum marginally-stable wavenumber (corresponding to the green x markers in Figure~\ref{fig:kx_marginals}) are inversely related to the boundary layer height $\delta$.
     $(\max \{ k_x \})^{-1}$ gives a minimum $x$ length scale for the perturbations, and consequently, the advection. 
@@
 
-The largest marginal wavenumber $\max \{ k_x \}$ (represented by the light green branch in Figure \ref{fig:kx_marginals}) serves as an inverse minimum length-scale in the $x$ direction.
+The largest marginal wavenumber $\max \{ k_x \}$ (represented by the light green branch in Figure~\ref{fig:kx_marginals}) serves as an inverse minimum length-scale in the $x$ direction.
 The finest vertical structures in $\bar{T}(z)$ appear near the boundaries, requiring more basis functions (resolution) at large $\Ra$.
@@
 \end{align}
-This height corresponds to the local extrema of the MSTE temperature profile, e.g., in Figure \ref{fig:T0_profiles}.
-In Figure \ref{fig:del_inv}, we show $\max \{ k_x\}$ is proportional to $\delta$ over our range of $\Ra$.
-Least-squares regression gives $\delta^{-1} = 1.71 \max \{ k_x \} - 2.13$.
+This height corresponds to the local extrema of the MSTE temperature profile, e.g., in Figure~\ref{fig:T0_profiles}.
+In Figure~\ref{fig:del_inv}, we show $\max \{ k_x\}$ is proportional to $\delta$ over our range of $\Ra$.
+Least-squares regression gives $\delta^{-1} = 1.71 \max \{ k_x \} - 2.13$ with $R^2 = 0.996$.
 We can assume from this length scale agreement that the mean-squared $x$ and $z$ components of the temperature and velocity gradients are proportional
@@
 We find the MSTE can be characterized by their boundary layer height.
-In Figure \ref{fig:bl_ra}, we illustrate the scaling behavior of the boundary layer height $\delta = \Ra^{-1/3}$. 
+In Figure~\ref{fig:bl_ra}, we illustrate the scaling behavior of the boundary layer height $\delta = \Ra^{-1/3}$. 
 This is consistent with Malkus' classical marginal-stability theory, a scaling argument which perceives the boundary regions as subdomains which are themselves marginally-stable \cite{Malkus_1954}.
@@
     MSTE have greater $\Nu$ than the ECS, which in turn, have greater $\Nu$ than the DNS. 
-    This can be explained by the contrasting boundary layer geometries shown in Figure \ref{fig:T0_profiles}.}%
+    This can be explained by the contrasting boundary layer geometries shown in Figure~\ref{fig:T0_profiles}.}%
     \label{fig:nu_vs_ra}%
@@
 There is no general consensus surrounding the scaling behavior of $\Nu$ for high $\Ra$ systems, which are of particular importance in astrophysical and geophysical systems.
-In Figure \ref{fig:nu_vs_ra} we report $\Nu$ for MSTE, ``steady rolls" ECS \cite{Wen}, and DNS \cite{Scheel_2016, Johnston}.
+In Figure~\ref{fig:nu_vs_ra} we report $\Nu$ for MSTE, ``steady rolls" ECS \cite{Wen}, and DNS \cite{Scheel_2016, Johnston}.
 We find that MSTE satisfy $\Nu \sim\Ra^{1/3}$, consistent with our finding that the boundary layer width scales like $\delta \sim \Ra^{1/3}$.
@@
 The emergence of small-scale velocity structures tends to increase total shear \cite{Lecoanet_KH, drazin_reid_2004, pope_2000}, thereby impeding buoyancy-driven flows and decreasing advection in the bulk of the domain.
-We could also attribute the diffuse DNS temperature profile in Figure \ref{fig:T0_profiles} with unsteady boundary-layer penetration and mixing that MSTE do not exhibit.
+We could also attribute the diffuse DNS temperature profile in Figure~\ref{fig:T0_profiles} with unsteady boundary-layer penetration and mixing that MSTE do not exhibit.
 
@@
         \includegraphics[width=3.4in]{sim_eq_ke.png}
-        \caption{Average kinetic energies are reported for the same simulations illustrated in Figure \ref{fig:nu_sim} ($\Ra = 10^8$). 
+        \caption{Average kinetic energies are reported for the same simulations illustrated in Figure~\ref{fig:nu_sim} ($\Ra = 10^8$). 
         The eigenfunctions belonging to MSTE have significantly more kinetic energy than the statistically-steady state. 
@@
 
-We also find that the average kinetic energies of simulations initialized with MSTE are significantly larger than those found in simulations initialized with the conductive state plus noise, as shown Figure \ref{fig:ke_sim}.
+We also find that the average kinetic energies of simulations initialized with MSTE are significantly larger than those found in simulations initialized with the conductive state plus noise, as shown Figure~\ref{fig:ke_sim}.
 This is because the MSTE contain strong large-scale flows, which decay on a viscous time-scale
@@
 It should be noted that when experimenting with various initial profiles $(\tanh, \rm{erf}, \rm{etc.})$, we obtain indistinguishable equilibrated states, implying that solutions may be unique. 
-An example of \eq{EQ:T0} is given by the blue curve in Figure \ref{fig:T0_profiles}.
+An example of \eq{EQ:T0} is given by the blue curve in Figure~\ref{fig:T0_profiles}.
 

### 2021-04-30 publication_materials/ms_rbc.tex
misc. publication changes

@@
 We begin with the Boussinesq approximation for Rayleigh-Bénard Convection, nondimensionalized on the freefall timescale. 
-The domain $\mathcal{D}$ is 2-dimensional, rectangular, and horizontally periodic with spatial dimensions $0 < x < 4$ and $-1/2 < z < 1/2$. 
+The domain $\mathcal{D}$ is 2-dimensional, rectangular, and horizontally periodic with spatial dimensions $0 \leq x < 4$ and $-1/2 < z < 1/2$. 
 The fluid of interest is constrained between two flat boundaries at $z = -1/2$ and $z = 1/2$ with fixed temperatures $1/2$ and $-1/2$ respectively. 
@@
     A^2 \approx -\frac{\sigma_{\rm{diff}}}{\sigma_{\rm{adv}}} \label{EQ:amp_approx}
+\end{equation}
+
+\begin{equation}
+    \partial_t\bar{T} = \langle w'T' \rangle_x
 \end{equation}
@@
 At $\Ra \geq 10^8$, a third branch appears (shown in blue), splitting the widening gap between the other two. 
-For these points regression gives $k_x \propto \Ra^{0.155}$ with $R^2 = 0.988$
-This development is associated with moderately wide advection profiles, filling a niche in the total flux by uniting the thin profiles of the maximum branch with those of the bulk-domain-oriented minimum branch.
+For these points regression gives $k_x \propto \Ra^{0.155}$ with $R^2 = 0.988$.
+The blue branch is associated with moderately wide advection profiles, filling a niche in the total flux by uniting the thin profiles of the maximum branch with those of the bulk-domain-oriented minimum branch.
 

### 2021-05-06 publication_materials/ms_rbc.tex
section 3 evan's suggestions

@@
 \begin{abstract}
-    Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important properties remain elusive---particularly in the large Rayleigh number regime.
+    Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important properties remain elusive---particularly in the turbulent regime.
     In this investigation, we derive and solve a quasilinear form of the Rayleigh-Bénard problem by representing the perturbations in terms of marginally stable eigenmodes.
@@
     We find the background temperature field evolves to an equilibrium state, where the advective flux from the marginally-stable eigenmodes and the diffusive flux sum to a constant.
-    These marginally-stable thermal equilibria are exact solutions of the quasilinear equations.
+    These marginally-stable thermal equilibria (MSTE) are exact solutions of the quasilinear equations.
     The mean temperature profile has thinner boundary layers and larger Nusselt numbers than thermally-equilibrated 2D and 3D simulations of the full nonlinear equations.
     We find the Nusselt number scales like $\Nu \sim\Ra^{1/3}$.
-    When initializing a 2D simulation with a marginally-stable thermal equilibrium, we find the simulation does not exhibit the initial burst of turbulence typical of simulations initialized with the conductive background state plus noise.
-    Although the $\Nu$ quickly equilibrates in these simulations, the kinetic energy evolves on a viscous timescale as domain-filling flywheel flows viscously attenuate.
+    When an MSTE is used as initial conditions for a 2D simulation, we find that Nu quickly equilibrates without the burst of turbulence often induced by purely conductive initial conditions, but we also find that the kinetic energy is too large and viscously attenuates on a long viscous timescale.
 \end{abstract}
@@
 The quasilinear approximation starts with a decomposition of all variables into a background and perturbations about this background.
-The approximation is to neglect the influence of nonlinear interactions between the perturbations on the perturbations themselves \cite{marston2016}.
+This approximation neglects the influence of nonlinear interactions between the perturbations on the perturbations themselves \cite{marston2016}.
 This renders the perturbation equations linear.
@@
 For various $\Ra$ and fixed $\Pr = 1$, we seek marginally-stable thermal equilibria (MSTE) satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to \eq{EQ:T0_IVP}. 
-We employ the \texttt{Dedalus} pseudo-spectral python framework \cite{Dedalus_2020} to solve the EVP outlined in Section \ref{sec:model} as well as the IVP \eq{EQ:T0_IVP} by representing each field with Chebyshev polynomials.
-We use the 3/2 dealiasing rule to calculate the advective heat flux.
-The necessary number of basis functions varies, as eigenfunctions and temperature profiles associated with large $\Ra$ admit increasingly small-scale features. 
-A two-stage Runge-Kutta timestepper is implemented for the IVP.
+We employ the \texttt{Dedalus} pseudo-spectral python framework \cite{Dedalus_2020} to solve the EVP outlined in Section \ref{sec:model} as well as the IVP \eq{EQ:T0_IVP}.
+We represent each field with Chebyshev polynomials use the 3/2 dealiasing rule to calculate the advective heat flux.
+The necessary number of basis functions increases with $\Ra$ as the eigenfunctions include increasingly small-scale features. 
 We use the \texttt{Eigentools} package \cite{Eigentools} to manipulate the eigenfunctions and calculate the advective heat flux $\langle w' T' \rangle_x$.
 
-At $t = 0$, we begin with a marginally-stable initial profile $\bar{T}(z, 0)$ whose construction is outlined in appendix~\ref{sec:initial_profile}. 
-At some arbitrary time $t = t_0 \geq 0$, we seek to evolve $\bar{T}(z, t_0)$ into a new marginally-stable profile $\bar{T}(z, t_0 + \Delta t)$ according to \eq{EQ:T0_IVP}, using backward Euler to evolve the diffusion term and forward Euler to evolve the advection term.
-This requires us to determine the amplitude of the eigenfunction $A$.
-We will now illustrate our method of finding $A^2$ through an example.
+At iteration 0 we construct a marginally-stable initial temperature profile $\bar{T}(z, 0)$ whose equation is given in appendix~\ref{sec:initial_profile}. 
+At an arbitrary iteration beginning at $t = t_0$, we seek to evolve $\bar{T}(z, t_0)$ into a new marginally-stable profile $\bar{T}(z, t_0 + \Delta t)$ according to \eq{EQ:T0_IVP}. 
+To achieve this, we use a second-order, two-stage IMEX Runge-Kutta method.
+We initialize \eq{EQ:T0_IVP} with the previous iteration's solution to \eq{EQ:T0_IVP} and maintain marginal stability at each iteration.
+The eigenfunctions and amplitude are assumed to be constant over the timestep.
+Put simply, we can solve the IVP over long periods of time by stopping at each iteration to adjust the eigenfunctions and their amplitude $A$.
+It is essential that we pick the correct eigenfunction amplitude when calculating the advective term to maintain marginal stability.
+We will now illustrate our method of finding the appropriate $A^2$ through an example.
 
@@
     Advection tends to stabilize the system, decreasing its eigenvalues. 
-    We find the eigenfunction amplitude $A^2$ such that the combination of diffusion and advection yields a new, ``evolved,'' marginally-stable mean temperature profile $\bar{T}(z, t_0 + \Delta t)$.}
+    We find the eigenfunction amplitude $A^2$ such that the combination of diffusion and advection yields a new, ``evolved,'' marginally-stable mean temperature profile $\bar{T}(z, t_0 + \Delta t)$.
+In this case $A^2 \approx 1$ due to approximately equal magnitudes of the diffused and advected eigenvalues.}
     \label{fig:iteration_spectra} 
@@
 By definition, its maximum eigenvalue is 0.
-Diffusing $\bar{T}(z, t_0)$ tends to increase its eigenvalues.
-Ignoring the diffusive term and evolving according to advection tends the stabilize the system.
+Diffusing $\bar{T}(z, t_0)$ tends to increase its eigenvalues while ignoring the diffusive term and evolving according to advection tends the stabilize the system.
+$A$ must be selected such that these two influences are equal and opposite.
+We can measure the effects of diffusion and advection on the maximum eigenvalue by solving two new IVPs
+\begin{align}
+    &\frac{\partial \bar{T}_{\rm{diff}}}{\partial t} = \mathcal{P} \frac{\partial^2 \bar{T}_{\rm{diff}}}{\partial z^2} \\
+    &\frac{\partial \bar{T}_{\rm{adv}}}{\partial t} + \frac{\partial}{\partial z} \langle w'T' \rangle_x = 0 
+\end{align}
+where $\bar{T}_{\rm{diff}}$ and $\bar{T}_{\rm{adv}}$ denote to the diffused and advected temperature profiles.
+We initialize these IVPs with the marginally stable temperature of the current iteration.
+Suppose $\tilde{k_x}$ is the wavenumber of the marginally-stable mode.
+Then from the diffused and advected profiles, we compute the associated maximum eigenvalues of $\sigma_{\rm{diff}}$ and $\sigma_{\rm{adv}}$ at $k_x = \tilde{k_x}$.
 The appropriate amplitude $A^2$ can then be approximated by 
 \begin{equation}
-    A^2 \approx -\frac{\sigma_{\rm{diff}}}{\sigma_{\rm{adv}}} \label{EQ:amp_approx}
+    A^2 \approx A^2_0 = -\frac{\sigma_{\rm{diff}}}{\sigma_{\rm{adv}}} \label{EQ:amp_approx}
 \end{equation}
-
-\begin{equation}
-    \partial_t\bar{T} = \langle w'T' \rangle_x
-\end{equation}
-where $\sigma_{\rm{diff}}$ and $\sigma_{\rm{adv}}$ refer to the diffused and advected eigenvalues of the initially marginal mode.
+where the square in $A^2_0$ is due to the quadratic nonlinearity of the eigenfunctions in the advective term and the minus sign is due to the fact that $\sigma_{\rm{adv}} < 0$ and $\sigma_{\rm{diff}} < 0$ in general.
 We illustrate these trends in Figure~\ref{fig:iteration_spectra}. 
+The subscript 0 denotes a preliminary estimate which we later refine.
 $\bar{T}(z, t)$ is then evolved according to \eq{EQ:T0_IVP} and another eigenvalue solve is performed. 
@@
 In most cases, we encounter eigenvalue spectra with multiple simultaneously marginal modes.
-If ignored, we are forced to reduce the timestep and allow the modes to alternate which is marginally stable.
-Instead, we generalize the advective term in \eq{EQ:T0_IVP} to accommodate $N$ simultaneously marginal modes
+To accommodate this we generalize the advective term in \eq{EQ:T0_IVP} to accommodate $N$ simultaneously marginal modes
 \begin{equation}
@@
 where $W_n$ and $\theta_n$ are the eigenmodes associated with $k_x = \frac{n\pi}{2}$. 
-There are now $N$ amplitudes to solve for and $N$ eigenvalues to keep marginally-stable. 
+There are now $N$ modes, each having their own amplitude to solve for and eigenvalue to keep marginally-stable. 
 Given a small fixed time step $\Delta t$, let $\vec{A^2}$ be the amplitude vector and $\vec{\sigma}(\vec{A^2})$ be the dependent eigenvalues.
 We expect a function $\vec{\sigma} \, : \, \mathbb{R}^N \to  \mathbb{R}^N$ to have isolated roots $\vec{\tilde{A}^2}$ (should they exist). 
-A coarse approximation $\vec{A^2_0}$ for the appropriate amplitude vector $\vec{\tilde{A}^2}$ is given by a generalized form of \eq{EQ:amp_approx}:
+A preliminary approximation $\vec{A^2_0}$ for the appropriate amplitude vector $\vec{\tilde{A}^2}$ is given by a generalized form of \eq{EQ:amp_approx}:
 \begin{equation}
@@
 Here $\vec{\sigma_{\rm{diff}}} = \vec{\sigma} (\vec{0})$ refers to the eigenvalues after a brief $\Delta t$ period of diffusion. 
-$\Sigma_{\rm{adv}} \in \mathbb{R}^{N \times N}$ is the matrix of eigenvalues after $N$ periods of advection (one for each mode).
-% The $k$th row of $J_0$ is then given by the gradient of the $k$th mode's eigenvalue $\nabla \sigma_k$.
-In this way, an arbitrary element of $\Sigma_{\rm{adv}}$ represents how a particular mode's eigenvalue responds to the advection of another mode. 
-At the point of our coarse estimate $\vec{A^2_0}$, we approximate the Jacobian matrix 
+We account for the influence f $N$ advection terms on $N$ eigenvalues (one for each mode) by constructing an eigenvalue matrix $\Sigma_{\rm{adv}} \in \mathbb{R}^{N \times N}$.
+For example, the element of $\Sigma_{\rm{adv}}$ at row $i$ and column $j$ is given by the $i$th mode's eigenvalue due to advection by the $j$th mode's eigenfunctions. 
+At the point of our preliminary estimate $\vec{A^2_0}$, we approximate the Jacobian matrix 
 \begin{equation}
@@
 via first-order finite differences, requiring $N^2$ more individual EVP solves.
-A refined estimate is then given by
+A once-refined estimate $\vec{A^2_1}$ is then given by
+% The $k$th row of $J_0$ is then given by the gradient of the $k$th mode's eigenvalue $\nabla \sigma_k$.
 \begin{equation}
@@
 \end{equation}
-Once constructed, we use each subsequent guess to adjust the Jacobian via Broyden's method for root-finding in multi-dimensional functions \cite{Broyden}.
+We then use each subsequent guess to adjust the Jacobian via Broyden's method for root-finding in multi-dimensional functions \cite{Broyden}.
 We find $\vec{\sigma}(\vec{A^2})$ does indeed have a unique root provided the time step is not too large and there are no numerical instabilities, as outlined in appendix \ref{sec:timestep}.
@@
 Over the course of a large time step, $\bar{T}$ evolves according to \eq{EQ:T0_IVP} and eventually the original eigenfunctions cease to provide a stabilizing influence.
+It is precisely for this reason why we must halt the IVP regularly to adjust the eigenfunctions and their amplitudes.
 

### 2021-05-07 publication_materials/ms_rbc.tex
Appendix A

@@
 The eigenfunctions and amplitude are assumed to be constant over the timestep.
-Put simply, we can solve the IVP over long periods of time by stopping at each iteration to adjust the eigenfunctions and their amplitude $A$.
+We can solve the IVP over long periods of time by stopping regularly (at each iteration) to adjust the eigenfunctions and their amplitude $A$.
 It is essential that we pick the correct eigenfunction amplitude when calculating the advective term to maintain marginal stability.
-We will now illustrate our method of finding the appropriate $A^2$ through an example.
+We will now illustrate our method of finding the appropriate $A$ through an example.
 
@@
 Suppose $\tilde{k_x}$ is the wavenumber of the marginally-stable mode.
-Then from the diffused and advected profiles, we compute the associated maximum eigenvalues of $\sigma_{\rm{diff}}$ and $\sigma_{\rm{adv}}$ at $k_x = \tilde{k_x}$.
+Then, using the diffused and advected profiles, we compute the eigenvalues $\sigma_{\rm{diff}}$ and $\sigma_{\rm{adv}}$ at $k_x = \tilde{k_x}$.
 The appropriate amplitude $A^2$ can then be approximated by 
 \begin{equation}
-    A^2 \approx A^2_0 = -\frac{\sigma_{\rm{diff}}}{\sigma_{\rm{adv}}} \label{EQ:amp_approx}
+    A^2 \approx A^2_0 \equiv -\frac{\sigma_{\rm{diff}}}{\sigma_{\rm{adv}}} \label{EQ:amp_approx}
 \end{equation}
-where the square in $A^2_0$ is due to the quadratic nonlinearity of the eigenfunctions in the advective term and the minus sign is due to the fact that $\sigma_{\rm{adv}} < 0$ and $\sigma_{\rm{diff}} < 0$ in general.
+where the square in $A^2_0$ is due to the quadratic nonlinearity of the eigenfunctions in the advective term and the minus sign is due to the fact that $\sigma_{\rm{adv}} < 0$ and $\sigma_{\rm{diff}} > 0$ in general.
 We illustrate these trends in Figure~\ref{fig:iteration_spectra}. 
@@
 \section{Initial buoyancy profile} \label{sec:initial_profile}
-We initialize the thermal-equilibration algorithm with \cite{Shishkina}'s analytical thermal boundary layer equation for turbulent Rayleigh-B\'enard convection, given by 
+We initialize the thermal-equilibration algorithm with an analytical thermal boundary layer equation, derived by \cite{Shishkina} 
 \begin{align}
-    \bar{T}_0(\xi) &= \frac{\sqrt{3}}{4\pi} \log \frac{(1 + a\xi)^3}{1 + (a\xi)^3} + \frac{3}{2\pi} \arctan \Big( \frac{4\pi}{9}\xi - \frac{1}{\sqrt{3}} \Big) + \frac{1}{4} \nonumber \\
-    \xi &= \frac{z}{\delta_0}, \qquad a = \frac{2\pi}{3\sqrt{3}}\label{EQ:T0}
+    \bar{\mathcal{T}}_0(\xi) &= \frac{\sqrt{3}}{4\pi} \log \frac{(1 + a\xi)^3}{1 + (a\xi)^3} + \frac{3}{2\pi} \arctan \Big( \frac{4\pi}{9}\xi - \frac{1}{\sqrt{3}} \Big) + \frac{1}{4} \nonumber \\
+    \xi &= \frac{z + 1/2}{\delta_0} \geq 0, \qquad a = \frac{2\pi}{3\sqrt{3}}\label{EQ:T0}
 \end{align}
 where $\delta_0$ is the boundary layer height. 
-We expect that each $\Ra$ is associated with a unique $\delta_0$ for which $\bar{T}_0(z)$ is marginally-stable. 
-It should be noted that when experimenting with various initial profiles $(\tanh, \rm{erf}, \rm{etc.})$, we obtain indistinguishable equilibrated states, implying that solutions may be unique. 
+This function is meant to describe the temperature near $z = -1/2$.
+It does not pass through the origin and it is undefined for $z > 0$. 
+An appropriate initial mean temperature profile $\bar{T}_0$ must be odd-symmetric, i.e.~$\bar{T}_0(-z) = -\bar{T}_0(z)$.
+Due to continuity, this implies $\bar{T}_0(0) = 0$.
+Accordingly, we construct $\bar{T}_0(z)$ by translating $\bar{\mathcal{T}}_0(z)$ vertically to pass through the origin.
+We then take its odd-extension and include a unique scaling coefficient to satisfy the boundary conditions $\bar{T}_0(-1/2) = 1/2$ and $\bar{T}_0(1/2) = -1/2$.
+The initial mean temperature profile is therefore given by
+\begin{align*}
+    \bar{T}_0(z) &= \frac{1}{2} \begin{cases}
+        1 - \frac{\bar{\mathcal{T}}_0\big(\frac{z + 1/2}{\delta_0}\big)}{\bar{\mathcal{T}}_0\big(\frac{1}{2\delta_0}\big)} \quad -1/2 \leq z \leq 0 \\[0.5cm]
+        -1 + \frac{\bar{\mathcal{T}}_0\big(\frac{1/2 - z}{\delta_0}\big)}{\bar{\mathcal{T}}_0\big(\frac{1}{2\delta_0}\big)} \quad 0 < z \leq 1/2.
+    \end{cases}
+\end{align*} 
+ We expect each $\Ra$ to be associated with a unique $\delta_0$ for which $\bar{T}_0(z)$ is marginally-stable. 
+It should be noted that when experimenting with various initial profiles $(\tanh, \rm{erf}, \rm{etc.})$, we obtain indistinguishable equilibrated states.
+Therefore these initial states lie in the MSTE basin of attraction.
+This might also suggest that solutions are unique. 
 An example of \eq{EQ:T0} is given by the blue curve in Figure~\ref{fig:T0_profiles}.

### 2021-05-10 publication_materials/ms_rbc.tex
section III and appendix A revs, appendix B&C init

@@
 
-In this paper we solve the Rayleigh-B\'{e}nard convection problem using an analogous strategy.
+In this paper we derive and solve a quasilinear form of the Rayleigh-B\'{e}nard convection problem using a similar time-scale separation argument.
 In section~\ref{sec:model} we recall the underlying equations, and in section~\ref{sec:evolution} we describe how we evolve the background temperature profile while maintaining marginal stability.
@@
 \section{Perturbation Evolution}\label{sec:evolution}
-The linearized system \eqss{EQ:linear1}{EQ:linear3} cannot determine the amplitude of the eigenmodes, $A$.
+The linearized system \eqss{EQ:linear1}{EQ:linear3} does not constrain the amplitude of the eigenmodes, $A$.
 However, the advective heat flux is proportional to $A^2$, so we need to specify the amplitude in order to solve equation~\ref{EQ:T0_IVP}.
@@
 
-\subsection{Treatment of multiple marginally-stable modes} \label{sec:multiple_modes}
+\subsection{Treatment of Multiple Marginally-Stable Modes} \label{sec:multiple_modes}
 In most cases, we encounter eigenvalue spectra with multiple simultaneously marginal modes.
@@
 \begin{equation}
-    \langle w' T' \rangle_x = \sum_{n = 1}^{N} 4 A_n^2 \int \, \Re\left[ W_n \theta_n^* \right] \,dz
+    \langle w' T' \rangle_x = \sum_{n = 1}^{N} 2 A_n^2  \Re\left[ W_n \theta_n^* \right] 
 \end{equation}
@@
 We facilitate these transitions by defining an adjustable candidate tolerance $\varepsilon_{\rm{cand}} \in [10^{-6}, 10^{-8}]$.
-We rely on $A^2 > 0$ by asserting that a mode which meets the candidate tolerance can be included as a candidate marginal mode.
-If the candidate mode's amplitude turns out to be positive, the candidate mode is now marginally-stable and can be regularly included in the subsequent iteration.
-If however we converge on a negative amplitude, the candidate mode must be discarded and the iteration is repeated.
+A mode which meets the candidate tolerance can be included as a candidate marginal mode.
+Candidate modes are rejected when the root-finding algorithm converges on a negative amplitude $A^2 < 0$.
+Otherwise the mode becomes marginally-stable.
 
@@
 \section{Properties of Thermally Equilibrated States}\label{sec:properties}
-We evolve $\bar{T}$ as described above until $\max\{|\partial_{t}\bar{T}|\} < 10^{-5}$.
+We evolve $\bar{T}$ as described above until $\max|\partial_{t}\bar{T}| < 10^{-5}$.
 In this marginally-stable thermal equilibrium, $\bar{T}$ does not evolve in time, and the perturbations also do not evolve in time, as they are marginally stable.
@@
     Marginal modes often appear in adjacent pairs, which we denote with a common color. 
+    Within each of these pairs, the largest and smallest $k_x$ are denoted with an + and x respectively.
     For example, the spectrum corresponding to $\Ra = 10^5$ has adjacent marginal wavenumbers $k_x = \pi, \, 1.5\pi$. 
     The $\Ra = 10^9$ spectrum, shown in lower right corner of Figure~\ref{fig:flux}, has three groups of maxima, with a single marginal mode in the first group ($k_x = 1.5\pi$), two adjacent marginal modes in the second group ($k_x = 6\pi, \, 6.5\pi$), and two adjacent marginal modes in the third group ($k_x = 23.5\pi, \, 24\pi$).
-    The largest wavenumbers of the green branch obey a power-law relationship with $\Ra$}
+    The largest wavenumbers of the green branch obey a power-law relationship $\max\{k_x\} \propto \Ra^{0.300}$ with $R^2 = 0.998$.}
     \label{fig:kx_marginals}
@@
 In Figure~\ref{fig:kx_marginals} we give the wavenumbers $k_x$ of marginal modes. 
-Sometimes we find two marginally-stable modes with wavenumbers separated by $\pi/2$.
+For some values of $\Ra$ we obtain states with pairs marginally-stable modes, with wavenumbers separated by $\pi/2$.
 Like $k_x = 6\pi, \, 6.5\pi$ and $k_x=23.5\pi, \, 24\pi$ for the $\Ra=10^9$ MSTE, these are due to the discretization of wavenumbers from our domain of width 4.
@@
 This height corresponds to the local extrema of the MSTE temperature profile, e.g., in Figure~\ref{fig:T0_profiles}.
-In Figure~\ref{fig:del_inv}, we show $\max \{ k_x\}$ is proportional to $\delta$ over our range of $\Ra$.
+In Figure~\ref{fig:del_inv}, we show $\max \{ k_x\}$ is proportional to $\delta^{-1}$ over our range of $\Ra$.
 Least-squares regression gives $\delta^{-1} = 1.71 \max \{ k_x \} - 2.13$ with $R^2 = 0.996$.
@@
 For high $\Ra$ experiments, researchers often ``bootstrap" data by initializing simulations with the results of similar $\Ra$ runs \cite{Verzicco, Johnston}. 
-MSTE can be perceived as a set of initial conditions, designed for avoiding the simulation of transitional high Reynolds number flows.
+MSTE can be perceived as a set of initial conditions, designed for avoiding the simulation of transient high Reynolds number flows.
 
@@
 We compute marginally-stable thermal equilibria (MSTE), which are equilibria of the quasilinear equations.
-To compute MSTE, we construct a marginally-stable mean temperature profile and evolved it according to the advective flux of its marginally-stable eigenfunctions, and its own diffusion. 
+To compute MSTE, we construct a marginally-stable mean temperature profile and evolve it according to the advective flux of its marginally-stable eigenfunctions, and its own diffusion. 
 We assume that at least some modes are always in a marginally-stable configuration. 
@@
 They also exhibit unique and unexpected features: mean temperature gradient-reversals/dips, high kinetic energy flows, and a larger $\Nu$ than other time-invariant solutions. 
-When initializing with different mean temperature profiles, we found the same MSTE, suggesting these equilibria might be unique.
+When initializing with different mean temperature profiles, we find the same MSTE, suggesting these equilibria might be unique.
 
@@
 
-As previously noted, using the mean temperature in a statistically-steady DNS as a background state for an eigenvalue problem yields positive eigenvalues: the system is in a perpetual state of instability.
+Using the mean temperature in a statistically-steady DNS as a background state for an eigenvalue problem yields positive eigenvalues: the system is in a perpetual state of instability. 
 Unstable modes tend to stabilize the system rapidly, creating a negative feedback loop whose average state is linearly unstable. 
@@
 
-\section{Initial buoyancy profile} \label{sec:initial_profile}
+\section{Initial Buoyancy Profile} \label{sec:initial_profile}
 We initialize the thermal-equilibration algorithm with an analytical thermal boundary layer equation, derived by \cite{Shishkina} 
@@
 
-% \begin{multicols}{1}
+\section{Timestep Management} \label{sec:timestep}
+Timesteps don't manage themselves! $\blacksquare$
+
+\onecolumngrid
 \section{MSTE Metrics}\label{sec:tables}
-\begin{longtable*}{cccccc}
+
+\begin{longtable*}{ccccl}
     %\begin{tabular}{cccccc}
@@
     %\begin{longtable}[c]{@{}*{6}{>{\arraybackslash}p{0.15\linewidth}}@{}}
-    \quad\quad\quad Ra	\quad\quad\quad	&	\quad\quad\quad		Pr	\quad\quad\quad		&	\quad\quad\quad		$k=2\pi/\Gamma$	\quad\quad\quad		&	\quad\quad\quad		$N_x \times N_z$	\quad\quad\quad		&	\quad\quad\quad		Nu	\quad\quad\quad		&	\quad\quad\quad		Re	\quad\quad\quad\\
+    \quad\quad\quad $\Ra$	\quad\quad\quad	&	\quad\quad\quad		$N_z$	\quad\quad\quad		&	\quad\quad\quad		$\Nu$	\quad\quad\quad		&	\quad\quad\quad		$\delta_0$	\quad\quad\quad		&	\quad\quad		$k_x$ marginals	\quad\quad\quad\\
     %\hline
-    $10^{13/4}$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.056590	&	1.617336\\
-    $1.9\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.145807	&	2.682155\\
-    $2\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.212037	&	3.317190\\
-    $2.25\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.355410	&	4.550975\\
-    $2.5\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.474455	&	5.537770\\
-    $2.75\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.575599	&	6.391812\\
-    $3\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.663162	&	7.159844\\
-    $10^{14/4}$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.714193	&	7.624400\\
-    $3.5\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.808754	&	8.526064\\
-    $4\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.926775	&	9.740578\\
-    $4.5\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	2.025985	&	10.85141\\
-    $5\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	2.111714	&	11.88534\\
-    $10^{15/4}$	&	1	&	$\pi$	&	128 $\times$ 65	&	2.204811	&	13.09152\\
-    $8\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	2.476330	&	17.05494\\
-    $10^4$	&	1	&	$\pi$	&	128 $\times$ 65	&	2.648664	&	20.07400\\
-    $10^{17/4}$	&	1	&	$\pi$	&	128 $\times$ 65	&	3.122843	&	29.50047\\
-    $10^{18/4}$	&	1	&	$\pi$	&	128 $\times$ 65	&	3.665041	&	42.29585\\
-    $10^{19/4}$	&	1	&	$\pi$	&	128 $\times$ 65	&	4.287042	&	59.56858\\
-    $10^{5}$	&	1	&	$\pi$	&	128 $\times$ 65	&	4.994322	&	82.84462\\
-    $10^{21/4}$	&	1	&	$\pi$	&	128 $\times$ 65	&	5.795869	&	114.2355\\
-    $10^{22/4}$	&	1	&	$\pi$	&	128 $\times$ 97	&	6.703915	&	156.5252\\
-    $10^{23/4}$	&	1	&	$\pi$	&	128 $\times$ 97	&	7.732236	&	213.4031\\
-    $10^{6}$	&	1	&	$\pi$	&	128 $\times$ 97	&	8.896615	&	289.7982\\
-    $10^{25/4}$	&	1	&	$\pi$	&	256 $\times$ 97	&	10.21546	&	392.2837\\
-    $10^{26/4}$	&	1	&	$\pi$	&	256 $\times$ 129	&	11.71065	&	529.6372\\
-    $10^{27/4}$	&	1	&	$\pi$	&	256 $\times$ 129	&	13.40898	&	713.6005\\
-    $10^{7}$	&	1	&	$\pi$	&	512 $\times$ 129	&	15.34493	&	959.9367\\
-    $1.35\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 129	&	16.46456	&	1119.932\\
-    $1.5\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 129	&	16.87881	&	1182.172\\
-    $1.6\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.13944	&	1222.005\\
-    $1.65\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.26636	&	1241.484\\
-    $1.7\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.39216	&	1260.709\\
-    $1.736\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.48282	&	1274.414\\
-    $1.76\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.54351	&	1283.493\\
-    $10^{29/4}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.58987	&	1290.377\\
-    $1.786\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.60946	&	1293.277\\
-    $1.8\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.64500	&	1298.522\\
-    $1.85\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.77160	&	1317.122\\
-    $1.9\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.89693	&	1335.501\\
-    $1.95\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	18.02044	&	1353.657\\
-    $2\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	18.14193	&	1371.593\\
-    $2.4\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	19.04221	&	1507.890\\
-    $2.8\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	19.83413	&	1633.418\\
-    $10^{30/4}$	&	1	&	$\pi$	&	512 $\times$ 193	&	20.47798	&	1739.647\\
-    $4.5\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	22.44036	&	2087.182\\
-    $10^{31/4}$	&	1	&	$\pi$	&	512 $\times$ 193	&	23.76002	&	2340.822\\
-    $10^{8}$	&	1	&	$\pi$	&	768 $\times$ 257	&	27.50669	&	3144.931\\
-    $10^{33/4}$	&	1	&	$\pi$	&	768 $\times$ 257	&	31.81154	&	4220.616\\
-    $2.15\times10^{8}$	&	1	&	$\pi$	&	768 $\times$ 257	&	33.36657	&	4649.541\\
-    $10^{34/4}$	&	1	&	$\pi$	&	768 $\times$ 257	&	36.75427	&	5658.648\\
-    $4.64\times10^{8}$	&	1	&	$\pi$	&	896 $\times$ 321	&	40.44652	&	6875.704\\
-    $10^{35/4}$	&	1	&	$\pi$	&	896 $\times$ 321	&	42.42917	&	7580.057\\
-    $10^{9}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	48.94284	&	10145.79\\
-    $10^{37/4}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	56.42926	&	13571.10\\
-    $2.15\times10^{9}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	59.13988	&	14935.81\\
-    $2.5\times10^{9}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	61.38714	&	16116.94\\
-    $10^{38/4}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	65.06338	&	18145.61\\
-    $10^{153/16}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	67.42466	&	19511.79\\
-    $4\times10^{9}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	68.96487	&	20429.24\\
-    $4.64\times10^{9}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	71.58241	&	22019.93\\
-    $10^{39/4}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	75.09725	&	24262.22\\
-    $10^{10}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	86.68318	&	32430.06\\
-    $10^{41/4}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	100.0909	&	43339.02\\
-    $2\times10^{10}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	103.0738	&	45995.60\\
-    $2.15\times10^{10}$ &	1	&	$\pi$	&	1024 $\times$ 321	&	104.9517	&	47705.08\vspace{0.1in}\\
+    1.00E+05 & 256   & 5.9343  & 0.15746 \;    &   \; 1$\pi$, 1.5$\pi$ \\
+    2.00E+05 & 256   & 7.45986 & 0.12341 \;    &   \; 1.5$\pi$ \\
+    4.00E+05 & 256   & 8.92597 & 0.10395 \;    &   \; 1.5$\pi$ \\
+    1.00E+06 & 256   & 11.6689 & 0.07922 \;    &   \; 1.5$\pi$, 2.5$\pi$, 3$\pi$ \\
+    2.00E+06 & 256   & 14.8463 & 0.06345 \;    &   \; 1.5$\pi$, 3.5$\pi$ \\
+    4.00E+06 & 256   & 18.9433 & 0.04933 \;    &   \; 1.5$\pi$, 4.5$\pi$ \\
+    1.00E+07 & 256   & 25.6821 & 0.03632 \;    &   \; 1.5$\pi$, 5.5$\pi$ \\
+    2.00E+07 & 256   & 32.4531 & 0.02820 \;    &   \; 1.5$\pi$, 6.5$\pi$, 7$\pi$\\
+    4.00E+07 & 512   & 40.7925 & 0.02289 \;    &   \; 1.5$\pi$, 8$\pi$, 8.5$\pi$ \\
+    1.00E+08 & 512   & 55.4383 & 0.01690 \;    &   \; 1.5$\pi$, 4.5$\pi$, 10.5$\pi$, 11$\pi$\\
+    2.00E+08 & 512   & 69.8349 & 0.01318 \;    &   \; 1.5$\pi$, 5$\pi$, 13.5$\pi$, 14$\pi$ \\
+    4.00E+08 & 512   & 87.8525 & 0.01053 \;    &   \; 1.5$\pi$, 5.5$\pi$,17.5$\pi$ \\
+    1.00E+09 & 768   & 119.318 & 0.00817 \;    &   \; 1.5$\pi$, 6.0$\pi$, 6.5$\pi$, 23.5$\pi$, 24$\pi$ \\\vspace{0.1in}\\
     %\hline
     %  \end{tabular}
-    \caption*{Table S1: Details for numerical solutions with $\Pran=1$ and $\Gamma=2$.  $N_x$ and $N_z$ represent the numbers of Fourier and Chebyshev modes, respectively.}
-    {\label{tab:Gamma2}}
+    \caption{Control parameters are given for the timestepping algorithm.
+$N_z$ denotes the number of Chebyshev basis functions employed.
+The remaining quantities are derived directly from MSTE solutions.}
+    {\label{tab:metrics}}
     \end{longtable*}
-% \end{multicols}
+
+\twocolumngrid
 

### 2021-05-12 publication_materials/ms_rbc.tex
appendix B and section V edits

@@
     We find the Nusselt number scales like $\Nu \sim\Ra^{1/3}$.
-    When an MSTE is used as initial conditions for a 2D simulation, we find that Nu quickly equilibrates without the burst of turbulence often induced by purely conductive initial conditions, but we also find that the kinetic energy is too large and viscously attenuates on a long viscous timescale.
+    When an MSTE is used as initial conditions for a 2D simulation, we find that Nu quickly equilibrates without the burst of turbulence often induced by purely conductive initial conditions, but we also find that the kinetic energy is too large and viscously attenuates on a long viscous time-scale.
 \end{abstract}
@@
 In \cite{Beaume_2015}, researchers compute ECS in parallel shear flows by deriving and solving a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments. 
-They assume the background velocity evolves on a slow timescale, and to determine the perturbation amplitudes they require marginal stability at each timestep.
+They assume the background velocity evolves on a slow time-scale, and to determine the perturbation amplitudes they require marginal stability at each timestep.
 A similar strategy is employed by \cite{michel_chini_2019} to studying acoustic streaming.
@@
 \section{Model Setup}\label{sec:model}
-We begin with the Boussinesq approximation for Rayleigh-Bénard Convection, nondimensionalized on the freefall timescale. 
+We begin with the Boussinesq approximation for Rayleigh-Bénard Convection, nondimensionalized on the freefall time-scale. 
 The domain $\mathcal{D}$ is 2-dimensional, rectangular, and horizontally periodic with spatial dimensions $0 \leq x < 4$ and $-1/2 < z < 1/2$. 
@@
 For completeness, we specify a final boundary condition $p = p_0$ at $z = \pm 1/2$. 
-Any system of this form can be characterized by its dimensionless Rayleigh number $\Ra = \frac{g\alpha L^3 \Delta T}{\nu \kappa}$ and Prandtl number $\Pr = \frac{\nu}{\kappa}$, where $g, \, \alpha, \, L, \, \Delta T, \nu, \kappa$ are the gravitational acceleration, coefficient of thermal expansion, domain height, opposed temperature difference, kinematic viscosity, and thermal diffusivity respectively.
+Any system of this form can be characterized by its dimensionless Rayleigh number $\Ra = \frac{g\alpha L^3 \Delta T}{\nu \kappa}$ and Prandtl number $\Pr = \frac{\nu}{\kappa}$, where $g, \, \alpha, \, L_z, \, \Delta T, \nu, \kappa$ are the gravitational acceleration, coefficient of thermal expansion, domain height, opposed temperature difference, kinematic viscosity, and thermal diffusivity respectively.
 In this paper, we fix $\Pr = 1$.
@@
 However, the advective heat flux is proportional to $A^2$, so we need to specify the amplitude in order to solve equation~\ref{EQ:T0_IVP}.
-To evolve $\bar{T}$, we assume the perturbations evolve on a much faster timescale than the mean temperature, as in \cite{michel_chini_2019}.
+To evolve $\bar{T}$, we assume the perturbations evolve on a much faster time-scale than the mean temperature, as in \cite{michel_chini_2019}.
 Stable modes $(\sigma < 0)$ decay away rapidly. 
-Unstable modes $(\sigma > 0)$ will not persist on the slow timescale because the advective term $\langle w'T' \rangle_x$ tends to stabilize $\bar{T}$, thereby creating a negative feedback loop.
-Only marginally stable modes can be maintained on the slow timescale.
+Unstable modes $(\sigma > 0)$ will not persist on the slow time-scale because the advective term $\langle w'T' \rangle_x$ tends to stabilize $\bar{T}$, thereby creating a negative feedback loop.
+Only marginally stable modes can be maintained on the slow time-scale.
 Therefore the amplitude $A$ must satisfy
@@
 We employ the \texttt{Dedalus} pseudo-spectral python framework \cite{Dedalus_2020} to solve the EVP outlined in Section \ref{sec:model} as well as the IVP \eq{EQ:T0_IVP}.
-We represent each field with Chebyshev polynomials use the 3/2 dealiasing rule to calculate the advective heat flux.
+We represent each field with Chebyshev polynomials and use the 3/2 dealiasing rule to calculate the advective heat flux.
 The necessary number of basis functions increases with $\Ra$ as the eigenfunctions include increasingly small-scale features. 
@@
     Advection tends to stabilize the system, decreasing its eigenvalues. 
-    We find the eigenfunction amplitude $A^2$ such that the combination of diffusion and advection yields a new, ``evolved,'' marginally-stable mean temperature profile $\bar{T}(z, t_0 + \Delta t)$.
+    We find the eigenfunction amplitude $A^2$ such that the combination of diffusion and advection yields a new, ``evolved'', marginally-stable mean temperature profile $\bar{T}(z, t_0 + \Delta t)$.
 In this case $A^2 \approx 1$ due to approximately equal magnitudes of the diffused and advected eigenvalues.}
@@
     For large $\Ra$, the boundary layers admit small scale features, requiring more vertical basis functions (higher resolution).
-    The boundary layer width gives an estimate of the minimum vertical lengthscale in the problem.
-    This suggests that the minimum horizontal and vertical lengthscales are proportional to each other over a wide range of $\Ra$.}
+    The boundary layer width gives an estimate of the minimum vertical length-scale in the problem.
+    This suggests that the minimum horizontal and vertical length-scales are proportional to each other over a wide range of $\Ra$.}
     \label{fig:del_inv}
@@
 Here we include noise as a source of asymmetries. 
+We also perform a simulation with MSTE absent any initial velocity ($\vec{u}(x, z)|_{t=0} = \vec{0}$). 
+This state is not in equilibrium but we refer to it as ``MSTE No Flow'' for clarity.
 
 \begin{figure}
-    \begin{minipage}{3.4in}
     \centering
-        \includegraphics[width=3.4in]{sim_eq_nu.png}
-        \caption{Nusselt numbers of simulations performed at $\Ra = 10^8$, initialized with the conductive equilibrium plus thermal noise (black) and the MSTE (blue). 
-        MSTE simulations do not undergo a convective-transient period because the characteristic large-scale convective cell structure exists on initialization.}
+    \includegraphics[width=3.4in]{sim_eq_nu_noflow.png}
+    \caption{Nusselt numbers of simulations performed at $\Ra = 10^8$, initialized with the conductive equilibrium plus thermal noise (black), the MSTE (blue), and the MSTE absent initial flow (green).
+    The MSTE simulation does not undergo a convective-transient period because the characteristic large-scale convective cell structure exists on initialization.
+    The MSTE no flow simulation exhibits quasi-periodic oscillations in $\Nu$ which appear to persist for long times.}
     \label{fig:nu_sim}
-    \end{minipage}
 \end{figure}
@@
 This is due to a burst of turbulence which occurs when the convective motions first become nonlinear.
+The MSTE no flow simulation undergoes a similar transient period, albeit less pronounced as denoted by the smaller peak in the green curve.
 A simulation initialized with the MSTE, however, does not exhibit this transient burst of turbulence, as the large-scale anatomy of convective cells exists on initialization. 
@@
 MSTE can be perceived as a set of initial conditions, designed for avoiding the simulation of transient high Reynolds number flows.
+MSTE absent velocity achieve the same goal but give way to seemingly-persistent oscillations in $\Nu$.
 
@@
 \begin{figure}
-    \begin{minipage}{3.4in}
     \centering
-        \includegraphics[width=3.4in]{sim_eq_ke.png}
+    \includegraphics[width=3.4in]{sim_eq_ke_noflow.png}
     \caption{Average kinetic energies are reported for the same simulations illustrated in Figure~\ref{fig:nu_sim} ($\Ra = 10^8$). 
     The eigenfunctions belonging to MSTE have significantly more kinetic energy than the statistically-steady state. 
-        Kinetic equilibrium is achieved on the viscous time-scale $t_{\nu} \sim \sqrt{\Ra / \Pr}$.}
+    Kinetic equilibrium is achieved on the viscous time-scale.}
     \label{fig:ke_sim}
-    \end{minipage}
 \end{figure}
 
-We also find that the average kinetic energies of simulations initialized with MSTE are significantly larger than those found in simulations initialized with the conductive state plus noise, as shown Figure~\ref{fig:ke_sim}.
-This is because the MSTE contain strong large-scale flows, which decay on a viscous time-scale
-\begin{equation}
-    t_{\nu} \sim \sqrt{\frac{\Ra}{\Pr}}. \nonumber
-\end{equation}
+We also find that the average kinetic energies of simulations initialized with MSTE are significantly larger than those found in simulations initialized with no-flow MSTE and with the conductive state plus noise, as shown Figure~\ref{fig:ke_sim}.
+This is because the MSTE contain strong large-scale flows, which decay on a viscous time-scale $t_{\nu}$. Two viscous time-scales can be derived for this problem: one for the boundary layer 
+\begin{align*}
+    t_{\nu,\delta} &= \frac{L_z}{\mathcal{P}} = 10^4
+\end{align*}
+\begin{align*}
+    \intertext{and another for the entire domain}
+    t_{\nu,\mathcal{D}} &= \frac{\delta^2_0}{\mathcal{P}} = 2.8561.
+\end{align*}
+Empirically, we find $t_{\nu} \approx 200$ suggesting the true kinetic energy decary time-scale is based on a length scale which is longer than the boundary layer weight $\delta_0$ but shorter than the domain height $L_z$.
 Consequently, MSTE initial conditions do not reduce the simulation time required to achieve a statistically-steady state---rather they increase it considerably!
@@
 It should be noted that when experimenting with various initial profiles $(\tanh, \rm{erf}, \rm{etc.})$, we obtain indistinguishable equilibrated states.
-Therefore these initial states lie in the MSTE basin of attraction.
+Therefore these initial states lie in the MSTE basin of attraction with respect to the quasilinear system.
 This might also suggest that solutions are unique. 
@@
 
-\section{Timestep Management} \label{sec:timestep}
-Timesteps don't manage themselves! $\blacksquare$
+\section{Numerical Instabilities and Timestep Management} \label{sec:timestep}
+A suitable timestep $\Delta t$ must be selected at the start of each iteration.
+For sufficiently large $\Delta t$, we find the advective flux terms fail to provide a stabilizing influence.
+This is due to coupling between the eigenfunctions $W(z)$, $\Theta(z)$ and the mean temperature profile $\bar{T}$.
+In the context of our algorithm, this effectively deletes the sought-after root of the maximum eigenvalue function $\sigma_{\rm{max}}(A^2)$ causing the root-finding methods to fail. 
+This is not a numerical instability, rather, it is a limitation of our timestepping algorithm.
+To curtail this, we halt the root-finding algorithms after 20 successive approximations in order to reduce the timestep by a factor of $1.1$.
+The iteration is then repeated.
+
+In general however, the timestep must be limited more strictly to avoid a numerical instability.
+We find that for large $\Delta t$, after several hundred iterations, highly concave features develop in the advective flux term $\langle w'T' \rangle$ near $z=0$. 
+Such features are undesired, as they are uncommon in similar calculations \cite{Malkus_1954} and we do not believe they accurately represent the problem's physics.
+Further, we expect our algorithm to converge to the analytic solution of \eq{EQ:T0_IVP} for small $\Delta t$.
+Therefore results obtained uniquely via the use of relatively large $\Delta t$ must not agree with the analytic solution.
+If ignored, the concave features grow in magnitude until they affect $\bar{T}$ on a readily apparent scale.
+Eventually $\bar{T}$ develops oscillations near $z = 0$ and the timestep must be reduced.
+Once these oscillations reach some amplitude, they cannot be eliminated via timestep reduction and the roots of $\sigma_{\rm{max}}(A^2)$ vanish as before.
+To avoid this, we measure the extent of the numerical instability preemptively by evaluating the concavity $\frac{\partial^2}{\partial z^2} \langle w'T' \rangle|_{z=0}$ of the dominant $k_x = 1.5\pi$ mode.
+We find that reducing the timestep $\Delta t$ by the same factor of 1.1 when this concavity measure exceeds $10^{-6}$ curtails the problem.
+Both of these issues appear to become more prominent as the boundary layers diffuse over the course of the algorithm's implementation (see Figure~\ref{fig:T0_profiles}).
+Thus there is never a practical opportunity to increase the timestep.
 
@@
     %\begin{longtable}[c]{@{}*{6}{>{\arraybackslash}p{0.15\linewidth}}@{}}
-    \quad\quad\quad $\Ra$	\quad\quad\quad	&	\quad\quad\quad		$N_z$	\quad\quad\quad		&	\quad\quad\quad		$\Nu$	\quad\quad\quad		&	\quad\quad\quad		$\delta_0$	\quad\quad\quad		&	\quad\quad		$k_x$ marginals	\quad\quad\quad\\
-    %\hline
-    1.00E+05 & 256   & 5.9343  & 0.15746 \;    &   \; 1$\pi$, 1.5$\pi$ \\
-    2.00E+05 & 256   & 7.45986 & 0.12341 \;    &   \; 1.5$\pi$ \\
-    4.00E+05 & 256   & 8.92597 & 0.10395 \;    &   \; 1.5$\pi$ \\
-    1.00E+06 & 256   & 11.6689 & 0.07922 \;    &   \; 1.5$\pi$, 2.5$\pi$, 3$\pi$ \\
-    2.00E+06 & 256   & 14.8463 & 0.06345 \;    &   \; 1.5$\pi$, 3.5$\pi$ \\
-    4.00E+06 & 256   & 18.9433 & 0.04933 \;    &   \; 1.5$\pi$, 4.5$\pi$ \\
-    1.00E+07 & 256   & 25.6821 & 0.03632 \;    &   \; 1.5$\pi$, 5.5$\pi$ \\
-    2.00E+07 & 256   & 32.4531 & 0.02820 \;    &   \; 1.5$\pi$, 6.5$\pi$, 7$\pi$\\
-    4.00E+07 & 512   & 40.7925 & 0.02289 \;    &   \; 1.5$\pi$, 8$\pi$, 8.5$\pi$ \\
-    1.00E+08 & 512   & 55.4383 & 0.01690 \;    &   \; 1.5$\pi$, 4.5$\pi$, 10.5$\pi$, 11$\pi$\\
-    2.00E+08 & 512   & 69.8349 & 0.01318 \;    &   \; 1.5$\pi$, 5$\pi$, 13.5$\pi$, 14$\pi$ \\
-    4.00E+08 & 512   & 87.8525 & 0.01053 \;    &   \; 1.5$\pi$, 5.5$\pi$,17.5$\pi$ \\
-    1.00E+09 & 768   & 119.318 & 0.00817 \;    &   \; 1.5$\pi$, 6.0$\pi$, 6.5$\pi$, 23.5$\pi$, 24$\pi$ \\\vspace{0.1in}\\
+    \quad\quad\quad $\Ra$	\quad\quad\quad	&	\quad\quad\quad		$N_z$	\quad\quad\quad		&	\quad\quad\quad		$\Nu$	\quad\quad\quad		&	\quad\quad\quad		$\delta_0$	\quad\quad\quad		&	\quad\quad		$k_x$ marginals	\quad\quad\quad\\[0.03cm]
+    \hline
+    $10^5$ & 256   & 5.9343  & 0.15746 \;    &   \; 1$\pi$, 1.5$\pi$   \\[0.03cm]
+    $2 \times 10^5$ & 256   & 7.45986 & 0.12341 \;    &   \; 1.5$\pi$   \\[0.03cm]
+    $4 \times 10^5$ & 256   & 8.92597 & 0.10395 \;    &   \; 1.5$\pi$   \\[0.03cm]
+    $10^6$ & 256   & 11.6689 & 0.07922 \;    &   \; 1.5$\pi$, 2.5$\pi$, 3$\pi$   \\[0.03cm]
+    $2 \times 10^6$ & 256   & 14.8463 & 0.06345 \;    &   \; 1.5$\pi$, 3.5$\pi$   \\[0.03cm]
+    $4 \times 10^6$ & 256   & 18.9433 & 0.04933 \;    &   \; 1.5$\pi$, 4.5$\pi$   \\[0.03cm]
+    $10^7$ & 256   & 25.6821 & 0.03632 \;    &   \; 1.5$\pi$, 5.5$\pi$   \\[0.03cm]
+    $2 \times 10^7$ & 256   & 32.4531 & 0.02820 \;    &   \; 1.5$\pi$, 6.5$\pi$, 7$\pi$  \\[0.03cm]
+    $4 \times 10^7$ & 512   & 40.7925 & 0.02289 \;    &   \; 1.5$\pi$, 8$\pi$, 8.5$\pi$   \\[0.03cm]
+    $10^8$ & 512   & 55.4383 & 0.01690 \;    &   \; 1.5$\pi$, 4.5$\pi$, 10.5$\pi$, 11$\pi$  \\[0.03cm]
+    $2 \times 10^8$ & 512   & 69.8349 & 0.01318 \;    &   \; 1.5$\pi$, 5$\pi$, 13.5$\pi$, 14$\pi$   \\[0.03cm]
+    $4 \times 10^8$ & 512   & 87.8525 & 0.01053 \;    &   \; 1.5$\pi$, 5.5$\pi$,17.5$\pi$   \\[0.03cm]
+    $10^9$ & 768   & 119.318 & 0.00817 \;    &   \; 1.5$\pi$, 6.0$\pi$, 6.5$\pi$, 23.5$\pi$, 24$\pi$ \\\vspace{0.1in}\\
     %\hline

### 2021-05-12 publication_materials/ms_rbc.tex
touch up sec V appendix B

@@
 where $p$ is pressure and $T$ is temperature. 
-For completeness, we specify a final boundary condition $p = p_0$ at $z = \pm 1/2$. 
+For completeness, we specify a final boundary condition $p = p_0$ at $z = - 1/2$. 
 Any system of this form can be characterized by its dimensionless Rayleigh number $\Ra = \frac{g\alpha L^3 \Delta T}{\nu \kappa}$ and Prandtl number $\Pr = \frac{\nu}{\kappa}$, where $g, \, \alpha, \, L_z, \, \Delta T, \nu, \kappa$ are the gravitational acceleration, coefficient of thermal expansion, domain height, opposed temperature difference, kinematic viscosity, and thermal diffusivity respectively.
@@
 We initialize these IVPs with the marginally stable temperature of the current iteration.
-Suppose $\tilde{k_x}$ is the wavenumber of the marginally-stable mode.
-Then, using the diffused and advected profiles, we compute the eigenvalues $\sigma_{\rm{diff}}$ and $\sigma_{\rm{adv}}$ at $k_x = \tilde{k_x}$.
+Suppose $k_0$ is the wavenumber of the marginally-stable mode.
+Then, using the diffused and advected profiles, we compute the eigenvalues $\sigma_{\rm{diff}}$ and $\sigma_{\rm{adv}}$ at $k_x = k_0$.
 The appropriate amplitude $A^2$ can then be approximated by 
@@
 where $W_n$ and $\theta_n$ are the eigenmodes associated with $k_x = \frac{n\pi}{2}$. 
-There are now $N$ modes, each having their own amplitude to solve for and eigenvalue to keep marginally-stable. 
+There are now $N$ modes, each with their own amplitude to solve for and eigenvalue to keep marginally-stable. 
 Given a small fixed time step $\Delta t$, let $\vec{A^2}$ be the amplitude vector and $\vec{\sigma}(\vec{A^2})$ be the dependent eigenvalues.
@@
 Here $\vec{\sigma_{\rm{diff}}} = \vec{\sigma} (\vec{0})$ refers to the eigenvalues after a brief $\Delta t$ period of diffusion. 
-We account for the influence f $N$ advection terms on $N$ eigenvalues (one for each mode) by constructing an eigenvalue matrix $\Sigma_{\rm{adv}} \in \mathbb{R}^{N \times N}$.
-For example, the element of $\Sigma_{\rm{adv}}$ at row $i$ and column $j$ is given by the $i$th mode's eigenvalue due to advection by the $j$th mode's eigenfunctions. 
+We account for the influence of $N$ advection terms on $N$ eigenvalues (one for each mode) by constructing an eigenvalue matrix $\Sigma_{\rm{adv}} \in \mathbb{R}^{N \times N}$.
+For example, the element of $\Sigma_{\rm{adv}}$ at row $i$ and column $j$ is given by the $i$th mode's eigenvalue after a $\Delta t$ period of advection by the $j$th mode's eigenfunctions. 
 At the point of our preliminary estimate $\vec{A^2_0}$, we approximate the Jacobian matrix 
@@
 We also find that the average kinetic energies of simulations initialized with MSTE are significantly larger than those found in simulations initialized with no-flow MSTE and with the conductive state plus noise, as shown Figure~\ref{fig:ke_sim}.
-This is because the MSTE contain strong large-scale flows, which decay on a viscous time-scale $t_{\nu}$. Two viscous time-scales can be derived for this problem: one for the boundary layer 
+This is because the MSTE contain strong large-scale flows, which decay on a viscous time-scale $t_{\nu}$. 
+Two viscous time-scales can be derived for this problem: one for the boundary layer 
 \begin{align*}
@@
 \end{align*}
-Empirically, we find $t_{\nu} \approx 200$ suggesting the true kinetic energy decary time-scale is based on a length scale which is longer than the boundary layer weight $\delta_0$ but shorter than the domain height $L_z$.
+Empirically, we find $t_{\nu} \approx 200$ suggesting the true kinetic energy decary time-scale is based on a length scale which is longer than the boundary layer height $\delta_0$ but shorter than the domain height $L_z$.
 Consequently, MSTE initial conditions do not reduce the simulation time required to achieve a statistically-steady state---rather they increase it considerably!
@@
 This is due to coupling between the eigenfunctions $W(z)$, $\Theta(z)$ and the mean temperature profile $\bar{T}$.
-In the context of our algorithm, this effectively deletes the sought-after root of the maximum eigenvalue function $\sigma_{\rm{max}}(A^2)$ causing the root-finding methods to fail. 
-This is not a numerical instability, rather, it is a limitation of our timestepping algorithm.
+In the context of our algorithm, this effectively deletes the sought-after root of the maximum eigenvalue function $\sigma_{\rm{max}}(A^2)$, causing the root-finding methods to fail. 
+This is not a numerical instability, rather, it is an inherent limitation of our timestepping algorithm.
 To curtail this, we halt the root-finding algorithms after 20 successive approximations in order to reduce the timestep by a factor of $1.1$.
@@
 
-In general however, the timestep must be limited more strictly to avoid a numerical instability.
+The timestep must be also reduced to avoid a numerical instability.
 We find that for large $\Delta t$, after several hundred iterations, highly concave features develop in the advective flux term $\langle w'T' \rangle$ near $z=0$. 
@@
 Once these oscillations reach some amplitude, they cannot be eliminated via timestep reduction and the roots of $\sigma_{\rm{max}}(A^2)$ vanish as before.
-To avoid this, we measure the extent of the numerical instability preemptively by evaluating the concavity $\frac{\partial^2}{\partial z^2} \langle w'T' \rangle|_{z=0}$ of the dominant $k_x = 1.5\pi$ mode.
-We find that reducing the timestep $\Delta t$ by the same factor of 1.1 when this concavity measure exceeds $10^{-6}$ curtails the problem.
+To avoid this, we measure the extent of the numerical instability preemptively by evaluating the absolute concavity $|\frac{\partial^2}{\partial z^2} \langle w'T' \rangle|_{z=0}|$ of the dominant $k_x = 1.5\pi$ mode.
+We find that reducing the timestep $\Delta t$ by the same factor of 1.1 whenever this concavity measure exceeds $10^{-6}$ curtails the problem.
 Both of these issues appear to become more prominent as the boundary layers diffuse over the course of the algorithm's implementation (see Figure~\ref{fig:T0_profiles}).

### 2021-05-13 publication_materials/ms_rbc.tex
More edits.

@@
 \begin{abstract}
-    Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important properties remain elusive---particularly in the turbulent regime.
+    Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important properties remain elusive.
     In this investigation, we derive and solve a quasilinear form of the Rayleigh-Bénard problem by representing the perturbations in terms of marginally stable eigenmodes.
@@
 The quasilinear approximation starts with a decomposition of all variables into a background and perturbations about this background.
-This approximation neglects the influence of nonlinear interactions between the perturbations on the perturbations themselves \cite{marston2016}.
+This approximation neglects the nonlinear interactions between perturbations which modify the perturbations themselves \cite{marston2016}.
 This renders the perturbation equations linear.
@@
 In \cite{Beaume_2015}, researchers compute ECS in parallel shear flows by deriving and solving a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments. 
-They assume the background velocity evolves on a slow time-scale, and to determine the perturbation amplitudes they require marginal stability at each timestep.
-A similar strategy is employed by \cite{michel_chini_2019} to studying acoustic streaming.
+They assume the background velocity evolves on a slow time-scale, and, to determine the perturbation amplitudes, they require marginal stability at each timestep.
+A similar strategy is employed by \cite{michel_chini_2019} to study acoustic streaming.
 In that work, an analytic expression for the first-order perturbation's amplitude is found by deriving a solvability condition.
@@
 where $p$ is pressure and $T$ is temperature. 
-For completeness, we specify a final boundary condition $p = p_0$ at $z = - 1/2$. 
+%For completeness, we specify a final boundary condition $p = p_0$ at $z = - 1/2$. 
 Any system of this form can be characterized by its dimensionless Rayleigh number $\Ra = \frac{g\alpha L^3 \Delta T}{\nu \kappa}$ and Prandtl number $\Pr = \frac{\nu}{\kappa}$, where $g, \, \alpha, \, L_z, \, \Delta T, \nu, \kappa$ are the gravitational acceleration, coefficient of thermal expansion, domain height, opposed temperature difference, kinematic viscosity, and thermal diffusivity respectively.
@@
 
-To solve \eq{EQ:T0_IVP} numerically, we need an expression for the perturbation so we can calculate the advective heat flux.
+To solve \eq{EQ:T0_IVP} numerically, we need an expression for the perturbations so we can calculate the advective heat flux.
 Here we will make the quasilinear approximation, dropping the $\vec{u}'\vec{\cdot}\vec{\nabla}\vec{u}'$ and $\vec{u}'\vec{\cdot}\vec{\nabla}T'$ terms from the evolution equations for the perturbations.
@@
 But the evolution of $\bar{T}$ also influences the perturbations, as equation~\ref{EQ:linear3} depends on $\partial_z \bar{T}$.
-Thus, the mean temperature and perturbations fields are coupled.
+Thus, the mean temperature and perturbation fields are coupled.
 
@@
 For various $\Ra$ and fixed $\Pr = 1$, we seek marginally-stable thermal equilibria (MSTE) satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to \eq{EQ:T0_IVP}. 
-We employ the \texttt{Dedalus} pseudo-spectral python framework \cite{Dedalus_2020} to solve the EVP outlined in Section \ref{sec:model} as well as the IVP \eq{EQ:T0_IVP}.
+We employ the \texttt{Dedalus} pseudo-spectral python framework \cite{Dedalus_2020} to solve the eigenvalue problem outlined in Section \ref{sec:model} as well as the time evolution equations \eq{EQ:T0_IVP}.
 We represent each field with Chebyshev polynomials and use the 3/2 dealiasing rule to calculate the advective heat flux.
@@
 
-At iteration 0 we construct a marginally-stable initial temperature profile $\bar{T}(z, 0)$ whose equation is given in appendix~\ref{sec:initial_profile}. 
-At an arbitrary iteration beginning at $t = t_0$, we seek to evolve $\bar{T}(z, t_0)$ into a new marginally-stable profile $\bar{T}(z, t_0 + \Delta t)$ according to \eq{EQ:T0_IVP}. 
-To achieve this, we use a second-order, two-stage IMEX Runge-Kutta method.
-We initialize \eq{EQ:T0_IVP} with the previous iteration's solution to \eq{EQ:T0_IVP} and maintain marginal stability at each iteration.
-The eigenfunctions and amplitude are assumed to be constant over the timestep.
-We can solve the IVP over long periods of time by stopping regularly (at each iteration) to adjust the eigenfunctions and their amplitude $A$.
+To initialize our calculations, we construct a marginally-stable initial temperature profile $\bar{T}(z, t=0)$ whose equation is given in appendix~\ref{sec:initial_profile}. 
+We use \eq{EQ:T0_IVP} to evolve $\bar{T}(z, t_0)$ into a new marginally-stable profile $\bar{T}(z, t_0 + \Delta t)$.
+We use a second-order, two-stage IMEX Runge-Kutta method.
+The eigenfunctions and amplitudes are assumed to be constant over the timestep.
+We symmetrize $\bar{T}$ by setting the coefficients of its even Chebyshev basis functions to zero at the start of each timestep.
+This ensures $\bar{T}(z) = -\bar{T}(-z)$.
+On every timestep, we calculate the marginally stable eigenfunctions and their amplitude $A$.
 It is essential that we pick the correct eigenfunction amplitude when calculating the advective term to maintain marginal stability.
@@
     \caption{Eigenvalue spectra for $\Ra = 10^5$. The spectrum of an ``initial" marginally-stable mean temperature profile $\bar{T}(z, t_0)$ has a maximum eigenvalue of 0. 
-    Given a small fixed timestep $\Delta t$, diffusion destabilizes the system, increasing its eigenvalues. 
-    Advection tends to stabilize the system, decreasing its eigenvalues. 
-    We find the eigenfunction amplitude $A^2$ such that the combination of diffusion and advection yields a new, ``evolved'', marginally-stable mean temperature profile $\bar{T}(z, t_0 + \Delta t)$.
+    Given a small fixed timestep $\Delta t$, diffusion destabilizes the system, increasing $\sigma$. 
+    Advection tends to stabilize the system, decreasing $\sigma$. 
+    We find the eigenfunction amplitude $A^2$ such that the combination of diffusion and advection yields a new, ``evolved,'' marginally-stable mean temperature profile $\bar{T}(z, t_0 + \Delta t)$.
 In this case $A^2 \approx 1$ due to approximately equal magnitudes of the diffused and advected eigenvalues.}
@@
 
-An iteration is performed as follows.
 Consider a marginally-stable temperature profile $\bar{T}(z, t_0)$.
-By definition, its maximum eigenvalue is 0.
-Diffusing $\bar{T}(z, t_0)$ tends to increase its eigenvalues while ignoring the diffusive term and evolving according to advection tends the stabilize the system.
+By definition, its maximum growth rate is 0.
+Diffusing $\bar{T}(z, t_0)$ tends to increase its growth rates while ignoring the diffusive term and evolving according to advection tends to decrease its growth rates.
 $A$ must be selected such that these two influences are equal and opposite.
 We can measure the effects of diffusion and advection on the maximum eigenvalue by solving two new IVPs
-\begin{align}
+\begin{align}\label{eqn:diffusion_only}
     &\frac{\partial \bar{T}_{\rm{diff}}}{\partial t} = \mathcal{P} \frac{\partial^2 \bar{T}_{\rm{diff}}}{\partial z^2} \\
@@
 where $\bar{T}_{\rm{diff}}$ and $\bar{T}_{\rm{adv}}$ denote to the diffused and advected temperature profiles.
-We initialize these IVPs with the marginally stable temperature of the current iteration.
+We initialize $\bar{T}_{\rm{diff}}$ and $\bar{T}_{\rm{adv}}$ with $\bar{T}(z, t_0)$, and evolve the equations to $t=t_0+\Delta t$.
 Suppose $k_0$ is the wavenumber of the marginally-stable mode.
-Then, using the diffused and advected profiles, we compute the eigenvalues $\sigma_{\rm{diff}}$ and $\sigma_{\rm{adv}}$ at $k_x = k_0$.
+Then, using the diffused and advected profiles, we compute the eigenvalues $\sigma_{\rm{diff}}$ and $\sigma_{\rm{adv}}$ at $k_x = k_0$ and $t=t_0+\Delta t$.
 The appropriate amplitude $A^2$ can then be approximated by 
@@
 The subscript 0 denotes a preliminary estimate which we later refine.
-$\bar{T}(z, t)$ is then evolved according to \eq{EQ:T0_IVP} and another eigenvalue solve is performed. 
-Given a fixed timestep $\Delta t$, we assume the dominant eigenvalue can be described by a continuous function $\sigma_{\rm{max}} (A^2)$ which is locally differentiable. 
-We use Newton's method to find an amplitude which satisfies our marginal stability tolerance criterion $|\sigma_{\rm{max}} (A^2)| < 10^{-9}$.
+
+Using the amplitude $A_0^2$, the background temperature $\bar{T}(z, t_0)$ is then evolved to $t=t_0+\Delta t$ according to \eq{EQ:T0_IVP} and another eigenvalue solve is performed. 
+This background temperature is typically close to, but not exactly, marginally stable.
+We use Newton's method to find an amplitude $A^2$ such that the maximum growth rate is zero to within $10^{-9}$.
 Marginally-stable modes do not oscillate in time, i.e. $\sigma = 0$ implies $\omega = 0$.
@@
 \subsection{Treatment of Multiple Marginally-Stable Modes} \label{sec:multiple_modes}
-In most cases, we encounter eigenvalue spectra with multiple simultaneously marginal modes.
+In most cases, we encounter eigenvalue spectra with multiple marginal modes.
 To accommodate this we generalize the advective term in \eq{EQ:T0_IVP} to accommodate $N$ simultaneously marginal modes
@@
 \end{equation}
-where $W_n$ and $\theta_n$ are the eigenmodes associated with $k_x = \frac{n\pi}{2}$. 
+where $W_n$ and $\theta_n$ are the marginally stable eigenmodes associated with different values of $k_x$. 
 There are now $N$ modes, each with their own amplitude to solve for and eigenvalue to keep marginally-stable. 
-Given a small fixed time step $\Delta t$, let $\vec{A^2}$ be the amplitude vector and $\vec{\sigma}(\vec{A^2})$ be the dependent eigenvalues.
-We expect a function $\vec{\sigma} \, : \, \mathbb{R}^N \to  \mathbb{R}^N$ to have isolated roots $\vec{\tilde{A}^2}$ (should they exist). 
-A preliminary approximation $\vec{A^2_0}$ for the appropriate amplitude vector $\vec{\tilde{A}^2}$ is given by a generalized form of \eq{EQ:amp_approx}:
+Given a small fixed time step $\Delta t$, let $\vec{A^2}$ be the amplitude vector and $\vec{\sigma}(\vec{A^2})$ be the eigenvalues of the $N$ modes.
+We are searching for $\vec{\tilde{A}^2}$ that satisfies of $\vec{\sigma}(\vec{\tilde{A}^2})=0$.
+We approximate the amplitudes with $\vec{A^2_0}$ by generalizing \eq{EQ:amp_approx}:
 \begin{equation}
@@
 \end{equation}
-Here $\vec{\sigma_{\rm{diff}}} = \vec{\sigma} (\vec{0})$ refers to the eigenvalues after a brief $\Delta t$ period of diffusion. 
-We account for the influence of $N$ advection terms on $N$ eigenvalues (one for each mode) by constructing an eigenvalue matrix $\Sigma_{\rm{adv}} \in \mathbb{R}^{N \times N}$.
-For example, the element of $\Sigma_{\rm{adv}}$ at row $i$ and column $j$ is given by the $i$th mode's eigenvalue after a $\Delta t$ period of advection by the $j$th mode's eigenfunctions. 
-At the point of our preliminary estimate $\vec{A^2_0}$, we approximate the Jacobian matrix 
+Here $\vec{\sigma_{\rm{diff}}} = \vec{\sigma} (\vec{0})$ refers to the eigenvalues of the background temperature after evolving under only diffusion (equation \ref{eqn:diffusion_only}) for a time interval $\Delta t$.
+We account for the influence of $N$ advection terms on $N$ eigenvalues (one for each mode) by constructing an eigenvalue matrix $\Sigma_{\rm{adv}}$.
+To calculate element of $\Sigma_{\rm{adv}}$ at row $i$ and column $j$, we evolve the background temperature under only advection by mode $j$ for a time interval $\Delta t$.
+Then the $i,j$ component of $\Sigma_{\rm{adv}}$ is given by the eigenvalue of the $i$th mode.
+
+Our estimate $\vec{A^2_0}$ does not give a background temperature for which all $N$ modes are exactly marginally stable.
+We refine our vector of amplitudes via Newton's method.
+This requires calculating the Jacobian matrix 
 \begin{equation}
@@
         \nabla \sigma_N (A_1, A_2, ..., A_N) 
-    \end{bmatrix}
+    \end{bmatrix}.
 \end{equation}
-via first-order finite differences, requiring $N^2$ more individual EVP solves.
-A once-refined estimate $\vec{A^2_1}$ is then given by
-% The $k$th row of $J_0$ is then given by the gradient of the $k$th mode's eigenvalue $\nabla \sigma_k$.
-\begin{equation}
-    \vec{\tilde{A}^2} \approx \vec{A^2_1} = -J^{-1} \vec{\sigma}(\vec{A^2_0}).
-\end{equation}
-We then use each subsequent guess to adjust the Jacobian via Broyden's method for root-finding in multi-dimensional functions \cite{Broyden}.
+We approximate $J$ via first-order finite differences, which requires an additional $N^2$ sparse eigenvalue solves.
+%A once-refined estimate $\vec{A^2_1}$ is then given by
+%% The $k$th row of $J_0$ is then given by the gradient of the $k$th mode's eigenvalue $\nabla \sigma_k$.
+%\begin{equation}
+%    \vec{\tilde{A}^2} \approx \vec{A^2_1} = -J^{-1} \vec{\sigma}(\vec{A^2_0}).
+%\end{equation}
+%We then use each subsequent guess to adjust the Jacobian via Broyden's method for root-finding in multi-dimensional functions \cite{Broyden}.
+We iterate Newton's method until all marginally stable modes have eigenvalues within $10^{-9}$ of zero.
 We find $\vec{\sigma}(\vec{A^2})$ does indeed have a unique root provided the time step is not too large and there are no numerical instabilities, as outlined in appendix \ref{sec:timestep}.
@@
 Over the course of a large time step, $\bar{T}$ evolves according to \eq{EQ:T0_IVP} and eventually the original eigenfunctions cease to provide a stabilizing influence.
-It is precisely for this reason why we must halt the IVP regularly to adjust the eigenfunctions and their amplitudes.
+This limits the timestep size we can take.
 
-Difficulty arises when transitioning between different numbers of marginal modes, particularly when stable modes become marginally-stable mid-iteration.
+Difficulty arises when transitioning between different numbers of marginal modes.
 We facilitate these transitions by defining an adjustable candidate tolerance $\varepsilon_{\rm{cand}} \in [10^{-6}, 10^{-8}]$.
@@
 Otherwise the mode becomes marginally-stable.
-
-After several time steps, $\bar{T}$ tends to asymmetrize due to numerical noise. 
-Though asymmetric pairs of solutions may exist, we further constrain $\bar{T}$ by setting the coefficients of its even Chebyshev basis functions to zero at the start of each iteration.
 
@@
 
-Figure~\ref{fig:T0_profiles} gives temperature profiles for $\Ra = 10^8$ where the initial profile, whose construction is outlined in appendix~\ref{sec:initial_profile}, is employed at iteration 0. 
-Direct numerical simulations (DNS) are performed by solving \eqss{EQ:motion1}{EQ:motion3} with \texttt{Dedalus}, followed by horizontal- and time- averaging. 
-The DNS curve is more diffuse than the MSTE curve, which in turn, is more diffuse than the initial curve. 
+Figure~\ref{fig:T0_profiles} gives temperature profiles for $\Ra = 10^8$, where the initial profile is outlined in appendix~\ref{sec:initial_profile}. 
+We ran a direct numerical simulation (DNS) of \eqss{EQ:motion1}{EQ:motion3} with \texttt{Dedalus}, and also plot the horizontal- and time- averaged temperature profile. 
+The temperature boundary layers in the DNS are wider than in the MSTE, which is in turn wider than the boundary layer of the initial temperature profile.
 Performing an eigenvalue solve by setting $\bar{T}$ equal to the DNS profile yields unstable eigenvalues. 
@@
     \end{tabular}
-    \caption{Heat fluxes (left) and eigenvalue spectra (right) of equilibrated states $\Ra = 2 \times 10^5$ (top) and $\Ra = 10^9$ (bottom). 
+    \caption{Heat fluxes (left) and eigenvalue spectra (right) of equilibrated states with $\Ra = 2 \times 10^5$ (top) and $\Ra = 10^9$ (bottom). 
     The heat flux profiles are symmetric about $z=0$, so we only plot for $z<0$.
-    Advection profiles belong to marginally-stable modes. 
-    For low $\Ra$, a single mode with $k_x = 1.5\pi$ is sufficient to oppose boundary layer diffusion and facilitate heat flux throughout the bulk of the domain. 
-    For large $\Ra$, high-wavenumber modes contribute pronounced small-scale advection profiles which tightly hug the thin boundary layers. 
-    A combination of of progressively wider advection profiles is necessary to transition to the $k_x = 1.5\pi$ mode.}
+    We plot the advection profiles for marginally-stable modes. 
+    At low $\Ra$, a single mode with $k_x = 1.5\pi$ is sufficient to oppose boundary layer diffusion and facilitate heat flux throughout the bulk of the domain. 
+    At large $\Ra$, high-wavenumber modes contribute pronounced small-scale advection profiles which tightly hug the thin boundary layers. 
+    A combination of of progressively wider advection profiles is necessary to transition to bulk advection provided by the $k_x = 1.5\pi$ mode.}
     \label{fig:flux}
@@
 
-In Figure~\ref{fig:flux}, where we give heat flux profiles and eigenvalue spectra for two cases: $\Ra = 2 \times 10^5$ (top) and $\Ra = 10^9$ (bottom). 
+In Figure~\ref{fig:flux}, we give heat flux profiles and eigenvalue spectra for two cases: $\Ra = 2 \times 10^5$ (top) and $\Ra = 10^9$ (bottom). 
 For $\Ra = 2 \times 10^5$, there is a single marginal mode at $k_x = 1.5\pi$ whose advective flux occupies the bulk of the domain. 
-These states have wide boundary layers which gradually subside as advection becomes the dominant flux component. 
+These states have wide boundary layers, with diffusive fluxes which gradually subside as advection becomes the dominant flux component. 
 Transitional regions occur over a smaller length scale for $\Ra = 10^9$ where the shift from diffusion to advection is sharp.
@@
 If we allowed wavenumbers to vary continuously, there would be an unstable mode between these pairs of wavenumbers.
-However, since we have fixed the horizontal size of our domain, we are left with pairs of discrete margin modes.
+However, since we have fixed the horizontal size of our domain, we are left with pairs of discrete marginal modes.
 
@@
 In Figure~\ref{fig:kx_marginals} we give the wavenumbers $k_x$ of marginal modes. 
-For some values of $\Ra$ we obtain states with pairs marginally-stable modes, with wavenumbers separated by $\pi/2$.
+For some values of $\Ra$ we obtain states with pairs of marginally-stable modes, with wavenumbers separated by $\pi/2$.
 Like $k_x = 6\pi, \, 6.5\pi$ and $k_x=23.5\pi, \, 24\pi$ for the $\Ra=10^9$ MSTE, these are due to the discretization of wavenumbers from our domain of width 4.
@@
 Least-squares regression gives $\max\{k_x\} \propto \Ra^{0.300}$ with $R^2 = 0.998$ for this maximum branch.
-For large $\Ra$, the advective fluxes of this maximum branch opposes the strong diffusion of the thin MSTE boundary layers. 
+For large $\Ra$, the advective fluxes of this maximum branch compensates for the strongly peaked diffusive flux in the thin boundary layers. 
 At $\Ra \geq 10^8$, a third branch appears (shown in blue), splitting the widening gap between the other two. 
@@
 \end{align}
-where $\theta_n(z), U_n(z), W_n(z), P_n(z); \, A_n; $ and $k_{x_n}$ refer to the complex eigenfunctions, amplitude, and wavenumber at the $n$th marginal mode respectively. 
+where $\theta_n(z), U_n(z), W_n(z), P_n(z); \, A_n; $ and $k_{x_n}$ refer to the complex eigenfunctions, amplitude, and wavenumber of the $n$th marginal mode respectively. 
 Note that although the MSTE is an equilibrium of the quasilinear equations, it is not an equilibrium of the full nonlinear equations.
@@
 \begin{align*}
-    t_{\nu,\delta} &= \frac{L_z}{\mathcal{P}} = 10^4
+    t_{\nu,\delta} &= \frac{L_z}{\mathcal{P}} = 2.8561
 \end{align*}
@@
     \intertext{and another for the entire domain}
-    t_{\nu,\mathcal{D}} &= \frac{\delta^2_0}{\mathcal{P}} = 2.8561.
+    t_{\nu,L_z} &= \frac{\delta^2_0}{\mathcal{P}} = 10^4.
 \end{align*}
-Empirically, we find $t_{\nu} \approx 200$ suggesting the true kinetic energy decary time-scale is based on a length scale which is longer than the boundary layer height $\delta_0$ but shorter than the domain height $L_z$.
+Empirically, we find $t_{\nu} \approx 200$ suggesting the true kinetic energy decary time-scale is based on a length scale which is longer than the boundary layer height $\delta$ but shorter than the domain height $L_z$.
 Consequently, MSTE initial conditions do not reduce the simulation time required to achieve a statistically-steady state---rather they increase it considerably!
-This suggests the MSTE background state perspective is partially flawed, as a more useful background state would approximate the kinetic energy with more fidelity.
+This is alleviated by using the MSTE temperature profile, without including any velocity perturbations.
+The MSTE temperature state is a promising candidate initial condition for high-Rayleigh number convection simulations.
 
@@
 The marginal stability constraint then fixes the ratio between advection and diffusion (eigenfunction amplitude $A^2$). 
-We use standard root-finding algorithms to solve for the appropriate $A^2$ at each iteration, until, the fixed combination of diffusion and advection sum to a constant flux.
+We use standard root-finding algorithms to solve for the appropriate $A^2$ at each timestep, until, the  combination of diffusive and advective flux sum to a constant.
 The MSTE calculation is a one-dimensional problem, combining eigenvalue solves, and the time evolution of the one-dimensional mean temperature profile.
@@
 This requires more computational effort to achieve relaxation when compared to the conventional conductive initial condition \eq{EQ:linear_ic}.
+Initializing with only the temperature state of the MSTE avoids an early convective transient, but does not have excessive large-scale flows.
+These state could be excellent initial conditions for high-Rayleigh number DNS.
 
@@
 \section{Numerical Instabilities and Timestep Management} \label{sec:timestep}
-A suitable timestep $\Delta t$ must be selected at the start of each iteration.
-For sufficiently large $\Delta t$, we find the advective flux terms fail to provide a stabilizing influence.
+To find MSTE, we advance $\bar{T}$ by timesteps of size $\Delta t$.
+For large $\Delta t$, we find the advective flux terms fail to provide a stabilizing influence.
 This is due to coupling between the eigenfunctions $W(z)$, $\Theta(z)$ and the mean temperature profile $\bar{T}$.
@@
 This is not a numerical instability, rather, it is an inherent limitation of our timestepping algorithm.
-To curtail this, we halt the root-finding algorithms after 20 successive approximations in order to reduce the timestep by a factor of $1.1$.
-The iteration is then repeated.
+To curtail this, we halt the root-finding algorithms after 20 successive approximations, and reduce the timestep by a factor of 1.1, and try again.
 
@@
 We find that for large $\Delta t$, after several hundred iterations, highly concave features develop in the advective flux term $\langle w'T' \rangle$ near $z=0$. 
-Such features are undesired, as they are uncommon in similar calculations \cite{Malkus_1954} and we do not believe they accurately represent the problem's physics.
-Further, we expect our algorithm to converge to the analytic solution of \eq{EQ:T0_IVP} for small $\Delta t$.
-Therefore results obtained uniquely via the use of relatively large $\Delta t$ must not agree with the analytic solution.
+Such features are undesired, as they are uncommon in similar calculations \cite{Malkus_1954} and we do not believe they accurately represent a physical process.
+%Further, we expect our algorithm to converge to the analytic solution of \eq{EQ:T0_IVP} for small $\Delta t$.
+%Therefore results obtained uniquely via the use of relatively large $\Delta t$ must not agree with the analytic solution.
 If ignored, the concave features grow in magnitude until they affect $\bar{T}$ on a readily apparent scale.
 Eventually $\bar{T}$ develops oscillations near $z = 0$ and the timestep must be reduced.
-Once these oscillations reach some amplitude, they cannot be eliminated via timestep reduction and the roots of $\sigma_{\rm{max}}(A^2)$ vanish as before.
-To avoid this, we measure the extent of the numerical instability preemptively by evaluating the absolute concavity $|\frac{\partial^2}{\partial z^2} \langle w'T' \rangle|_{z=0}|$ of the dominant $k_x = 1.5\pi$ mode.
-We find that reducing the timestep $\Delta t$ by the same factor of 1.1 whenever this concavity measure exceeds $10^{-6}$ curtails the problem.
+Once these oscillations reach some amplitude, they cannot be eliminated via timestep reduction and the roots of $\sigma_{\rm{max}}(A^2)$ vanish.
+To avoid this, we measure the curvature of the advective flux $|\frac{\partial^2}{\partial z^2} \langle w'T' \rangle|_{z=0}|$ of the dominant $k_x = 1.5\pi$ mode.
+We find that reducing the timestep $\Delta t$ by the same factor of 1.1 whenever this curvature measure exceeds $10^{-6}$ curtails the problem.
 Both of these issues appear to become more prominent as the boundary layers diffuse over the course of the algorithm's implementation (see Figure~\ref{fig:T0_profiles}).
@@
     %\begin{longtable}[c]{@{}*{6}{>{\arraybackslash}p{0.15\linewidth}}@{}}
-    \quad\quad\quad $\Ra$	\quad\quad\quad	&	\quad\quad\quad		$N_z$	\quad\quad\quad		&	\quad\quad\quad		$\Nu$	\quad\quad\quad		&	\quad\quad\quad		$\delta_0$	\quad\quad\quad		&	\quad\quad		$k_x$ marginals	\quad\quad\quad\\[0.03cm]
+    \quad\quad\quad $\Ra$	\quad\quad\quad	&	\quad\quad\quad		$N_z$	\quad\quad\quad		&	\quad\quad\quad		$\Nu$	\quad\quad\quad		&	\quad\quad\quad		$\delta_0$	\quad\quad\quad		&	\quad\quad	marginal $k_x$	\quad\quad\quad\\[0.03cm]
     \hline

### 2021-05-14 publication_materials/ms_rbc.tex
merged yesterday's changes: forgot to push

@@
 Reduced models are potentially useful in this context because they may allow us to study the problem with less expensive computations.
-Another approach relates to unstable exact coherent states (ECS) \cite{Waleffe, Sondak, Wen, chini_cells}. 
+Another approach relates to unstable exact coherent states (ECS) which are steady solutions to the full nonlinear problem \cite{Waleffe, Sondak, Wen, chini_cells}. 
 Simulations and analysis performed by \cite{Yalniz, Cvitanovic} suggest that chaotic solution trajectories might ``visit'' these ECS.
@@
 
-To solve \eq{EQ:T0_IVP} numerically, we need an expression for the perturbations so we can calculate the advective heat flux.
+To solve \eq{EQ:T0_IVP} numerically, we need an expression for the perturbation so we can calculate the advective heat flux.
 Here we will make the quasilinear approximation, dropping the $\vec{u}'\vec{\cdot}\vec{\nabla}\vec{u}'$ and $\vec{u}'\vec{\cdot}\vec{\nabla}T'$ terms from the evolution equations for the perturbations.
-Substituting \eqss{EQ:reynolds_dc_u}{EQ:reynolds_dc_p} into \eqss{EQ:motion1}{EQ:motion3} followed by subtracting \eq{EQ:T0_IVP} and \eq{EQ:p_bar} from the resulting temperature and $\hat{z}$ momentum equations gives
+Substituting \eqss{EQ:reynolds_dc_u}{EQ:reynolds_dc_p} into \eqss{EQ:motion1}{EQ:motion3} followed by subtracting \eqs{EQ:T0_IVP}{EQ:p_bar} from the resulting temperature and $\hat{z}$ momentum equations gives
 \begin{align}
@@
 We represent each field with Chebyshev polynomials and use the 3/2 dealiasing rule to calculate the advective heat flux.
-The necessary number of basis functions increases with $\Ra$ as the eigenfunctions include increasingly small-scale features. 
+The necessary number of basis functions increases with $\Ra$ as the eigenfunctions include increasingly small-scale features (see Appendix \ref{sec:tables}). 
 We use the \texttt{Eigentools} package \cite{Eigentools} to manipulate the eigenfunctions and calculate the advective heat flux $\langle w' T' \rangle_x$.
@@
 Then, using the diffused and advected profiles, we compute the eigenvalues $\sigma_{\rm{diff}}$ and $\sigma_{\rm{adv}}$ at $k_x = k_0$ and $t=t_0+\Delta t$.
-The appropriate amplitude $A^2$ can then be approximated by 
+A preliminary approximation $\Lambda^2_0$ of the appropriate amplitude $A^2$ is given by
 \begin{equation}
-    A^2 \approx A^2_0 \equiv -\frac{\sigma_{\rm{diff}}}{\sigma_{\rm{adv}}} \label{EQ:amp_approx}
+    A^2 \approx \Lambda^2_0 \equiv -\frac{\sigma_{\rm{diff}}}{\sigma_{\rm{adv}}} \label{EQ:amp_approx}
 \end{equation}
-where the square in $A^2_0$ is due to the quadratic nonlinearity of the eigenfunctions in the advective term and the minus sign is due to the fact that $\sigma_{\rm{adv}} < 0$ and $\sigma_{\rm{diff}} > 0$ in general.
+where the square in $A^2$ and $\Lambda^2_0$ is due to the quadratic nonlinearity of the eigenfunctions in the advective term and the minus sign is due to the fact that $\sigma_{\rm{adv}} < 0$ and $\sigma_{\rm{diff}} > 0$ in general.
 We illustrate these trends in Figure~\ref{fig:iteration_spectra}. 
@@
 
-Using the amplitude $A_0^2$, the background temperature $\bar{T}(z, t_0)$ is then evolved to $t=t_0+\Delta t$ according to \eq{EQ:T0_IVP} and another eigenvalue solve is performed. 
+Using the approximate amplitude $\Lambda_0^2$, the background temperature $\bar{T}(z, t_0)$ is then evolved to $t=t_0+\Delta t$ according to \eq{EQ:T0_IVP} and another eigenvalue solve is performed. 
 This background temperature is typically close to, but not exactly, marginally stable.
@@
 We are searching for $\vec{\tilde{A}^2}$ that satisfies of $\vec{\sigma}(\vec{\tilde{A}^2})=0$.
-We approximate the amplitudes with $\vec{A^2_0}$ by generalizing \eq{EQ:amp_approx}:
+We approximate the amplitudes with $\vec{\Lambda^2_0}$ by generalizing \eq{EQ:amp_approx}:
 \begin{equation}
-    \vec{\tilde{A}^2} \approx \vec{A^2_0} = -\Sigma_{\rm{adv}}^{-1} \vec{\sigma_{\rm{diff}}}.
+    \vec{\tilde{A}^2} \approx \vec{\Lambda^2_0} = -\Sigma_{\rm{adv}}^{-1} \vec{\sigma_{\rm{diff}}}.
     \label{EQ:AN_approx}
@@
 Otherwise the mode becomes marginally-stable.
-
+In a similar manner, a once-marginally-stable mode need not remain marginally-stable.
+If it's amplitude converges to some $A^2 < 0$ as before, then that mode is discarded and the iteration is repeated.
 \section{Properties of Thermally Equilibrated States}\label{sec:properties}
@@
     Marginal modes often appear in adjacent pairs, which we denote with a common color. 
-    Within each of these pairs, the largest and smallest $k_x$ are denoted with an + and x respectively.
+    Within each of these pairs, the largest and smallest $k_x$ are denoted with an x and a + respectively.
     For example, the spectrum corresponding to $\Ra = 10^5$ has adjacent marginal wavenumbers $k_x = \pi, \, 1.5\pi$. 
     The $\Ra = 10^9$ spectrum, shown in lower right corner of Figure~\ref{fig:flux}, has three groups of maxima, with a single marginal mode in the first group ($k_x = 1.5\pi$), two adjacent marginal modes in the second group ($k_x = 6\pi, \, 6.5\pi$), and two adjacent marginal modes in the third group ($k_x = 23.5\pi, \, 24\pi$).
-    The largest wavenumbers of the green branch obey a power-law relationship $\max\{k_x\} \propto \Ra^{0.300}$ with $R^2 = 0.998$.}
+    The largest wavenumbers of the green and blue branches depend on  $\Ra$ according to power laws.
+    For the green branch, $\max\{k_x\} \propto \Ra^{0.300}$ with $R^2 = 0.998$ while for the blue branch, $k_x \propto \Ra^{0.155}$ with $R^2 = 0.988$.}
     \label{fig:kx_marginals}
@@
     $(\max \{ k_x \})^{-1}$ gives a minimum $x$ length scale for the perturbations, and consequently, the advection. 
-    For large $\Ra$, the boundary layers admit small scale features, requiring more vertical basis functions (higher resolution).
+    For large $\Ra$, the boundary layers admit small scale features, requiring more vertical basis functions (higher resolution, see Appendix \ref{sec:tables} for specifications).
     The boundary layer width gives an estimate of the minimum vertical length-scale in the problem.
@@
 \begin{align}\label{eqn:delta}
-\left.\frac{\partial \bar{T}}{\partial z}\right|_{z=-\frac{1}{2}+\delta} = 0.
+    \left.\frac{\partial \bar{T}}{\partial z}\right|_{z=-\frac{1}{2}+\delta} = 0, \qquad 0 < \delta < 1/2.
 \end{align}
@@
 Least-squares regression gives $\delta^{-1} = 1.71 \max \{ k_x \} - 2.13$ with $R^2 = 0.996$.
-We can assume from this length scale agreement that the mean-squared $x$ and $z$ components of the temperature and velocity gradients are proportional
-\begin{align}
-    \Big\langle \frac{\partial T}{\partial x} \cdot \frac{\partial T}{\partial x} \Big\rangle_{\mathcal{D}} &\propto \Big\langle \frac{\partial T}{\partial z} \cdot \frac{\partial T}{\partial z} \Big\rangle_{\mathcal{D}} \nonumber   \\
-    \Big\langle \frac{\partial \vec{u}}{\partial x} \cdot \frac{\partial \vec{u}}{\partial x} \Big\rangle_{\mathcal{D}} &\propto \Big\langle \frac{\partial \vec{u}}{\partial z} \cdot \frac{\partial \vec{u}}{\partial z} \Big\rangle_{\mathcal{D}}.
-\end{align}
-This is consistent with the mean squared gradient assumptions of \cite{Malkus_1954}.
+% We can assume from this length scale agreement that the mean-squared $x$ and $z$ components of the temperature and velocity gradients are proportional
+% \begin{align}
+%     \Big\langle \frac{\partial T}{\partial x} \cdot \frac{\partial T}{\partial x} \Big\rangle_{\mathcal{D}} &\propto \Big\langle \frac{\partial T}{\partial z} \cdot \frac{\partial T}{\partial z} \Big\rangle_{\mathcal{D}} \nonumber   \\
+%     \Big\langle \frac{\partial \vec{u}}{\partial x} \cdot \frac{\partial \vec{u}}{\partial x} \Big\rangle_{\mathcal{D}} &\propto \Big\langle \frac{\partial \vec{u}}{\partial z} \cdot \frac{\partial \vec{u}}{\partial z} \Big\rangle_{\mathcal{D}}.
+% \end{align}
+% This is consistent with the mean squared gradient assumptions of \cite{Malkus_1954}.
 %The quasilinear model cannot describe arbitrarily small scale structures. This is a consequence of us collapsing the problem into a single dimension via mode-discretization.
@@
 In Figure~\ref{fig:nu_vs_ra} we report $\Nu$ for MSTE, ``steady rolls" ECS \cite{Wen}, and DNS \cite{Scheel_2016, Johnston}.
-We find that MSTE satisfy $\Nu \sim\Ra^{1/3}$, consistent with our finding that the boundary layer width scales like $\delta \sim \Ra^{1/3}$.
+We find that MSTE satisfy $\Nu \sim\Ra^{1/3}$, consistent with our finding that the boundary layer height scales like $\delta \sim \Ra^{1/3}$.
 The Nusselt numbers of the ECS are somewhat lower and the DNS Nusselt numbers are yet lower still.
@@
 \begin{align}
-    T(x, z)\big|_{t=0} &= 0.5 - z + N \nonumber \\
+    T(x, z)\big|_{t=0} &= 0.5 - z + \mathcal{N} \nonumber \\
     \vec{u}(x, z)\big|_{t=0} &= \vec{0} \nonumber \\
@@
 \end{align}
-where $N$ is low-amplitude random noise.
+where $\mathcal{N}$ is low-amplitude random noise.
 Here we instead initialize using the MSTE,
 \begin{align}
-    T(x, z)\big|_{t=0} &= \bar{T}(z) + \sum_{n=1}^N  A_n \Re \Big[ \theta_n(z) e^{ik_{x_n}x} \Big] + N \nonumber \\
+    T(x, z)\big|_{t=0} &= \bar{T}(z) + \sum_{n=1}^N  A_n \Re \Big[ \theta_n(z) e^{ik_{x_n}x} \Big] + \mathcal{N} \nonumber \\
     \vec{u}(x, z)\big|_{t=0} &= \sum_{n=1}^N A_n \Re \Big[\Big( U_n (z) \hat{x} + W_n(z) \hat{z} \Big) e^{ik_{x_n}x} \Big] \nonumber\\
@@
     The MSTE simulation does not undergo a convective-transient period because the characteristic large-scale convective cell structure exists on initialization.
-    The MSTE no flow simulation exhibits quasi-periodic oscillations in $\Nu$ which appear to persist for long times.}
+    The MSTE no flow simulation exhibits quasi-periodic oscillations in $\Nu$ which appear to persist for long times.
+    The oscillations are great enough in amplitude that $\Nu$ is quasi-periodically negative, indicating brief periods of average heat transfer reversal.}
     \label{fig:nu_sim}
@@
 This is due to a burst of turbulence which occurs when the convective motions first become nonlinear.
-The MSTE no flow simulation undergoes a similar transient period, albeit less pronounced as denoted by the smaller peak in the green curve.
+The MSTE no flow simulation undergoes a similar transient period, albeit less pronounced as illustrated by the smaller peak in the green curve.
 A simulation initialized with the MSTE, however, does not exhibit this transient burst of turbulence, as the large-scale anatomy of convective cells exists on initialization. 
@@
 
-MSTE are laminar, lacking the small-scale structures associated with moderate to high $\Ra$ experiments. 
+MSTE are laminar, lacking the small-scale structures associated with moderate- to high-$\Ra$ experiments. 
 This is an apparent consequence of the quasilinear assumptions. 
@@
 This perspective agrees with conventional models of transitions to turbulent flows, such as Boussinesq's turbulent-viscosity hypothesis \cite{boussinesq_1877}. 
-The emergence of small-scale velocity structures tends to increase total shear \cite{Lecoanet_KH, drazin_reid_2004, pope_2000}, thereby impeding buoyancy-driven flows and decreasing advection in the bulk of the domain.
+The emergence of small-scale velocity structures is indicative of a Kolmogrov energy cascade, where kinetic energy is transferred to progressively smaller scales via inviscid processes until, at microscopic scales, energy is lost due to viscous shearing.
+Buoyancy driven flows are therefore impeded and the advection in the bulk of the domain decreases in magnitude \cite{drazin_reid_2004, pope_2000}. 
 We could also attribute the diffuse DNS temperature profile in Figure~\ref{fig:T0_profiles} with unsteady boundary-layer penetration and mixing that MSTE do not exhibit.
@@
     The eigenfunctions belonging to MSTE have significantly more kinetic energy than the statistically-steady state. 
-    Kinetic equilibrium is achieved on the viscous time-scale.}
+    Kinetic equilibrium is achieved on a long viscous time-scale.}
     \label{fig:ke_sim}
@@
 
-We also find that the average kinetic energies of simulations initialized with MSTE are significantly larger than those found in simulations initialized with no-flow MSTE and with the conductive state plus noise, as shown Figure~\ref{fig:ke_sim}.
-This is because the MSTE contain strong large-scale flows, which decay on a viscous time-scale $t_{\nu}$. 
+We also find that the average kinetic energy of the simulation initialized with MSTE is significantly larger than those found in either of the other cases, as shown Figure~\ref{fig:ke_sim}. 
+This is because the MSTE contain strong large-scale flows, which decay on a long viscous time-scale $t_{\nu}$, whereas fluid in the other cases is initialized at rest. 
 Two viscous time-scales can be derived for this problem: one for the boundary layer 
 \begin{align*}
-    t_{\nu,\delta} &= \frac{L_z}{\mathcal{P}} = 2.8561
+    t_{\nu,\delta} &= \frac{\delta^2}{\mathcal{P}} = 2.8561
+    \intertext{and another for entire domain}
+    t_{\nu,L} &= \frac{L_z}{\mathcal{P}} = 10^4.
 \end{align*}
-\begin{align*}
-    \intertext{and another for the entire domain}
-    t_{\nu,L_z} &= \frac{\delta^2_0}{\mathcal{P}} = 10^4.
-\end{align*}
-Empirically, we find $t_{\nu} \approx 200$ suggesting the true kinetic energy decary time-scale is based on a length scale which is longer than the boundary layer height $\delta$ but shorter than the domain height $L_z$.
+Empirically, we find $t_{\nu} \approx 200$ suggesting the true kinetic energy decay time-scale is based on a length scale which is longer than the boundary layer height $\delta$ but shorter than the domain height $L_z$.
 Consequently, MSTE initial conditions do not reduce the simulation time required to achieve a statistically-steady state---rather they increase it considerably!
@@
 Should the fast and slow time scales not be entirely separate, we might anticipate the long-term persistance of moderately unstable modes. 
-To find MSTE, we initialize the time-evolution algorithm with the analytic temperature profile derived by \cite{Shishkina}.
-This involves modifying the boundary layer thickness $\delta_0$ to achieve marginal stability.
+% To find MSTE, we initialize the time-evolution algorithm with the analytic temperature profile derived by \cite{Shishkina}.
+% This involves modifying the boundary layer thickness $\delta_0$ to achieve marginal stability.
 
-Instead of imposing marginal stability, we can use quasilinear model to thermally-equilibrate and expand 1D approximations into 2D.
-As previously noted, there is no shortage of theories pertaining to the scaling behavior $\Nu \sim \Ra^{\beta}$ \cite{Malkus_1954, Howard_1966, Kraichnan, Spiegel, Castaing, Grossman, Ahlers}.
-For large $\Ra$, we can approximate $\delta_0 \approx \Nu^{-1}$ and construct a 1D temperature profile according to \eq{EQ:T0} or some other approximation.
-In this way, other 2D quasilinear thermal equilibria can be obtained and analyzed.
+% Instead of imposing marginal stability, we can use quasilinear model to thermally-equilibrate and expand 1D approximations into 2D.
+% As previously noted, there is no shortage of theories pertaining to the scaling behavior $\Nu \sim \Ra^{\beta}$ \cite{Malkus_1954, Howard_1966, Kraichnan, Spiegel, Castaing, Grossman, Ahlers}.
+% For large $\Ra$, we can approximate $\delta_0 \approx \Nu^{-1}$ and construct a 1D temperature profile according to \eq{EQ:T0} or some other approximation.
+% In this way, other 2D quasilinear thermal equilibria can be obtained and analyzed.
 
 \section*{Acknowledgments}
-The authors thank Geoff Vasil, Greg Chini, and Emma Kaufman for their valuable feedback and suggestions. 
+The authors thank Geoff Vasil, Greg Chini, Kyle Augustson, and Emma Kaufman for their valuable feedback and suggestions. 
 We also thank the \texttt{Dedalus} and \texttt{Eigentools} development teams. 
@@
 \end{align}
-where $\delta_0$ is the boundary layer height. 
-This function is meant to describe the temperature near $z = -1/2$.
-It does not pass through the origin and it is undefined for $z > 0$. 
+where $\delta_0$ is a new measure of the boundary layer height ($\delta_0 \neq \delta$ in general). 
+This function is meant to describe the temperature near $z = -1/2$ so it does not pass through the origin.
 An appropriate initial mean temperature profile $\bar{T}_0$ must be odd-symmetric, i.e.~$\bar{T}_0(-z) = -\bar{T}_0(z)$.
@@
 The timestep must be also reduced to avoid a numerical instability.
-We find that for large $\Delta t$, after several hundred iterations, highly concave features develop in the advective flux term $\langle w'T' \rangle$ near $z=0$. 
+We find that for large $\Delta t$, after several hundred iterations, highly concave features develop in the advective flux term $\langle w'T' \rangle_x$ near $z=0$. 
 Such features are undesired, as they are uncommon in similar calculations \cite{Malkus_1954} and we do not believe they accurately represent a physical process.
@@
 \onecolumngrid
-\section{MSTE Metrics}\label{sec:tables}
+\section{MSTE Parameters and Results}\label{sec:tables}
 
@@
     %  \end{tabular}
-    \caption{Control parameters are given for the timestepping algorithm.
-$N_z$ denotes the number of Chebyshev basis functions employed.
-The remaining quantities are derived directly from MSTE solutions.}
+    \caption{Control parameters and results are given for the MSTE timestepping algorithm. $N_z$ denotes the number of Chebyshev basis functions employed. 
+    This, along with $\Ra$ are specified on initialization.
+    The remaining quantities are computed directly from the MSTE.}
     {\label{tab:metrics}}

### 2021-05-14 publication_materials/ms_rbc.tex
typos

@@
     t_{\nu,\delta} &= \frac{\delta^2}{\mathcal{P}} = 2.8561
-    \intertext{and another for entire domain}
+    \intertext{and another for the entire domain}
     t_{\nu,L} &= \frac{L_z}{\mathcal{P}} = 10^4.
@@
 Once these oscillations reach some amplitude, they cannot be eliminated via timestep reduction and the roots of $\sigma_{\rm{max}}(A^2)$ vanish.
-To avoid this, we measure the curvature of the advective flux $|\frac{\partial^2}{\partial z^2} \langle w'T' \rangle|_{z=0}|$ of the dominant $k_x = 1.5\pi$ mode.
+To avoid this, we measure the curvature of the advective flux $|\frac{\partial^2}{\partial z^2} \langle w'T' \rangle_x|_{z=0}|$ of the dominant $k_x = 1.5\pi$ mode.
 We find that reducing the timestep $\Delta t$ by the same factor of 1.1 whenever this curvature measure exceeds $10^{-6}$ curtails the problem.

### 2021-05-14 publication_materials/ms_rbc.tex
minor
merge agreement

@@
 Otherwise the mode becomes marginally-stable.
-In a similar manner, a once-marginally-stable mode need not remain marginally-stable.
+In a similar manner, a marginally-stable mode need not remain marginally-stable.
 If it's amplitude converges to some $A^2 < 0$ as before, then that mode is discarded and the iteration is repeated.
@@
 This perspective agrees with conventional models of transitions to turbulent flows, such as Boussinesq's turbulent-viscosity hypothesis \cite{boussinesq_1877}. 
-The emergence of small-scale velocity structures is indicative of a Kolmogrov energy cascade, where kinetic energy is transferred to progressively smaller scales via inviscid processes until, at microscopic scales, energy is lost due to viscous shearing.
+The emergence of small-scale velocity structures is indicative of nonlinear energy transfer to small scales where energy is lost due to viscosity. 
 Buoyancy driven flows are therefore impeded and the advection in the bulk of the domain decreases in magnitude \cite{drazin_reid_2004, pope_2000}. 
@@
 Unstable modes tend to stabilize the system rapidly, creating a negative feedback loop whose average state is linearly unstable. 
-We might curtail the disagreement between MSTE and DNS by adjusting our marginal-stability criterion. 
-Should the fast and slow time scales not be entirely separate, we might anticipate the long-term persistance of moderately unstable modes. 
+Future work could adjust the marginal-stability criterion to allow for moderately unstable modes.
+Should the fast and slow time scales not be entirely separate, these modes might persist for long times. 
+This might lead to greater agreement with DNS.
+
 % To find MSTE, we initialize the time-evolution algorithm with the analytic temperature profile derived by \cite{Shishkina}.
@@
 
-\section{Numerical Instabilities and Timestep Management} \label{sec:timestep}
+\section{Timestep Management} \label{sec:timestep}
 To find MSTE, we advance $\bar{T}$ by timesteps of size $\Delta t$.

### 2021-05-15 publication_materials/ms_rbc.tex
Evan's feedback

@@
-\documentclass[reprint,amsmath,amssymb,aps]{revtex4-1}
+\documentclass[reprint,amsmath,amssymb,aps,nofootinbib]{revtex4-1}
 
@@
 \renewcommand\L {\mathcal{L}}
+\renewcommand{\citet}[1]{ref.~\cite{#1}}
+\renewcommand{\Citet}[1]{Ref.~\cite{#1}}
 
@@
 The scaling behavior of the Nusselt number $\Nu \sim \Ra^{\beta}$ in the asymptotic ultimate regime is of particular interest.
-There exists a substantial body of work pertaining to this specific topic with no general consensus \cite{Malkus_1954, Howard_1966, Kraichnan, Spiegel, Castaing, Grossman, Ahlers}.
+There is a substantial body of work pertaining to this specific topic with no general agreement between numerical simulations and asymptotic theories \cite{Malkus_1954, Howard_1966, Kraichnan, Spiegel, Castaing, Grossman, Ahlers}.
 
@@
 In the presence of other physical effects (e.g., rotation, magnetic fields), one can sometimes derive an asymptotically consistent set of reduced equations \cite{Julien2007, Julien2012}.
-Reduced models are potentially useful in this context because they may allow us to study the problem with less expensive computations.
+Reduced models are useful because they allow us to study the problem with less expensive computations.
 Another approach relates to unstable exact coherent states (ECS) which are steady solutions to the full nonlinear problem \cite{Waleffe, Sondak, Wen, chini_cells}. 
-Simulations and analysis performed by \cite{Yalniz, Cvitanovic} suggest that chaotic solution trajectories might ``visit'' these ECS.
+Simulations and analyses performed by \cite{Yalniz, Cvitanovic} suggest that chaotic solution trajectories might ``visit'' these ECS.
 Should that be the case, it is crucial that we discover and classify such equilibria.
@@
 Although the quasilinear approximation greatly simplifies the problem, an additional condition must be imposed to determine the amplitude of the perturbations.
-In \cite{Beaume_2015}, researchers compute ECS in parallel shear flows by deriving and solving a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments. 
+In \citet{Beaume_2015}, researchers compute ECS in parallel shear flows by deriving and solving a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments. 
 They assume the background velocity evolves on a slow time-scale, and, to determine the perturbation amplitudes, they require marginal stability at each timestep.
-A similar strategy is employed by \cite{michel_chini_2019} to study acoustic streaming.
+A similar strategy is employed by \citet{michel_chini_2019} to study acoustic streaming.
 In that work, an analytic expression for the first-order perturbation's amplitude is found by deriving a solvability condition.
@@
 We begin with the Boussinesq approximation for Rayleigh-Bénard Convection, nondimensionalized on the freefall time-scale. 
-The domain $\mathcal{D}$ is 2-dimensional, rectangular, and horizontally periodic with spatial dimensions $0 \leq x < 4$ and $-1/2 < z < 1/2$. 
+The domain $\mathcal{D}$ is 2-dimensional, rectangular, and horizontally periodic with cartesian spatial coordinates $0 \leq x < 4$ and $-1/2 < z < 1/2$. 
 The fluid of interest is constrained between two flat boundaries at $z = -1/2$ and $z = 1/2$ with fixed temperatures $1/2$ and $-1/2$ respectively. 
@@
 
-To derive the quasilinear form, we posit that an arbitrary field $f$ can be represented as the sum of a mean profile (denoted by $\bar{f}$) and a perturbation function (denoted by $f'$).
+To derive the quasilinear form, we posit that an arbitrary field $f$ can be represented as the sum of a mean profile (denoted by $\overline{f}$) and a perturbation function (denoted by $f'$).
 \begin{align}
@@
     &= u'(x, z, t)\hat{x} + w'(x, z, t)\hat{z} \\
-    T(x, z, t) &= \bar{T}(z, t) + T'(x, z, t) \label{EQ:reynolds_dc_T}\\
-    p(x, z, t) &= \bar{p}(z, t) +  p'(x, z, t) \label{EQ:reynolds_dc_p}.
+    T(x, z, t) &= \overline{T}(z, t) + T'(x, z, t) \label{EQ:reynolds_dc_T}\\
+    p(x, z, t) &= \overline{p}(z, t) +  p'(x, z, t) \label{EQ:reynolds_dc_p}.
 \end{align}
@@
 %thereby alleviating any ambiguity in $A(t)$. 
-Substituting \eq{EQ:reynolds_dc_T} into \eq{EQ:motion3} and taking the horizontal-average reduces the system to a simple initial value problem (IVP) for $\bar{T}$
+Substituting \eq{EQ:reynolds_dc_T} into \eq{EQ:motion3} and taking the horizontal-average reduces the system to a simple initial value problem (IVP) for $\overline{T}$
 \begin{equation}
-  \frac{\partial \bar{T}}{\partial t} + \frac{\partial}{\partial z} \langle w'T' \rangle_x = \mathcal{P} \frac{\partial^2 \bar{T}}{\partial z^2}, \label{EQ:T0_IVP}
+  \frac{\partial \overline{T}}{\partial t} + \frac{\partial}{\partial z} \langle w'T' \rangle_x = \mathcal{P} \frac{\partial^2 \overline{T}}{\partial z^2}, \label{EQ:T0_IVP}
 \end{equation}
-with associated boundary conditions $\bar{T}(-1/2, t) = 1/2$ and $\bar{T}(1/2, t) = -1/2$.
-It should be noted that we could obtain a similar IVP for $u$ by breaking symmetry and considering some nontrivial mean horizontal flow $\bar{u}(z, t)$.
-However we must have $\bar{w}(z, t) = 0$ due to incompressibility.
+with associated boundary conditions $\overline{T}(-1/2, t) = 1/2$ and $\overline{T}(1/2, t) = -1/2$.
+It should be noted that we could obtain a similar IVP for $u$ by breaking symmetry and considering some nontrivial mean horizontal flow $\overline{u}(z, t)$.
+However we must have $\overline{w}(z, t) = 0$ due to incompressibility.
 
-Substituting \eq{EQ:reynolds_dc_p} into \eq{EQ:motion2} and taking the horizontal average reveals that the mean pressure field $\bar{p}(z)$ must satisfy
+Substituting \eq{EQ:reynolds_dc_p} into \eq{EQ:motion2} and taking the horizontal average reveals that the mean pressure field $\overline{p}(z)$ must satisfy
 \begin{equation}
-    0 = -\frac{\partial \bar{p}}{\partial z} + \bar{T}\label{EQ:p_bar}
+    0 = -\frac{\partial \overline{p}}{\partial z} + \overline{T}\label{EQ:p_bar}
 \end{equation}
@@
     \frac{\partial\vec{u'}}{\partial t} &= - \nabla p' + T'\hat{z} + \mathcal{R} \nabla^2 \vec{u'} \label{EQ:linear2}\\
-    \frac{\partial T'}{\partial t} + \frac{\partial \bar{T}}{\partial z} w' &= \mathcal{P} \nabla^2 T' \label{EQ:linear3}
+    \frac{\partial T'}{\partial t} + \frac{\partial \overline{T}}{\partial z} w' &= \mathcal{P} \nabla^2 T' \label{EQ:linear3}
 \end{align}
@@
 \begin{equation}
-    T'|_{z = \pm \frac{1}{2}} = 0, \quad u'|_{z = \pm \frac{1}{2}} = 0, \quad p'|_{z = \pm \frac{1}{2}} = 0.
+    T'|_{z = \pm \frac{1}{2}} = 0, \quad \vec{u'}|_{z = \pm \frac{1}{2}} = 0, \quad p'|_{z = \pm \frac{1}{2}} = 0.
 \end{equation}
@@
 A complete linear stability analysis requires solution over the full spectrum of wavenumbers. 
-The prototypical case is used to demonstrate that the critical Rayleigh number $\Ra_c = 1708$ when $\frac{\partial \bar{T}}{\partial z} = -1$.
+The prototypical case is used to demonstrate that the critical Rayleigh number $\Ra_c = 1708$ when $\frac{\partial \overline{T}}{\partial z} = -1$.
 
 To calculate the advective heat flux in equation~\ref{EQ:T0_IVP}, we can sum $\langle w'T' \rangle_x$ from each horizontal wavenumber individually.
-In this way, the heat flux from the perturbations influence the evolution of $\bar{T}$.
-But the evolution of $\bar{T}$ also influences the perturbations, as equation~\ref{EQ:linear3} depends on $\partial_z \bar{T}$.
+In this way, the heat flux from the perturbations influence the evolution of $\overline{T}$.
+But the evolution of $\overline{T}$ also influences the perturbations, as equation~\ref{EQ:linear3} depends on $\partial_z \overline{T}$.
 Thus, the mean temperature and perturbation fields are coupled.
@@
 However, the advective heat flux is proportional to $A^2$, so we need to specify the amplitude in order to solve equation~\ref{EQ:T0_IVP}.
-To evolve $\bar{T}$, we assume the perturbations evolve on a much faster time-scale than the mean temperature, as in \cite{michel_chini_2019}.
+To evolve $\overline{T}$, we assume the perturbations evolve on a much faster time-scale than the mean temperature, as in \cite{michel_chini_2019}.
 Stable modes $(\sigma < 0)$ decay away rapidly. 
-Unstable modes $(\sigma > 0)$ will not persist on the slow time-scale because the advective term $\langle w'T' \rangle_x$ tends to stabilize $\bar{T}$, thereby creating a negative feedback loop.
+Unstable modes $(\sigma > 0)$ will not persist on the slow time-scale because the advective term $\langle w'T' \rangle_x$ tends to stabilize $\overline{T}$, thereby creating a negative feedback loop.
 Only marginally stable modes can be maintained on the slow time-scale.
@@
 
-For various $\Ra$ and fixed $\Pr = 1$, we seek marginally-stable thermal equilibria (MSTE) satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to \eq{EQ:T0_IVP}. 
-We employ the \texttt{Dedalus} pseudo-spectral python framework \cite{Dedalus_2020} to solve the eigenvalue problem outlined in Section \ref{sec:model} as well as the time evolution equations \eq{EQ:T0_IVP}.
+For various $\Ra$ and fixed $\Pr = 1$, we seek marginally-stable thermal equilibria (MSTE) satisfying $\frac{\partial \overline{T}}{\partial t} = 0$ according to \eq{EQ:T0_IVP}. 
+We employ the \texttt{Dedalus} pseudo-spectral python framework\footnotemark[1] \cite{Dedalus_2020} to solve the eigenvalue problem outlined in Section \ref{sec:model} as well as the time evolution equations \eq{EQ:T0_IVP}.
 We represent each field with Chebyshev polynomials and use the 3/2 dealiasing rule to calculate the advective heat flux.
 The necessary number of basis functions increases with $\Ra$ as the eigenfunctions include increasingly small-scale features (see Appendix \ref{sec:tables}). 
-We use the \texttt{Eigentools} package \cite{Eigentools} to manipulate the eigenfunctions and calculate the advective heat flux $\langle w' T' \rangle_x$.
+We use the \texttt{Eigentools} package\footnotemark[2] \cite{Eigentools} to manipulate the eigenfunctions and calculate the advective heat flux $\langle w' T' \rangle_x$.
 
-To initialize our calculations, we construct a marginally-stable initial temperature profile $\bar{T}(z, t=0)$ whose equation is given in appendix~\ref{sec:initial_profile}. 
-We use \eq{EQ:T0_IVP} to evolve $\bar{T}(z, t_0)$ into a new marginally-stable profile $\bar{T}(z, t_0 + \Delta t)$.
+\footnotetext[1]{We employ \texttt{Dedalus} version v2.2006
+
+\url{https://github.com/DedalusProject/dedalus/releases}}
+
+\footnotetext[2]{We employ \texttt{Eigentools} commit
+
+f457afc3193c32c16fdff94cdad962d07edea56b
+
+\url{https://github.com/jsoishi/eigentools}}
+
+To initialize our calculations, we construct a marginally-stable initial temperature profile $\overline{T}(z, t=0)$ whose equation is given in appendix~\ref{sec:initial_profile}. 
+We use \eq{EQ:T0_IVP} to evolve $\overline{T}(z, t_0)$ into a new marginally-stable profile $\overline{T}(z, t_0 + \Delta t)$.
 We use a second-order, two-stage IMEX Runge-Kutta method.
 The eigenfunctions and amplitudes are assumed to be constant over the timestep.
-We symmetrize $\bar{T}$ by setting the coefficients of its even Chebyshev basis functions to zero at the start of each timestep.
-This ensures $\bar{T}(z) = -\bar{T}(-z)$.
+We symmetrize $\overline{T}$ by setting the coefficients of its even Chebyshev basis functions to zero at the start of each timestep.
+This ensures $\overline{T}(z) = -\overline{T}(-z)$.
 On every timestep, we calculate the marginally stable eigenfunctions and their amplitude $A$.
@@
     \includegraphics[width=3.4in]{EV_spectrum_ol.png}
-    \caption{Eigenvalue spectra for $\Ra = 10^5$. The spectrum of an ``initial" marginally-stable mean temperature profile $\bar{T}(z, t_0)$ has a maximum eigenvalue of 0. 
+    \caption{Eigenvalue spectra for $\Ra = 10^5$. The spectrum of an ``initial" marginally-stable mean temperature profile $\overline{T}(z, t_0)$ has a maximum eigenvalue of 0. 
     Given a small fixed timestep $\Delta t$, diffusion destabilizes the system, increasing $\sigma$. 
     Advection tends to stabilize the system, decreasing $\sigma$. 
-    We find the eigenfunction amplitude $A^2$ such that the combination of diffusion and advection yields a new, ``evolved,'' marginally-stable mean temperature profile $\bar{T}(z, t_0 + \Delta t)$.
+    We find the eigenfunction amplitude $A^2$ such that the combination of diffusion and advection yields a new, ``evolved,'' marginally-stable mean temperature profile $\overline{T}(z, t_0 + \Delta t)$.
 In this case $A^2 \approx 1$ due to approximately equal magnitudes of the diffused and advected eigenvalues.}
@@
 
-Consider a marginally-stable temperature profile $\bar{T}(z, t_0)$.
+Consider a marginally-stable temperature profile $\overline{T}(z, t_0)$.
 By definition, its maximum growth rate is 0.
-Diffusing $\bar{T}(z, t_0)$ tends to increase its growth rates while ignoring the diffusive term and evolving according to advection tends to decrease its growth rates.
+Diffusing $\overline{T}(z, t_0)$ tends to increase its growth rates while ignoring the diffusive term and evolving according to advection tends to decrease its growth rates.
 $A$ must be selected such that these two influences are equal and opposite.
@@
 \begin{align}\label{eqn:diffusion_only}
-    &\frac{\partial \bar{T}_{\rm{diff}}}{\partial t} = \mathcal{P} \frac{\partial^2 \bar{T}_{\rm{diff}}}{\partial z^2} \\
-    &\frac{\partial \bar{T}_{\rm{adv}}}{\partial t} + \frac{\partial}{\partial z} \langle w'T' \rangle_x = 0 
+    &\frac{\partial \overline{T}_{\rm{diff}}}{\partial t} = \mathcal{P} \frac{\partial^2 \overline{T}_{\rm{diff}}}{\partial z^2} \\
+    &\frac{\partial \overline{T}_{\rm{adv}}}{\partial t} + \frac{\partial}{\partial z} \langle w'T' \rangle_x = 0 
 \end{align}
-where $\bar{T}_{\rm{diff}}$ and $\bar{T}_{\rm{adv}}$ denote to the diffused and advected temperature profiles.
-We initialize $\bar{T}_{\rm{diff}}$ and $\bar{T}_{\rm{adv}}$ with $\bar{T}(z, t_0)$, and evolve the equations to $t=t_0+\Delta t$.
+where $\overline{T}_{\rm{diff}}$ and $\overline{T}_{\rm{adv}}$ denote to the diffused and advected temperature profiles.
+We initialize $\overline{T}_{\rm{diff}}$ and $\overline{T}_{\rm{adv}}$ with $\overline{T}(z, t_0)$, and evolve the equations to $t=t_0+\Delta t$.
 Suppose $k_0$ is the wavenumber of the marginally-stable mode.
@@
 
-Using the approximate amplitude $\Lambda_0^2$, the background temperature $\bar{T}(z, t_0)$ is then evolved to $t=t_0+\Delta t$ according to \eq{EQ:T0_IVP} and another eigenvalue solve is performed. 
+Using the approximate amplitude $\Lambda_0^2$, the background temperature $\overline{T}(z, t_0)$ is then evolved to $t=t_0+\Delta t$ according to \eq{EQ:T0_IVP} and another eigenvalue solve is performed.
 This background temperature is typically close to, but not exactly, marginally stable.
@@
 
-Our estimate $\vec{A^2_0}$ does not give a background temperature for which all $N$ modes are exactly marginally stable.
+Our estimate $\vec{\Lambda^2_0}$ does not give a background temperature for which all $N$ modes are exactly marginally stable.
 We refine our vector of amplitudes via Newton's method.
@@
 We find $\vec{\sigma}(\vec{A^2})$ does indeed have a unique root provided the time step is not too large and there are no numerical instabilities, as outlined in appendix \ref{sec:timestep}.
-Presumably this is due to the coupling of $\langle w'T' \rangle_x$ with $\bar{T}$.
-Over the course of a large time step, $\bar{T}$ evolves according to \eq{EQ:T0_IVP} and eventually the original eigenfunctions cease to provide a stabilizing influence.
+Presumably this is due to the coupling of $\langle w'T' \rangle_x$ with $\overline{T}$.
+Over the course of a large time step, $\overline{T}$ evolves according to \eq{EQ:T0_IVP} and eventually the original eigenfunctions cease to provide a stabilizing influence.
 This limits the timestep size we can take.
@@
 In a similar manner, a marginally-stable mode need not remain marginally-stable.
-If it's amplitude converges to some $A^2 < 0$ as before, then that mode is discarded and the iteration is repeated.
+If its amplitude converges to some $A^2 < 0$ as before, then that mode is discarded and the iteration is repeated.
 \section{Properties of Thermally Equilibrated States}\label{sec:properties}
-We evolve $\bar{T}$ as described above until $\max|\partial_{t}\bar{T}| < 10^{-5}$.
-In this marginally-stable thermal equilibrium, $\bar{T}$ does not evolve in time, and the perturbations also do not evolve in time, as they are marginally stable.
+We evolve $\overline{T}$ as described above until $\max|\partial_{t}\overline{T}| < 10^{-5}$.
+In this marginally-stable thermal equilibrium, $\overline{T}$ does not evolve in time, and the perturbations also do not evolve in time, as they are marginally stable.
 Thus, these configurations are exact solutions to the quasilinear equations (equations~\ref{EQ:T0_IVP}--\ref{EQ:linear3}).
@@
     \includegraphics[width=3.4in]{T_profs_na.png}
-    \caption{Mean temperature profiles $\bar{T}$ for $\Ra = 10^8$. 
+    \caption{Mean temperature profiles $\overline{T}$ for $\Ra = 10^8$. 
     The initial profile is given by \eq{EQ:T0}. 
@@
 The temperature boundary layers in the DNS are wider than in the MSTE, which is in turn wider than the boundary layer of the initial temperature profile.
-Performing an eigenvalue solve by setting $\bar{T}$ equal to the DNS profile yields unstable eigenvalues. 
+Performing an eigenvalue solve by setting $\overline{T}$ equal to the DNS profile yields unstable eigenvalues. 
 This suggests that MSTE might maximize boundary layer thickness, subject to the marginal stability constraint.
@@
 The largest marginal wavenumber $\max \{ k_x \}$ (represented by the light green branch in Figure~\ref{fig:kx_marginals}) serves as an inverse minimum length-scale in the $x$ direction.
-The finest vertical structures in $\bar{T}(z)$ appear near the boundaries, requiring more basis functions (resolution) at large $\Ra$.
+The finest vertical structures in $\overline{T}(z)$ appear near the boundaries, requiring more basis functions (resolution) at large $\Ra$.
 Naturally, this provides a complementary minimum length-scale for $z$.
@@
 \begin{align}\label{eqn:delta}
-    \left.\frac{\partial \bar{T}}{\partial z}\right|_{z=-\frac{1}{2}+\delta} = 0, \qquad 0 < \delta < 1/2.
+    \left.\frac{\partial \overline{T}}{\partial z}\right|_{z=-\frac{1}{2}+\delta} = 0, \qquad 0 < \delta < 1/2.
 \end{align}
@@
     \caption{Boundary layer height $\delta$ of MSTE. 
-    We define the boundary layer height based off the location where $\frac{\partial \bar{T}}{\partial z} = 0$ (see equation~\ref{eqn:delta}). 
+    We define the boundary layer height based off the location where $\frac{\partial \overline{T}}{\partial z} = 0$ (see equation~\ref{eqn:delta}). 
     Plotting on a log-log scale, we find that $\delta$ and $\Ra$ obey a power-law relationship.
@@
 \begin{equation}
-    \Nu = \frac{\langle \langle w'T' \rangle_x - \mathcal{P}\frac{\partial \bar{T}}{\partial z} \rangle_z}{\langle- \mathcal{P}\frac{\partial \bar{T}}{\partial z} \rangle_z}.
+    \Nu = \frac{\langle \langle w'T' \rangle_x - \mathcal{P}\frac{\partial \overline{T}}{\partial z} \rangle_z}{\langle- \mathcal{P}\frac{\partial \overline{T}}{\partial z} \rangle_z}.
 \end{equation}
@@
 \begin{align}
-    T(x, z)\big|_{t=0} &= \bar{T}(z) + \sum_{n=1}^N  A_n \Re \Big[ \theta_n(z) e^{ik_{x_n}x} \Big] + \mathcal{N} \nonumber \\
+    T(x, z)\big|_{t=0} &= \overline{T}(z) + \sum_{n=1}^N  A_n \Re \Big[ \theta_n(z) e^{ik_{x_n}x} \Big] + \mathcal{N} \nonumber \\
     \vec{u}(x, z)\big|_{t=0} &= \sum_{n=1}^N A_n \Re \Big[\Big( U_n (z) \hat{x} + W_n(z) \hat{z} \Big) e^{ik_{x_n}x} \Big] \nonumber\\
@@
 We also find that the average kinetic energy of the simulation initialized with MSTE is significantly larger than those found in either of the other cases, as shown Figure~\ref{fig:ke_sim}. 
-This is because the MSTE contain strong large-scale flows, which decay on a long viscous time-scale $t_{\nu}$, whereas fluid in the other cases is initialized at rest. 
+This is because the MSTE contain strong large-scale flows, which decay on a long viscous time-scale $t_{\nu}$. 
+Fluid in the other cases is initialized at rest. 
 Two viscous time-scales can be derived for this problem: one for the boundary layer 
 \begin{align*}
-    t_{\nu,\delta} &= \frac{\delta^2}{\mathcal{P}} = 2.8561
+    t_{\nu,\delta} &= \frac{\delta^2}{\mathcal{P}} = 2.86
     \intertext{and another for the entire domain}
-    t_{\nu,L} &= \frac{L_z}{\mathcal{P}} = 10^4.
+    t_{\nu,L} &= \frac{L^2_z}{\mathcal{P}} = 10^4.
 \end{align*}
-Empirically, we find $t_{\nu} \approx 200$ suggesting the true kinetic energy decay time-scale is based on a length scale which is longer than the boundary layer height $\delta$ but shorter than the domain height $L_z$.
+Empirically, we find $t_{\nu} \approx 200$ suggesting the true kinetic energy decay time-scale is based on a length scale $\ell \approx 0.14$ which is longer than the boundary layer height $\delta$ but shorter than the domain height $L_z$.
 Consequently, MSTE initial conditions do not reduce the simulation time required to achieve a statistically-steady state---rather they increase it considerably!
-This is alleviated by using the MSTE temperature profile, without including any velocity perturbations.
+This is alleviated by using no-flow MSTE initial conditions.
 The MSTE temperature state is a promising candidate initial condition for high-Rayleigh number convection simulations.
@@
 The marginal stability constraint then fixes the ratio between advection and diffusion (eigenfunction amplitude $A^2$). 
-We use standard root-finding algorithms to solve for the appropriate $A^2$ at each timestep, until, the  combination of diffusive and advective flux sum to a constant.
+We use standard root-finding algorithms to solve for the appropriate $A^2$ at each timestep until the  combination of diffusive and advective flux sum to a constant.
 The MSTE calculation is a one-dimensional problem, combining eigenvalue solves, and the time evolution of the one-dimensional mean temperature profile.
-Thus, they can be calculated on a single workstation.
+Thus, MSTE can be calculated on a single workstation.
 
@@
 \begin{align}
-    \bar{\mathcal{T}}_0(\xi) &= \frac{\sqrt{3}}{4\pi} \log \frac{(1 + a\xi)^3}{1 + (a\xi)^3} + \frac{3}{2\pi} \arctan \Big( \frac{4\pi}{9}\xi - \frac{1}{\sqrt{3}} \Big) + \frac{1}{4} \nonumber \\
+    \overline{\mathcal{T}}_0(\xi) &= \frac{\sqrt{3}}{4\pi} \log \frac{(1 + a\xi)^3}{1 + (a\xi)^3} + \frac{3}{2\pi} \arctan \Big( \frac{4\pi}{9}\xi - \frac{1}{\sqrt{3}} \Big) + \frac{1}{4} \nonumber \\
     \xi &= \frac{z + 1/2}{\delta_0} \geq 0, \qquad a = \frac{2\pi}{3\sqrt{3}}\label{EQ:T0}
@@
 This function is meant to describe the temperature near $z = -1/2$ so it does not pass through the origin.
-An appropriate initial mean temperature profile $\bar{T}_0$ must be odd-symmetric, i.e.~$\bar{T}_0(-z) = -\bar{T}_0(z)$.
-Due to continuity, this implies $\bar{T}_0(0) = 0$.
-Accordingly, we construct $\bar{T}_0(z)$ by translating $\bar{\mathcal{T}}_0(z)$ vertically to pass through the origin.
-We then take its odd-extension and include a unique scaling coefficient to satisfy the boundary conditions $\bar{T}_0(-1/2) = 1/2$ and $\bar{T}_0(1/2) = -1/2$.
+An appropriate initial mean temperature profile $\overline{T}_0$ must be odd-symmetric, i.e.~$\overline{T}_0(-z) = -\overline{T}_0(z)$.
+Due to continuity, this implies $\overline{T}_0(0) = 0$.
+Accordingly, we construct $\overline{T}_0(z)$ by translating $\overline{\mathcal{T}}_0(z)$ vertically to pass through the origin.
+We then take its odd-extension and include a unique scaling coefficient to satisfy the boundary conditions $\overline{T}_0(-1/2) = 1/2$ and $\overline{T}_0(1/2) = -1/2$.
 The initial mean temperature profile is therefore given by
 \begin{align*}
-    \bar{T}_0(z) &= \frac{1}{2} \begin{cases}
-        1 - \frac{\bar{\mathcal{T}}_0\big(\frac{z + 1/2}{\delta_0}\big)}{\bar{\mathcal{T}}_0\big(\frac{1}{2\delta_0}\big)} \quad -1/2 \leq z \leq 0 \\[0.5cm]
-        -1 + \frac{\bar{\mathcal{T}}_0\big(\frac{1/2 - z}{\delta_0}\big)}{\bar{\mathcal{T}}_0\big(\frac{1}{2\delta_0}\big)} \quad 0 < z \leq 1/2.
+    \overline{T}_0(z) &= \frac{1}{2} \begin{cases}
+        1 - \frac{\overline{\mathcal{T}}_0\big(\frac{z + 1/2}{\delta_0}\big)}{\overline{\mathcal{T}}_0\big(\frac{1}{2\delta_0}\big)} \quad -1/2 \leq z \leq 0 \\[0.5cm]
+        -1 + \frac{\overline{\mathcal{T}}_0\big(\frac{1/2 - z}{\delta_0}\big)}{\overline{\mathcal{T}}_0\big(\frac{1}{2\delta_0}\big)} \quad 0 < z \leq 1/2.
     \end{cases}
 \end{align*} 
- We expect each $\Ra$ to be associated with a unique $\delta_0$ for which $\bar{T}_0(z)$ is marginally-stable. 
+ We expect each $\Ra$ to be associated with a unique $\delta_0$ for which $\overline{T}_0(z)$ is marginally-stable. 
 It should be noted that when experimenting with various initial profiles $(\tanh, \rm{erf}, \rm{etc.})$, we obtain indistinguishable equilibrated states.
@@
 \section{Timestep Management} \label{sec:timestep}
-To find MSTE, we advance $\bar{T}$ by timesteps of size $\Delta t$.
+To find MSTE, we advance $\overline{T}$ by timesteps of size $\Delta t$.
 For large $\Delta t$, we find the advective flux terms fail to provide a stabilizing influence.
-This is due to coupling between the eigenfunctions $W(z)$, $\Theta(z)$ and the mean temperature profile $\bar{T}$.
+This is due to coupling between the eigenfunctions $W(z)$, $\Theta(z)$ and the mean temperature profile $\overline{T}$.
 In the context of our algorithm, this effectively deletes the sought-after root of the maximum eigenvalue function $\sigma_{\rm{max}}(A^2)$, causing the root-finding methods to fail. 
@@
 %Therefore results obtained uniquely via the use of relatively large $\Delta t$ must not agree with the analytic solution.
-If ignored, the concave features grow in magnitude until they affect $\bar{T}$ on a readily apparent scale.
-Eventually $\bar{T}$ develops oscillations near $z = 0$ and the timestep must be reduced.
+If ignored, the concave features grow in magnitude until they affect $\overline{T}$ on a readily apparent scale.
+Eventually $\overline{T}$ develops oscillations near $z = 0$ and the timestep must be reduced.
 Once these oscillations reach some amplitude, they cannot be eliminated via timestep reduction and the roots of $\sigma_{\rm{max}}(A^2)$ vanish.
@@
     This, along with $\Ra$ are specified on initialization.
-    The remaining quantities are computed directly from the MSTE.}
+    The remaining quantities are computed directly from the MSTE. 
+    The low $\Ra = 10^5$ case requires $\sim 12$ hours while the high $\Ra = 10^9$ case requires $\sim 72$ hours. 
+    Eigenvalue solves are performed for various $k_x$ simultaneously using 28 cores.}
     {\label{tab:metrics}}

### 2021-05-15 publication_materials/ms_rbc.tex
minor nomenclature

@@
     We find the Nusselt number scales like $\Nu \sim\Ra^{1/3}$.
-    When an MSTE is used as initial conditions for a 2D simulation, we find that Nu quickly equilibrates without the burst of turbulence often induced by purely conductive initial conditions, but we also find that the kinetic energy is too large and viscously attenuates on a long viscous time-scale.
+    When an MSTE is used as initial conditions for a 2D simulation, we find that Nu quickly equilibrates without the burst of turbulence often induced by purely conductive initial conditions, but we also find that the kinetic energy is too large and viscously attenuates on a long viscous time scale.
 \end{abstract}
@@
 In \citet{Beaume_2015}, researchers compute ECS in parallel shear flows by deriving and solving a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments. 
-They assume the background velocity evolves on a slow time-scale, and, to determine the perturbation amplitudes, they require marginal stability at each timestep.
+They assume the background velocity evolves on a slow time scale, and, to determine the perturbation amplitudes, they require marginal stability at each timestep.
 A similar strategy is employed by \citet{michel_chini_2019} to study acoustic streaming.
@@
 
-In this paper we derive and solve a quasilinear form of the Rayleigh-B\'{e}nard convection problem using a similar time-scale separation argument.
+In this paper we derive and solve a quasilinear form of the Rayleigh-B\'{e}nard convection problem using a similar time scale separation argument.
 In section~\ref{sec:model} we recall the underlying equations, and in section~\ref{sec:evolution} we describe how we evolve the background temperature profile while maintaining marginal stability.
@@
 \section{Model Setup}\label{sec:model}
-We begin with the Boussinesq approximation for Rayleigh-Bénard Convection, nondimensionalized on the freefall time-scale. 
+We begin with the Boussinesq approximation for Rayleigh-Bénard Convection, nondimensionalized on the freefall time scale. 
 The domain $\mathcal{D}$ is 2-dimensional, rectangular, and horizontally periodic with cartesian spatial coordinates $0 \leq x < 4$ and $-1/2 < z < 1/2$. 
@@
 However, the advective heat flux is proportional to $A^2$, so we need to specify the amplitude in order to solve equation~\ref{EQ:T0_IVP}.
-To evolve $\overline{T}$, we assume the perturbations evolve on a much faster time-scale than the mean temperature, as in \cite{michel_chini_2019}.
+To evolve $\overline{T}$, we assume the perturbations evolve on a much faster time scale than the mean temperature, as in \cite{michel_chini_2019}.
 Stable modes $(\sigma < 0)$ decay away rapidly. 
-Unstable modes $(\sigma > 0)$ will not persist on the slow time-scale because the advective term $\langle w'T' \rangle_x$ tends to stabilize $\overline{T}$, thereby creating a negative feedback loop.
-Only marginally stable modes can be maintained on the slow time-scale.
+Unstable modes $(\sigma > 0)$ will not persist on the slow time scale because the advective term $\langle w'T' \rangle_x$ tends to stabilize $\overline{T}$, thereby creating a negative feedback loop.
+Only marginally stable modes can be maintained on the slow time scale.
 Therefore the amplitude $A$ must satisfy
@@
     The eigenfunctions belonging to MSTE have significantly more kinetic energy than the statistically-steady state. 
-    Kinetic equilibrium is achieved on a long viscous time-scale.}
+    Kinetic equilibrium is achieved on a long viscous time scale.}
     \label{fig:ke_sim}
@@
 We also find that the average kinetic energy of the simulation initialized with MSTE is significantly larger than those found in either of the other cases, as shown Figure~\ref{fig:ke_sim}. 
-This is because the MSTE contain strong large-scale flows, which decay on a long viscous time-scale $t_{\nu}$. 
+This is because the MSTE contain strong large-scale flows, which decay on a long viscous time scale $t_{\nu}$. 
 Fluid in the other cases is initialized at rest. 
-Two viscous time-scales can be derived for this problem: one for the boundary layer 
+Two viscous time scales can be derived for this problem: one for the boundary layer 
 \begin{align*}
@@
 \end{align*}
-Empirically, we find $t_{\nu} \approx 200$ suggesting the true kinetic energy decay time-scale is based on a length scale $\ell \approx 0.14$ which is longer than the boundary layer height $\delta$ but shorter than the domain height $L_z$.
+Empirically, we find $t_{\nu} \approx 200$ suggesting the true kinetic energy decay time scale is based on a length scale $\ell \approx 0.14$ which is longer than the boundary layer height $\delta$ but shorter than the domain height $L_z$.
 Consequently, MSTE initial conditions do not reduce the simulation time required to achieve a statistically-steady state---rather they increase it considerably!
@@
 Simulations initialized with the MSTE \eq{EQ:mste_ic} do not undergo an early convective transient period, but have faster flows when compared with DNS.
-From a dynamical systems perspective, unstable orbits depart from MSTE and approach the global attractor on a viscous time-scale.
+From a dynamical systems perspective, unstable orbits depart from MSTE and approach the global attractor on a viscous time scale.
 This requires more computational effort to achieve relaxation when compared to the conventional conductive initial condition \eq{EQ:linear_ic}.

### 2021-05-26 RA1E6/Main.py
simulations

@@ -20,7 +20,7 @@ from Simulation import *     # pylint: disable=unused-wildcard-import
 # Settings/options
 restart = False
 load_profile = False
-subDir = '/results_conv'
+subDir = '/results_sqrt2'
 profile_file_name = os.path.dirname(os.path.abspath(__file__)) + '/avg_profs/averaged_avg_profs_ra1e8.h5'
 path = os.path.dirname(os.path.abspath(__file__)) + subDir
 if (not os.path.exists(path)):

### 2021-05-26 RA1E6/Simulation.py

@@ -684,7 +684,7 @@ class Simulation():
             #     plt.title(r'$<wb>_{zz}$' + ', ' + r'$k_x = $' + str(pi_mult) + r'$\pi$')
             #     plt.savefig(self.iteration_path + '/figures/' + str(int(pi_mult)) + 'p' + str(int(10*(pi_mult - int(pi_mult)))) + 'pi_wbzz')
             #     plt.close()
-            wb_zz_ar[i] = wb_zz.real
+            wb_zz_ar[i] = 0.5 * wb_zz.real
             logger.warning('Approximate unstable growth: ' + str(growth_m) + ' at kx: ' + str(kx))
         if CW.rank == 0:
             CW.Reduce(MPI.IN_PLACE, wb_zz_ar, op=MPI.SUM, root=0)
@@ -1027,10 +1027,12 @@ class Simulation():
             del_t = conv_data['del_t']
             kx1 = conv_data['kx1']
             kx2 = conv_data['kx2']
-            kx3 = conv_data['kx3']
             amp1 = conv_data['amp1']            
             amp2 = conv_data['amp2']
-            amp3 = conv_data['amp3']
+            threemodes = 'kx3' in conv_data.keys()
+            if (threemodes):
+                kx3 = conv_data['kx3']
+                amp3 = conv_data['amp3']
             delta_T += del_t
             for file in os.listdir(iteration_i_path + 'data'):
                 if (not file.endswith('.pick')):
@@ -1042,7 +1044,7 @@ class Simulation():
                     amp = np.sqrt(amp1)
                 elif (abs(kx - kx2) < 1e-8):
                     amp = np.sqrt(amp2)
-                elif (abs(kx - kx3) < 1e-8):
+                elif (threemodes and abs(kx - kx3) < 1e-8):
                     amp = np.sqrt(amp3)
                 else:
                     raise ValueError('Wavenumber in data file matches none of the converged wavenumbers!')

### 2021-05-26 RA1E7/Main.py

@@ -20,7 +20,7 @@ from Simulation import *     # pylint: disable=unused-wildcard-import
 # Settings/options
 restart = False
 load_profile = False
-subDir = '/results'
+subDir = '/results_conv'
 profile_file_name = os.path.dirname(os.path.abspath(__file__)) + '/avg_profs/averaged_avg_profs_ra1e8.h5'
 path = os.path.dirname(os.path.abspath(__file__)) + subDir
 if (not os.path.exists(path)):
@@ -28,7 +28,7 @@ if (not os.path.exists(path)):
     restart = True
     
 # Global parameters
-Nz = 512
+Nz = 256
 pi_range = 20
 Prandtl = 1
 Rayleigh = 2e7
@@ -48,9 +48,9 @@ rapid_adapt = False
 dT_regime = False
 suppress_dT = True
 del_T = 0.001
-avgd_iter_count = 50
+avgd_iter_count = 1
 show_avg_flux = False
-write_avgd_efs = False
+write_avgd_efs = True
 
 # Ra growth params
 ra_growth_mode = False

### 2021-05-26 RA1E7/Simulation.py

@@ -1013,10 +1013,12 @@ class Simulation():
             del_t = conv_data['del_t']
             kx1 = conv_data['kx1']
             kx2 = conv_data['kx2']
-            kx3 = conv_data['kx3']
             amp1 = conv_data['amp1']            
             amp2 = conv_data['amp2']
-            amp3 = conv_data['amp3']
+            threemodes = 'kx3' in conv_data.keys()
+            if (threemodes):
+                kx3 = conv_data['kx3']
+                amp3 = conv_data['amp3']
             delta_T += del_t
             for file in os.listdir(iteration_i_path + 'data'):
                 if (not file.endswith('.pick')):
@@ -1028,7 +1030,7 @@ class Simulation():
                     amp = np.sqrt(amp1)
                 elif (abs(kx - kx2) < 1e-8):
                     amp = np.sqrt(amp2)
-                elif (abs(kx - kx3) < 1e-8):
+                elif (threemodes and abs(kx - kx3) < 1e-8):
                     amp = np.sqrt(amp3)
                 else:
                     raise ValueError('Wavenumber in data file matches none of the converged wavenumbers!')

### 2021-05-26 RA1E8/Main.py

@@ -376,7 +376,7 @@ else:
         sim.ev_dict = dict(sim.evs)
         pickle.dump(sim.evs, open(sim.iteration_path + '/evs.pick', 'wb'))
 
-# sim.store_avg_eigenfunctions(2)
+sim.store_avg_eigenfunctions(2)
 print_nu_del()
 
 ##################################################

### 2021-05-26 rbc_sim_eq.sh

@@ -1,7 +1,7 @@
 #PBS -S /bin/bash
 #PBS -N rbc_sim_eq
 #PBS -l select=4:ncpus=28:mpiprocs=28:model=bro
-#PBS -l walltime=24:00:00
+#PBS -l walltime=48:00:00
 #PBS -j oe
 module load mpi-sgi/mpt
 module load comp-intel

### 2021-05-26 rbc_sim_load_ic.py

@@ -92,7 +92,8 @@ if not pathlib.Path('restart.h5').exists():
 
     # Accomodate differing resolutions in EVP and IVP processes
     N_evp = len(b0z_g)
-    evp_scale = int(N_evp / Nz)
+    evp_scale = N_evp / Nz
+    print(N_evp)
     x_evp, z_evp = domain.all_grids(scales=evp_scale)
     
     # Random perturbations, initialized globally for same results in parallel
@@ -169,7 +170,7 @@ else:
 
     # Timestepping and output
     dt = last_dt
-    stop_sim_time = 100
+    stop_sim_time = 400
     fh_mode = 'append'
 
 # Integration parameters
@@ -177,10 +178,10 @@ solver.stop_sim_time = stop_sim_time
 # solver.stop_iteration = 20
 
 # Analysis
-snapshots = solver.evaluator.add_file_handler('snapshots_eq', sim_dt=0.1, max_writes=50, mode=fh_mode)
-snapshots.add_task('b')
-snapshots.add_task('w')
-snapshots.add_task('u')
+# snapshots = solver.evaluator.add_file_handler('snapshots_eq_noflow', sim_dt=0.1, max_writes=50, mode=fh_mode)
+# snapshots.add_task('b')
+# snapshots.add_task('w')
+# snapshots.add_task('u')
 
 profiles = solver.evaluator.add_file_handler('profiles_noflow', sim_dt=0.1, max_writes=100, mode=fh_mode)
 profiles.add_task("P*integ(dz(b) - 1, 'x') / Lx", name='diffusive_flux')

### 2021-05-26 rewind_iterations.py

@@ -2,8 +2,8 @@ import os
 import sys
 import pickle
 
-rewind_iterations = 50
-path = os.path.dirname(os.path.abspath(__file__)) + '/RA1E9/results'
+rewind_iterations = 2
+path = os.path.dirname(os.path.abspath(__file__)) + '/RA1E6/results_conv'
 
 profiles = pickle.load(open(path + '/rbc_profiles_grid.pick', "rb"))[:-rewind_iterations]
 sim_times = pickle.load(open(path + '/sim_times.pick', 'rb'))[:-rewind_iterations]

### 2021-05-26 publication_materials/ms_rbc.tex

@@
 
-The MSTE retain several key features that are prevalent in experiments and simulations: $\Nu \sim\Ra^{1/3}$ scaling, large-scale convective cell structures, and minimum length scale agreement. 
-They also exhibit unique and unexpected features: mean temperature gradient-reversals/dips, high kinetic energy flows, and a larger $\Nu$ than other time-invariant solutions. 
+The MSTE contain large-scale convective cell structures, and have $\Nu\sim\Ra^{1/3}$.
+These are similar to what has been found in experiments and direct numerical simulations.
+But MSTE also exhibit unique and unexpected features: mean temperature gradient-reversals/dips, high kinetic energy flows, and a larger $\Nu$ than other time-invariant solutions. 
 When initializing with different mean temperature profiles, we find the same MSTE, suggesting these equilibria might be unique.
@@
 
+Another significant difference with DNS is the treatment of shear in the boundary layers.
+At sufficiently high $\Ra$, the shear in the kinetic boundary layers could become unstable and turbulent \cite{Ahlers}.
+This cannot occur in our quasilinear model because the background state has no velocity shear.
+One avenue for future work is to include a mean horizontal flow, which could develop boundary layer structures.
+In that case, we would search for states which also balance viscous and Reynolds stresses across the domain.
+Perturbations about this background state could include shear flow instabilities.
+Another approach would be to use the generalized quasilinear approximation, in which the background state includes both the mean and low-wavenumber temperature and velocity profiles \cite{marston2016}.
+This would allow for linear instabilities of the shear driven by low-wavenumber rolls, as we see in all MSTE.
+Generalized quasilinear calculations are inherently multi-dimensional, so they are more computationally expensive than the eigenvalue-based analysis used to find MSTE.
+Despite these limitations, our one-dimensional MSTE states capture many interesting features of convection.
+
 % To find MSTE, we initialize the time-evolution algorithm with the analytic temperature profile derived by \cite{Shishkina}.
@@
 \section*{Acknowledgments}
+This paper is dedicated to Charlie Doering, who greatly influenced the way many of us think about Rayleigh-Benard convection.
+DL met Charlie as a WHOI GFD summer fellow, and has difficulty imagining Walsh Cottage without Charlie's friendly and open scientific style, and enthusiasm for softball.
 The authors thank Geoff Vasil, Greg Chini, Kyle Augustson, and Emma Kaufman for their valuable feedback and suggestions.
-We also thank the \texttt{Dedalus} and \texttt{Eigentools} development teams. 
+We would also like to thank Charlie Doering and Baole Wen for the tabulated DNS and ECS data for figure~\ref{fig:nu_vs_ra}.
+We thank the \texttt{Dedalus} and \texttt{Eigentools} development teams. 
 Computations were conducted with support by the NASA High End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades with allocation GIDs s2276.

### 2021-05-26 plot_flux.py
pdf figs pfe

@@ -59,7 +59,7 @@ def plot_flux(Rayleigh, ax, path, iteration):
         advection4 = wb4*amp4
         advection5 = wb5*amp5
         flux = diffusion + advection1 + advection2 + advection3 + advection4 + advection5
-        ax.plot(z, diffusion, label = 'Diffusion', color='black', linestyle=(0, (5, 1)), zorder=10)
+        ax.plot(z, diffusion, label = 'Diffusion', color='black', zorder=10)
         pi_mult1 = str(round(kx1/np.pi, 1))
         pi_mult2 = str(round(kx2/np.pi, 1))
         pi_mult3 = str(round(kx3/np.pi, 1))
@@ -70,7 +70,7 @@ def plot_flux(Rayleigh, ax, path, iteration):
         ax.plot(z, advection3, label = 'Advection ($k_x  = $' + pi_mult3 + '$\pi$)')
         ax.plot(z, advection4, label = 'Advection ($k_x  = $' + pi_mult4 + '$\pi$)')
         ax.plot(z, advection5, label = 'Advection ($k_x  = $' + pi_mult5 + '$\pi$)')
-        ax.plot(z, flux, label = 'Total', color='black')
+        ax.plot(z, flux, label = 'Total', linestyle=(0, (5, 1)), color='black')
         ax.set_xlim(-0.5, 0.0)
         ax.set_yticks([0.000, 0.001, 0.002, 0.003])
         # ax.set_ylim(-0.0002, 0.0039)
@@ -92,10 +92,10 @@ def plot_flux(Rayleigh, ax, path, iteration):
         advection = wb*amp
         flux = diffusion + advection
         pi_mult = str(round(kx/np.pi, 1))
-        ax.plot(z, diffusion, label = 'Diffusion', color='black', linestyle=(0, (5, 1)), zorder=10)
+        ax.plot(z, diffusion, label = 'Diffusion', color='black', zorder=10)
         colors = plt.rcParams['axes.prop_cycle'].by_key()['color']
         ax.plot(z, advection, label = 'Advection ($k_x  = $' + pi_mult + '$\pi$)', color=colors[-1])
-        ax.plot(z, flux, label = 'Total', color='black')
+        ax.plot(z, flux, label = 'Total', linestyle=(0, (5, 1)), color='black')
         ax.set_xlim(-0.5, 0.0)
         ax.legend(frameon=False, loc='center right')
[…]

### 2021-05-26 plot_ke.py

@@ -55,7 +55,7 @@ if __name__ == "__main__":
 
     global path 
     path = os.path.dirname(os.path.abspath(__file__))
-    write_data = False
+    write_data = True
     plot = True
     if (write_data):
         args = docopt(__doc__)
@@ -91,4 +91,4 @@ if __name__ == "__main__":
         plt.ylabel(r'$\langle |\mathbf{u}|^2 \rangle_{\mathcal{D}}$')
         plt.title(r'$\rm{Ra} \, = \, 10^8$')
         # plt.savefig(path + '/publication_materials/sim_eq_ke_nonoise')
-        plt.savefig(path + '/publication_materials/sim_eq_ke_noflow')
+        plt.savefig(path + '/publication_materials/sim_eq_ke_noflow.pdf')

### 2021-05-26 plot_nu.py

@@ -121,4 +121,4 @@ if __name__ == "__main__":
         plt.ylabel(r'$\mathrm{Nu}$')
         plt.title(r'$\rm{Ra} \, = \, 10^8$')
         # plt.savefig(path + '/pubfigs/sim_eq_nu')
-        plt.savefig(path + '/publication_materials/sim_eq_nu_noflow')
+        plt.savefig(path + '/publication_materials/sim_eq_nu_noflow.pdf')

### 2021-05-26 plot_profiles.py

@@ -98,5 +98,5 @@ ax1.yaxis.tick_right()
 ax.set_title(r'$\rm{Ra} \, = \, 10^8$')
 # plt.legend(loc=3, prop={'size': 8})
 # plt.title('$b0_z$ Profiles')
-plt.savefig(root_path + '/publication_materials/T_profs_na', bbox_inches='tight')
+plt.savefig(root_path + '/publication_materials/T_profs_na.pdf', bbox_inches='tight')
 # plt.savefig(root_path + '/publication_materials/T_profs_na', bbox_inches='tight')

### 2021-05-26 plot_spectra_2ra.py

@@ -68,7 +68,7 @@ def plot_EVs(evs_mat, labels):
     # plt.legend(loc='lower right')
     # fig.text(0.00, 0.5, r'$\omega$', ha='center', va='center', rotation='vertical', fontsize=10)
     plt.savefig(path + '/pubfigs/EV_spectra_2ra', bbox_inches='tight')
-    plt.savefig(path + '/publication_materials/EV_spectra_2ra', bbox_inches='tight')
+    plt.savefig(path + '/publication_materials/EV_spectra_2ra.pdf', bbox_inches='tight')
 
 # fig = plt.figure()
 path = os.path.dirname(os.path.abspath(__file__))

### 2021-05-26 rbc_sim_load_ic.py

@@ -161,7 +161,7 @@ if not pathlib.Path('restart.h5').exists():
 
     # Timestepping and output
     dt = 5e-4
-    stop_sim_time = 100
+    stop_sim_time = 400
     fh_mode = 'overwrite'
 
 else:

### 2021-05-26 sim_figs.sh

@@ -1,7 +1,7 @@
 #PBS -S /bin/bash
-#PBS -N sim_figs0
+#PBS -N rbc_sim_noflow3
 #PBS -l select=32:ncpus=28:mpiprocs=28:model=bro
-#PBS -l walltime=24:00:00
+#PBS -l walltime=48:00:00
 #PBS -j oe
 module load mpi-sgi/mpt
 module load comp-intel
@@ -15,6 +15,6 @@ conda activate dedalus
 export MPI_UNBUFFERED_STDIO=true
 cd ~/scratch/dedalus/EVP_evolution/
 mpiexec_mpt -np 896 python3 rbc_sim_load_ic.py
-mpiexec_mpt -np 896 python3 -m dedalus merge_procs checkpoints_nonoise
-mpiexec_mpt -np 896 python3 plot_slices.py checkpoints_nonoise/*.h5 --output=frames_nonoise
-mpiexec_mpt -np 896 python3 -m dedalus merge_procs profiles_nonoise
+mpiexec_mpt -np 896 python3 -m dedalus merge_procs checkpoints_noflow
+mpiexec_mpt -np 896 python3 plot_slices.py checkpoints_noflow/*.h5 --output=frames_noflow
+mpiexec_mpt -np 896 python3 -m dedalus merge_procs profiles_noflow

### 2021-05-26 publication_materials/ms_rbc.tex
local pdf figs

@@
 \begin{figure}
-    \includegraphics[width=3.4in]{EV_spectrum_ol.png}
+    \includegraphics[width=3.4in]{EV_spectrum_ol.pdf}
     \caption{Eigenvalue spectra for $\Ra = 10^5$. The spectrum of an ``initial" marginally-stable mean temperature profile $\overline{T}(z, t_0)$ has a maximum eigenvalue of 0. 
@@
     \centering
-    \includegraphics[width=3.4in]{T_profs_na.png}
+    \includegraphics[width=3.4in]{T_profs_na.pdf}
     \caption{Mean temperature profiles $\overline{T}$ for $\Ra = 10^8$. 
@@
     \begin{tabular}{@{}c@{}}
-        \includegraphics[width=3.4in]{flux_sup_n.png}
+        \includegraphics[width=3.4in]{flux_sup_n.pdf}
     \end{tabular}
     \begin{tabular}{@{}c@{}}
-        \includegraphics[width=3.4in]{EV_spectra_2ra.png}
+        \includegraphics[width=3.4in]{EV_spectra_2ra.pdf}
     \end{tabular}
@@
     \centering
-    \includegraphics[width=3.4in]{kx_m_ra1.png}
+    \includegraphics[width=3.4in]{kx_m_ra1.pdf}
     \caption{Wavenumbers of marginally-stable modes in thermally equilibrated states. 
@@
     \centering
-    \includegraphics[width=3.4in]{del_kx_inv.png}
+    \includegraphics[width=3.4in]{del_kx_inv.pdf}
     \caption{For $\Ra \geq 10^6$, the maximum marginally-stable wavenumber (corresponding to the green x markers in Figure~\ref{fig:kx_marginals}) are inversely related to the boundary layer height $\delta$.
@@
     \centering
-    \includegraphics[width=3.4in]{del_ra.PNG}
+    \includegraphics[width=3.4in]{del_ra.pdf}
     \caption{Boundary layer height $\delta$ of MSTE. 
@@
     \centering
-    \includegraphics[width=7.1in]{nu_ra.PNG}
+    \includegraphics[width=7.1in]{nu_ra.pdf}
     \caption{Nusselt numbers are shown for MSTE, aspect-ratio-optimized ``steady rolls'' ECS \cite{Wen}, as well as statistically-steady 2D and 3D DNS \cite{Johnston, Scheel_2016}.
@@
     \centering
-    \includegraphics[width=3.4in]{sim_eq_nu_noflow.png}
+    \includegraphics[width=3.4in]{sim_eq_nu_noflow.pdf}
     \caption{Nusselt numbers of simulations performed at $\Ra = 10^8$, initialized with the conductive equilibrium plus thermal noise (black), the MSTE (blue), and the MSTE absent initial flow (green).
@@
     \centering
-    \includegraphics[width=3.4in]{sim_eq_ke_noflow.png}
+    \includegraphics[width=3.4in]{sim_eq_ke_noflow.pdf}
     \caption{Average kinetic energies are reported for the same simulations illustrated in Figure~\ref{fig:nu_sim} ($\Ra = 10^8$). 

### 2021-05-26 plot_bl.py
eigenfunctions

@@ -1,0 +1,67 @@
+import matplotlib
+import matplotlib.pyplot as plt
+import matplotlib.ticker as tck
+import numpy as np
+import pickle
+from mpi4py import MPI
+CW = MPI.COMM_WORLD
+import logging
+import dedalus.public as de
+logger = logging.getLogger(__name__)
+import sys
+import os
+import publication_settings
+matplotlib.rcParams.update(publication_settings.params)
+plt.rcParams.update({'figure.autolayout': True})
+golden_mean = (np.sqrt(5)-1.0)/2.0
+plt.rcParams.update({'figure.figsize': [3.4, 3.4*golden_mean]})
+path = os.path.dirname(os.path.abspath(__file__))
+colors = plt.rcParams['axes.prop_cycle'].by_key()['color']
+
+ra_vec = [1e5, 1e7, 1e9]
+ra_dirs = ['/RA1E5/results_conv/', '/RA1E7/results_conv/', '/RA1E9/results/']
+ra_strs = [r'$\rm{Ra} = 10^5$', r'$\rm{Ra} = 10^7$', r'$\rm{Ra} = 10^9$']
+# final_iterations = [9664, 8098, 12639]
+
+for i in range(len(ra_vec)):
+    f = open(path + ra_dirs[i] + 'rbc_profiles_grid.pick', 'rb')
+    b0z = pickle.load(f)[-1].real
+    N = len(b0z)
+    Nevp = int(1024 / N)
+    z_basis0 = de.Chebyshev('z', N, interval=(-1/2, 1/2), dealias=3/2)
+    z_basis = de.Chebyshev('z', 1024, interval=(-1/2, 1/2), dealias=3/2)
+    domain0 = de.Domain([z_basis0], grid_dtype=np.complex128, comm=MPI.COMM_SELF)
+    domain = de.Domain([z_basis], grid_dtype=np.complex128, comm=MPI.COMM_SELF)
+    z = domain.grid(0)
+    b0z_f = domain0.new_field()
+    b0z_f['g'] = b0z
+    b0_f = b0z_f.antidifferentiate(z_basis0, ('left', 0.5))
+    b0_f.set_scales(Nevp)
+    b0 = b0_f['g'].copy()
+
+    ind = 0;
+    for k in range(N - 1):
+        if (b0[k] > 0 and b0[k + 1] < 0):
+            if (abs(b0z[k]) > abs(b0z[k + 1])):
[…]

### 2021-05-26 plot_vars.py

@@ -1,0 +1,125 @@
+import matplotlib
+import matplotlib.pyplot as plt
+import matplotlib.ticker as tck
+import numpy as np
+import pickle
+from mpi4py import MPI
+CW = MPI.COMM_WORLD
+import logging
+import dedalus.public as de
+logger = logging.getLogger(__name__)
+import sys
+import os
+import publication_settings2
+matplotlib.rcParams.update(publication_settings2.params)
+plt.rcParams.update({'figure.autolayout': True})
+golden_mean = (np.sqrt(5)-1.0)/2.0
+plt.rcParams.update({'figure.figsize': [2*3.4, 2*3.4*golden_mean]})
+path = os.path.dirname(os.path.abspath(__file__))
+colors = plt.rcParams['axes.prop_cycle'].by_key()['color']
+
+Prandtl = 1
+Rayleigh = 4e8
+P = (Rayleigh * Prandtl)**(-1/2)
+iteration = 7471
+iteration_path = path + '/RA4E8/results_conv/Iteration' + str(iteration)
+
+z_basis = de.Chebyshev('z', 512, interval=(-1/2, 1/2))
+d = de.Domain([z_basis], grid_dtype=np.complex128, comm=MPI.COMM_SELF)
+z = d.grid(0)
+
+T = d.new_field()
+w = d.new_field()
+
+kxs = []
+labels = []
+
+for file in os.listdir(iteration_path + '/data'):
+    if (not file.endswith('.pick')):
+        continue
+    f = open(iteration_path + '/data/' + file, 'rb')
+    data = pickle.load(f)
+
+    kx = data['kx']
+    T['g'] = data['b']
+    w['g'] = data['w']
+
+    p_vars = {
+        w : '$w\'$',
+        T : '$T\'$',
+    }
+
+    pi_mult_str = r'$k_x = $' + str(round(kx/np.pi, 1)) + r'$\pi$'
+    kxs.append(kx)
+    labels.append(pi_mult_str)
+
+    nrow = 2
+    ncol = 2
+    sign = 1
+    if (np.max(np.abs(T['g'].real)) != np.max(T['g'].real)):
+        sign = -1
+
+    # plt.legend()
+    C = sign / max(np.abs(T['g'].real))
+
+    plt.subplot(2, 2, 3)
+    plt.plot(z, C * T['g'].imag)
[…]

### 2021-05-26 publication_materials/ms_rbc.tex
appendix D: eigenfunctions
G chini and G vassil's feedback

@@
 They assume the background velocity evolves on a slow time scale, and, to determine the perturbation amplitudes, they require marginal stability at each timestep.
-A similar strategy is employed by \citet{michel_chini_2019} to study acoustic streaming.
-In that work, an analytic expression for the first-order perturbation's amplitude is found by deriving a solvability condition.
+% A similar strategy is employed by \citet{michel_chini_2019} to study acoustic streaming.
+% In that work, an analytic expression for the first-order perturbation's amplitude is found by deriving a solvability condition.
+This quasilinear approach, which relies on multiple scales arguments in conjunction with a marginal stability constraint, is generalized by \cite{Chini_ql}.
+Studying two somewhat generic systems, researchers observe interdependent evolution of a background state and its perturbations within a marginally-stable manifold.
 
-In this paper we derive and solve a quasilinear form of the Rayleigh-B\'{e}nard convection problem using a similar time scale separation argument.
+In this paper employ the same strategy to the more complicated Rayleigh-B\'{e}nard convection problem.
 In section~\ref{sec:model} we recall the underlying equations, and in section~\ref{sec:evolution} we describe how we evolve the background temperature profile while maintaining marginal stability.
@@
 
+The temperature boundary layers of MSTE with various $\Ra$ exhibit self-similarity. 
+We illustrate this in Figure~\ref{fig:b0_delta} where the mean temperature $\overline{T}$ is plotted along a re-scaled $z$-coordinate.
+$\Delta$ denotes the minimum $z$-offset from the boundary layer which satisfies
+\begin{equation*}
+    \overline{T}|_{z = \Delta} = 0.
+\end{equation*}
+However $\Delta$ depends only on $\Ra$, effectively being constrained by marginal-stability.
+This suggests the re-scaled boundary layer geometry is intrinsic to MSTE, possibly minimizing diffusion as previously hypothesized.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=3.4in]{b0_delta.pdf}
+    \caption{Temperature boundary layer geometries of various MSTE. 
+    $\Delta$ denotes the minimum $z$-offset away from the boundary at which the mean temperature changes sign, i.e.~$\overline{T}(1/2 + \Delta) = 0$. 
+    Rescaling according to this quantity reveals self-similarity in the temperature boundary layers despite large changes in $\Ra$.}
+    \label{fig:b0_delta}
+\end{figure}
+
 The Nusselt number, which measures convective performance is given by
@@
 \onecolumngrid
-\section{MSTE Parameters and Results}\label{sec:tables}
+\section{MSTE Properties, Parameters, and Results}\label{sec:tables}
 
@@
 
+% \section{MSTE Eigenfunctions}\label{sec:eigenfunctions}
+\begin{figure}
+    \centering
+    \includegraphics[width=7.1in]{grid_vars.pdf}
+    \caption{The real and imaginary components of the temperature and pressure MSTE eigenfunctions are illustrated in separate plots for various marginally-stable modes. 
+    For the large-scale $k_x = 1.5\pi$ mode, we find the vertical velocity eigenfunction $W$ is maximized near the center of the domain.
+    In both other cases ($k_x = 5.5\pi, \, 17.5\pi$) the vertical velocity is localized near the boundaries.
+    In the temperature eigenfunction $\Theta$, small-scale zig-zags appear near the boundaries at $k_x = 1.5\pi$, subsiding as $k_x$ increases.}%
+    \label{fig:eigenfunctions}%
+\end{figure}
+
 \twocolumngrid
-
+\clearpage
 % \bibliographystyle{plain}

### 2021-05-26 plot_bl.py
delta

@@ -33,6 +33,7 @@ for i in range(len(ra_vec)):
     domain0 = de.Domain([z_basis0], grid_dtype=np.complex128, comm=MPI.COMM_SELF)
     domain = de.Domain([z_basis], grid_dtype=np.complex128, comm=MPI.COMM_SELF)
     z = domain.grid(0)
+    z0 = domain0.grid(0)
     b0z_f = domain0.new_field()
     b0z_f['g'] = b0z
     b0_f = b0z_f.antidifferentiate(z_basis0, ('left', 0.5))
@@ -40,28 +41,38 @@ for i in range(len(ra_vec)):
     b0 = b0_f['g'].copy()
 
     ind = 0;
-    for k in range(N - 1):
-        if (b0[k] > 0 and b0[k + 1] < 0):
+    xtra = 2.1
+    endind = 0;
+    for k in range(1023):
+        if (b0[k] > 0 and b0[k + 1] < 0 and ind == 0):
             if (abs(b0z[k]) > abs(b0z[k + 1])):
                 ind = k + 1
             else:
                 ind = k
-            break
 
-    z_bl = z[:ind] + 0.5
-    b0_bl = b0[:ind]
-    b0_bl = (b0_bl - b0_bl[-1]) / (1 - 2 * b0_bl[-1])
+        if (ind != 0 and z[k] + 0.5 > xtra * (z[ind] + 0.5)):
+            endind = k;
+            break;
+
+            
+            
+
+    z_bl = z[:endind] + 0.5
+    b0_bl = b0[:endind]
+    b0_bl = (b0_bl - b0_bl[ind]) / (1 - 2 * b0_bl[ind])
 
     if (i == 2):
-        plt.plot(z_bl / z_bl[-1], b0_bl, linestyle = 'dotted', linewidth = 3, label = ra_strs[i])
+        plt.plot(z_bl / z_bl[ind], b0_bl, linestyle = 'dashed', linewidth = 0.8, label = ra_strs[i])
+        # plt.plot(z_bl / z_bl[ind], b0_bl, linewidth = 2, label = ra_strs[i])
     elif (i == 1):
-        plt.plot(z_bl / z_bl[-1], b0_bl, linestyle = '-.', color = 'black', linewidth = 4, label = ra_strs[i])
[…]

### 2021-05-26 plot_bl.py
delta

@@ -38,17 +38,21 @@ for i in range(len(ra_vec)):
     b0z_f['g'] = b0z
     b0_f = b0z_f.antidifferentiate(z_basis0, ('left', 0.5))
     b0_f.set_scales(Nevp)
+    b0z_f.set_scales(Nevp)
     b0 = b0_f['g'].copy()
+    b0z = b0z_f['g'].copy()
 
     ind = 0;
     xtra = 2.1
     endind = 0;
     for k in range(1023):
-        if (b0[k] > 0 and b0[k + 1] < 0 and ind == 0):
-            if (abs(b0z[k]) > abs(b0z[k + 1])):
-                ind = k + 1
-            else:
-                ind = k
+        if (b0z[k] < 0 and b0z[k + 1] > 0 and ind == 0):
+            ind = k + 1
+            # if (abs(b0z[k]) > abs(b0z[k + 1])):
+            #     ind = k + 1
+            # else:
+            #     ind = k
+            print(0.5 + z[ind])
 
         if (ind != 0 and z[k] + 0.5 > xtra * (z[ind] + 0.5)):
             endind = k;
@@ -70,7 +74,7 @@ for i in range(len(ra_vec)):
     else:
         plt.plot(z_bl / z_bl[ind], b0_bl, linewidth = 3.5, color = colors[3], label = ra_strs[i])
 
-plt.xlabel(r'$\frac{z + 0.5}{\Delta}$')
+plt.xlabel(r'$\frac{z + 0.5}{\delta}$')
 plt.ylabel(r'$\overline{T}$')
 plt.legend()
 plt.xlim(0, xtra - 0.1)

### 2021-05-26 publication_materials/ms_rbc.tex
delta_0 appendix typo
boundary layer discussion (delta)

@@
 
+The temperature boundary layers of MSTE exhibit self-similarity despite great variation in $\Ra$. 
+We illustrate this in Figure~\ref{fig:b0_delta} where the mean temperature $\overline{T}$ is plotted along a rescaled $z$-coordinate $\frac{z + 1/2}{\delta}$.
+The rescaled boundary layer geometry appears intrinsic to the MSTE, possibly minimizing diffusion as previously hypothesized.
+This again highlights the importance of the boundary layer height's dependence on $\Ra$.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=3.4in]{b0_delta_solid.pdf}
+    \caption{Temperature boundary layer geometries of various MSTE. 
+    Rescaling according to the previously defined boundary layer height $\delta$ reveals self-similarity in the temperature boundary layers despite large variation in $\Ra$. 
+    The rescaled curves remain approximately self-similar for $z < 0$.
+    }
+    \label{fig:b0_delta}
+\end{figure}
+
 \begin{figure*}
@@
 \end{figure*}
-
-The temperature boundary layers of MSTE with various $\Ra$ exhibit self-similarity. 
-We illustrate this in Figure~\ref{fig:b0_delta} where the mean temperature $\overline{T}$ is plotted along a re-scaled $z$-coordinate.
-$\Delta$ denotes the minimum $z$-offset from the boundary layer which satisfies
-\begin{equation*}
-    \overline{T}|_{z = \Delta} = 0.
-\end{equation*}
-However $\Delta$ depends only on $\Ra$, effectively being constrained by marginal-stability.
-This suggests the re-scaled boundary layer geometry is intrinsic to MSTE, possibly minimizing diffusion as previously hypothesized.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=3.4in]{b0_delta.pdf}
-    \caption{Temperature boundary layer geometries of various MSTE. 
-    $\Delta$ denotes the minimum $z$-offset away from the boundary at which the mean temperature changes sign, i.e.~$\overline{T}(1/2 + \Delta) = 0$. 
-    Rescaling according to this quantity reveals self-similarity in the temperature boundary layers despite large changes in $\Ra$.}
-    \label{fig:b0_delta}
-\end{figure}
 
@@
     %\begin{longtable}[c]{@{}*{6}{>{\arraybackslash}p{0.15\linewidth}}@{}}
-    \quad\quad\quad $\Ra$	\quad\quad\quad	&	\quad\quad\quad		$N_z$	\quad\quad\quad		&	\quad\quad\quad		$\Nu$	\quad\quad\quad		&	\quad\quad\quad		$\delta_0$	\quad\quad\quad		&	\quad\quad	marginal $k_x$	\quad\quad\quad\\[0.03cm]
+    \quad\quad\quad $\Ra$	\quad\quad\quad	&	\quad\quad\quad		$N_z$	\quad\quad\quad		&	\quad\quad\quad		$\Nu$	\quad\quad\quad		&	\quad\quad\quad		$\delta$	\quad\quad\quad		&	\quad\quad	marginal $k_x$	\quad\quad\quad\\[0.03cm]
     \hline

### 2021-05-26 publication_materials/ms_rbc.tex
moving to pfe: eigenfunction plots

@@
 %For completeness, we specify a final boundary condition $p = p_0$ at $z = - 1/2$. 
-Any system of this form can be characterized by its dimensionless Rayleigh number $\Ra = \frac{g\alpha L^3 \Delta T}{\nu \kappa}$ and Prandtl number $\Pr = \frac{\nu}{\kappa}$, where $g, \, \alpha, \, L_z, \, \Delta T, \nu, \kappa$ are the gravitational acceleration, coefficient of thermal expansion, domain height, opposed temperature difference, kinematic viscosity, and thermal diffusivity respectively.
+Any system of this form can be characterized by its dimensionless Rayleigh number $\Ra = \frac{g\alpha L^3 \Delta T}{\nu \kappa}$ and Prandtl number $\Pr = \frac{\nu}{\kappa}$, where $g, \, \alpha, \, L_z, \, \Delta T, \nu, \kappa$ are the gravitational acceleration, coefficient of thermal expansion, domain height, imposed temperature difference, kinematic viscosity, and thermal diffusivity respectively.
 In this paper, we fix $\Pr = 1$.

### 2021-05-26 plot_vars.py

@@ -33,16 +33,32 @@ w = d.new_field()
 
 kxs = []
 labels = []
-
+z_ar = dict()
 for file in os.listdir(iteration_path + '/data'):
     if (not file.endswith('.pick')):
         continue
     f = open(iteration_path + '/data/' + file, 'rb')
     data = pickle.load(f)
-
-    kx = data['kx']
     T['g'] = data['b']
     w['g'] = data['w']
+
+    mod = T['g'].real * T['g'].real + T['g'].imag * T['g'].imag
+    nb = np.argmax(mod)
+    # print(nb)
+
+    mid_re = T['g'].real[nb]
+    mid_im = T['g'].imag[nb]
+    r = np.sqrt(mid_re * mid_re + mid_im * mid_im)
+    theta = np.arctan(mid_im / mid_re)
+    if ((mid_im < 0 and mid_re < 0) or (mid_im < 0 and mid_re > 0)):
+        theta += 2 * np.pi
+
+    ZC = np.exp(-1j * theta) / r
+    # ZC = 1.0
+    kx = data['kx']
+    z_ar[kx] = ZC
+
+
 
     p_vars = {
         w : '$w\'$',
@@ -55,29 +71,27 @@ for file in os.listdir(iteration_path + '/data'):
 
     nrow = 2
     ncol = 2
-    sign = 1
-    if (np.max(np.abs(T['g'].real)) != np.max(T['g'].real)):
-        sign = -1
 
-    # plt.legend()
-    C = sign / max(np.abs(T['g'].real))
-
+    nr = len(z) // 2
     plt.subplot(2, 2, 3)
-    plt.plot(z, C * T['g'].imag)
-    plt.xlim(-0.5, 0.5)
+    plt.plot(z[:nr], (T['g'] * ZC).imag[:nr])
+    plt.xlim(-0.5, 0.0)
     plt.xlabel(r'$z$')
     plt.ylabel(r'$\Im[\Theta]$', rotation=90)
 
     plt.subplot(2, 2, 1)
-    plt.plot(z, C * T['g'].real, label = pi_mult_str)
-    plt.xlim(-0.5, 0.5)
+    plt.plot(z[:nr], (T['g'] * ZC).real[:nr], label = pi_mult_str)
+    plt.xlim(-0.5, 0.0)
+    plt.ylim(-0.05, 1.05)
     plt.xlabel(r'$z$')
     plt.ylabel(r'$\Re[\Theta]$', rotation=90)
 
[…]

### 2021-05-27 plot_vars.py
move to local: eigenfunction plot done I think?

@@ -14,15 +14,14 @@ import publication_settings2
 matplotlib.rcParams.update(publication_settings2.params)
 plt.rcParams.update({'figure.autolayout': True})
 golden_mean = (np.sqrt(5)-1.0)/2.0
-plt.rcParams.update({'figure.figsize': [2*3.4, 2*3.4*golden_mean]})
+plt.rcParams.update({'figure.figsize': [2*3.4, 3*3.4*golden_mean]})
 path = os.path.dirname(os.path.abspath(__file__))
 colors = plt.rcParams['axes.prop_cycle'].by_key()['color']
 
 Prandtl = 1
-Rayleigh = 4e8
+Rayleigh = 1e9
 P = (Rayleigh * Prandtl)**(-1/2)
-iteration = 7471
-iteration_path = path + '/RA4E8/results_conv/Iteration' + str(iteration)
+iteration_path = path + '/RA1E9/results/Iteration00000'
 
 z_basis = de.Chebyshev('z', 512, interval=(-1/2, 1/2))
 d = de.Domain([z_basis], grid_dtype=np.complex128, comm=MPI.COMM_SELF)
@@ -34,7 +33,9 @@ w = d.new_field()
 kxs = []
 labels = []
 z_ar = dict()
-for file in os.listdir(iteration_path + '/data'):
+spi = 1
+mode = 0
+for file in sorted(os.listdir(iteration_path + '/data')):
     if (not file.endswith('.pick')):
         continue
     f = open(iteration_path + '/data/' + file, 'rb')
@@ -69,32 +70,41 @@ for file in os.listdir(iteration_path + '/data'):
     kxs.append(kx)
     labels.append(pi_mult_str)
 
-    nrow = 2
-    ncol = 2
 
     nr = len(z) // 2
-    plt.subplot(2, 2, 3)
-    plt.plot(z[:nr], (T['g'] * ZC).imag[:nr])
+    plt.subplot(3, 2, spi)
+    if (mode == 2 or mode == 4):
+        plt.plot(z[:nr], (T['g'] * ZC).real[:nr], color = colors[0], linestyle = 'dashed', linewidth = 2, label=pi_mult_str)
+    else:
[…]

### 2021-05-27 plot_vars.py
eigenfuncions: done

@@ -49,12 +49,16 @@ for file in sorted(os.listdir(iteration_path + '/data')):
 
     mid_re = T['g'].real[nb]
     mid_im = T['g'].imag[nb]
-    r = np.sqrt(mid_re * mid_re + mid_im * mid_im)
+    # r = np.sqrt(mid_re * mid_re + mid_im * mid_im)
     theta = np.arctan(mid_im / mid_re)
     if ((mid_im < 0 and mid_re < 0) or (mid_im < 0 and mid_re > 0)):
         theta += 2 * np.pi
 
-    ZC = np.exp(-1j * theta) / r
+
+    ZC = np.exp(-1j * theta)
+    A = de.operators.integrate((ZC * T) * (ZC * T), 'z').evaluate()['g'].real[0]
+    print("A = " + str(A))
+    ZC /= np.sqrt(2 * A)
     # ZC = 1.0
     kx = data['kx']
     z_ar[kx] = ZC
@@ -73,18 +77,19 @@ for file in sorted(os.listdir(iteration_path + '/data')):
 
     nr = len(z) // 2
     plt.subplot(3, 2, spi)
+    print("volume integral = " + str(2 * de.operators.integrate((T * ZC) * (T * ZC)).evaluate()['g'].real[0]))
     if (mode == 2 or mode == 4):
         plt.plot(z[:nr], (T['g'] * ZC).real[:nr], color = colors[0], linestyle = 'dashed', linewidth = 2, label=pi_mult_str)
     else:
-        plt.vlines(0.01053 - 0.5, -1, 2, linestyle = 'solid', label=r'$z = \delta - 0.5$', color = 'black', alpha = 0.6, linewidth = 2)
+        # plt.vlines(0.00817 - 0.5, -1, 2, linestyle = 'solid', label=r'$z = \delta - 0.5$', color = 'black', alpha = 0.6, linewidth = 2)
         plt.plot(z[:nr], (T['g'] * ZC).real[:nr], color = colors[-1], linewidth = 5, label=pi_mult_str)
     plt.xlim(-0.5, 0.0)
-    plt.ylim(-0.1, 1.1)
+    # plt.ylim(-0.1, 1.1)
     plt.xlabel(r'$z$')
-    plt.ylabel(r'$\Theta$', rotation=90)
+    plt.ylabel(r'$\theta$', rotation=90)
     plt.legend()
-    if (mode == 0):
-        plt.title('Temperature')
[…]

### 2021-05-27 publication_materials/ms_rbc.tex
appendix D completed

@@
 For large $\Delta t$, we find the advective flux terms fail to provide a stabilizing influence.
-This is due to coupling between the eigenfunctions $W(z)$, $\Theta(z)$ and the mean temperature profile $\overline{T}$.
+This is due to coupling between the eigenfunctions $W(z)$, $\theta(z)$ and the mean temperature profile $\overline{T}$.
 In the context of our algorithm, this effectively deletes the sought-after root of the maximum eigenvalue function $\sigma_{\rm{max}}(A^2)$, causing the root-finding methods to fail. 
@@
 \onecolumngrid
-\section{MSTE Properties, Parameters, and Results}\label{sec:tables}
+\section{MSTE Parameters, and Results}\label{sec:tables}
 
@@
 
-% \section{MSTE Eigenfunctions}\label{sec:eigenfunctions}
-\begin{figure}
+\clearpage
+\section{MSTE Eigenfunctions}\label{sec:eigenfunctions}
+\begin{figure}[H]
     \centering
     \includegraphics[width=7.1in]{grid_vars.pdf}
-    \caption{The real and imaginary components of the temperature and pressure MSTE eigenfunctions are illustrated in separate plots for various marginally-stable modes. 
+    \caption{The temperature and pressure MSTE eigenfunctions are shown in separate plots for various marginally-stable modes. 
+    Adjacent modes, whose wavenumbers only differ by $\pi/2$, are superimposed to illustrate their similarity.
     For the large-scale $k_x = 1.5\pi$ mode, we find the vertical velocity eigenfunction $W$ is maximized near the center of the domain.
-    In both other cases ($k_x = 5.5\pi, \, 17.5\pi$) the vertical velocity is localized near the boundaries.
-    In the temperature eigenfunction $\Theta$, small-scale zig-zags appear near the boundaries at $k_x = 1.5\pi$, subsiding as $k_x$ increases.}%
+    As $k_x$ increases, the vertical velocity is becomes more localized to the boundaries.
+    This trend is also apparent in the two pairs of adjacent modes.
+    In the temperature eigenfunctions $\theta$, small-scale zig-zags appear near the boundaries at $k_x = 1.5\pi$, subsiding as $k_x$ increases.
+    The left-most peaks of these profiles approximately coincide with the previously-defined boundary layer height $\delta$.
+    }%
     \label{fig:eigenfunctions}%

### 2021-05-27 publication_materials/ms_rbc.tex
Kyle's suggestions reflected

@@
     Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important properties remain elusive.
-    In this investigation, we derive and solve a quasilinear form of the Rayleigh-Bénard problem by representing the perturbations in terms of marginally stable eigenmodes.
+    To study convection in a novel context, we derive and solve a quasilinear form of the Rayleigh-Bénard problem by representing the perturbations in terms of marginally stable eigenmodes.
     The amplitude of each eigenmode is determined by requiring that the background state maintains marginal stability.
-    The background temperature profile evolves due to the advective flux of each eigenmode, as well as diffusion.
-    The entire calculation is one-dimensional, and can be run on a workstation.
-    We find the background temperature field evolves to an equilibrium state, where the advective flux from the marginally-stable eigenmodes and the diffusive flux sum to a constant.
+    The background temperature profile evolves due to the advective flux of every marginally-stable eigenmode, as well as diffusion.
+    To ensure marginal stability and to obtain the eigenfunctions at each timestep, we perform a one-dimensional eigenvalue solve on each of the allowable wavenumbers.
+    The background temperature field evolves to an equilibrium state, where the advective flux from the marginally-stable eigenmodes and the diffusive flux sum to a constant.
     These marginally-stable thermal equilibria (MSTE) are exact solutions of the quasilinear equations.
@@
     When an MSTE is used as initial conditions for a 2D simulation, we find that Nu quickly equilibrates without the burst of turbulence often induced by purely conductive initial conditions, but we also find that the kinetic energy is too large and viscously attenuates on a long viscous time scale.
+    This is due to the thin temperature boundary layers which diffuse heat more effectively, thereby requiring high-velocity advective flows to reach an equilibrium.
 \end{abstract}
@@
 Another approach relates to unstable exact coherent states (ECS) which are steady solutions to the full nonlinear problem \cite{Waleffe, Sondak, Wen, chini_cells}. 
-Simulations and analyses performed by \cite{Yalniz, Cvitanovic} suggest that chaotic solution trajectories might ``visit'' these ECS.
+Simulations and analyses performed by \cite{Yalniz, Cvitanovic} suggest that chaotic solution trajectories might intermittently resemble these ECS.
 Should that be the case, it is crucial that we discover and classify such equilibria.
@@
 In this paper employ the same strategy to the more complicated Rayleigh-B\'{e}nard convection problem.
-In section~\ref{sec:model} we recall the underlying equations, and in section~\ref{sec:evolution} we describe how we evolve the background temperature profile while maintaining marginal stability.
-Section~\ref{sec:properties} describes the properties of the marginally-stable thermal equilibria, in particular how the Nusselt number and characteristic wavenumbers vary with the Rayleigh number.
-Finally, we describe the results of simulations initialized with marginally-stable thermal equilibria in section~\ref{sec:sims}, and conclude in section~\ref{sec:Discussion}.
+In section~\ref{sec:model} we recall the underlying equations, and in section~\ref{sec:evolution} we outline how we evolve the background temperature profile while maintaining marginal stability.
+Section~\ref{sec:properties} pertains to the properties of the marginally-stable thermal equilibria, in particular how the Nusselt number and characteristic wavenumbers vary with the Rayleigh number.
+Finally, we analyze the results of simulations initialized with marginally-stable thermal equilibria in section~\ref{sec:sims}, and conclude in section~\ref{sec:Discussion}.
 
 \section{Model Setup}\label{sec:model}
-We begin with the Boussinesq approximation for Rayleigh-Bénard Convection, nondimensionalized on the freefall time scale. 
+We begin with the Boussinesq approximation for Rayleigh-Bénard Convection, nondimensionalized on the free-fall time scale. 
 The domain $\mathcal{D}$ is 2-dimensional, rectangular, and horizontally periodic with cartesian spatial coordinates $0 \leq x < 4$ and $-1/2 < z < 1/2$.
+We define the corresponding domain width $L_x = 4$ and height  $L_z = 1$.
 The fluid of interest is constrained between two flat boundaries at $z = -1/2$ and $z = 1/2$ with fixed temperatures $1/2$ and $-1/2$ respectively. 
@@
 %For completeness, we specify a final boundary condition $p = p_0$ at $z = - 1/2$. 
-Any system of this form can be characterized by its dimensionless Rayleigh number $\Ra = \frac{g\alpha L^3 \Delta T}{\nu \kappa}$ and Prandtl number $\Pr = \frac{\nu}{\kappa}$, where $g, \, \alpha, \, L_z, \, \Delta T, \nu, \kappa$ are the gravitational acceleration, coefficient of thermal expansion, domain height, imposed temperature difference, kinematic viscosity, and thermal diffusivity respectively.
+A Boussinesq convection system of this form can be characterized by its dimensionless Rayleigh number $\Ra = \frac{g\alpha L^3_z \Delta T}{\nu \kappa}$ and Prandtl number $\Pr = \frac{\nu}{\kappa}$, where $g, \, \alpha, \, L_z, \, \Delta T, \nu, \kappa$ are the gravitational acceleration, coefficient of thermal expansion, domain height, imposed temperature difference, kinematic viscosity, and thermal diffusivity respectively.
 In this paper, we fix $\Pr = 1$.
@@
 \begin{equation}
-    \langle f'(x, z, t) \rangle_x \equiv \int_{0}^4 f'(x, z, t) dx = 0.
+    \langle f'(x, z, t) \rangle_x \equiv \int_{0}^{L_x} f'(x, z, t) dx = 0.
 \end{equation}
@@
 with associated boundary conditions $\overline{T}(-1/2, t) = 1/2$ and $\overline{T}(1/2, t) = -1/2$.
-It should be noted that we could obtain a similar IVP for $u$ by breaking symmetry and considering some nontrivial mean horizontal flow $\overline{u}(z, t)$.
+It should be noted that we could obtain a similar IVP for $u$ by breaking reflection symmetry about the midplane $z = 0$ and considering some nontrivial mean horizontal flow $\overline{u}(z, t)$.
 However we must have $\overline{w}(z, t) = 0$ due to incompressibility.
 
-Substituting \eq{EQ:reynolds_dc_p} into \eq{EQ:motion2} and taking the horizontal average reveals that the mean pressure field $\overline{p}(z)$ must satisfy
+Substituting \eq{EQ:reynolds_dc_p} into \eq{EQ:motion2} and taking the horizontal average reveals that the mean pressure field $\overline{p}(z, \, t)$ must satisfy
 \begin{equation}
-    0 = -\frac{\partial \overline{p}}{\partial z} + \overline{T}\label{EQ:p_bar}
+    0 = -\frac{\partial \overline{p}}{\partial z} + \overline{T}. \label{EQ:p_bar}
 \end{equation}
@@
 For each $k_x$, we can assess the stability of the perturbations by solving for the eigenvalue $s$, whose imaginary component $\sigma$ plays the role of an exponential growth rate. 
-Positive eigenvalues indicate that the system is unstable to small disturbances of wavenumber $k_x$, while negative eigenvalues indicate stability. 
+Positive eigenvalues indicate that the system is unstable to small disturbances whose Fourier decomposition includes a nontrivial component of wavenumber $k_x$.
+Negative eigenvalues indicate stability. 
 A complete linear stability analysis requires solution over the full spectrum of wavenumbers. 
@@
 \end{align}
-where $\overline{T}_{\rm{diff}}$ and $\overline{T}_{\rm{adv}}$ denote to the diffused and advected temperature profiles.
+where $\overline{T}_{\rm{diff}}$ and $\overline{T}_{\rm{adv}}$ denote the diffused and advected temperature profiles.
 We initialize $\overline{T}_{\rm{diff}}$ and $\overline{T}_{\rm{adv}}$ with $\overline{T}(z, t_0)$, and evolve the equations to $t=t_0+\Delta t$.
@@
 The subscript 0 denotes a preliminary estimate which we later refine.
+In general, when $\Lambda^2_0 > 0$, the root-finding algorithm is stable.
+The alternative can occur when the timestep approaches machine precision, in which case $\sigma_{\rm{diff}}$ and $\sigma_{\rm{adv}}$ are subject to floating point errors.
 
@@
 where $W_n$ and $\theta_n$ are the marginally stable eigenmodes associated with different values of $k_x$. 
+The factor of 2 is due to horizontal averaging.
 There are now $N$ modes, each with their own amplitude to solve for and eigenvalue to keep marginally-stable. 
@@
 Performing an eigenvalue solve by setting $\overline{T}$ equal to the DNS profile yields unstable eigenvalues. 
-This suggests that MSTE might maximize boundary layer thickness, subject to the marginal stability constraint.
+Every marginally-stable initial profile we experiment with ($\tanh$, $\rm{erf}$) has thinner boundary layers than the DNS and MSTE profiles.
+In conjunction, these two facts suggest that MSTE maximize boundary layer thickness, subject to the marginal stability constraint.
 
@@
     At large $\Ra$, high-wavenumber modes contribute pronounced small-scale advection profiles which tightly hug the thin boundary layers. 
-    A combination of of progressively wider advection profiles is necessary to transition to bulk advection provided by the $k_x = 1.5\pi$ mode.}
+    A combination of of progressively wider advection profiles is necessary to transition to bulk advection provided by the $k_x = 1.5\pi$ mode. 
+    This bulk mode mimics the large-scale convective cells which are characteristic of Rayleigh–Bénard convection, both in qualitative structure and number of cells in the domain.
+    The eigenfunctions which compose the advective profiles are illustrated in Appendix~\ref{sec:eigenfunctions}.}
     \label{fig:flux}
@@
 These dips appear in every solution, regardless of $\Ra$. 
-Physically, they correspond to thin layers in which the mean temperature gradient reverses, contradicting an important hypothesis of \cite{Malkus_1954,Howard_1966}. 
+Physically, they correspond to thin layers in which the mean temperature gradient reverses, contradicting an important hypothesis of \cite{Malkus_1954}. 
 This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure~\ref{fig:flux}. 
@@
 Closer to the bulk of the domain, we see wider advection profiles corresponding to modes in a second group of marginal modes $k_x = 6\pi, \, 6.5\pi$.
-The $k_x = 1.5\pi$ mode forms the large-scale convective cell structures observed in DNS, again occupying the bulk of the domain.
+The $k_x = 1.5\pi$ mode forms the same arrangement and number of large-scale convective cells observed in DNS, again occupying the bulk of the domain.
 The pairs of modes $k_x = 6\pi, \, 6.5\pi$ and $k_x=23.5\pi, \, 24\pi$ are each associated with a single maximum in our plots of growth rate $\sigma$ as a function of $k_x$ (lower right panel of Figure~\ref{fig:flux}).
@@
 In Figure~\ref{fig:bl_ra}, we illustrate the scaling behavior of the boundary layer height $\delta = \Ra^{-1/3}$. 
-This is consistent with Malkus' classical marginal-stability theory, a scaling argument which perceives the boundary regions as subdomains which are themselves marginally-stable \cite{Malkus_1954}.
+This is consistent with Malkus' classical marginal stability theory, a scaling argument which perceives the boundary regions as subdomains which are themselves marginally-stable \cite{Malkus_1954}.
 
@@
 Unstable modes tend to stabilize the system rapidly, creating a negative feedback loop whose average state is linearly unstable. 
-Future work could adjust the marginal-stability criterion to allow for moderately unstable modes.
+Future work could adjust the marginal stability criterion to allow for moderately unstable modes.
 Should the fast and slow time scales not be entirely separate, these modes might persist for long times. 
@@
 We find that reducing the timestep $\Delta t$ by the same factor of 1.1 whenever this curvature measure exceeds $10^{-6}$ curtails the problem.
-Both of these issues appear to become more prominent as the boundary layers diffuse over the course of the algorithm's implementation (see Figure~\ref{fig:T0_profiles}).
+Both of these issues appear to become more prominent as the boundary layers diffuse over the course of the algorithm's execution (see Figure~\ref{fig:T0_profiles}).
 Thus there is never a practical opportunity to increase the timestep.
@@
     \caption{The temperature and pressure MSTE eigenfunctions are shown in separate plots for various marginally-stable modes. 
+    Though the eigenfunctions are allowed to be complex, the linear system \eqss{EQ:linear1}{EQ:linear3} obeys phase-shift symmetry.
+    Any set of solutions can be phase-shifted by multiplying the perturbations by an arbitrary complex quantity $e^{i\phi}$.
+    In this particular case, we can eliminate the perturbations' imaginary components by selecting the proper $\phi$.
+    This is due to the exchange of stabilities mentioned previously: $\omega = 0$ at marginal stability implies that the system admits a set of real solutions.
     Adjacent modes, whose wavenumbers only differ by $\pi/2$, are superimposed to illustrate their similarity.

### 2021-05-27 plot_ke.py
noflow sim 400 time units

@@ -82,9 +82,9 @@ if __name__ == "__main__":
         sim_times_ar = ke_data['sim_times_ar']
         colors = plt.rcParams['axes.prop_cycle'].by_key()['color']
         plt.plot(sim_times_ar_eq_noflow, ke_ar_eq_noflow, color=colors[0])
-        plt.plot(sim_times_ar, ke_ar, color='black', label = 'Linear IC')
-        plt.plot(sim_times_ar_eq, ke_ar_eq, color=colors[-1], label = 'MSTE IC')
-        plt.plot(sim_times_ar_eq_noflow, ke_ar_eq_noflow, color=colors[0], label = 'MSTE No Flow IC')
+        plt.plot(sim_times_ar, ke_ar, color='black', label = 'Linear IC', linewidth = 3)
+        plt.plot(sim_times_ar_eq, ke_ar_eq, color=colors[-1], label = 'MSTE IC', linewidth = 2)
+        plt.plot(sim_times_ar_eq_noflow, ke_ar_eq_noflow, color=colors[0], label = 'MSTE No Flow IC', linewidth = 1.3)
         plt.xlim(0, 400)
         plt.legend(frameon=False)
         plt.xlabel(r'$t$')

### 2021-05-27 plot_nu.py

@@ -115,10 +115,10 @@ if __name__ == "__main__":
         plt.plot(sim_times_ar, nu_ar, color='black', label = 'Linear IC')
         plt.plot(sim_times_ar_eq, nu_ar_eq, color=colors[-1], label = 'MSTE IC')
         plt.plot(sim_times_ar_eq_noflow, nu_ar_eq_noflow, color=colors[0], label = 'MSTE No Flow IC')
-        plt.xlim(0, 100)
+        plt.xlim(0, 400)
         plt.legend(frameon=False)
         plt.xlabel(r'$t$')
         plt.ylabel(r'$\mathrm{Nu}$')
         plt.title(r'$\rm{Ra} \, = \, 10^8$')
         # plt.savefig(path + '/pubfigs/sim_eq_nu')
-        plt.savefig(path + '/publication_materials/sim_eq_nu_noflow.pdf')
+        plt.savefig(path + '/publication_materials/sim_eq_nu_noflow2.pdf')

### 2021-05-27 publication_materials/ms_rbc.tex
Small edits to appendix D.

@@
 In Figure~\ref{fig:flux}, we give heat flux profiles and eigenvalue spectra for two cases: $\Ra = 2 \times 10^5$ (top) and $\Ra = 10^9$ (bottom). 
+Appendix~\ref{sec:eigenfunctions} shows representative vertical velocity and temperature perturbation eigenfunctions.
 For $\Ra = 2 \times 10^5$, there is a single marginal mode at $k_x = 1.5\pi$ whose advective flux occupies the bulk of the domain. 
@@
 
-\clearpage
 \section{MSTE Eigenfunctions}\label{sec:eigenfunctions}
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=7.1in]{grid_vars.pdf}
-    \caption{The temperature and pressure MSTE eigenfunctions are shown in separate plots for various marginally-stable modes. 
-    Though the eigenfunctions are allowed to be complex, the linear system \eqss{EQ:linear1}{EQ:linear3} obeys phase-shift symmetry.
+
+In Figure~\ref{fig:eigenfunctions} we plot the velocity and temperature perturbation eigenfunctions for the marginally stable modes in the $\Ra =10^9$ MSTE.
+Though the eigenfunctions are in general complex, the linear system \eqss{EQ:linear1}{EQ:linear3} obeys phase-shift symmetry.
 Any set of solutions can be phase-shifted by multiplying the perturbations by an arbitrary complex quantity $e^{i\phi}$.
@@
 As $k_x$ increases, the vertical velocity is becomes more localized to the boundaries.
+However, in all cases, the temperature perturbations are more concentrated at the boundaries than the vertical velocity.
 This trend is also apparent in the two pairs of adjacent modes.
 In the temperature eigenfunctions $\theta$, small-scale zig-zags appear near the boundaries at $k_x = 1.5\pi$, subsiding as $k_x$ increases.
-    The left-most peaks of these profiles approximately coincide with the previously-defined boundary layer height $\delta$.
+The left-most peaks of these temperature perturbation profiles approximately coincide with the previously-defined boundary layer height $\delta$.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=7.1in]{grid_vars.pdf}
+    \caption{The temperature and pressure MSTE eigenfunctions are shown in separate plots for various marginally-stable modes. 
+    The eigenfunctions are normalized such that $\langle |\theta|^2\rangle_{\mathcal{D}}=1$.
+    We select a phase such that the eigenfunctions are real.
     }%

### 2021-05-27 publication_materials/ms_rbc.tex
minor proof-reading edits

@@
     The background temperature profile evolves due to the advective flux of every marginally-stable eigenmode, as well as diffusion.
-    To ensure marginal stability and to obtain the eigenfunctions at each timestep, we perform a one-dimensional eigenvalue solve on each of the allowable wavenumbers.
+    To ensure marginal stability and to obtain the eigenfunctions at every timestep, we perform a one-dimensional eigenvalue solve on each of the allowable wavenumbers.
     The background temperature field evolves to an equilibrium state, where the advective flux from the marginally-stable eigenmodes and the diffusive flux sum to a constant.
@@
 The quasilinear approximation starts with a decomposition of all variables into a background and perturbations about this background.
-This approximation neglects the nonlinear interactions between perturbations which modify the perturbations themselves \cite{marston2016}.
+This approximation neglects the nonlinear interactions between perturbations which would otherwise modify the perturbations themselves \cite{marston2016}.
 This renders the perturbation equations linear.
@@
 % In that work, an analytic expression for the first-order perturbation's amplitude is found by deriving a solvability condition.
-This quasilinear approach, which relies on multiple scales arguments in conjunction with a marginal stability constraint, is generalized by \cite{Chini_ql}.
-Studying two somewhat generic systems, researchers observe interdependent evolution of a background state and its perturbations within a marginally-stable manifold.
+This quasilinear approach, which relies on multi-scale arguments in conjunction with a marginal stability constraint, is generalized by \citet{Chini_ql}.
+Studying two somewhat generic systems, researchers observe the interdependent evolution of a background state and its perturbations within a marginally-stable manifold.
 
-In this paper employ the same strategy to the more complicated Rayleigh-B\'{e}nard convection problem.
-In section~\ref{sec:model} we recall the underlying equations, and in section~\ref{sec:evolution} we outline how we evolve the background temperature profile while maintaining marginal stability.
+In this paper we employ the same strategy to the more complicated Rayleigh-B\'{e}nard convection problem.
+In Section~\ref{sec:model} we recall the underlying equations, and in Section~\ref{sec:evolution} we outline how we evolve the background temperature profile while maintaining marginal stability.
 Section~\ref{sec:properties} pertains to the properties of the marginally-stable thermal equilibria, in particular how the Nusselt number and characteristic wavenumbers vary with the Rayleigh number.
-Finally, we analyze the results of simulations initialized with marginally-stable thermal equilibria in section~\ref{sec:sims}, and conclude in section~\ref{sec:Discussion}.
+Finally, we analyze the results of simulations initialized with marginally-stable thermal equilibria in Section~\ref{sec:sims}, and conclude in Section~\ref{sec:Discussion}.
 
@@
 %For completeness, we specify a final boundary condition $p = p_0$ at $z = - 1/2$. 
-A Boussinesq convection system of this form can be characterized by its dimensionless Rayleigh number $\Ra = \frac{g\alpha L^3_z \Delta T}{\nu \kappa}$ and Prandtl number $\Pr = \frac{\nu}{\kappa}$, where $g, \, \alpha, \, L_z, \, \Delta T, \nu, \kappa$ are the gravitational acceleration, coefficient of thermal expansion, domain height, imposed temperature difference, kinematic viscosity, and thermal diffusivity respectively.
+A Boussinesq convection system of this form can be characterized by its dimensionless Rayleigh number $\Ra = \frac{g\alpha L^3_z \Delta T}{\nu \kappa}$ and Prandtl number $\Pr = \frac{\nu}{\kappa}$, where $g, \, \alpha,, \, \Delta T, \nu, \kappa$ are the gravitational acceleration, coefficient of thermal expansion, imposed temperature difference, kinematic viscosity, and thermal diffusivity respectively.
 In this paper, we fix $\Pr = 1$.
@@
 \end{align}
-where $A$ is the (undetermined) mode amplitude, $s = \omega + i\sigma$ and $k_x$ is constrained, by periodicity, to the countably infinite set (spectrum) of wavenumbers
+where $A$ is the (undetermined) mode amplitude, $s = \omega + i\sigma$ is the eigenvalue, and $k_x$ is constrained, by periodicity, to the countably infinite set (spectrum) of wavenumbers
 \begin{align}
@@
 
-To calculate the advective heat flux in equation~\ref{EQ:T0_IVP}, we can sum $\langle w'T' \rangle_x$ from each horizontal wavenumber individually.
+To calculate the advective heat flux in equation~\ref{EQ:T0_IVP}, we can sum the individual advective terms $\langle w'T' \rangle_x$ of every marginally stable mode.
 In this way, the heat flux from the perturbations influence the evolution of $\overline{T}$.
 But the evolution of $\overline{T}$ also influences the perturbations, as equation~\ref{EQ:linear3} depends on $\partial_z \overline{T}$.
-Thus, the mean temperature and perturbation fields are coupled.
+Thus, the mean temperature and perturbation fields are coupled, as is the case in~\cite{Beaume_2015, Chini_ql}.
 
@@
 For various $\Ra$ and fixed $\Pr = 1$, we seek marginally-stable thermal equilibria (MSTE) satisfying $\frac{\partial \overline{T}}{\partial t} = 0$ according to \eq{EQ:T0_IVP}. 
-We employ the \texttt{Dedalus} pseudo-spectral python framework\footnotemark[1] \cite{Dedalus_2020} to solve the eigenvalue problem outlined in Section \ref{sec:model} as well as the time evolution equations \eq{EQ:T0_IVP}.
+We employ the \texttt{Dedalus} pseudo-spectral python framework\footnotemark[1] \cite{Dedalus_2020} to solve the eigenvalue problem outlined in Section~\ref{sec:model} as well as the time evolution equation \eq{EQ:T0_IVP}.
 We represent each field with Chebyshev polynomials and use the 3/2 dealiasing rule to calculate the advective heat flux.
-The necessary number of basis functions increases with $\Ra$ as the eigenfunctions include increasingly small-scale features (see Appendix \ref{sec:tables}). 
+The necessary number of basis functions increases with $\Ra$ as the eigenfunctions include increasingly small-scale features (see Appendices \ref{sec:tables} \& \ref{sec:eigenfunctions}). 
 We use the \texttt{Eigentools} package\footnotemark[2] \cite{Eigentools} to manipulate the eigenfunctions and calculate the advective heat flux $\langle w' T' \rangle_x$.
@@
 
-\url{https://github.com/DedalusProject/dedalus/releases}}
+\url{https://dedalus-project.org/}
+
+\url{https://github.com/DedalusProject/dedalus/releases}
+}
 
@@
 
-To initialize our calculations, we construct a marginally-stable initial temperature profile $\overline{T}(z, t=0)$ whose equation is given in appendix~\ref{sec:initial_profile}. 
+To initialize our calculations, we construct a marginally-stable initial temperature profile $\overline{T}(z, t=0)$ whose equation is given in Appendix~\ref{sec:initial_profile}. 
 We use \eq{EQ:T0_IVP} to evolve $\overline{T}(z, t_0)$ into a new marginally-stable profile $\overline{T}(z, t_0 + \Delta t)$.
@@
 \begin{figure}
-    \includegraphics[width=3.4in]{EV_spectrum_ol.pdf}
+    \includegraphics[width=3.375in]{EV_spectrum_ol.pdf}
     \caption{Eigenvalue spectra for $\Ra = 10^5$. The spectrum of an ``initial" marginally-stable mean temperature profile $\overline{T}(z, t_0)$ has a maximum eigenvalue of 0. 
@@
 Diffusing $\overline{T}(z, t_0)$ tends to increase its growth rates while ignoring the diffusive term and evolving according to advection tends to decrease its growth rates.
-$A$ must be selected such that these two influences are equal and opposite.
+The amplitude $A$ must be selected such that these two influences are equal and opposite.
 We can measure the effects of diffusion and advection on the maximum eigenvalue by solving two new IVPs
@@
 In general, when $\Lambda^2_0 > 0$, the root-finding algorithm is stable.
-The alternative can occur when the timestep approaches machine precision, in which case $\sigma_{\rm{diff}}$ and $\sigma_{\rm{adv}}$ are subject to floating point errors.
+The alternative can occur when the timestep approaches machine precision, in which case $\sigma_{\rm{diff}}$ and $\sigma_{\rm{adv}}$ are subject to floating point errors of comparable order to themselves.
 
@@
 Crucially, we do not assume the $k_x$ of the marginally-stable mode is fixed.
-In section \ref{sec:multiple_modes} we specify procedures for the treatment of multiple simultaneously marginal modes.
+In Section~\ref{sec:multiple_modes} we specify procedures for the treatment of multiple simultaneously marginal modes.
 
@@
 We account for the influence of $N$ advection terms on $N$ eigenvalues (one for each mode) by constructing an eigenvalue matrix $\Sigma_{\rm{adv}}$.
-To calculate element of $\Sigma_{\rm{adv}}$ at row $i$ and column $j$, we evolve the background temperature under only advection by mode $j$ for a time interval $\Delta t$.
+To calculate the element of $\Sigma_{\rm{adv}}$ at row $i$ and column $j$, we evolve the background temperature under only advection by mode $j$ for a time interval $\Delta t$.
 Then the $i,j$ component of $\Sigma_{\rm{adv}}$ is given by the eigenvalue of the $i$th mode.
 
-Our estimate $\vec{\Lambda^2_0}$ does not give a background temperature for which all $N$ modes are exactly marginally stable.
+Our estimate $\vec{\Lambda^2_0}$ does not typically give a background temperature for which all $N$ modes are exactly marginally stable.
 We refine our vector of amplitudes via Newton's method.
@@
 We iterate Newton's method until all marginally stable modes have eigenvalues within $10^{-9}$ of zero.
-We find $\vec{\sigma}(\vec{A^2})$ does indeed have a unique root provided the time step is not too large and there are no numerical instabilities, as outlined in appendix \ref{sec:timestep}.
+We find $\vec{\sigma}(\vec{A^2})$ does indeed have a unique root provided the time step is not too large and there are no numerical instabilities, as outlined in Appendix~\ref{sec:timestep}.
 Presumably this is due to the coupling of $\langle w'T' \rangle_x$ with $\overline{T}$.
@@
 We facilitate these transitions by defining an adjustable candidate tolerance $\varepsilon_{\rm{cand}} \in [10^{-6}, 10^{-8}]$.
-A mode which meets the candidate tolerance can be included as a candidate marginal mode.
+A mode which meets the candidate tolerance can be included in the subsequent timestep as a candidate marginal mode.
 Candidate modes are rejected when the root-finding algorithm converges on a negative amplitude $A^2 < 0$.
@@
 In a similar manner, a marginally-stable mode need not remain marginally-stable.
-If its amplitude converges to some $A^2 < 0$ as before, then that mode is discarded and the iteration is repeated.
+If its amplitude converges to some $A^2 < 0$ as before, then that mode is discarded and the timestep is repeated.
 \section{Properties of Thermally Equilibrated States}\label{sec:properties}
@@
     \centering
-    \includegraphics[width=3.4in]{T_profs_na.pdf}
+    \includegraphics[width=3.375in]{T_profs_na.pdf}
     \caption{Mean temperature profiles $\overline{T}$ for $\Ra = 10^8$. 
     The initial profile is given by \eq{EQ:T0}. 
-    We evolve this background temperature profile according to section~\ref{sec:evolution} until we reach a marginally-stable thermal equilibrium (MSTE).
+    We evolve this background temperature profile according to Section~\ref{sec:evolution} until we reach a marginally-stable thermal equilibrium (MSTE).
     The DNS curve is obtained from a 2D nonlinear simulation of \eqss{EQ:motion1}{EQ:motion3} with \texttt{Dedalus}.
@@
 
-Figure~\ref{fig:T0_profiles} gives temperature profiles for $\Ra = 10^8$, where the initial profile is outlined in appendix~\ref{sec:initial_profile}. 
+Figure~\ref{fig:T0_profiles} gives temperature profiles for $\Ra = 10^8$, where the initial profile is outlined in Appendix~\ref{sec:initial_profile}. 
 We ran a direct numerical simulation (DNS) of \eqss{EQ:motion1}{EQ:motion3} with \texttt{Dedalus}, and also plot the horizontal- and time- averaged temperature profile. 
@@
     \begin{tabular}{@{}c@{}}
-        \includegraphics[width=3.4in]{flux_sup_n.pdf}
+        \includegraphics[width=3.375in]{flux_sup_n.pdf}
     \end{tabular}
     \begin{tabular}{@{}c@{}}
-        \includegraphics[width=3.4in]{EV_spectra_2ra.pdf}
+        \includegraphics[width=3.375in]{EV_spectra_2ra.pdf}
     \end{tabular}
@@
     \centering
-    \includegraphics[width=3.4in]{kx_m_ra1.pdf}
+    \includegraphics[width=3.375in]{kx_m_ra1.pdf}
     \caption{Wavenumbers of marginally-stable modes in thermally equilibrated states. 
@@
     \centering
-    \includegraphics[width=3.4in]{del_kx_inv.pdf}
+    \includegraphics[width=3.375in]{del_kx_inv.pdf}
     \caption{For $\Ra \geq 10^6$, the maximum marginally-stable wavenumber (corresponding to the green x markers in Figure~\ref{fig:kx_marginals}) are inversely related to the boundary layer height $\delta$.
     $(\max \{ k_x \})^{-1}$ gives a minimum $x$ length scale for the perturbations, and consequently, the advection. 
-    For large $\Ra$, the boundary layers admit small scale features, requiring more vertical basis functions (higher resolution, see Appendix \ref{sec:tables} for specifications).
+    For large $\Ra$, the boundary layers admit small scale features, requiring more vertical basis functions (higher resolution, see Appendix~\ref{sec:tables} for specifications).
     The boundary layer width gives an estimate of the minimum vertical length-scale in the problem.
@@
     \centering
-    \includegraphics[width=3.4in]{del_ra.pdf}
+    \includegraphics[width=3.375in]{del_ra.pdf}
     \caption{Boundary layer height $\delta$ of MSTE. 
@@
     \centering
-    \includegraphics[width=3.4in]{b0_delta_solid.pdf}
+    \includegraphics[width=3.375in]{b0_delta_solid.pdf}
     \caption{Temperature boundary layer geometries of various MSTE. 
@@
     \centering
-    \includegraphics[width=7.1in]{nu_ra.pdf}
+    \includegraphics[width=6.75in]{nu_ra.pdf}
     \caption{Nusselt numbers are shown for MSTE, aspect-ratio-optimized ``steady rolls'' ECS \cite{Wen}, as well as statistically-steady 2D and 3D DNS \cite{Johnston, Scheel_2016}.
@@
     \centering
-    \includegraphics[width=3.4in]{sim_eq_nu_noflow.pdf}
+    \includegraphics[width=3.375in]{sim_eq_nu_noflow.pdf}
     \caption{Nusselt numbers of simulations performed at $\Ra = 10^8$, initialized with the conductive equilibrium plus thermal noise (black), the MSTE (blue), and the MSTE absent initial flow (green).
@@
     \centering
-    \includegraphics[width=3.4in]{sim_eq_ke_noflow.pdf}
+    \includegraphics[width=3.375in]{sim_eq_ke_noflow.pdf}
     \caption{Average kinetic energies are reported for the same simulations illustrated in Figure~\ref{fig:nu_sim} ($\Ra = 10^8$). 
@@
 The authors thank Geoff Vasil, Greg Chini, Kyle Augustson, and Emma Kaufman for their valuable feedback and suggestions.
-We would also like to thank Charlie Doering and Baole Wen for the tabulated DNS and ECS data for figure~\ref{fig:nu_vs_ra}.
+We would also like to thank Charlie Doering and Baole Wen for the tabulated DNS and ECS data for Figure~\ref{fig:nu_vs_ra}.
 We thank the \texttt{Dedalus} and \texttt{Eigentools} development teams. 
@@
 Though the eigenfunctions are in general complex, the linear system \eqss{EQ:linear1}{EQ:linear3} obeys phase-shift symmetry.
-Any set of solutions can be phase-shifted by multiplying the perturbations by an arbitrary complex quantity $e^{i\phi}$.
+Any set of solutions can be phase-shifted by multiplying the perturbations by a complex quantity of unit modulus $e^{i\phi}$.
 In this particular case, we can eliminate the perturbations' imaginary components by selecting the proper $\phi$.
@@
 For the large-scale $k_x = 1.5\pi$ mode, we find the vertical velocity eigenfunction $W$ is maximized near the center of the domain.
-As $k_x$ increases, the vertical velocity is becomes more localized to the boundaries.
+As $k_x$ increases, we observe two vertical velocity maxima, each tending towards their respective boundary.
 However, in all cases, the temperature perturbations are more concentrated at the boundaries than the vertical velocity.
@@
     \centering
-    \includegraphics[width=7.1in]{grid_vars.pdf}
+    \includegraphics[width=6.75in]{grid_vars.pdf}
     \caption{The temperature and pressure MSTE eigenfunctions are shown in separate plots for various marginally-stable modes. 
@@
     We select a phase such that the eigenfunctions are real.
+    In this case the eigenfunctions are even which we exploit by plotting over half the domain.
     }%

### 2021-05-27 plot_flux.py
enumerate subfigs

@@ -79,6 +79,7 @@ def plot_flux(Rayleigh, ax, path, iteration):
         # plt.title('Heat Flux')
         ax.set_xlabel(r'$z$')
         ax.set_ylabel('Flux')
+        ax.annotate('(C)', xy=(-0.2, 1.1), xycoords='axes fraction', fontsize = plt.rcParams['font.size'] * 1.5)
     
     elif ('kx' in data.keys()):
         b0z = domain.new_field()
@@ -104,6 +105,7 @@ def plot_flux(Rayleigh, ax, path, iteration):
         # plt.title('Heat Flux (Iteration ' + str(self.iteration) + ')')
         # plt.savefig(self.iteration_path + '/figures' + '/Iteration' + str(self.iteration) + '_flux.png')
         # plt.close()
+        ax.annotate('(A)', xy=(-0.2, 1.1), xycoords='axes fraction', fontsize = plt.rcParams['font.size'] * 1.5)
     try:
         flux_avg = np.mean(flux)
         flux_const_dev = np.mean(np.abs(flux - flux_avg))

### 2021-05-27 plot_spectra_2ra.py

@@ -62,6 +62,12 @@ def plot_EVs(evs_mat, labels):
         ax.set_xlabel(r'$k_x$')
         ax.set_ylabel(r'$\sigma$')
         ax.yaxis.set_major_formatter(FormatStrFormatter('%.4f'))
+        if (i == 0):
+            ax.annotate('(B)', xy=(-0.2, 1.1), xycoords='axes fraction', fontsize = plt.rcParams['font.size'] * 1.5)
+        elif (i == 1):
+            ax.annotate('(D)', xy=(-0.2, 1.1), xycoords='axes fraction', fontsize = plt.rcParams['font.size'] * 1.5)
+        else:
+            raise Exception("index out of range")
 
     plt.tight_layout()
     # plt.title(r'Growth Rates: $Ra = 2e9$')

### 2021-05-27 publication_materials/ms_rbc.tex
amplitude equation arguments

@@
 %thereby alleviating any ambiguity in $A(t)$. 
-Substituting \eq{EQ:reynolds_dc_T} into \eq{EQ:motion3} and taking the horizontal-average reduces the system to a simple initial value problem (IVP) for $\overline{T}$
+Substituting \eq{EQ:reynolds_dc_T} into \eq{EQ:motion3} and taking the horizontal-average reduces the system to a simple initial value problem for $\overline{T}$
 \begin{equation}
@@
 with associated boundary conditions $\overline{T}(-1/2, t) = 1/2$ and $\overline{T}(1/2, t) = -1/2$.
-It should be noted that we could obtain a similar IVP for $u$ by breaking reflection symmetry about the midplane $z = 0$ and considering some nontrivial mean horizontal flow $\overline{u}(z, t)$.
+It should be noted that we could obtain a similar equation for $u$ by breaking reflection symmetry about the midplane $z = 0$ and considering some nontrivial mean horizontal flow $\overline{u}(z, t)$.
 However we must have $\overline{w}(z, t) = 0$ due to incompressibility.
@@
 where $\langle \cdot \rangle_{\mathcal{D}}$ denotes the spatial mean over the entire domain.
+Crucially, we emphasize that  \eqs{EQ:normal_modes1}{EQ:normal_modes3} are solutions to the linear problem.
+In the quasilinear context, the background state and its eigenmodes vary in time.
+By convention, our notation neglects this $t$-dependence in the eigenfunctions as they will always computed from the autonomous linear system.
 
@@
 We use a second-order, two-stage IMEX Runge-Kutta method.
-The eigenfunctions and amplitudes are assumed to be constant over the timestep.
+The eigenfunctions and amplitudes are assumed to be constant with respect to $t$ over the timestep.
 We symmetrize $\overline{T}$ by setting the coefficients of its even Chebyshev basis functions to zero at the start of each timestep.
@@
 The amplitude $A$ must be selected such that these two influences are equal and opposite.
-We can measure the effects of diffusion and advection on the maximum eigenvalue by solving two new IVPs
+We can measure the effects of diffusion and advection on the maximum eigenvalue by solving two new initial value problems
 \begin{align}\label{eqn:diffusion_only}
     &\frac{\partial \overline{T}_{\rm{diff}}}{\partial t} = \mathcal{P} \frac{\partial^2 \overline{T}_{\rm{diff}}}{\partial z^2} \\
-    &\frac{\partial \overline{T}_{\rm{adv}}}{\partial t} + \frac{\partial}{\partial z} \langle w'T' \rangle_x = 0 
+    &\frac{\partial \overline{T}_{\rm{adv}}}{\partial t} + \frac{\partial}{\partial z} \Re\left[ W \theta^* \right] = 0 \label{eqn:advection_only}
 \end{align}
-where $\overline{T}_{\rm{diff}}$ and $\overline{T}_{\rm{adv}}$ denote the diffused and advected temperature profiles.
-We initialize $\overline{T}_{\rm{diff}}$ and $\overline{T}_{\rm{adv}}$ with $\overline{T}(z, t_0)$, and evolve the equations to $t=t_0+\Delta t$.
+where $\overline{T}_{\rm{diff}}$ and $\overline{T}_{\rm{adv}}$ denote the diffused and advected temperature profiles respectively. 
+The advective term must be defined in this way because we do not yet know its amplitude $A^2$. 
+In the original problem \eq{EQ:T0_IVP}, evolution due to advection is proportional to $A^2$.
+That is not the case in \eq{eqn:advection_only}.
+
+To approximate $A^2$, we assume the system is in a state of near-equilibrium, evolving on a slow time scale relative to diffusion or advection individually. 
+If we initialize both \eqs{eqn:diffusion_only}{eqn:advection_only} with a marginally-stable\footnote[3]{Note that marginal stability differs from equilibrium in this quasilinear context because a marginally-stable state need not satisfy $\frac{\partial \overline{T}}{\partial t} = 0$.} temperature profile $\overline{T}$, the evolution of the background state due to diffusion must be approximately opposite the evolution due to advection on the fast time scale, i.e.
+\begin{align}
+    \overline{T}_{\rm{diff}} - \overline{T} &\approx -A^2(\overline{T}_{\rm{adv}} - \overline{T})
+\end{align}
+where the $A^2$ factor is meant to reconcile the different advective terms in \eqs{EQ:T0_IVP}{eqn:advection_only}.
+
+This approximation is valid in equilibrium, but in general, we would obtain undesired $z$-dependence in $A^2$.
+Though we might be tempted to take a norm, the best way to account for this $z$-dependence, is to make an analogous argument with respect to the growth rates
+\begin{align}
+    \sigma_{\rm{diff}} - \sigma &\approx -A^2(\sigma_{\rm{adv}} - \sigma).
+\end{align}
+where $\sigma_{\rm{diff}}$ and $\sigma_{\rm{adv}}$ are the growth rates computed from $\overline{T}_{\rm{diff}}$ and $\overline{T}_{\rm{adv}}$ respectively.
+$\sigma$ vanishes due to marginal stability.
+Later we will see that this approach can be easily generalized to account for multiple simultaneously marginal modes.
+
+In practice, we initialize $\overline{T}_{\rm{diff}}$ and $\overline{T}_{\rm{adv}}$ with $\overline{T}(z, t_0)$, and evolve the equations to $t=t_0+\Delta t$.
 Suppose $k_0$ is the wavenumber of the marginally-stable mode.
-Then, using the diffused and advected profiles, we compute the eigenvalues $\sigma_{\rm{diff}}$ and $\sigma_{\rm{adv}}$ at $k_x = k_0$ and $t=t_0+\Delta t$.
+Then we compute $\sigma_{\rm{diff}}$ and $\sigma_{\rm{adv}}$ at $k_x = k_0$ and $t=t_0+\Delta t$.
 A preliminary approximation $\Lambda^2_0$ of the appropriate amplitude $A^2$ is given by
@@
 We use Newton's method to find an amplitude $A^2$ such that the maximum growth rate is zero to within $10^{-9}$.
-Marginally-stable modes do not oscillate in time, i.e. $\sigma = 0$ implies $\omega = 0$.
+Marginally-stable modes do not oscillate in time, i.e.~$\sigma = 0$ implies $\omega = 0$.
 This agrees with the conventional notion of exchange of stabilities \cite{drazin_reid_2004}.

### 2021-05-27 publication_materials/ms_rbc.tex
timeout

@@
 This approximation is valid in equilibrium, but in general, we would obtain undesired $z$-dependence in $A^2$.
-Though we might be tempted to take a norm, the best way to account for this $z$-dependence, is to make an analogous argument with respect to the growth rates
+Though we might be tempted to take a norm, the best way to account for this $z$-dependence, is to make an analogous argument with the growth rates
 \begin{align}
@@
 \end{align}
-where $\sigma_{\rm{diff}}$ and $\sigma_{\rm{adv}}$ are the growth rates computed from $\overline{T}_{\rm{diff}}$ and $\overline{T}_{\rm{adv}}$ respectively.
+where $\sigma_{\rm{diff}}$ and $\sigma_{\rm{adv}}$ are computed from $\overline{T}_{\rm{diff}}$ and $\overline{T}_{\rm{adv}}$ respectively.
 $\sigma$ vanishes due to marginal stability.
@@
 
-In practice, we initialize $\overline{T}_{\rm{diff}}$ and $\overline{T}_{\rm{adv}}$ with $\overline{T}(z, t_0)$, and evolve the equations to $t=t_0+\Delta t$.
+In practice, we initialize $\overline{T}_{\rm{diff}}$ and $\overline{T}_{\rm{adv}}$ at $t = t_0$, and evolve the equations to $t=t_0+\Delta t$.
 Suppose $k_0$ is the wavenumber of the marginally-stable mode.

### 2021-05-28 publication_materials/ms_rbc.tex
Fiddled with discussion around eqn 25.

@@
 By definition, its maximum growth rate is 0.
-Diffusing $\overline{T}(z, t_0)$ tends to increase its growth rates while ignoring the diffusive term and evolving according to advection tends to decrease its growth rates.
+Diffusing $\overline{T}(z, t_0)$ tends to increase its growth rates while ignoring the diffusive term and evolving according to advection tends to decrease its growth rates (see Figure~\ref{fig:iteration_spectra}).
 The amplitude $A$ must be selected such that these two influences are equal and opposite.
@@
 where $\overline{T}_{\rm{diff}}$ and $\overline{T}_{\rm{adv}}$ denote the diffused and advected temperature profiles respectively. 
-The advective term must be defined in this way because we do not yet know its amplitude $A^2$. 
-In the original problem \eq{EQ:T0_IVP}, evolution due to advection is proportional to $A^2$.
-That is not the case in \eq{eqn:advection_only}.
+In equation~\ref{eqn:advection_only} we have set the amplitude of the eigenfunctions $A=1$ so we can determine how advection changes the temperature profiles.
 
-To approximate $A^2$, we assume the system is in a state of near-equilibrium, evolving on a slow time scale relative to diffusion or advection individually. 
-If we initialize both \eqs{eqn:diffusion_only}{eqn:advection_only} with a marginally-stable\footnote[3]{Note that marginal stability differs from equilibrium in this quasilinear context because a marginally-stable state need not satisfy $\frac{\partial \overline{T}}{\partial t} = 0$.} temperature profile $\overline{T}$, the evolution of the background state due to diffusion must be approximately opposite the evolution due to advection on the fast time scale, i.e.
-\begin{align}
-    \overline{T}_{\rm{diff}} - \overline{T} &\approx -A^2(\overline{T}_{\rm{adv}} - \overline{T})
-\end{align}
-where the $A^2$ factor is meant to reconcile the different advective terms in \eqs{EQ:T0_IVP}{eqn:advection_only}.
-
-This approximation is valid in equilibrium, but in general, we would obtain undesired $z$-dependence in $A^2$.
-Though we might be tempted to take a norm, the best way to account for this $z$-dependence, is to make an analogous argument with the growth rates
-\begin{align}
-    \sigma_{\rm{diff}} - \sigma &\approx -A^2(\sigma_{\rm{adv}} - \sigma).
-\end{align}
-where $\sigma_{\rm{diff}}$ and $\sigma_{\rm{adv}}$ are computed from $\overline{T}_{\rm{diff}}$ and $\overline{T}_{\rm{adv}}$ respectively.
-$\sigma$ vanishes due to marginal stability.
-Later we will see that this approach can be easily generalized to account for multiple simultaneously marginal modes.
-
-In practice, we initialize $\overline{T}_{\rm{diff}}$ and $\overline{T}_{\rm{adv}}$ at $t = t_0$, and evolve the equations to $t=t_0+\Delta t$.
+We solve equations \eqs{eqn:diffusion_only}{eqn:advection_only} from $t=t_0$ to $t=t_0+\Delta t$, initializing each temperature profile with $\overline{T}(z, t_0)$.
 Suppose $k_0$ is the wavenumber of the marginally-stable mode.
-Then we compute $\sigma_{\rm{diff}}$ and $\sigma_{\rm{adv}}$ at $k_x = k_0$ and $t=t_0+\Delta t$.
-A preliminary approximation $\Lambda^2_0$ of the appropriate amplitude $A^2$ is given by
+We then calculate the largest eigenvalues for the $\overline{T}_{\rm{diff}}$ and $\overline{T}_{\rm{adv}}$ profiles, $\sigma_{\rm{diff}}$ and $\sigma_{\rm{adv}}$.
+A good guess for $A^2$ is
 \begin{equation}
-    A^2 \approx \Lambda^2_0 \equiv -\frac{\sigma_{\rm{diff}}}{\sigma_{\rm{adv}}} \label{EQ:amp_approx}
+    A^2 \approx \Lambda^2_0 \equiv -\frac{\sigma_{\rm{diff}}}{\sigma_{\rm{adv}}}. \label{EQ:amp_approx}
 \end{equation}
-where the square in $A^2$ and $\Lambda^2_0$ is due to the quadratic nonlinearity of the eigenfunctions in the advective term and the minus sign is due to the fact that $\sigma_{\rm{adv}} < 0$ and $\sigma_{\rm{diff}} > 0$ in general.
-We illustrate these trends in Figure~\ref{fig:iteration_spectra}. 
-The subscript 0 denotes a preliminary estimate which we later refine.
-In general, when $\Lambda^2_0 > 0$, the root-finding algorithm is stable.
-The alternative can occur when the timestep approaches machine precision, in which case $\sigma_{\rm{diff}}$ and $\sigma_{\rm{adv}}$ are subject to floating point errors of comparable order to themselves.
+This estimate follows from first-order perturbation theory.
+Note that $\sigma_{\rm{adv}} < 0$ and $\sigma_{\rm{diff}} > 0$, so $\Lambda_0^2>0$.
 
@@
 This background temperature is typically close to, but not exactly, marginally stable.
+In fact, in the limit $\Delta t \rightarrow 0$, the estimate $\Lambda_0^2$ approaches the amplitude $A^2$ necessary to keep the background temperature marginally stable \cite{Chini_ql}.
 We use Newton's method to find an amplitude $A^2$ such that the maximum growth rate is zero to within $10^{-9}$.

### 2021-05-28 publication_materials/ms_rbc.tex
Time evolution.
Intro.

@@
 Although the quasilinear approximation greatly simplifies the problem, an additional condition must be imposed to determine the amplitude of the perturbations.
-In \citet{Beaume_2015}, researchers compute ECS in parallel shear flows by deriving and solving a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments. 
+The simplest approach is to initialize the perturbations to low amplitude, and evolve them together with the background (this is, e.g., the approach of \cite{marston2016} and many others).
+A different approach was taken in \citet{Beaume_2015}, which computes ECS in parallel shear flows by deriving and solving a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments.
 They assume the background velocity evolves on a slow time scale, and, to determine the perturbation amplitudes, they require marginal stability at each timestep.
@@
 
-In this paper we employ the same strategy to the more complicated Rayleigh-B\'{e}nard convection problem.
+In this paper we employ this strategy for the Rayleigh-B\'{e}nard convection problem.
 In Section~\ref{sec:model} we recall the underlying equations, and in Section~\ref{sec:evolution} we outline how we evolve the background temperature profile while maintaining marginal stability.
@@
 To initialize our calculations, we construct a marginally-stable initial temperature profile $\overline{T}(z, t=0)$ whose equation is given in Appendix~\ref{sec:initial_profile}. 
+Although this background temperature is marginally-stable, it is not in thermal equilibrium, so it will evolve in time.
 We use \eq{EQ:T0_IVP} to evolve $\overline{T}(z, t_0)$ into a new marginally-stable profile $\overline{T}(z, t_0 + \Delta t)$.

### 2021-05-28 publication_materials/ms_rbc.tex
final edits

@@
     Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important properties remain elusive.
-    To study convection in a novel context, we derive and solve a quasilinear form of the Rayleigh-Bénard problem by representing the perturbations in terms of marginally stable eigenmodes.
+    To study convection in a novel context, we derive and solve a quasilinear form of the Rayleigh-Bénard problem by representing the perturbations in terms of marginally-stable eigenmodes.
     The amplitude of each eigenmode is determined by requiring that the background state maintains marginal stability.
@@
     When an MSTE is used as initial conditions for a 2D simulation, we find that Nu quickly equilibrates without the burst of turbulence often induced by purely conductive initial conditions, but we also find that the kinetic energy is too large and viscously attenuates on a long viscous time scale.
-    This is due to the thin temperature boundary layers which diffuse heat more effectively, thereby requiring high-velocity advective flows to reach an equilibrium.
+    This is due to the thin temperature boundary layers which diffuse heat very effectively, thereby requiring high-velocity advective flows to reach an equilibrium.
 \end{abstract}
@@
 Although the quasilinear approximation greatly simplifies the problem, an additional condition must be imposed to determine the amplitude of the perturbations.
-The simplest approach is to initialize the perturbations to low amplitude, and evolve them together with the background (this is, e.g., the approach of \cite{marston2016} and many others).
+The simplest approach is to initialize the perturbations to low amplitude, and evolve them together with the background (this is, e.g., the approach of \citet{marston2016} and many others).
 A different approach was taken in \citet{Beaume_2015}, which computes ECS in parallel shear flows by deriving and solving a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments.
@@
 The fluid of interest is constrained between two flat boundaries at $z = -1/2$ and $z = 1/2$ with fixed temperatures $1/2$ and $-1/2$ respectively. 
-At both boundaries we specify impenetrable, no-slip conditions, such that the velocity $\vec{u} = u \hat{x} + w \hat{z} = \vec{0}$ at $z = \pm 1/2$, where $\hat{x}, \hat{z}$ are the unit vectors in the $x$ and $z$ directions.
+At both boundaries we specify impenetrable, no-slip conditions, such that the velocity $\vec{u} = u \hat{x} + w \hat{z} = \vec{0}$ at $z = \pm 1/2$, where $\hat{x}$ and $\hat{z}$ are the unit vectors in the $x$ and $z$ directions.
 The equations of motion are then given by
@@
 
-To derive the quasilinear form, we posit that an arbitrary field $f$ can be represented as the sum of a mean profile (denoted by $\overline{f}$) and a perturbation function (denoted by $f'$).
+To derive the quasilinear form, we posit that an arbitrary field $f$ can be represented as the sum of a mean profile (denoted by $\overline{f}$) and a perturbation function (denoted by $f'$)
 \begin{align}
@@
     T(x, z, t) &= \overline{T}(z, t) + T'(x, z, t) \label{EQ:reynolds_dc_T}\\
-    p(x, z, t) &= \overline{p}(z, t) +  p'(x, z, t) \label{EQ:reynolds_dc_p}.
+    p(x, z, t) &= \overline{p}(z, t) +  p'(x, z, t) \label{EQ:reynolds_dc_p}
 \end{align}
@@
 
-Substituting \eq{EQ:reynolds_dc_p} into \eq{EQ:motion2} and taking the horizontal average reveals that the mean pressure field $\overline{p}(z, \, t)$ must satisfy
+Substituting \eq{EQ:reynolds_dc_p} into \eq{EQ:motion2} and taking the horizontal average reveals that the mean pressure field $\overline{p}(z, t)$ must satisfy
 \begin{equation}
@@
 Here we will make the quasilinear approximation, dropping the $\vec{u}'\vec{\cdot}\vec{\nabla}\vec{u}'$ and $\vec{u}'\vec{\cdot}\vec{\nabla}T'$ terms from the evolution equations for the perturbations.
-Substituting \eqss{EQ:reynolds_dc_u}{EQ:reynolds_dc_p} into \eqss{EQ:motion1}{EQ:motion3} followed by subtracting \eqs{EQ:T0_IVP}{EQ:p_bar} from the resulting temperature and $\hat{z}$ momentum equations gives
+Substituting \eqss{EQ:reynolds_dc_u}{EQ:reynolds_dc_p} into \eqss{EQ:motion1}{EQ:motion3} followed by subtracting \eqs{EQ:T0_IVP}{EQ:p_bar} from the resulting temperature and $\hat{z}$ momentum equations respectively gives
 \begin{align}
@@
 \begin{align}
-    w'(x, z, t) &= A\, \Re\left[W(z) \, e^{i(k_xx-st)}\right], \label{EQ:normal_modes1}\\ 
-    u'(x, z, t) &= A\, \Re\left[U(z) \, e^{i(k_xx-st)}\right], \label{EQ:normal_modes2}\\ 
-    T'(x, z, t) &= A\, \Re\left[\theta(z) \, e^{i(k_xx-st)}\right], \label{EQ:normal_modes3}\\ 
-    p'(x, z, t) &= A\, \Re\left[P(z) \, e^{i(k_xx-st)}\right], \label{EQ:normal_modes4}
+    w'(x, z, t) &= A\, \Re\left[W(z) \, e^{i(k_xx-st)}\right] \label{EQ:normal_modes1}\\ 
+    u'(x, z, t) &= A\, \Re\left[U(z) \, e^{i(k_xx-st)}\right] \label{EQ:normal_modes2}\\ 
+    T'(x, z, t) &= A\, \Re\left[\theta(z) \, e^{i(k_xx-st)}\right] \label{EQ:normal_modes3}\\ 
+    p'(x, z, t) &= A\, \Re\left[P(z) \, e^{i(k_xx-st)}\right] \label{EQ:normal_modes4}
 \end{align}
@@
 In the quasilinear context, the background state and its eigenmodes vary in time.
-By convention, our notation neglects this $t$-dependence in the eigenfunctions as they will always computed from the autonomous linear system.
+By convention, our notation neglects this $t$-dependence in the eigenfunctions as they will always be computed from the autonomous linear system.
 
@@
 
-To calculate the advective heat flux in equation~\ref{EQ:T0_IVP}, we can sum the individual advective terms $\langle w'T' \rangle_x$ of every marginally stable mode.
+To calculate the advective heat flux in equation~\ref{EQ:T0_IVP}, we can sum the individual advective terms $\langle w'T' \rangle_x$ of every marginally-stable mode.
 In this way, the heat flux from the perturbations influence the evolution of $\overline{T}$.
@@
 Unstable modes $(\sigma > 0)$ will not persist on the slow time scale because the advective term $\langle w'T' \rangle_x$ tends to stabilize $\overline{T}$, thereby creating a negative feedback loop.
-Only marginally stable modes can be maintained on the slow time scale.
+Only marginally-stable modes can be maintained on the slow time scale.
 Therefore the amplitude $A$ must satisfy
@@
 For various $\Ra$ and fixed $\Pr = 1$, we seek marginally-stable thermal equilibria (MSTE) satisfying $\frac{\partial \overline{T}}{\partial t} = 0$ according to \eq{EQ:T0_IVP}. 
-We employ the \texttt{Dedalus} pseudo-spectral python framework\footnotemark[1] \cite{Dedalus_2020} to solve the eigenvalue problem outlined in Section~\ref{sec:model} as well as the time evolution equation \eq{EQ:T0_IVP}.
+We employ the \texttt{Dedalus} pseudo-spectral python framework\footnotemark[1] \cite{Dedalus_2020} to solve the eigenvalue problem outlined in Section~\ref{sec:model} as well as the time evolution equation~\ref{EQ:T0_IVP}.
 We represent each field with Chebyshev polynomials and use the 3/2 dealiasing rule to calculate the advective heat flux.
@@
 This ensures $\overline{T}(z) = -\overline{T}(-z)$.
-On every timestep, we calculate the marginally stable eigenfunctions and their amplitude $A$.
+On every timestep, we calculate the marginally-stable eigenfunctions and their amplitude $A$.
 It is essential that we pick the correct eigenfunction amplitude when calculating the advective term to maintain marginal stability.
@@
     \caption{Eigenvalue spectra for $\Ra = 10^5$. The spectrum of an ``initial" marginally-stable mean temperature profile $\overline{T}(z, t_0)$ has a maximum eigenvalue of 0. 
-    Given a small fixed timestep $\Delta t$, diffusion destabilizes the system, increasing $\sigma$. 
-    Advection tends to stabilize the system, decreasing $\sigma$. 
+    Given a small fixed timestep $\Delta t$, diffusion (equation~\ref{eqn:diffusion_only}) destabilizes the system, increasing $\sigma$. 
+    Advection (equation~\ref{eqn:advection_only}) tends to stabilize the system, decreasing $\sigma$. 
     We find the eigenfunction amplitude $A^2$ such that the combination of diffusion and advection yields a new, ``evolved,'' marginally-stable mean temperature profile $\overline{T}(z, t_0 + \Delta t)$.
@@
 The amplitude $A$ must be selected such that these two influences are equal and opposite.
-We can measure the effects of diffusion and advection on the maximum eigenvalue by solving two new initial value problems
+We can measure the effects of diffusion and advection on the maximum growth rate by solving two new initial value problems
 \begin{align}\label{eqn:diffusion_only}
     &\frac{\partial \overline{T}_{\rm{diff}}}{\partial t} = \mathcal{P} \frac{\partial^2 \overline{T}_{\rm{diff}}}{\partial z^2} \\
-    &\frac{\partial \overline{T}_{\rm{adv}}}{\partial t} + \frac{\partial}{\partial z} \Re\left[ W \theta^* \right] = 0 \label{eqn:advection_only}
+    &\frac{\partial \overline{T}_{\rm{adv}}}{\partial t} + 2\frac{\partial}{\partial z} \Re\left[ W \theta^* \right] = 0 \label{eqn:advection_only}
 \end{align}
@@
 In equation~\ref{eqn:advection_only} we have set the amplitude of the eigenfunctions $A=1$ so we can determine how advection changes the temperature profiles.
+The factor of 2 arises due to the horizontal averaging of the advective term in \eq{EQ:T0_IVP}.
 
@@
 Suppose $k_0$ is the wavenumber of the marginally-stable mode.
-We then calculate the largest eigenvalues for the $\overline{T}_{\rm{diff}}$ and $\overline{T}_{\rm{adv}}$ profiles, $\sigma_{\rm{diff}}$ and $\sigma_{\rm{adv}}$.
+We then calculate the $k_x = k_0$ mode's growth rates $\sigma_{\rm{diff}}$ and $\sigma_{\rm{adv}}$ for $\overline{T}_{\rm{diff}}$ and $\overline{T}_{\rm{adv}}$.
 A good guess for $A^2$ is
@@
 Using the approximate amplitude $\Lambda_0^2$, the background temperature $\overline{T}(z, t_0)$ is then evolved to $t=t_0+\Delta t$ according to \eq{EQ:T0_IVP} and another eigenvalue solve is performed.
-This background temperature is typically close to, but not exactly, marginally stable.
-In fact, in the limit $\Delta t \rightarrow 0$, the estimate $\Lambda_0^2$ approaches the amplitude $A^2$ necessary to keep the background temperature marginally stable \cite{Chini_ql}.
+This background temperature is typically close to, but not exactly, marginally-stable.
+In fact, in the limit $\Delta t \rightarrow 0$, the estimate $\Lambda_0^2$ approaches the amplitude $A^2$ necessary to keep the background temperature marginally-stable \cite{Chini_ql}.
 We use Newton's method to find an amplitude $A^2$ such that the maximum growth rate is zero to within $10^{-9}$.
@@
 \end{equation}
-where $W_n$ and $\theta_n$ are the marginally stable eigenmodes associated with different values of $k_x$. 
-The factor of 2 is due to horizontal averaging.
+where $W_n$ and $\theta_n$ are the marginally-stable eigenmodes associated with different values of $k_x$. 
+The factor of 2 is again due to horizontal averaging.
 There are now $N$ modes, each with their own amplitude to solve for and eigenvalue to keep marginally-stable. 
 Given a small fixed time step $\Delta t$, let $\vec{A^2}$ be the amplitude vector and $\vec{\sigma}(\vec{A^2})$ be the eigenvalues of the $N$ modes.
-We are searching for $\vec{\tilde{A}^2}$ that satisfies of $\vec{\sigma}(\vec{\tilde{A}^2})=0$.
+We are searching for $\vec{\tilde{A}^2}$ that satisfies $\vec{\sigma}(\vec{\tilde{A}^2})=0$.
 We approximate the amplitudes with $\vec{\Lambda^2_0}$ by generalizing \eq{EQ:amp_approx}:
@@
 
-Our estimate $\vec{\Lambda^2_0}$ does not typically give a background temperature for which all $N$ modes are exactly marginally stable.
+Our estimate $\vec{\Lambda^2_0}$ does not typically give a background temperature for which all $N$ modes are exactly marginally-stable.
 We refine our vector of amplitudes via Newton's method.
@@
 %We then use each subsequent guess to adjust the Jacobian via Broyden's method for root-finding in multi-dimensional functions \cite{Broyden}.
-We iterate Newton's method until all marginally stable modes have eigenvalues within $10^{-9}$ of zero.
+We iterate Newton's method until all marginally-stable modes have eigenvalues within $10^{-9}$ of zero.
 We find $\vec{\sigma}(\vec{A^2})$ does indeed have a unique root provided the time step is not too large and there are no numerical instabilities, as outlined in Appendix~\ref{sec:timestep}.
@@
 We evolve $\overline{T}$ as described above until $\max|\partial_{t}\overline{T}| < 10^{-5}$.
-In this marginally-stable thermal equilibrium, $\overline{T}$ does not evolve in time, and the perturbations also do not evolve in time, as they are marginally stable.
-Thus, these configurations are exact solutions to the quasilinear equations (equations~\ref{EQ:T0_IVP}--\ref{EQ:linear3}).
+In this marginally-stable thermal equilibrium, $\overline{T}$ does not evolve in time, and the perturbations also do not evolve in time, as they are marginally-stable.
+Thus, these configurations are exact solutions to the quasilinear system (equations~\ref{EQ:T0_IVP}--\ref{EQ:linear3}).
 They differ from the usual ECS in that ECS are fixed points of the full nonlinear problem \eqss{EQ:motion1}{EQ:motion3}. 
@@
 Figure~\ref{fig:T0_profiles} gives temperature profiles for $\Ra = 10^8$, where the initial profile is outlined in Appendix~\ref{sec:initial_profile}. 
-We ran a direct numerical simulation (DNS) of \eqss{EQ:motion1}{EQ:motion3} with \texttt{Dedalus}, and also plot the horizontal- and time- averaged temperature profile. 
+We run a direct numerical simulation (DNS) of \eqss{EQ:motion1}{EQ:motion3} with \texttt{Dedalus} and plot the horizontal- and time- averaged temperature profile. 
 The temperature boundary layers in the DNS are wider than in the MSTE, which is in turn wider than the boundary layer of the initial temperature profile.
@@
 Every marginally-stable initial profile we experiment with ($\tanh$, $\rm{erf}$) has thinner boundary layers than the DNS and MSTE profiles.
-In conjunction, these two facts suggest that MSTE maximize boundary layer thickness, subject to the marginal stability constraint.
+In conjunction, these two facts suggest that MSTE maximize boundary layer thickness while subject to the marginal stability constraint.
 
@@
     At large $\Ra$, high-wavenumber modes contribute pronounced small-scale advection profiles which tightly hug the thin boundary layers. 
-    A combination of of progressively wider advection profiles is necessary to transition to bulk advection provided by the $k_x = 1.5\pi$ mode. 
+    A combination of progressively wider advection profiles is necessary to transition to bulk advection provided by the $k_x = 1.5\pi$ mode. 
     This bulk mode mimics the large-scale convective cells which are characteristic of Rayleigh–Bénard convection, both in qualitative structure and number of cells in the domain.
@@
 Thin advection profiles, belonging to high-wavenumber modes with $k_x=23.5\pi, \, 24\pi$, hug the boundary layer. 
-Closer to the bulk of the domain, we see wider advection profiles corresponding to modes in a second group of marginal modes $k_x = 6\pi, \, 6.5\pi$.
-The $k_x = 1.5\pi$ mode forms the same arrangement and number of large-scale convective cells observed in DNS, again occupying the bulk of the domain.
+Closer to the bulk of the domain, we see wider advection profiles corresponding to modes in a second pair of marginal modes $k_x = 6\pi, \, 6.5\pi$.
+Adjacent pairs of marginal modes whose wavenumbers differ by $0.5\pi$ are common among MSTE.
+The isolated $k_x = 1.5\pi$ mode forms the same arrangement and number of large-scale convective cells observed in DNS, again occupying the bulk of the domain.
 The pairs of modes $k_x = 6\pi, \, 6.5\pi$ and $k_x=23.5\pi, \, 24\pi$ are each associated with a single maximum in our plots of growth rate $\sigma$ as a function of $k_x$ (lower right panel of Figure~\ref{fig:flux}).
@@
     For example, the spectrum corresponding to $\Ra = 10^5$ has adjacent marginal wavenumbers $k_x = \pi, \, 1.5\pi$. 
-    The $\Ra = 10^9$ spectrum, shown in lower right corner of Figure~\ref{fig:flux}, has three groups of maxima, with a single marginal mode in the first group ($k_x = 1.5\pi$), two adjacent marginal modes in the second group ($k_x = 6\pi, \, 6.5\pi$), and two adjacent marginal modes in the third group ($k_x = 23.5\pi, \, 24\pi$).
+    The $\Ra = 10^9$ spectrum, shown in the lower right corner of Figure~\ref{fig:flux}, has three groups of maxima, with a single marginal mode in the first group ($k_x = 1.5\pi$), two adjacent marginal modes in the second group ($k_x = 6\pi, \, 6.5\pi$), and two adjacent marginal modes in the third group ($k_x = 23.5\pi, \, 24\pi$).
     The largest wavenumbers of the green and blue branches depend on  $\Ra$ according to power laws.
@@
 In Figure~\ref{fig:kx_marginals} we give the wavenumbers $k_x$ of marginal modes. 
-For some values of $\Ra$ we obtain states with pairs of marginally-stable modes, with wavenumbers separated by $\pi/2$.
+Adjacent pairs of marginal modes are common but not ubiquitous.
 Like $k_x = 6\pi, \, 6.5\pi$ and $k_x=23.5\pi, \, 24\pi$ for the $\Ra=10^9$ MSTE, these are due to the discretization of wavenumbers from our domain of width 4.
@@
 Least-squares regression gives $\max\{k_x\} \propto \Ra^{0.300}$ with $R^2 = 0.998$ for this maximum branch.
-For large $\Ra$, the advective fluxes of this maximum branch compensates for the strongly peaked diffusive flux in the thin boundary layers. 
+For large $\Ra$, the advective fluxes of this maximum branch compensate for the strongly peaked diffusive flux in the thin boundary layers. 
 At $\Ra \geq 10^8$, a third branch appears (shown in blue), splitting the widening gap between the other two. 
@@
     For large $\Ra$, the boundary layers admit small scale features, requiring more vertical basis functions (higher resolution, see Appendix~\ref{sec:tables} for specifications).
-    The boundary layer width gives an estimate of the minimum vertical length-scale in the problem.
-    This suggests that the minimum horizontal and vertical length-scales are proportional to each other over a wide range of $\Ra$.}
+    The boundary layer height gives an estimate of the minimum vertical length scale in the problem.
+    This suggests that the minimum horizontal and vertical length scales are proportional to each other over a wide range of $\Ra$.}
     \label{fig:del_inv}
@@
 
-The largest marginal wavenumber $\max \{ k_x \}$ (represented by the light green branch in Figure~\ref{fig:kx_marginals}) serves as an inverse minimum length-scale in the $x$ direction.
+The largest marginal wavenumber $\max \{ k_x \}$ (represented by the light green branch in Figure~\ref{fig:kx_marginals}) serves as an inverse minimum length scale in the $x$ direction.
 The finest vertical structures in $\overline{T}(z)$ appear near the boundaries, requiring more basis functions (resolution) at large $\Ra$.
-Naturally, this provides a complementary minimum length-scale for $z$.
-We define the boundary layer width $\delta$ as the distance from the boundary where $\partial_z T$ equals zero, i.e.,
+Naturally, this provides a complementary minimum length scale for $z$.
+We define the boundary layer height $\delta$ as the distance from the boundary where $\partial_z \overline{T}$ equals zero, i.e.,
 \begin{align}\label{eqn:delta}
@@
 We find the MSTE can be characterized by their boundary layer height.
-In Figure~\ref{fig:bl_ra}, we illustrate the scaling behavior of the boundary layer height $\delta = \Ra^{-1/3}$. 
+In Figure~\ref{fig:bl_ra}, we illustrate the scaling behavior of the boundary layer height $\delta \sim \Ra^{-1/3}$. 
 This is consistent with Malkus' classical marginal stability theory, a scaling argument which perceives the boundary regions as subdomains which are themselves marginally-stable \cite{Malkus_1954}.
@@
 In both cases, the $\Ra$ dependence appear slightly more shallow than for the MSTE.
-\cite{Wen} hypothesized that the $\Nu$ of all ECS which admit classical Malkus scaling must always exceed the $\Nu$ of turbulent convection.
+\Citet{Wen} hypothesized that the $\Nu$ of all ECS which admit classical Malkus scaling must always exceed the $\Nu$ of turbulent convection.
 If we generalize this notion to include quasilinear equilibria, our findings agree; MSTE have larger $\Nu$ than 2D and 3D DNS.
@@
 \end{align}
-where $\mathcal{N}$ is low-amplitude random noise.
+where $\mathcal{N}$ is low-amplitude random noise concentrated in the bulk of the domain.
 Here we instead initialize using the MSTE,
@@
 \end{align}
-where $\theta_n(z), U_n(z), W_n(z), P_n(z); \, A_n; $ and $k_{x_n}$ refer to the complex eigenfunctions, amplitude, and wavenumber of the $n$th marginal mode respectively. 
+where $\theta_n(z), \, U_n(z), \, W_n(z), \, P_n(z); \; A_n; $ and $k_{x_n}$ refer to the complex eigenfunctions, amplitude, and wavenumber of the $n$th marginal mode respectively. 
 Note that although the MSTE is an equilibrium of the quasilinear equations, it is not an equilibrium of the full nonlinear equations.
@@
 MSTE can be perceived as a set of initial conditions, designed for avoiding the simulation of transient high Reynolds number flows.
-MSTE absent velocity achieve the same goal but give way to seemingly-persistent oscillations in $\Nu$.
+MSTE absent velocity effectively achieve the same goal.
 
@@
 We also find that the average kinetic energy of the simulation initialized with MSTE is significantly larger than those found in either of the other cases, as shown Figure~\ref{fig:ke_sim}. 
-This is because the MSTE contain strong large-scale flows, which decay on a long viscous time scale $t_{\nu}$. 
+This is because MSTE contain strong large-scale high-velocity flows, which decay on a long viscous time scale $t_{\nu}$. 
+These powerful advective flows balance the heat flux in the bulk of the domain with the strong diffusion of thin MSTE temperature boundary layers.
 Fluid in the other cases is initialized at rest. 
 Two viscous time scales can be derived for this problem: one for the boundary layer 
-\begin{align*}
+\begin{align}
     t_{\nu,\delta} &= \frac{\delta^2}{\mathcal{P}} = 2.86
@@
     t_{\nu,L} &= \frac{L^2_z}{\mathcal{P}} = 10^4.
-\end{align*}
+\end{align}
 Empirically, we find $t_{\nu} \approx 200$ suggesting the true kinetic energy decay time scale is based on a length scale $\ell \approx 0.14$ which is longer than the boundary layer height $\delta$ but shorter than the domain height $L_z$.
@@
 To compute MSTE, we construct a marginally-stable mean temperature profile and evolve it according to the advective flux of its marginally-stable eigenfunctions, and its own diffusion. 
-We assume that at least some modes are always in a marginally-stable configuration. 
+We assume that at least some modes are always in a marginally-stable configuration and all other modes are stable. 
 The marginal stability constraint then fixes the ratio between advection and diffusion (eigenfunction amplitude $A^2$). 
@@
 These are similar to what has been found in experiments and direct numerical simulations.
-But MSTE also exhibit unique and unexpected features: mean temperature gradient-reversals/dips, high kinetic energy flows, and a larger $\Nu$ than other time-invariant solutions. 
+But MSTE also exhibit unique and unexpected features: mean temperature gradient-reversals/dips, high kinetic energy flows, and a larger $\Nu$ than other equilibrated solutions. 
 When initializing with different mean temperature profiles, we find the same MSTE, suggesting these equilibria might be unique.
@@
 Initializing with only the temperature state of the MSTE avoids an early convective transient, but does not have excessive large-scale flows.
-These state could be excellent initial conditions for high-Rayleigh number DNS.
+These states could be excellent initial conditions for high-Rayleigh number DNS.
 
@@
 This function is meant to describe the temperature near $z = -1/2$ so it does not pass through the origin.
-An appropriate initial mean temperature profile $\overline{T}_0$ must be odd-symmetric, i.e.~$\overline{T}_0(-z) = -\overline{T}_0(z)$.
+An appropriate initial mean temperature profile $\overline{T}_0$ must be odd-symmetric, i.e.~$\overline{T}_0(z) = -\overline{T}_0(-z)$.
 Due to continuity, this implies $\overline{T}_0(0) = 0$.
 Accordingly, we construct $\overline{T}_0(z)$ by translating $\overline{\mathcal{T}}_0(z)$ vertically to pass through the origin.
-We then take its odd-extension and include a unique scaling coefficient to satisfy the boundary conditions $\overline{T}_0(-1/2) = 1/2$ and $\overline{T}_0(1/2) = -1/2$.
+We then take its odd-extension and include a scaling coefficient to satisfy the boundary conditions $\overline{T}_0(-1/2) = 1/2$ and $\overline{T}_0(1/2) = -1/2$.
 The initial mean temperature profile is therefore given by
@@
  We expect each $\Ra$ to be associated with a unique $\delta_0$ for which $\overline{T}_0(z)$ is marginally-stable. 
-It should be noted that when experimenting with various initial profiles $(\tanh, \rm{erf}, \rm{etc.})$, we obtain indistinguishable equilibrated states.
+It should be noted that when experimenting with various initial profiles $(\tanh, \, \rm{erf})$, we obtain indistinguishable equilibrated states.
 Therefore these initial states lie in the MSTE basin of attraction with respect to the quasilinear system.
@@
 This is due to coupling between the eigenfunctions $W(z)$, $\theta(z)$ and the mean temperature profile $\overline{T}$.
-In the context of our algorithm, this effectively deletes the sought-after root of the maximum eigenvalue function $\sigma_{\rm{max}}(A^2)$, causing the root-finding methods to fail. 
+In the context of our algorithm, this effectively deletes the sought-after root of the maximum eigenvalue function $\sigma_{\rm{max}}(A^2)$, causing the root-finding method to fail. 
 This is not a numerical instability, rather, it is an inherent limitation of our timestepping algorithm.
@@
 \onecolumngrid
-\section{MSTE Parameters, and Results}\label{sec:tables}
+\section{MSTE Parameters and Results}\label{sec:tables}
 
@@
     The remaining quantities are computed directly from the MSTE. 
-    The low $\Ra = 10^5$ case requires $\sim 12$ hours while the high $\Ra = 10^9$ case requires $\sim 72$ hours. 
+    The low $\Ra = 10^5$ case requires $\sim 12$ hours to compute while the high $\Ra = 10^9$ case requires $\sim 72$ hours. 
     Eigenvalue solves are performed for various $k_x$ simultaneously using 28 cores.}
@@
 
-In Figure~\ref{fig:eigenfunctions} we plot the velocity and temperature perturbation eigenfunctions for the marginally stable modes in the $\Ra =10^9$ MSTE.
+In Figure~\ref{fig:eigenfunctions} we plot the velocity and temperature perturbation eigenfunctions for the marginally-stable modes in the $\Ra =10^9$ MSTE.
 Though the eigenfunctions are in general complex, the linear system \eqss{EQ:linear1}{EQ:linear3} obeys phase-shift symmetry.
@@
 This is due to the exchange of stabilities mentioned previously: $\omega = 0$ at marginal stability implies that the system admits a set of real solutions.
-Adjacent modes, whose wavenumbers only differ by $\pi/2$, are superimposed to illustrate their similarity.
+Adjacent modes, whose wavenumbers only differ by $0.5\pi$, are superimposed to illustrate their similarity.
 For the large-scale $k_x = 1.5\pi$ mode, we find the vertical velocity eigenfunction $W$ is maximized near the center of the domain.

### 2021-06-03 publication_materials/ms_rbc.tex
housekeeping

@@
-\documentclass[reprint,amsmath,amssymb,aps,nofootinbib]{revtex4-1}
+\documentclass[longbibliography,twocolumn,amsmath,amssymb,aps,nofootinbib]{revtex4-2}
 
@@
 \newcommand{\Z}{{\cal Z}}
-
-\bibliographystyle{apsrev4-1}
 
@@
 If we perceive MSTE as background states, DNS suggest that plumes, vortex sheets, and other unstable turbulent features inhibit total heat transfer. 
-This perspective agrees with conventional models of transitions to turbulent flows, such as Boussinesq's turbulent-viscosity hypothesis \cite{boussinesq_1877}. 
+This perspective agrees with conventional models of transitions to turbulent flows, such as Boussinesq's turbulent-viscosity hypothesis \cite{pope_2000}. 
 The emergence of small-scale velocity structures is indicative of nonlinear energy transfer to small scales where energy is lost due to viscosity. 
@@
 % \bibliographystyle{plain}
-\bibliography{he}
+% \bibliographystyle{apsrev4-1}
+
+\bibliography{ms_rbc.bib}
 

### 2021-07-19 publication_materials/ms_rbc.tex
abstract round 2

@@
     Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important properties remain elusive.
-    To study convection in a novel context, we derive and solve a quasilinear form of the Rayleigh-Bénard problem by representing the perturbations in terms of marginally-stable eigenmodes.
-    The amplitude of each eigenmode is determined by requiring that the background state maintains marginal stability.
+    To study convection in a novel context, we solve Herring's quasilinear form of the Rayleigh-Bénard problem (\citet{herring63}) using a new approach: the perturbations are represented in terms of \textit{marginally-stable eigenmodes}.
     The background temperature profile evolves due to the advective flux of every marginally-stable eigenmode, as well as diffusion. 
-    To ensure marginal stability and to obtain the eigenfunctions at every timestep, we perform a one-dimensional eigenvalue solve on each of the allowable wavenumbers.
-    The background temperature field evolves to an equilibrium state, where the advective flux from the marginally-stable eigenmodes and the diffusive flux sum to a constant.
-    These marginally-stable thermal equilibria (MSTE) are exact solutions of the quasilinear equations.
+    We find the system tends toward an equilibrium where advection and diffusion sum to a constant.
+    The eigenmode amplitudes must be chosen such that the background state maintains marginal stability. 
+    We accomplish this by applying Newton's method to the eigenvalues, which themselves are a function of the perturbation amplitudes.
+    In this way, marginal stability is maintained and several modes are allowed to simultaneously participate in the evolution of the background state.
+    We consider only the countable set of modes whose wavenumbers agree with the problem's periodic domain.
+    This approach is unique in that we traverse a marginally-stable manifold to equilibrium, rather than beginning with an unstable state and allowing it to saturate via the advection of a single unstable mode, thereby allowing us to extend Herring's findings to larger $\Ra$.
+    In agreement with \citet{herring63}, we find that only a small subset of the allowable wavenumbers achieve marginal-stability, with a single ``dominant'' mode (whose spatial wavenumber $k_x = 1.5\pi$) participating when $\Ra < 10^6$.
+    For $\Ra \geq 10^6$, we find the dominant mode acts in cooperation with higher-wavenumber modes to accommodate the sharp change in diffusive flux which is commonly observed in high-$\Ra$ convection boundary layers.
+    We then compare our findings with direct numerical simulations.
     The mean temperature profile has thinner boundary layers and larger Nusselt numbers than thermally-equilibrated 2D and 3D simulations of the full nonlinear equations.
-    We find the Nusselt number scales like $\Nu \sim\Ra^{1/3}$.
+    We find the Nusselt number continues to scale like $\Nu \sim\Ra^{1/3}$ beyond $\Ra = 10^6$.
     When an MSTE is used as initial conditions for a 2D simulation, we find that Nu quickly equilibrates without the burst of turbulence often induced by purely conductive initial conditions, but we also find that the kinetic energy is too large and viscously attenuates on a long viscous time scale.

### 2021-07-20 ecs_analysis.m
ecs profiles

@@ -1,0 +1,1 @@
+plot(z, T_meanx)

### 2021-07-20 plot_profiles.py

@@ -8,6 +8,7 @@ import eigentools as eig
 import numpy as np
 from collections import OrderedDict
 from mpi4py import MPI
+import pandas as pd
 import os
 import pickle
 import h5py
@@ -28,6 +29,16 @@ ra = 1e8
 P = ra**(-1/2)
 root_path = os.path.dirname(os.path.abspath(__file__))
 e = h5py.File(root_path + '/profiles_nom/profiles_nom_s40.h5','r')
+
+path = os.path.dirname(os.path.abspath(__file__)) + '/'
+file_nm = path + 'ecs_profiles.xls'
+
+xl = pd.ExcelFile(file_nm)
+data = xl.parse("Sheet1")
+ra_ss = np.array(list(data.iloc[:, 0])[:9])
+nu_ss = np.array(list(data.iloc[:, 1])[:9])
+print(ra_ss)
+
 Tz_nom = np.mean((e['tasks']['diffusive_flux'][()]), axis=0).squeeze() / P
 z_nom = e['scales/z']['1.0'][:]
 # z_nom = e['scales']['z'][()].squeeze()

### 2021-07-29 publication_materials/ms_rbc.tex
meeting

--- 2021-06-03 publication_materials/ms_rbc.tex
@@
 \usepackage{nonfloat}
+\usepackage{soul}
+\usepackage{ulem}
 % \usepackage{multicol}
@@
 \renewcommand{\Citet}[1]{Ref.~\cite{#1}}
+\newcommand{\citets}[1]{refs.~\cite{#1}}
+\newcommand{\Citets}[1]{Refs.~\cite{#1}}
 
@@
 \begin{abstract}
-    Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important properties remain elusive.
-    To study convection in a novel context, we derive and solve a quasilinear form of the Rayleigh-Bénard problem by representing the perturbations in terms of marginally-stable eigenmodes.
-    The amplitude of each eigenmode is determined by requiring that the background state maintains marginal stability.
-    The background temperature profile evolves due to the advective flux of every marginally-stable eigenmode, as well as diffusion.
-    To ensure marginal stability and to obtain the eigenfunctions at every timestep, we perform a one-dimensional eigenvalue solve on each of the allowable wavenumbers.
-    The background temperature field evolves to an equilibrium state, where the advective flux from the marginally-stable eigenmodes and the diffusive flux sum to a constant.
+    \textcolor{blue}{Natural convection exhibits turbulent flows which are difficult or impossible to resolve in nonlinear direct numerical simulations.
+In this work, we investigate a quasilinear form of the Rayleigh-B\'enard problem which describes the bulk one-dimensional properties of convection without resolving the turbulent dynamics.
+We represent perturbations away from the mean as marginally-stable eigenmodes.
+By constraining the perturbation amplitudes, the marginal-stability criterion allows us to evolve the background temperature profile under the influence of multiple eigenmodes representing bulk flows at different length scales.}
+    We find the quasilinear system evolves to an equilibrium state where advective and diffusive fluxes sum to a constant.
     These marginally-stable thermal equilibria (MSTE) are exact solutions of the quasilinear equations.
-    The mean temperature profile has thinner boundary layers and larger Nusselt numbers than thermally-equilibrated 2D and 3D simulations of the full nonlinear equations.
-    We find the Nusselt number scales like $\Nu \sim\Ra^{1/3}$.
+    The mean MSTE temperature profiles have thinner boundary layers and larger Nusselt numbers than thermally-equilibrated 2D and 3D simulations of the full nonlinear equations.  
+    \textcolor{blue}{MSTE solutions exhibit a classic boundary-layer scaling of the Nusselt number $\Nu$ with the Rayleigh number $\Ra$ of $\Nu \sim \Ra^{1/3}$.}
     When an MSTE is used as initial conditions for a 2D simulation, we find that Nu quickly equilibrates without the burst of turbulence often induced by purely conductive initial conditions, but we also find that the kinetic energy is too large and viscously attenuates on a long viscous time scale.
-    This is due to the thin temperature boundary layers which diffuse heat very effectively, thereby requiring high-velocity advective flows to reach an equilibrium.
 \end{abstract}
@@
 Although the quasilinear approximation greatly simplifies the problem, an additional condition must be imposed to determine the amplitude of the perturbations.
-The simplest approach is to initialize the perturbations to low amplitude, and evolve them together with the background (this is, e.g., the approach of \citet{marston2016} and many others).
-A different approach was taken in \citet{Beaume_2015}, which computes ECS in parallel shear flows by deriving and solving a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments.
+
+\textcolor{blue}{\Citets{herring63, marston2016} address this by} initializing the perturbations to low amplitude and evolving them together with the background.
+\textcolor{blue}{More recently,} a different approach was taken in \citet{Beaume_2015}, which computes ECS in parallel shear flows by deriving and solving a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments.
 They assume the background velocity evolves on a slow time scale, and, to determine the perturbation amplitudes, they require marginal stability at each timestep.
@@
 
-In this paper we employ this strategy for the Rayleigh-B\'{e}nard convection problem.
-In Section~\ref{sec:model} we recall the underlying equations, and in Section~\ref{sec:evolution} we outline how we evolve the background temperature profile while maintaining marginal stability.
+\textcolor{blue}{
+In \citet{herring63}, Herring derives a quasilinear model for Boussinesq convection and provides supporting arguments for the model's physical validity.
+He demonstrates that a single eigenmode is dominant only when $\Ra < 10^6$.
+Herring uses numerical integration along with Fourier decomposition to approximate the transient solution to his model, allowing the system to saturate in a state of marginal stability.
+Though efficient, this method is limited in its inability to model high-$\Ra$ convection due to the appearance of a second unstable mode at $\Ra \approx 10^6$.
+How these modes interact to form thermal equilibria is also of interest.
+In this paper we apply \citet{Chini_ql}'s generalized approach to \citet{herring63}'s reduced convection model by requiring marginal stability at the point of initialization.
+When evolving the background state, we select the perturbation amplitudes such that marginal stability is maintained with each successive timestep.
+This new method allows us to calculate marginal-stable thermal equilibria up to $\Ra = 10^9$, requiring as many as five eigenmodes each with a unique horizontal wavenumber.
+}
+
+\textcolor{blue}{The paper is organized as follows:} in Section~\ref{sec:model} we recall the underlying equations, and in Section~\ref{sec:evolution} we outline how we evolve the background temperature profile while maintaining marginal stability.
 Section~\ref{sec:properties} pertains to the properties of the marginally-stable thermal equilibria, in particular how the Nusselt number and characteristic wavenumbers vary with the Rayleigh number.
@@
 We use Newton's method to find an amplitude $A^2$ such that the maximum growth rate is zero to within $10^{-9}$.
-Marginally-stable modes do not oscillate in time, i.e.~$\sigma = 0$ implies $\omega = 0$.
-This agrees with the conventional notion of exchange of stabilities \cite{drazin_reid_2004}.
+We observe that marginally-stable modes do not oscillate in time, i.e.~$\sigma = 0$ implies $\omega = 0$.
+This \textcolor{blue}{finding} is consistent with the conventional notion of exchange of stabilities \cite{drazin_reid_2004}.
 Crucially, we do not assume the $k_x$ of the marginally-stable mode is fixed.
@@
     We evolve this background temperature profile according to Section~\ref{sec:evolution} until we reach a marginally-stable thermal equilibrium (MSTE).
+    \textcolor{blue}{ECS refers to a steady nonlinear solution for Boussinesq convection, given by \citet{Wen}.}
     The DNS curve is obtained from a 2D nonlinear simulation of \eqss{EQ:motion1}{EQ:motion3} with \texttt{Dedalus}.
@@
     The initial profile has the narrowest boundary layer, while the DNS profile has the widest boundary layer.
-    The MSTE profile exhibits prominent dips, nested alongside the boundary regions. }
+    \textcolor{blue}{The equilibrated MSTE and ECS curves lie between the initial and DNS curves, with the ECS having a more diffuse boundary layer than that of the MSTE.}
+    The MSTE profile exhibits prominent dips, nested alongside the boundary regions. 
+    }
 %    The source of this feature is not well understood, but similar temperature gradient reversal regions were found by \cite{chini_cells} along the midlines of 2D convective cellular solutions at $\Ra \sim 10^6$.}
@@
 The temperature boundary layers in the DNS are wider than in the MSTE, which is in turn wider than the boundary layer of the initial temperature profile.
-Performing an eigenvalue solve by setting $\overline{T}$ equal to the DNS profile yields unstable eigenvalues. 
+\textcolor{blue}{By computing the maximum growth rates of the linearized system \eqss{EQ:linear1}{EQ:linear3}, we found that both the DNS and the ECS profiles are linearly unstable when used as background states.}
+\note{Need to perform EVP on ECS to confirm this!}
 Every marginally-stable initial profile we experiment with ($\tanh$, $\rm{erf}$) has thinner boundary layers than the DNS and MSTE profiles.
+\textcolor{blue}{When comparing our quasilinear equilibrium (MSTE) with \citet{Wen}'s nonlinear equilibrium (ECS), we find that the ECS profile is significantly more diffuse than that of the MSTE.}
 In conjunction, these two facts suggest that MSTE maximize boundary layer thickness while subject to the marginal stability constraint.
@@
 This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure~\ref{fig:flux}. 
-We do not understand the source of these dips, but similar temperature gradient reversals were reported by \cite{chini_cells} along the midlines of 2D convective cellular solutions at $\Ra \sim 10^6$.
-In that case, the reversals were due to nonlinear advection, which is not present in our quasilinear model.
+\textcolor{blue}{\Citet{herring63} observed this when studying the same system.
+Similar temperature gradient reversals were reported by \cite{chini_cells} along the midlines of 2D convective cellular solutions at $\Ra \sim 10^6$. 
+In that case, the reversals are due to nonlinear advection, which is not present in our quasilinear model.
+Neither the present authors, nor Herring were able to provide a rigorous mathematical explanation for this behavior.}
 
@@
     \caption{Wavenumbers of marginally-stable modes in thermally equilibrated states.
+    \textcolor{blue}{Consistent with Herring's findings, we observe the appearance of a second characteristic eigenmode branch (shown in green) near $\Ra \approx 10^6$.}
     Marginal modes often appear in adjacent pairs, which we denote with a common color. 
@@
 We illustrate this in Figure~\ref{fig:b0_delta} where the mean temperature $\overline{T}$ is plotted along a rescaled $z$-coordinate $\frac{z + 1/2}{\delta}$.
+\textcolor{blue}{It is also noteworthy that we do not encounter any appreciable variation in the boundary layer geometry as we extend Herring's findings beyond $\Ra = 10^6$.}
 The rescaled boundary layer geometry appears intrinsic to the MSTE, possibly minimizing diffusion as previously hypothesized.
@@
     All datasets obey power-law relationships, with the MSTE and ECS scaling like $\Nu \sim\Ra^{1/3}$. 
+    \textcolor{blue}{Herring demonstrates this in the low-$\Ra$ regime---we confirm his findings and demonstrate that this scaling law holds for high-$\Ra$ MSTE.}
     MSTE have greater $\Nu$ than the ECS, which in turn, have greater $\Nu$ than the DNS. 
@@
 We find that MSTE satisfy $\Nu \sim\Ra^{1/3}$, consistent with our finding that the boundary layer height scales like $\delta \sim \Ra^{1/3}$.
+\textcolor{blue}{Herring was able to demonstrate this for $\Ra \leq 10^6$.
+Our results confirm this trend in MSTE up to $\Ra = 10^9$.}
 The Nusselt numbers of the ECS are somewhat lower and the DNS Nusselt numbers are yet lower still.
@@
     T(x, z)\big|_{t=0} &= 0.5 - z + \mathcal{N} \nonumber \\
-    \vec{u}(x, z)\big|_{t=0} &= \vec{0} \nonumber \\
-    p(x, z)\big|_{t=0} &= 0 \label{EQ:linear_ic}
+    \vec{u}(x, z)\big|_{t=0} &= \vec{0} \label{EQ:linear_ic}
 \end{align}
@@
     T(x, z)\big|_{t=0} &= \overline{T}(z) + \sum_{n=1}^N  A_n \Re \Big[ \theta_n(z) e^{ik_{x_n}x} \Big] + \mathcal{N} \nonumber \\
-    \vec{u}(x, z)\big|_{t=0} &= \sum_{n=1}^N A_n \Re \Big[\Big( U_n (z) \hat{x} + W_n(z) \hat{z} \Big) e^{ik_{x_n}x} \Big] \nonumber\\
-    p(x, z)\big|_{t=0} &= \sum_{n=1}^N A_n \Re \Big[P_n (z) e^{ik_{x_n}x}\Big] \label{EQ:mste_ic}
+    \vec{u}(x, z)\big|_{t=0} &= \sum_{n=1}^N A_n \Re \Big[\Big( U_n (z) \hat{x} + W_n(z) \hat{z} \Big) e^{ik_{x_n}x} \Big] \label{EQ:mste_ic}
 \end{align}
-where $\theta_n(z), \, U_n(z), \, W_n(z), \, P_n(z); \; A_n; $ and $k_{x_n}$ refer to the complex eigenfunctions, amplitude, and wavenumber of the $n$th marginal mode respectively. 
+where $\theta_n(z), \, U_n(z), \, W_n(z); \; A_n; $ and $k_{x_n}$ refer to the complex eigenfunctions, amplitude, and wavenumber of the $n$th marginal mode respectively. 
 Note that although the MSTE is an equilibrium of the quasilinear equations, it is not an equilibrium of the full nonlinear equations.
@@
 In this particular case, we can eliminate the perturbations' imaginary components by selecting the proper $\phi$.
-This is due to the exchange of stabilities mentioned previously: $\omega = 0$ at marginal stability implies that the system admits a set of real solutions.
+This is due to the exchange of stabilities \textcolor{blue}{observed} previously: $\omega = 0$ at marginal stability implies that the system admits a set of real solutions.
 Adjacent modes, whose wavenumbers only differ by $0.5\pi$, are superimposed to illustrate their similarity.

### 2021-07-29 plot_profiles.py

@@ -4,7 +4,6 @@ import matplotlib.pyplot as plt
 import matplotlib.ticker as tck
 from matplotlib.patches import Rectangle
 import dedalus.public as de
-import eigentools as eig
 import numpy as np
 from collections import OrderedDict
 from mpi4py import MPI
@@ -35,9 +34,8 @@ file_nm = path + 'ecs_profiles.xls'
 
 xl = pd.ExcelFile(file_nm)
 data = xl.parse("Sheet1")
-ra_ss = np.array(list(data.iloc[:, 0])[:9])
-nu_ss = np.array(list(data.iloc[:, 1])[:9])
-print(ra_ss)
+z_ecs = np.array(list(data.iloc[:, 1])[:])
+T_ecs = np.array(list(data.iloc[:, 0])[:])
 
 Tz_nom = np.mean((e['tasks']['diffusive_flux'][()]), axis=0).squeeze() / P
 z_nom = e['scales/z']['1.0'][:]
@@ -82,21 +80,23 @@ colors = plt.rcParams['axes.prop_cycle'].by_key()['color']
 # ax1 = fig.add_axes([0.29, 0.315, 0.3, 0.18])
 ax1 = ax.inset_axes([0.1, 0.1, 0.35, 0.3])
 ax.plot(z0, T0, label='Initial', color='black')
-ax.plot(z1, T1, label='MSTE', color=colors[-1])
+ax.plot(z1, T1, label='MSTE', color=colors[1])
+ax.plot(z_ecs - 0.5, T_ecs - 0.5, label='ECS', color=colors[-1])
 ax.plot(z2, T2, label='DNS', color=colors[0])
 ax.set_xlim(-0.5, 0.5)
 ax.set_ylim(-0.5, 0.5)
 ax.set_xlabel(r'$\rm{z}$')
 ax.set_ylabel(r'$\bar{T}$')
 # plt.xticks([-0.5, -0.495, -0.49])
-ax.legend(frameon=False)
+ax.legend(frameon=False, ncol=2)
 ax.add_patch(Rectangle((-0.5, -0.02), 0.05, 0.12, alpha=0.5, fill=None, linewidth=0.5))
 ax.plot([-0.05, -0.45], [-0.1, 0.1], color='k', alpha=0.5, linewidth=0.5)
 ax.plot([-0.4, -0.5], [-0.4, -0.02], color='k', alpha=0.5, linewidth=0.5)
[…]

### 2021-07-30 publication_materials/ms_rbc.tex
minor changes

@@
 We represent perturbations away from the mean as marginally-stable eigenmodes.
-By constraining the perturbation amplitudes, the marginal-stability criterion allows us to evolve the background temperature profile under the influence of multiple eigenmodes representing bulk flows at different length scales.}
+By constraining the perturbation amplitudes, the marginal-stability criterion allows us to evolve the background temperature profile under the influence of multiple eigenmodes representing flows at different length scales.}
     We find the quasilinear system evolves to an equilibrium state where advective and diffusive fluxes sum to a constant.
@@
     \caption{Wavenumbers of marginally-stable modes in thermally equilibrated states.
-    \textcolor{blue}{Consistent with Herring's findings, we observe the appearance of a second characteristic eigenmode branch (shown in green) near $\Ra \approx 10^6$.}
     Marginal modes often appear in adjacent pairs, which we denote with a common color. 

### 2021-08-31 publication_materials/ms_rbc.tex
pre-accepted

@@
 \begin{abstract}
-    \textcolor{blue}{Natural convection exhibits turbulent flows which are difficult or impossible to resolve in nonlinear direct numerical simulations.
+    \textcolor{blue}{Natural convection exhibits turbulent flows which are difficult or impossible to resolve in direct numerical simulations.
 In this work, we investigate a quasilinear form of the Rayleigh-B\'enard problem which describes the bulk one-dimensional properties of convection without resolving the turbulent dynamics.
-We represent perturbations away from the mean as marginally-stable eigenmodes.
-By constraining the perturbation amplitudes, the marginal-stability criterion allows us to evolve the background temperature profile under the influence of multiple eigenmodes representing flows at different length scales.}
+We represent perturbations away from the mean using a sum of marginally-stable eigenmodes.
+By constraining the perturbation amplitudes, the marginal stability criterion allows us to evolve the background temperature profile under the influence of multiple eigenmodes representing flows at different length scales.}
     We find the quasilinear system evolves to an equilibrium state where advective and diffusive fluxes sum to a constant.
@@
 He demonstrates that a single eigenmode is dominant only when $\Ra < 10^6$.
-Herring uses numerical integration along with Fourier decomposition to approximate the transient solution to his model, allowing the system to saturate in a state of marginal stability.
+Herring uses numerical integration along with Fourier decomposition to approximate the transient solution to his model, allowing the system to saturate to a state of marginal stability.
 Though efficient, this method is limited in its inability to model high-$\Ra$ convection due to the appearance of a second unstable mode at $\Ra \approx 10^6$.
@@
 When evolving the background state, we select the perturbation amplitudes such that marginal stability is maintained with each successive timestep.
-This new method allows us to calculate marginal-stable thermal equilibria up to $\Ra = 10^9$, requiring as many as five eigenmodes each with a unique horizontal wavenumber.
+This new method allows us to calculate marginally-stable thermal equilibria up to $\Ra = 10^9$, involving as many as five eigenmodes each with a unique horizontal wavenumber.
 }
@@
 We observe that marginally-stable modes do not oscillate in time, i.e.~$\sigma = 0$ implies $\omega = 0$.
-This \textcolor{blue}{finding} is consistent with the conventional notion of exchange of stabilities \cite{drazin_reid_2004}.
+This \textcolor{blue}{numerical result} is consistent with the conventional notion of exchange of stabilities \cite{drazin_reid_2004}.
 Crucially, we do not assume the $k_x$ of the marginally-stable mode is fixed.
@@
 \textcolor{blue}{By computing the maximum growth rates of the linearized system \eqss{EQ:linear1}{EQ:linear3}, we found that both the DNS and the ECS profiles are linearly unstable when used as background states.}
-\note{Need to perform EVP on ECS to confirm this!}
+% \note{Need to perform EVP on ECS to confirm this!}
 Every marginally-stable initial profile we experiment with ($\tanh$, $\rm{erf}$) has thinner boundary layers than the DNS and MSTE profiles.
@@
 This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure~\ref{fig:flux}. 
-\textcolor{blue}{\Citet{herring63} observed this when studying the same system.
-Similar temperature gradient reversals were reported by \cite{chini_cells} along the midlines of 2D convective cellular solutions at $\Ra \sim 10^6$. 
+\textcolor{blue}{\Citet{herring63} observes this when studying the same system.
+Similar temperature gradient reversals are reported by \cite{chini_cells} along the midlines of 2D convective cellular solutions at $\Ra \sim 10^6$. 
 In that case, the reversals are due to nonlinear advection, which is not present in our quasilinear model.
@@
     The largest wavenumbers of the green and blue branches depend on  $\Ra$ according to power laws.
-    For the green branch, $\max\{k_x\} \propto \Ra^{0.300}$ with $R^2 = 0.998$ while for the blue branch, $k_x \propto \Ra^{0.155}$ with $R^2 = 0.988$.}
+    For the green branch, $\max\{k_x\} \propto \Ra^{0.300}$ with $R^2 = 0.998$ while for the blue branch, $k_x \propto \Ra^{0.155}$ with $R^2 = 0.988$.
+    }
     \label{fig:kx_marginals}
@@
 Least-squares regression gives $\max\{k_x\} \propto \Ra^{0.300}$ with $R^2 = 0.998$ for this maximum branch.
+\textcolor{blue}{This relationship does not appear to be asymptotic. 
+If we consider only those MSTE whose $\Ra \geq 10^8$, we observe $\max\{k_x\} \sim \Ra^{1/3}$ in agreement with classical scaling arguments.} 
 For large $\Ra$, the advective fluxes of this maximum branch compensate for the strongly peaked diffusive flux in the thin boundary layers.
@@
     All datasets obey power-law relationships, with the MSTE and ECS scaling like $\Nu \sim\Ra^{1/3}$. 
-    \textcolor{blue}{Herring demonstrates this in the low-$\Ra$ regime---we confirm his findings and demonstrate that this scaling law holds for high-$\Ra$ MSTE.}
     MSTE have greater $\Nu$ than the ECS, which in turn, have greater $\Nu$ than the DNS. 
@@
 
-The MSTE contain large-scale convective cell structures, and have $\Nu\sim\Ra^{1/3}$.
+\textcolor{blue}{Our method allows several marginally-stable eigenmodes to participate in the evolution of the background state simultaneously.
+Consequently, we are able to exceed Herring's $\Ra = 10^6$ threshold.
+For $\Ra > 10^6$ we did not observe any significant deviations from the trends observed in low-$\Ra$ MSTE.
+}
+
+MSTE contain large-scale convective cell structures, and have $\Nu\sim\Ra^{1/3}$.
 These are similar to what has been found in experiments and direct numerical simulations.
@@
 In this particular case, we can eliminate the perturbations' imaginary components by selecting the proper $\phi$.
-This is due to the exchange of stabilities \textcolor{blue}{observed} previously: $\omega = 0$ at marginal stability implies that the system admits a set of real solutions.
+This is due to the \textcolor{blue}{apparent} exchange of stabilities \textcolor{blue}{observed} previously: $\omega = 0$ at marginal stability implies that the system admits a set of real solutions.
 Adjacent modes, whose wavenumbers only differ by $0.5\pi$, are superimposed to illustrate their similarity.

### 2021-08-31 publication_materials/ref_resp1.tex
pre-accepted

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx,amsmath,amsfonts,amssymb}
\usepackage{enumitem}
\usepackage{xcolor}
\setlength{\parindent}{0pt}

\begin{document}

\subsection*{MSTE Paper Referee Response}

We would like to take this opportunity to thank the referee for their time and consideration of our work.
The comments we received were informative.
The relevant changes are highlighted in blue in the updated manuscript.

We address each remark below:

\vspace{0.4cm}

\noindent ``This study investigates a quasilinear model of two-dimensional convection. By neglecting
several nonlinear terms and assuming that the dynamics of the horizontal mean and of the
fluctuation fields involve separate timescales, a new way of timestepping is possible in which
the two dimensional partial differential equations are turned into a one dimensional pde
complemented with a 2D eigenvalue problem. Steady states are numerically computed for
a large range of Rayleigh numbers and their properties are discussed.
The paper is interesting and the numerical scheme is clearly introduced.''

\vspace{0.4cm}
We thank the referee for their praise of our new numerical scheme.
\vspace{0.4cm}

``However, it
lacks a thorough discussion of the previous numerical studies of this QL model of convection.
For instance, the two pioneer papers of Herring$^1$
evidence similar features, e.g.:
\begin{enumerate}
    \item the “temperature dips” close to the walls
    \item the transition from a single wave number $k_x$ to two wavenumbers at $\rm{Ra} \sim 10^6$
    \item the scaling of the Nusselt number $\rm{Nu} \propto \rm{Ra}^{1/3}\;$ ''
\end{enumerate}

\vspace{0.4cm}

\noindent We revised much of our discussion and analysis of results to include comparisons and references to Herring's work.
Our equilibrated states agree with established results for $10^5 < \rm{Ra} < 10^6$.
We discuss this and note those similar features listed above.
In this way, we were able to (unintentionally) verify the validity of our results before extending Herring's work to $\rm{Ra} > 10^6$.

\vspace{0.4cm}
\noindent
``The novelty of the present study should then be clearly stated. Does it consist of:
\begin{enumerate}
    \item the extension of these QL steady solutions to larger values of Ra ? Then values of Ra
          at least as large as the ones obtained in Ref. [16] for the full Boussinesq convection
          system should be reached.

    \item the introduction of this new numerical method ? It would then benefit from a comparison with the ‘usual’ way of advancing in time the QL set of equations (timestep (12)-(14) with some noise as initial condition). In particular, is it actually faster to compute these steady states with this new method?

    \item the comparison of these QL steady states to the ones of the full nonlinear system ? A quantitative comparison of the fields (and not only of Nu) would be interesting, see point 3. below $\;$ ''
\end{enumerate}

\vspace{0.4cm}

\noindent We aim to address points 1 \& 2 above.
The novelty of this work is now stated in Section I paragraph 5.
After providing a brief review of Herring's methods and findings, we write:

\vspace{0.4cm}
``Though efficient, this method is limited in its inability to model high-$\rm{Ra}$ convection due to the appearance of a second marginally-stable mode at $\rm{Ra} \approx 10^6$. How these modes interact to form thermal equilibria is also of interest.
In  this  paper  we  apply  ref.  [23]’s  generalized approach to ref. [21]’s reduced convection model by requiring  marginal  stability  at  the  point  of  initialization.  ''
\vspace{0.4cm}

Directly timestepping the QL equations would involve solving a 2D problem, so would probably require more computer time.
We did attempt to find MSTE for $\rm{Ra} > 10^9$.
As the mean temperature profiles' boundary layers wane, increasingly large resolutions are necessary.
Eigenvalue solves must be performed over a wide range of horizontal wavenumbers to ensure marginal stability, particularly at high-$\rm{Ra}$ where the highest-wavenumber modes are widely dispersed over the eigenvalue spectrum (see Figure 3, lower right subfigure).

\vspace{0.4cm}

One difference between our approach to solving for equilibrium solutions and, e.g., Ref. [16], is that we initialized our search from a marginally-stable solution, whereas many others use continuation techniques to use lower-Ra states to guess solutions at higher Ra. We tried using continuation, but difficulty arises due to the discretization of allowed wavenumbers, i.e. $k_x \in \{\frac{n\pi}{2}\; | \; n \in \mathbb{N}\}$.
Allowing the wavenumbers of marginal modes to take on continuous values might address this issue, but that is outside the scope of this paper.

\vspace{0.4cm}

We found that several marginally-stable modes act in cooperation to yield equilibria.
We believe this is exciting and novel because similar reduced convection models often involve a single mode.
By constraining the amplitudes to a state of marginal stability (an intrinsic property of certain QL equilibria), our work underscores the importance of a dominant low-wavenumber mode while highlighting the role of non-dominant high-wavenumber modes---particularly in the context of diffusive boundary layers.

\vspace{0.4cm}

We address the minor remarks below:

\vspace{0.4cm}

``1. The authors find with their procedure eigenvalues such that $s = \omega + i\sigma$ with $\omega= 0$.
They refer to the principle of exchange of stability, but I think this theoretical result, derived in e.g. ref [27] of the manuscript, only holds when $\partial_z \overline{T} = -1$, i.e.  at the critical Rayleigh number $\rm{Ra}_c= 1708$. For $\rm{Ra} > \rm{Ra}_c$, the fact that $\omega$ remains zero is an output of their numerical study.''

\vspace{0.4cm}
It was not our intention to imply that this was anything other than an output of the numerical study. Thank you for bringing this to our attention, we updated the manuscript in two places:
\vspace{0.4cm}
\begin{enumerate}[label=\alph*)]
    \item In Section III paragraph 6 we write:

          ``This \textcolor{blue}{numerical result} is consistent with the conventional notion of exchange of stabilities [28].''

    \item In Appendix D paragraph 1 we write:

          ``This is due to the \textcolor{blue}{apparent} exchange of stabilities \textcolor{blue}{observed} previously: $\omega = 0$ at marginal stability implies that the system admits a set of real solutions.''

\end{enumerate}

``2. I am not confident in using the pressure field from MSTE as an initial condition (IC) for DNS, as proposed in equation (32) of the manuscript...''

\vspace{0.4cm}
You are correct. We removed the pressure equation from both sets of initial conditions (MSTE and linear diffusive) so as not to overconstrain the problem.
\vspace{0.4cm}

``3. The discussion of the MSTE in Figure 2 and/or Figure 7 would benefit from the additional plot of the mean temperature profiles from the ECS of Ref. [16]. To what extent are these two stationary solutions similar ?''

\vspace{0.4cm}
Thank you for recommending this! We included the relevant ECS mean temperature profile (along with discussion) in Figure 2 of the updated manuscript.

\end{document}

### 2021-08-31 publication_materials/ms_rbc.tex
accepted--title fixed, blue removed

@@
 
-\title{Marginally-Stable Thermal Equilibria of Rayleigh-Bénard Convection}
+\title{Marginally-Stable Thermal Equilibria of Rayleigh-B\'enard Convection}
 
@@
 \begin{abstract}
-    \textcolor{blue}{Natural convection exhibits turbulent flows which are difficult or impossible to resolve in direct numerical simulations.
+    Natural convection exhibits turbulent flows which are difficult or impossible to resolve in direct numerical simulations.
 In this work, we investigate a quasilinear form of the Rayleigh-B\'enard problem which describes the bulk one-dimensional properties of convection without resolving the turbulent dynamics.
 We represent perturbations away from the mean using a sum of marginally-stable eigenmodes.
-By constraining the perturbation amplitudes, the marginal stability criterion allows us to evolve the background temperature profile under the influence of multiple eigenmodes representing flows at different length scales.}
+By constraining the perturbation amplitudes, the marginal stability criterion allows us to evolve the background temperature profile under the influence of multiple eigenmodes representing flows at different length scales.
     We find the quasilinear system evolves to an equilibrium state where advective and diffusive fluxes sum to a constant.
@@
     The mean MSTE temperature profiles have thinner boundary layers and larger Nusselt numbers than thermally-equilibrated 2D and 3D simulations of the full nonlinear equations.  
-    \textcolor{blue}{MSTE solutions exhibit a classic boundary-layer scaling of the Nusselt number $\Nu$ with the Rayleigh number $\Ra$ of $\Nu \sim \Ra^{1/3}$.}
+    MSTE solutions exhibit a classic boundary-layer scaling of the Nusselt number $\Nu$ with the Rayleigh number $\Ra$ of $\Nu \sim \Ra^{1/3}$.
     When an MSTE is used as initial conditions for a 2D simulation, we find that Nu quickly equilibrates without the burst of turbulence often induced by purely conductive initial conditions, but we also find that the kinetic energy is too large and viscously attenuates on a long viscous time scale.
@@
 
-\textcolor{blue}{\Citets{herring63, marston2016} address this by} initializing the perturbations to low amplitude and evolving them together with the background.
-\textcolor{blue}{More recently,} a different approach was taken in \citet{Beaume_2015}, which computes ECS in parallel shear flows by deriving and solving a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments.
+\Citets{herring63, marston2016} address this by initializing the perturbations to low amplitude and evolving them together with the background.
+More recently, a different approach was taken in \citet{Beaume_2015}, which computes ECS in parallel shear flows by deriving and solving a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments.
 They assume the background velocity evolves on a slow time scale, and, to determine the perturbation amplitudes, they require marginal stability at each timestep.
@@
 
-\textcolor{blue}{
 In \citet{herring63}, Herring derives a quasilinear model for Boussinesq convection and provides supporting arguments for the model's physical validity.
@@
 This new method allows us to calculate marginally-stable thermal equilibria up to $\Ra = 10^9$, involving as many as five eigenmodes each with a unique horizontal wavenumber.
-}
 
-\textcolor{blue}{The paper is organized as follows:} in Section~\ref{sec:model} we recall the underlying equations, and in Section~\ref{sec:evolution} we outline how we evolve the background temperature profile while maintaining marginal stability.
+The paper is organized as follows: in Section~\ref{sec:model} we recall the underlying equations, and in Section~\ref{sec:evolution} we outline how we evolve the background temperature profile while maintaining marginal stability.
 Section~\ref{sec:properties} pertains to the properties of the marginally-stable thermal equilibria, in particular how the Nusselt number and characteristic wavenumbers vary with the Rayleigh number.
@@
 We observe that marginally-stable modes do not oscillate in time, i.e.~$\sigma = 0$ implies $\omega = 0$.
-This \textcolor{blue}{numerical result} is consistent with the conventional notion of exchange of stabilities \cite{drazin_reid_2004}.
+This numerical result is consistent with the conventional notion of exchange of stabilities \cite{drazin_reid_2004}.
 Crucially, we do not assume the $k_x$ of the marginally-stable mode is fixed.
@@
     We evolve this background temperature profile according to Section~\ref{sec:evolution} until we reach a marginally-stable thermal equilibrium (MSTE).
-    \textcolor{blue}{ECS refers to a steady nonlinear solution for Boussinesq convection, given by \citet{Wen}.}
+    ECS refers to a steady nonlinear solution for Boussinesq convection, given by \citet{Wen}.
     The DNS curve is obtained from a 2D nonlinear simulation of \eqss{EQ:motion1}{EQ:motion3} with \texttt{Dedalus}.
@@
     The initial profile has the narrowest boundary layer, while the DNS profile has the widest boundary layer.
-    \textcolor{blue}{The equilibrated MSTE and ECS curves lie between the initial and DNS curves, with the ECS having a more diffuse boundary layer than that of the MSTE.}
+    The equilibrated MSTE and ECS curves lie between the initial and DNS curves, with the ECS having a more diffuse boundary layer than that of the MSTE.
     The MSTE profile exhibits prominent dips, nested alongside the boundary regions. 
@@
 The temperature boundary layers in the DNS are wider than in the MSTE, which is in turn wider than the boundary layer of the initial temperature profile.
-\textcolor{blue}{By computing the maximum growth rates of the linearized system \eqss{EQ:linear1}{EQ:linear3}, we found that both the DNS and the ECS profiles are linearly unstable when used as background states.}
-% \note{Need to perform EVP on ECS to confirm this!}
+By computing the maximum growth rates of the linearized system \eqss{EQ:linear1}{EQ:linear3}, we found that both the DNS and the ECS profiles are linearly unstable when used as background states.
 Every marginally-stable initial profile we experiment with ($\tanh$, $\rm{erf}$) has thinner boundary layers than the DNS and MSTE profiles.
-\textcolor{blue}{When comparing our quasilinear equilibrium (MSTE) with \citet{Wen}'s nonlinear equilibrium (ECS), we find that the ECS profile is significantly more diffuse than that of the MSTE.}
+When comparing our quasilinear equilibrium (MSTE) with \citet{Wen}'s nonlinear equilibrium (ECS), we find that the ECS profile is significantly more diffuse than that of the MSTE.
 In conjunction, these two facts suggest that MSTE maximize boundary layer thickness while subject to the marginal stability constraint.
@@
 This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure~\ref{fig:flux}. 
-\textcolor{blue}{\Citet{herring63} observes this when studying the same system.
+\Citet{herring63} observes this when studying the same system.
 Similar temperature gradient reversals are reported by \cite{chini_cells} along the midlines of 2D convective cellular solutions at $\Ra \sim 10^6$. 
 In that case, the reversals are due to nonlinear advection, which is not present in our quasilinear model.
-Neither the present authors, nor Herring were able to provide a rigorous mathematical explanation for this behavior.}
+Neither the present authors, nor Herring were able to provide a rigorous mathematical explanation for this behavior.
 
@@
 Least-squares regression gives $\max\{k_x\} \propto \Ra^{0.300}$ with $R^2 = 0.998$ for this maximum branch.
-\textcolor{blue}{This relationship does not appear to be asymptotic. 
-If we consider only those MSTE whose $\Ra \geq 10^8$, we observe $\max\{k_x\} \sim \Ra^{1/3}$ in agreement with classical scaling arguments.} 
+This relationship does not appear to be asymptotic. 
+If we consider only those MSTE whose $\Ra \geq 10^8$, we observe $\max\{k_x\} \sim \Ra^{1/3}$ in agreement with classical scaling arguments. 
 For large $\Ra$, the advective fluxes of this maximum branch compensate for the strongly peaked diffusive flux in the thin boundary layers.
@@
 We illustrate this in Figure~\ref{fig:b0_delta} where the mean temperature $\overline{T}$ is plotted along a rescaled $z$-coordinate $\frac{z + 1/2}{\delta}$.
-\textcolor{blue}{It is also noteworthy that we do not encounter any appreciable variation in the boundary layer geometry as we extend Herring's findings beyond $\Ra = 10^6$.}
+It is also noteworthy that we do not encounter any appreciable variation in the boundary layer geometry as we extend Herring's findings beyond $\Ra = 10^6$.
 The rescaled boundary layer geometry appears intrinsic to the MSTE, possibly minimizing diffusion as previously hypothesized.
@@
 We find that MSTE satisfy $\Nu \sim\Ra^{1/3}$, consistent with our finding that the boundary layer height scales like $\delta \sim \Ra^{1/3}$.
-\textcolor{blue}{Herring was able to demonstrate this for $\Ra \leq 10^6$.
-Our results confirm this trend in MSTE up to $\Ra = 10^9$.}
+Herring was able to demonstrate this for $\Ra \leq 10^6$.
+Our results confirm this trend in MSTE up to $\Ra = 10^9$.
 The Nusselt numbers of the ECS are somewhat lower and the DNS Nusselt numbers are yet lower still.
@@
 
-\textcolor{blue}{Our method allows several marginally-stable eigenmodes to participate in the evolution of the background state simultaneously.
+Our method allows several marginally-stable eigenmodes to participate in the evolution of the background state simultaneously.
 Consequently, we are able to exceed Herring's $\Ra = 10^6$ threshold.
 For $\Ra > 10^6$ we did not observe any significant deviations from the trends observed in low-$\Ra$ MSTE.
-}
 
@@
 In this particular case, we can eliminate the perturbations' imaginary components by selecting the proper $\phi$.
-This is due to the \textcolor{blue}{apparent} exchange of stabilities \textcolor{blue}{observed} previously: $\omega = 0$ at marginal stability implies that the system admits a set of real solutions.
+This is due to the apparent exchange of stabilities observed previously: $\omega = 0$ at marginal stability implies that the system admits a set of real solutions.
 Adjacent modes, whose wavenumbers only differ by $0.5\pi$, are superimposed to illustrate their similarity.

### 2021-08-31 publication_materials/ms_rbc.tex
PRL: final draft

@@
 \section*{Acknowledgments}
-This paper is dedicated to Charlie Doering, who greatly influenced the way many of us think about Rayleigh-Benard convection.
-DL met Charlie as a WHOI GFD summer fellow, and has difficulty imagining Walsh Cottage without Charlie's friendly and open scientific style, and enthusiasm for softball.
+We would like to thank Charlie Doering, who greatly influenced the way many of us think about Rayleigh-B\'enard convection.
+Some of the ideas in this work came from discussions with Charlie at Walsh Cottage during the WHOI GFD summer programs; it is difficult to imagining Walsh Cottage without Charlie's friendly and open scientific style, and enthusiasm for softball.
 The authors thank Geoff Vasil, Greg Chini, Kyle Augustson, and Emma Kaufman for their valuable feedback and suggestions.

### 2021-11-12 ms_rbc_dfd/Tex/Sec_Method.tex
dfd talk half

%---------------------------------------------------------------------------%
\lecture{Research Presentation}{lec_present_method}
%---------------------------------------------------------------------------%
\section{\enorcn{Methods}{研究方法}}
%---------------------------------------------------------------------------%
\begin{frame}[fragile]
    \frametitle{Rayleigh's Linear Stability Analysis}
    \begin{itemize}
        \item Assume variables can be decomposed like 
        \begin{align}
            \vec{u}(x, z, t) &= \vec{u'}(x, z, t) \label{EQ:reynolds_dc_u} = u'(x, z, t)\hat{x} + w'(x, z, t)\hat{z} \\
            T(x, z, t) &= \overline{T}(z, t) + T'(x, z, t) \label{EQ:reynolds_dc_T}\\
            p(x, z, t) &= \overline{p}(z, t) +  p'(x, z, t). \label{EQ:reynolds_dc_p}
        \end{align}
        \item The Eigenvalue Problem (EVP) is given by
        \begin{align}
            \nabla \cdot \vec{u'} &= 0 \label{EQ:linear1}\\
            \frac{\partial\vec{u'}}{\partial t} &= - \nabla p' + T'\hat{z} + \mathcal{R} \nabla^2 \vec{u'} \label{EQ:linear2}\\
            \frac{\partial T'}{\partial t} + \frac{\partial \overline{T}}{\partial z} w' &= \mathcal{P} \nabla^2 T' \label{EQ:linear3}
        \end{align}
    \end{itemize}

\end{frame}

\begin{frame}[fragile]
    \frametitle{Solutions to the Linear Problem}
        Solutions are given by
        \begin{align}
            w'(x, z, t) &= A\, \Re\left[W(z) \, e^{i(k_xx-st)}\right] \label{EQ:normal_modes1}\\ 
            u'(x, z, t) &= A\, \Re\left[U(z) \, e^{i(k_xx-st)}\right] \label{EQ:normal_modes2}\\ 
            T'(x, z, t) &= A\, \Re\left[\theta(z) \, e^{i(k_xx-st)}\right] \label{EQ:normal_modes3}\\ 
            p'(x, z, t) &= A\, \Re\left[P(z) \, e^{i(k_xx-st)}\right] \label{EQ:normal_modes4}
        \end{align}
        where $A$ is the (undetermined) mode amplitude, $s = \omega + i\sigma$ is the eigenvalue, \newline

        and the allowed wavenumbers $k_x \in \left\{\frac{n\pi}{2} \, \big| \, n \in \mathbb{N}\right\}$.

\end{frame}

\begin{frame}[fragile]
    \frametitle{The Quasilinear Model}
    \begin{itemize}
        \item The 1D quasilinear initial value problem (IVP)
        \begin{equation}
            \frac{\partial \overline{T}}{\partial t} + \frac{\partial}{\partial z} \langle w'T' \rangle_x = \mathcal{P} \frac{\partial^2 \overline{T}}{\partial z^2} \label{EQ:T0_IVP}
        \end{equation}
        \item Evolution due to \textbf{Advection}: $\frac{\partial}{\partial z} \langle w'T' \rangle_x $
        and \textbf{Diffusion}: $\mathcal{P} \frac{\partial^2 \overline{T}}{\partial z^2}$\newline

        \item Derived by manipulating the nonlinear and linear equations\newline

        \item Can be solved in conjunction with the EVP provided the amplitude $A$ is known\newline

        \hspace{0.5cm} $\mathbf{\longrightarrow}$ \textbf{Marginal Stability}

    \end{itemize}

\end{frame}

\begin{frame}[fragile]
    \frametitle{Marginal Stability Constraint}
    \begin{itemize}
        \item We assume the perturbations evolve on a shorter timescale than the background state\newline

        \item We impose \textbf{Marginal Stability} at each timestep
        \begin{equation}
            \max_{k_x} \{ \sigma \} = 0.
        \end{equation}\newline

        \item The growth rate $\sigma$ is obtained by solving the EVP for some $\overline{T}(z,t)$\newline

        \item Does not allow us to solve for $A$ directly $\longrightarrow$ discrete root-finding methods
    \end{itemize}

\end{frame}

\begin{frame}[fragile]
    \frametitle{Solving for the Perturbation Amplitude $A$}
    \begin{enumerate}
        \item Given some guess for the amplitude $A$ and a fixed timestep $\Delta t$\newline

        \item We evolve the initial (marginally stable) temperature profile $\overline{T}(z,t) \; \longrightarrow \; \overline{T}(z,t+\Delta t)$\newline

        \item Solve the EVP using $\overline{T}(z,t+\Delta t)$\newline

        \item This renders $\sigma(A)$\newline

        \item Use Newton's method with finite differences to solve $\sigma(A) = 0$
    \end{enumerate}

\end{frame}

\begin{frame}[fragile]
    \frametitle{The Amplitude Guess}
    \begin{itemize}
        \item Consider advection and diffusion separately on $t\;\to\; t+\Delta t$\newline

        \item Solve $\frac{\partial\overline{T}}{\partial t} + \langle w'T' \rangle_x=0$, yielding $\overline{T}_{adv} \; \longrightarrow \; \sigma_{\rm{adv}}$\newline

        \item Solve $\frac{\partial\overline{T}}{\partial t} = \mathcal{P}\frac{\partial^2 \overline{T}}{\partial z^2}$, yielding $\overline{T}_{adv} \; \longrightarrow \; \sigma_{\rm{diff}}$\newline

        \item For small timesteps, we assume diffusion and advection act independently, i.e.
        \begin{equation}
            0 = \Delta \sigma \approx A^2\sigma_{\rm{adv}} + \sigma_{\rm{diff}} \quad \longrightarrow \quad A^2 \approx -\frac{\sigma_{\rm{diff}}}{\sigma_{\rm{adv}}}
        \end{equation}

    \end{itemize}

\end{frame}
%---------------------------------------------------------------------------%

### 2021-12-02 ms_rbc_dfd/Tex/Sec_Conclusion.tex
dfd talk done

%---------------------------------------------------------------------------%
\lecture{Research Presentation}{lec_present_conclude}
%---------------------------------------------------------------------------%
\section{\enorcn{Conclusion}{结论}}
%---------------------------------------------------------------------------%
\begin{frame}[fragile]
    \frametitle{Future Work}

    \begin{itemize}
        \item Explore mappings and $\rm{Ra}-\rm{Pr}$ parameter space\newline

        \item MSTE in different domains: non-cartesian and different aspect ratios\newline

        \item Compute high-$\rm{Ra}$ MSTE using intrinsic $\overline{T}$ profile and $\delta$ scaling
    \end{itemize}
    \begin{columns}[T]
        \begin{column}{.3\textwidth}
            {\includegraphics[height=0.75\textwidth]{kx_m_ra1.pdf}}
        \end{column}
        \begin{column}{.3\textwidth}
            {\includegraphics[height=0.75\textwidth]{b0_delta_solid.pdf}}
        \end{column}
    \end{columns}
\end{frame}

\begin{frame}[fragile]
    \frametitle{Acknowledgments}

    \begin{description}
        \item{\textbf{Co-Authors: }} Daniel Lecoanet (Northwestern ESAM), Evan Anders (Northwestern CIERA)\newline

        \item{\textbf{Special Thanks: }} Charlie Doering, Baole Wen, Greg Chini, Kyle Augustson, Emma Kaufman, Mallory Drevline\newline

        \item{\textbf{Supported By:}} Northwestern's Walter P. Murphy Fellowship for early career graduate students\newline
    \end{description}
\end{frame}
%%---------------------------------------------------------------------------%

### 2021-12-02 ms_rbc_dfd/Tex/Sec_Method.tex
dfd talk done

@@
         \end{align}
-        \item The Eigenvalue Problem (EVP) is given by
+        \item The linear Eigenvalue Problem (EVP) is given by
         \begin{align}
@@
             \max_{k_x} \{ \sigma \} = 0.
-        \end{equation}\newline
+        \end{equation}
 
@@
 
-        \item We evolve the initial (marginally stable) temperature profile $\overline{T}(z,t) \; \longrightarrow \; \overline{T}(z,t+\Delta t)$\newline
+        \item We evolve the initial (marginally stable) temperature profile $\overline{T}(z,t) \; \xrightarrow{\text{IVP}} \; \overline{T}(z,t+\Delta t)$\newline
 
@@
 
-        \item Solve $\frac{\partial\overline{T}}{\partial t} + \langle w'T' \rangle_x=0$, yielding $\overline{T}_{adv} \; \longrightarrow \; \sigma_{\rm{adv}}$\newline
+        \item Solve $\frac{\partial\overline{T}}{\partial t} + 2\frac{\partial}{\partial z} \Re\left[ W \theta^* \right] = 0$, yielding $\overline{T}_{adv} \; \xrightarrow{\text{EVP}} \; \sigma_{\rm{adv}}$\newline
 
-        \item Solve $\frac{\partial\overline{T}}{\partial t} = \mathcal{P}\frac{\partial^2 \overline{T}}{\partial z^2}$, yielding $\overline{T}_{adv} \; \longrightarrow \; \sigma_{\rm{diff}}$\newline
+        \item Solve $\frac{\partial\overline{T}}{\partial t} = \mathcal{P}\frac{\partial^2 \overline{T}}{\partial z^2}$, yielding $\overline{T}_{adv} \; \xrightarrow{\text{EVP}} \; \sigma_{\rm{diff}}$\newline
 
@@
 %---------------------------------------------------------------------------%
+
+\begin{frame}[fragile]
+    \frametitle{Multiple Marginally Stable Modes}
+    \begin{itemize}
+        \item Generalize
+        \begin{equation}
+            \langle w' T' \rangle_x = \sum_{n = 1}^{N} 2 A_n^2  \Re\left[ W_n \theta_n^* \right] 
+        \end{equation}
+        to accommodate $N$ simultaneously marginally stable modes\newline
+
+        \item $N$ amplitudes ($\vec{A}\in\mathbb{R}^N$) to maintain marginal stability in $N$ modes
+        \begin{equation}
+            \vec{\sigma}(\vec{A}) = \vec{0}
+        \end{equation} 
+        \item Modes with negative amplitudes are not included
+    \end{itemize}
+
+\end{frame}
+%---------------------------------------------------------------------------%
+
+\begin{frame}[fragile]
+    \frametitle{Solving for the Amplitude Vector $\vec{A}$}
+    \begin{enumerate}
+        \item Given some guess for the amplitude vector $\vec{A}$ and a fixed timestep $\Delta t$\newline
+
+        \item We construct a Jacobian matrix with finite differences
+        \begin{equation}
+            J = \begin{bmatrix}
+                \nabla \sigma_1 (A_1, A_2, ..., A_N) \\
+                \nabla \sigma_2 (A_1, A_2, ..., A_N) \\
+                \vdots \\
+                \nabla \sigma_N (A_1, A_2, ..., A_N) 
+            \end{bmatrix}.
+        \end{equation}\newline
+
+        \item Use Newton's method to solve $\vec{\sigma}(\vec{A}) = \vec{0}$
+    \end{enumerate}
+
+\end{frame}
+
+\begin{frame}[fragile]
+    \frametitle{The Amplitude Guess for $N$ modes}
+    \begin{itemize}
+        \item The amplitude vector can be approximated by
+        \begin{equation}
+            \vec{A^2} \approx = -\Sigma_{\rm{adv}}^{-1} \vec{\sigma_{\rm{diff}}}.
+            \label{EQ:AN_approx}
+        \end{equation}
+        \item The advective growth rate matrix $\Sigma_{\rm{adv}}$ measures the effect of the $j$th mode's advection on the $i$th mode's growth rate\newline
+
+        \item The diffusive growth rate vector $\vec{\sigma_{\rm{diff}}}$ measures the effect of diffusion on the $i$th mode's growth rate
+    \end{itemize}
+
+\end{frame}
+%---------------------------------------------------------------------------%
+%---------------------------------------------------------------------------%
+\begin{frame}[fragile]
+    \frametitle{Marginally Stable Thermal Equilibria}
+    \begin{itemize}
+        \item Evolve until the \textbf{advection} cancels \textbf{diffusion}
+        \begin{equation}
+            \frac{\partial}{\partial z} \langle w'T' \rangle_x = \mathcal{P} \frac{\partial^2 \overline{T}}{\partial z^2} \quad \longrightarrow \quad \frac{\partial \overline{T}}{\partial t} = 0
+        \end{equation}
+
+        \item Such states are referred to as Marginally Stable Thermal Equilibria (MSTE)\newline
+
+        \item We compute symmetric MSTE for $10^6 \leq \rm{Ra}\leq 10^9$
+
+    \end{itemize}
+\end{frame}

### 2021-12-02 plot_flow.py

@@ -20,7 +20,133 @@ Prandtl = 1.
 Rayleigh = 1e8
 
 # Create bases and domain
-Nx, Nz = 32, 32
+Nx, Nz = 128, 128
+x_basis = de.Fourier('x', Nx, interval=(0, Lx), dealias=3/2)
+z_basis = de.Chebyshev('z', Nz, interval=(-Lz/2, Lz/2), dealias=3/2)
+domain = de.Domain([x_basis, z_basis], grid_dtype=np.float64)
+
+# 2D Boussinesq hydrodynamics
+problem = de.IVP(domain, variables=['p','b','u','w','bz','uz','wz'])
+problem.meta['p','b','u','w']['z']['dirichlet'] = True
+problem.parameters['P'] = (Rayleigh * Prandtl)**(-1/2)
+problem.parameters['R'] = (Rayleigh / Prandtl)**(-1/2)
+problem.parameters['F'] = F = 1
+problem.parameters['Lx'] = Lx
+problem.add_equation("dx(u) + wz = 0")
+problem.add_equation("dt(b) - P*(dx(dx(b)) + dz(bz)) - F*w       = -(u*dx(b) + w*bz)")
+problem.add_equation("dt(u) - R*(dx(dx(u)) + dz(uz)) + dx(p)     = -(u*dx(u) + w*uz)")
+problem.add_equation("dt(w) - R*(dx(dx(w)) + dz(wz)) + dz(p) - b = -(u*dx(w) + w*wz)")
+problem.add_equation("bz - dz(b) = 0")
+problem.add_equation("uz - dz(u) = 0")
+problem.add_equation("wz - dz(w) = 0")
+problem.add_bc("left(b) = 0")
+problem.add_bc("left(u) = 0")
+problem.add_bc("left(w) = 0")
+problem.add_bc("right(b) = 0")
+problem.add_bc("right(u) = 0")
+problem.add_bc("right(w) = 0", condition="(nx != 0)")
+problem.add_bc("right(p) = 0", condition="(nx == 0)")
+
+# Build solver
+solver = problem.build_solver(de.timesteppers.RK222)
+logger.info('Solver built')
+
+path = os.path.dirname(os.path.abspath(__file__)) + '/RA1E8/results_conv1'
+iteration = 9228
+iteration_path = path + '/Iteration'+str(iteration)
[…]
